### 2019-12-24 paper/paper.tex
Incomplete implementation of conditional independence

\documentclass{article}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{amsmath}

\author{Paulius Dilkas}
\title{Using Constraint Programming to Generate Random Logic Programs}

\begin{document}
\maketitle

\section{TODO}

\begin{itemize}
\item Show that the set of all ProbLog programs is equal to the set of programs
  I can generate (alternatively, show that, given any ProbLog program, there are
  parameter values high enough to generate it).
\item Given fixed parameters, use combinatorial arguments to calculate how many
  different programs there are and check that I'm generating the same number.
\end{itemize}

Both determined $\implies$ fail(). Both determined but at least is one masked by
a (probable/determined) mask $\implies$ nothing. One determined $\implies$ the
other one cannot exist.

\section{The Independence Constraint}

A dependency is an algebraic data type that is either determined (in which case
it holds only the index of the predicate) or undetermined (in which case it also
holds the indices of the source and target vertices, corresponding to the edge
responsible for making the dependency undetermined).

\begin{algorithm}
  \SetKwFunction{getDependencies}{getDependencies}
  \SetKwFunction{isDetermined}{isDetermined}
  \SetKwFunction{fail}{fail}
  \SetKwFunction{removeValue}{removeValue}
  \SetKwData{predicate}{predicate}
  \SetKwData{source}{source}
  \SetKwData{target}{target}
  \KwData{predicates $p_1$, $p_2$; adjacency matrix $\mathbf{A}$}
  \For{$(d_1, d_2) \in \getDependencies{$p_1$} \times
    \getDependencies{$p_2$}$ s.t. $d_1.\predicate = d_2.\predicate$}{
    \If{$d_1$.\isDetermined{} {\bf and} $d_2$.\isDetermined{}}{
      \fail{}\;
    }
    \uIf{$d_1$.\isDetermined{}}{
      $\mathbf{A}[d_2.\source][d_2.\target]$.\removeValue{$1$}\;
    }
    \ElseIf{$d_2$.\isDetermined{}}{
      $\mathbf{A}[d_1.\source][d_1.\target]$.\removeValue{$1$}\;
    }
  }
  \caption{Propagation}
\end{algorithm}

\begin{algorithm}
  \SetKwFunction{getDependencies}{getDependencies}
  \SetKwFunction{isDetermined}{isDetermined}
  \SetKwData{predicate}{predicate}
  \KwData{predicates $p_1$, $p_2$}
  $D \gets \{ (d_1, d_2) \in \getDependencies{$p_1$} \times
  \getDependencies{$p_2$} \mid d_1.\predicate = d_2.\predicate \}$\;
  \If{$\{ (d_1, d_2) \in D \mid d_1.\isDetermined{}, d_2.\isDetermined{} \} \ne
    \emptyset$}{
    \Return{FALSE}\;
  }
  \If{$D = \emptyset$}{
    \Return{TRUE}\;
  }
  \Return{UNDEFINED}\;
  \caption{Entailment}
\end{algorithm}

\begin{algorithm}
  \SetKwData{edgeExists}{edgeExists}
  \SetKwData{predicate}{predicate}
  \SetKwData{source}{source}
  \SetKwData{target}{target}
  \SetKwFunction{isDetermined}{isDetermined}
  \SetKwFunction{getDependencies}{getDependencies}
  \SetKwProg{Fn}{Function}{:}{}
  \KwData{an $n \times n$ adjacency matrix $\mathbf{A}$}
  \Fn{\getDependencies{$p$}} {
    $D \gets \{ p \}$\;
    \Repeat{$D' = D$}{
      $D' \gets D$\;
      \For{$d \in D$}{
        \For{$i \gets 1$ \KwTo $n$}{
          $\edgeExists \gets \mathbf{A}[i][d.\predicate] = \{ 1 \}$\;
          \uIf{$\edgeExists$ {\bf and} $d$.\isDetermined{}}{
            $D' \gets D' \cup \{ i \}$\;
          }
          \uElseIf{$\edgeExists$ {\bf and not} $d$.\isDetermined{}}{
            $D' \gets D' \cup \{ (i, d.\source, d.\target) \}$\;
          }
          \ElseIf{$|\mathbf{A}[i][d.\predicate]| > 1$ {\bf and} $d$.\isDetermined{}}{
            $D' \gets D' \cup \{ (i, i, d.\predicate) \}$\;
          }
        }
      }
    }
    \Return{$D$}\;
  }
  \caption{Computing the dependencies of a predicate}
\end{algorithm}

\section{Conditional Independence}

\begin{algorithm}
  \SetKwProg{Fn}{Function}{:}{}
  \SetKwFunction{potentialRoots}{potentialRoots}
  \SetKwFunction{getTreeValues}{getTreeValues}
  \SetKwFunction{getTreeStructureDomainValues}{getTreeStructureDomainValues}
  \SetKwData{clause}{clause}
  \KwData{connective $c$, a set of predicates $P$}
  \Fn{\potentialRoots{\clause, $i$}} {
    $R \gets \emptyset$\;
    $V \gets \clause.\getTreeValues{$i$}$\;
    \For{$v \in V$}{
      \uIf{$v = c$}{
        $R \gets R \cup \{ (i, |V| = 1) \}$\;
      }
      \ElseIf{$v \in P$}{
        $R' \gets \clause.\getTreeStructureDomainValues{$i$}$\;
        $R \gets R \cup \{ (r, |R'| = 1) \mid r \in R' \}$\;
      }
    }
    \Return{$R$}\;
  }
  \caption{Potential root nodes of the required expression, assuming that the
    node at index $i$ is part of the expression}
\end{algorithm}

\end{document}

### 2019-12-24 src/GeneratePrograms.java

@@ -15,8 +15,8 @@ class GeneratePrograms {
 
     private static final int NUM_SOLUTIONS = 10000;
     private static final int MAX_NUM_NODES = 5;
-    private static final String[] PREDICATES = {"p(X)", "q(X)", "r(X)", "s(X)"};
-    private static final int MAX_NUM_CLAUSES = 4;
+    static final String[] PREDICATES = {"p(X)", "q(X)", "r(X)", "s(X)"};
+    private static final int MAX_NUM_CLAUSES = 5;
     private static final boolean FORBID_ALL_CYCLES = false;
     private static final double[] PROBABILITIES = {0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9,
             1, 1, 1, 1, 1, 1}; // let's make probability 1 a bit more likely
@@ -50,9 +50,10 @@ class GeneratePrograms {
 
         model.sort(clauseAssignments, clauseAssignments).post();
 
-        // Each possible value (< PREDICATES.length) should be mentioned at least once
         IntVar numDisabledClauses = model.intVar(0, MAX_NUM_CLAUSES - PREDICATES.length);
         model.count(PREDICATES.length, clauseAssignments, numDisabledClauses).post();
+
+        // Each possible value (< PREDICATES.length) should be mentioned at least once
         IntVar numDistinctValues = model.intVar(PREDICATES.length, PREDICATES.length + 1);
         model.nValues(clauseAssignments, numDistinctValues).post();
 
@@ -88,7 +89,7 @@ class GeneratePrograms {
                 Constraint[] clausesAssignedToJHaveNoI = new Constraint[clauses.length];
                 for (int k = 0; k < clauses.length; k++) {
                     Constraint notAssignedToJ = model.arithm(clauseAssignments[k], "!=", j);
-                    Constraint hasNoI = model.count(i + Clause.countConstantValues(),
+                    Constraint hasNoI = model.count(i + Token.values().length,
                             clauses[k].getTreeValues(), zero);
                     clausesAssignedToJHaveNoI[k] = model.or(notAssignedToJ, hasNoI);
                 }
@@ -106,13 +107,18 @@ class GeneratePrograms {
         model.arithm(clauseAssignments[0], "=", 0).post();
         IntVar[] treeStructure = clauses[0].getTreeStructure();
         IntVar[] treeValues = clauses[0].getTreeValues();
-        model.arithm(treeValues[0], "=", 2).post();
+        model.arithm(treeValues[0], "=", 1).post();
[…]

### 2019-12-24 src/IndependencePropagator.java

@@ -14,11 +14,28 @@ class IndependencePropagator extends Propagator<IntVar> {
     private int predicate1;
     private int predicate2;
 
+    // Fields specific to conditional independence
+    private IntVar[] clauseAssignments;
+    private Clause[] clauses;
+    private Mask mask;
+
     IndependencePropagator(IntVar[][] adjacencyMatrix, int predicate1, int predicate2) {
         super(ArrayUtils.flatten(adjacencyMatrix));
         this.adjacencyMatrix = adjacencyMatrix;
         this.predicate1 = predicate1;
         this.predicate2 = predicate2;
+    }
+
+    IndependencePropagator(IntVar[][] adjacencyMatrix, IntVar[] clauseAssignments, Clause[] clauses,
+                           int predicate1, int predicate2,  Mask mask) {
+        super(ArrayUtils.concat(ArrayUtils.flatten(adjacencyMatrix),
+                NegativeCyclePropagator.constructDecisionVariables(clauseAssignments, clauses)));
+        this.adjacencyMatrix = adjacencyMatrix;
+        this.predicate1 = predicate1;
+        this.predicate2 = predicate2;
+        this.clauseAssignments = clauseAssignments;
+        this.clauses = clauses;
+        this.mask = mask;
     }
 
     @Override
@@ -31,15 +48,18 @@ class IndependencePropagator extends Propagator<IntVar> {
                     if (dependency1.isDetermined() && dependency2.isDetermined())
                         fails();
                     if (dependency1.isDetermined()) {
-                        adjacencyMatrix[dependency2.getSource()][dependency2.getTarget()].removeValue(1, this);
+                        adjacencyMatrix[dependency2.getSource()][dependency2.getTarget()].removeValue(1,
+                                this);
                     } else if (dependency2.isDetermined()) {
-                        adjacencyMatrix[dependency1.getSource()][dependency1.getTarget()].removeValue(1, this);
+                        adjacencyMatrix[dependency1.getSource()][dependency1.getTarget()].removeValue(1,
+                                this);
                     }
                 }
             }
         }
     }
 
+    // TODO: this could be improved (see the pseudocode)
     @Override
     public ESat isEntailed() {
         Set<Dependency> dependencies1 = getDependencies(predicate1);
@@ -74,7 +94,19 @@ class IndependencePropagator extends Propagator<IntVar> {
         while (true) {
             Set<Dependency> newDependencies = new HashSet<>();
             for (Dependency dependency : dependencies) {
+
[…]

### 2019-12-24 src/Mask.java

@@ -1,0 +1,92 @@
+import org.chocosolver.solver.variables.IntVar;
+import org.chocosolver.util.iterators.DisposableValueIterator;
+
+import java.util.*;
+
+/** An expression of the form a /\ b or a \/ b for some predicates a and b. */
+class Mask {
+
+    private Token connective;
+    private List<Integer> predicates;
+
+    Mask(Token connective, List<Integer> predicates) {
+        this.connective = connective;
+        this.predicates = predicates;
+    }
+
+    /** Return the set of indices where the head of the AND/OR expression could be, according to the information at
+     * index `index' (which could be the head or one of the elements inside the AND/OR expression). */
+    private Set<PotentialValue> potentialRoots(Clause clause, int index) {
+        IntVar treeValue = clause.getTreeValues()[index];
+        DisposableValueIterator it = treeValue.getValueIterator(true);
+        Set<PotentialValue> possibleMasks = new HashSet<>();
+        while ( it.hasNext()) {
+            int value = it.next();
+            if (value == connective.ordinal()) {
+                possibleMasks.add(new PotentialValue(index, treeValue.getDomainSize() == 1));
+            } else if (predicates.contains(value)) {
+                List<Integer> potentialHeads = clause.getTreeStructureDomainValues(index);
+                if (potentialHeads.size() == 1) {
+                    possibleMasks.add(new PotentialValue(potentialHeads.get(0), true));
+                } else {
+                    for (int h : potentialHeads)
+                        possibleMasks.add(new PotentialValue(h, false));
+                }
+            }
+        }
+        it.dispose();
+        return possibleMasks;
+    }
+
+    /** Return a list of size GeneratePrograms.PREDICATES.length of boolean values. True means that the clause's
+     * dependence on that variable has been 'masked', i.e., is no longer relevant. */
+    private void markInstances(Clause clause, MaskValue[] masked) {
+        IntVar[] structure = clause.getTreeStructure();
+        IntVar[] values = clause.getTreeValues();
+
+        List<Set<PotentialPredicate>> predicatesPerMask = new ArrayList<>();
+        for (int i = 0; i < masked.length; i++)
+            predicatesPerMask.add(new HashSet<>());
+        List<Set<PotentialValue>> masksPerIndex = new ArrayList<>();
+        for (int i = 0; i < structure.length; i++) {
+            Set<PotentialValue> iMasks = potentialRoots(clause, i);
+            masksPerIndex.add(iMasks);
[…]

### 2019-12-24 src/MaskValue.java

@@ -1,0 +1,4 @@
+public enum MaskValue {
+    UNMASKED, POTENTIALLY_MASKED, MASKED
+    // TODO: upgradeTo(value): if this.value < value, this.value = value
+}

### 2019-12-24 src/NegativeCyclePropagator.java

@@ -16,7 +16,7 @@ class NegativeCyclePropagator extends Propagator<IntVar> {
     private boolean forbidAllCycles;
     private List<List<SignedPredicate>> adjacencyList;
 
-    private static IntVar[] constructDecisionVariables(IntVar[] clauseAssignments, Clause[] clauses) {
+    static IntVar[] constructDecisionVariables(IntVar[] clauseAssignments, Clause[] clauses) {
         IntVar[] decisionVariables = clauseAssignments;
         for (Clause clause : clauses)
             decisionVariables = ArrayUtils.concat(decisionVariables, clause.getDecisionVariables());

### 2019-12-24 src/PotentialPredicate.java

@@ -1,0 +1,17 @@
+import java.util.List;
+
+class PotentialPredicate {
+
+    private boolean[] compatible;
+    private boolean determined;
+
+    PotentialPredicate(List<Integer> domainValues, List<Integer> predicatesOfInterest) {
+        compatible = new boolean[predicatesOfInterest.size()];
+        determined = domainValues.size() == 1;
+        for (int value : domainValues) {
+            int index = predicatesOfInterest.indexOf(value);
+            if (index > -1)
+                compatible[index] = true;
+        }
+    }
+}

### 2019-12-24 src/PotentialValue.java

@@ -1,0 +1,19 @@
+class PotentialValue {
+
+    private int value;
+    private boolean determined;
+
+    PotentialValue(int value, boolean determined) {
+        this.value = value;
+        this.determined = determined;
+    }
+
+    boolean isDetermined() {
+        return determined;
+    }
+
+    public int getValue() {
+        return value;
+    }
+
+}

### 2019-12-24 src/Token.java

@@ -1,0 +1,29 @@
+public enum Token {
+    NOT {
+        @Override
+        public String toString() {
+            return "\\+";
+        }
+    },
+
+    AND {
+        @Override
+        public String toString() {
+            return ",";
+        }
+    },
+
+    OR {
+        @Override
+        public String toString() {
+            return ";";
+        }
+    },
+
+    TRUE {
+        @Override
+        public String toString() {
+            return "";
+        }
+    }
+}

### 2019-12-24 paper/paper.tex
More restructuring

@@
 
+\section{Introduction}
+
+Motivation:
+\begin{itemize}
+\item Generating random programs that generate random data.
+  %For example, enforcing that the decision is independent of gender.
+\item Learning: how this can be used for (targeted) learning, when (atomic)
+  probabilities can be assigned based on counting and we can have extra
+  constraints. A more primitive angle: generate structures, learn weights.
+\end{itemize}
+
 \section{TODO}
@@
 \begin{itemize}
+\item Support for constants and multiple variables.
+  \begin{itemize}
+  \item Each clause is defined for each predicate with standard variable names
+    (X, Y, etc.).
+  \item There is a list of constants and a list of predicates with their
+    arities. Maybe also a list of variables.
+  \end{itemize}
+\item Make negative cycle detection use the graph representation.
+\item Finish the propagation algorithm for conditional independence. The
+  propagation algorithm for independence is extended with masks that are either
+  potential or definite. Masking happens in two stages: first, we mask
+  expressions within formulas, and then predicates. Masking algorithm uses an
+  algorithm for perfect bipartite matching.
 \item Show that the set of all ProbLog programs is equal to the set of programs

### 2019-12-24 src/MaskValue.java

@@ -1,4 +1,0 @@
-public enum MaskValue {
-    UNMASKED, POTENTIALLY_MASKED, MASKED
-    // TODO: upgradeTo(value): if this.value < value, this.value = value
-}

### 2019-12-24 src/main/GeneratePrograms.java

@@ -1,7 +1,14 @@
+package main;
+
 import java.io.BufferedWriter;
 import java.io.FileWriter;
 import java.io.IOException;
+import java.util.LinkedList;
+import java.util.List;
 
+import main.Clause;
+import main.Mask;
+import main.Token;
 import org.chocosolver.solver.Model;
 import org.chocosolver.solver.Solver;
 import org.chocosolver.solver.constraints.Constraint;
@@ -116,7 +123,10 @@ class GeneratePrograms {
         model.arithm(treeValues[2], "=", 6).post();
         new Constraint("q and r are independent",
                 new IndependencePropagator(adjacencyMatrix, 1, 2)).post();
-        Mask qAndR = new Mask(Token.AND, 1, 2);
+        List<Integer> predicates = new LinkedList<>();
+        predicates.add(1);
+        predicates.add(2);
+        Mask qAndR = new Mask(Token.AND, predicates);
         new Constraint("p is independent of q given q and r", new IndependencePropagator(adjacencyMatrix,
                 clauseAssignments, clauses, 0, 1, qAndR)).post();
         new Constraint("p is independent of r given q and r", new IndependencePropagator(adjacencyMatrix,

### 2019-12-24 src/main/PotentialValue.java

@@ -1,3 +1,5 @@
+package main;
+
 class PotentialValue {
 
     private int value;

### 2019-12-24 src/propagators/IndependencePropagator.java

@@ -1,12 +1,13 @@
 package propagators;
 
+import main.Clause;
+import main.Mask;
+import main.Possibility;
 import org.chocosolver.solver.constraints.Propagator;
 import org.chocosolver.solver.exception.ContradictionException;
 import org.chocosolver.solver.variables.IntVar;
 import org.chocosolver.util.ESat;
 import org.chocosolver.util.tools.ArrayUtils;
-import propagators.Dependency;
-import propagators.NegativeCyclePropagator;
 
 import java.util.HashSet;
 import java.util.Set;
@@ -23,14 +24,14 @@ public class IndependencePropagator extends Propagator<IntVar> {
     private Clause[] clauses;
     private Mask mask;
 
-    IndependencePropagator(IntVar[][] adjacencyMatrix, int predicate1, int predicate2) {
+    public IndependencePropagator(IntVar[][] adjacencyMatrix, int predicate1, int predicate2) {
         super(ArrayUtils.flatten(adjacencyMatrix));
         this.adjacencyMatrix = adjacencyMatrix;
         this.predicate1 = predicate1;
         this.predicate2 = predicate2;
     }
 
-    IndependencePropagator(IntVar[][] adjacencyMatrix, IntVar[] clauseAssignments, Clause[] clauses,
+    public IndependencePropagator(IntVar[][] adjacencyMatrix, IntVar[] clauseAssignments, Clause[] clauses,
                            int predicate1, int predicate2,  Mask mask) {
         super(ArrayUtils.concat(ArrayUtils.flatten(adjacencyMatrix),
                 NegativeCyclePropagator.constructDecisionVariables(clauseAssignments, clauses)));
@@ -100,17 +101,17 @@ public class IndependencePropagator extends Propagator<IntVar> {
             for (Dependency dependency : dependencies) {
 
                 // The only difference between conditional and unconditional independence
-                MaskValue[] masked = new MaskValue[adjacencyMatrix.length];
+                /*Possibility[] masked = new Possibility[adjacencyMatrix.length];
                 if (mask != null) {
                     masked = mask.applyMask(clauses, clauseAssignments, dependency.getPredicate());
                 } else {
                     for (int i = 0; i < adjacencyMatrix.length; i++)
-                        masked[i] = MaskValue.UNMASKED;
-                }
+                        masked[i] = Possibility.NO;
+                }*/
 
                 for (int i = 0; i < adjacencyMatrix.length; i++) {
-                    if (masked[i] == MaskValue.MASKED)
[…]

### 2019-12-25 src/main/Clause.java
Support for variables, constants, and higher arities

@@ -8,15 +8,78 @@ import org.chocosolver.util.tools.ArrayUtils;
 import propagators.Sign;
 import propagators.SignedPredicate;
 
+import java.util.Arrays;
 import java.util.LinkedList;
 import java.util.List;
 
 public class Clause {
 
     private int maxNumNodes;
-    private String[] values;
     private IntVar[] treeStructure;
-    private IntVar[] treeValues;
+    private Atom[] treeValues;
+
+    public Clause(Model model, IntVar assignment, int maxNumNodes) {
+        this.maxNumNodes = maxNumNodes;
+
+        IntVar numNodes = model.intVar(1, maxNumNodes);
+        treeStructure = model.intVarArray(maxNumNodes, 0, maxNumNodes - 1);
+        treeValues = new Atom[maxNumNodes];
+        for (int i = 0; i < maxNumNodes; i++)
+            treeValues[i] = new Atom(model);
+
+        // Tree structure
+        IntVar numTrees = model.intVar(1, maxNumNodes);
+        model.tree(treeStructure, numTrees).post();
+        model.arithm(treeStructure[0], "=", 0).post(); // the 0th element is always a root
+
+        model.arithm(numTrees, "+", numNodes, "=", maxNumNodes + 1).post();
+        model.sort(treeStructure, treeStructure).post();
+
+        for (int i = 0; i < maxNumNodes; i++) {
+            Constraint outsideScope = model.arithm(numNodes, "<=", i);
+            Constraint mustBeALoop = model.arithm(treeStructure[i], "=", i);
+            Constraint fixValue = model.arithm(treeValues[i].getPredicate(), "=", Token.TRUE.ordinal());
+            Constraint isRestricted = model.arithm(treeStructure[i], "<", numNodes);
+            model.ifThenElse(outsideScope, model.and(mustBeALoop, fixValue), isRestricted);
+        }
+
+        // Tree values
+        for (int i = 0; i < maxNumNodes; i++) {
+            IntVar exactlyZero = model.intVar(0);
+            IntVar exactlyOne = model.intVar(1);
+            IntVar moreThanOne = model.intVar(2, Math.max(maxNumNodes, 2));
+
+            IntVar[] structureWithoutI = new IntVar[maxNumNodes - 1];
+            for (int j = 0; j < i; j++)
+                structureWithoutI[j] = treeStructure[j];
+            for (int j = i + 1; j < maxNumNodes; j++)
[…]

### 2019-12-25 src/main/GeneratePrograms.java

@@ -3,32 +3,36 @@ package main;
 import java.io.BufferedWriter;
 import java.io.FileWriter;
 import java.io.IOException;
-import java.util.LinkedList;
-import java.util.List;
+import java.util.Arrays;
 
-import main.Clause;
-import main.Mask;
-import main.Token;
 import org.chocosolver.solver.Model;
 import org.chocosolver.solver.Solver;
 import org.chocosolver.solver.constraints.Constraint;
+import org.chocosolver.solver.constraints.extension.Tuples;
 import org.chocosolver.solver.search.strategy.Search;
 import org.chocosolver.solver.search.strategy.selectors.values.IntDomainRandom;
 import org.chocosolver.solver.search.strategy.selectors.variables.Random;
 import org.chocosolver.solver.variables.IntVar;
 import org.chocosolver.util.tools.ArrayUtils;
-import propagators.IndependencePropagator;
 import propagators.NegativeCyclePropagator;
 
 class GeneratePrograms {
 
+    private static final String DIRECTORY = "../programs/";
     private static final int NUM_SOLUTIONS = 10000;
-    private static final int MAX_NUM_NODES = 5;
-    static final String[] PREDICATES = {"p(X)", "q(X)", "r(X)", "s(X)"};
-    private static final int MAX_NUM_CLAUSES = 5;
+    private static final int MAX_NUM_NODES = 3;
+    private static final int MAX_NUM_CLAUSES = 2;
     private static final boolean FORBID_ALL_CYCLES = false;
     private static final double[] PROBABILITIES = {0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9,
             1, 1, 1, 1, 1, 1}; // let's make probability 1 a bit more likely
+
+    static final String[] PREDICATES = {"p", "q"};
+    static final int[] ARITIES = {1, 2};
+    static final String[] VARIABLES = {"X", "Y"};
+    static final String[] CONSTANTS = {};
+    static final int MAX_ARITY = Arrays.stream(ARITIES).max().getAsInt();
+
+    static Tuples arities;
 
     private static Model model;
     private static IntVar[] clauseAssignments;
@@ -49,9 +53,16 @@ class GeneratePrograms {
         if (clause.equals("T."))
             return probabilityString + PREDICATES[predicate] + ".\n";
         return probabilityString + PREDICATES[predicate] + " :- " + clause + "\n";
+        // TODO: will need to update, once I know how I want to represent heads of clauses
     }
 
[…]

### 2019-12-25 src/main/PotentialMask.java

@@ -1,20 +1,0 @@
-package main;
-
-import main.Possibility;
-
-class PotentialMask {
-    private Possibility mask;
-
-    PotentialMask(Possibility mask) {
-        this.mask = mask;
-    }
-
-    Possibility getMask() {
-        return mask;
-    }
-
-    void upgradeTo(Possibility newValue) {
-        if (mask.ordinal() < newValue.ordinal())
-            mask = newValue;
-    }
-}

### 2019-12-26 paper/paper.tex
Support for variables, constants, and higher arities
Full support for variables
A bit of writing

@@
 \usepackage{amsmath}
+\usepackage{amsthm}
+\usepackage{amssymb}
+
+\newtheorem{constraint}{Constraint}
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}
+
+\newcommand{\variable}[1]{\texttt{\textup{#1}}}
 
@@
   constraints. A more primitive angle: generate structures, learn weights.
+\item Describe how the trees work with many examples.
+\item Have a 'Constraint' environment.
 \end{itemize}
@@
   different programs there are and check that I'm generating the same number.
+\item Formal definition (here and in the predicate invention paper): two
+  predicates are independent if all of their groundings are independent.
+\item Describe: entailment checking for cycles and negative cycles.
 \end{itemize}
@@
 other one cannot exist.
+
+\section{Parameters}
+
+Parameters:
+\begin{itemize}
+\item maximum number of solutions
+\item \variable{maxNumNodes} (in the tree representation of a clause)
+\item list of predicates with their variables
+\item maximum number of clauses
+\item option to forbid all cycles or just negative cycles
+\item list of probabilities that are randomly assigned to clauses: $\{ 0.1,
+  0.2, \dots, 0.9, 1, 1, 1, 1, 1, 1 \}$
+\end{itemize}
+
+Decision variables: % TODO: rename these things
+% TODO: specify the decision variables inside clauses and their heads
+\begin{itemize}
+\item \variable{IntVar[] clauseAssignments}: a predicate or disabled
+\item \variable{Clause[] clauses}
+\item \variable{Head[] clauseHeads}
+\end{itemize}
+
+\section{General Constraints}
+
+\begin{constraint}[Each predicate gets at least one clause]
+  \variable{numDisabledClauses} is defined by a \variable{count} constraint.
+  \[
+    \variable{numDistinctValues} =
+    \begin{cases}
+      \variable{numPredicates} + 1 & \text{if } \variable{numDisabledValues} > 0 \\
+      \variable{numPredicates} & \text{otherwise}
+    \end{cases}
+  \]
+  (also constrained using the \variable{nValues} constraint).
+\end{constraint}
+
+\begin{constraint}[\variable{clauseAssignments} are sorted]
+  \[
+    \variable{clauseAssignments}[i-1] = \variable{clauseAssignments}[i] \implies
+    \variable{clause}[i-1] \preceq \variable{clause}[i].
+  \]
+\end{constraint}
+
+\section{Bodies of Clauses}
+
+\begin{definition}
+  The body of a clause is defined by:
+  \begin{itemize}
+  \item \variable{IntVar[] treeStructure}
+    \begin{itemize}
+    \item $\texttt{treeStructure}[i] = i$: the $i$-th node is a root.
+    \item $\texttt{treeStructure}[i] = j$: the $i$-th node's parent is node $j$.
+    \end{itemize}
+  \item \variable{IntVar[] treeValues}: $\neg$, $\land$, $\lor$, $\top$, and any
+    predefined predicates with variables.
+  \end{itemize}
+\end{definition}
+% TODO: examples
+% TODO: update the info on treeValues
+
+Auxiliary variables: $\variable{numNodes}, \variable{numTrees} \in \{ 1, \dots,
+\variable{maxNumNodes} \}$.
+
+\subsection{Constraints}
+
+\begin{constraint}
+  \variable{treeStructure} represents \variable{numTrees} trees.
+\end{constraint}
+
+\begin{constraint}
+  $\variable{treeStructure}[0] = 0$.
+\end{constraint}
+
+\begin{constraint}
+  $\variable{numTrees} + \variable{numNodes} = \variable{maxNumNodes} + 1$.
+\end{constraint}
+
+\begin{constraint}
+  \variable{treeStructure} is sorted.
+\end{constraint}
+
+\begin{constraint}
+  For $i = 0, \dots, \variable{maxNumNodes} - 1$, if $\variable{numNodes} \le
+  i$, then
+  \[
+    \variable{treeStructure}[i] = i \quad \text{and} \quad
+    \variable{treeValues}[i] = \top,
+  \]
+  else
+  \[
+    \variable{treeStructure}[i] < \variable{numNodes}.
+  \]
+\end{constraint}
+
+\begin{constraint}
+  For $i = 0, \dots, \variable{maxNumNodes} - 1$,
+  \begin{itemize}
+  \item has 0 children $\iff$ $\variable{treeValues}[i]$ is a predicate;
+  \item has 1 child $\iff$ $\variable{treeValues}[i] = \neg$;
+  \item has $>1$ child $\iff$ $\variable{treeValues}[i] \in \{ \land, \lor \}$.
+  \end{itemize}
+\end{constraint}
+
+\begin{constraint}
+  For $i = 0, \dots, \variable{maxNumNodes} - 1$,
+  \[
+    \variable{treeStructure}[i] \ne i \implies \variable{treeValues}[i] \ne
+    \top.
+  \]
+\end{constraint}
+
+If the clause should be disabled, $\variable{numNodes} = 1$ and
+$\variable{treeValues}[0] = \top$.
+
+\begin{constraint}
+  Adjacency matrix representation:
+  \[
+    A[i][j] = 0 \iff \nexists k: \variable{clauseAssignments}[k] = j \text{ and }
+    i \in \variable{clauses}[k].\variable{treeValues}
+  \]
+\end{constraint}
 
@@
 responsible for making the dependency undetermined).
+
+Propagation for independence:
+\begin{itemize}
+\item Two types of dependencies: determined and
+  one-undetermined-edge-away-from-being-determined.
+\item Look up the dependencies of both predicates. For each pair of
+  matching dependencies:
+  \begin{itemize}
+  \item If both are determined, fail.
+  \item If one is determined, the selected edge of the other must not
+    exist.
+  \end{itemize}
+\end{itemize}
 
@@
 
-\section{Conditional Independence}
+% \section{Conditional Independence}
 
-\begin{algorithm}
-  \SetKwProg{Fn}{Function}{:}{}
-  \SetKwFunction{potentialRoots}{potentialRoots}
-  \SetKwFunction{getTreeValues}{getTreeValues}
-  \SetKwFunction{getTreeStructureDomainValues}{getTreeStructureDomainValues}
-  \SetKwData{clause}{clause}
-  \KwData{connective $c$, a set of predicates $P$}
-  \Fn{\potentialRoots{\clause, $i$}} {
-    $R \gets \emptyset$\;
-    $V \gets \clause.\getTreeValues{$i$}$\;
-    \For{$v \in V$}{
-      \uIf{$v = c$}{
-        $R \gets R \cup \{ (i, |V| = 1) \}$\;
-      }
-      \ElseIf{$v \in P$}{
-        $R' \gets \clause.\getTreeStructureDomainValues{$i$}$\;
-        $R \gets R \cup \{ (r, |R'| = 1) \mid r \in R' \}$\;
-      }
-    }
-    \Return{$R$}\;
-  }
-  \caption{Potential root nodes of the required expression, assuming that the
-    node at index $i$ is part of the expression}
-\end{algorithm}
+% \begin{algorithm}
+%   \SetKwProg{Fn}{Function}{:}{}
+%   \SetKwFunction{potentialRoots}{potentialRoots}
+%   \SetKwFunction{getTreeValues}{getTreeValues}
+%   \SetKwFunction{getTreeStructureDomainValues}{getTreeStructureDomainValues}
+%   \SetKwData{clause}{clause}
+%   \KwData{connective $c$, a set of predicates $P$}
+%   \Fn{\potentialRoots{\clause, $i$}} {
+%     $R \gets \emptyset$\;
+%     $V \gets \clause.\getTreeValues{$i$}$\;
+%     \For{$v \in V$}{
+%       \uIf{$v = c$}{
+%         $R \gets R \cup \{ (i, |V| = 1) \}$\;
+%       }
+%       \ElseIf{$v \in P$}{
+%         $R' \gets \clause.\getTreeStructureDomainValues{$i$}$\;
+%         $R \gets R \cup \{ (r, |R'| = 1) \mid r \in R' \}$\;
+%       }
+%     }
+%     \Return{$R$}\;
+%   }
+%   \caption{Potential root nodes of the required expression, assuming that the
+%     node at index $i$ is part of the expression}
+% \end{algorithm}
 

### 2019-12-28 paper/paper.tex
Refactoring + one more anti-symmetry constraint

@@
 \newcommand{\variable}[1]{\texttt{\textup{#1}}}
+\newcommand{\predicates}{\mathcal{P}}
+\newcommand{\variables}{\mathcal{V}}
+\newcommand{\constants}{\mathcal{C}}
+\newcommand{\tokens}{\mathcal{T}}
+\newcommand{\arities}{\mathcal{A}}
+\newcommand{\maxArity}{\textsc{max\_arity}}
+\newcommand{\maxNumNodes}{\textsc{max\_num\_nodes}}
+\newcommand{\maxNumClauses}{\textsc{max\_num\_clauses}}
 
 \author{Paulius Dilkas}
-\title{Using Constraint Programming to Generate Random Logic Programs}
+\title{Generating Random Logic Programs Using Constraint Programming}
 
@@
   constraints. A more primitive angle: generate structures, learn weights.
-\item Describe how the trees work with many examples.
-\item Have a 'Constraint' environment.
 \end{itemize}
+
+We will often use $\Box$ as a special domain value to indicate some kind of
+exception.
 
@@
 \begin{itemize}
-\item Support for constants and multiple variables.
-  \begin{itemize}
-  \item Each clause is defined for each predicate with standard variable names
-    (X, Y, etc.).
-  \item There is a list of constants and a list of predicates with their
-    arities. Maybe also a list of variables.
-  \end{itemize}
 \item Make negative cycle detection use the graph representation.
-\item Finish the propagation algorithm for conditional independence. The
-  propagation algorithm for independence is extended with masks that are either
-  potential or definite. Masking happens in two stages: first, we mask
-  expressions within formulas, and then predicates. Masking algorithm uses an
-  algorithm for perfect bipartite matching.
 \item Show that the set of all ProbLog programs is equal to the set of programs
@@
 \item Describe: entailment checking for cycles and negative cycles.
+\item A constraint for logical equivalence.
+\item Rename everything into something more appropriate.
 \end{itemize}
@@
 \item maximum number of solutions
-\item \variable{maxNumNodes} (in the tree representation of a clause)
-\item list of predicates with their variables
-\item maximum number of clauses
+\item \maxNumNodes{} (in the tree representation of a clause)
+\item \maxNumClauses{}
 \item option to forbid all cycles or just negative cycles
-\item list of probabilities that are randomly assigned to clauses: $\{ 0.1,
-  0.2, \dots, 0.9, 1, 1, 1, 1, 1, 1 \}$
+\item a list of probabilities that are randomly assigned to clauses: $\{ 0.1,
+  0.2, \dots, 0.9, 1, 1, 1, 1, 1, 1 \}$.
+\item a list of predicates $\predicates{}$,
+\item a list of their arities $\arities{}$,
+  \begin{itemize}
+  \item $\maxArity{} = \max \arities{}$.
+  \end{itemize}
+\item a list of variables $\variables{}$,
+\item and a list of constants $\constants{}$.
 \end{itemize}
 
-Decision variables: % TODO: rename these things
+We also define $\tokens{} = \{ \neg, \land, \lor, \top \}$.
+
+Decision variables:
 % TODO: specify the decision variables inside clauses and their heads
 \begin{itemize}
-\item \variable{IntVar[] clauseAssignments}: a predicate or disabled
-\item \variable{Clause[] clauses}
-\item \variable{Head[] clauseHeads}
+\item \variable{Body[] bodiesOfClauses}
+\item \variable{Head[] headsOfClauses}: a list of length \maxNumClauses{}
 \end{itemize}
@@
 \begin{constraint}[Each predicate gets at least one clause]
-  \variable{numDisabledClauses} is defined by a \variable{count} constraint.
+  Let $P = \{ h.\variable{predicate} \mid h \in \variable{clauseHeads} \}$. Then
   \[
-    \variable{numDistinctValues} =
+    \variable{nValues}(P) =
     \begin{cases}
-      \variable{numPredicates} + 1 & \text{if } \variable{numDisabledValues} > 0 \\
-      \variable{numPredicates} & \text{otherwise}
+      \variable{numPredicates} + 1 & \text{if } \variable{count}(\Box, P) > 0 \\
+      \variable{numPredicates} & \text{otherwise.}
     \end{cases}
   \]
-  (also constrained using the \variable{nValues} constraint).
 \end{constraint}
 
-\begin{constraint}[\variable{clauseAssignments} are sorted]
+\begin{constraint}
+  Let $\prec$ be any total order defined over bodies of clauses, and let
+  $\preceq$ be its extension with equality (in the same way as $\le$ extends
+  $<$).
   \[
-    \variable{clauseAssignments}[i-1] = \variable{clauseAssignments}[i] \implies
-    \variable{clause}[i-1] \preceq \variable{clause}[i].
+    \variable{headsOfClauses}[i-1].\variable{predicate} =
+    \variable{headsOfClauses}[i].\variable{predicate} \implies
+    \variable{bodiesOfClauses}[i-1] \preceq \variable{bodiesOfClauses}[i].
+  \]
+\end{constraint}
+For example, $\preceq$ can be implemented as \variable{lexLessEq} over the
+decision variables of each body.
+% TODO: might need to include clause heads as well.
+
+\section{Atoms}
+
+\begin{definition}
+  An \emph{atom} is a $\variable{predicate} \in \tokens{} \cup \predicates{}$ and a
+  list of \variable{arguments} of length \maxArity{} in $\variables{} \cup
+  \constants{} \cup \{ \Box \}$, where $\Box$ means the position is either
+  reserved for a variable, or disabled. The atom's \variable{arity} is a number
+  in $[0, \maxArity{}]$ defined by a \variable{table} constraint,
+  according to the \variable{predicate}.
+\end{definition}
+
+\begin{constraint}
+  For $i = 0, \dots, \maxArity{} - 1$,
+  \[
+    i \ge \variable{arity} \implies \variable{arguments}[i] = 0.
   \]
@@
   \begin{itemize}
-  \item \variable{IntVar[] treeStructure}
+  \item \variable{treeStructure}: list of length \maxNumNodes{} with
+    domain $[0, \maxNumNodes{}]$.
     \begin{itemize}
-    \item $\texttt{treeStructure}[i] = i$: the $i$-th node is a root.
-    \item $\texttt{treeStructure}[i] = j$: the $i$-th node's parent is node $j$.
+    \item $\variable{treeStructure}[i] = i$: the $i$-th node is a root.
+    \item $\variable{treeStructure}[i] = j$: the $i$-th node's parent is node $j$.
     \end{itemize}
-  \item \variable{IntVar[] treeValues}: $\neg$, $\land$, $\lor$, $\top$, and any
-    predefined predicates with variables.
+  \item \variable{treeValues}: \maxNumNodes{} atoms.
   \end{itemize}
@@
 % TODO: examples
-% TODO: update the info on treeValues
 
 Auxiliary variables: $\variable{numNodes}, \variable{numTrees} \in \{ 1, \dots,
-\variable{maxNumNodes} \}$.
+\maxNumNodes{} \}$.
 
@@
 \begin{constraint}
-  $\variable{numTrees} + \variable{numNodes} = \variable{maxNumNodes} + 1$.
+  $\variable{numTrees} + \variable{numNodes} = \maxNumNodes{} + 1$.
 \end{constraint}
@@
 \begin{constraint}
-  For $i = 0, \dots, \variable{maxNumNodes} - 1$, if $\variable{numNodes} \le
+  For $i = 0, \dots, \maxNumNodes{} - 1$, if $\variable{numNodes} \le
   i$, then
@@
     \variable{treeStructure}[i] = i \quad \text{and} \quad
-    \variable{treeValues}[i] = \top,
+    \variable{treeValues}[i].\variable{predicate} = \top,
   \]
@@
 \begin{constraint}
-  For $i = 0, \dots, \variable{maxNumNodes} - 1$,
+  For $i = 0, \dots, \maxNumNodes{} - 1$,
   \begin{itemize}
-  \item has 0 children $\iff$ $\variable{treeValues}[i]$ is a predicate;
-  \item has 1 child $\iff$ $\variable{treeValues}[i] = \neg$;
-  \item has $>1$ child $\iff$ $\variable{treeValues}[i] \in \{ \land, \lor \}$.
+  \item has 0 children $\iff$ $\variable{treeValues}[i].\variable{predicate} \in
+    \predicates{}$;
+  \item has 1 child $\iff$ $\variable{treeValues}[i].\variable{predicate} = \neg$;
+  \item has $>1$ child $\iff$ $\variable{treeValues}[i].\variable{predicate} \in
+    \{ \land, \lor \}$.
   \end{itemize}
@@
 \begin{constraint}
-  For $i = 0, \dots, \variable{maxNumNodes} - 1$,
+  For $i = 0, \dots, \maxNumNodes{} - 1$,
   \[
-    \variable{treeStructure}[i] \ne i \implies \variable{treeValues}[i] \ne
-    \top.
+    \variable{treeStructure}[i] \ne i \implies
+    \variable{treeValues}[i].\variable{predicate} \ne \top.
   \]
@@
 If the clause should be disabled, $\variable{numNodes} = 1$ and
-$\variable{treeValues}[0] = \top$.
+$\variable{treeValues}[0].\variable{predicate} = \top$.
 
@@
   Adjacency matrix representation:
+  \begin{align*}
+    A[i][j] = 0 \iff &\nexists k: \variable{headsOfClauses}[k].\variable{predicate} = j \text{ and } \\
+    &i \in \{ a.\variable{predicate} \mid a \in \variable{bodiesOfClauses}[k].\variable{treeValues} \}.
+  \end{align*}
+\end{constraint}
+
+\section{Head of a Clause}
+
+\begin{definition} % TODO: variables are always ordered, constants are not.
+  The \emph{head} of a clause is defined by two lists:
+  \begin{itemize}
+  \item $\variable{predicate} \in \predicates \cup \{ \Box \}$, where $\Box$
+    denotes a disabled clause.
+  \item \variable{variables} of length $|\variables{}|$ and with domain
+    $[0, \maxArity{}]$: how many times each variable appears in the head atom.
+  \item \variable{constants} of length $\maxArity{}$ and with domain
+    $\constants{} \cup \{ \Box \}$, where $\Box$ denotes that the position is
+    reserved for a variable.
+  \end{itemize}
+  We also define the predicate's \variable{arity} using the same
+  \variable{table} constraint.
+\end{definition}
+
+\begin{constraint}
+  For each variable $v \in \variable{variables}$, $v \le \variable{arity}$.
+\end{constraint}
+
+\begin{constraint}
+  For $i = 0, \dots, \maxArity{} - 1$,
   \[
-    A[i][j] = 0 \iff \nexists k: \variable{clauseAssignments}[k] = j \text{ and }
-    i \in \variable{clauses}[k].\variable{treeValues}
+    i \ge \variable{arity} \implies \variable{constants}[i] = 0.
+  \]
+\end{constraint}
+
+\begin{constraint}[Connecting the two lists]
+  $\sum_{v \in \variable{variables}} v = \variable{count}(\Box,
+  \variable{constants}) + \variable{arity} - \maxArity{}$.
+\end{constraint}
+
+In \variable{variables}, all zeros must go after all non-zeros. For example,
+if we have to pick one variable out of two, we must pick the first one.
+\begin{constraint}
+  For $i = 0, \dots, |\variables{}| - 2$, and $j = i + 1, \dots,
+  |\variables{}| - 1$,
+  \[
+    \variable{variables}[i] \ne 0 \quad \text{or} \quad \variable{variables}[j]
+    = 0.
   \]
@@
 
+% Finish the propagation algorithm for conditional independence. The
+%  propagation algorithm for independence is extended with masks that are either
+%  potential or definite. Masking happens in two stages: first, we mask
+%  expressions within formulas, and then predicates. Masking algorithm uses an
+%  algorithm for perfect bipartite matching.
+
 % \begin{algorithm}

### 2019-12-28 src/main/Head.java

@@ -14,6 +14,7 @@ class Head {
     // A map from positions to constants, where 0 means that either that position is disabled or occupied by a variable
     private IntVar[] constants;
 
+    // Auxiliary variables
     private IntVar sumOfVars;
     private IntVar countVariables;
     private IntVar negRemainingArity;
@@ -21,7 +22,6 @@ class Head {
     Head(Model model, IntVar predicate) {
         this.predicate = predicate;
 
-        // TODO: what if the predicate is disabled?
         IntVar indexToTable = model.intOffsetView(predicate, Token.values().length);
         arity = model.intVar(0, GeneratePrograms.MAX_ARITY);
         model.table(indexToTable, arity, GeneratePrograms.arities).post();
@@ -46,6 +46,18 @@ class Head {
         negRemainingArity = model.intVar(-GeneratePrograms.MAX_ARITY, 0);
         model.arithm(negRemainingArity, "=", arity, "-", GeneratePrograms.MAX_ARITY).post();
         model.arithm(sumOfVars, "=", countVariables, "+", negRemainingArity).post();
+
+        // All zeros go after all non-zeros
+        // v[i] = 0 /\ v[j] != 0 => j < i
+        // j < i \/ v[i] != 0 \/ v[j] = 0
+        // For j > i, v[i] != 0 \/ v[j] = 0
+        for (int i = 0; i < variables.length - 1; i++) {
+            for (int j = i + 1; j < variables.length; j++) {
+                Constraint iNotZero = model.arithm(variables[i], "!=", 0);
+                Constraint jIsZero = model.arithm(variables[j], "=", 0);
+                model.or(iNotZero, jIsZero).post();
+            }
+        }
     }
 
     public IntVar[] getDecisionVariables() {

### 2019-12-28 src/main/Mask.java

@@ -18,8 +18,8 @@ public class Mask {
 
     /** Return the set of indices where the head of the AND/OR expression could be, according to the information at
      * index `index' (which could be the head or one of the elements inside the AND/OR expression). */
-    private Set<PotentialValue> potentialRoots(Clause clause, int index) {
-        IntVar treeValue = clause.getTreeValues()[index];
+    private Set<PotentialValue> potentialRoots(Body body, int index) {
+        IntVar treeValue = body.getTreeValues()[index];
         DisposableValueIterator it = treeValue.getValueIterator(true);
         Set<PotentialValue> possibleMasks = new HashSet<>();
         while ( it.hasNext()) {
@@ -27,7 +27,7 @@ public class Mask {
             if (value == connective.ordinal()) {
                 possibleMasks.add(new PotentialValue(index, treeValue.getDomainSize() == 1));
             } else if (predicates.contains(value)) {
-                List<Integer> potentialHeads = clause.getTreeStructureDomainValues(index);
+                List<Integer> potentialHeads = body.getTreeStructureDomainValues(index);
                 if (potentialHeads.size() == 1) {
                     possibleMasks.add(new PotentialValue(potentialHeads.get(0), true));
                 } else {
@@ -42,9 +42,9 @@ public class Mask {
 
     /** Return a list of size GeneratePrograms.PREDICATES.length of boolean values. True means that the clause's
      * dependence on that variable has been 'masked', i.e., is no longer relevant. */
-    private void markInstances(Clause clause, Possibility[] masked) {
-/*        IntVar[] structure = clause.getTreeStructure();
-        IntVar[] values = clause.getTreeValues();
+    private void markInstances(Body body, Possibility[] masked) {
+/*        IntVar[] structure = body.getTreeStructure();
+        IntVar[] values = body.getTreeValues();
         Token[] tokens = Token.values();
 
         // Old stuff
@@ -53,12 +53,12 @@ public class Mask {
             predicatesPerMask.add(new HashSet<>());
         List<Set<PotentialValue>> masksPerIndex = new ArrayList<>();
         for (int i = 0; i < structure.length; i++) {
-            Set<PotentialValue> iMasks = potentialRoots(clause, i);
+            Set<PotentialValue> iMasks = potentialRoots(body, i);
             masksPerIndex.add(iMasks);
             for (PotentialValue mask : iMasks) {
                 if (mask.getValue() == i)
[…]

### 2019-12-28 paper/paper.tex
References + formatting

@@
-\documentclass{article}
-\usepackage[UKenglish]{babel}
-\usepackage[UKenglish]{isodate}
-\usepackage[utf8]{inputenc}
-\usepackage{fullpage}
+\documentclass[runningheads]{llncs}
+\usepackage{graphicx}
+%\usepackage[UKenglish]{babel}
+%\usepackage[UKenglish]{isodate}
+%\usepackage[utf8]{inputenc}
 \usepackage[ruled,vlined]{algorithm2e}
-\usepackage{amsmath}
-\usepackage{amsthm}
 \usepackage{amssymb}
+\usepackage{mathtools}
+\usepackage[capitalise]{cleveref}
 
 \newtheorem{constraint}{Constraint}
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
 
@@
 \newcommand{\arities}{\mathcal{A}}
-\newcommand{\maxArity}{\textsc{max\_arity}}
-\newcommand{\maxNumNodes}{\textsc{max\_num\_nodes}}
-\newcommand{\maxNumClauses}{\textsc{max\_num\_clauses}}
-
-\author{Paulius Dilkas}
-\title{Generating Random Logic Programs Using Constraint Programming}
+\newcommand{\maxArity}{\mathcal{M}_{\mathcal{A}}}
+\newcommand{\maxNumNodes}{\mathcal{M}_{\mathcal{N}}}
+\newcommand{\maxNumClauses}{\mathcal{M}_{\mathcal{C}}}
 
 \begin{document}
+
+\title{Generating Random Logic Programs Using Constraint Programming}
+\author{Paulius Dilkas\orcidID{0000-1111-2222-3333}}
+\authorrunning{P. Dilkas}
+% First names are abbreviated in the running head.
+% If there are more than two authors, 'et al.' is used.
+
+\institute{University of Edinburgh, Edinburgh, UK\\
+\email{p.dilkas@sms.ed.ac.uk}}
 \maketitle
+
+\begin{abstract}
+The abstract should briefly summarize the contents of the paper in
+150--250 words.
+
+\keywords{Constraint Programming \and Logic Programming \and Probabilistic Logic
+  Programming.}
+\end{abstract}
 
@@
 We will often use $\Box$ as a special domain value to indicate some kind of
-exception.
+exception. We also use Choco \cite{choco}. This works with both Prolog
+\cite{DBLP:books/daglib/0041598} and ProbLog \cite{DBLP:conf/ijcai/RaedtKT07}.
+Tested with SWI-Prolog \cite{DBLP:journals/tplp/WielemakerSTL12}.
+
+Inference options to explore. Logspace vs normal space. Symbolic vs
+non-symbolic. Propagate evidence (might be irrelevant)? Propagate weights?
+Supported knowledge compilation techniques: sdd, sddx, bdd, nnf, ddnnf, kbest,
+fsdd, fbdd.
 
@@
 \begin{itemize}
-\item Make negative cycle detection use the graph representation.
-\item Show that the set of all ProbLog programs is equal to the set of programs
-  I can generate (alternatively, show that, given any ProbLog program, there are
-  parameter values high enough to generate it).
 \item Given fixed parameters, use combinatorial arguments to calculate how many
@@
   predicates are independent if all of their groundings are independent.
-\item Describe: entailment checking for cycles and negative cycles.
 \item A constraint for logical equivalence.
-\item Rename everything into something more appropriate.
+\item Show that the set of all ProbLog programs is equal to the set of programs
+  I can generate (alternatively, show that, given any ProbLog program, there are
+  parameter values high enough to generate it).
+\item Perhaps negative cycle detection could use the same graph as the
+  independence propagator? If we extend each domain to {-1, 0, 1}, but that
+  might make propagation weaker or slower.
 \end{itemize}
-
-Both determined $\implies$ fail(). Both determined but at least is one masked by
-a (probable/determined) mask $\implies$ nothing. One determined $\implies$ the
-other one cannot exist.
 
@@
 \begin{itemize}
-\item maximum number of solutions
-\item \maxNumNodes{} (in the tree representation of a clause)
-\item \maxNumClauses{}
-\item option to forbid all cycles or just negative cycles
-\item a list of probabilities that are randomly assigned to clauses: $\{ 0.1,
-  0.2, \dots, 0.9, 1, 1, 1, 1, 1, 1 \}$.
+\item maximum number of solutions,
+\item $\maxNumNodes{}$: maximum number of nodes in the tree representation of a
+  clause,
+\item $\maxNumClauses{}$: maximum number of clauses in a program,
+\item option to forbid all cycles or just negative cycles,
+\item a list of probabilities that are randomly assigned to clauses,
 \item a list of predicates $\predicates{}$,
@@
   \begin{itemize}
-  \item $\maxArity{} = \max \arities{}$.
+  \item maximum arity $\maxArity{} \coloneqq \max \arities{}$.
   \end{itemize}
@@
 
-We also define $\tokens{} = \{ \neg, \land, \lor, \top \}$.
-
-Decision variables:
-% TODO: specify the decision variables inside clauses and their heads
+We also define $\tokens{} = \{ \neg, \land, \lor, \top \}$. All decision
+variables of the model are contained in two arrays of length $\maxNumClauses{}$:
 \begin{itemize}
 \item \variable{Body[] bodiesOfClauses}
-\item \variable{Head[] headsOfClauses}: a list of length \maxNumClauses{}
+\item \variable{Head[] headsOfClauses}
 \end{itemize}
@@
 
-\begin{constraint}[Each predicate gets at least one clause]
-  Let $P = \{ h.\variable{predicate} \mid h \in \variable{clauseHeads} \}$. Then
+\begin{constraint}
+  For $i = 0, \dots, \maxNumClauses - 1$, let $p_i =
+  \variable{headsOfClauses}[i].\variable{predicate}$. Then
+  \[
+    \variable{sort}((p_i)_{i=0}^{\maxNumClauses - 1}, (p_i)_{i=0}^{\maxNumClauses
+      - 1}),
+  \]
+  i.e., all clauses describing the same predicate are listed together and
+  sorted.
+\end{constraint}
+
+\begin{constraint}
+  Each predicate gets at least one clause. Let $P = \{ h.\variable{predicate}
+  \mid h \in \variable{clauseHeads} \}$. Then
   \[
@@
   $\preceq$ be its extension with equality (in the same way as $\le$ extends
-  $<$).
+  $<$). If
   \[
     \variable{headsOfClauses}[i-1].\variable{predicate} =
-    \variable{headsOfClauses}[i].\variable{predicate} \implies
-    \variable{bodiesOfClauses}[i-1] \preceq \variable{bodiesOfClauses}[i].
+    \variable{headsOfClauses}[i].\variable{predicate},
   \]
+  then $\variable{bodiesOfClauses}[i-1] \preceq \variable{bodiesOfClauses}[i]$.
 \end{constraint}
@@
 
-\begin{definition}
+\begin{definition} \label{def:atom}
   An \emph{atom} is a $\variable{predicate} \in \tokens{} \cup \predicates{}$ and a
-  list of \variable{arguments} of length \maxArity{} in $\variables{} \cup
+  list of \variable{arguments} of length $\maxArity{}$ in $\variables{} \cup
   \constants{} \cup \{ \Box \}$, where $\Box$ means the position is either
@@
   \begin{itemize}
-  \item \variable{treeStructure}: list of length \maxNumNodes{} with
-    domain $[0, \maxNumNodes{}]$.
+  \item \variable{treeStructure}: list of length $\maxNumNodes{}$ with
+    domain $[0, \maxNumNodes{} - 1]$.
     \begin{itemize}
@@
     \end{itemize}
-  \item \variable{treeValues}: \maxNumNodes{} atoms.
+  \item \variable{treeValues}: $\maxNumNodes{}$ atoms.
   \end{itemize}
@@
 \begin{constraint}
-  \variable{treeStructure} represents \variable{numTrees} trees.
+  $\variable{tree}(\variable{treeStructure}, \variable{numTrees})$, i.e.,
+  \variable{treeStructure} represents \variable{numTrees} trees (dominator-based
+  filtering \cite{DBLP:conf/cp/FagesL11}).
 \end{constraint}
@@
 \begin{constraint}
+  $\variable{sort}(\variable{treeStructure}, \variable{treeStructure})$, i.e.,
   \variable{treeStructure} is sorted.
@@
 
+Our definition of a head of a clause is more restrictive than \cref{def:atom}.
+
 \begin{definition} % TODO: variables are always ordered, constants are not.
@@
 \begin{constraint}
-  For each variable $v \in \variable{variables}$, $v \le \variable{arity}$.
+  For each $v \in \variable{variables}$, $v \le \variable{arity}$.
 \end{constraint}
@@
 
-\begin{constraint}[Connecting the two lists]
-  $\sum_{v \in \variable{variables}} v = \variable{count}(\Box,
-  \variable{constants}) + \variable{arity} - \maxArity{}$.
+\begin{constraint}
+  Connecting the two lists:
+  \[
+    \sum_{v \in \variable{variables}} v = \variable{count}(\Box,
+    \variable{constants}) + \variable{arity} - \maxArity{}.
+  \]
 \end{constraint}
@@
 
+\section{Entailment Checking for Negative/All Cycles}
+
+\begin{enumerate}
+\item Let $C$ be a set of clauses such that their bodies and predicates in their
+  heads are fully determined.
+\item If $C = \emptyset$, return UNDEFINED.
+\item Construct an adjacency list representation of a graph where vertices
+  represent predicates. Each edge is either \emph{positive} or \emph{negative}.
+  There is an edge from $p$ to $q$ if $q$ appears in the body of a predicate
+  with $p$ as its head. The edge is negative if, when traversing the tree to
+  reach some instance of $q$, we pass through a $\neg$ node. Otherwise, it's
+  positive.
+\item Run a modified cycle detection algorithm that detects all cycles that have
+  at least one negative edge.
+\item If we found a cycle, return FALSE.
+\item If $C$ encompasses all clauses, return TRUE.
+\item Return UNDEFINED.
+\end{enumerate}
+
 % \section{Conditional Independence}
@@
 %  algorithm for perfect bipartite matching.
+
+% Both determined $\implies$ fail(). Both determined but at least is one masked by
+% a (probable/determined) mask $\implies$ nothing. One determined $\implies$ the
+% other one cannot exist.
 
@@
 
+\section*{Acknowledgments}
+
+The author would like to thank Vaishak Belle for his comments. This work was
+supported by the EPSRC Centre for Doctoral Training in Robotics and Autonomous
+Systems, funded by the UK Engineering and Physical Sciences Research Council
+(grant EP/S023208/1).
+
+\bibliographystyle{splncs04}
+\bibliography{paper}
+
 \end{document}

### 2019-12-29 paper/paper.tex
Preliminary attempt at counting the number of possible programs

@@
 
-\section{Atoms}
+\section{Atoms} % TODO: rename to 'nodes'
+
+%, where $\Box$ means the position is either
+%  reserved for a variable, or disabled
 
 \begin{definition} \label{def:atom}
-  An \emph{atom} is a $\variable{predicate} \in \tokens{} \cup \predicates{}$ and a
-  list of \variable{arguments} of length $\maxArity{}$ in $\variables{} \cup
-  \constants{} \cup \{ \Box \}$, where $\Box$ means the position is either
-  reserved for a variable, or disabled. The atom's \variable{arity} is a number
-  in $[0, \maxArity{}]$ defined by a \variable{table} constraint,
-  according to the \variable{predicate}.
+  An \emph{atom} is a $\variable{predicate} \in \tokens{} \cup \predicates{}$
+  and a list of \variable{arguments} of length $\maxArity{}$ in $\variables{}
+  \cup \constants{}$. The atom's \variable{arity} is a number in $[0,
+  \maxArity{}]$ defined by a \variable{table} constraint, according to the
+  \variable{predicate}.
 \end{definition}
@@
 \end{constraint}
+
+\section{Counting Programs}
+
+Let $p_a$ be the number of predicates in $\predicates{}$ with arity $a \in
+\arities{}$.
+
+Number of atoms:
+\[
+  A = \sum_{a \in \arities{}} p_a(|\variables{}| + |\constants{}|)^a
+\]
+
+Number of clauses:
+\[
+  C = 1 + \sum_{n=1}^{\maxNumNodes{}} T(n),
+\]
+where $T(n)$ is defined recursively as:
+\[
+  T(1) = A
+\]
+and
+\[
+  T(n) = T(n-1) + 2\sum_{\substack{\text{ordered partitions}\\
+      c_1 + \dots + c_k = n - 1,\\
+      k \ge 2}} \prod_{i=1}^k T(c_i).
+\]
+
+Example of ordered partitions:
+\[
+  3 = 2 + 1 = 2 + 1 = 1 + 1 + 1,
+\]
+so for $n=4$, the sum would have three terms.
+
+Number of heads for a specific predicate with arity $a \in \arities{}$:
+\[
+  H_a = \sum_{v=1}^a \binom{a}{v} |\constants{}|^{a-v}
+  \sum_{k=0}^{|\variables{}|-1} \binom{v-1}{k}.
+\]
+First, select the $v$ positions dedicated for variables. The remaining $a-v$
+constants can then be filled in $|\constants{}|^{a-v}$ ways. Filling $v$
+positions with $k+1$ variables in a non-decreasing manner (without skipping any
+variables) can be seen as putting $k$ `bars' in the $v-1$ spaces between $v$
+positions. Each bar represents switching to the next variable.
+% TODO: the equation is not always defined
+
+Number of programs:
+\[
+  \left( C^{|\predicates{}|} \prod_{\mathsf{P}/a \in \predicates{}} H_a \right)
+  \left( \sum_{n=0}^{\maxNumClauses{} - |\predicates{}|} \left( C
+    \sum_{a \in \arities{}} p_aH_a \right)^n \right)
+\]
+The first half of the equation represents setting up a single clause for every
+predicate, i.e., we select its body and its head. The second half iterates over
+the number of clauses that could be added. For each of the $n$ additional
+clauses, we choose its body and its head (defined by a predicate and its arity).
+
+Parameters that affect this:
+\begin{itemize}
+\item $\arities{}$ and $(p_a)_{a \in \arities{}}$. Consider even zero arity.
+\item $|\predicates{}| = \sum_{a \in \arities{}} p_a$
+\item $|\variables{}|$
+\item $|\constants{}|$. Consider no variables and no constants.
+\item $\maxNumNodes{} \ge 1$
+\item $\maxNumClauses{} \ge |\predicates{}|$
+\end{itemize}
+% TODO: this is without any kind of cycle detection and without probabilities
 

### 2019-12-30 paper/paper.tex
Counting: Attempt 2

@@
 We will often use $\Box$ as a special domain value to indicate some kind of
-exception. We also use Choco \cite{choco}. This works with both Prolog
+exception. We also use Choco~4.10.2 \cite{choco}. This works with both Prolog
 \cite{DBLP:books/daglib/0041598} and ProbLog \cite{DBLP:conf/ijcai/RaedtKT07}.
 Tested with SWI-Prolog \cite{DBLP:journals/tplp/WielemakerSTL12}.
-
-Inference options to explore. Logspace vs normal space. Symbolic vs
-non-symbolic. Propagate evidence (might be irrelevant)? Propagate weights?
-Supported knowledge compilation techniques: sdd, sddx, bdd, nnf, ddnnf, kbest,
-fsdd, fbdd.
 
@@
   might make propagation weaker or slower.
+\item Could investigate how uniform the generated distribution of programs is.
+  Distributions of individual parameters will often favour larger values
+  because, e.g., there are more 5-tuples than 4-tuples.
+\item Inference options to explore. Logspace vs normal space. Symbolic vs
+  non-symbolic. Propagate evidence (might be irrelevant)? Propagate weights?
+  Supported knowledge compilation techniques: sdd, sddx, bdd, nnf, ddnnf, kbest,
+  fsdd, fbdd.
+\item Mention the random heuristic. Mention that restarting gives better
+  randomness, but duplicates become possible. Restarting after each run is
+  expensive. Periodic restarts could be an option.
 \end{itemize}
@@
   \variable{headsOfClauses}[i].\variable{predicate}$. Then
-  \[
-    \variable{sort}((p_i)_{i=0}^{\maxNumClauses - 1}, (p_i)_{i=0}^{\maxNumClauses
-      - 1}),
-  \]
-  i.e., all clauses describing the same predicate are listed together and
-  sorted.
+  $(p_i)_{i=0}^{\maxNumClauses - 1}$ is sorted.
 \end{constraint}
@@
 \begin{constraint}
-  $\variable{sort}(\variable{treeStructure}, \variable{treeStructure})$, i.e.,
   \variable{treeStructure} is sorted.
@@
 positions. Each bar represents switching to the next variable.
-% TODO: the equation is not always defined
 
-Number of programs:
+Let us order the elements of $\predicates{}$, and let $a_i$ be the arity of the
+$i$-th predicate. The number of programs is then:
 \[
-  \left( C^{|\predicates{}|} \prod_{\mathsf{P}/a \in \predicates{}} H_a \right)
-  \left( \sum_{n=0}^{\maxNumClauses{} - |\predicates{}|} \left( C
-    \sum_{a \in \arities{}} p_aH_a \right)^n \right)
+  \sum_{\substack{ \sum_{i=1}^{|\predicates{}|} h_i = n,\\
+%      h_1 + \dots + h_{|\predicates{}|} = n,\\
+      |\predicates{}| \le n \le \maxNumClauses,\\
+      h_i \ge 1 \text{ for all } i}} \prod_{i=1}^{|\predicates{}|}
+  \binom{C}{h_i} H_{a_i}^{h_i}
 \]
-The first half of the equation represents setting up a single clause for every
-predicate, i.e., we select its body and its head. The second half iterates over
-the number of clauses that could be added. For each of the $n$ additional
-clauses, we choose its body and its head (defined by a predicate and its arity).
 
@@
 % TODO: this is without any kind of cycle detection and without probabilities
+% describe the parameters of the test cases
 

### 2019-12-30 src/main/GeneratePrograms.java

@@ -1,12 +1,10 @@
 package main;
 
-import java.io.BufferedWriter;
-import java.io.FileWriter;
-import java.io.IOException;
+import java.io.*;
 import java.util.Arrays;
+import java.util.List;
 
 import org.chocosolver.solver.Model;
-import org.chocosolver.solver.Solver;
 import org.chocosolver.solver.constraints.Constraint;
 import org.chocosolver.solver.constraints.extension.Tuples;
 import org.chocosolver.solver.search.strategy.Search;
@@ -16,30 +14,35 @@ import org.chocosolver.solver.variables.IntVar;
 import org.chocosolver.util.tools.ArrayUtils;
 import propagators.NegativeCyclePropagator;
 
+import static java.util.stream.Collectors.toList;
+
 class GeneratePrograms {
 
     private static final String DIRECTORY = "../programs/";
     private static final int NUM_SOLUTIONS = 10000;
-    private static final int MAX_NUM_NODES = 1;
-    private static final int MAX_NUM_CLAUSES = 1;
+    private static int MAX_NUM_NODES = 1;
+    private static int MAX_NUM_CLAUSES = 1;
     private static final boolean FORBID_ALL_CYCLES = false;
     //private static final double[] PROBABILITIES = {0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9,
     //        1, 1, 1, 1, 1, 1}; // let's make probability 1 a bit more likely
     private static final double[] PROBABILITIES = {1};
 
-    static final String[] PREDICATES = {"p"};
-    static final int[] ARITIES = {2};
-    static final String[] VARIABLES = {"X", "Y"};
-    static final String[] CONSTANTS = {};
-    static final int MAX_ARITY = Arrays.stream(ARITIES).max().getAsInt();
+    static String[] PREDICATES = {"p"};
+    static int[] ARITIES = {2};
+    static String[] VARIABLES = {"X", "Y"};
+    static String[] CONSTANTS = {};
+    static int MAX_ARITY = Arrays.stream(ARITIES).max().getAsInt();
 
     static Tuples arities;
 
-    private static IntVar[] clauseAssignments;
-    private static Head[] clauseHeads;
-    private static Body[] bodies;
+    private static Model model;
+    private static IntVar[] clauseAssignments; // an array of predicates occurring at the heads of clauses
+    private static Head[] clauseHeads; // full heads (predicates, variables, constants)
[…]

### 2019-12-30 src/main/Head.java

@@ -66,7 +66,7 @@ class Head {
 
     @Override
     public String toString() {
-        System.out.println("Predicate: " + predicate.getValue());
+        /*System.out.println("Predicate: " + predicate.getValue());
         System.out.println("Arity: " + arity.getValue());
         System.out.print("Variables: ");
         for (IntVar variable : variables)
@@ -78,7 +78,7 @@ class Head {
         System.out.println("\n");
         System.out.println("sum of variables: " + sumOfVars.getValue());
         System.out.println("number of variables: " + countVariables.getValue());
-        System.out.println("negated remaining arity: " + negRemainingArity.getValue() + "\n");
+        System.out.println("negated remaining arity: " + negRemainingArity.getValue() + "\n");*/
 
         StringBuilder s = new StringBuilder();
         s.append(GeneratePrograms.PREDICATES[predicate.getValue()]).append("(");

### 2019-12-31 src/main/Head.java
Counting: It's working!

@@ -16,7 +16,7 @@ class Head {
 
     // Auxiliary variables
     private IntVar sumOfVars;
-    private IntVar countVariables;
+    private IntVar variableCount;
     private IntVar negRemainingArity;
 
     Head(Model model, IntVar predicate) {
@@ -33,19 +33,23 @@ class Head {
         constants = model.intVarArray(GeneratePrograms.MAX_ARITY, 0, GeneratePrograms.CONSTANTS.length);
         for (int i = 0; i < constants.length; i++) {
             Constraint iGeArity = model.arithm(arity, "<=", i);
-            Constraint isZero = model.arithm(constants[i], "=", 0);
-            model.ifThen(iGeArity, isZero);
+            Constraint isDisabled = model.arithm(constants[i], "=", GeneratePrograms.CONSTANTS.length);
+            model.ifThen(iGeArity, isDisabled);
         }
 
         // Connecting the two arrays
         // countZeros - (MAX_ARITY - arity) = sumOfVars
-        countVariables = model.intVar(0, constants.length);
-        model.count(GeneratePrograms.CONSTANTS.length, constants, countVariables).post();
+        variableCount = model.intVar(0, constants.length);
+        Constraint clauseIsDisabled = model.arithm(predicate, "=", GeneratePrograms.PREDICATES.length);
+        Constraint countVariables = model.count(GeneratePrograms.CONSTANTS.length, constants, variableCount);
+        Constraint zeroVariables = model.arithm(variableCount, "=", GeneratePrograms.MAX_ARITY);
+        model.ifThenElse(clauseIsDisabled, zeroVariables, countVariables);
+
         sumOfVars = model.intVar(0, GeneratePrograms.MAX_ARITY);
         model.sum(variables, "=", sumOfVars).post();
         negRemainingArity = model.intVar(-GeneratePrograms.MAX_ARITY, 0);
         model.arithm(negRemainingArity, "=", arity, "-", GeneratePrograms.MAX_ARITY).post();
-        model.arithm(sumOfVars, "=", countVariables, "+", negRemainingArity).post();
+        model.arithm(sumOfVars, "=", variableCount, "+", negRemainingArity).post();
 
         // All zeros go after all non-zeros
         // v[i] = 0 /\ v[j] != 0 => j < i

### 2019-12-31 paper/paper.tex
Counting: It's working!
Renaming

@@
 \newcommand{\variable}[1]{\texttt{\textup{#1}}}
+\newcommand{\arrayd}[3]{\variable{{#1}[}{#2}\variable{]} \in {#3}}
+\newcommand{\arrayt}[3]{\variable{{#3}[}{#2}\variable{] {#1}}}
 \newcommand{\predicates}{\mathcal{P}}
@@
 \newcommand{\maxNumClauses}{\mathcal{M}_{\mathcal{C}}}
+
+\def\multiset#1#2{\ensuremath{\left(\kern-.3em\left(\genfrac{}{}{0pt}{}{#1}{#2}\right)\kern-.3em\right)}}
 
@@
 We will often use $\Box$ as a special domain value to indicate some kind of
-exception. We also use Choco~4.10.2 \cite{choco}. This works with both Prolog
+exception. We write $\arrayd{a}{b}{c}$ to mean that
+$\variable{a}$ is an array of variables of length $b$ such that each element of
+$\variable{a}$ has domain $c$. Similarly, we write $\arrayt{a}{b}{c}$ to denote
+an array $\variable{a}$ of length $b$ such that each element of $\variable{a}$
+has type $\variable{c}$.
+
+We also use Choco~4.10.2 \cite{choco}. This works with both Prolog
 \cite{DBLP:books/daglib/0041598} and ProbLog \cite{DBLP:conf/ijcai/RaedtKT07}.
@@
 We also define $\tokens{} = \{ \neg, \land, \lor, \top \}$. All decision
-variables of the model are contained in two arrays of length $\maxNumClauses{}$:
+variables of the model are contained in two arrays:
 \begin{itemize}
-\item \variable{Body[] bodiesOfClauses}
-\item \variable{Head[] headsOfClauses}
+\item $\arrayt{bodiesOfClauses}{\maxNumClauses{}}{Body}$,
+\item $\arrayt{headsOfClauses}{\maxNumClauses{}}{Head}$
 \end{itemize}
@@
   Each predicate gets at least one clause. Let $P = \{ h.\variable{predicate}
-  \mid h \in \variable{clauseHeads} \}$. Then
+  \mid h \in \variable{headsOfClauses} \}$. Then
   \[
@@
 
-\section{Atoms} % TODO: rename to 'nodes'
+\section{Bodies of Clauses}
 
+\begin{definition}
+  The body of a clause is defined by:
+  \begin{itemize}
+  \item $\arrayd{treeStructure}{\maxNumNodes{}}{[0, \maxNumNodes{} - 1]}$ such
+    that:
+    \begin{itemize}
+    \item $\variable{treeStructure}[i] = i$: the $i$-th node is a root.
+    \item $\variable{treeStructure}[i] = j$: the $i$-th node's parent is node $j$.
+    \end{itemize}
+  \item $\arrayt{treeValues}{\maxNumNodes{}}{Node}$.
+  \end{itemize}
+\end{definition}
+% TODO: examples
+
+Auxiliary variables: $\variable{numNodes}, \variable{numTrees} \in \{ 1, \dots,
+\maxNumNodes{} \}$.
+
+\subsection{Nodes}
 %, where $\Box$ means the position is either
@@
 
-\begin{definition} \label{def:atom}
-  An \emph{atom} is a $\variable{predicate} \in \tokens{} \cup \predicates{}$
-  and a list of \variable{arguments} of length $\maxArity{}$ in $\variables{}
-  \cup \constants{}$. The atom's \variable{arity} is a number in $[0,
-  \maxArity{}]$ defined by a \variable{table} constraint, according to the
-  \variable{predicate}.
+\begin{definition} \label{def:node}
+  A \emph{node} has a $\variable{name} \in \tokens{} \cup \predicates{}$ and
+  $\arrayd{arguments}{\maxArity{}}{\variables{} \cup \constants{}}$. The node's
+  \variable{arity} is a number in $[0, \maxArity{}]$ defined by a
+  \variable{table} constraint as
+  \[
+    \variable{arity} = \begin{cases}
+      \text{the arity of } \variable{name} & \text{if } \variable{name} \in
+      \predicates{}\\
+      0 & \text{otherwise.}
+    \end{cases}
+  \]
 \end{definition}
@@
 \end{constraint}
-
-\section{Bodies of Clauses}
-
-\begin{definition}
-  The body of a clause is defined by:
-  \begin{itemize}
-  \item \variable{treeStructure}: list of length $\maxNumNodes{}$ with
-    domain $[0, \maxNumNodes{} - 1]$.
-    \begin{itemize}
-    \item $\variable{treeStructure}[i] = i$: the $i$-th node is a root.
-    \item $\variable{treeStructure}[i] = j$: the $i$-th node's parent is node $j$.
-    \end{itemize}
-  \item \variable{treeValues}: $\maxNumNodes{}$ atoms.
-  \end{itemize}
-\end{definition}
-% TODO: examples
-
-Auxiliary variables: $\variable{numNodes}, \variable{numTrees} \in \{ 1, \dots,
-\maxNumNodes{} \}$.
 
@@
     \variable{treeStructure}[i] = i \quad \text{and} \quad
-    \variable{treeValues}[i].\variable{predicate} = \top,
+    \variable{treeValues}[i].\variable{name} = \top,
   \]
@@
   \begin{itemize}
-  \item has 0 children $\iff$ $\variable{treeValues}[i].\variable{predicate} \in
+  \item has 0 children $\iff$ $\variable{treeValues}[i].\variable{name} \in
     \predicates{}$;
-  \item has 1 child $\iff$ $\variable{treeValues}[i].\variable{predicate} = \neg$;
-  \item has $>1$ child $\iff$ $\variable{treeValues}[i].\variable{predicate} \in
+  \item has 1 child $\iff$ $\variable{treeValues}[i].\variable{name} = \neg$;
+  \item has $>1$ child $\iff$ $\variable{treeValues}[i].\variable{name} \in
     \{ \land, \lor \}$.
@@
     \variable{treeStructure}[i] \ne i \implies
-    \variable{treeValues}[i].\variable{predicate} \ne \top.
+    \variable{treeValues}[i].\variable{name} \ne \top.
   \]
@@
 If the clause should be disabled, $\variable{numNodes} = 1$ and
-$\variable{treeValues}[0].\variable{predicate} = \top$.
+$\variable{treeValues}[0].\variable{name} = \top$.
 
@@
     A[i][j] = 0 \iff &\nexists k: \variable{headsOfClauses}[k].\variable{predicate} = j \text{ and } \\
-    &i \in \{ a.\variable{predicate} \mid a \in \variable{bodiesOfClauses}[k].\variable{treeValues} \}.
+    &i \in \{ a.\variable{name} \mid a \in \variable{bodiesOfClauses}[k].\variable{treeValues} \}.
   \end{align*}
@@
 
-\section{Head of a Clause}
+\section{Heads of Clauses}
 
-Our definition of a head of a clause is more restrictive than \cref{def:atom}.
+Our definition of a head of a clause is more restrictive than \cref{def:node}.
 
-\begin{definition} % TODO: variables are always ordered, constants are not.
-  The \emph{head} of a clause is defined by two lists:
+\begin{definition} % mention: variables are always ordered, constants are not.
+  The \emph{head} of a clause is composed of:
   \begin{itemize}
@@
     denotes a disabled clause.
-  \item \variable{variables} of length $|\variables{}|$ and with domain
-    $[0, \maxArity{}]$: how many times each variable appears in the head atom.
-  \item \variable{constants} of length $\maxArity{}$ and with domain
-    $\constants{} \cup \{ \Box \}$, where $\Box$ denotes that the position is
-    reserved for a variable.
+  \item $\arrayd{variables}{|\variables{}|}{[0, \maxArity{}]}$: how many times
+    each variable appears in the head atom.
+  \item $\arrayd{constants}{\maxArity{}}{\constants{} \cup \{ \Box \}}$, where
+    $\Box$ denotes that the position is reserved for a variable.
   \end{itemize}
-  We also define the predicate's \variable{arity} using the same
-  \variable{table} constraint.
+  We also define the \variable{predicate}'s \variable{arity} using the same
+  \variable{table} constraint as
+  \[
+    \variable{arity} = \begin{cases}
+      0 & \text{if } \variable{predicate} = \Box\\
+      \text{the arity of } \variable{predicate} & \text{otherwise.}
+    \end{cases}
+  \]
 \end{definition}
@@
   \[
-    i \ge \variable{arity} \implies \variable{constants}[i] = 0.
+    i \ge \variable{arity} \implies \variable{constants}[i] = \Box.
   \]
@@
   \[
-    \sum_{v \in \variable{variables}} v = \variable{count}(\Box,
-    \variable{constants}) + \variable{arity} - \maxArity{}.
+    \maxArity{} - \variable{arity} + \sum_{v \in \variable{variables}} v
+    = \begin{cases}
+      \maxArity{} & \text{if } \variable{predicate} = \Box \\
+      \variable{count}(\Box, \variable{constants}) & \text{otherwise}.
+      \end{cases}
   \]
@@
 
-Number of atoms:
+Number of atoms (leaves of the tree):
 \[
@@
 \[
-  T(n) = T(n-1) + 2\sum_{\substack{\text{ordered partitions}\\
-      c_1 + \dots + c_k = n - 1,\\
-      k \ge 2}} \prod_{i=1}^k T(c_i).
+  T(n) = T(n-1) + 2\sum_{\substack{c_1 + \dots + c_k = n - 1,\\
+      k \ge 2,\\
+      c_i \ge 1 \text{ for all } i}} \prod_{i=1}^k T(c_i).
 \]
@@
 \[
-  H_a = \sum_{v=1}^a \binom{a}{v} |\constants{}|^{a-v}
+  H_a = |\constants{}|^a + \sum_{v=1}^a \binom{a}{v} |\constants{}|^{a-v}
   \sum_{k=0}^{|\variables{}|-1} \binom{v-1}{k}.
@@
       h_i \ge 1 \text{ for all } i}} \prod_{i=1}^{|\predicates{}|}
-  \binom{C}{h_i} H_{a_i}^{h_i}
+  \multiset{C}{h_i} H_{a_i}^{h_i},
+\]
+where
+\[
+  \multiset{n}{k} = \binom{n + k - 1}{k}.
 \]

### 2019-12-31 src/main/Body.java

@@ -16,16 +16,16 @@ public class Body {
 
     private int maxNumNodes;
     private IntVar[] treeStructure;
-    private Atom[] treeValues;
+    private Node[] treeValues;
 
     public Body(Model model, IntVar assignment, int maxNumNodes) {
         this.maxNumNodes = maxNumNodes;
 
         IntVar numNodes = model.intVar(1, maxNumNodes); // number of nodes in the main tree
         treeStructure = model.intVarArray(maxNumNodes, 0, maxNumNodes - 1);
-        treeValues = new Atom[maxNumNodes];
+        treeValues = new Node[maxNumNodes];
         for (int i = 0; i < maxNumNodes; i++)
-            treeValues[i] = new Atom(model);
+            treeValues[i] = new Node(model);
 
         // Tree structure
         IntVar numTrees = model.intVar(1, maxNumNodes);
@@ -133,8 +133,8 @@ public class Body {
 
     public IntVar[] getDecisionVariables() {
         IntVar[] variables = treeStructure;
-        for (Atom atom : treeValues)
-            variables = ArrayUtils.concat(variables, atom.getDecisionVariables());
+        for (Node node : treeValues)
+            variables = ArrayUtils.concat(variables, node.getDecisionVariables());
         return variables;
     }
 

### 2019-12-31 src/main/Node.java

@@ -5,13 +5,13 @@ import org.chocosolver.solver.constraints.Constraint;
 import org.chocosolver.solver.variables.IntVar;
 import org.chocosolver.util.tools.ArrayUtils;
 
-class Atom {
+class Node {
 
     private IntVar predicate; // tokens first, then predicates
     private IntVar[] arguments; // variables first, then constants
     private IntVar arity;
 
-    Atom(Model model) {
+    Node(Model model) {
         int numPossibleArguments = GeneratePrograms.VARIABLES.length + GeneratePrograms.CONSTANTS.length;
         predicate = model.intVar(0, GeneratePrograms.PREDICATES.length + Token.values().length - 1);
         arguments = model.intVarArray(GeneratePrograms.MAX_ARITY, 0, numPossibleArguments - 1);

### 2019-12-31 paper/paper.tex
Some examples

@@
 \usepackage[capitalise]{cleveref}
+\usepackage{tikz}
 
@@
 an array $\variable{a}$ of length $b$ such that each element of $\variable{a}$
-has type $\variable{c}$.
+has type $\variable{c}$. All constraint variables in the model are integer
+variables, but, e.g., if the integer $i$ refers to a logical variable $X$, we
+will use $i$ and $X$ interchangeably.
 
@@
 
-\section{TODO}
+\subsection{TODO}
 
 \begin{itemize}
-\item Given fixed parameters, use combinatorial arguments to calculate how many
-  different programs there are and check that I'm generating the same number.
+\item Heads are too restrictive: $\variable{P}(X, Y, X)$ should be allowed.
 \item Formal definition (here and in the predicate invention paper): two
@@
 \item A constraint for logical equivalence.
-\item Show that the set of all ProbLog programs is equal to the set of programs
-  I can generate (alternatively, show that, given any ProbLog program, there are
-  parameter values high enough to generate it).
 \item Perhaps negative cycle detection could use the same graph as the
@@
 
-\section{Parameters}
+\subsection{Parameters}
 
@@
 \begin{itemize}
-\item maximum number of solutions,
-\item $\maxNumNodes{}$: maximum number of nodes in the tree representation of a
-  clause,
-\item $\maxNumClauses{}$: maximum number of clauses in a program,
-\item option to forbid all cycles or just negative cycles,
-\item a list of probabilities that are randomly assigned to clauses,
 \item a list of predicates $\predicates{}$,
-\item a list of their arities $\arities{}$,
+\item a list of their arities $\arities{}$ (including zero),
   \begin{itemize}
@@
 \item and a list of constants $\constants{}$.
+  \begin{itemize}
+  \item Each of them can be empty, but $|\constants{}| + |\variables{}| > 0$.
+  \end{itemize}
+\item a list of probabilities that are randomly assigned to clauses,
+\item option to forbid all cycles or just negative cycles,
+\item $\maxNumNodes{} \ge 1$: maximum number of nodes in the tree representation
+  of a clause,
+\item $\maxNumClauses{} \ge |\predicates{}|$: maximum number of clauses in a
+  program,
+\item maximum number of solutions,
 \end{itemize}
@@
 
-\section{General Constraints}
-
-\begin{constraint}
-  For $i = 0, \dots, \maxNumClauses - 1$, let $p_i =
-  \variable{headsOfClauses}[i].\variable{predicate}$. Then
-  $(p_i)_{i=0}^{\maxNumClauses - 1}$ is sorted.
-\end{constraint}
-
-\begin{constraint}
-  Each predicate gets at least one clause. Let $P = \{ h.\variable{predicate}
-  \mid h \in \variable{headsOfClauses} \}$. Then
-  \[
-    \variable{nValues}(P) =
-    \begin{cases}
-      \variable{numPredicates} + 1 & \text{if } \variable{count}(\Box, P) > 0 \\
-      \variable{numPredicates} & \text{otherwise.}
-    \end{cases}
-  \]
-\end{constraint}
-
-\begin{constraint}
-  Let $\prec$ be any total order defined over bodies of clauses, and let
-  $\preceq$ be its extension with equality (in the same way as $\le$ extends
-  $<$). If
-  \[
-    \variable{headsOfClauses}[i-1].\variable{predicate} =
-    \variable{headsOfClauses}[i].\variable{predicate},
-  \]
-  then $\variable{bodiesOfClauses}[i-1] \preceq \variable{bodiesOfClauses}[i]$.
-\end{constraint}
-For example, $\preceq$ can be implemented as \variable{lexLessEq} over the
-decision variables of each body.
-% TODO: might need to include clause heads as well.
-
-\section{Bodies of Clauses}
-
-\begin{definition}
-  The body of a clause is defined by:
-  \begin{itemize}
-  \item $\arrayd{treeStructure}{\maxNumNodes{}}{[0, \maxNumNodes{} - 1]}$ such
-    that:
-    \begin{itemize}
-    \item $\variable{treeStructure}[i] = i$: the $i$-th node is a root.
-    \item $\variable{treeStructure}[i] = j$: the $i$-th node's parent is node $j$.
-    \end{itemize}
-  \item $\arrayt{treeValues}{\maxNumNodes{}}{Node}$.
-  \end{itemize}
-\end{definition}
-% TODO: examples
-
-Auxiliary variables: $\variable{numNodes}, \variable{numTrees} \in \{ 1, \dots,
-\maxNumNodes{} \}$.
-
-\subsection{Nodes}
-%, where $\Box$ means the position is either
-%  reserved for a variable, or disabled
-
-\begin{definition} \label{def:node}
-  A \emph{node} has a $\variable{name} \in \tokens{} \cup \predicates{}$ and
-  $\arrayd{arguments}{\maxArity{}}{\variables{} \cup \constants{}}$. The node's
-  \variable{arity} is a number in $[0, \maxArity{}]$ defined by a
-  \variable{table} constraint as
-  \[
-    \variable{arity} = \begin{cases}
-      \text{the arity of } \variable{name} & \text{if } \variable{name} \in
-      \predicates{}\\
-      0 & \text{otherwise.}
-    \end{cases}
-  \]
-\end{definition}
-
-\begin{constraint}
-  For $i = 0, \dots, \maxArity{} - 1$,
-  \[
-    i \ge \variable{arity} \implies \variable{arguments}[i] = 0.
-  \]
-\end{constraint}
-
-\subsection{Constraints}
-
-\begin{constraint}
-  $\variable{tree}(\variable{treeStructure}, \variable{numTrees})$, i.e.,
-  \variable{treeStructure} represents \variable{numTrees} trees (dominator-based
-  filtering \cite{DBLP:conf/cp/FagesL11}).
-\end{constraint}
-
-\begin{constraint}
-  $\variable{treeStructure}[0] = 0$.
-\end{constraint}
-
-\begin{constraint}
-  $\variable{numTrees} + \variable{numNodes} = \maxNumNodes{} + 1$.
-\end{constraint}
-
-\begin{constraint}
-  \variable{treeStructure} is sorted.
-\end{constraint}
-
-\begin{constraint}
-  For $i = 0, \dots, \maxNumNodes{} - 1$, if $\variable{numNodes} \le
-  i$, then
-  \[
-    \variable{treeStructure}[i] = i \quad \text{and} \quad
-    \variable{treeValues}[i].\variable{name} = \top,
-  \]
-  else
-  \[
-    \variable{treeStructure}[i] < \variable{numNodes}.
-  \]
-\end{constraint}
-
-\begin{constraint}
-  For $i = 0, \dots, \maxNumNodes{} - 1$,
-  \begin{itemize}
-  \item has 0 children $\iff$ $\variable{treeValues}[i].\variable{name} \in
-    \predicates{}$;
-  \item has 1 child $\iff$ $\variable{treeValues}[i].\variable{name} = \neg$;
-  \item has $>1$ child $\iff$ $\variable{treeValues}[i].\variable{name} \in
-    \{ \land, \lor \}$.
-  \end{itemize}
-\end{constraint}
-
-\begin{constraint}
-  For $i = 0, \dots, \maxNumNodes{} - 1$,
-  \[
-    \variable{treeStructure}[i] \ne i \implies
-    \variable{treeValues}[i].\variable{name} \ne \top.
-  \]
-\end{constraint}
-
-If the clause should be disabled, $\variable{numNodes} = 1$ and
-$\variable{treeValues}[0].\variable{name} = \top$.
-
-\begin{constraint}
-  Adjacency matrix representation:
-  \begin{align*}
-    A[i][j] = 0 \iff &\nexists k: \variable{headsOfClauses}[k].\variable{predicate} = j \text{ and } \\
-    &i \in \{ a.\variable{name} \mid a \in \variable{bodiesOfClauses}[k].\variable{treeValues} \}.
-  \end{align*}
-\end{constraint}
-
 \section{Heads of Clauses}
 
-Our definition of a head of a clause is more restrictive than \cref{def:node}.
+Our definition is slightly more involved because we want to impose some
+additional constraints, namely, that the variables in the atom are consecutive
 
@@
   \end{itemize}
-  We also define the \variable{predicate}'s \variable{arity} using the same
+  We define the \variable{predicate}'s \variable{arity} using the
   \variable{table} constraint as
@@
   \]
+\end{constraint}
+
+\section{Bodies of Clauses}
+
+\begin{definition}
+  The body of a clause is defined by:
+  \begin{itemize}
+  \item $\arrayd{treeStructure}{\maxNumNodes{}}{[0, \maxNumNodes{} - 1]}$ such
+    that:
+    \begin{itemize}
+    \item $\variable{treeStructure}[i] = i$: the $i$-th node is a root.
+    \item $\variable{treeStructure}[i] = j$: the $i$-th node's parent is node $j$.
+    \end{itemize}
+  \item $\arrayt{treeValues}{\maxNumNodes{}}{Node}$.
+  \end{itemize}
+\end{definition}
+
+Auxiliary variables: $\variable{numNodes}, \variable{numTrees} \in \{ 1, \dots,
+\maxNumNodes{} \}$. The former counts the number of nodes in the main tree. The
+latter counts the number of trees in total.
+
+\begin{figure}[t]
+  \centering
+  \begin{tikzpicture}
+    \node[draw,circle,gray,text=black] (or) at (0, 0) {$\lor$};
+    \node[draw,circle,gray,text=black] (not) at (-1, -1) {$\neg$};
+    \node (P) at (-1, -2) {$\variable{P}(X)$};
+    \node[draw,circle,gray,text=black] (and) at (1, -1) {$\land$};
+    \node (Q) at (0, -2) {$\variable{Q}(X)$};
+    \node (R) at (2, -2) {$\variable{P}(X)$};
+    \draw[gray] (or) -- (not);
+    \draw[gray] (or) -- (and);
+    \draw[gray] (not) -- (P);
+    \draw[gray] (and) -- (Q);
+    \draw[gray] (and) -- (R);
+  \end{tikzpicture}
+  \label{fig:example_tree}
+  \caption{A tree representation of the formula from \cref{example:formula}}
+\end{figure}
+
+\begin{example} \label{example:formula} % TODO: describe (and refer to the figure)
+  Let $\maxNumNodes{} = 8$. Then $\neg\variable{P}(X) \lor (\variable{Q}(X)
+  \land \variable{P}(X))$...
+  \begin{alignat*}{8}
+    \variable{treeStructure} &= [0, &&0, &&0, &&1, &&2, &&2, &&6, &&7],\\
+    \variable{treeValues} &= [{\lor}, &&{\neg}, &&{\land}, \variable{P}(&&X), \variable{Q}(&&X), \variable{P}(&&X), &&\top, &&\top],\\
+    \variable{numNodes} &= 6, && && && && && && &&\\
+    \variable{numTrees} &= 3. && && && && && && &&
+  \end{alignat*}
+\end{example}
+
+\subsection{Nodes}
+
+\begin{definition} \label{def:node}
+  A \emph{node} has a $\variable{name} \in \tokens{} \cup \predicates{}$ and
+  $\arrayd{arguments}{\maxArity{}}{\variables{} \cup \constants{}}$. The node's
+  $\variable{arity} \in [0, \maxArity{}]$ is defined by a \variable{table}
+  constraint as
+  \[
+    \variable{arity} = \begin{cases}
+      \text{the arity of } \variable{name} & \text{if } \variable{name} \in
+      \predicates{}\\
+      0 & \text{otherwise.}
+    \end{cases}
+  \]
+\end{definition}
+
+\begin{constraint}
+  For $i = 0, \dots, \maxArity{} - 1$,
+  \[
+    i \ge \variable{arity} \implies \variable{arguments}[i] = 0\footnote{Zero
+      here represents the first variable or constant, regardless of what it is.}.
+  \]
+\end{constraint}
+
+\begin{example}
+  Let $\maxArity{} = 2$, $\predicates{} = [\variable{P}, \dots]$, $\arities{}
+  = [1, \dots]$, and $X \in \variables{}$. Then the node representing atom
+  $\variable{P}(X)$ has:
+  \begin{align*}
+    \variable{name} &= \variable{P},\\
+    \variable{arguments} &= [X, 0],\\
+    \variable{arity} &= 1.
+  \end{align*}
+\end{example}
+
+\subsection{Constraints}
+
+\begin{constraint}
+  $\variable{tree}(\variable{treeStructure}, \variable{numTrees})$, i.e.,
+  \variable{treeStructure} represents \variable{numTrees} trees (dominator-based
+  filtering \cite{DBLP:conf/cp/FagesL11}).
+\end{constraint}
+
+\begin{constraint}
+  $\variable{treeStructure}[0] = 0$.
+\end{constraint}
+
+\begin{constraint}
+  $\variable{numTrees} + \variable{numNodes} = \maxNumNodes{} + 1$.
+\end{constraint}
+
+\begin{constraint}
+  \variable{treeStructure} is sorted.
+\end{constraint}
+
+\begin{constraint}
+  For $i = 0, \dots, \maxNumNodes{} - 1$, if $\variable{numNodes} \le
+  i$, then
+  \[
+    \variable{treeStructure}[i] = i \quad \text{and} \quad
+    \variable{treeValues}[i].\variable{name} = \top,
+  \]
+  else
+  \[
+    \variable{treeStructure}[i] < \variable{numNodes}.
+  \]
+\end{constraint}
+
+\begin{constraint}
+  For $i = 0, \dots, \maxNumNodes{} - 1$,
+  \begin{align*}
+    \variable{count}(i, \variable{treeStructure}_{-i}) = 0 &\iff \variable{treeValues}[i].\variable{name} \in \predicates{} \cup \{ \top \},\\
+    \variable{count}(i, \variable{treeStructure}_{-i}) = 1 &\iff \variable{treeValues}[i].\variable{name} = \neg,\\
+    \variable{count}(i, \variable{treeStructure}_{-i}) > 1 &\iff \variable{treeValues}[i].\variable{name} \in \{ \land, \lor \}.
+  \end{align*}
+  $\variable{treeStructure}_{-i}$ denotes array $\variable{treeStructure}$ with
+  position $i$ skipped.
+\end{constraint}
+Each constraint corresponds to node $i$ having no children, one child, and
+multiple children, respectively.
+
+\begin{constraint}
+  For $i = 0, \dots, \maxNumNodes{} - 1$,
+  \[
+    \variable{treeStructure}[i] \ne i \implies
+    \variable{treeValues}[i].\variable{name} \ne \top.
+  \]
+\end{constraint}
+
+If the clause should be disabled, $\variable{numNodes} = 1$ and
+$\variable{treeValues}[0].\variable{name} = \top$.
+
+\section{Managing Clauses}
+
+\begin{constraint}
+  For $i = 0, \dots, \maxNumClauses - 1$, let $p_i =
+  \variable{headsOfClauses}[i].\variable{predicate}$. Then
+  $(p_i)_{i=0}^{\maxNumClauses - 1}$ is sorted.
+\end{constraint}
+
+\begin{constraint}
+  Each predicate gets at least one clause. Let $P = \{ h.\variable{predicate}
+  \mid h \in \variable{headsOfClauses} \}$. Then
+  \[
+    \variable{nValues}(P) =
+    \begin{cases}
+      \variable{numPredicates} + 1 & \text{if } \variable{count}(\Box, P) > 0 \\
+      \variable{numPredicates} & \text{otherwise.}
+    \end{cases}
+  \]
+\end{constraint}
+
+\begin{constraint}
+  Let $\prec$ be any total order defined over bodies of clauses, and let
+  $\preceq$ be its extension with equality (in the same way as $\le$ extends
+  $<$). If
+  \[
+    \variable{headsOfClauses}[i-1].\variable{predicate} =
+    \variable{headsOfClauses}[i].\variable{predicate},
+  \]
+  then $\variable{bodiesOfClauses}[i-1] \preceq \variable{bodiesOfClauses}[i]$.
+\end{constraint}
+For example, $\preceq$ can be implemented as \variable{lexLessEq} over the
+decision variables of each body.
+
+\begin{constraint}
+  Adjacency matrix representation:
+  \begin{align*}
+    A[i][j] = 0 \iff &\nexists k: \variable{headsOfClauses}[k].\variable{predicate} = j \text{ and } \\
+    &i \in \{ a.\variable{name} \mid a \in \variable{bodiesOfClauses}[k].\variable{treeValues} \}.
+  \end{align*}
 \end{constraint}
@@
 
-Parameters that affect this:
-\begin{itemize}
-\item $\arities{}$ and $(p_a)_{a \in \arities{}}$. Consider even zero arity.
-\item $|\predicates{}| = \sum_{a \in \arities{}} p_a$
-\item $|\variables{}|$
-\item $|\constants{}|$. Consider no variables and no constants.
-\item $\maxNumNodes{} \ge 1$
-\item $\maxNumClauses{} \ge |\predicates{}|$
-\end{itemize}
-% TODO: this is without any kind of cycle detection and without probabilities
-% describe the parameters of the test cases
+This is without any kind of cycle detection and without probabilities.
+% TODO: describe what parameter values were used to test the model.
 

### 2019-12-31 paper/paper.tex
Small changes

@@
 \item Heads are too restrictive: $\variable{P}(X, Y, X)$ should be allowed.
-\item Formal definition (here and in the predicate invention paper): two
-  predicates are independent if all of their groundings are independent.
 \item A constraint for logical equivalence.
@@
   \end{tikzpicture}
+  \caption{A tree representation of the formula from \cref{example:formula}}
   \label{fig:example_tree}
-  \caption{A tree representation of the formula from \cref{example:formula}}
 \end{figure}
 
-\begin{example} \label{example:formula} % TODO: describe (and refer to the figure)
+\begin{example} \label{example:formula}
   Let $\maxNumNodes{} = 8$. Then $\neg\variable{P}(X) \lor (\variable{Q}(X)
-  \land \variable{P}(X))$...
+  \land \variable{P}(X))$ corresponds to the tree in \cref{fig:example_tree} and
+  can be encoded as:
   \begin{alignat*}{8}
@@
   \end{alignat*}
+  In the rest of this section, we will describe how the elements of
+  $\variable{treeValues}$ are encoded and list a series of constraints that make
+  this representation unique.
 \end{example}
@@
 \begin{constraint}
-  $\variable{tree}(\variable{treeStructure}, \variable{numTrees})$, i.e.,
-  \variable{treeStructure} represents \variable{numTrees} trees (dominator-based
-  filtering \cite{DBLP:conf/cp/FagesL11}).
+  \variable{treeStructure} represents \variable{numTrees} trees, i.e.,
+  \[
+    \variable{tree}(\variable{treeStructure}, \variable{numTrees})\footnote{This
+      constraint uses dominator-based filtering by Fages and Lorca
+      \cite{DBLP:conf/cp/FagesL11}.}.
+  \]
 \end{constraint}
@@
 \section{The Independence Constraint}
+
+% TODO: define independence of predicates
+% Formal definition (here and in the predicate invention paper): two
+% predicates are independent if all of their groundings are independent.
 

### 2020-01-02 paper/paper.tex
A better approach to symmetry reduction for clause heads

@@
 \usepackage{tikz}
+\usepackage{mathrsfs}
 
@@
 
+%\relpenalty=10000
+%\binoppenalty=10000
 \def\multiset#1#2{\ensuremath{\left(\kern-.3em\left(\genfrac{}{}{0pt}{}{#1}{#2}\right)\kern-.3em\right)}}
@@
 variables, but, e.g., if the integer $i$ refers to a logical variable $X$, we
-will use $i$ and $X$ interchangeably.
+will use $i$ and $X$ interchangeably. All indices start at zero.
 
@@
 \begin{itemize}
-\item Heads are too restrictive: $\variable{P}(X, Y, X)$ should be allowed.
-\item A constraint for logical equivalence.
+\item Heads are too restrictive: $\mathsf{P}(X, Y, X)$ should be allowed.
+\item A constraint for logical equivalence. An algorithm to reduce each tree to
+  some kind of normal form.
 \item Perhaps negative cycle detection could use the same graph as the
@@
 
-Our definition is slightly more involved because we want to impose some
-additional constraints, namely, that the variables in the atom are consecutive
+Our definition is slightly more involved because we want to eliminate some
+symmetries.
 
-\begin{definition} % mention: variables are always ordered, constants are not.
+\begin{definition}
   The \emph{head} of a clause is composed of:
   \begin{itemize}
-  \item $\variable{predicate} \in \predicates \cup \{ \Box \}$, where $\Box$
-    denotes a disabled clause.
-  \item $\arrayd{variables}{|\variables{}|}{[0, \maxArity{}]}$: how many times
-    each variable appears in the head atom.
-  \item $\arrayd{constants}{\maxArity{}}{\constants{} \cup \{ \Box \}}$, where
-    $\Box$ denotes that the position is reserved for a variable.
+  \item a $\variable{predicate} \in \predicates \cup \{ \Box \}$, where $\Box$
+    denotes a disabled clause,
+  \item and $\arrayd{arguments}{\maxArity{}}{\constants{} \cup \variables{}}$.
   \end{itemize}
-  We define the \variable{predicate}'s \variable{arity} using the
-  \variable{table} constraint as
+\end{definition}
+
+\begin{definition}
+  The \variable{predicate}'s $\variable{arity} \in [0, \maxArity{}]$ can then be
+  defined using the \variable{table} constraint as
   \[
@@
 \begin{constraint}
-  For each $v \in \variable{variables}$, $v \le \variable{arity}$.
-\end{constraint}
-
-\begin{constraint}
   For $i = 0, \dots, \maxArity{} - 1$,
   \[
-    i \ge \variable{arity} \implies \variable{constants}[i] = \Box.
+    i \ge \variable{arity} \implies \variable{arguments}[i] = 0.
   \]
@@
 
+\begin{definition} We define an array \variable{occurrences} of $|\variables{}|$
+  sets such that, for all $v \in \variables{}$, $\variable{occurrences}[v]$ is a
+  subset of $\{ 0, \dots, \maxArity{} - 1\}$ that stores the indices of
+  \variable{arguments} at which $v$ is located. It is defined by the
+  \variable{setsIntsChanneling} constraint equivalent to the following
+  condition: for $i = 0, \dots, \maxArity{} - 1$ and $v \in \variables{}$,
+  \[
+    \variable{arguments}[i] = v \quad \iff \quad i \in \variable{occurrences}[v].
+  \]
+\end{definition}
+
+\begin{definition}
+  We define a $|\variables{}| \times 2$ matrix $\mathbf{M}$ with domain $[0,
+  \maxArity{}]$ such that for $v = 0, \dots, |\variables{}| - 1$,
+  \begin{align*}
+    \mathbf{M}_{v,0} &= |\variable{occurrences}[v]|.\\
+    \mathbf{M}_{v,1} &= \begin{cases}
+      \min \variable{occurrences}[v] & \text{if } \variable{occurrences}[v] \ne \emptyset\\
+      0\footnotemark & \text{otherwise.}
+    \end{cases}
+  \end{align*}
+\end{definition}
+\footnotetext{This could be any fixed value in the domain.}
+
 \begin{constraint}
-  Connecting the two lists:
+  We can then impose the \variable{lexChainLessEq} constraint on $\mathbf{M}$
+  which means that for $v = 1, \dots, |\variables{}| - 1$,
   \[
-    \maxArity{} - \variable{arity} + \sum_{v \in \variable{variables}} v
-    = \begin{cases}
-      \maxArity{} & \text{if } \variable{predicate} = \Box \\
-      \variable{count}(\Box, \variable{constants}) & \text{otherwise}.
-      \end{cases}
+    |\variable{occurrences}[v - 1]| \le |\variable{occurrences}[v]|,
+  \]
+  and if $|\variable{occurrences}[v - 1]| = |\variable{occurrences}[v]| > 0$,
+  then
+  \[
+    \min \variable{occurrences}[v - 1] \le \min \variable{occurrences}[v].
   \]
@@
 
-In \variable{variables}, all zeros must go after all non-zeros. For example,
-if we have to pick one variable out of two, we must pick the first one.
-\begin{constraint}
-  For $i = 0, \dots, |\variables{}| - 2$, and $j = i + 1, \dots,
-  |\variables{}| - 1$,
-  \[
-    \variable{variables}[i] \ne 0 \quad \text{or} \quad \variable{variables}[j]
-    = 0.
-  \]
-\end{constraint}
+\begin{example}
+  Let $\maxArity{} = 4$, $\mathsf{P} \in \predicates{}$, $\variables{} = \{
+  X, Y, Z \}$. Then $\mathsf{P}(Z, Y, Z)$ would be represented as:
+  \begin{align*}
+    \variable{predicate} &= \mathsf{P},\\
+    \variable{arguments} &= [Z, Y, Z, 0],\\
+    \variable{arity} &= 3,\\
+    \variable{occurrences} &= [\emptyset, \{ 1 \}, \{ 0, 2 \}],\\
+    \mathbf{M} &= \begin{bmatrix}
+      0 & 0\\
+      1 & 1\\
+      2 & 0
+    \end{bmatrix}.
+  \end{align*}
+\end{example}
 
@@
     \node[draw,circle,gray,text=black] (not) at (-1, -1) {$\neg$};
-    \node (P) at (-1, -2) {$\variable{P}(X)$};
+    \node (P) at (-1, -2) {$\mathsf{P}(X)$};
     \node[draw,circle,gray,text=black] (and) at (1, -1) {$\land$};
-    \node (Q) at (0, -2) {$\variable{Q}(X)$};
-    \node (R) at (2, -2) {$\variable{P}(X)$};
+    \node (Q) at (0, -2) {$\mathsf{Q}(X)$};
+    \node (R) at (2, -2) {$\mathsf{P}(X)$};
     \draw[gray] (or) -- (not);
@@
 \begin{example} \label{example:formula}
-  Let $\maxNumNodes{} = 8$. Then $\neg\variable{P}(X) \lor (\variable{Q}(X)
-  \land \variable{P}(X))$ corresponds to the tree in \cref{fig:example_tree} and
+  Let $\maxNumNodes{} = 8$. Then $\neg\mathsf{P}(X) \lor (\mathsf{Q}(X)
+  \land \mathsf{P}(X))$ corresponds to the tree in \cref{fig:example_tree} and
   can be encoded as:
@@
     \variable{treeStructure} &= [0, &&0, &&0, &&1, &&2, &&2, &&6, &&7],\\
-    \variable{treeValues} &= [{\lor}, &&{\neg}, &&{\land}, \variable{P}(&&X), \variable{Q}(&&X), \variable{P}(&&X), &&\top, &&\top],\\
+    \variable{treeValues} &= [{\lor}, &&{\neg}, &&{\land}, \mathsf{P}(&&X), \mathsf{Q}(&&X), \mathsf{P}(&&X), &&\top, &&\top],\\
     \variable{numNodes} &= 6, && && && && && && &&\\
@@
 \begin{example}
-  Let $\maxArity{} = 2$, $\predicates{} = [\variable{P}, \dots]$, $\arities{}
+  Let $\maxArity{} = 2$, $\predicates{} = [\mathsf{P}, \dots]$, $\arities{}
   = [1, \dots]$, and $X \in \variables{}$. Then the node representing atom
-  $\variable{P}(X)$ has:
+  $\mathsf{P}(X)$ has:
   \begin{align*}
-    \variable{name} &= \variable{P},\\
+    \variable{name} &= \mathsf{P},\\
     \variable{arguments} &= [X, 0],\\
@@
 \begin{constraint}
-  Each predicate gets at least one clause. Let $P = \{ h.\variable{predicate}
-  \mid h \in \variable{headsOfClauses} \}$. Then
+  Each predicate gets at least one clause. Let
+  \[
+    P = \{ h.\variable{predicate} \mid h \in \variable{headsOfClauses} \}.
+  \]
+  Then
   \[
@@
   \]
+  Here, $\variable{nValues}(P)$ counts the number of unique values in $P$.
 \end{constraint}
@@
 For example, $\preceq$ can be implemented as \variable{lexLessEq} over the
-decision variables of each body.
+decision variables of each body. % TODO: can this be turned into lexChainLessEq?
 
@@
 \section{Counting Programs}
+% TODO: update to account for the new definition of head
 
@@
 
-\section{The Independence Constraint}
+\section{Predicate Independence}
 
-% TODO: define independence of predicates
-% Formal definition (here and in the predicate invention paper): two
-% predicates are independent if all of their groundings are independent.
+\begin{definition}
+  Let $\mathscr{P}$ be a probabilistic logic program. Its \emph{predicate
+    dependency graph} is a directed graph $G_{\mathscr{P}} = (V, E)$ with the
+  set of nodes $V$ consisting of all predicates in $\mathscr{P}$. We add an edge
+  from predicate $\mathsf{P}$ to predicate $\mathsf{Q}$ if there is a clause in
+  $\mathscr{P}$ with $\mathsf{Q}$ as the head and $\mathsf{P}$ mentioned in the
+  body.
+\end{definition}
+
+\begin{definition}
+  Let $\mathsf{P}$ be a predicate in a program $\mathscr{P}$. The
+  \emph{dependencies} of $\mathsf{P}$ is the smallest set $D_{\mathsf{P}}$ such
+  that:
+  \begin{itemize}
+  \item $\mathsf{P} \in D_{\mathsf{P}}$,
+  \item for every $\mathsf{Q} \in D_{\mathsf{P}}$, the nodes with arrows to
+    $\mathsf{Q}$ in $G_{\mathscr{P}}$ are all in $D_{\mathsf{P}}$.
+  \end{itemize}
+\end{definition}
+
+\begin{definition}
+  Two predicates $\mathsf{P}$ and $\mathsf{Q}$ are \emph{independent} if
+  $D_{\mathsf{P}} \cap D_{\mathsf{Q}} = \emptyset$.
+\end{definition}
 

### 2020-01-02 src/main/Body.java

@@ -27,6 +27,10 @@ public class Body {
         for (int i = 0; i < maxNumNodes; i++)
             treeValues[i] = new Node(model);
 
+        // Convenient for testing purposes
+        // TODO: comment it out!
+        model.arithm(treeValues[0].getPredicate(), "=", Token.TRUE.ordinal()).post();
+
         // Tree structure
         IntVar numTrees = model.intVar(1, maxNumNodes);
         model.tree(treeStructure, numTrees).post();

### 2020-01-02 src/main/GeneratePrograms.java

@@ -21,16 +21,16 @@ class GeneratePrograms {
     private static final String DIRECTORY = "../programs/";
     private static final int NUM_SOLUTIONS = 10000;
     private static int MAX_NUM_NODES = 1;
-    private static int MAX_NUM_CLAUSES = 2;
+    private static int MAX_NUM_CLAUSES = 1;
     private static final boolean FORBID_ALL_CYCLES = false;
     //private static final double[] PROBABILITIES = {0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9,
     //        1, 1, 1, 1, 1, 1}; // let's make probability 1 a bit more likely
     private static final double[] PROBABILITIES = {1};
 
     static String[] PREDICATES = {"p"};
-    static int[] ARITIES = {1};
-    static String[] VARIABLES = {"X"};
-    static String[] CONSTANTS = {"a"};
+    static int[] ARITIES = {3};
+    static String[] VARIABLES = {"X", "Y", "Z"};
+    static String[] CONSTANTS = {};
     static int MAX_ARITY = Arrays.stream(ARITIES).max().getAsInt();
 
     static Tuples arities;
@@ -168,7 +168,7 @@ class GeneratePrograms {
 
     private static void saveProgramsToFiles() throws IOException {
         for (int i = 0; i < NUM_SOLUTIONS && model.getSolver().solve(); i++) {
-            System.out.println("========== " + i + " ==========");
+            //System.out.println("========== " + i + " ==========");
             StringBuilder program = new StringBuilder();
             for (int j = 0; j < MAX_NUM_CLAUSES; j++)
                 program.append(clauseToString(j, rng));
@@ -180,12 +180,7 @@ class GeneratePrograms {
         }
     }
 
-    public static void main(String[] args) throws IOException {
-        /*setUp();
-        //setUpExtraConditions();
-        configureSearchStrategy();
-        saveProgramsToFiles();*/
-
+    private static void checkNumPrograms() throws IOException {
         BufferedReader reader = new BufferedReader(new FileReader("../program_counts.csv"));
         String row;
         while ((row = reader.readLine()) != null) {
@@ -236,5 +231,12 @@ class GeneratePrograms {
             }
         }
         reader.close();
+    }
+
+    public static void main(String[] args) throws IOException {
+        setUp();
+        //setUpExtraConditions();
+        configureSearchStrategy();
+        saveProgramsToFiles();
     }
 }

### 2020-01-02 src/main/Head.java

@@ -3,104 +3,70 @@ package main;
 import org.chocosolver.solver.Model;
 import org.chocosolver.solver.constraints.Constraint;
 import org.chocosolver.solver.variables.IntVar;
-import org.chocosolver.util.tools.ArrayUtils;
+import org.chocosolver.solver.variables.SetVar;
 
 /** The head of a clause */
 class Head {
 
     private IntVar predicate; // PREDICATES.length means that the clause is disabled
+    private IntVar[] arguments;
     private IntVar arity;
-    private IntVar[] variables; // How many times each variable should be included as an argument
-    // A map from positions to constants, where 0 means that either that position is disabled or occupied by a variable
-    private IntVar[] constants;
-
-    // Auxiliary variables
-    private IntVar sumOfVars;
-    private IntVar variableCount;
-    private IntVar negRemainingArity;
 
     Head(Model model, IntVar predicate) {
         this.predicate = predicate;
 
+        // Define arity
         IntVar indexToTable = model.intOffsetView(predicate, Token.values().length);
         arity = model.intVar(0, GeneratePrograms.MAX_ARITY);
         model.table(indexToTable, arity, GeneratePrograms.arities).post();
 
-        variables = model.intVarArray(GeneratePrograms.VARIABLES.length, 0, GeneratePrograms.MAX_ARITY);
-        for (IntVar variable : variables)
-            model.arithm(variable, "<=", arity).post();
-
-        constants = model.intVarArray(GeneratePrograms.MAX_ARITY, 0, GeneratePrograms.CONSTANTS.length);
-        for (int i = 0; i < constants.length; i++) {
+        // Arity regulates how many arguments the predicate has
+        arguments = model.intVarArray(GeneratePrograms.MAX_ARITY, 0,
+                GeneratePrograms.CONSTANTS.length + GeneratePrograms.VARIABLES.length - 1);
+        for (int i = 0; i < arguments.length; i++) {
             Constraint iGeArity = model.arithm(arity, "<=", i);
-            Constraint isDisabled = model.arithm(constants[i], "=", GeneratePrograms.CONSTANTS.length);
+            Constraint isDisabled = model.arithm(arguments[i], "=", GeneratePrograms.CONSTANTS.length);
             model.ifThen(iGeArity, isDisabled);
         }
 
-        // Connecting the two arrays
-        // countZeros - (MAX_ARITY - arity) = sumOfVars
-        variableCount = model.intVar(0, constants.length);
[…]

### 2020-01-02 paper/paper.tex
Counting is closer to working

@@
 \begin{itemize}
-\item Heads are too restrictive: $\mathsf{P}(X, Y, X)$ should be allowed.
+\item Construct matrix M for variables that don't participate in the head. Have
+  a variable variablesThatParticipateInTheHead that separates the set of
+  variables.
 \item A constraint for logical equivalence. An algorithm to reduce each tree to
-  some kind of normal form.
+  some kind of normal form. Not doing this on purpose. Leaving for further work.
 \item Perhaps negative cycle detection could use the same graph as the
@@
   \[
-    i \ge \variable{arity} \implies \variable{arguments}[i] = 0.
+    i \ge \variable{arity} \implies \variable{arguments}[i] = |\constants{}| +
+    |\variables{}| - 1.
   \]
 \end{constraint}
+In other words, we fix the unused arguments to be the last variable in
+$\variables{}$ if there are any, and a constant otherwise. Because of the way
+constants and variables are ordered, this is the only constant value in $\{ 0,
+\dots, |\constants{}| + |\variables{}| - 1 \}$ that satisfies all other
+constraints on the head.
 
-\begin{definition} We define an array \variable{occurrences} of $|\variables{}|$
-  sets such that, for all $v \in \variables{}$, $\variable{occurrences}[v]$ is a
-  subset of $\{ 0, \dots, \maxArity{} - 1\}$ that stores the indices of
-  \variable{arguments} at which $v$ is located. It is defined by the
-  \variable{setsIntsChanneling} constraint equivalent to the following
-  condition: for $i = 0, \dots, \maxArity{} - 1$ and $v \in \variables{}$,
-  \[
-    \variable{arguments}[i] = v \quad \iff \quad i \in \variable{occurrences}[v].
-  \]
-\end{definition}
-
-\begin{definition}
-  We define a $|\variables{}| \times 2$ matrix $\mathbf{M}$ with domain $[0,
-  \maxArity{}]$ such that for $v = 0, \dots, |\variables{}| - 1$,
-  \begin{align*}
-    \mathbf{M}_{v,0} &= |\variable{occurrences}[v]|.\\
-    \mathbf{M}_{v,1} &= \begin{cases}
-      \min \variable{occurrences}[v] & \text{if } \variable{occurrences}[v] \ne \emptyset\\
-      0\footnotemark & \text{otherwise.}
-    \end{cases}
-  \end{align*}
-\end{definition}
-\footnotetext{This could be any fixed value in the domain.}
-
-\begin{constraint}
-  We can then impose the \variable{lexChainLessEq} constraint on $\mathbf{M}$
-  which means that for $v = 1, \dots, |\variables{}| - 1$,
-  \[
-    |\variable{occurrences}[v - 1]| \le |\variable{occurrences}[v]|,
-  \]
-  and if $|\variable{occurrences}[v - 1]| = |\variable{occurrences}[v]| > 0$,
-  then
-  \[
-    \min \variable{occurrences}[v - 1] \le \min \variable{occurrences}[v].
-  \]
-\end{constraint}
-
+% TODO: will need to be updated
 \begin{example}
-  Let $\maxArity{} = 4$, $\mathsf{P} \in \predicates{}$, $\variables{} = \{
-  X, Y, Z \}$. Then $\mathsf{P}(Z, Y, Z)$ would be represented as:
+  Let $\maxArity{} = 4$, $\mathsf{P} \in \predicates{}$, $\constants{} = \{ a
+  \}$, $\variables{} = \{X, Y, Z \}$. Then $\mathsf{P}(Z, Y, Z)$ would be
+  represented as:
   \begin{align*}
@@
     \variable{arity} &= 3,\\
-    \variable{occurrences} &= [\emptyset, \{ 1 \}, \{ 0, 2 \}],\\
+    \variable{occurrences} &= [\emptyset, \emptyset, \{ 1 \}, \{ 0, 2 \}],\\
     \mathbf{M} &= \begin{bmatrix}
@@
 
-If the clause should be disabled, $\variable{numNodes} = 1$ and
-$\variable{treeValues}[0].\variable{name} = \top$.
+\begin{constraint}
+  For $i = 0, \dots, \maxNumClauses{} - 1$, if
+  $\variable{headsOfClauses}[i].\variable{predicate} = \Box$, then
+  \[
+    \variable{bodiesOfClauses}[i].\variable{numNodes} = 1,
+  \]
+  and
+  \[
+    \variable{bodiesOfClauses}[i].\variable{treeValues}[0].\variable{name} =
+    \top.
+  \]
+\end{constraint}
 
-\section{Managing Clauses}
+\section{Eliminating Variable Symmetries}
+% TODO: the matrix should include two more columns for bodies
+
+\begin{definition} We define an array \variable{occurrences} of $|\constants{}|
+  + |\variables{}|$ sets such that, for all $t \in \constants{} \cup
+  \variables{}$, $\variable{occurrences}[t]$ is a subset of $\{ 0, \dots,
+  \maxArity{} - 1\}$ that stores the indices of \variable{arguments} at which
+  $t$ is located. It is defined by the \variable{setsIntsChanneling} constraint
+  equivalent to the following condition: for $i = 0, \dots, \maxArity{} - 1$ and
+  $t \in \constants{} \cup \variables{}$,
+  \[
+    \variable{arguments}[i] = t \quad \iff \quad i \in \variable{occurrences}[t].
+  \]
+\end{definition}
+
+\begin{definition}
+  We define a $|\variables{}| \times 2$ matrix $\mathbf{M}$ with domain $[0,
+  \maxArity{}]$ such that for $v = 0, \dots, |\variables{}| - 1$,
+  \begin{align*}
+    M_{v,0} &= |\variable{occurrences}[v]|.\\
+    M_{v,1} &= \begin{cases}
+      \min \variable{occurrences}[v] & \text{if } \variable{occurrences}[v] \ne \emptyset\\
+      0\footnotemark & \text{otherwise.}
+    \end{cases}
+  \end{align*}
+\end{definition}
+\footnotetext{This could be any fixed value in the domain.}
+
+\begin{constraint}
+  We can then impose the \variable{lexChainLessEq} constraint on $\mathbf{M}$
+  which means that for $v = 1, \dots, |\variables{}| - 1$,
+  \[
+    |\variable{occurrences}[v - 1]| \le |\variable{occurrences}[v]|,
+  \]
+  and if $|\variable{occurrences}[v - 1]| = |\variable{occurrences}[v]| > 0$,
+  then
+  \[
+    \min \variable{occurrences}[v - 1] \le \min \variable{occurrences}[v].
+  \]
+\end{constraint}
+
+\section{Interactions Between Clauses}
 
@@
 For example, $\preceq$ can be implemented as \variable{lexLessEq} over the
-decision variables of each body. % TODO: can this be turned into lexChainLessEq?
-
-\begin{constraint}
-  Adjacency matrix representation:
-  \begin{align*}
-    A[i][j] = 0 \iff &\nexists k: \variable{headsOfClauses}[k].\variable{predicate} = j \text{ and } \\
-    &i \in \{ a.\variable{name} \mid a \in \variable{bodiesOfClauses}[k].\variable{treeValues} \}.
-  \end{align*}
-\end{constraint}
+decision variables of each body.
+% TODO: turn this into lexChainLessEq. But before: update the counting section.
 
@@
 
-Example of ordered partitions:
-\[
-  3 = 2 + 1 = 2 + 1 = 1 + 1 + 1,
-\]
-so for $n=4$, the sum would have three terms.
-
+% TODO: does it work? explain why it works
 Number of heads for a specific predicate with arity $a \in \arities{}$:
 \[
-  H_a = |\constants{}|^a + \sum_{v=1}^a \binom{a}{v} |\constants{}|^{a-v}
-  \sum_{k=0}^{|\variables{}|-1} \binom{v-1}{k}.
+  H_a = \sum_{v = 0}^a |\constants{}|^{a-v} \sum_{k=1}^{\min\{|\variables{}|,
+    a\}} p_k(a),
 \]
-First, select the $v$ positions dedicated for variables. The remaining $a-v$
-constants can then be filled in $|\constants{}|^{a-v}$ ways. Filling $v$
-positions with $k+1$ variables in a non-decreasing manner (without skipping any
-variables) can be seen as putting $k$ `bars' in the $v-1$ spaces between $v$
-positions. Each bar represents switching to the next variable.
+where $p_k(a)$ denotes the number of ways to partition integer $a$ into exactly
+$k$ parts.
 
@@
   $D_{\mathsf{P}} \cap D_{\mathsf{Q}} = \emptyset$.
+\end{definition}
+
+\begin{definition}[Adjacency matrix representation]
+  An $|\predicates{}| \times |\predicates{}|$ adjacency matrix $\mathbf{A}$
+  defined by
+  \begin{align*}
+    A_{i,j} = 0 \iff &\nexists k: \variable{headsOfClauses}[k].\variable{predicate} = j \text{ and } \\
+    &i \in \{ a.\variable{name} \mid a \in \variable{bodiesOfClauses}[k].\variable{treeValues} \}.
+  \end{align*}
 \end{definition}

### 2020-01-02 src/main/Body.java

@@ -8,7 +8,6 @@ import org.chocosolver.util.tools.ArrayUtils;
 import propagators.Sign;
 import propagators.SignedPredicate;
 
-import java.util.Arrays;
 import java.util.LinkedList;
 import java.util.List;
 
@@ -28,8 +27,7 @@ public class Body {
             treeValues[i] = new Node(model);
 
         // Convenient for testing purposes
-        // TODO: comment it out!
-        model.arithm(treeValues[0].getPredicate(), "=", Token.TRUE.ordinal()).post();
+        //model.arithm(treeValues[0].getPredicate(), "=", Token.TRUE.ordinal()).post();
 
         // Tree structure
         IntVar numTrees = model.intVar(1, maxNumNodes);
@@ -194,20 +192,6 @@ public class Body {
             }
         }
         return output.toString();
-    }
-
-    public void report() {
-        System.out.print("structure: " + arrayToString(treeStructure));
-        System.out.println("values: " + Arrays.toString(treeValues));
-        System.out.println();
-    }
-
-    private static String arrayToString(IntVar[] array) {
-        StringBuilder builder = new StringBuilder();
-        for (IntVar i : array)
-            builder.append(i.getValue()).append(" ");
-        builder.append("\n");
-        return builder.toString();
     }
 
     @Override

### 2020-01-04 paper/paper.tex
Variable symmetry elimination still needs some work

@@
 \begin{itemize}
-\item Construct matrix M for variables that don't participate in the head. Have
-  a variable variablesThatParticipateInTheHead that separates the set of
-  variables.
 \item A constraint for logical equivalence. An algorithm to reduce each tree to
@@
 
-% TODO: will need to be updated
-\begin{example}
-  Let $\maxArity{} = 4$, $\mathsf{P} \in \predicates{}$, $\constants{} = \{ a
-  \}$, $\variables{} = \{X, Y, Z \}$. Then $\mathsf{P}(Z, Y, Z)$ would be
-  represented as:
-  \begin{align*}
-    \variable{predicate} &= \mathsf{P},\\
-    \variable{arguments} &= [Z, Y, Z, 0],\\
-    \variable{arity} &= 3,\\
-    \variable{occurrences} &= [\emptyset, \emptyset, \{ 1 \}, \{ 0, 2 \}],\\
-    \mathbf{M} &= \begin{bmatrix}
-      0 & 0\\
-      1 & 1\\
-      2 & 0
-    \end{bmatrix}.
-  \end{align*}
-\end{example}
-
 \section{Bodies of Clauses}
@@
   A \emph{node} has a $\variable{name} \in \tokens{} \cup \predicates{}$ and
-  $\arrayd{arguments}{\maxArity{}}{\variables{} \cup \constants{}}$. The node's
+  $\arrayd{arguments}{\maxArity{}}{\variables{} \cup \constants{} \cup \{ \Box
+    \}}$, where $\Box$ denotes a disabled argument (the reason why this value is
+  needed will become clear in \cref{sec:variable_symmetry}). The node's
   $\variable{arity} \in [0, \maxArity{}]$ is defined by a \variable{table}
@@
 \begin{constraint}
-  For $i = 0, \dots, \maxArity{} - 1$,
-  \[
-    i \ge \variable{arity} \implies \variable{arguments}[i] = 0\footnote{Zero
-      here represents the first variable or constant, regardless of what it is.}.
-  \]
+  For $i = 0, \dots, \maxArity{} - 1$, if $i \ge \variable{arity}$, then
+  $\variable{arguments}[i] = \Box$, else $\variable{arguments}[i] \ne \Box$.
 \end{constraint}
@@
     \variable{name} &= \mathsf{P},\\
-    \variable{arguments} &= [X, 0],\\
+    \variable{arguments} &= [X, \Box],\\
     \variable{arity} &= 1.
@@
 
-\section{Eliminating Variable Symmetries}
-% TODO: the matrix should include two more columns for bodies
+\section{Eliminating Variable Symmetries} \label{sec:variable_symmetry}
 
-\begin{definition} We define an array \variable{occurrences} of $|\constants{}|
-  + |\variables{}|$ sets such that, for all $t \in \constants{} \cup
-  \variables{}$, $\variable{occurrences}[t]$ is a subset of $\{ 0, \dots,
-  \maxArity{} - 1\}$ that stores the indices of \variable{arguments} at which
-  $t$ is located. It is defined by the \variable{setsIntsChanneling} constraint
-  equivalent to the following condition: for $i = 0, \dots, \maxArity{} - 1$ and
-  $t \in \constants{} \cup \variables{}$,
+Given any clause, we can permute the variables in it without changing the
+meaning of the clause or the entire program. Thus, we want to fix an order on
+variables to eliminate unnecessary symmetries. Informally, we can say that
+variable $X$ goes before variable $Y$ if its first occurrence in either the head
+or the body of the clause is before the first occurrence of $Y$.
+
+\begin{definition}
+  Head:
+
+  size: $|\constants{}| + |\variables{}|$
+
+  domain: $\{ 0, \dots, \maxArity{} - 1\}$
+
+  condition: for $i = 0, \dots, \maxArity{} - 1$ and $t \in \constants{} \cup \variables{}$,
   \[
@@
   \]
+
+  Body:
+
+  size: $|\constants{}| + |\variables{}| + 1$
+
+  domain: $\maxNumNodes{} \times \maxArity{}$
+
+  condition: for $i = 0, \dots, \maxNumNodes{} - 1$, $j = 0, \dots, \maxArity{}
+  - 1$, $t \in \constants{} \cup \variables{} \cup \{ \Box \}$,
+  \[
+    \variable{treeValues}[i].\variable{arguments}[j] = t \quad \iff \quad i
+    \times \maxNumNodes{} + j \in \variable{occurrences}[t]
+  \]
+
+  We define an array \variable{occurrences} of  sets such that, for all $t \in
+  \constants{} \cup \variables{}$, $\variable{occurrences}[t]$ is a subset of
+  that stores the indices of \variable{arguments} at which $t$ is located. It is
+  defined by the \variable{setsIntsChanneling} constraint equivalent to the
+  following condition:
 \end{definition}
@@
   We define a $|\variables{}| \times 2$ matrix $\mathbf{M}$ with domain $[0,
-  \maxArity{}]$ such that for $v = 0, \dots, |\variables{}| - 1$,
+  \maxNumNodes{} \times \maxArity{}]$ such that for $v = 0, \dots, |\variables{}| - 1$,
   \begin{align*}
@@
       \min \variable{occurrences}[v] & \text{if } \variable{occurrences}[v] \ne \emptyset\\
-      0\footnotemark & \text{otherwise.}
+      \maxNumNodes{} \times \maxArity{} & \text{otherwise.}
     \end{cases}
@@
 \end{definition}
-\footnotetext{This could be any fixed value in the domain.}
 
@@
 \end{constraint}
+
+\begin{example}
+  Let $\maxArity{} = 4$, $\mathsf{P} \in \predicates{}$, $\constants{} = \{ a
+  \}$, $\variables{} = \{X, Y, Z \}$. Then $\mathsf{P}(Z, Y, Z)$ would be
+  represented as:
+  \begin{align*}
+    \variable{predicate} &= \mathsf{P},\\
+    \variable{arguments} &= [Z, Y, Z, 0],\\
+    \variable{arity} &= 3,\\
+    \variable{occurrences} &= [\emptyset, \emptyset, \{ 1 \}, \{ 0, 2 \}],\\
+    \mathbf{M} &= \begin{bmatrix}
+      0 & 0\\
+      1 & 1\\
+      2 & 0
+    \end{bmatrix}.
+  \end{align*}
+\end{example}
 
@@
 decision variables of each body.
-% TODO: turn this into lexChainLessEq. But before: update the counting section.
+% TODO: turn this into lexChainLessEq
 
@@
 
-% TODO: does it work? explain why it works
+% TODO: explain how it works
 Number of heads for a specific predicate with arity $a \in \arities{}$:
@@
   \sum_{\substack{ \sum_{i=1}^{|\predicates{}|} h_i = n,\\
-%      h_1 + \dots + h_{|\predicates{}|} = n,\\
       |\predicates{}| \le n \le \maxNumClauses,\\
@@
 This is without any kind of cycle detection and without probabilities.
-% TODO: describe what parameter values were used to test the model.
+% TODO: describe what parameter values were used to test the model (or... not).
 

### 2020-01-04 src/main/GeneratePrograms.java

@@ -11,6 +11,7 @@ import org.chocosolver.solver.search.strategy.Search;
 import org.chocosolver.solver.search.strategy.selectors.values.IntDomainRandom;
 import org.chocosolver.solver.search.strategy.selectors.variables.Random;
 import org.chocosolver.solver.variables.IntVar;
+import org.chocosolver.solver.variables.SetVar;
 import org.chocosolver.util.tools.ArrayUtils;
 import propagators.NegativeCyclePropagator;
 
@@ -29,8 +30,8 @@ class GeneratePrograms {
 
     static String[] PREDICATES = {"p"};
     static int[] ARITIES = {1};
-    static String[] VARIABLES = {"Z", "Y", "X"};
-    static String[] CONSTANTS = {};
+    static String[] VARIABLES = {"X", "Y", "Z"};
+    static String[] CONSTANTS = {"a"};
     static int MAX_ARITY = Arrays.stream(ARITIES).max().getAsInt();
 
     static Tuples arities;
@@ -40,10 +41,24 @@ class GeneratePrograms {
     private static Head[] clauseHeads; // full heads (predicates, variables, constants)
     private static Body[] bodies; // the body of each clause
     private static IntVar[] decisionVariables; // all decision variables relevant to the problem
+    private static IntVar[][][] M; // a tensor for eliminating variable symmetries
     private static java.util.Random rng;
 
     /** The entire clause, i.e., both body and head */
     private static String clauseToString(int i, java.util.Random rng) {
+        // Print M
+        for (int j = 0; j < M[i].length; j++) {
+            for (int k = 0; k < M[i][j].length; k++)
+                System.out.print(M[i][j][k].getValue() + " ");
+            System.out.println();
+        }
+
+        System.out.print("Occurrences of variables in the body: ");
+        SetVar[] bodyOccurrences = bodies[i].getOccurrences();
+        for (int j = 0; j < bodyOccurrences.length; j++)
+            System.out.print(bodyOccurrences[j].getValue() + " ");
+        System.out.println();
+
         // Is this clause disabled?
         int predicate = clauseAssignments[i].getValue();
         if (predicate == PREDICATES.length)
@@ -133,6 +148,25 @@ class GeneratePrograms {
             }
         }
 
+        // Remove variable symmetries
+        M = new IntVar[MAX_NUM_CLAUSES][][];
[…]

### 2020-01-04 src/main/Head.java

@@ -11,6 +11,7 @@ class Head {
     private IntVar predicate; // PREDICATES.length means that the clause is disabled
     private IntVar[] arguments;
     private IntVar arity;
+    private SetVar[] occurrences;
 
     Head(Model model, IntVar predicate) {
         this.predicate = predicate;
@@ -34,24 +35,13 @@ class Head {
         for (int i = 0; i < GeneratePrograms.MAX_ARITY; i++)
             possibleIndices[i] = i;
         // For each variable, we store the set of indices where it occurs
-        SetVar[] occurrences = model.setVarArray(GeneratePrograms.CONSTANTS.length +
+        occurrences = model.setVarArray(GeneratePrograms.CONSTANTS.length +
                 GeneratePrograms.VARIABLES.length, new int[0], possibleIndices);
         model.setsIntsChanneling(occurrences, arguments).post();
+    }
 
-        // Information about occurrences that we're going to sort
-        IntVar[][] occurrenceCardAndMin = model.intVarMatrix(GeneratePrograms.VARIABLES.length, 2, 0,
-                GeneratePrograms.MAX_ARITY);
-        for (int i = 0; i < GeneratePrograms.VARIABLES.length; i++) {
-            occurrenceCardAndMin[i][0] = occurrences[GeneratePrograms.CONSTANTS.length + i].getCard();
-            model.min(occurrences[GeneratePrograms.CONSTANTS.length + i], occurrenceCardAndMin[i][1],
-                    false).post();
-            SetVar[] occurrencesAtI = new SetVar[1];
-            occurrencesAtI[0] = occurrences[GeneratePrograms.CONSTANTS.length + i];
-            Constraint noOccurrences = model.nbEmpty(occurrencesAtI, 1);
-            Constraint fixMinOccurrence = model.arithm(occurrenceCardAndMin[i][1], "=", 0);
-            model.ifThen(noOccurrences, fixMinOccurrence);
-        }
-        model.lexChainLessEq(occurrenceCardAndMin).post();
+    SetVar[] getOccurrences() {
+        return occurrences;
     }
 
     public IntVar[] getDecisionVariables() {

### 2020-01-04 src/main/Node.java

@@ -12,7 +12,7 @@ class Node {
     private IntVar arity;
 
     Node(Model model) {
-        int numPossibleArguments = GeneratePrograms.VARIABLES.length + GeneratePrograms.CONSTANTS.length;
+        int numPossibleArguments = GeneratePrograms.VARIABLES.length + GeneratePrograms.CONSTANTS.length + 1;
         predicate = model.intVar(0, GeneratePrograms.PREDICATES.length + Token.values().length - 1);
         arguments = model.intVarArray(GeneratePrograms.MAX_ARITY, 0, numPossibleArguments - 1);
 
@@ -21,10 +21,11 @@ class Node {
         arity = model.intVar(0, GeneratePrograms.MAX_ARITY);
         model.table(predicate, arity, GeneratePrograms.arities).post();
         for (int i = 0; i < arguments.length; i++) {
-            // If i >= arity, then arguments[i] must be zero
+            // If i >= arity, then arguments[i] must be undefined
             Constraint iGTEQArity = model.arithm(arity, "<=", i);
-            Constraint fixArgument = model.arithm(arguments[i], "=", 0);
-            model.ifThen(iGTEQArity, fixArgument);
+            Constraint fixArgument = model.arithm(arguments[i], "=", numPossibleArguments - 1);
+            Constraint notDisabled = model.arithm(arguments[i], "!=", numPossibleArguments - 1);
+            model.ifThenElse(iGTEQArity, fixArgument, notDisabled);
         }
     }
 
@@ -34,6 +35,10 @@ class Node {
 
     IntVar[] getDecisionVariables() {
         return ArrayUtils.concat(arguments, predicate);
+    }
+
+    IntVar[] getArguments() {
+        return arguments;
     }
 
     @Override
@@ -54,11 +59,6 @@ class Node {
             }
         }
         atom.append(")");
-
-        /*atom.append(" (");
-        atom.append(arity.getValue());
-        atom.append(")");*/
-
         return atom.toString();
     }
 }

### 2020-01-07 src/main/Body.java
Treating each clause uniformly, without dividing it into two parts

@@ -3,7 +3,6 @@ package main;
 import org.chocosolver.solver.Model;
 import org.chocosolver.solver.constraints.Constraint;
 import org.chocosolver.solver.variables.IntVar;
-import org.chocosolver.solver.variables.SetVar;
 import org.chocosolver.util.iterators.DisposableValueIterator;
 import org.chocosolver.util.tools.ArrayUtils;
 import propagators.Sign;
@@ -17,7 +16,7 @@ public class Body {
     private int maxNumNodes;
     private IntVar[] treeStructure;
     private Node[] treeValues;
-    private SetVar[] occurrences;
+    private IntVar[] arguments; // concatenated arguments of all nodes in treeValues
 
     public Body(Model model, IntVar assignment, int maxNumNodes) {
         this.maxNumNodes = maxNumNodes;
@@ -27,9 +26,6 @@ public class Body {
         treeValues = new Node[maxNumNodes];
         for (int i = 0; i < maxNumNodes; i++)
             treeValues[i] = new Node(model);
-
-        // Convenient for testing purposes
-        //model.arithm(treeValues[0].getPredicate(), "=", Token.TRUE.ordinal()).post();
 
         // Tree structure
         IntVar numTrees = model.intVar(1, maxNumNodes);
@@ -85,20 +81,14 @@ public class Body {
         model.ifThen(shouldBeDisabled, model.and(oneNode, alwaysTrue));
 
         int numIndices = treeValues.length * GeneratePrograms.MAX_ARITY;
-        IntVar[] arguments = new IntVar[numIndices];
+        arguments = new IntVar[numIndices];
         for (int i = 0; i < treeValues.length; i++)
             System.arraycopy(treeValues[i].getArguments(), 0, arguments, i * GeneratePrograms.MAX_ARITY,
                     GeneratePrograms.MAX_ARITY);
-        int[] possibleIndices = new int[numIndices];
-        for (int i = 0; i < numIndices; i++)
-            possibleIndices[i] = i;
-        occurrences = model.setVarArray(GeneratePrograms.VARIABLES.length + GeneratePrograms.CONSTANTS.length + 1,
-                new int[0], possibleIndices);
-        model.setsIntsChanneling(occurrences, arguments).post();
     }
 
-    SetVar[] getOccurrences() {
-        return occurrences;
+    IntVar[] getArguments() {
+        return arguments;
     }
 
     /** A list of predicates featured in this clause. The sign of each predicate denotes whether the predicate is

### 2020-01-07 src/main/GeneratePrograms.java

@@ -41,23 +41,28 @@ class GeneratePrograms {
     private static Head[] clauseHeads; // full heads (predicates, variables, constants)
     private static Body[] bodies; // the body of each clause
     private static IntVar[] decisionVariables; // all decision variables relevant to the problem
-    private static IntVar[][][] M; // a tensor for eliminating variable symmetries
+    private static IntVar[][] termsPerClause; // a flattened-out view of the term positions in each clause
+    private static SetVar[][] occurrences; // for each clause and variable, a set of positions with that variable
+    private static IntVar[][] M; // for eliminating variable symmetries
     private static java.util.Random rng;
 
     /** The entire clause, i.e., both body and head */
     private static String clauseToString(int i, java.util.Random rng) {
-        // Print M
-        for (int j = 0; j < M[i].length; j++) {
-            for (int k = 0; k < M[i][j].length; k++)
-                System.out.print(M[i][j][k].getValue() + " ");
-            System.out.println();
-        }
+        for (int j = 0; j < termsPerClause[i].length; j++)
+            System.out.print(termsPerClause[i][j].getValue() + " ");
+        System.out.println();
+        for (int j = 0; j < occurrences[i].length; j++)
+            System.out.print(occurrences[i][j].getValue() + " ");
+        System.out.println();
+        for (int j = 0; j < M[i].length; j++)
+            System.out.print(M[i][j].getValue() + " ");
+        System.out.println();
 
-        System.out.print("Occurrences of variables in the body: ");
+        /*System.out.print("Occurrences of variables in the body: ");
         SetVar[] bodyOccurrences = bodies[i].getOccurrences();
         for (int j = 0; j < bodyOccurrences.length; j++)
             System.out.print(bodyOccurrences[j].getValue() + " ");
-        System.out.println();
+        System.out.println();*/
 
         // Is this clause disabled?
         int predicate = clauseAssignments[i].getValue();
@@ -148,25 +153,38 @@ class GeneratePrograms {
             }
         }
 
-        // Remove variable symmetries
-        M = new IntVar[MAX_NUM_CLAUSES][][];
-        for (int i = 0; i < M.length; i++) {
[…]

### 2020-01-07 src/main/Head.java

@@ -3,7 +3,6 @@ package main;
 import org.chocosolver.solver.Model;
 import org.chocosolver.solver.constraints.Constraint;
 import org.chocosolver.solver.variables.IntVar;
-import org.chocosolver.solver.variables.SetVar;
 
 /** The head of a clause */
 class Head {
@@ -11,7 +10,6 @@ class Head {
     private IntVar predicate; // PREDICATES.length means that the clause is disabled
     private IntVar[] arguments;
     private IntVar arity;
-    private SetVar[] occurrences;
 
     Head(Model model, IntVar predicate) {
         this.predicate = predicate;
@@ -22,26 +20,19 @@ class Head {
         model.table(indexToTable, arity, GeneratePrograms.arities).post();
 
         // Arity regulates how many arguments the predicate has
-        arguments = model.intVarArray(GeneratePrograms.MAX_ARITY, 0,
-                GeneratePrograms.CONSTANTS.length + GeneratePrograms.VARIABLES.length - 1);
+        int numValues = GeneratePrograms.CONSTANTS.length + GeneratePrograms.VARIABLES.length;
+        arguments = model.intVarArray(GeneratePrograms.MAX_ARITY, 0, numValues);
         for (int i = 0; i < arguments.length; i++) {
             Constraint iGeArity = model.arithm(arity, "<=", i);
-            Constraint isDisabled = model.arithm(arguments[i], "=",
-                    GeneratePrograms.CONSTANTS.length + GeneratePrograms.VARIABLES.length - 1);
-            model.ifThen(iGeArity, isDisabled);
+            Constraint isDisabled = model.arithm(arguments[i], "=", numValues);
+            Constraint notDisabled = model.arithm(arguments[i], "!=", numValues);
+            model.ifThenElse(iGeArity, isDisabled, notDisabled);
         }
 
-        int[] possibleIndices = new int[GeneratePrograms.MAX_ARITY];
-        for (int i = 0; i < GeneratePrograms.MAX_ARITY; i++)
-            possibleIndices[i] = i;
-        // For each variable, we store the set of indices where it occurs
-        occurrences = model.setVarArray(GeneratePrograms.CONSTANTS.length +
-                GeneratePrograms.VARIABLES.length, new int[0], possibleIndices);
-        model.setsIntsChanneling(occurrences, arguments).post();
     }
 
-    SetVar[] getOccurrences() {
-        return occurrences;
+    IntVar[] getArguments() {
+        return arguments;
     }
 
[…]

### 2020-01-08 paper/paper.tex
Treating each clause uniformly, without dividing it into two parts
Bug fix in the code

@@
 \institute{University of Edinburgh, Edinburgh, UK\\
+  Heriot-Watt University, Edinburgh, UK\\
   \email{p.dilkas@sms.ed.ac.uk}}
@@
 \section{Heads of Clauses}
+% TODO: section for clauses. define heads & bodies, then separate subsections
+% for head and body constraints
 
@@
   \begin{itemize}
-  \item a $\variable{predicate} \in \predicates \cup \{ \Box \}$, where $\Box$
-    denotes a disabled clause,
-  \item and $\arrayd{arguments}{\maxArity{}}{\constants{} \cup \variables{}}$.
+  \item a $\variable{predicate} \in \predicates \cup \{ \Box \}$.
+  \item and $\arrayd{arguments}{\maxArity{}}{\constants{} \cup \variables{}}
+    \cup \{ \Box \}$
   \end{itemize}
+  In both cases, $\Box$ is the disabled value.
 \end{definition}
@@
   \[
-    i \ge \variable{arity} \implies \variable{arguments}[i] = |\constants{}| +
-    |\variables{}| - 1.
+    \variable{arguments}[i] = \Box \iff i \ge \variable{arity}.
   \]
 \end{constraint}
-In other words, we fix the unused arguments to be the last variable in
-$\variables{}$ if there are any, and a constant otherwise. Because of the way
-constants and variables are ordered, this is the only constant value in $\{ 0,
-\dots, |\constants{}| + |\variables{}| - 1 \}$ that satisfies all other
-constraints on the head.
 
@@
 \begin{constraint}
-  For $i = 0, \dots, \maxArity{} - 1$, if $i \ge \variable{arity}$, then
-  $\variable{arguments}[i] = \Box$, else $\variable{arguments}[i] \ne \Box$.
+  For $i = 0, \dots, \maxArity{} - 1$,
+  \[
+  \variable{arguments}[i] = \Box \quad \iff \quad i \ge \variable{arity}.
+  \]
 \end{constraint}
+% TODO: this could merged into a single constraint for termsPerClause
 
@@
 \begin{constraint}
-  For $i = 0, \dots, \maxNumClauses - 1$, let $p_i =
-  \variable{headsOfClauses}[i].\variable{predicate}$. Then
-  $(p_i)_{i=0}^{\maxNumClauses - 1}$ is sorted.
-\end{constraint}
-
-\begin{constraint}
   Each predicate gets at least one clause. Let
@@
 \begin{constraint}
-  Let $\prec$ be any total order defined over bodies of clauses, and let
-  $\preceq$ be its extension with equality (in the same way as $\le$ extends
-  $<$). If
-  \[
-    \variable{headsOfClauses}[i-1].\variable{predicate} =
-    \variable{headsOfClauses}[i].\variable{predicate},
-  \]
-  then $\variable{bodiesOfClauses}[i-1] \preceq \variable{bodiesOfClauses}[i]$.
+  Clauses are sorted.
 \end{constraint}
-For example, $\preceq$ can be implemented as \variable{lexLessEq} over the
-decision variables of each body.
-% TODO: turn this into lexChainLessEq
 
 \section{Counting Programs}
-% TODO: update to account for the new definition of head
+
+This is without any kind of cycle detection and without probabilities.
+
+Number of ways to fill $n$ positions with terms: % TODO: what's the smallest n?
+\[
+  P(n) = |\constants{}|^n + |\constants{}|^{n-1}|\variables{}| +
+  \sum_{i=0}^{n-2} |\constants{}|^i \sum_{j=0}^{\min\{|\variables{}| - 1, n - i
+    - 1\}} \binom{n-i-1}{j} (|\constants{}| + 1)^{n-i-j-1}
+\]
+where $i$ iterates over the number of constants before the first variable, and
+$j$ iterates over the number of `new variable actions'. Explain:
+$|\constants{}|+2$ possible actions.
 
 Let $p_a$ be the number of predicates in $\predicates{}$ with arity $a \in
-\arities{}$.
-
-Number of atoms (leaves of the tree):
+\arities{}$. Number of clauses with total arity $a$:
+\begin{align*}
+  C(0) &= 1,\\
+  C(a) &= \sum_{n=1}^{\maxNumNodes{}} T(n, a),
+\end{align*}
+where $T(n, a)$ is defined recursively as:
 \[
-  A = \sum_{a \in \arities{}} p_a(|\variables{}| + |\constants{}|)^a
-\]
-
-Number of clauses:
-\[
-  C = 1 + \sum_{n=1}^{\maxNumNodes{}} T(n),
-\]
-where $T(n)$ is defined recursively as:
-\[
-  T(1) = A
+  T(1, a) = p_a
 \]
@@
 \[
-  T(n) = T(n-1) + 2\sum_{\substack{c_1 + \dots + c_k = n - 1,\\
-      k \ge 2,\\
-      c_i \ge 1 \text{ for all } i}} \prod_{i=1}^k T(c_i).
+  T(n, a) = T(n-1, a) + 2\sum_{\substack{c_1 + \dots + c_k = n - 1,\\
+      2 \le k \le \frac{a}{\min \arities{}},\\
+      c_i \ge 1 \text{ for all } i}} \sum_{\substack{d_1 + \dots + d_k = a,\\
+    d_i \ge \min \arities{} \text{ for all } i}} \prod_{i=1}^k T(c_i, d_i).
 \]
-
-% TODO: explain how it works
-Number of heads for a specific predicate with arity $a \in \arities{}$:
-\[
-  H_a = \sum_{v = 0}^a |\constants{}|^{a-v} \sum_{k=1}^{\min\{|\variables{}|,
-    a\}} p_k(a),
-\]
-where $p_k(a)$ denotes the number of ways to partition integer $a$ into exactly
-$k$ parts.
 
@@
       h_i \ge 1 \text{ for all } i}} \prod_{i=1}^{|\predicates{}|}
-  \multiset{C}{h_i} H_{a_i}^{h_i},
+  \multiset{\sum_{a=0}^{\maxArity{} \times \maxNumNodes{}} C(a) P(a+a_i)}{h_i},
 \]
@@
 \[
-  \multiset{n}{k} = \binom{n + k - 1}{k}.
+  \multiset{n}{k} = \binom{n+k-1}{k}.
 \]
-
-This is without any kind of cycle detection and without probabilities.
-% TODO: describe what parameter values were used to test the model (or... not).
 

### 2020-01-09 paper/paper.tex
It looks like counting is working!

@@
 
-\institute{University of Edinburgh, Edinburgh, UK\\
-  Heriot-Watt University, Edinburgh, UK\\
+\institute{University of Edinburgh, Edinburgh, United Kingdom\\
   \email{p.dilkas@sms.ed.ac.uk}}
@@
 
-Number of ways to fill $n$ positions with terms: % TODO: what's the smallest n?
+Number of ways to fill $n$ positions with terms:
 \[
-  P(n) = |\constants{}|^n + |\constants{}|^{n-1}|\variables{}| +
-  \sum_{i=0}^{n-2} |\constants{}|^i \sum_{j=0}^{\min\{|\variables{}| - 1, n - i
-    - 1\}} \binom{n-i-1}{j} (|\constants{}| + 1)^{n-i-j-1}
+  P(n) = |\constants{}|^n + \sum_{\substack{1 \le k \le |\variables{}|, \\ 0 =
+      s_0 < s_1 < \dots < s_k < s_{k+1} = n+1}} \prod_{i=0}^k (|\constants{}| +
+  i)^{s_{i+1} - s_i - 1}
 \]
-where $i$ iterates over the number of constants before the first variable, and
-$j$ iterates over the number of `new variable actions'. Explain:
-$|\constants{}|+2$ possible actions.
 

### 2020-01-09 src/main/GeneratePrograms.java

@@ -28,10 +28,10 @@ class GeneratePrograms {
     //        1, 1, 1, 1, 1, 1}; // let's make probability 1 a bit more likely
     private static final double[] PROBABILITIES = {1};
 
-    static String[] PREDICATES = {"p"};
-    static int[] ARITIES = {1};
+    static String[] PREDICATES = {"p", "q"};
+    static int[] ARITIES = {1, 1};
     static String[] VARIABLES = {"X"};
-    static String[] CONSTANTS = {"a"};
+    static String[] CONSTANTS = {};
     static int MAX_ARITY = Arrays.stream(ARITIES).max().getAsInt();
 
     static Tuples arities;
@@ -238,7 +238,8 @@ class GeneratePrograms {
 
             int numPredicates = predicatesWithArity.stream().reduce(0, Integer::sum);
             PREDICATES = new String[numPredicates];
-            Arrays.fill(PREDICATES, "p"); // Names don't matter
+            for (int i = 0; i < numPredicates; i++)
+                PREDICATES[i] = "p" + (i + 1);
             ARITIES = new int[numPredicates];
             int k = 0;
             for (int i = 0; i < arities.size(); i++)
@@ -246,9 +247,11 @@ class GeneratePrograms {
                     ARITIES[k++] = arities.get(i);
 
             VARIABLES = new String[Integer.parseInt(data[2])];
-            Arrays.fill(VARIABLES, "X");
+            for (int i = 0; i < VARIABLES.length; i++)
+                VARIABLES[i] = "X" + (i + 1);
             CONSTANTS = new String[Integer.parseInt(data[3])];
-            Arrays.fill(CONSTANTS, "a");
+            for (int i = 0; i < CONSTANTS.length; i++)
+                CONSTANTS[i] = "a" + (i + 1);
             MAX_NUM_NODES = Integer.parseInt(data[4]);
             MAX_NUM_CLAUSES = Integer.parseInt(data[5]);
             MAX_ARITY = Arrays.stream(ARITIES).max().getAsInt();
@@ -260,7 +263,8 @@ class GeneratePrograms {
 
             // Count the number of solutions
             int i = 0;
-            System.out.println("========================================");
+            System.out.print(".");
+            //System.out.println("========================================");
             while (model.getSolver().solve()) {
                 i++;
                 /*System.out.println("=====Program=====");
@@ -279,11 +283,11 @@ class GeneratePrograms {
     }
 
[…]

### 2020-01-09 src/main/Head.java

@@ -3,6 +3,7 @@ package main;
 import org.chocosolver.solver.Model;
 import org.chocosolver.solver.constraints.Constraint;
 import org.chocosolver.solver.variables.IntVar;
+import org.chocosolver.util.tools.ArrayUtils;
 
 /** The head of a clause */
 class Head {
@@ -35,7 +36,7 @@ class Head {
     }
 
     public IntVar[] getDecisionVariables() {
-        return arguments;
+        return ArrayUtils.concat(new IntVar[]{predicate}, arguments);
     }
 
     @Override

### 2020-01-09 paper/paper.tex
Some writing on counting

@@
 
-\section{Heads of Clauses}
+\section{Considering Each Clause Separately}
+% TODO: define heads & bodies
+
+\subsection{Heads of Clauses}
 % TODO: section for clauses. define heads & bodies, then separate subsections
@@
 
-\section{Bodies of Clauses}
+\subsection{Bodies of Clauses}
 
@@
 
-\subsection{Nodes}
+\subsubsection{Nodes}
 
@@
 
-\subsection{Constraints}
+\subsubsection{Constraints}
 
@@
 
-\section{Eliminating Variable Symmetries} \label{sec:variable_symmetry}
+\subsection{Eliminating Variable Symmetries} \label{sec:variable_symmetry}
 
 Given any clause, we can permute the variables in it without changing the
-meaning of the clause or the entire program. Thus, we want to fix an order on
+meaning of the clause or the entire program. Thus, we want to fix the order of
 variables to eliminate unnecessary symmetries. Informally, we can say that
@@
 \begin{definition}
-  Head:
+  % TODO: what odes this mean? example?
+  Let $N = \maxArity{} \times (\maxNumNodes{} + 1)$. Let
+  $\variable{termsPerClause}[N] \in \constants{} \cup \variables{} \cup \{ \Box
+  \}$ be a matrix, each row of which is a flattened list of all positions for
+  terms in a particular clause.
 
-  size: $|\constants{}| + |\variables{}|$
-
-  domain: $\{ 0, \dots, \maxArity{} - 1\}$
-
-  condition: for $i = 0, \dots, \maxArity{} - 1$ and $t \in \constants{} \cup \variables{}$,
+  Then we can use the $\variable{setsIntsChanneling}$ constraint
+  to define $\variable{occurrences}[|\constants{}| + |\variables{}| + 1]$ as a
+  matrix of subsets of $\{ 0, \dots, N-1 \}$ such that for all $i = 0, \dots, N
+  - 1$, and $t \in \constants{} \cup \variables{} \cup \{ \Box \}$,
   \[
-    \variable{arguments}[i] = t \quad \iff \quad i \in \variable{occurrences}[t].
+    i \in \variable{occurrences}[t] \quad \iff \quad
+    \variable{termsPerClause}[i] = t
   \]
-
-  Body:
-
-  size: $|\constants{}| + |\variables{}| + 1$
-
-  domain: $\maxNumNodes{} \times \maxArity{}$
-
-  condition: for $i = 0, \dots, \maxNumNodes{} - 1$, $j = 0, \dots, \maxArity{}
-  - 1$, $t \in \constants{} \cup \variables{} \cup \{ \Box \}$,
-  \[
-    \variable{treeValues}[i].\variable{arguments}[j] = t \quad \iff \quad i
-    \times \maxNumNodes{} + j \in \variable{occurrences}[t]
-  \]
-
-  We define an array \variable{occurrences} of  sets such that, for all $t \in
-  \constants{} \cup \variables{}$, $\variable{occurrences}[t]$ is a subset of
-  that stores the indices of \variable{arguments} at which $t$ is located. It is
-  defined by the \variable{setsIntsChanneling} constraint equivalent to the
-  following condition:
 \end{definition}
@@
 \begin{definition}
-  We define a $|\variables{}| \times 2$ matrix $\mathbf{M}$ with domain $[0,
-  \maxNumNodes{} \times \maxArity{}]$ such that for $v = 0, \dots, |\variables{}| - 1$,
-  \begin{align*}
-    M_{v,0} &= |\variable{occurrences}[v]|.\\
-    M_{v,1} &= \begin{cases}
-      \min \variable{occurrences}[v] & \text{if } \variable{occurrences}[v] \ne \emptyset\\
-      \maxNumNodes{} \times \maxArity{} & \text{otherwise.}
+  We define $\arrayd{M}{|\variables{}|}{\{ 0, \dots, N \}}$ such that for $v \in
+  \variables{}$,
+  \[
+    \variable{M}[v] = \begin{cases}
+      \min \variable{occurrences}[v] & \text{if }
+      \variable{occurrences}[v] \ne \emptyset\\
+      N & \text{otherwise.}
     \end{cases}
-  \end{align*}
+  \]
 \end{definition}
@@
 \begin{constraint}
-  We can then impose the \variable{lexChainLessEq} constraint on $\mathbf{M}$
-  which means that for $v = 1, \dots, |\variables{}| - 1$,
-  \[
-    |\variable{occurrences}[v - 1]| \le |\variable{occurrences}[v]|,
-  \]
-  and if $|\variable{occurrences}[v - 1]| = |\variable{occurrences}[v]| > 0$,
-  then
-  \[
-    \min \variable{occurrences}[v - 1] \le \min \variable{occurrences}[v].
-  \]
+  $\variable{M}$ is sorted.
 \end{constraint}
 
-\begin{example}
+\begin{example} % TODO: update the example to cover an entire clause
   Let $\maxArity{} = 4$, $\mathsf{P} \in \predicates{}$, $\constants{} = \{ a
@@
 \section{Counting Programs}
+% TODO: define combined arity.
+% TODO: define 'gap', 'argument', 'position' or something like that.
 
-This is without any kind of cycle detection and without probabilities.
+In order to demonstrate the correctness of the model and explain it in more
+detail, in this section we are going to derive combinatorial expressions for
+counting the number of programs with up to $\maxNumClauses{}$ clauses and up to
+$\maxNumNodes{}$ nodes per clause, and arbitrary $\predicates{}$,
+$\arities{}$, $\variables{}$, and $\constants{}$. To simplify the task, we only
+consider clauses without probabilities and disable (negative) cycle elimination.
+It was experimentally confirmed that the model agrees with the combinatorial
+formula from this section in 985 different scenarios.
 
-Number of ways to fill $n$ positions with terms:
-\[
-  P(n) = |\constants{}|^n + \sum_{\substack{1 \le k \le |\variables{}|, \\ 0 =
-      s_0 < s_1 < \dots < s_k < s_{k+1} = n+1}} \prod_{i=0}^k (|\constants{}| +
-  i)^{s_{i+1} - s_i - 1}
-\]
-
-Let $p_a$ be the number of predicates in $\predicates{}$ with arity $a \in
-\arities{}$. Number of clauses with total arity $a$:
-\begin{align*}
-  C(0) &= 1,\\
-  C(a) &= \sum_{n=1}^{\maxNumNodes{}} T(n, a),
-\end{align*}
-where $T(n, a)$ is defined recursively as:
-\[
-  T(1, a) = p_a
-\]
-and
+We will first consider clauses with `gaps', i.e., without taking variables and
+constants into account. Let $T(n, a)$ denote the number of possible clause
+bodies with $n$ nodes and combined arity $a$. Then $T(1, a)$ is the number of
+predicates in $\predicates{}$ with arity $a$, and the following recursive
+definition can be applied for $n > 1$:
 \[
@@
 \]
+The first term here represents negation, i.e., negating an expression consumes
+one node but otherwise leaves the task unchanged. If the first operation is not
+negation, then it must be either conjunction or disjunction (hence the
+coefficient `2'). In the first sum, $k$ represents the number of children of the
+root node, and each $c_i$ is the number of nodes dedicated to child $i$. Thus,
+the first sum iterates over all possible ways to partition the remaining $n-1$
+nodes. Similarly, the second sum considers every possible way to partition the
+total arity $a$ across the $k$ children nodes.
+
+We can then count the number of possible clause bodies with total arity $a$ (and
+any number of nodes) as
+\[
+  C(a) = \begin{cases}
+    1 & \text{if } a = 0\\
+    \sum_{n=1}^{\maxNumNodes{}} T(n, a) & \text{otherwise.}
+  \end{cases}
+\]
+Here, the empty clause is considered separately.
+
+The number of ways to fill $n$ positions with terms can be expressed as
+\[
+  P(n) = |\constants{}|^n + \sum_{\substack{1 \le k \le |\variables{}|, \\ 0 =
+      s_0 < s_1 < \dots < s_k < s_{k+1} = n+1}} \prod_{i=0}^k (|\constants{}| +
+  i)^{s_{i+1} - s_i - 1}.
+\]
+The first term is simply the number of ways to fill all $n$ positions with
+constants. The parameter $k$ is the number of variables used in the clause, and
+$s_1, \dots, s_k$ mark the first occurrence of each variable. For each gap
+between any two introductions (or before the first introduction, or after the last
+introduction), we have $s_{i+1}-s_i-1$ spaces to be filled with any of the
+$\constants{}$ constants or any of the $i$ already-introduced variables.
 
@@
 \[
-  \multiset{n}{k} = \binom{n+k-1}{k}.
+  \multiset{n}{k} = \binom{n+k-1}{k}
 \]
+counts the number of ways to select $k$ out of $n$ items with repetition (and
+without ordering). Here, we sum over all possible ways to distribute
+$|\predicates{}| \le n \le \maxNumClauses{}$ clauses among $|\predicates{}|$
+predicates so that each predicate gets at least one clause. For each predicate,
+we can then count the number of ways to select its clauses out of all possible
+clauses. The number of possible clauses can be computed by considering each
+possible arity $a$, and multiplying the number of `unfinished' clauses $C(a)$ by
+the number of ways to fill the $a+a_i$ gaps in the body and the head of the
+clause with terms.
 

### 2020-01-09 paper/paper.tex
Editing

@@
 
-We will often use $\Box$ as a special domain value to indicate some kind of
-exception. We write $\arrayd{a}{b}{c}$ to mean that
-$\variable{a}$ is an array of variables of length $b$ such that each element of
-$\variable{a}$ has domain $c$. Similarly, we write $\arrayt{a}{b}{c}$ to denote
-an array $\variable{a}$ of length $b$ such that each element of $\variable{a}$
-has type $\variable{c}$. All constraint variables in the model are integer
-variables, but, e.g., if the integer $i$ refers to a logical variable $X$, we
-will use $i$ and $X$ interchangeably. All indices start at zero.
+% TODO: define 'gap'
+
+We will often use $\Box$ as a special domain value indicating a `disabled'
+(i.e., fixed and ignored) part of the model. We write $\arrayd{a}{b}{c}$ to mean
+that $\variable{a}$ is an array of variables of length $b$ such that each
+element of $\variable{a}$ has domain $c$. Similarly, we write $\arrayt{a}{b}{c}$
+to denote an array $\variable{a}$ of length $b$ such that each element of
+$\variable{a}$ has type $\variable{c}$. All constraint variables in the model
+are integer variables, but, e.g., if the integer $i$ refers to a logical
+variable $X$, we will use $i$ and $X$ interchangeably. All indices start at
+zero.
 
@@
 \section{Considering Each Clause Separately}
-% TODO: define heads & bodies
 
 \subsection{Heads of Clauses}
-% TODO: section for clauses. define heads & bodies, then separate subsections
-% for head and body constraints
-
-Our definition is slightly more involved because we want to eliminate some
-symmetries.
 
@@
   \end{itemize}
-  In both cases, $\Box$ is the disabled value.
 \end{definition}
+The reason why $\Box$ must be a separate value will become clear in
+\cref{sec:variable_symmetry}.
 
-\begin{definition}
+\begin{definition} \label{def:arity}
   The \variable{predicate}'s $\variable{arity} \in [0, \maxArity{}]$ can then be
@@
     \variable{arity} = \begin{cases}
-      0 & \text{if } \variable{predicate} = \Box\\
-      \text{the arity of } \variable{predicate} & \text{otherwise.}
+      \text{the arity of } \variable{predicate} & \text{if }
+      \variable{predicate} \in \predicates{}\\
+      0 & \text{otherwise.}
     \end{cases}
@@
 
-\begin{constraint}
+\begin{constraint} \label{constr:arity}
   For $i = 0, \dots, \maxArity{} - 1$,
@@
   $\arrayd{arguments}{\maxArity{}}{\variables{} \cup \constants{} \cup \{ \Box
-    \}}$, where $\Box$ denotes a disabled argument (the reason why this value is
-  needed will become clear in \cref{sec:variable_symmetry}). The node's
-  $\variable{arity} \in [0, \maxArity{}]$ is defined by a \variable{table}
-  constraint as
-  \[
-    \variable{arity} = \begin{cases}
-      \text{the arity of } \variable{name} & \text{if } \variable{name} \in
-      \predicates{}\\
-      0 & \text{otherwise.}
-    \end{cases}
-  \]
+    \}}$. The node's $\variable{arity}$ can then be
+  defined analogously to \cref{def:arity}.
 \end{definition}
 
-\begin{constraint}
-  For $i = 0, \dots, \maxArity{} - 1$,
-  \[
-  \variable{arguments}[i] = \Box \quad \iff \quad i \ge \variable{arity}.
-  \]
-\end{constraint}
-% TODO: this could merged into a single constraint for termsPerClause
+We can use \cref{constr:arity} again to disable extra arguments.
 
@@
     \variable{count}(i, \variable{treeStructure}_{-i}) = 1 &\iff \variable{treeValues}[i].\variable{name} = \neg,\\
-    \variable{count}(i, \variable{treeStructure}_{-i}) > 1 &\iff \variable{treeValues}[i].\variable{name} \in \{ \land, \lor \}.
+    \variable{count}(i, \variable{treeStructure}_{-i}) > 1 &\iff \variable{treeValues}[i].\variable{name} \in \{ \land, \lor \},
   \end{align*}
-  $\variable{treeStructure}_{-i}$ denotes array $\variable{treeStructure}$ with
-  position $i$ skipped.
+  where $\variable{treeStructure}_{-i}$ denotes array $\variable{treeStructure}$
+  with position $i$ skipped.
 \end{constraint}
@@
 \begin{definition}
-  % TODO: what odes this mean? example?
   Let $N = \maxArity{} \times (\maxNumNodes{} + 1)$. Let
-  $\variable{termsPerClause}[N] \in \constants{} \cup \variables{} \cup \{ \Box
-  \}$ be a matrix, each row of which is a flattened list of all positions for
-  terms in a particular clause.
+  $\variable{terms}[N] \in \constants{} \cup \variables{} \cup \{ \Box
+  \}$ be a flattened array of all gaps in a particular clause.
 
   Then we can use the $\variable{setsIntsChanneling}$ constraint
-  to define $\variable{occurrences}[|\constants{}| + |\variables{}| + 1]$ as a
-  matrix of subsets of $\{ 0, \dots, N-1 \}$ such that for all $i = 0, \dots, N
+  to define $\variable{occurrences}[|\constants{}| + |\variables{}| + 1]$ as an
+  array of subsets of $\{ 0, \dots, N-1 \}$ such that for all $i = 0, \dots, N
   - 1$, and $t \in \constants{} \cup \variables{} \cup \{ \Box \}$,
@@
     i \in \variable{occurrences}[t] \quad \iff \quad
-    \variable{termsPerClause}[i] = t
+    \variable{terms}[i] = t
   \]
@@
 \begin{definition}
-  We define $\arrayd{M}{|\variables{}|}{\{ 0, \dots, N \}}$ such that for $v \in
-  \variables{}$,
+  We define $\arrayd{introductions}{|\variables{}|}{\{ 0, \dots, N \}}$ such
+  that for $v \in \variables{}$,
   \[
-    \variable{M}[v] = \begin{cases}
+    \variable{introductions}[v] = \begin{cases}
       \min \variable{occurrences}[v] & \text{if }
@@
 \begin{constraint}
-  $\variable{M}$ is sorted.
+  $\variable{introductions}$ are sorted.
 \end{constraint}
 
-\begin{example} % TODO: update the example to cover an entire clause
-  Let $\maxArity{} = 4$, $\mathsf{P} \in \predicates{}$, $\constants{} = \{ a
-  \}$, $\variables{} = \{X, Y, Z \}$. Then $\mathsf{P}(Z, Y, Z)$ would be
-  represented as:
-  \begin{align*}
-    \variable{predicate} &= \mathsf{P},\\
-    \variable{arguments} &= [Z, Y, Z, 0],\\
-    \variable{arity} &= 3,\\
-    \variable{occurrences} &= [\emptyset, \emptyset, \{ 1 \}, \{ 0, 2 \}],\\
-    \mathbf{M} &= \begin{bmatrix}
-      0 & 0\\
-      1 & 1\\
-      2 & 0
-    \end{bmatrix}.
-  \end{align*}
+\begin{example}
+  Let $\constants{} = \emptyset$, $\variables{} = \{ X, Y, Z \}$, $\maxArity{} =
+  2$, $\maxNumNodes{} = 3$, and consider the clause
+  \[
+    \variable{sibling}(X, Y) \gets \variable{parent}(X, Z) \land
+    \variable{parent}(Y, Z).
+  \]
+  Then $\variable{terms} = [X, Y, \Box, \Box, X, Z, Y, Z]$ (the boxes represent
+  the conjunction node), $\variable{occurrences} = [\{ 0, 4 \}, \{ 1, 6 \},
+  \{ 5, 7 \}, \{ 2, 3 \}]$, and $\variable{introductions} = [0, 1, 5]$.
 \end{example}
@@
 \section{Counting Programs}
-% TODO: define combined arity.
-% TODO: define 'gap', 'argument', 'position' or something like that.
 
@@
 It was experimentally confirmed that the model agrees with the combinatorial
-formula from this section in 985 different scenarios.
+formula from this section in 985 different scenarios. The \emph{total arity} of
+a body of a clause is the sum total of arities of all predicates in the body.
 
-We will first consider clauses with `gaps', i.e., without taking variables and
+We will first consider clauses with gaps, i.e., without taking variables and
 constants into account. Let $T(n, a)$ denote the number of possible clause
-bodies with $n$ nodes and combined arity $a$. Then $T(1, a)$ is the number of
+bodies with $n$ nodes and total arity $a$. Then $T(1, a)$ is the number of
 predicates in $\predicates{}$ with arity $a$, and the following recursive
@@
 
-The number of ways to fill $n$ positions with terms can be expressed as
+The number of ways to fill $n$ gaps with terms can be expressed as
 \[
@@
 \]
-The first term is simply the number of ways to fill all $n$ positions with
+The first term is simply the number of ways to fill all $n$ gaps with
 constants. The parameter $k$ is the number of variables used in the clause, and

### 2020-01-10 paper/paper.tex
An example for predicate independence

@@
 \usepackage{mathrsfs}
+
+\usetikzlibrary{arrows.meta}
 
@@
 
-% TODO: define 'gap'
+TODO: define all the relevant terminology from logic. If a predicate has arity
+$n$ and it is as of yet undecided what $n$ terms will fill those spots, we will
+say that the predicate has $n$ \emph{gaps}.
 
@@
 Tested with SWI-Prolog \cite{DBLP:journals/tplp/WielemakerSTL12}.
-
-\subsection{TODO}
-
-\begin{itemize}
-\item A constraint for logical equivalence. An algorithm to reduce each tree to
-  some kind of normal form. Not doing this on purpose. Leaving for further work.
-\item Perhaps negative cycle detection could use the same graph as the
-  independence propagator? If we extend each domain to {-1, 0, 1}, but that
-  might make propagation weaker or slower.
-\item Could investigate how uniform the generated distribution of programs is.
-  Distributions of individual parameters will often favour larger values
-  because, e.g., there are more 5-tuples than 4-tuples.
-\item Inference options to explore. Logspace vs normal space. Symbolic vs
-  non-symbolic. Propagate evidence (might be irrelevant)? Propagate weights?
-  Supported knowledge compilation techniques: sdd, sddx, bdd, nnf, ddnnf, kbest,
-  fsdd, fbdd.
-\item Mention the random heuristic. Mention that restarting gives better
-  randomness, but duplicates become possible. Restarting after each run is
-  expensive. Periodic restarts could be an option.
-\end{itemize}
 
@@
 
-\section{Considering Each Clause Separately}
-
-\subsection{Heads of Clauses}
+\section{Heads of Clauses}
 
@@
 
-\subsection{Bodies of Clauses}
+\section{Bodies of Clauses}
 
@@
 \end{definition}
-
-Auxiliary variables: $\variable{numNodes}, \variable{numTrees} \in \{ 1, \dots,
-\maxNumNodes{} \}$. The former counts the number of nodes in the main tree. The
-latter counts the number of trees in total.
 
@@
 
-\subsubsection{Nodes}
+\subsection{Nodes}
 
@@
 
-\subsubsection{Constraints}
+\subsection{Constraints}
 
-\begin{constraint}
-  \variable{treeStructure} represents \variable{numTrees} trees, i.e.,
+\begin{definition}
+  We define $\variable{numTrees} \in \{ 1, \dots, \maxNumNodes{} \}$ to count
+  the number of trees in our representation of a clause using the
+  $\variable{tree}(\variable{treeStructure}, \variable{numTrees})$\footnote{This
+    constraint uses dominator-based filtering by Fages and Lorca
+    \cite{DBLP:conf/cp/FagesL11}.} constraint.
+\end{definition}
+
+\begin{definition}
+  For convenience, we also define $\variable{numNodes} \in \{ 1, \dots,
+  \maxNumNodes{} \}$ to count the number of nodes in the main tree. We define it
+  as
   \[
-    \variable{tree}(\variable{treeStructure}, \variable{numTrees})\footnote{This
-      constraint uses dominator-based filtering by Fages and Lorca
-      \cite{DBLP:conf/cp/FagesL11}.}.
+    \variable{numNodes} = \maxNumNodes{} - \variable{numTrees} + 1.
   \]
-\end{constraint}
+\end{definition}
 
@@
   $\variable{treeStructure}[0] = 0$.
-\end{constraint}
-
-\begin{constraint}
-  $\variable{numTrees} + \variable{numNodes} = \maxNumNodes{} + 1$.
 \end{constraint}
@@
 
-\subsection{Eliminating Variable Symmetries} \label{sec:variable_symmetry}
+\section{Eliminating Variable Symmetries} \label{sec:variable_symmetry}
 
@@
   \[
-    \variable{sibling}(X, Y) \gets \variable{parent}(X, Z) \land
-    \variable{parent}(Y, Z).
+    \mathsf{sibling}(X, Y) \gets \mathsf{parent}(X, Z) \land
+    \mathsf{parent}(Y, Z).
   \]
@@
 
+In this section, we define a notion of predicate independence as a way to
+constrain the probability distributions defined by the generated programs. We
+also describe efficient algorithms for propagation and entailment checking.
+
 \begin{definition}
@@
 
+\begin{figure}[t]
+  \centering
+  \begin{tikzpicture}
+    \node[draw] (father) at (0, 0.5) {$\mathsf{father}$};
+    \node[draw] (mother) at (0, -0.5) {$\mathsf{mother}$};
+    \node[draw] (parent) at (2, 0) {$\mathsf{parent}$};
+    \node[draw] (sibling) at (4, 0) {$\mathsf{sibling}$};
+    \draw[-{Stealth[scale=1.5]}] (father) -- (parent);
+    \draw[-{Stealth[scale=1.5]}] (mother) -- (parent);
+    \draw[-{Stealth[scale=1.5]}] (parent) -- (sibling);
+  \end{tikzpicture}
+  \caption{The predicate dependency graph of the program in \cref{ex:program}}
+  \label{fig:predicate_dependencies}
+\end{figure}
+
+\begin{example} \label{ex:program}
+  Consider the following program:
+  \begin{align*}
+    \mathsf{sibling}(X, Y) &\gets \mathsf{parent}(X, Z) \land \mathsf{parent}(Y, Z),\\
+    \mathsf{parent}(X, Y) &\gets \mathsf{father}(X, Y) \lor \mathsf{mother}(X, Y).
+  \end{align*}
+  Its predicate dependency graph is in \cref{fig:predicate_dependencies}. We can
+  then list the dependencies of each predicate:
+  \begin{alignat*}{3}
+    D_{\mathsf{father}} &= \{ \mathsf{father} \}, \quad && D_{\mathsf{parent}} &&= \{ \mathsf{father}, \mathsf{mother}, \mathsf{parent} \}, \\
+    D_{\mathsf{mother}} &= \{ \mathsf{mother} \}, \quad && D_{\mathsf{sibling}} &&= \{ \mathsf{father}, \mathsf{mother}, \mathsf{parent}, \mathsf{sibling} \}.
+  \end{alignat*}
+  Hence, the only pair of independent predicates in this program is
+  $\mathsf{father}$ and $\mathsf{mother}$.
+\end{example}
+
+% TODO: continue writing from here
 \begin{definition}[Adjacency matrix representation]
@@
 
-\begin{algorithm}
+\begin{algorithm}[p]
   \SetKwFunction{getDependencies}{getDependencies}
@@
 
-\begin{algorithm}
+\begin{algorithm}[p]
   \SetKwData{edgeExists}{edgeExists}
@@
 
+\section{Conclusion \& Future Work}
+
+\begin{itemize}
+\item A constraint for logical equivalence. An algorithm to reduce each tree to
+  some kind of normal form. Not doing this on purpose. Leaving for further work.
+\item Perhaps negative cycle detection could use the same graph as the
+  independence propagator? If we extend each domain to {-1, 0, 1}, but that
+  might make propagation weaker or slower.
+\item Could investigate how uniform the generated distribution of programs is.
+  Distributions of individual parameters will often favour larger values
+  because, e.g., there are more 5-tuples than 4-tuples.
+\item Inference options to explore. Logspace vs normal space. Symbolic vs
+  non-symbolic. Propagate evidence (might be irrelevant)? Propagate weights?
+  Supported knowledge compilation techniques: sdd, sddx, bdd, nnf, ddnnf, kbest,
+  fsdd, fbdd.
+\item Mention the random heuristic. Mention that restarting gives better
+  randomness, but duplicates become possible. Restarting after each run is
+  expensive. Periodic restarts could be an option.
+\end{itemize}
+
 \section*{Acknowledgments}
 
-The author would like to thank Vaishak Belle for his comments. This work was
-supported by the EPSRC Centre for Doctoral Training in Robotics and Autonomous
-Systems, funded by the UK Engineering and Physical Sciences Research Council
-(grant EP/S023208/1).
+% The author would like to thank Vaishak Belle for his comments.
+This work was supported by the EPSRC Centre for Doctoral Training in Robotics
+and Autonomous Systems, funded by the UK Engineering and Physical Sciences
+Research Council (grant EP/S023208/1).
 

### 2020-01-12 paper/paper.tex
Some writing

@@
 
-TODO: define all the relevant terminology from logic. If a predicate has arity
-$n$ and it is as of yet undecided what $n$ terms will fill those spots, we will
-say that the predicate has $n$ \emph{gaps}.
+TODO: define all the relevant terminology from logic and constraint programming.
+
+If a predicate has arity $n$ and it is as of yet undecided what $n$ terms will
+fill those spots, we will say that the predicate has $n$ \emph{gaps}. We say
+that a constraint variable is \emph{(fully) determined} if its domain (at the
+given moment in the execution) has exactly one value.
+
+A \emph{(logic) program} is a multiset of clauses. Given a program
+$\mathscr{P}$, a \emph{subprogram} $\mathscr{R}$ of $\mathscr{P}$ is a subset of
+the clauses of $\mathscr{P}$ and is denoted by $\mathscr{R} \subseteq
+\mathscr{P}$.
 
@@
   \begin{tikzpicture}
-    \node[draw,circle,gray,text=black] (or) at (0, 0) {$\lor$};
-    \node[draw,circle,gray,text=black] (not) at (-1, -1) {$\neg$};
-    \node (P) at (-1, -2) {$\mathsf{P}(X)$};
-    \node[draw,circle,gray,text=black] (and) at (1, -1) {$\land$};
-    \node (Q) at (0, -2) {$\mathsf{Q}(X)$};
-    \node (R) at (2, -2) {$\mathsf{P}(X)$};
+    \node[draw,circle,gray,text=black] (or) at (-0.375, 0) {$\lor$};
+    \node[draw,circle,gray,text=black] (not) at (-1.5, -1) {$\neg$};
+    \node[draw,circle,gray,text=black] (and) at (0.75, -1) {$\land$};
+    \node[draw,gray,text=black] (P) at (-1.5, -2) {$\mathsf{P}(X)$};
+    \node[draw,gray,text=black] (Q) at (0, -2) {$\mathsf{Q}(X)$};
+    \node[draw,gray,text=black] (R) at (1.5, -2) {$\mathsf{P}(X)$};
     \draw[gray] (or) -- (not);
@@
     dependency graph} is a directed graph $G_{\mathscr{P}} = (V, E)$ with the
-  set of nodes $V$ consisting of all predicates in $\mathscr{P}$. We add an edge
-  from predicate $\mathsf{P}$ to predicate $\mathsf{Q}$ if there is a clause in
-  $\mathscr{P}$ with $\mathsf{Q}$ as the head and $\mathsf{P}$ mentioned in the
-  body.
+  set of nodes $V$ consisting of all predicates in $\mathscr{P}$. For any two
+  different predicates $\mathsf{P}$ and $\mathsf{Q}$, we add an edge from
+  $\mathsf{P}$ to $\mathsf{Q}$ if there is a clause in $\mathscr{P}$ with
+  $\mathsf{Q}$ as the head and $\mathsf{P}$ mentioned in the body. We say that
+  the edge is \emph{negative} if there exists a clause with $\mathsf{Q}$ as the
+  head and at least one instance of $\mathsf{P}$ at the body such that the path
+  from the root to the $\mathsf{P}$ node in the tree representation of the
+  clause passes through at least one negation node. Otherwise it is
+  \emph{positive}. We say that $\mathscr{P}$ (or $G_{\mathscr{P}}$) has a
+  \emph{negative cycle} if $G_{\mathscr{P}}$ has a cycle with at least one
+  negative edge.
 \end{definition}
@@
   \centering
+  \begin{minipage}{.5\textwidth}
+    \centering
     \begin{tikzpicture}
-    \node[draw] (father) at (0, 0.5) {$\mathsf{father}$};
+      \node[draw,circle,gray,text=black] (and) at (0, 0) {$\land$};
+      \node[draw,circle,gray,text=black] (not) at (1.5, -1) {$\neg$};
+      \node[draw,gray,text=black] (parent) at (-1.5, -1) {$\mathsf{parent}(X, Y)$};
+      \node[draw,gray,text=black] (mother) at (1.5, -2) {$\mathsf{mother}(X, Y)$};
+      \draw[gray] (and) -- (parent);
+      \draw[gray] (and) -- (not);
+      \draw[gray] (not) -- (mother);
+    \end{tikzpicture}
+    \caption{The tree representation of the body of Clause~\eqref{eq:example_clause}.}
+    \label{fig:example_tree2}
+  \end{minipage}
+  \begin{minipage}{.49\textwidth}
+    \centering
+    \begin{tikzpicture}
+      \node[draw] (parent) at (0, 0.5) {$\mathsf{parent}$};
       \node[draw] (mother) at (0, -0.5) {$\mathsf{mother}$};
-    \node[draw] (parent) at (2, 0) {$\mathsf{parent}$};
-    \node[draw] (sibling) at (4, 0) {$\mathsf{sibling}$};
-    \draw[-{Stealth[scale=1.5]}] (father) -- (parent);
-    \draw[-{Stealth[scale=1.5]}] (mother) -- (parent);
-    \draw[-{Stealth[scale=1.5]}] (parent) -- (sibling);
+      \node[draw] (sibling) at (2, 0.5) {$\mathsf{sibling}$};
+      \node[draw] (father) at (2, -0.5) {$\mathsf{father}$};
+      \draw[-{Stealth[scale=1.5]}] (parent) edge node[above] {$+$} (sibling);
+      \draw[-{Stealth[scale=1.5]}] (parent) edge node[above] {$+$} (father);
+      \draw[-{Stealth[scale=1.5]}] (mother) edge node[below] {$-$} (father);
     \end{tikzpicture}
-  \caption{The predicate dependency graph of the program in \cref{ex:program}}
+    \caption{The predicate dependency graph of the program in \cref{ex:program}.
+      Positive edges are labeled with `$+$', and negative edges with `$-$'.}
     \label{fig:predicate_dependencies}
+  \end{minipage}
 \end{figure}
 
+% TODO: example of edge positivity/negativity
 \begin{example} \label{ex:program}
   Consider the following program:
-  \begin{align*}
-    \mathsf{sibling}(X, Y) &\gets \mathsf{parent}(X, Z) \land \mathsf{parent}(Y, Z),\\
-    \mathsf{parent}(X, Y) &\gets \mathsf{father}(X, Y) \lor \mathsf{mother}(X, Y).
-  \end{align*}
-  Its predicate dependency graph is in \cref{fig:predicate_dependencies}. We can
-  then list the dependencies of each predicate:
+  \begin{align}
+    \mathsf{sibling}(X, Y) &\gets \mathsf{parent}(X, Z) \land \mathsf{parent}(Y, Z), \nonumber \\
+    \mathsf{father}(X, Y) &\gets \mathsf{parent}(X, Y) \land \neg\mathsf{mother}(X, Y). \label{eq:example_clause}
+  \end{align}
+  Its predicate dependency graph is in \cref{fig:predicate_dependencies}.
+  Because of the negation in \cref{eq:example_clause} (as seen in
+  \cref{fig:example_tree2}), the edge from $\mathsf{mother}$ to
+  $\mathsf{father}$ is negative, while the other two edges are positive.
+
+  We can now list the dependencies of each predicate:
   \begin{alignat*}{3}
-    D_{\mathsf{father}} &= \{ \mathsf{father} \}, \quad && D_{\mathsf{parent}} &&= \{ \mathsf{father}, \mathsf{mother}, \mathsf{parent} \}, \\
-    D_{\mathsf{mother}} &= \{ \mathsf{mother} \}, \quad && D_{\mathsf{sibling}} &&= \{ \mathsf{father}, \mathsf{mother}, \mathsf{parent}, \mathsf{sibling} \}.
+    D_{\mathsf{parent}} &= \{ \mathsf{parent} \}, \quad && D_{\mathsf{sibling}}
+    &&= \{\mathsf{sibling}, \mathsf{parent} \},\\
+    D_{\mathsf{mother}} &= \{ \mathsf{mother} \}, \quad && D_{\mathsf{father}}
+    &&= \{ \mathsf{father}, \mathsf{mother}, \mathsf{parent} \}.
   \end{alignat*}
-  Hence, the only pair of independent predicates in this program is
-  $\mathsf{father}$ and $\mathsf{mother}$.
+  Hence, we have two pairs of independent predicates, i.e., $\mathsf{mother}$ is
+  independent from $\mathsf{parent}$ and $\mathsf{sibling}$.
 \end{example}
 
-% TODO: continue writing from here
 \begin{definition}[Adjacency matrix representation]
-  An $|\predicates{}| \times |\predicates{}|$ adjacency matrix $\mathbf{A}$
-  defined by
+  An $|\predicates{}| \times |\predicates{}|$ adjacency matrix $\mathbf{A}$ with
+  $\{ 0, 1 \}$ as its domain is defined by
   \begin{align*}
-    A_{i,j} = 0 \iff &\nexists k: \variable{headsOfClauses}[k].\variable{predicate} = j \text{ and } \\
+    \mathbf{A}[i][j] = 0 \iff &\nexists k \in \{ 0, \dots, \maxNumClauses{} \}: \variable{headsOfClauses}[k].\variable{predicate} = j \text{ and } \\
     &i \in \{ a.\variable{name} \mid a \in \variable{bodiesOfClauses}[k].\variable{treeValues} \}.
@@
 
-A dependency is an algebraic data type that is either determined (in which case
-it holds only the index of the predicate) or undetermined (in which case it also
-holds the indices of the source and target vertices, corresponding to the edge
-responsible for making the dependency undetermined).
+% TODO: continue writing from here
+We define a \emph{dependency} as an algebraic data type that is either
+determined (in which case it holds only the index of the \texttt{predicate}) or
+undetermined (in which case it also holds the indices of the \texttt{source} and
+\texttt{target} vertices, corresponding to the edge responsible for making the
+dependency undetermined (exactly one, otherwise we don't consider the edge)).
 
@@
 \begin{itemize}
-\item Two types of dependencies: determined and
-  one-undetermined-edge-away-from-being-determined.
 \item Look up the dependencies of both predicates. For each pair of
@@
   \For{$(d_1, d_2) \in \getDependencies{$p_1$} \times
-    \getDependencies{$p_2$}$ s.t. $d_1.\predicate = d_2.\predicate$}{
-    \If{$d_1$.\isDetermined{} {\bf and} $d_2$.\isDetermined{}}{
-      \fail{}\;
-    }
+    \getDependencies{$p_2$}$ such that $d_1.\predicate = d_2.\predicate$}{
+    \lIf{$d_1$.\isDetermined{} {\bf and} $d_2$.\isDetermined{}}{\fail{}}
     \uIf{$d_1$.\isDetermined{}}{
@@
   \getDependencies{$p_2$} \mid d_1.\predicate = d_2.\predicate \}$\;
-  \If{$\{ (d_1, d_2) \in D \mid d_1.\isDetermined{}, d_2.\isDetermined{} \} \ne
-    \emptyset$}{
-    \Return{FALSE}\;
+  \If{$\exists (d_1, d_2) \in D$ such that $d_1.\isDetermined{}$ {\bf and}
+    $d_2.\isDetermined{}$}{
+    \Return{\textsc{false}}\;
   }
-  \If{$D = \emptyset$}{
-    \Return{TRUE}\;
-  }
-  \Return{UNDEFINED}\;
+  \lIf{$D = \emptyset$}{\Return{\textsc{true}}}
+  \Return{\textsc{undefined}}\;
   \caption{Entailment}
@@
     $D \gets \{ p \}$\;
-    \Repeat{$D' = D$}{
-      $D' \gets D$\;
+    \While{{\normalfont \texttt{true}}}{
+      $D' \gets \emptyset$\;
       \For{$d \in D$}{
@@
       }
+      \lIf{$D' = D$}{\Return{$D$}}
+      $D \gets D'$\;
     }
-    \Return{$D$}\;
   }
@@
 \section{Entailment Checking for Negative/All Cycles}
+% TODO: explain that the hasNegativeCycles algorithm is an extension of a simple
+% cycle detection algorithm.
 
-\begin{enumerate}
-\item Let $C$ be a set of clauses such that their bodies and predicates in their
-  heads are fully determined.
-\item If $C = \emptyset$, return UNDEFINED.
-\item Construct an adjacency list representation of a graph where vertices
-  represent predicates. Each edge is either \emph{positive} or \emph{negative}.
-  There is an edge from $p$ to $q$ if $q$ appears in the body of a predicate
-  with $p$ as its head. The edge is negative if, when traversing the tree to
-  reach some instance of $q$, we pass through a $\neg$ node. Otherwise, it's
-  positive.
-\item Run a modified cycle detection algorithm that detects all cycles that have
-  at least one negative edge.
-\item If we found a cycle, return FALSE.
-\item If $C$ encompasses all clauses, return TRUE.
-\item Return UNDEFINED.
-\end{enumerate}
+\begin{algorithm}[t]
+  \KwData{a constraint model for a logic program $\mathscr{P}$ amid execution}
+  \SetKwFunction{hasNegativeCycles}{hasNegativeCycles}
+  Let $\mathscr{R} \subseteq \mathscr{P}$ be the largest subprogram of
+  $\mathscr{P}$ with all bodies and all predicates in heads fully
+  determined\footnotemark\;
+  \lIf{$\mathscr{R} = \emptyset$}{\Return{\textsc{undefined}}}
+  \lIf{\hasNegativeCycles($G_{\mathscr{R}}$)}{\Return{\textsc{false}}}
+  \lIf{$\mathscr{R} = \mathscr{P}$}{\Return{\textsc{true}}}
+  \Return{\textsc{undefined}}\;
+  \caption{Entailment checking for negative cycles}
+\end{algorithm}
+\footnotetext{Due to the definition of independence, the arguments of the head
+  atom need not be determined.}
 

### 2020-01-15 src/main/ForbidCycles.java
Separate the model from other functionality

@@ -1,0 +1,5 @@
+package main;
+
+public enum ForbidCycles {
+    ALL, NEGATIVE, NONE;
+}

### 2020-01-15 src/main/GeneratePrograms.java

@@ -1,229 +1,17 @@
 package main;
 
 import java.io.*;
+import java.util.ArrayList;
 import java.util.Arrays;
 import java.util.List;
 
-import org.chocosolver.solver.Model;
-import org.chocosolver.solver.constraints.Constraint;
-import org.chocosolver.solver.constraints.extension.Tuples;
-import org.chocosolver.solver.search.strategy.Search;
-import org.chocosolver.solver.search.strategy.selectors.values.IntDomainRandom;
-import org.chocosolver.solver.search.strategy.selectors.variables.Random;
-import org.chocosolver.solver.variables.IntVar;
-import org.chocosolver.solver.variables.SetVar;
 import org.chocosolver.util.tools.ArrayUtils;
-import propagators.NegativeCyclePropagator;
 
 import static java.util.stream.Collectors.toList;
 
 class GeneratePrograms {
 
-    private static final String DIRECTORY = "../programs/";
-    private static final int NUM_SOLUTIONS = 10000;
-    private static int MAX_NUM_NODES = 1;
-    private static int MAX_NUM_CLAUSES = 2;
-    private static final boolean FORBID_ALL_CYCLES = false;
-    //private static final double[] PROBABILITIES = {0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9,
-    //        1, 1, 1, 1, 1, 1}; // let's make probability 1 a bit more likely
-    private static final double[] PROBABILITIES = {1};
-
-    static String[] PREDICATES = {"p", "q"};
-    static int[] ARITIES = {1, 1};
-    static String[] VARIABLES = {"X"};
-    static String[] CONSTANTS = {};
-    static int MAX_ARITY = Arrays.stream(ARITIES).max().getAsInt();
-
-    static Tuples arities;
-
-    private static Model model;
-    private static IntVar[] clauseAssignments; // an array of predicates occurring at the heads of clauses
-    private static Head[] clauseHeads; // full heads (predicates, variables, constants)
-    private static Body[] bodies; // the body of each clause
-    private static IntVar[] decisionVariables; // all decision variables relevant to the problem
-    private static IntVar[][] termsPerClause; // a flattened-out view of the term positions in each clause
-    private static SetVar[][] occurrences; // for each clause and variable, a set of positions with that variable
-    private static IntVar[][] M; // for eliminating variable symmetries
-    private static java.util.Random rng;
-
[…]

### 2020-01-15 src/main/Head.java

@@ -11,18 +11,20 @@ class Head {
     private IntVar predicate; // PREDICATES.length means that the clause is disabled
     private IntVar[] arguments;
     private IntVar arity;
+    private Program program;
 
-    Head(Model model, IntVar predicate) {
+    Head(Program program, Model model, IntVar predicate) {
+        this.program = program;
         this.predicate = predicate;
 
         // Define arity
         IntVar indexToTable = model.intOffsetView(predicate, Token.values().length);
-        arity = model.intVar(0, GeneratePrograms.MAX_ARITY);
-        model.table(indexToTable, arity, GeneratePrograms.arities).post();
+        arity = model.intVar(0, program.maxArity);
+        model.table(indexToTable, arity, program.arities).post();
 
         // Arity regulates how many arguments the predicate has
-        int numValues = GeneratePrograms.CONSTANTS.length + GeneratePrograms.VARIABLES.length;
-        arguments = model.intVarArray(GeneratePrograms.MAX_ARITY, 0, numValues);
+        int numValues = program.constants.length + program.variables.length;
+        arguments = model.intVarArray(program.maxArity, 0, numValues);
         for (int i = 0; i < arguments.length; i++) {
             Constraint iGeArity = model.arithm(arity, "<=", i);
             Constraint isDisabled = model.arithm(arguments[i], "=", numValues);
@@ -42,15 +44,19 @@ class Head {
     @Override
     public String toString() {
         StringBuilder s = new StringBuilder();
-        s.append(GeneratePrograms.PREDICATES[predicate.getValue()]).append("(");
+        s.append(program.predicates[predicate.getValue()]);
+        if (arity.getValue() == 0)
+            return s.toString();
+
+        s.append("(");
         for (int i = 0; i < arity.getValue(); i++) {
             if (i > 0)
                 s.append(", ");
             int argument = arguments[i].getValue();
-            if (argument < GeneratePrograms.VARIABLES.length) {
-                s.append(GeneratePrograms.VARIABLES[argument]);
+            if (argument < program.variables.length) {
+                s.append(program.variables[argument]);
             } else {
-                s.append(GeneratePrograms.CONSTANTS[argument - GeneratePrograms.VARIABLES.length]);
+                s.append(program.constants[argument - program.variables.length]);
             }
         }
         s.append(")");

### 2020-01-15 src/main/Node.java

@@ -10,16 +10,18 @@ class Node {
     private IntVar predicate; // tokens first, then predicates
     private IntVar[] arguments; // variables first, then constants
     private IntVar arity;
+    private Program program;
 
-    Node(Model model) {
-        int numPossibleArguments = GeneratePrograms.VARIABLES.length + GeneratePrograms.CONSTANTS.length + 1;
-        predicate = model.intVar(0, GeneratePrograms.PREDICATES.length + Token.values().length - 1);
-        arguments = model.intVarArray(GeneratePrograms.MAX_ARITY, 0, numPossibleArguments - 1);
+    Node(Program program, Model model) {
+        this.program = program;
+        int numPossibleArguments = program.variables.length + program.constants.length + 1;
+        predicate = model.intVar(0, program.predicates.length + Token.values().length - 1);
+        arguments = model.intVarArray(program.maxArity, 0, numPossibleArguments - 1);
 
         // Restrict the number of arguments to the right arity.
         // This also takes care of nullifying the arguments of tokens
-        arity = model.intVar(0, GeneratePrograms.MAX_ARITY);
-        model.table(predicate, arity, GeneratePrograms.arities).post();
+        arity = model.intVar(0, program.maxArity);
+        model.table(predicate, arity, program.arities).post();
         for (int i = 0; i < arguments.length; i++) {
             // If i >= arity, then arguments[i] must be undefined
             Constraint iGTEQArity = model.arithm(arity, "<=", i);
@@ -45,16 +47,19 @@ class Node {
         int value = predicate.getValue();
         if (value < Token.values().length)
             return Token.values()[value].toString();
-        StringBuilder atom = new StringBuilder(GeneratePrograms.PREDICATES[value - Token.values().length]);
+        StringBuilder atom = new StringBuilder(program.predicates[value - Token.values().length]);
+        if (arity.getValue() == 0)
+            return atom.toString();
+
         atom.append("(");
         for (int i = 0; i < arity.getValue(); i++) {
             if (i > 0)
                 atom.append(", ");
             int index = arguments[i].getValue();
-            if (index < GeneratePrograms.VARIABLES.length) {
-                atom.append(GeneratePrograms.VARIABLES[index]);
+            if (index < program.variables.length) {
+                atom.append(program.variables[index]);
             } else {
-                atom.append(GeneratePrograms.CONSTANTS[index - GeneratePrograms.VARIABLES.length]);
+                atom.append(program.constants[index - program.variables.length]);
             }
         }
         atom.append(")");

### 2020-01-15 src/main/Program.java

@@ -1,0 +1,235 @@
+package main;
+
+import org.chocosolver.solver.Model;
+import org.chocosolver.solver.constraints.Constraint;
+import org.chocosolver.solver.constraints.extension.Tuples;
+import org.chocosolver.solver.search.strategy.Search;
+import org.chocosolver.solver.search.strategy.selectors.values.IntDomainRandom;
+import org.chocosolver.solver.search.strategy.selectors.variables.Random;
+import org.chocosolver.solver.variables.IntVar;
+import org.chocosolver.solver.variables.SetVar;
+import org.chocosolver.util.tools.ArrayUtils;
+import propagators.NegativeCyclePropagator;
+
+import java.io.BufferedWriter;
+import java.io.FileWriter;
+import java.io.IOException;
+import java.util.Arrays;
+
+public class Program {
+    private String directory;
+    private int numSolutions;
+    private int maxNumNodes;
+    private int maxNumClauses;
+    private double[] probabilities;
+
+    String[] predicates;
+    private int[] ARITIES;
+    String[] variables;
+    String[] constants;
+    int maxArity;
+
+    Tuples arities; // used in defining constraints
+
+    private Model model;
+    private IntVar[] clauseAssignments; // an array of predicates occurring at the heads of clauses
+    private Head[] clauseHeads; // full heads (predicates, variables, constants)
+    private Body[] bodies; // the body of each clause
+    private IntVar[] decisionVariables; // all decision variables relevant to the problem
+    private IntVar[][] termsPerClause; // a flattened-out view of the term positions in each clause
+    private SetVar[][] occurrences; // for each clause and variable, a set of positions with that variable
+    private IntVar[][] M; // for eliminating variable symmetries
+    private java.util.Random rng;
+
+    Program(String directory, int numSolutions, int maxNumNodes, int maxNumClauses, ForbidCycles forbidCycles,
+            double[] probabilities, String[] predicates, int[] arities, String[] variables, String[] constants) {
+        this.directory = directory;
+        this.numSolutions = numSolutions;
+        this.maxNumNodes = maxNumNodes;
+        this.maxNumClauses = maxNumClauses;
+        this.probabilities = probabilities;
+        this.predicates = predicates;
+        ARITIES = arities;
+        this.variables = variables;
+        this.constants = constants;
+        maxArity = Arrays.stream(ARITIES).max().getAsInt();
+
+        setUpConstraints();
[…]

### 2020-01-15 src/propagators/NegativeCyclePropagator.java

@@ -1,6 +1,7 @@
 package propagators;
 
 import main.Body;
+import main.ForbidCycles;
 import org.chocosolver.solver.constraints.Propagator;
 import org.chocosolver.solver.exception.ContradictionException;
 import org.chocosolver.solver.variables.IntVar;
@@ -16,7 +17,7 @@ public class NegativeCyclePropagator extends Propagator<IntVar> {
 
     private IntVar[] clauseAssignments;
     private Body[] bodies;
-    private boolean forbidAllCycles;
+    private ForbidCycles forbidAllCycles;
     private List<List<SignedPredicate>> adjacencyList;
 
     static IntVar[] constructDecisionVariables(IntVar[] clauseAssignments, Body[] bodies) {
@@ -26,7 +27,7 @@ public class NegativeCyclePropagator extends Propagator<IntVar> {
         return decisionVariables;
     }
 
-    public NegativeCyclePropagator(IntVar[] clauseAssignments, Body[] bodies, boolean forbidAllCycles) {
+    public NegativeCyclePropagator(IntVar[] clauseAssignments, Body[] bodies, ForbidCycles forbidAllCycles) {
         super(constructDecisionVariables(clauseAssignments, bodies));
         this.clauseAssignments = clauseAssignments;
         this.bodies = bodies;
@@ -112,6 +113,9 @@ public class NegativeCyclePropagator extends Propagator<IntVar> {
         int numNodes = adjacencyList.size();
         boolean[] visited = new boolean[numNodes];
         boolean[] recursionStack = new boolean[numNodes];
+        boolean forbidAllCycles = false;
+        if (this.forbidAllCycles == ForbidCycles.ALL)
+            forbidAllCycles = true;
         for (int i = 0; i < numNodes; i++)
             if (isCyclic(i, forbidAllCycles, visited, recursionStack))
                 return ESat.FALSE;

### 2020-01-15 src/main/Body.java
Make constraint variables more readable

@@ -18,17 +18,19 @@ public class Body {
     private Node[] treeValues;
     private IntVar[] arguments; // concatenated arguments of all nodes in treeValues
 
-    public Body(Program program, Model model, IntVar assignment, int maxNumNodes) {
+    public Body(Program program, Model model, IntVar assignment, int maxNumNodes, int clauseIndex) {
         this.maxNumNodes = maxNumNodes;
 
-        IntVar numNodes = model.intVar(1, maxNumNodes); // number of nodes in the main tree
-        treeStructure = model.intVarArray(maxNumNodes, 0, maxNumNodes - 1);
+        // number of nodes in the main tree
+        IntVar numNodes = model.intVar("numNodes[" + clauseIndex + "]", 1, maxNumNodes);
+        treeStructure = model.intVarArray("treeStructure[" + clauseIndex + "]", maxNumNodes, 0,
+                maxNumNodes - 1);
         treeValues = new Node[maxNumNodes];
         for (int i = 0; i < maxNumNodes; i++)
-            treeValues[i] = new Node(program, model);
+            treeValues[i] = new Node(program, model, clauseIndex, i);
 
         // Tree structure
-        IntVar numTrees = model.intVar(1, maxNumNodes);
+        IntVar numTrees = model.intVar("numTrees[" + clauseIndex + "]", 1, maxNumNodes);
         model.tree(treeStructure, numTrees).post();
         model.arithm(treeStructure[0], "=", 0).post(); // the 0th element is always a root
 
@@ -139,6 +141,14 @@ public class Body {
             if (i != parent && treeStructure[i].getValue() == parent)
                 break;
         return i;
+    }
+
+    /** The decision variables relevant to negative cycle detection (i.e., everything except arguments) */
+    public IntVar[] getStructuralDecisionVariables() {
+        IntVar[] variables = treeStructure;
+        for (Node treeValue : treeValues)
+            variables = ArrayUtils.concat(variables, treeValue.getPredicate());
+        return variables;
     }
 
     public IntVar[] getDecisionVariables() {

### 2020-01-15 src/main/GeneratePrograms.java

@@ -149,11 +149,11 @@ class GeneratePrograms {
     }
 
     public static void main(String[] args) throws IOException {
-        generateAllPrograms();
+        //generateAllPrograms();
 
-        /*Program p = new Program("../programs/", 10000, 1, 1,
-                ForbidCycles.NEGATIVE, DEFAULT_PROBABILITIES, new String[]{"p"}, new int[]{2}, new String[0],
-                new String[]{"c"});
-        p.saveProgramsToFiles();*/
+        Program p = new Program("../programs/", 10000, 4, 1,
+                ForbidCycles.NEGATIVE, DEFAULT_PROBABILITIES, new String[]{"p"}, new int[]{4}, new String[]{"X"},
+                new String[]{"a", "b", "c"});
+        p.saveProgramsToFiles();
     }
 }

### 2020-01-15 src/main/Node.java

@@ -12,15 +12,17 @@ class Node {
     private IntVar arity;
     private Program program;
 
-    Node(Program program, Model model) {
+    Node(Program program, Model model, int clauseIndex, int position) {
         this.program = program;
         int numPossibleArguments = program.variables.length + program.constants.length + 1;
-        predicate = model.intVar(0, program.predicates.length + Token.values().length - 1);
-        arguments = model.intVarArray(program.maxArity, 0, numPossibleArguments - 1);
+        predicate = model.intVar("nodePredicate[" + clauseIndex + "][" + position + "]", 0,
+                program.predicates.length + Token.values().length - 1);
+        arguments = model.intVarArray("nodeArguments[" + clauseIndex + "][" + position + "]", program.maxArity,
+                0, numPossibleArguments - 1);
 
         // Restrict the number of arguments to the right arity.
         // This also takes care of nullifying the arguments of tokens
-        arity = model.intVar(0, program.maxArity);
+        arity = model.intVar("nodeArity[" + clauseIndex + "][" + position + "]", 0, program.maxArity);
         model.table(predicate, arity, program.arities).post();
         for (int i = 0; i < arguments.length; i++) {
             // If i >= arity, then arguments[i] must be undefined

### 2020-01-15 src/main/Program.java

@@ -1,6 +1,7 @@
 package main;
 
 import org.chocosolver.solver.Model;
+import org.chocosolver.solver.Solver;
 import org.chocosolver.solver.constraints.Constraint;
 import org.chocosolver.solver.constraints.extension.Tuples;
 import org.chocosolver.solver.search.strategy.Search;
@@ -69,7 +70,10 @@ public class Program {
     }
 
     void saveProgramsToFiles() throws IOException {
-        for (int i = 0; i < numSolutions && model.getSolver().solve(); i++) {
+        Solver solver = model.getSolver();
+        solver.showDecisions();
+        solver.showContradiction();
+        for (int i = 0; i < numSolutions && solver.solve(); i++) {
             //System.out.println("========== " + i + " ==========");
             StringBuilder program = new StringBuilder();
             for (int j = 0; j < maxNumClauses; j++)
@@ -143,17 +147,19 @@ public class Program {
         rng = new java.util.Random();
 
         // numbers < PREDICATES.length assign a clause to a predicate, PREDICATES.length is used to discard the clause
-        clauseAssignments = model.intVarArray(maxNumClauses, 0, predicates.length);
+        clauseAssignments = model.intVarArray("clauseAssignments", maxNumClauses, 0, predicates.length);
 
         clauseHeads = new Head[clauseAssignments.length];
         for (int i = 0; i < clauseHeads.length; i++)
-            clauseHeads[i] = new Head(this, model, clauseAssignments[i]);
+            clauseHeads[i] = new Head(this, model, clauseAssignments[i], i);
 
-        IntVar numDisabledClauses = model.intVar(0, maxNumClauses - predicates.length);
+        IntVar numDisabledClauses = model.intVar("numDisabledClauses", 0,
+                maxNumClauses - predicates.length);
         model.count(predicates.length, clauseAssignments, numDisabledClauses).post();
 
         // Each possible value (< PREDICATES.length) should be mentioned at least once
-        IntVar numDistinctValues = model.intVar(predicates.length, predicates.length + 1);
+        IntVar numDistinctValues = model.intVar("numDistinctValues", predicates.length,
+                predicates.length + 1);
         model.nValues(clauseAssignments, numDistinctValues).post();
 
         Constraint containsDisabledClause = model.arithm(numDisabledClauses, ">", 0);
@@ -163,7 +169,7 @@ public class Program {
 
         bodies = new Body[maxNumClauses];
[…]

### 2020-01-16 src/main/GeneratePrograms.java
A redundant constraint for occurrences

@@ -113,13 +113,13 @@ class GeneratePrograms {
 
     private static void generateAllPrograms() throws IOException {
         for (int numPredicates = 1; numPredicates < 5; numPredicates++) {
-            System.out.println("\n" + numPredicates);
+            //System.out.println("\n" + numPredicates);
             String[] predicates = new String[numPredicates];
             fillWithNames(predicates, "");
             for (int numAdditionalClauses = 0; numAdditionalClauses < 5; numAdditionalClauses++) {
                 int maxNumClauses = predicates.length + numAdditionalClauses;
                 for (int numVariables = 0; numVariables < 5; numVariables++) {
-                    System.out.print(".");
+                    //System.out.print(".");
                     String[] variables = new String[numVariables];
                     fillWithNames(variables, "v");
                     for (int numConstants = 0; numConstants < 5; numConstants++) {
@@ -135,10 +135,13 @@ class GeneratePrograms {
                                         maxArity + "a/";
                                 new File(directory).mkdir();
                                 for (int[] localArities: arities) {
-                                    Program p = new Program(directory, 100, maxNumNodes, maxNumClauses,
+                                    Program p = new Program(directory, 1, maxNumNodes, maxNumClauses,
                                             ForbidCycles.NEGATIVE, DEFAULT_PROBABILITIES, predicates, localArities,
                                             variables, constants);
+                                    long start = System.nanoTime();
                                     p.saveProgramsToFiles();
+                                    long finish = System.nanoTime();
+                                    System.out.println(directory + ", " + (finish - start));
                                 }
                             }
                         }
@@ -150,10 +153,11 @@ class GeneratePrograms {
 
     public static void main(String[] args) throws IOException {
         //generateAllPrograms();
+        checkNumPrograms();
 
-        Program p = new Program("../programs/", 1000, 4, 1,
-                ForbidCycles.NEGATIVE, DEFAULT_PROBABILITIES, new String[]{"p"}, new int[]{4}, new String[]{"X", "Y", "Z"},
+        /*Program p = new Program("../programs/", 1000, 4, 1,
+                ForbidCycles.NEGATIVE, DEFAULT_PROBABILITIES, new String[]{"p"}, new int[]{4}, new String[]{"W", "X", "Y", "Z"},
                 new String[]{"a"});
-        p.saveProgramsToFiles();
+        p.saveProgramsToFiles();*/
     }
 }

### 2020-01-16 paper/paper.tex
Separate the model from other functionality
Make constraint variables more readable
A redundant constraint for occurrences
Some redundant constraints

@@
 \item a list of predicates $\predicates{}$,
-\item a list of their arities $\arities{}$ (including zero),
+\item a list of their arities $\arities{}$ (including zero, but assuming that at
+  least one predicate has non-zero arity),
   \begin{itemize}
@@
 \section{Eliminating Variable Symmetries} \label{sec:variable_symmetry}
+% TODO: only if we have multiple variables
 
@@
 
+\begin{constraint}[Redundant]
+  For $u \ne v \in \constants{} \cup \variables{} \cup \{ \Box \}$,
+  \[
+    \variable{occurrences}[u] \cap \variable{occurrences}[v] = \emptyset.
+  \]
+\end{constraint}
+
 \begin{definition}
@@
     \variable{introductions}[v] = \begin{cases}
-      \min \variable{occurrences}[v] & \text{if }
+      1 + \min \variable{occurrences}[v] & \text{if }
       \variable{occurrences}[v] \ne \emptyset\\
-      N & \text{otherwise.}
+      0 & \text{otherwise.}
     \end{cases}
@@
 \end{definition}
+
+\begin{constraint}[Redundant]
+  $\variable{allDifferentExcept0}(\variable{introductions})$.
+\end{constraint}
 
@@
 \end{example}
+
+\subsection{A Redundant Constraint}
+
+For each clause...
+
+\begin{definition}
+  We define an auxiliary set variable
+  \[
+    \variable{potentialIntroductions} \subseteq \{ 0, \dots, N \}
+  \]
+  by: for $i = 0, \dots, \maxNumNodes{} - 1$, if
+  $\variable{treeValues}[i].\variable{name} \in \tokens{}$, then
+  \[
+    \variable{potentialIntroductions} \cap \{ \maxArity{} \times (i + 1) + j + 1
+    \mid j = 0, \dots, \maxArity{} - 1 \} = \emptyset.
+  \]
+\end{definition} % TODO: maybe add to the example
+In other words, if the node not a predicate, a variable cannot be introduced as
+one of its `arguments'.
+
+\begin{constraint}
+  For $v \in \variables{}$, $\variable{introductions}[v] \in
+  \variable{potentialIntroductions}$.
+\end{constraint}
 
@@
 % cycle detection algorithm.
+% TODO: the difficulty with propagation is that there is no good way to define
+% the adjacency matrix with 0/-1/+1 values, the negativity condition is too
+% difficult.
+% TODO: NB: the set of decision variables for this constraint must exclude all
+% arguments.
 
@@
   expensive. Periodic restarts could be an option.
+\item Could add statistics about what constraints tend to conflict.
 \end{itemize}

### 2020-01-16 src/main/Program.java

@@ -75,7 +75,7 @@ public class Program {
         if (variables.length > 1) {
             IntStrategy intStrategy15 = Search.intVarSearch(new Random<>(rng.nextLong()), new IntDomainRandom(rng.nextLong()), ArrayUtils.flatten(introductions));
             SetStrategy setStrategy = Search.setVarSearch(new GeneralizedMinDomVarSelector(), new SetDomainMin(), true, ArrayUtils.flatten(occurrences));
-            model.getSolver().setSearch(new StrategiesSequencer(intStrategy1, intStrategy15, setStrategy, intStrategy17, intStrategy2));
+            model.getSolver().setSearch(new StrategiesSequencer(intStrategy1, intStrategy15, intStrategy17, setStrategy, intStrategy2));
         } else {
             model.getSolver().setSearch(new StrategiesSequencer(intStrategy1, intStrategy17, intStrategy2));
         }
@@ -247,9 +247,12 @@ public class Program {
 
         // Set up occurrences
         int maxValue = constants.length + variables.length;
+        int[] weights = new int[numIndices];
         int[] possibleIndices = new int[numIndices];
-        for (int i = 0; i < numIndices; i++)
+        for (int i = 0; i < numIndices; i++) {
             possibleIndices[i] = i;
+            weights[i] = i + 1;
+        }
         occurrences = model.setVarMatrix("occurrences", maxNumClauses, maxValue + 1, new int[0],
                 possibleIndices);
         for (int i = 0; i < maxNumClauses; i++) {
@@ -264,18 +267,19 @@ public class Program {
         for (int i = 0; i < maxNumClauses; i++) {
             introductions[i] = model.intVarArray("introductions[" + i + "]", variables.length, 0, numIndices);
             for (int v = 0; v < variables.length; v++) {
-                model.min(occurrences[i][v], introductions[i][v], false).post();
+                model.min(occurrences[i][v], weights, 0, introductions[i][v], false).post();
                 SetVar[] occurrencesAtI = new SetVar[1];
                 occurrencesAtI[0] = occurrences[i][v];
                 Constraint noOccurrences = model.nbEmpty(occurrencesAtI, 1);
-                Constraint fixMinOccurrence = model.arithm(introductions[i][v], "=", numIndices);
+                Constraint fixMinOccurrence = model.arithm(introductions[i][v], "=", 0);
                 model.ifThen(noOccurrences, fixMinOccurrence);
             }
[…]

### 2020-01-16 src/main/Program.java
Another redundant constraint

@@ -43,7 +43,8 @@ public class Program {
     private Body[] bodies; // the body of each clause
     private IntVar[] structuralDecisionVariables;
     private IntVar[] predicateDecisionVariables;
-    private IntVar[] gapDecisionVariables;
+    private IntVar[] headGapDecisionVariables;
+    private IntVar[] bodyGapDecisionVariables;
     private IntVar[][] termsPerClause; // a flattened-out view of the term positions in each clause
     private SetVar[][] occurrences; // for each clause and variable, a set of positions with that variable
     private IntVar[][] introductions; // for eliminating variable symmetries
@@ -68,16 +69,17 @@ public class Program {
             new Constraint("NoNegativeCycles",
                     new NegativeCyclePropagator(clauseAssignments, bodies, forbidCycles)).post();
 
-        IntStrategy intStrategy1 = Search.intVarSearch(new Random<>(rng.nextLong()), new IntDomainRandom(rng.nextLong()), structuralDecisionVariables);
-        IntStrategy intStrategy2 = Search.intVarSearch(new Random<>(rng.nextLong()), new IntDomainRandom(rng.nextLong()), gapDecisionVariables);
-        IntStrategy intStrategy17 = Search.intVarSearch(new Random<>(rng.nextLong()), new IntDomainRandom(rng.nextLong()), predicateDecisionVariables);
+        IntStrategy structuralStrategy = Search.intVarSearch(new Random<>(rng.nextLong()), new IntDomainRandom(rng.nextLong()), structuralDecisionVariables);
+        IntStrategy bodyGapStrategy = Search.intVarSearch(new Random<>(rng.nextLong()), new IntDomainRandom(rng.nextLong()), bodyGapDecisionVariables);
+        IntStrategy headGapStrategy = Search.intVarSearch(new Random<>(rng.nextLong()), new IntDomainRandom(rng.nextLong()), headGapDecisionVariables);
+        IntStrategy predicateStrategy = Search.intVarSearch(new Random<>(rng.nextLong()), new IntDomainRandom(rng.nextLong()), predicateDecisionVariables);
 
         if (variables.length > 1) {
-            IntStrategy intStrategy15 = Search.intVarSearch(new Random<>(rng.nextLong()), new IntDomainRandom(rng.nextLong()), ArrayUtils.flatten(introductions));
-            SetStrategy setStrategy = Search.setVarSearch(new GeneralizedMinDomVarSelector(), new SetDomainMin(), true, ArrayUtils.flatten(occurrences));
[…]

### 2020-01-17 src/main/GeneratePrograms.java
Cleanup: step 2

@@ -11,7 +11,8 @@ import static java.util.stream.Collectors.toList;
 
 class GeneratePrograms {
 
-    private static final double[] DEFAULT_PROBABILITIES = {0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1, 1, 1, 1, 1, 1};
+    private static final double[] DEFAULT_PROBABILITIES = {0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9,
+            1, 1, 1, 1, 1, 1};
 
     private static void checkNumPrograms() throws IOException {
         BufferedReader reader = new BufferedReader(new FileReader("../program_counts.csv"));

### 2020-01-17 src/main/Head.java

@@ -20,7 +20,7 @@ class Head {
         // Define arity
         IntVar indexToTable = model.intOffsetView(predicate, Token.values().length);
         arity = model.intVar("headArity[" + clauseIndex + "]", 0, program.maxArity);
-        model.table(indexToTable, arity, program.arities).post();
+        model.table(indexToTable, arity, program.aritiesTable).post();
 
         // Arity regulates how many arguments the predicate has
         int numValues = program.constants.length + program.variables.length;

### 2020-01-17 src/main/Node.java

@@ -23,7 +23,7 @@ class Node {
         // Restrict the number of arguments to the right arity.
         // This also takes care of nullifying the arguments of tokens
         arity = model.intVar("nodeArity[" + clauseIndex + "][" + position + "]", 0, program.maxArity);
-        model.table(predicate, arity, program.arities).post();
+        model.table(predicate, arity, program.aritiesTable).post();
         for (int i = 0; i < arguments.length; i++) {
             // If i >= arity, then arguments[i] must be undefined
             Constraint iGTEQArity = model.arithm(arity, "<=", i);

### 2020-01-17 src/main/Program.java

@@ -21,19 +21,22 @@ import java.io.IOException;
 import java.util.Arrays;
 
 public class Program {
+
+    private static final boolean PRINT_DEBUG_INFO = false;
+
     private String directory;
     private int numSolutions;
-    private int maxNumNodes;
     private int maxNumClauses;
     private double[] probabilities;
+    private int[] arities;
 
+    int maxNumNodes;
     String[] predicates;
-    private int[] ARITIES;
     String[] variables;
     String[] constants;
     int maxArity;
 
-    Tuples arities; // used in defining constraints
+    Tuples aritiesTable; // used in defining constraints
 
     private Model model;
     private IntVar[] clauseAssignments; // an array of predicates occurring at the heads of clauses
@@ -43,17 +46,17 @@ public class Program {
     private java.util.Random rng;
 
     Program(String directory, int numSolutions, int maxNumNodes, int maxNumClauses, ForbidCycles forbidCycles,
-            double[] probabilities, String[] predicates, int[] arities, String[] variables, String[] constants) {
+            double[] probabilities, String[] predicates, int[] aritiesTable, String[] variables, String[] constants) {
         this.directory = directory;
         this.numSolutions = numSolutions;
         this.maxNumNodes = maxNumNodes;
         this.maxNumClauses = maxNumClauses;
         this.probabilities = probabilities;
         this.predicates = predicates;
-        ARITIES = arities;
+        arities = aritiesTable;
         this.variables = variables;
         this.constants = constants;
-        maxArity = Arrays.stream(ARITIES).max().getAsInt();
+        maxArity = Arrays.stream(arities).max().getAsInt();
 
         setUpConstraints();
         if (forbidCycles != ForbidCycles.NONE)
@@ -67,18 +70,24 @@ public class Program {
         if (variables.length > 1)
             numStrategies = maxNumClauses * 5 + 1;
         IntStrategy[] strategies = new IntStrategy[numStrategies];
-        strategies[0] = Search.intVarSearch(new Random<>(rng.nextLong()), new IntDomainRandom(rng.nextLong()), clauseAssignments);
+        strategies[0] = Search.intVarSearch(new Random<>(rng.nextLong()), new IntDomainRandom(rng.nextLong()),
+                clauseAssignments);
         int j = 1;
         for (int i = 0; i < maxNumClauses; i++) {
[…]

### 2020-01-17 src/main/Body.java
Cleanup: step 4

@@ -18,7 +18,7 @@ public class Body {
     // The decision variables relevant to negative cycle detection (i.e., everything except arguments)
     private IntVar[] structuralDecisionVariables;
 
-    public Body(Program program, Model model, IntVar assignment, int clauseIndex) {
+    Body(Program program, Model model, IntVar assignment, int clauseIndex) {
         this.program = program;
 
         // Auxiliary variables

### 2020-01-17 src/main/Head.java

@@ -5,7 +5,6 @@ import org.chocosolver.solver.constraints.Constraint;
 import org.chocosolver.solver.variables.IntVar;
 import org.chocosolver.util.tools.ArrayUtils;
 
-/** The head of a clause */
 class Head {
 
     private IntVar predicate; // PREDICATES.length means that the clause is disabled
@@ -36,7 +35,7 @@ class Head {
         return arguments;
     }
 
-    public IntVar[] getDecisionVariables() {
+    IntVar[] getDecisionVariables() {
         return ArrayUtils.concat(new IntVar[]{predicate}, arguments);
     }
 

### 2020-01-17 src/main/Node.java

@@ -7,8 +7,8 @@ import org.chocosolver.util.tools.ArrayUtils;
 
 class Node {
 
-    private IntVar predicate; // tokens first, then predicates
-    private IntVar[] arguments; // variables first, then constants
+    private IntVar predicate; // Tokens first, then predicates
+    private IntVar[] arguments; // Variables first, then constants
     private IntVar arity;
     private Program program;
 

### 2020-01-17 src/propagators/Dependency.java

@@ -2,6 +2,8 @@ package propagators;
 
 import java.util.Objects;
 
+/** A dependency is either determined (in which case it only holds the predicate name) or undetermined (in which case
+ * it also holds the source and target vertices of the edge that makes it undetermined). */
 final class Dependency {
 
     private final int predicate;

### 2020-01-17 src/propagators/NegativeCyclePropagator.java

@@ -12,13 +12,20 @@ import java.util.ArrayList;
 import java.util.LinkedList;
 import java.util.List;
 
-/** A simple propagator to check if the program contains negative cycles */
+/** A simple propagator to check if the program contains negative cycles (or any cycles) */
 public class NegativeCyclePropagator extends Propagator<IntVar> {
 
     private IntVar[] clauseAssignments;
     private Body[] bodies;
-    private ForbidCycles forbidAllCycles;
+    private ForbidCycles forbidCycles;
     private List<List<SignedPredicate>> adjacencyList;
+
+    public NegativeCyclePropagator(IntVar[] clauseAssignments, Body[] bodies, ForbidCycles forbidCycles) {
+        super(constructDecisionVariables(clauseAssignments, bodies));
+        this.clauseAssignments = clauseAssignments;
+        this.bodies = bodies;
+        this.forbidCycles = forbidCycles;
+    }
 
     static IntVar[] constructDecisionVariables(IntVar[] clauseAssignments, Body[] bodies) {
         IntVar[] decisionVariables = clauseAssignments;
@@ -27,46 +34,20 @@ public class NegativeCyclePropagator extends Propagator<IntVar> {
         return decisionVariables;
     }
 
-    public NegativeCyclePropagator(IntVar[] clauseAssignments, Body[] bodies, ForbidCycles forbidAllCycles) {
-        super(constructDecisionVariables(clauseAssignments, bodies));
-        this.clauseAssignments = clauseAssignments;
-        this.bodies = bodies;
-        this.forbidAllCycles = forbidAllCycles;
-    }
-
     @Override
     public void propagate(int evtmask) throws ContradictionException {
         if (isEntailed() == ESat.FALSE)
             fails();
     }
 
-    /* Adapted from http://geeksforgeeks.org/detect-cycle-in-a-graph/ */
-    private boolean isCyclic(int node, boolean encounteredNegativeEdge, boolean[] visited, boolean[] recursionStack) {
-        // Mark the current node as visited and part of recursion stack
-        if (recursionStack[node] && encounteredNegativeEdge)
-            return true;
-        if (visited[node])
-            return false;
-        visited[node] = true;
-        recursionStack[node] = true;
-
-        for (SignedPredicate p : adjacencyList.get(node)) {
-            if (isCyclic(p.getIndex(), encounteredNegativeEdge || p.getSign() == Sign.NEG,
-                    visited, recursionStack))
-                return true;
-        }
-        recursionStack[node] = false;
-        return false;
-    }
-
[…]

### 2020-01-17 paper/paper.tex
Another redundant constraint
Cleanup: step 2
Cleanup: step 4
Fix a bug in how dependencies are treated

@@
 \usepackage{mathrsfs}
+\usepackage[nounderscore]{syntax}
 
@@
 \newcommand{\arrayt}[3]{\variable{{#3}[}{#2}\variable{] {#1}}}
+\newcommand{\logical}[1]{{\normalfont \texttt{#1}}}
+
 \newcommand{\predicates}{\mathcal{P}}
@@
 \newcommand{\maxNumClauses}{\mathcal{M}_{\mathcal{C}}}
+
+\DeclareMathOperator{\Determined}{Determined}
+\DeclareMathOperator{\Undetermined}{Undetermined}
+\DeclareMathOperator{\AlmostDetermined}{AlmostDetermined}
 
@@
 
+\begin{constraint}[Redundant]
+  For $v \in \variables{}$,
+  \[
+    \variable{introductions}[v] \ne 0 \quad \implies \quad
+    \variable{introductions}[v] - 1 \in \variable{occurrences}[v].
+  \]
+\end{constraint}
+
 \subsection{A Redundant Constraint}
@@
   \KwData{predicates $p_1$, $p_2$; adjacency matrix $\mathbf{A}$}
-  \For{$(d_1, d_2) \in \getDependencies{$p_1$} \times
-    \getDependencies{$p_2$}$ such that $d_1.\predicate = d_2.\predicate$}{
-    \lIf{$d_1$.\isDetermined{} {\bf and} $d_2$.\isDetermined{}}{\fail{}}
-    \uIf{$d_1$.\isDetermined{}}{
-      $\mathbf{A}[d_2.\source][d_2.\target]$.\removeValue{$1$}\;
-    }
-    \ElseIf{$d_2$.\isDetermined{}}{
-      $\mathbf{A}[d_1.\source][d_1.\target]$.\removeValue{$1$}\;
+  \For{$(d_1, d_2) \in \getDependencies{$p_1$, \logical{false}} \times
+      \getDependencies{$p_2$, \logical{false}}$ such that $d_1.\predicate =
+      d_2.\predicate$}{
+    \lIf{$d_1$ {\bf is} $\Determined$ {\bf and} $d_2$ {\bf is}
+      $\Determined$}{\fail{}}
+    \If{$d_1$ {\bf is} $\Determined$ {\bf and} $d_2$ {\bf is}
+      $\AlmostDetermined(\_, s, t)$ {\bf or} \hspace{50pt} $d_2$ {\bf is} $\Determined$ {\bf
+        and} $d_1$ {\bf is} $\AlmostDetermined(\_, s, t)$}{
+      $\mathbf{A}[s][t]$.\removeValue{$1$}\;
     }
   }
-  \caption{Propagation}
+  \caption{Propagation algorithm for predicate independence}
 \end{algorithm}
@@
   \KwData{predicates $p_1$, $p_2$}
-  $D \gets \{ (d_1, d_2) \in \getDependencies{$p_1$} \times
-  \getDependencies{$p_2$} \mid d_1.\predicate = d_2.\predicate \}$\;
-  \If{$\exists (d_1, d_2) \in D$ such that $d_1.\isDetermined{}$ {\bf and}
-    $d_2.\isDetermined{}$}{
-    \Return{\textsc{false}}\;
-  }
+  $D \gets \{ (d_1, d_2) \in \getDependencies{$p_1$, \logical{true}} \times
+  \getDependencies{$p_2$, \logical{true}} \mid d_1.\predicate = d_2.\predicate
+  \}$\;
   \lIf{$D = \emptyset$}{\Return{\textsc{true}}}
+  \lIf{$\exists (\Determined \_, \Determined \_) \in D$}{\Return{\textsc{false}}}
   \Return{\textsc{undefined}}\;
-  \caption{Entailment}
+  \caption{Entailment check for predicate independence}
 \end{algorithm}
+
+% TODO: introduce this sum data type syntax
+\begin{grammar}
+  <dependency> ::= $\Determined p$ | $\Undetermined p$ | $\AlmostDetermined(p, s, t)$
+\end{grammar}
+where $p,s,t \in \predicates{}$. For a dependency $d$---regardless of its exact
+type---we will refer to its predicate $p$ as $d.\variable{predicate}$.
+% TODO: underscore represents a variable that can take any value (different
+% underscores can take different values)
 
@@
   \SetKwData{target}{target}
+  \SetKwData{all}{allDependencies}
   \SetKwFunction{isDetermined}{isDetermined}
@@
   \SetKwProg{Fn}{Function}{:}{}
-  \KwData{an $n \times n$ adjacency matrix $\mathbf{A}$}
-  \Fn{\getDependencies{$p$}} {
-    $D \gets \{ p \}$\;
-    \While{{\normalfont \texttt{true}}}{
+  \KwData{a $|\predicates{}| \times |\predicates{}|$ adjacency matrix
+    $\mathbf{A}$ with $\{ 0, 1 \}$ as the domain}
+  \Fn{\getDependencies{$p$, \all}} {
+    $D \gets \{ \Determined p \}$\;
+    \While{\logical{true}}{
       $D' \gets \emptyset$\;
-      \For{$d \in D$}{
-        \For{$i \gets 1$ \KwTo $n$}{
-          $\edgeExists \gets \mathbf{A}[i][d.\predicate] = \{ 1 \}$\;
-          \uIf{$\edgeExists$ {\bf and} $d$.\isDetermined{}}{
-            $D' \gets D' \cup \{ i \}$\;
+      \For{$d \in D$ {\bf and} $q \in \predicates{}$}{
+        $\edgeExists \gets \mathbf{A}[q][d.\predicate] = \{ 1 \}$\;
+        \uIf{$\edgeExists$ {\bf and} $d$ {\bf is} $\Determined$}{
+          $D' \gets D' \cup \{ \Determined q \}$
         }
-          \uElseIf{$\edgeExists$ {\bf and not} $d$.\isDetermined{}}{
-            $D' \gets D' \cup \{ (i, d.\source, d.\target) \}$\;
+        \uElseIf{$\edgeExists$ {\bf and} $d$ {\bf is} $\AlmostDetermined(\_, s, t)$}{
+          $D' \gets D' \cup \{ \AlmostDetermined(q, s, t) \}$\;
         }
-          \ElseIf{$|\mathbf{A}[i][d.\predicate]| > 1$ {\bf and} $d$.\isDetermined{}}{
-            $D' \gets D' \cup \{ (i, i, d.\predicate) \}$\;
+        \uElseIf{$|\mathbf{A}[q][d.\predicate]| > 1$ {\bf and} $d$ {\bf is}
+          $\Determined r$}{
+          $D' \gets D' \cup \{ \AlmostDetermined(q, q, r) \}$\;
         }
+        \ElseIf{$|\mathbf{A}[q][d.\predicate]| > 1$ {\bf and} \all}{
+          $D' \gets D' \cup \{ \Undetermined q \}$\;
         }
@@
 \end{algorithm}
+% TODO: any way to test all of this?
+
+% TODO: Discuss that the algorithms work in case there are multiple 'paths'
+% without any issues.
+% TODO: An example of algorithms, showing a program that's not fully determined
+% yet, a dependency graph (with dashed and grayed out edges). Create a situation
+% with multiple different dependency paths such that propagation would result in
+% a solution).
 
@@
 % arguments.
+% In order to avoid thrashing, we fix the following variable ordering: [...].
+Example of thrashing: P(X, a) <- ~P(X, b) contradicts the negative cycle constrant.
+Let's try P(X, a) <- P(X, c) instead (and so on).
 
@@
   \Return{\textsc{undefined}}\;
-  \caption{Entailment checking for negative cycles}
+  \caption{Entailment check for negative cycles}
 \end{algorithm}
@@
   atom need not be determined.}
-
-% \section{Conditional Independence}
-
-% Finish the propagation algorithm for conditional independence. The
-%  propagation algorithm for independence is extended with masks that are either
-%  potential or definite. Masking happens in two stages: first, we mask
-%  expressions within formulas, and then predicates. Masking algorithm uses an
-%  algorithm for perfect bipartite matching.
-
-% Both determined $\implies$ fail(). Both determined but at least is one masked by
-% a (probable/determined) mask $\implies$ nothing. One determined $\implies$ the
-% other one cannot exist.
-
-% \begin{algorithm}
-%   \SetKwProg{Fn}{Function}{:}{}
-%   \SetKwFunction{potentialRoots}{potentialRoots}
-%   \SetKwFunction{getTreeValues}{getTreeValues}
-%   \SetKwFunction{getTreeStructureDomainValues}{getTreeStructureDomainValues}
-%   \SetKwData{clause}{clause}
-%   \KwData{connective $c$, a set of predicates $P$}
-%   \Fn{\potentialRoots{\clause, $i$}} {
-%     $R \gets \emptyset$\;
-%     $V \gets \clause.\getTreeValues{$i$}$\;
-%     \For{$v \in V$}{
-%       \uIf{$v = c$}{
-%         $R \gets R \cup \{ (i, |V| = 1) \}$\;
-%       }
-%       \ElseIf{$v \in P$}{
-%         $R' \gets \clause.\getTreeStructureDomainValues{$i$}$\;
-%         $R \gets R \cup \{ (r, |R'| = 1) \mid r \in R' \}$\;
-%       }
-%     }
-%     \Return{$R$}\;
-%   }
-%   \caption{Potential root nodes of the required expression, assuming that the
-%     node at index $i$ is part of the expression}
-% \end{algorithm}
 

### 2020-01-17 src/propagators/IndependencePropagator.java

@@ -5,6 +5,8 @@ import org.chocosolver.solver.exception.ContradictionException;
 import org.chocosolver.solver.variables.IntVar;
 import org.chocosolver.util.ESat;
 import org.chocosolver.util.tools.ArrayUtils;
+import propagators.dependencies.Dependency;
+import propagators.dependencies.Status;
 
 import java.util.HashSet;
 import java.util.Set;
@@ -25,16 +27,16 @@ public class IndependencePropagator extends Propagator<IntVar> {
 
     @Override
     public void propagate(int evtmask) throws ContradictionException {
-        Set<Dependency> dependencies1 = getDependencies(predicate1);
-        Set<Dependency> dependencies2 = getDependencies(predicate2);
+        Set<Dependency> dependencies1 = getDependencies(predicate1, false);
+        Set<Dependency> dependencies2 = getDependencies(predicate2, false);
         for (Dependency dependency1 : dependencies1) {
             for (Dependency dependency2 : dependencies2) {
                 if (dependency1.getPredicate() == dependency2.getPredicate()) {
-                    if (dependency1.isDetermined() && dependency2.isDetermined())
+                    if (dependency1.getStatus() == Status.DETERMINED && dependency2.getStatus() == Status.DETERMINED)
                         fails();
-                    if (dependency1.isDetermined()) {
+                    if (dependency1.getStatus() == Status.DETERMINED) {
                         adjacencyMatrix[dependency2.getSource()][dependency2.getTarget()].removeValue(1, this);
-                    } else if (dependency2.isDetermined()) {
+                    } else if (dependency2.getStatus() == Status.DETERMINED) {
                         adjacencyMatrix[dependency1.getSource()][dependency1.getTarget()].removeValue(1, this);
                     }
                 }
@@ -42,15 +44,14 @@ public class IndependencePropagator extends Propagator<IntVar> {
         }
     }
 
-    // TODO: this could be improved (see the pseudocode)
     @Override
     public ESat isEntailed() {
-        Set<Dependency> dependencies1 = getDependencies(predicate1);
-        Set<Dependency> dependencies2 = getDependencies(predicate2);
+        Set<Dependency> dependencies1 = getDependencies(predicate1, true);
+        Set<Dependency> dependencies2 = getDependencies(predicate2, true);
         for (Dependency dependency1 : dependencies1) {
             for (Dependency dependency2 : dependencies2) {
                 if (dependency1.getPredicate() == dependency2.getPredicate()) {
[…]

### 2020-01-17 paper/paper.tex
An example for predicate independence algorithms

@@
 \usepackage[nounderscore]{syntax}
+\usepackage{blkarray}
 
@@
 \newtheorem{constraint}{Constraint}
+
+\renewcommand\fbox{\fcolorbox{red}{white}}
 
@@
 % TODO: example of edge positivity/negativity
+% TODO: this is not a complete program (by my definition). Make it clear in the text.
 \begin{example} \label{ex:program}
@@
 
-\begin{definition}[Adjacency matrix representation]
+\begin{definition}[Adjacency matrix representation] \label{def:adjacency_matrix}
   An $|\predicates{}| \times |\predicates{}|$ adjacency matrix $\mathbf{A}$ with
@@
   \caption{Entailment check for predicate independence}
+  \label{alg:independence_entailment}
 \end{algorithm}
@@
 % a solution).
+
+\begin{figure}[t]
+  \centering
+\end{figure}
+
+\begin{figure}[t]
+  \centering
+  \begin{minipage}{.49\textwidth}
+    \centering
+    \[
+      \begin{blockarray}{ccccccc}
+        \begin{block}{ccc(cccc)}
+          \mathsf{father} & & & 0 & 0 & 0 & 0 \\
+          \mathsf{mother} & & & 1 & 0 & 0 & 0 \\
+          \mathsf{parent} & & & 1 & \fbox{\{ 0, 1 \}} & \{ 0, 1 \} & \{ 0, 1 \} \\
+          \mathsf{sibling} & & & 0 & 0 & 0 & 0 \\
+        \end{block}
+      \end{blockarray}
+    \]
+    \caption{The adjacency matrix defined using \cref{def:adjacency_matrix} for
+      \cref{example:independence}}
+    \label{fig:dependencies_matrix}
+  \end{minipage}
+  \begin{minipage}{.5\textwidth}
+    \centering
+    \begin{tikzpicture}
+      \node[draw] (parent) at (0, 0.5) {$\mathsf{parent}$};
+      \node[draw] (mother) at (0, -0.5) {$\mathsf{mother}$};
+      \node[draw] (sibling) at (2, 0.5) {$\mathsf{sibling}$};
+      \node[draw] (father) at (2, -0.5) {$\mathsf{father}$};
+      \draw[-{Stealth}] (parent) edge (father);
+      \draw[-{Stealth}] (mother) edge (father);
+      \draw[-{Stealth},dashed,darkgray] (parent) edge (sibling);
+      \draw[-{Stealth},dashed,darkgray] (parent) edge (mother);
+    \end{tikzpicture}
+    \caption{The predicate dependency graph that corresponds to
+      \cref{fig:dependencies_matrix}. Dashed edges are undetermined---they may
+      or may not exist.}
+    \label{fig:dependencies2}
+  \end{minipage}
+\end{figure}
+% TODO: make sure my definitions and examples are consistent with loops
+
+\begin{example} \label{example:independence}
+  Consider this partially determined (fragment of a) program:
+  \begin{align*}
+    \Box(X, Y) &\gets \mathsf{parent}(X, Z) \land \mathsf{parent}(Y, Z),\\
+    \mathsf{father}(X, Y) &\gets \mathsf{parent}(X, Y) \land \neg\mathsf{mother}(X, Y)
+  \end{align*}
+  where $\Box$ indicates an unknown predicate with domain
+  \[
+    D = \{ \mathsf{father}, \mathsf{mother}, \mathsf{parent}, \mathsf{sibling}
+    \}.
+  \]
+  The predicate dependency graph (without positivity/negativity) defined by
+  \cref{def:adjacency_matrix} is represented in
+  \cref{fig:dependencies_matrix,fig:dependencies2}.
+
+  Suppose we have a constraint that $\mathsf{mother}$ and $\mathsf{parent}$ must
+  be independent. The lists of potential dependencies for both predicates are:
+  \begin{align*}
+    D_{\mathsf{mother}} &= \{ \Determined \mathsf{mother}, \AlmostDetermined(\mathsf{parent}, \mathsf{parent}, \mathsf{mother}) \}, \\
+    D_{\mathsf{parent}} &= \{ \Determined \mathsf{parent} \}.
+  \end{align*}
+  An entailment check at this stage would produce \textsc{undefined}, but
+  propagation replaces the boxed value in \cref{fig:dependencies_matrix} with
+  zero, eliminating the potential edge from $\mathsf{parent}$ to
+  $\mathsf{mother}$. This also eliminates $\mathsf{mother}$ from $D$, and,
+  although some undetermined variables remain, this is enough to make
+  \cref{alg:independence_entailment} return \textsc{true}.
+\end{example}
 

### 2020-01-18 analyse_data.R
Generating some  data

@@ -1,0 +1,5 @@
+data <- read.csv("src/runtime.csv", header = FALSE, sep = ";", skip = 1)
+names(data) <- c("numPredicates", "maxArity", "numVariables", "numConstants", "numAdditionalClauses", "numIndependentPairs", "maxNumNodes",
+                 "solutionCount", "buildingTime", "initTime", "totalTime", "nodes", "backtracks", "fails", "restarts")
+small <- data[sample(nrow(data), 1000), ]
+boxplot(small$nodes ~ small$maxNumNodes)

### 2020-01-18 src/main/GeneratePrograms.java

@@ -1,11 +1,11 @@
 package main;
 
 import java.io.*;
-import java.util.ArrayList;
-import java.util.Arrays;
-import java.util.List;
+import java.util.*;
+import java.util.function.Predicate;
 
 import org.chocosolver.util.tools.ArrayUtils;
+import org.jgrapht.util.PrefetchIterator;
 
 import static java.util.stream.Collectors.toList;
 
@@ -43,9 +43,8 @@ class GeneratePrograms {
                 constants[i] = "a" + (i + 1);
             int predictedProgramCount = Integer.parseInt(data[6]);
 
-            Program p = new Program("../programs/", 10000, Integer.parseInt(data[4]),
-                    Integer.parseInt(data[5]), ForbidCycles.NONE, new double[]{1}, predicates, arities, variables,
-                    constants, new PredicatePair[0]);
+            Program p = new Program(Integer.parseInt(data[4]), Integer.parseInt(data[5]), ForbidCycles.NONE,
+                    new double[]{1}, predicates, arities, variables, constants, new PredicatePair[0]);
 
             // Count the number of solutions
             int i = 0;
@@ -111,38 +110,72 @@ class GeneratePrograms {
         return possibilities;
     }
 
+    private static List<PredicatePair> generateAllPairsOfPredicates(String[] predicates) {
+        List<PredicatePair> pairs = new LinkedList<>();
+        for (int i = 0; i < predicates.length; i++)
+            for (int j = i + 1; j < predicates.length; j++)
+                pairs.add(new PredicatePair(predicates, predicates[i], predicates[j]));
+            return pairs;
+    }
 
-    private static void generateAllPrograms() throws IOException {
+    private static PredicatePair[] selectRandomSubset(List<PredicatePair> pairs, int M, Random rng) {
+        int m = M;
+        PredicatePair[] selection = new PredicatePair[m];
+        for (int i = 0; i < pairs.size(); i++) {
+            if (rng.nextInt(pairs.size() - i) < m) {
+                selection[M - m] = pairs.get(i);
+                m--;
+            }
+        }
+        return selection;
+    }
+
+    private static void generateAllPrograms() {
+        Random rng = new Random();
         for (int numPredicates = 1; numPredicates < 5; numPredicates++) {
-            //System.out.println("\n" + numPredicates);
             String[] predicates = new String[numPredicates];
             fillWithNames(predicates, "");
[…]

### 2020-01-18 src/main/Program.java

@@ -23,10 +23,7 @@ import java.util.Arrays;
 public class Program {
 
     private static final boolean PRINT_DEBUG_INFO = false;
-    private static final boolean RESTART_ON_SOLUTIONS = false; // takes much longer but solutions are more random
 
-    private String directory;
-    private int numSolutions;
     private int maxNumClauses;
     private double[] probabilities;
     private int[] arities;
@@ -47,11 +44,9 @@ public class Program {
     private IntVar[][] introductions; // for eliminating variable symmetries
     private java.util.Random rng;
 
-    Program(String directory, int numSolutions, int maxNumNodes, int maxNumClauses, ForbidCycles forbidCycles,
+    Program(int maxNumNodes, int maxNumClauses, ForbidCycles forbidCycles,
             double[] probabilities, String[] predicates, int[] aritiesTable, String[] variables, String[] constants,
             PredicatePair[] independentPairs) {
-        this.directory = directory;
-        this.numSolutions = numSolutions;
         this.maxNumNodes = maxNumNodes;
         this.maxNumClauses = maxNumClauses;
         this.probabilities = probabilities;
@@ -71,8 +66,7 @@ public class Program {
                     new NegativeCyclePropagator(clauseAssignments, bodies, forbidCycles)).post();
 
         setUpVariableOrdering();
-        if (RESTART_ON_SOLUTIONS)
-            model.getSolver().setRestartOnSolutions();
+        //model.getSolver().setRestartOnSolutions();
     }
 
     // ================================================== CONSTRAINTS ==================================================
@@ -269,7 +263,7 @@ public class Program {
         return model.getSolver().solve();
     }
 
-    void saveProgramsToFiles() throws IOException {
+    void saveProgramsToFiles(int numSolutions, String directory) throws IOException {
         Solver solver = model.getSolver();
         if (PRINT_DEBUG_INFO) {
             solver.showDecisions();
@@ -283,6 +277,16 @@ public class Program {
             BufferedWriter writer = new BufferedWriter(new FileWriter(directory + i + ".pl"));
             writer.write(program.toString());
             writer.close();
+        }
+    }
+
+    void compileStatistics(int numSolutions, String prefix) {
+        Solver solver = model.getSolver();
+        solver.setRestartOnSolutions();
+        for (int i = 0; i < numSolutions; i++) {
+            solver.solve();
+            System.out.print(prefix + ";");
+            solver.printCSVStatistics();
         }
     }
 

### 2020-01-18 src/main/GeneratePrograms.java
Found an improvement to one of the constraints

@@ -2,10 +2,8 @@ package main;
 
 import java.io.*;
 import java.util.*;
-import java.util.function.Predicate;
 
 import org.chocosolver.util.tools.ArrayUtils;
-import org.jgrapht.util.PrefetchIterator;
 
 import static java.util.stream.Collectors.toList;
 
@@ -130,7 +128,7 @@ class GeneratePrograms {
         return selection;
     }
 
-    private static void generateAllPrograms() {
+    private static void generateSmallPrograms() {
         Random rng = new Random();
         for (int numPredicates = 1; numPredicates < 5; numPredicates++) {
             String[] predicates = new String[numPredicates];
@@ -173,7 +171,7 @@ class GeneratePrograms {
                                             Program p = new Program(maxNumNodes, maxNumClauses, ForbidCycles.NEGATIVE,
                                                     DEFAULT_PROBABILITIES, predicates, arities, variables, constants,
                                                     independentPairs);
-                                            p.compileStatistics(10, prefix);
+                                            p.compileStatistics(10, prefix, null);
                                         }
                                     }
                                 }
@@ -185,14 +183,65 @@ class GeneratePrograms {
         }
     }
 
-    public static void main(String[] args) throws IOException {
-        generateAllPrograms();
-        //checkNumPrograms();
+    private static void generateBigPrograms(List<Integer> possibilities) {
+        Random rng = new Random();
+        for (int numPredicates : possibilities) {
+            String[] predicates = new String[numPredicates];
+            fillWithNames(predicates, "");
+            List<PredicatePair> potentialIndependentPairs = generateAllPairsOfPredicates(predicates);
 
-        /*String[] predicates = new String[]{"p", "q", "r", "s", "t"};
-        Program p = new Program("../programs/", 2, 5,
-                ForbidCycles.NEGATIVE, DEFAULT_PROBABILITIES, predicates, new int[]{1, 1, 1, 1, 1}, new String[0],
-                new String[]{"a"}, new PredicatePair[]{new PredicatePair(predicates, "p", "q")});
-        p.saveProgramsToFiles(1000);*/
+            for (int maxArity = 1; maxArity < 6; maxArity++) {
+                List<int[]> potentialArities = generateArities(new int[0], predicates.length, maxArity);
+
+                for (int numVariables : possibilities) {
+                    String[] variables = new String[numVariables];
+                    fillWithNames(variables, "v");
+
+                    for (int numConstants : possibilities) {
+                        String[] constants = new String[numConstants];
+                        fillWithNames(constants, "c");
+
[…]

### 2020-01-18 paper/paper.tex
Generating some  data
Found an improvement to one of the constraints
A bit of writing

@@
 \cite{DBLP:books/daglib/0041598} and ProbLog \cite{DBLP:conf/ijcai/RaedtKT07}.
-Tested with SWI-Prolog \cite{DBLP:journals/tplp/WielemakerSTL12}.
+%Tested with SWI-Prolog \cite{DBLP:journals/tplp/WielemakerSTL12}.
 
@@
 
+\begin{constraint}
+  Clauses are sorted.
+\end{constraint}
+
 \section{Heads of Clauses}
@@
   \]
+\end{constraint}
+
+\begin{constraint}
+  Each predicate gets at least one clause. Let
+  \[
+    P = \{ h.\variable{predicate} \mid h \in \variable{headsOfClauses} \}.
+  \]
+  Then
+  \[
+    \variable{nValues}(P) =
+    \begin{cases}
+      \variable{numPredicates} + 1 & \text{if } \variable{count}(\Box, P) > 0 \\
+      \variable{numPredicates} & \text{otherwise.}
+    \end{cases}
+  \]
+  Here, $\variable{nValues}(P)$ counts the number of unique values in $P$.
 \end{constraint}
@@
 \begin{constraint}
-  For $i = 0, \dots, \maxNumNodes{} - 1$, if $\variable{numNodes} \le
-  i$, then
+  For $i = 1, \dots, \maxNumNodes{} - 1$, if $i \ge \variable{numNodes}$, then
   \[
@@
   \[
-    \variable{treeStructure}[i] < \variable{numNodes}.
+    \variable{treeStructure}[i] < i.
   \]
@@
 \section{Eliminating Variable Symmetries} \label{sec:variable_symmetry}
-% TODO: only if we have multiple variables
 
@@
 variable $X$ goes before variable $Y$ if its first occurrence in either the head
-or the body of the clause is before the first occurrence of $Y$.
+or the body of the clause is before the first occurrence of $Y$. Note that the
+constrains described in this section only make sense if $|\variables| > 1$. Also
+note that all definitions and constraints here are on a per-clause basis.
 
@@
 
-\begin{constraint}[Redundant]
-  For $u \ne v \in \constants{} \cup \variables{} \cup \{ \Box \}$,
-  \[
-    \variable{occurrences}[u] \cap \variable{occurrences}[v] = \emptyset.
-  \]
-\end{constraint}
-
 \begin{definition}
@@
 \end{definition}
-
-\begin{constraint}[Redundant]
-  $\variable{allDifferentExcept0}(\variable{introductions})$.
-\end{constraint}
 
@@
 
-\begin{constraint}[Redundant]
+\subsection{Redundant Constraints}
+
+We add a number of redundant constraints to make search more efficient.
+
+\begin{constraint}
+  For $u \ne v \in \constants{} \cup \variables{} \cup \{ \Box \}$,
+  \[
+    \variable{occurrences}[u] \cap \variable{occurrences}[v] = \emptyset.
+  \]
+\end{constraint}
+
+\begin{constraint}
+  $\variable{allDifferentExcept0}(\variable{introductions})$.
+\end{constraint}
+
+\begin{constraint}
   For $v \in \variables{}$,
@@
 
-\subsection{A Redundant Constraint}
-
-For each clause...
-
 \begin{definition}
@@
   by: for $i = 0, \dots, \maxNumNodes{} - 1$, if
-  $\variable{treeValues}[i].\variable{name} \in \tokens{}$, then
+  $\variable{treeValues}[i].\variable{name} \not\in \predicates{}$, then
   \[
@@
   \]
-\end{definition} % TODO: maybe add to the example
-In other words, if the node not a predicate, a variable cannot be introduced as
-one of its `arguments'.
+\end{definition} % TODO: explain these numbers
+In other words, if the node is not a predicate, a variable cannot be introduced
+as one of its `arguments'.
 
@@
   \variable{potentialIntroductions}$.
-\end{constraint}
-
-\section{Interactions Between Clauses}
-
-\begin{constraint}
-  Each predicate gets at least one clause. Let
-  \[
-    P = \{ h.\variable{predicate} \mid h \in \variable{headsOfClauses} \}.
-  \]
-  Then
-  \[
-    \variable{nValues}(P) =
-    \begin{cases}
-      \variable{numPredicates} + 1 & \text{if } \variable{count}(\Box, P) > 0 \\
-      \variable{numPredicates} & \text{otherwise.}
-    \end{cases}
-  \]
-  Here, $\variable{nValues}(P)$ counts the number of unique values in $P$.
-\end{constraint}
-
-\begin{constraint}
-  Clauses are sorted.
 \end{constraint}
@@
 \begin{definition}
-  Let $\mathsf{P}$ be a predicate in a program $\mathscr{P}$. The
+  Let $\mathsf{P}$ be a predicate in a program $\mathscr{P}$. The set of
   \emph{dependencies} of $\mathsf{P}$ is the smallest set $D_{\mathsf{P}}$ such
@@
   \item $\mathsf{P} \in D_{\mathsf{P}}$,
-  \item for every $\mathsf{Q} \in D_{\mathsf{P}}$, the nodes with arrows to
-    $\mathsf{Q}$ in $G_{\mathscr{P}}$ are all in $D_{\mathsf{P}}$.
+  \item for every $\mathsf{Q} \in D_{\mathsf{P}}$, all direct predecessors of
+    $\mathsf{Q}$ in $G_{\mathscr{P}}$ are in $D_{\mathsf{P}}$.
   \end{itemize}
@@
 
-% TODO: example of edge positivity/negativity
-% TODO: this is not a complete program (by my definition). Make it clear in the text.
 \begin{example} \label{ex:program}
-  Consider the following program:
+  Consider the following (fragment of a) program:
   \begin{align}
@@
 
-% TODO: continue writing from here
-We define a \emph{dependency} as an algebraic data type that is either
-determined (in which case it holds only the index of the \texttt{predicate}) or
-undetermined (in which case it also holds the indices of the \texttt{source} and
-\texttt{target} vertices, corresponding to the edge responsible for making the
-dependency undetermined (exactly one, otherwise we don't consider the edge)).
-
-Propagation for independence:
-\begin{itemize}
-\item Look up the dependencies of both predicates. For each pair of
-  matching dependencies:
-  \begin{itemize}
-  \item If both are determined, fail.
-  \item If one is determined, the selected edge of the other must not
-    exist.
-  \end{itemize}
-\end{itemize}
+Given an undetermined model, we can classify all dependencies of a predicate
+$\mathsf{P}$ into three categories based on how many of the edges on the path
+from the dependency to $\mathsf{P}$ are undetermined. In the case of zero, we
+call the dependency \emph{determined}. In the case of one, we call it
+\emph{almost determined}. Otherwise, it is \emph{undetermined}. In the context
+of propagation and entailment algorithms, we define a \emph{dependency} as the
+sum type:
+\begin{grammar}
+  <dependency> ::= $\Determined p$ | $\Undetermined p$ | $\AlmostDetermined(p,
+  s, t)$
+\end{grammar}
+where $p \in \predicates{}$ is the name of the predicate which is the
+dependency of $\mathsf{P}$, and---in the case of $\AlmostDetermined$---$(s, t)
+\in \predicates{}^2$ is the one undetermined edge in $\mathbf{A}$ that prevents
+the dependency from being determined. For a dependency $d$---regardless of its
+exact type---we will refer to its predicate $p$ as $d.\variable{predicate}$. In
+describing the algorithms, we will use an underscore to replace any of $p$, $s$,
+$t$ in situations where the name is unimportant.
 
@@
 \end{algorithm}
-
 \begin{algorithm}[p]
@@
 \end{algorithm}
-
-% TODO: introduce this sum data type syntax
-\begin{grammar}
-  <dependency> ::= $\Determined p$ | $\Undetermined p$ | $\AlmostDetermined(p, s, t)$
-\end{grammar}
-where $p,s,t \in \predicates{}$. For a dependency $d$---regardless of its exact
-type---we will refer to its predicate $p$ as $d.\variable{predicate}$.
-% TODO: underscore represents a variable that can take any value (different
-% underscores can take different values)
-
 \begin{algorithm}[p]
@@
 \end{algorithm}
-% TODO: any way to test all of this?
-
-% TODO: Discuss that the algorithms work in case there are multiple 'paths'
-% without any issues.
-% TODO: An example of algorithms, showing a program that's not fully determined
-% yet, a dependency graph (with dashed and grayed out edges). Create a situation
-% with multiple different dependency paths such that propagation would result in
-% a solution).
-
-\begin{figure}[t]
-  \centering
-\end{figure}
-
 \begin{figure}[t]
@@
 \end{figure}
+
+Propagation for independence:
+\begin{itemize}
+\item Look up the dependencies of both predicates. For each pair of
+  matching dependencies:
+  \begin{itemize}
+  \item If both are determined, fail.
+  \item If one is determined, the selected edge of the other must not
+    exist.
+  \end{itemize}
+\end{itemize}
+
+% TODO: Discuss that the algorithms work in case there are multiple 'paths'
+% without any issues.
 % TODO: make sure my definitions and examples are consistent with loops
@@
 
-\section{Entailment Checking for Negative/All Cycles}
-% TODO: explain that the hasNegativeCycles algorithm is an extension of a simple
-% cycle detection algorithm.
-% TODO: the difficulty with propagation is that there is no good way to define
-% the adjacency matrix with 0/-1/+1 values, the negativity condition is too
-% difficult.
+\section{Entailment Checking for Negative Cycles}
 % TODO: NB: the set of decision variables for this constraint must exclude all
 % arguments.
-% In order to avoid thrashing, we fix the following variable ordering: [...].
-Example of thrashing: P(X, a) <- ~P(X, b) contradicts the negative cycle constrant.
-Let's try P(X, a) <- P(X, c) instead (and so on).
+% TODO: My paper has two slightly different graphs with the same name.
 
@@
   \caption{Entailment check for negative cycles}
+  \label{alg:negative_cycles}
 \end{algorithm}
@@
   atom need not be determined.}
+
+The \texttt{hasNegativeCycles} function is just a simple extension of the cycle
+detection algorithm that `travels' around the graph following edges and
+checking if each vertex has already been visited or not.
+
+The difficulty with creating a propagation algorithm for negative cycles is that
+there seems to be no good way to extend \cref{def:adjacency_matrix} so that the
+adjacency matrix captures positivity/negativity.
+
+\section{Empirical Performance}
+% TODO: need a lot more writing
+
+We split the decision variables into the following groups:
+\begin{enumerate}
+\item all head predicates,
+\item for each clause:
+  \begin{enumerate}
+  \item $\variable{treeStructure}$,
+  \item body predicates,
+  \item head arguments,
+  \item (if $|\variables{}| > 1$) $\variable{introductions}$,
+  \item body arguments.
+  \end{enumerate}
+\end{enumerate}
+And use the `fail first' variable ordering heuristic within each group.
+
+We make no claim that this is optimal, but it does avoid major sources of
+thrashing.
+% Example of thrashing: P(X, a) <- ~P(X, b) contradicts the negative cycle
+% constrant. Let's try P(X, a) <- P(X, c) instead (and so on).
+
+%If we're thrashing on the negative cycle constraint, there's not much I can do
+%about that.
+
+Value ordering heuristic is random (to make the results random).
+
+We also employ a geometric restart policy, restarting after 10, 20, 40,...
+failures (contradictions).
 

### 2020-01-18 analyse_data.R

@@ -1,5 +1,16 @@
 data <- read.csv("src/runtime.csv", header = FALSE, sep = ";", skip = 1)
 names(data) <- c("numPredicates", "maxArity", "numVariables", "numConstants", "numAdditionalClauses", "numIndependentPairs", "maxNumNodes",
-                 "solutionCount", "buildingTime", "initTime", "totalTime", "nodes", "backtracks", "fails", "restarts")
-small <- data[sample(nrow(data), 1000), ]
-boxplot(small$nodes ~ small$maxNumNodes)
+                 "solutionCount", "buildingTime", "totalTime", "initTime", "nodes", "backtracks", "fails", "restarts")
+
+big <- data[data$totalTime == 60, ]
+
+nrow(big)/nrow(data)*100
+tail(sort(data$totalTime), 100)
+
+boxplot(data$nodes ~ data$maxNumNodes)
+boxplot(data$nodes ~ data$numIndependentPairs)
+boxplot(data$nodes ~ data$maxArity)
+
+quantile(data$totalTime, probs = 0.99)
+
+hist(data$totalTime)

### 2020-01-18 src/main/GeneratePrograms.java

@@ -232,11 +232,9 @@ class GeneratePrograms {
     }
 
     public static void main(String[] args) throws IOException {
+        //checkNumPrograms();
         //generateSmallPrograms();
-        checkNumPrograms();
-
-        //Integer[] pars = new Integer[]{1, 2, 4, 8, 16};
-        //generateBigPrograms(Arrays.asList(pars));
+        generateBigPrograms(Arrays.asList(1, 2, 4, 8, 16));
 
         /*String[] predicates = new String[]{"p"};
         Program p = new Program(16, 2,

### 2020-01-18 src/main/Program.java

@@ -241,12 +241,10 @@ public class Program {
         for (int i = 0; i < maxNumClauses; i++) {
             IntStrategy structuralStrategy = Search.intVarSearch(new FirstFail(model),
                     new IntDomainRandom(rng.nextLong()), bodies[i].getTreeStructure());
-            IntStrategy bodyGapStrategy = Search.intVarSearch(new FirstFail(model),
-                    new IntDomainRandom(rng.nextLong()), bodies[i].getArguments());
-            IntStrategy headGapStrategy = Search.intVarSearch(new FirstFail(model),
-                    new IntDomainRandom(rng.nextLong()), clauseHeads[i].getArguments());
             IntStrategy predicateStrategy = Search.intVarSearch(new FirstFail(model),
                     new IntDomainRandom(rng.nextLong()), ArrayUtils.concat(bodies[i].getPredicates()));
+            IntStrategy headGapStrategy = Search.intVarSearch(new FirstFail(model),
+                    new IntDomainRandom(rng.nextLong()), clauseHeads[i].getArguments());
             strategies[j++] = structuralStrategy;
             strategies[j++] = predicateStrategy;
             strategies[j++] = headGapStrategy;
@@ -255,6 +253,8 @@ public class Program {
                         new IntDomainRandom(rng.nextLong()), introductions[i]);
                 strategies[j++] = introductionStrategy;
             }
+            IntStrategy bodyGapStrategy = Search.intVarSearch(new FirstFail(model),
+                    new IntDomainRandom(rng.nextLong()), bodies[i].getArguments());
             strategies[j++] = bodyGapStrategy;
         }
         model.getSolver().setSearch(new StrategiesSequencer(strategies));
@@ -283,7 +283,7 @@ public class Program {
 
     void compileStatistics(int numSolutions, String prefix, String timeout) {
         Solver solver = model.getSolver();
-        solver.setGeometricalRestart(2, 2, new FailCounter(model, 1), 16);
+        solver.setGeometricalRestart(10, 2, new FailCounter(model, 1), 100);
         //solver.setRestartOnSolutions();
         if (timeout != null)
             solver.limitTime(timeout);

### 2020-01-19 paper/one_column/paper.tex
New formatting

--- 2020-01-18 paper/paper.tex
@@
 \usepackage{graphicx}
-%\usepackage[UKenglish]{babel}
-%\usepackage[UKenglish]{isodate}
-%\usepackage[utf8]{inputenc}
 \usepackage[ruled,vlined]{algorithm2e}
@@
 \usepackage{blkarray}
+\usepackage{siunitx}
 
@@
 \newtheorem{constraint}{Constraint}
+\let\definition\relax
+\spnewtheorem{definition}{Definition}{\bfseries}{\rmfamily}
 
@@
   \begin{itemize}
-  \item maximum arity $\maxArity{} \coloneqq \max \arities{}$.
+  \item \emph{maximum arity} $\maxArity{} \coloneqq \max \arities{}$.
   \end{itemize}
@@
   program,
-\item maximum number of solutions,
 \end{itemize}
@@
 \end{constraint}
+
+A random selection of probabilities is added at the end in case a
+probabilistic program is desired. Regular logic programs can be generated by
+setting the list of probabilities to $\{ 1 \}$.
 
@@
 \begin{definition}
-  We define $\variable{numTrees} \in \{ 1, \dots, \maxNumNodes{} \}$ to count
-  the number of trees in our representation of a clause using the
-  $\variable{tree}(\variable{treeStructure}, \variable{numTrees})$\footnote{This
-    constraint uses dominator-based filtering by Fages and Lorca
-    \cite{DBLP:conf/cp/FagesL11}.} constraint.
+  Let $\variable{numTrees} \in \{ 1, \dots, \maxNumNodes{} \}$ be the number of
+  trees in $\variable{treeStructure}$, defined using the $\variable{tree}$
+  constraint \cite{DBLP:conf/cp/FagesL11}.
 \end{definition}
@@
 
-\begin{constraint}
+% TODO: could be improved by only considering positions >i
+\begin{constraint} \label{constraint:node_types}
   For $i = 0, \dots, \maxNumNodes{} - 1$,
@@
   where $\variable{treeStructure}_{-i}$ denotes array $\variable{treeStructure}$
-  with position $i$ skipped.
+  with position $i$ omitted.
 \end{constraint}
-Each constraint corresponds to node $i$ having no children, one child, and
-multiple children, respectively.
+Each of the three equivalences in \cref{constraint:node_types} corresponds to
+node $i$ having no children, one child, and multiple children, respectively.
 
 \begin{constraint}
-  For $i = 0, \dots, \maxNumNodes{} - 1$,
+  Only root nodes can have $\top$ as the value. For $i = 0, \dots,
+  \maxNumNodes{} - 1$,
   \[
@@
 
+A way to `disable' a clause:
 \begin{constraint}
@@
 
+We introduce an array that, for each variable, holds the position of its first
+occurrence.
 \begin{definition}
-  We define $\arrayd{introductions}{|\variables{}|}{\{ 0, \dots, N \}}$ such
-  that for $v \in \variables{}$,
+  Let $\arrayd{introductions}{|\variables{}|}{\{ 0, \dots, N \}}$ be such that
+  for $v \in \variables{}$,
   \[
@@
 \end{definition}
+Here, a value of zero means that the variable does not occur in the clause. We
+want to use specifically zero for this so that we could use
+\cref{constraint:diffbutzero} later. Because of this choice, the definition of
+$\variable{introductions}$ shifts all indices by one.
 
@@
 
-\begin{constraint}
+\begin{constraint} \label{constraint:diffbutzero}
   $\variable{allDifferentExcept0}(\variable{introductions})$.
@@
   \]
-  by: for $i = 0, \dots, \maxNumNodes{} - 1$, if
+  to act as a set of possible values that $\variable{introdutions}$ can take,
+  i.e., for $v \in \variables{}$, $\variable{introductions}[v] \in
+  \variable{potentialIntroductions}$.
+\end{definition}
+
+\begin{constraint} \label{constraint:potentialIntroductions}
+  For $i = 0, \dots, \maxNumNodes{} - 1$, if
   $\variable{treeValues}[i].\variable{name} \not\in \predicates{}$, then
@@
   \]
-\end{definition} % TODO: explain these numbers
-In other words, if the node is not a predicate, a variable cannot be introduced
-as one of its `arguments'.
-
-\begin{constraint}
-  For $v \in \variables{}$, $\variable{introductions}[v] \in
-  \variable{potentialIntroductions}$.
 \end{constraint}
+In simpler terms, \cref{constraint:potentialIntroductions} says that if a node
+in the tree representation of a clause represents something other than a
+predicate, then a variable cannot be introduced as one of its `arguments'.
 
@@
 \end{figure}
-
-Propagation for independence:
-\begin{itemize}
-\item Look up the dependencies of both predicates. For each pair of
-  matching dependencies:
-  \begin{itemize}
-  \item If both are determined, fail.
-  \item If one is determined, the selected edge of the other must not
-    exist.
-  \end{itemize}
-\end{itemize}
+% TODO: make sure my definitions and examples are consistent with loops
 
@@
 % without any issues.
-% TODO: make sure my definitions and examples are consistent with loops
 
@@
   Let $\mathscr{R} \subseteq \mathscr{P}$ be the largest subprogram of
-  $\mathscr{P}$ with all bodies and all predicates in heads fully
-  determined\footnotemark\;
+  $\mathscr{P}$ with its $\variable{treeStructure}$ and predicates in both body
+  and head fully determined\footnotemark\;
   \lIf{$\mathscr{R} = \emptyset$}{\Return{\textsc{undefined}}}
@@
 \end{algorithm}
-\footnotetext{Due to the definition of independence, the arguments of the head
-  atom need not be determined.}
+\footnotetext{The arguments (whether variables or constants) are irrelevant to
+  our definition of independence.}
 
@@
 \section{Empirical Performance}
-% TODO: need a lot more writing
+% TODO: describe the experimental setup (variables), hardware/software (CPU,
+% anything else?)
 
@@
 failures (contradictions).
+
+% TODO: consider replacing \maxNumClauses{} with max_num_additional_clauses
+\begin{itemize}
+\item $|\predicates{}|, |\variables{}|, |\constants{}|, \maxNumNodes{},
+  \text{the number of additional clauses} \in \{ 1, 2, 4, 8, 16 \}$.
+\item $\maxArity{} \in \{ 1, 2, 3, 4, 5 \}$.
+\item all possible numbers of independent pairs: $0, \dots,
+  \binom{|\predicates{}|}{2}$.
+\end{itemize}
+Repeat 10 times:
+\begin{itemize}
+\item Pick a random combination of $|\predicates{}|$ arities such that
+  $\maxArity{}$ is occurs at least once (in an ordered way, since order doesn't
+  matter).
+\item Pick the required number of independent pairs (without repetition).
+\item Run the solver with a \SI{60}{\second} timeout.
+\end{itemize}
+
+Results:
+\begin{itemize}
+\item ??\% of total running times is less than 1 s
+\item ??\% timed out. All of them had $\maxNumNodes{} = 16$.
+\item Out of the ten almost-identical runs with each set of parameters, the
+  number of runs that timed out was always less than ??.
+\item Running time (or number of nodes) as a function of various parameters.
+\end{itemize}
 

### 2020-01-19 analyse_data.R

@@ -1,16 +1,33 @@
 data <- read.csv("src/runtime.csv", header = FALSE, sep = ";", skip = 1)
 names(data) <- c("numPredicates", "maxArity", "numVariables", "numConstants", "numAdditionalClauses", "numIndependentPairs", "maxNumNodes",
                  "solutionCount", "buildingTime", "totalTime", "initTime", "nodes", "backtracks", "fails", "restarts")
+data$percentageIndependent <- round(ifelse(data$numIndependentPairs >= 2, data$numIndependentPairs / choose(data$numPredicates, 2), 0), 2)
 
 big <- data[data$totalTime == 60, ]
-
 nrow(big)/nrow(data)*100
-tail(sort(data$totalTime), 100)
+small <- data[data$totalTime < 1, ]
+nrow(small)/nrow(data)*100
 
-boxplot(data$nodes ~ data$maxNumNodes)
-boxplot(data$nodes ~ data$numIndependentPairs)
-boxplot(data$nodes ~ data$maxArity)
+library(ggplot2)
 
-quantile(data$totalTime, probs = 0.99)
+boxplots <- function(x, y, xl = "", yl = "") {
+  ggplot(data, aes(factor(x), y, group = x)) + geom_boxplot(outlier.shape = NA) +
+    scale_y_continuous(limits = quantile(y, c(0.1, 0.9))) + xlab(xl) + ylab(yl)
+}
 
-hist(data$totalTime)
+boxplots(data$numVariables, data$totalTime)
+boxplots(data$numVariables, data$nodes)
+boxplots(data$numConstants, data$totalTime)
+boxplots(data$numConstants, data$nodes)
+boxplots(data$numAdditionalClauses, data$totalTime)
+boxplots(data$numAdditionalClauses, data$nodes)
+boxplots(data$maxNumNodes, data$totalTime)
+boxplots(data$maxNumNodes, data$nodes)
+
+boxplots(data$percentageIndependent, data$totalTime)
+boxplots(data$percentageIndependent, data$nodes)
+
+boxplots <- function(x, y) {
+  ggplot(data, aes(factor(x), y, group = x)) + geom_boxplot(outlier.shape = NA) +
+    scale_y_continuous(limits = quantile(y, c(0.1, 0.9)))
+}

### 2020-01-19 paper/paper.tex
Fix the appearance of algorithms

@@
-\documentclass[runningheads]{llncs}
-\usepackage{graphicx}
-%\usepackage[UKenglish]{babel}
-%\usepackage[UKenglish]{isodate}
-%\usepackage[utf8]{inputenc}
+\documentclass[letterpaper]{article}
+\usepackage{uai2019}
+\usepackage[margin=1in]{geometry}
 \usepackage[ruled,vlined]{algorithm2e}
@@
 \usepackage{blkarray}
-
-\usetikzlibrary{arrows.meta}
+\usepackage{siunitx}
+\usepackage{amsthm}
+\usepackage[round]{natbib}
 
 \newtheorem{constraint}{Constraint}
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}
+\newtheorem{example}{Example}
 
@@
 
+\makeatletter
+\newcommand{\nosemic}{\renewcommand{\@endalgocfline}{\relax}}% Drop semi-colon ;
+\newcommand{\dosemic}{\renewcommand{\@endalgocfline}{\algocf@endline}}% Reinstate semi-colon ;
+\newcommand{\pushline}{\Indp}% Indent
+\newcommand{\popline}{\Indm\dosemic}% Undent
+\makeatother
+
+\newcommand{\logical}[1]{{\normalfont \texttt{#1}}}
 \newcommand{\variable}[1]{\texttt{\textup{#1}}}
@@
 \newcommand{\arrayt}[3]{\variable{{#3}[}{#2}\variable{] {#1}}}
-\newcommand{\logical}[1]{{\normalfont \texttt{#1}}}
 
@@
 
-\DeclareMathOperator{\Determined}{Determined}
-\DeclareMathOperator{\Undetermined}{Undetermined}
-\DeclareMathOperator{\AlmostDetermined}{AlmostDetermined}
+\DeclareMathOperator{\Determined}{\Delta}
+\DeclareMathOperator{\Undetermined}{\Upsilon}
+\DeclareMathOperator{\AlmostDetermined}{\Gamma}
 
-%\relpenalty=10000
-%\binoppenalty=10000
+\usetikzlibrary{arrows.meta}
+\Crefname{constraint}{Constraint}{Constraints}
+\relpenalty=10000
+\binoppenalty=10000
 \def\multiset#1#2{\ensuremath{\left(\kern-.3em\left(\genfrac{}{}{0pt}{}{#1}{#2}\right)\kern-.3em\right)}}
 
-\begin{document}
+% Set the typeface to Times Roman
+\usepackage{times}
 
 \title{Generating Random Logic Programs Using Constraint Programming}
-\author{Paulius Dilkas\orcidID{0000-1111-2222-3333}}
-\authorrunning{P. Dilkas}
-% First names are abbreviated in the running head.
-% If there are more than two authors, 'et al.' is used.
 
-\institute{University of Edinburgh, Edinburgh, United Kingdom\\
-  \email{p.dilkas@sms.ed.ac.uk}}
+\author{} % LEAVE BLANK FOR ORIGINAL SUBMISSION.
+          % UAI  reviewing is double-blind.
+
+% The author names and affiliations should appear only in the accepted paper.
+%
+%\author{ {\bf Harry Q.~Bovik\thanks{Footnote for author to give an
+%alternate address.}} \\
+%Computer Science Dept. \\
+%Cranberry University\\
+%Pittsburgh, PA 15213 \\
+%\And
+%{\bf Coauthor}  \\
+%Affiliation          \\
+%Address \\
+%\And
+%{\bf Coauthor}   \\
+%Affiliation \\
+%Address    \\
+%(if needed)\\
+%}
+
+% \begin{figure}[h]
+% \vspace{1in}
+% \caption{Sample Figure Caption}
+% \end{figure}
+
+% \begin{table}[h]
+% \caption{Sample Table Title}
+% \label{sample-table}
+% \begin{center}
+% \begin{tabular}{ll}
+% \multicolumn{1}{c}{\bf PART}  &\multicolumn{1}{c}{\bf DESCRIPTION} \\
+% \hline \\
+% Dendrite         &Input terminal \\
+% Axon             &Output terminal \\
+% Soma             &Cell body (contains cell nucleus) \\
+% \end{tabular}
+% \end{center}
+% \end{table}
+
+\begin{document}
+\bibliographystyle{plainnat}
 \maketitle
@@
 \begin{abstract}
-The abstract should briefly summarize the contents of the paper in
-150--250 words.
-
-\keywords{Constraint Programming \and Logic Programming \and Probabilistic Logic
-  Programming.}
+The Abstract paragraph should be indented 0.25 inch (1.5 picas) on
+both left and right-hand margins.  Use 10~point type, with a vertical
+spacing of 11~points.  {\bf Abstract} must be centered, bold, and in
+point size 12. Two line spaces precede the Abstract. The Abstract must
+be limited to one paragraph.
 \end{abstract}
 
-\section{Introduction}
+\section{INTRODUCTION}
 
@@
 
-We also use Choco~4.10.2 \cite{choco}. This works with both Prolog
-\cite{DBLP:books/daglib/0041598} and ProbLog \cite{DBLP:conf/ijcai/RaedtKT07}.
-%Tested with SWI-Prolog \cite{DBLP:journals/tplp/WielemakerSTL12}.
+We also use Choco~4.10.2 \citep{choco}. This works with both Prolog
+\citep{DBLP:books/daglib/0041598} and ProbLog \citep{DBLP:conf/ijcai/RaedtKT07}.
+%Tested with SWI-Prolog \citep{DBLP:journals/tplp/WielemakerSTL12}.
 
-\subsection{Parameters}
+\subsection{PARAMETERS}
 
@@
 variables of the model are contained in two arrays:
-\begin{itemize}
-\item $\arrayt{bodiesOfClauses}{\maxNumClauses{}}{Body}$,
-\item $\arrayt{headsOfClauses}{\maxNumClauses{}}{Head}$
-\end{itemize}
+$\arrayt{bodies}{\maxNumClauses{}}{Body}$ and
+$\arrayt{heads}{\maxNumClauses{}}{Head}$.
 
@@
 
-\section{Heads of Clauses}
+A random selection of probabilities is added at the end in case a
+probabilistic program is desired. Regular logic programs can be generated by
+setting the list of probabilities to $\{ 1 \}$.
+
+\section{HEADS OF CLAUSES}
 
 \begin{definition}
-  The \emph{head} of a clause is composed of:
+  The \emph{head} of a clause is composed of
   \begin{itemize}
@@
   The \variable{predicate}'s $\variable{arity} \in [0, \maxArity{}]$ can then be
-  defined using the \variable{table} constraint as
-  \[
-    \variable{arity} = \begin{cases}
-      \text{the arity of } \variable{predicate} & \text{if }
-      \variable{predicate} \in \predicates{}\\
-      0 & \text{otherwise.}
-    \end{cases}
-  \]
+  defined using the \variable{table} constraint as the arity of the
+  $\variable{predicate}$ if $\variable{predicate} \in \predicates{}$, and zero
+  otherwise.
 \end{definition}
@@
   \[
-    P = \{ h.\variable{predicate} \mid h \in \variable{headsOfClauses} \}.
+    P = \{ h.\variable{predicate} \mid h \in \variable{heads} \}.
   \]
@@
     \begin{cases}
-      \variable{numPredicates} + 1 & \text{if } \variable{count}(\Box, P) > 0 \\
-      \variable{numPredicates} & \text{otherwise.}
+      |\predicates{}| + 1 & \text{if } \variable{count}(\Box, P) > 0 \\
+      |\predicates{}| & \text{otherwise.}
     \end{cases}
@@
 
-\section{Bodies of Clauses}
+\section{BODIES OF CLAUSES}
 
@@
   \begin{itemize}
-  \item $\arrayd{treeStructure}{\maxNumNodes{}}{[0, \maxNumNodes{} - 1]}$ such
+  \item $\arrayd{cstructure}{\maxNumNodes{}}{[0, \maxNumNodes{} - 1]}$ such
     that:
     \begin{itemize}
-    \item $\variable{treeStructure}[i] = i$: the $i$-th node is a root.
-    \item $\variable{treeStructure}[i] = j$: the $i$-th node's parent is node $j$.
+    \item $\variable{structure}[i] = i$: the $i$-th node is a root.
+    \item $\variable{structure}[i] = j$: the $i$-th node's parent is node $j$.
     \end{itemize}
-  \item $\arrayt{treeValues}{\maxNumNodes{}}{Node}$.
+  \item $\arrayt{values}{\maxNumNodes{}}{Node}$.
   \end{itemize}
@@
 
-\begin{figure}[t]
+\begin{figure}
   \centering
@@
   \begin{alignat*}{8}
-    \variable{treeStructure} &= [0, &&0, &&0, &&1, &&2, &&2, &&6, &&7],\\
-    \variable{treeValues} &= [{\lor}, &&{\neg}, &&{\land}, \mathsf{P}(&&X), \mathsf{Q}(&&X), \mathsf{P}(&&X), &&\top, &&\top],\\
+    \variable{structure} &= [0, &&0, &&0, &&1, &&2, &&2, &&6, &&7],\\
+    \variable{values} &= [{\lor}, &&{\neg}, &&{\land}, \mathsf{P}(&&X), \mathsf{Q}(&&X), \mathsf{P}(&&X), &&\top, &&\top],\\
     \variable{numNodes} &= 6, && && && && && && &&\\
@@
   In the rest of this section, we will describe how the elements of
-  $\variable{treeValues}$ are encoded and list a series of constraints that make
+  $\variable{values}$ are encoded and list a series of constraints that make
   this representation unique.
@@
 
-\subsection{Nodes}
+\subsection{NODES}
 
@@
 
-\subsection{Constraints}
+\subsection{CONSTRAINTS}
 
 \begin{definition}
-  We define $\variable{numTrees} \in \{ 1, \dots, \maxNumNodes{} \}$ to count
-  the number of trees in our representation of a clause using the
-  $\variable{tree}(\variable{treeStructure}, \variable{numTrees})$\footnote{This
-    constraint uses dominator-based filtering by Fages and Lorca
-    \cite{DBLP:conf/cp/FagesL11}.} constraint.
+  Let $\variable{numTrees} \in \{ 1, \dots, \maxNumNodes{} \}$ be the number of
+  trees in $\variable{structure}$, defined using the $\variable{tree}$
+  constraint \citep{DBLP:conf/cp/FagesL11}.
 \end{definition}
@@
 \begin{constraint}
-  $\variable{treeStructure}[0] = 0$.
+  $\variable{structure}[0] = 0$.
 \end{constraint}
@@
 \begin{constraint}
-  \variable{treeStructure} is sorted.
+  \variable{structure} is sorted.
 \end{constraint}
@@
   \[
-    \variable{treeStructure}[i] = i \quad \text{and} \quad
-    \variable{treeValues}[i].\variable{name} = \top,
+    \variable{structure}[i] = i, \quad \text{and} \quad
+    \variable{values}[i].\variable{name} = \top,
   \]
-  else
+  else $\variable{structure}[i] < i$.
+\end{constraint}
+
+\begin{constraint} \label{constraint:node_types}
+  For $i = 0, \dots, \maxNumNodes{} - 1$, let $C_i$ be the number of times $i$
+  appears in the \variable{struture} array with index greater than $i$. Then
+  \begin{align*}
+    C = 0 &\iff \variable{values}[i].\variable{name} \in \predicates{} \cup \{ \top \},\\
+    C = 1 &\iff \variable{values}[i].\variable{name} = \neg,\\
+    C > 1 &\iff \variable{values}[i].\variable{name} \in \{ \land, \lor \},
+  \end{align*}
+  where $\variable{structure}_{>i}$ denotes array $\variable{structure}$ with positions
+  greater than $i$.
+\end{constraint}
+Each of the three equivalences in \cref{constraint:node_types} corresponds to
+node $i$ having no children, one child, and multiple children, respectively.
+
+\begin{constraint}
+  Only root nodes can have $\top$ as the value. For $i = 0, \dots,
+  \maxNumNodes{} - 1$,
   \[
-    \variable{treeStructure}[i] < i.
+    \variable{structure}[i] \ne i \implies
+    \variable{values}[i].\variable{name} \ne \top.
   \]
@@
 
-\begin{constraint}
-  For $i = 0, \dots, \maxNumNodes{} - 1$,
-  \begin{align*}
-    \variable{count}(i, \variable{treeStructure}_{-i}) = 0 &\iff \variable{treeValues}[i].\variable{name} \in \predicates{} \cup \{ \top \},\\
-    \variable{count}(i, \variable{treeStructure}_{-i}) = 1 &\iff \variable{treeValues}[i].\variable{name} = \neg,\\
-    \variable{count}(i, \variable{treeStructure}_{-i}) > 1 &\iff \variable{treeValues}[i].\variable{name} \in \{ \land, \lor \},
-  \end{align*}
-  where $\variable{treeStructure}_{-i}$ denotes array $\variable{treeStructure}$
-  with position $i$ skipped.
-\end{constraint}
-Each constraint corresponds to node $i$ having no children, one child, and
-multiple children, respectively.
-
-\begin{constraint}
-  For $i = 0, \dots, \maxNumNodes{} - 1$,
-  \[
-    \variable{treeStructure}[i] \ne i \implies
-    \variable{treeValues}[i].\variable{name} \ne \top.
-  \]
-\end{constraint}
-
+A way to `disable' a clause:
 \begin{constraint}
   For $i = 0, \dots, \maxNumClauses{} - 1$, if
-  $\variable{headsOfClauses}[i].\variable{predicate} = \Box$, then
+  $\variable{heads}[i].\variable{predicate} = \Box$, then
   \[
-    \variable{bodiesOfClauses}[i].\variable{numNodes} = 1,
+    \variable{bodies}[i].\variable{numNodes} = 1,
   \]
@@
   \[
-    \variable{bodiesOfClauses}[i].\variable{treeValues}[0].\variable{name} =
+    \variable{bodies}[i].\variable{values}[0].\variable{name} =
     \top.
@@
 
-\section{Eliminating Variable Symmetries} \label{sec:variable_symmetry}
+\section{VARIABLE SYMMETRIES} \label{sec:variable_symmetry}
 
@@
   Then we can use the $\variable{setsIntsChanneling}$ constraint
-  to define $\variable{occurrences}[|\constants{}| + |\variables{}| + 1]$ as an
+  to define $\variable{occ}[|\constants{}| + |\variables{}| + 1]$ as an
   array of subsets of $\{ 0, \dots, N-1 \}$ such that for all $i = 0, \dots, N
@@
   \[
-    i \in \variable{occurrences}[t] \quad \iff \quad
+    i \in \variable{occ}[t] \quad \iff \quad
     \variable{terms}[i] = t
@@
 
+We introduce an array that, for each variable, holds the position of its first
+occurrence.
 \begin{definition}
-  We define $\arrayd{introductions}{|\variables{}|}{\{ 0, \dots, N \}}$ such
-  that for $v \in \variables{}$,
+  Let $\arrayd{intros}{|\variables{}|}{\{ 0, \dots, N \}}$ be such that
+  for $v \in \variables{}$,
   \[
-    \variable{introductions}[v] = \begin{cases}
-      1 + \min \variable{occurrences}[v] & \text{if }
-      \variable{occurrences}[v] \ne \emptyset\\
+    \variable{intros}[v] = \begin{cases}
+      1 + \min \variable{occ}[v] & \text{if }
+      \variable{occ}[v] \ne \emptyset\\
       0 & \text{otherwise.}
@@
 \end{definition}
+Here, a value of zero means that the variable does not occur in the clause. We
+want to use specifically zero for this so that we could use
+\cref{constraint:diffbutzero} later. Because of this choice, the definition of
+$\variable{intros}$ shifts all indices by one.
 
 \begin{constraint}
-  $\variable{introductions}$ are sorted.
+  $\variable{intros}$ are sorted.
 \end{constraint}
@@
   Then $\variable{terms} = [X, Y, \Box, \Box, X, Z, Y, Z]$ (the boxes represent
-  the conjunction node), $\variable{occurrences} = [\{ 0, 4 \}, \{ 1, 6 \},
-  \{ 5, 7 \}, \{ 2, 3 \}]$, and $\variable{introductions} = [0, 1, 5]$.
+  the conjunction node), $\variable{occ} = [\{ 0, 4 \}, \{ 1, 6 \},
+  \{ 5, 7 \}, \{ 2, 3 \}]$, and $\variable{intros} = [0, 1, 5]$.
 \end{example}
 
-\subsection{Redundant Constraints}
+\subsection{REDUNDANT CONSTRAINTS}
 
@@
   \[
-    \variable{occurrences}[u] \cap \variable{occurrences}[v] = \emptyset.
+    \variable{occ}[u] \cap \variable{occ}[v] = \emptyset.
   \]
@@
 
-\begin{constraint}
-  $\variable{allDifferentExcept0}(\variable{introductions})$.
+\begin{constraint} \label{constraint:diffbutzero}
+  $\variable{allDifferentExcept0}(\variable{intros})$.
 \end{constraint}
@@
   \[
-    \variable{introductions}[v] \ne 0 \quad \implies \quad
-    \variable{introductions}[v] - 1 \in \variable{occurrences}[v].
+    \variable{intros}[v] \ne 0 \quad \iff \quad
+    \variable{intros}[v] - 1 \in \variable{occ}[v].
   \]
@@
   \[
-    \variable{potentialIntroductions} \subseteq \{ 0, \dots, N \}
+    \variable{potentialIntros} \subseteq \{ 0, \dots, N \}
   \]
-  by: for $i = 0, \dots, \maxNumNodes{} - 1$, if
-  $\variable{treeValues}[i].\variable{name} \not\in \predicates{}$, then
+  to act as a set of possible values that $\variable{intros}$ can take,
+  i.e., for $v \in \variables{}$, $\variable{intros}[v] \in
+  \variable{potentialIntros}$.
+\end{definition}
+
+\begin{constraint} \label{constraint:potentialIntroductions}
+  For $i = 0, \dots, \maxNumNodes{} - 1$, let
   \[
-    \variable{potentialIntroductions} \cap \{ \maxArity{} \times (i + 1) + j + 1
-    \mid j = 0, \dots, \maxArity{} - 1 \} = \emptyset.
+    S = \{ \maxArity{} \times (i + 1) + j + 1 \mid j = 0, \dots, \maxArity{} - 1.
+    \}
   \]
-\end{definition} % TODO: explain these numbers
-In other words, if the node is not a predicate, a variable cannot be introduced
-as one of its `arguments'.
+  If $\variable{values}[i].\variable{name} \not\in \predicates{}$, then
+  \[
+    \variable{potentialIntros} \cap S = \emptyset.
+  \]
+\end{constraint}
+In simpler terms, \cref{constraint:potentialIntroductions} says that if a node
+in the tree representation of a clause represents something other than a
+predicate, then a variable cannot be introduced as one of its `arguments'.
 
-\begin{constraint}
-  For $v \in \variables{}$, $\variable{introductions}[v] \in
-  \variable{potentialIntroductions}$.
-\end{constraint}
-
-\section{Counting Programs}
+\section{COUNTING PROGRAMS}
 
@@
 definition can be applied for $n > 1$:
-\[
-  T(n, a) = T(n-1, a) + 2\sum_{\substack{c_1 + \dots + c_k = n - 1,\\
+\begin{align*}
+  T(n, a) = T(n-1, a) + 2&\sum_{\substack{c_1 + \dots + c_k = n - 1,\\
       2 \le k \le \frac{a}{\min \arities{}},\\
-      c_i \ge 1 \text{ for all } i}} \sum_{\substack{d_1 + \dots + d_k = a,\\
+  c_i \ge 1 \text{ for all } i}}\\
+  &\sum_{\substack{d_1 + \dots + d_k = a,\\
   d_i \ge \min \arities{} \text{ for all } i}} \prod_{i=1}^k T(c_i, d_i).
-\]
+\end{align*}
 The first term here represents negation, i.e., negating an expression consumes
@@
 The number of ways to fill $n$ gaps with terms can be expressed as
-\[
-  P(n) = |\constants{}|^n + \sum_{\substack{1 \le k \le |\variables{}|, \\ 0 =
-      s_0 < s_1 < \dots < s_k < s_{k+1} = n+1}} \prod_{i=0}^k (|\constants{}| +
-  i)^{s_{i+1} - s_i - 1}.
-\]
+\begin{align*}
+  P(n) = |\constants{}|^n + &\sum_{\substack{1 \le k \le |\variables{}|, \\ 0 =
+      s_0 < s_1 < \dots < s_k < s_{k+1} = n+1}}\\
+  &\prod_{i=0}^k (|\constants{}| + i)^{s_{i+1} - s_i - 1}.
+\end{align*}
 The first term is simply the number of ways to fill all $n$ gaps with
@@
 
-\section{Predicate Independence}
+\section{PREDICATE INDEPENDENCE}
 
@@
   \centering
-  \begin{minipage}{.5\textwidth}
-    \centering
   \begin{tikzpicture}
@@
   \label{fig:example_tree2}
-  \end{minipage}
-  \begin{minipage}{.49\textwidth}
+\end{figure}
+\begin{figure}
   \centering
@@
   \label{fig:predicate_dependencies}
-  \end{minipage}
 \end{figure}
@@
   \begin{alignat*}{3}
-    D_{\mathsf{parent}} &= \{ \mathsf{parent} \}, \quad && D_{\mathsf{sibling}}
+    D_{\mathsf{parent}} &= \{ \mathsf{parent} \}, && D_{\mathsf{sibling}}
     &&= \{\mathsf{sibling}, \mathsf{parent} \},\\
-    D_{\mathsf{mother}} &= \{ \mathsf{mother} \}, \quad && D_{\mathsf{father}}
+    D_{\mathsf{mother}} &= \{ \mathsf{mother} \}, && D_{\mathsf{father}}
     &&= \{ \mathsf{father}, \mathsf{mother}, \mathsf{parent} \}.
@@
   An $|\predicates{}| \times |\predicates{}|$ adjacency matrix $\mathbf{A}$ with
-  $\{ 0, 1 \}$ as its domain is defined by
-  \begin{align*}
-    \mathbf{A}[i][j] = 0 \iff &\nexists k \in \{ 0, \dots, \maxNumClauses{} \}: \variable{headsOfClauses}[k].\variable{predicate} = j \text{ and } \\
-    &i \in \{ a.\variable{name} \mid a \in \variable{bodiesOfClauses}[k].\variable{treeValues} \}.
-  \end{align*}
+  $\{ 0, 1 \}$ as its domain is defined by stating that $\mathbf{A}[i][j] = 0$
+  if and only if, for all $k \in \{ 0, \dots, \maxNumClauses{} - 1 \}$, either
+$\variable{heads}[k].\variable{predicate} \ne j$ or $i \not\in \{
+a.\variable{name} \mid a \in \variable{bodies}[k].\variable{values} \}$.
 \end{definition}
@@
 \begin{grammar}
-  <dependency> ::= $\Determined p$ | $\Undetermined p$ | $\AlmostDetermined(p,
+  <dependency> ::= $\Determined(p)$ | $\Undetermined(p)$ | $\AlmostDetermined(p,
   s, t)$
@@
 
-\begin{algorithm}[p]
-  \SetKwFunction{getDependencies}{getDependencies}
-  \SetKwFunction{isDetermined}{isDetermined}
+\begin{algorithm}
+  \SetKwFunction{getDependencies}{deps}
   \SetKwFunction{fail}{fail}
@@
   \KwData{predicates $p_1$, $p_2$; adjacency matrix $\mathbf{A}$}
-  \For{$(d_1, d_2) \in \getDependencies{$p_1$, \logical{false}} \times
-      \getDependencies{$p_2$, \logical{false}}$ such that $d_1.\predicate =
-      d_2.\predicate$}{
-    \lIf{$d_1$ {\bf is} $\Determined$ {\bf and} $d_2$ {\bf is}
-      $\Determined$}{\fail{}}
-    \If{$d_1$ {\bf is} $\Determined$ {\bf and} $d_2$ {\bf is}
-      $\AlmostDetermined(\_, s, t)$ {\bf or} \hspace{50pt} $d_2$ {\bf is} $\Determined$ {\bf
-        and} $d_1$ {\bf is} $\AlmostDetermined(\_, s, t)$}{
+  \For{$(d_1, d_2) \in \getDependencies{$p_1$, 0} \times \getDependencies{$p_2$,
+      0}$ such that $d_1.\predicate = d_2.\predicate$}{
+    \lIf{$d_1$ {\bf is} $\Determined(\_)$ {\bf and} $d_2$ {\bf is}
+      $\Determined(\_)$}{\fail{}}
+    \If{$d_1$ {\bf is} $\Determined(\_)$ {\bf and} $d_2$ {\bf is}
+      $\AlmostDetermined(\_, s, t)$ {\bf or} \hspace{50pt} $d_2$ {\bf is}
+      $\Determined(\_)$ {\bf and} $d_1$ {\bf is} $\AlmostDetermined(\_, s, t)$}{
       $\mathbf{A}[s][t]$.\removeValue{$1$}\;
@@
   }
-  \caption{Propagation algorithm for predicate independence}
+  \caption{Propagation for independence}
 \end{algorithm}
-\begin{algorithm}[p]
-  \SetKwFunction{getDependencies}{getDependencies}
+\begin{algorithm}
+  \SetKwFunction{getDependencies}{deps}
   \SetKwFunction{isDetermined}{isDetermined}
@@
   \KwData{predicates $p_1$, $p_2$}
-  $D \gets \{ (d_1, d_2) \in \getDependencies{$p_1$, \logical{true}} \times
-  \getDependencies{$p_2$, \logical{true}} \mid d_1.\predicate = d_2.\predicate
-  \}$\;
+  \nosemic $D \gets \{ (d_1, d_2) \in \getDependencies{$p_1$, 1} \times \getDependencies{$p_2$, 1}$\;
+  \hspace{27pt}\dosemic $\mid d_1.\predicate = d_2.\predicate \}$\;
   \lIf{$D = \emptyset$}{\Return{\textsc{true}}}
@@
   \Return{\textsc{undefined}}\;
-  \caption{Entailment check for predicate independence}
+  \caption{Entailment for independence}
   \label{alg:independence_entailment}
 \end{algorithm}
-\begin{algorithm}[p]
-  \SetKwData{edgeExists}{edgeExists}
+\begin{algorithm}
+  \SetKwData{edgeExists}{edge}
   \SetKwData{predicate}{predicate}
@@
   \SetKwFunction{isDetermined}{isDetermined}
-  \SetKwFunction{getDependencies}{getDependencies}
+  \SetKwFunction{getDependencies}{deps}
   \SetKwProg{Fn}{Function}{:}{}
-  \KwData{a $|\predicates{}| \times |\predicates{}|$ adjacency matrix
-    $\mathbf{A}$ with $\{ 0, 1 \}$ as the domain}
+  \KwData{adjacency matrix $\mathbf{A}$}
   \Fn{\getDependencies{$p$, \all}} {
-    $D \gets \{ \Determined p \}$\;
+    $D \gets \{ \Determined(p) \}$\;
     \While{\logical{true}}{
@@
         $\edgeExists \gets \mathbf{A}[q][d.\predicate] = \{ 1 \}$\;
-        \uIf{$\edgeExists$ {\bf and} $d$ {\bf is} $\Determined$}{
-          $D' \gets D' \cup \{ \Determined q \}$
+        \uIf{$\edgeExists$ {\bf and} $d$ {\bf is} $\Determined(\_)$}{
+          $D' \gets D' \cup \{ \Determined(q) \}$
         }
-        \uElseIf{$\edgeExists$ {\bf and} $d$ {\bf is} $\AlmostDetermined(\_, s, t)$}{
+        \uElseIf{$\edgeExists$ {\bf and} $d$ {\bf is} $\AlmostDetermined(\_, s,
+          t)$}{
           $D' \gets D' \cup \{ \AlmostDetermined(q, s, t) \}$\;
         }
-        \uElseIf{$|\mathbf{A}[q][d.\predicate]| > 1$ {\bf and} $d$ {\bf is}
-          $\Determined r$}{
+        \uElseIf{$|\mathbf{A}[q][d.\predicate]| > 1$ {\bf and} $d$~{\bf is}~$\Determined(r)$}{
           $D' \gets D' \cup \{ \AlmostDetermined(q, q, r) \}$\;
@@
         \ElseIf{$|\mathbf{A}[q][d.\predicate]| > 1$ {\bf and} \all}{
-          $D' \gets D' \cup \{ \Undetermined q \}$\;
+          $D' \gets D' \cup \{ \Undetermined(q) \}$\;
         }
@@
   }
-  \caption{Computing the dependencies of a predicate}
+  \caption{Dependencies of a predicate}
 \end{algorithm}
-\begin{figure}[t]
-  \centering
-  \begin{minipage}{.49\textwidth}
+\begin{figure}
   \centering
@@
   \label{fig:dependencies_matrix}
-  \end{minipage}
-  \begin{minipage}{.5\textwidth}
+\end{figure}
+\begin{figure}
   \centering
@@
   \label{fig:dependencies2}
-  \end{minipage}
 \end{figure}
-
-Propagation for independence:
-\begin{itemize}
-\item Look up the dependencies of both predicates. For each pair of
-  matching dependencies:
-  \begin{itemize}
-  \item If both are determined, fail.
-  \item If one is determined, the selected edge of the other must not
-    exist.
-  \end{itemize}
-\end{itemize}
+% TODO: make sure my definitions and examples are consistent with loops
 
@@
   \begin{align*}
-    D_{\mathsf{mother}} &= \{ \Determined \mathsf{mother}, \AlmostDetermined(\mathsf{parent}, \mathsf{parent}, \mathsf{mother}) \}, \\
-    D_{\mathsf{parent}} &= \{ \Determined \mathsf{parent} \}.
+    D_{\mathsf{mother}} &= \{ \Determined(\mathsf{mother}), \AlmostDetermined(\mathsf{parent}, \mathsf{parent}, \mathsf{mother}) \}, \\
+    D_{\mathsf{parent}} &= \{ \Determined(\mathsf{parent}) \}.
   \end{align*}
@@
 
-\section{Entailment Checking for Negative Cycles}
+\section{NEGATIVE CYCLES}
 % TODO: NB: the set of decision variables for this constraint must exclude all
@@
 \begin{algorithm}[t]
-  \KwData{a constraint model for a logic program $\mathscr{P}$ amid execution}
+  \KwData{a program $\mathscr{P}$}
   \SetKwFunction{hasNegativeCycles}{hasNegativeCycles}
   Let $\mathscr{R} \subseteq \mathscr{P}$ be the largest subprogram of
-  $\mathscr{P}$ with all bodies and all predicates in heads fully
-  determined\footnotemark\;
+  $\mathscr{P}$ with its $\variable{structure}$ and predicates in both body
+  and head fully determined\footnotemark\;
   \lIf{$\mathscr{R} = \emptyset$}{\Return{\textsc{undefined}}}
-  \lIf{\hasNegativeCycles($G_{\mathscr{R}}$)}{\Return{\textsc{false}}}
+  \If{\hasNegativeCycles($G_{\mathscr{R}}$)}{
+    \Return{\textsc{false}}\;
+  }
   \lIf{$\mathscr{R} = \mathscr{P}$}{\Return{\textsc{true}}}
@@
 
-\section{Empirical Performance}
-% TODO: need a lot more writing
+\section{EMPIRICAL PERFORMANCE}
+% TODO: describe the experimental setup (variables), hardware/software (CPU,
+% anything else?)
 
@@
   \begin{enumerate}
-  \item $\variable{treeStructure}$,
+  \item $\variable{structure}$,
   \item body predicates,
   \item head arguments,
-  \item (if $|\variables{}| > 1$) $\variable{introductions}$,
+  \item (if $|\variables{}| > 1$) $\variable{intros}$,
   \item body arguments.
@@
 
-\section{Conclusion \& Future Work}
+% TODO: consider replacing \maxNumClauses{} with max_num_additional_clauses
+\begin{itemize}
+\item $|\predicates{}|$, $|\variables{}|$, $|\constants{}|$, $\maxNumNodes{}$,
+  the number of additional clauses are in $\{ 1, 2, 4, 8, 16 \}$.
+\item $\maxArity{} \in \{ 1, 2, 3, 4, 5 \}$.
+\item all possible numbers of independent pairs: $0, \dots,
+  \binom{|\predicates{}|}{2}$.
+\end{itemize}
+Repeat 10 times:
+\begin{itemize}
+\item Pick a random combination of $|\predicates{}|$ arities such that
+  $\maxArity{}$ is occurs at least once (in an ordered way, since order doesn't
+  matter).
+\item Pick the required number of independent pairs (without repetition).
+\item Run the solver with a \SI{60}{\second} timeout.
+\end{itemize}
+
+Results:
+\begin{itemize}
+\item ??\% of total running times is less than 1 s
+\item ??\% timed out. All of them had $\maxNumNodes{} = 16$.
+\item Out of the ten almost-identical runs with each set of parameters, the
+  number of runs that timed out was always less than ??.
+\item Running time (or number of nodes) as a function of various parameters.
+\end{itemize}
+
+\section{CONCLUSION \& FUTURE WORK}
 
@@
 
-\section*{Acknowledgments}
+\subsubsection*{Acknowledgements}
 
@@
 
-\bibliographystyle{splncs04}
+\renewcommand{\bibsection}{\subsubsection*{References}}
 \bibliography{paper}
-
 \end{document}

### 2020-01-19 src/main/Body.java

@@ -7,6 +7,7 @@ import org.chocosolver.util.tools.ArrayUtils;
 import propagators.Sign;
 import propagators.SignedPredicate;
 
+import java.util.Arrays;
 import java.util.LinkedList;
 import java.util.List;
 
@@ -53,15 +54,11 @@ public class Body {
             IntVar exactlyOne = model.intVar(1);
             IntVar moreThanOne = model.intVar(2, Math.max(program.maxNumNodes, 2));
 
-            IntVar[] structureWithoutI = new IntVar[program.maxNumNodes - 1];
-            for (int j = 0; j < i; j++)
-                structureWithoutI[j] = treeStructure[j];
-            for (int j = i + 1; j < program.maxNumNodes; j++)
-                structureWithoutI[j - 1] = treeStructure[j];
+            IntVar[] potentialChildren = Arrays.copyOfRange(treeStructure, i + 1, treeStructure.length);
 
-            Constraint isLeaf = model.count(i, structureWithoutI, exactlyZero);
-            Constraint isNegation = model.count(i, structureWithoutI, exactlyOne);
-            Constraint isInternal = model.count(i, structureWithoutI, moreThanOne);
+            Constraint isLeaf = model.count(i, potentialChildren, exactlyZero);
+            Constraint isNegation = model.count(i, potentialChildren, exactlyOne);
+            Constraint isInternal = model.count(i, potentialChildren, moreThanOne);
             Constraint mustBeAConnective = model.member(treeValues[i].getPredicate(),
                     new int[]{Token.AND.ordinal(), Token.OR.ordinal()});
 

### 2020-01-19 src/main/GeneratePrograms.java

@@ -190,7 +190,7 @@ class GeneratePrograms {
             fillWithNames(predicates, "");
             List<PredicatePair> potentialIndependentPairs = generateAllPairsOfPredicates(predicates);
 
-            for (int maxArity = 1; maxArity < 6; maxArity++) {
+            for (int maxArity = 1; maxArity < 5; maxArity++) {
                 List<int[]> potentialArities = generateArities(new int[0], predicates.length, maxArity);
 
                 for (int numVariables : possibilities) {
@@ -234,7 +234,7 @@ class GeneratePrograms {
     public static void main(String[] args) throws IOException {
         //checkNumPrograms();
         //generateSmallPrograms();
-        generateBigPrograms(Arrays.asList(1, 2, 4, 8, 16));
+        generateBigPrograms(Arrays.asList(1, 2, 4, 8));
 
         /*String[] predicates = new String[]{"p"};
         Program p = new Program(16, 2,

### 2020-01-20 paper/paper.tex
And the data is in (with a nice plot)

@@
   \begin{itemize}
-  \item $\arrayd{cstructure}{\maxNumNodes{}}{[0, \maxNumNodes{} - 1]}$ such
+  \item $\arrayd{structure}{\maxNumNodes{}}{[0, \maxNumNodes{} - 1]}$ such
     that:
@@
   \begin{align*}
-    C = 0 &\iff \variable{values}[i].\variable{name} \in \predicates{} \cup \{ \top \},\\
-    C = 1 &\iff \variable{values}[i].\variable{name} = \neg,\\
-    C > 1 &\iff \variable{values}[i].\variable{name} \in \{ \land, \lor \},
+    C_i = 0 &\iff \variable{values}[i].\variable{name} \in \predicates{} \cup \{ \top \},\\
+    C_i = 1 &\iff \variable{values}[i].\variable{name} = \neg,\\
+    C_i > 1 &\iff \variable{values}[i].\variable{name} \in \{ \land, \lor \}.
   \end{align*}
-  where $\variable{structure}_{>i}$ denotes array $\variable{structure}$ with positions
-  greater than $i$.
 \end{constraint}
@@
   \caption{Propagation for independence}
+  \label{alg:independence_propagation}
 \end{algorithm}
@@
   \caption{Dependencies of a predicate}
+  \label{alg:dependencies}
 \end{algorithm}
@@
 \end{figure}
+
+% TODO: start here
 % TODO: make sure my definitions and examples are consistent with loops
-
 % TODO: Discuss that the algorithms work in case there are multiple 'paths'
 % without any issues.
+
+Note that if there are multiple paths in the dependency graph from $\mathsf{Q}$
+to $\mathsf{P}$, when constructing $D_{\mathsf{P}}$, \cref{alg:dependencies}
+could include $\mathsf{Q}$ once for each possible type ($\Determined$,
+$\Undetermined$, and $\AlmostDetermined$). However,
+\cref{alg:independence_propagation,alg:independence_entailment}
 
@@
 
-\begin{algorithm}[t]
+\begin{algorithm}
   \KwData{a program $\mathscr{P}$}
@@
 \section{EMPIRICAL PERFORMANCE}
-% TODO: describe the experimental setup (variables), hardware/software (CPU,
-% anything else?)
+% TODO: describe the experimental setup (variables), hardware/software (CPU, anything else?)
+% see Downloads/cp2019-wiggles.pdf for an example.
+
+\begin{figure*}[t]
+  \centering
+  \input{phase_transition.tex}
+  \caption{TODO}
+\end{figure*}
 
@@
 
-We also employ a geometric restart policy, restarting after 10, 20, 40,...
+We also employ a geometric restart policy, restarting after $10, 20, 40,\dots$
 failures (contradictions).
@@
 \item $|\predicates{}|$, $|\variables{}|$, $|\constants{}|$, $\maxNumNodes{}$,
-  the number of additional clauses are in $\{ 1, 2, 4, 8, 16 \}$.
-\item $\maxArity{} \in \{ 1, 2, 3, 4, 5 \}$.
+  the number of additional clauses are in $\{ 1, 2, 4, 8 \}$.
+\item $\maxArity{} \in \{ 1, 2, 3, 4 \}$.
 \item all possible numbers of independent pairs: $0, \dots,
@@
 \begin{itemize}
-\item ??\% of total running times is less than 1 s
-\item ??\% timed out. All of them had $\maxNumNodes{} = 16$.
-\item Out of the ten almost-identical runs with each set of parameters, the
-  number of runs that timed out was always less than ??.
-\item Running time (or number of nodes) as a function of various parameters.
+\item almost \num{400000} experiments.
+\item \SI{97.7}{\percent} of total running times is less than \SI{1}{\second}
+\item 4 timeouts: all with 8 predicates, 8 additional clauses, and
+  $\maxNumNodes{} = 8$; the rest of the parameters differ.
+\item Running time (or number of nodes) as a function of various parameters:
+  \begin{itemize}
+  \item The number of clauses has a clear impact on time but not number of
+    nodes.
+  \item $\maxNumNodes{}$ has a huge impact on both.
+  \item The proportion of independent pairs of predicates is acting weird.
+    Investigate.
+  \end{itemize}
 \end{itemize}
@@
   some kind of normal form. Not doing this on purpose. Leaving for further work.
-\item Perhaps negative cycle detection could use the same graph as the
-  independence propagator? If we extend each domain to {-1, 0, 1}, but that
-  might make propagation weaker or slower.
 \item Could investigate how uniform the generated distribution of programs is.
@@
   because, e.g., there are more 5-tuples than 4-tuples.
-\item Inference options to explore. Logspace vs normal space. Symbolic vs
-  non-symbolic. Propagate evidence (might be irrelevant)? Propagate weights?
-  Supported knowledge compilation techniques: sdd, sddx, bdd, nnf, ddnnf, kbest,
-  fsdd, fbdd.
+%\item Inference options to explore. Logspace vs normal space. Symbolic vs
+%  non-symbolic. Propagate evidence (might be irrelevant)? Propagate weights?
+%  Supported knowledge compilation techniques: sdd, sddx, bdd, nnf, ddnnf, kbest,
+%  fsdd, fbdd.
 \item Mention the random heuristic. Mention that restarting gives better
-  randomness, but duplicates become possible. Restarting after each run is
-  expensive. Periodic restarts could be an option.
+  randomness, but duplicates become possible.
 \item Could add statistics about what constraints tend to conflict.

### 2020-01-20 paper/phase_transition.tex
And the data is in (with a nice plot)

% Created by tikzDevice version 0.12.3 on 2020-01-20 17:11:57
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (433.62,144.54);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,144.54);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (433.62,144.54);
\end{scope}
\begin{scope}
\path[clip] ( 34.79, 30.69) rectangle (428.12,139.04);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] ( 34.79, 30.69) rectangle (428.12,139.04);
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.79, 84.06) --
	(428.12, 84.06);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.79,114.41) --
	(428.12,114.41);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.79,122.88) --
	(428.12,122.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.79, 30.69) --
	(428.12, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.79,102.78) --
	(428.12,102.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 47.60, 30.69) --
	( 47.60,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 60.73, 30.69) --
	( 60.73,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.86, 30.69) --
	( 73.86,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 86.99, 30.69) --
	( 86.99,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (100.13, 30.69) --
	(100.13,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (113.26, 30.69) --
	(113.26,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (126.39, 30.69) --
	(126.39,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.53, 30.69) --
	(139.53,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (152.66, 30.69) --
	(152.66,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.79, 30.69) --
	(165.79,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (178.92, 30.69) --
	(178.92,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (192.06, 30.69) --
	(192.06,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (205.19, 30.69) --
	(205.19,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (218.32, 30.69) --
	(218.32,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.46, 30.69) --
	(231.46,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (244.59, 30.69) --
	(244.59,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (257.72, 30.69) --
	(257.72,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (270.85, 30.69) --
	(270.85,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (283.99, 30.69) --
	(283.99,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (297.12, 30.69) --
	(297.12,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (310.25, 30.69) --
	(310.25,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (323.39, 30.69) --
	(323.39,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (336.52, 30.69) --
	(336.52,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (349.65, 30.69) --
	(349.65,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (362.78, 30.69) --
	(362.78,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (375.92, 30.69) --
	(375.92,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (389.05, 30.69) --
	(389.05,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (402.18, 30.69) --
	(402.18,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (415.32, 30.69) --
	(415.32,139.04);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 47.60, 82.72) --
	( 47.60,103.19);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 47.60, 52.70) --
	( 47.60, 41.88) --
	( 47.60, 25.23) --
	( 47.60,  0.00);
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 42.67, 82.72) --
	( 42.67, 52.70) --
	( 47.60, 52.70) --
	( 52.52, 52.70) --
	( 52.52, 82.72) --
	( 47.60, 82.72) --
	( 42.67, 82.72) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 42.67, 67.97) --
	( 47.60, 67.97) --
	( 52.52, 67.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 60.73, 85.45) --
	( 60.73,106.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 60.73, 52.70) --
	( 60.73, 36.00) --
	( 60.73,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 55.80, 85.45) --
	( 55.80, 52.70) --
	( 60.73, 52.70) --
	( 65.65, 52.70) --
	( 65.65, 85.45) --
	( 60.73, 85.45) --
	( 55.80, 85.45) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 55.80, 68.54) --
	( 60.73, 68.54) --
	( 65.65, 68.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.86, 85.83) --
	( 73.86,107.32);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.86, 51.92) --
	( 73.86, 34.23) --
	( 73.86,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 68.94, 85.83) --
	( 68.94, 51.92) --
	( 73.86, 51.92) --
	( 78.79, 51.92) --
	( 78.79, 85.83) --
	( 73.86, 85.83) --
	( 68.94, 85.83) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 68.94, 68.82) --
	( 73.86, 68.82) --
	( 78.79, 68.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 86.99, 86.94) --
	( 86.99,108.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 86.99, 52.07) --
	( 86.99, 34.79) --
	( 86.99,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 82.07, 86.94) --
	( 82.07, 52.07) --
	( 86.99, 52.07) --
	( 91.92, 52.07) --
	( 91.92, 86.94) --
	( 86.99, 86.94) --
	( 82.07, 86.94) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 82.07, 68.82) --
	( 86.99, 68.82) --
	( 91.92, 68.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] (100.13, 87.86) --
	(100.13,109.89);

\path[draw=drawColor,line width= 0.6pt,line join=round] (100.13, 52.07) --
	(100.13, 34.79) --
	(100.13,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 95.20, 87.86) --
	( 95.20, 52.07) --
	(100.13, 52.07) --
	(105.05, 52.07) --
	(105.05, 87.86) --
	(100.13, 87.86) --
	( 95.20, 87.86) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 95.20, 69.46) --
	(100.13, 69.46) --
	(105.05, 69.46);

\path[draw=drawColor,line width= 0.6pt,line join=round] (113.26, 88.21) --
	(113.26,110.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (113.26, 52.23) --
	(113.26, 34.65) --
	(113.26,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (108.34, 88.21) --
	(108.34, 52.23) --
	(113.26, 52.23) --
	(118.18, 52.23) --
	(118.18, 88.21) --
	(113.26, 88.21) --
	(108.34, 88.21) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (108.34, 69.19) --
	(113.26, 69.19) --
	(118.18, 69.19);

\path[draw=drawColor,line width= 0.6pt,line join=round] (126.39, 87.91) --
	(126.39,110.12);

\path[draw=drawColor,line width= 0.6pt,line join=round] (126.39, 51.43) --
	(126.39, 34.23) --
	(126.39,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (121.47, 87.91) --
	(121.47, 51.43) --
	(126.39, 51.43) --
	(131.32, 51.43) --
	(131.32, 87.91) --
	(126.39, 87.91) --
	(121.47, 87.91) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (121.47, 68.82) --
	(126.39, 68.82) --
	(131.32, 68.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.53, 89.24) --
	(139.53,111.73);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.53, 51.43) --
	(139.53, 34.51) --
	(139.53,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (134.60, 89.24) --
	(134.60, 51.43) --
	(139.53, 51.43) --
	(144.45, 51.43) --
	(144.45, 89.24) --
	(139.53, 89.24) --
	(134.60, 89.24) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (134.60, 69.28) --
	(139.53, 69.28) --
	(144.45, 69.28);

\path[draw=drawColor,line width= 0.6pt,line join=round] (152.66, 88.81) --
	(152.66,111.09);

\path[draw=drawColor,line width= 0.6pt,line join=round] (152.66, 51.92) --
	(152.66, 35.33) --
	(152.66,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (147.73, 88.81) --
	(147.73, 51.92) --
	(152.66, 51.92) --
	(157.58, 51.92) --
	(157.58, 88.81) --
	(152.66, 88.81) --
	(147.73, 88.81) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (147.73, 69.37) --
	(152.66, 69.37) --
	(157.58, 69.37);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.79, 89.53) --
	(165.79,112.08);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.79, 51.43) --
	(165.79, 34.09) --
	(165.79,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (160.87, 89.53) --
	(160.87, 51.43) --
	(165.79, 51.43) --
	(170.72, 51.43) --
	(170.72, 89.53) --
	(165.79, 89.53) --
	(160.87, 89.53) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (160.87, 69.19) --
	(165.79, 69.19) --
	(170.72, 69.19);

\path[draw=drawColor,line width= 0.6pt,line join=round] (178.92, 89.53) --
	(178.92,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (178.92, 51.60) --
	(178.92, 40.77) --
	(178.92, 24.09) --
	(178.92,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (174.00, 89.53) --
	(174.00, 51.60) --
	(178.92, 51.60) --
	(183.85, 51.60) --
	(183.85, 89.53) --
	(178.92, 89.53) --
	(174.00, 89.53) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (174.00, 69.64) --
	(178.92, 69.64) --
	(183.85, 69.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (192.06, 89.63) --
	(192.06,112.20);

\path[draw=drawColor,line width= 0.6pt,line join=round] (192.06, 51.43) --
	(192.06, 34.51) --
	(192.06,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (187.13, 89.63) --
	(187.13, 51.43) --
	(192.06, 51.43) --
	(196.98, 51.43) --
	(196.98, 89.63) --
	(192.06, 89.63) --
	(187.13, 89.63) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (187.13, 69.64) --
	(192.06, 69.64) --
	(196.98, 69.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (205.19, 90.11) --
	(205.19,112.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] (205.19, 51.27) --
	(205.19, 33.95) --
	(205.19,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (200.27, 90.11) --
	(200.27, 51.27) --
	(205.19, 51.27) --
	(210.11, 51.27) --
	(210.11, 90.11) --
	(205.19, 90.11) --
	(200.27, 90.11) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (200.27, 69.37) --
	(205.19, 69.37) --
	(210.11, 69.37);

\path[draw=drawColor,line width= 0.6pt,line join=round] (218.32, 90.05) --
	(218.32,112.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (218.32, 51.11) --
	(218.32, 34.09) --
	(218.32,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (213.40, 90.05) --
	(213.40, 51.11) --
	(218.32, 51.11) --
	(223.25, 51.11) --
	(223.25, 90.05) --
	(218.32, 90.05) --
	(213.40, 90.05) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (213.40, 69.00) --
	(218.32, 69.00) --
	(223.25, 69.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.46, 90.34) --
	(231.46,112.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.46, 51.27) --
	(231.46, 34.51) --
	(231.46,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (226.53, 90.34) --
	(226.53, 51.27) --
	(231.46, 51.27) --
	(236.38, 51.27) --
	(236.38, 90.34) --
	(231.46, 90.34) --
	(226.53, 90.34) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (226.53, 69.37) --
	(231.46, 69.37) --
	(236.38, 69.37);

\path[draw=drawColor,line width= 0.6pt,line join=round] (244.59, 90.24) --
	(244.59,112.89);

\path[draw=drawColor,line width= 0.6pt,line join=round] (244.59, 51.60) --
	(244.59, 34.79) --
	(244.59,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (239.66, 90.24) --
	(239.66, 51.60) --
	(244.59, 51.60) --
	(249.51, 51.60) --
	(249.51, 90.24) --
	(244.59, 90.24) --
	(239.66, 90.24) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (239.66, 69.64) --
	(244.59, 69.64) --
	(249.51, 69.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (257.72, 90.95) --
	(257.72,113.87);

\path[draw=drawColor,line width= 0.6pt,line join=round] (257.72, 51.11) --
	(257.72, 33.95) --
	(257.72,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (252.80, 90.95) --
	(252.80, 51.11) --
	(257.72, 51.11) --
	(262.65, 51.11) --
	(262.65, 90.95) --
	(257.72, 90.95) --
	(252.80, 90.95) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (252.80, 69.69) --
	(257.72, 69.69) --
	(262.65, 69.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (270.85, 90.86) --
	(270.85,113.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (270.85, 50.95) --
	(270.85, 34.51) --
	(270.85,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (265.93, 90.86) --
	(265.93, 50.95) --
	(270.85, 50.95) --
	(275.78, 50.95) --
	(275.78, 90.86) --
	(270.85, 90.86) --
	(265.93, 90.86) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (265.93, 69.37) --
	(270.85, 69.37) --
	(275.78, 69.37);

\path[draw=drawColor,line width= 0.6pt,line join=round] (283.99, 91.13) --
	(283.99,114.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] (283.99, 50.62) --
	(283.99, 33.67) --
	(283.99,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (279.06, 91.13) --
	(279.06, 50.62) --
	(283.99, 50.62) --
	(288.91, 50.62) --
	(288.91, 91.13) --
	(283.99, 91.13) --
	(279.06, 91.13) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (279.06, 69.28) --
	(283.99, 69.28) --
	(288.91, 69.28);

\path[draw=drawColor,line width= 0.6pt,line join=round] (297.12, 91.84) --
	(297.12,114.91);

\path[draw=drawColor,line width= 0.6pt,line join=round] (297.12, 50.95) --
	(297.12, 33.95) --
	(297.12,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (292.20, 91.84) --
	(292.20, 50.95) --
	(297.12, 50.95) --
	(302.04, 50.95) --
	(302.04, 91.84) --
	(297.12, 91.84) --
	(292.20, 91.84) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (292.20, 69.46) --
	(297.12, 69.46) --
	(302.04, 69.46);

\path[draw=drawColor,line width= 0.6pt,line join=round] (310.25, 91.71) --
	(310.25,114.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (310.25, 50.62) --
	(310.25, 33.24) --
	(310.25,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (305.33, 91.71) --
	(305.33, 50.62) --
	(310.25, 50.62) --
	(315.18, 50.62) --
	(315.18, 91.71) --
	(310.25, 91.71) --
	(305.33, 91.71) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (305.33, 69.28) --
	(310.25, 69.28) --
	(315.18, 69.28);

\path[draw=drawColor,line width= 0.6pt,line join=round] (323.39, 92.36) --
	(323.39,115.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (323.39, 50.45) --
	(323.39, 33.24) --
	(323.39,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (318.46, 92.36) --
	(318.46, 50.45) --
	(323.39, 50.45) --
	(328.31, 50.45) --
	(328.31, 92.36) --
	(323.39, 92.36) --
	(318.46, 92.36) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (318.46, 69.28) --
	(323.39, 69.28) --
	(328.31, 69.28);

\path[draw=drawColor,line width= 0.6pt,line join=round] (336.52, 91.48) --
	(336.52,114.11);

\path[draw=drawColor,line width= 0.6pt,line join=round] (336.52, 50.78) --
	(336.52, 33.95) --
	(336.52,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (331.59, 91.48) --
	(331.59, 50.78) --
	(336.52, 50.78) --
	(341.44, 50.78) --
	(341.44, 91.48) --
	(336.52, 91.48) --
	(331.59, 91.48) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (331.59, 69.09) --
	(336.52, 69.09) --
	(341.44, 69.09);

\path[draw=drawColor,line width= 0.6pt,line join=round] (349.65, 92.41) --
	(349.65,115.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (349.65, 50.28) --
	(349.65, 33.38) --
	(349.65,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (344.73, 92.41) --
	(344.73, 50.28) --
	(349.65, 50.28) --
	(354.58, 50.28) --
	(354.58, 92.41) --
	(349.65, 92.41) --
	(344.73, 92.41) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (344.73, 68.54) --
	(349.65, 68.54) --
	(354.58, 68.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (362.78, 92.67) --
	(362.78,115.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (362.78, 50.12) --
	(362.78, 33.24) --
	(362.78,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (357.86, 92.67) --
	(357.86, 50.12) --
	(362.78, 50.12) --
	(367.71, 50.12) --
	(367.71, 92.67) --
	(362.78, 92.67) --
	(357.86, 92.67) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (357.86, 68.91) --
	(362.78, 68.91) --
	(367.71, 68.91);

\path[draw=drawColor,line width= 0.6pt,line join=round] (375.92, 93.23) --
	(375.92,116.80);

\path[draw=drawColor,line width= 0.6pt,line join=round] (375.92, 49.78) --
	(375.92, 33.67) --
	(375.92,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (370.99, 93.23) --
	(370.99, 78.50) --
	(370.99, 49.78) --
	(375.92, 49.78) --
	(380.84, 49.78) --
	(380.84, 78.50) --
	(380.84, 93.23) --
	(375.92, 93.23) --
	(370.99, 93.23) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (370.99, 68.54) --
	(375.92, 68.54) --
	(380.84, 68.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (389.05, 93.35) --
	(389.05,117.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] (389.05, 49.44) --
	(389.05, 32.36) --
	(389.05,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (384.12, 93.35) --
	(384.12, 78.54) --
	(384.12, 49.44) --
	(389.05, 49.44) --
	(393.97, 49.44) --
	(393.97, 78.54) --
	(393.97, 93.35) --
	(389.05, 93.35) --
	(384.12, 93.35) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (384.12, 68.35) --
	(389.05, 68.35) --
	(393.97, 68.35);

\path[draw=drawColor,line width= 0.6pt,line join=round] (402.18, 94.07) --
	(402.18,117.92);

\path[draw=drawColor,line width= 0.6pt,line join=round] (402.18, 49.09) --
	(402.18, 32.51) --
	(402.18,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (397.26, 94.07) --
	(397.26, 79.05) --
	(397.26, 49.09) --
	(402.18, 49.09) --
	(407.11, 49.09) --
	(407.11, 79.05) --
	(407.11, 94.07) --
	(402.18, 94.07) --
	(397.26, 94.07) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (397.26, 67.01) --
	(402.18, 67.01) --
	(407.11, 67.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (415.32, 95.91) --
	(415.32,120.16);

\path[draw=drawColor,line width= 0.6pt,line join=round] (415.32, 48.56) --
	(415.32, 31.76) --
	(415.32,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (410.39, 95.91) --
	(410.39, 80.45) --
	(410.39, 48.56) --
	(415.32, 48.56) --
	(420.24, 48.56) --
	(420.24, 80.45) --
	(420.24, 95.91) --
	(415.32, 95.91) --
	(410.39, 95.91) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (410.39, 65.50) --
	(415.32, 65.50) --
	(420.24, 65.50);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 47.60, 77.28) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 60.73, 87.17) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 73.86, 97.77) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 86.99,102.29) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (100.13,104.22) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.26,111.33) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.39,113.70) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.53,118.81) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.66,120.55) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.79,126.30) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (178.92,126.57) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (192.06,125.59) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (205.19,132.15) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (218.32,130.53) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (231.46,133.04) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (244.59,134.65) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (257.72,133.46) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (270.85,135.90) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (283.99,133.70) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (297.12,135.55) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (310.25,135.74) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (323.39,136.17) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (336.52,135.30) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (349.65,134.10) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (362.78,130.89) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (375.92,129.45) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (389.05,122.60) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (402.18,115.93) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (415.32,111.18) circle (  1.96);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,144.54);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96, 26.91) {10};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.62] at ( 26.76, 30.51) {2};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96, 99.01) {10};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.62] at ( 26.76,102.60) {3};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,144.54);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.04, 30.69) --
	( 34.79, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.04,102.78) --
	( 34.79,102.78);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,144.54);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 47.60, 27.94) --
	( 47.60, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 60.73, 27.94) --
	( 60.73, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.86, 27.94) --
	( 73.86, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 86.99, 27.94) --
	( 86.99, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (100.13, 27.94) --
	(100.13, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (113.26, 27.94) --
	(113.26, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (126.39, 27.94) --
	(126.39, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.53, 27.94) --
	(139.53, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (152.66, 27.94) --
	(152.66, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.79, 27.94) --
	(165.79, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (178.92, 27.94) --
	(178.92, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (192.06, 27.94) --
	(192.06, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (205.19, 27.94) --
	(205.19, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (218.32, 27.94) --
	(218.32, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.46, 27.94) --
	(231.46, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (244.59, 27.94) --
	(244.59, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (257.72, 27.94) --
	(257.72, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (270.85, 27.94) --
	(270.85, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (283.99, 27.94) --
	(283.99, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (297.12, 27.94) --
	(297.12, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (310.25, 27.94) --
	(310.25, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (323.39, 27.94) --
	(323.39, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (336.52, 27.94) --
	(336.52, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (349.65, 27.94) --
	(349.65, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (362.78, 27.94) --
	(362.78, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (375.92, 27.94) --
	(375.92, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (389.05, 27.94) --
	(389.05, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (402.18, 27.94) --
	(402.18, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (415.32, 27.94) --
	(415.32, 30.69);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,144.54);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 47.60, 19.68) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 60.73, 19.68) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 73.86, 19.68) {2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 86.99, 19.68) {3};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (100.13, 19.68) {4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (113.26, 19.68) {5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (126.39, 19.68) {6};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (139.53, 19.68) {7};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (152.66, 19.68) {8};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (165.79, 19.68) {9};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (178.92, 19.68) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (192.06, 19.68) {11};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (205.19, 19.68) {12};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (218.32, 19.68) {13};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (231.46, 19.68) {14};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (244.59, 19.68) {15};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (257.72, 19.68) {16};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (270.85, 19.68) {17};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (283.99, 19.68) {18};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (297.12, 19.68) {19};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (310.25, 19.68) {20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (323.39, 19.68) {21};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (336.52, 19.68) {22};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (349.65, 19.68) {23};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (362.78, 19.68) {24};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (375.92, 19.68) {25};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (389.05, 19.68) {26};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (402.18, 19.68) {27};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (415.32, 19.68) {28};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,144.54);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (231.46,  7.64) {Independent pairs};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,144.54);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08, 84.86) {Nodes};
\end{scope}
\end{tikzpicture}

### 2020-01-21 paper/impact.tex
Another plot

% Created by tikzDevice version 0.12.3 on 2020-01-21 14:48:17
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (234.88,176.16);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (234.88,176.16);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (234.88,176.16);
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] ( 25.78, 19.53) rectangle (231.38,172.66);
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 25.78, 51.08) --
	(231.38, 51.08);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 25.78,102.07) --
	(231.38,102.07);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 25.78,153.07) --
	(231.38,153.07);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 63.26, 19.53) --
	( 63.26,172.66);

\path[draw=drawColor,line width= 0.2pt,line join=round] (119.52, 19.53) --
	(119.52,172.66);

\path[draw=drawColor,line width= 0.2pt,line join=round] (175.79, 19.53) --
	(175.79,172.66);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 25.78, 25.58) --
	(231.38, 25.58);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 25.78, 76.58) --
	(231.38, 76.58);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 25.78,127.57) --
	(231.38,127.57);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.12, 19.53) --
	( 35.12,172.66);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 91.39, 19.53) --
	( 91.39,172.66);

\path[draw=drawColor,line width= 0.4pt,line join=round] (147.65, 19.53) --
	(147.65,172.66);

\path[draw=drawColor,line width= 0.4pt,line join=round] (203.92, 19.53) --
	(203.92,172.66);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 35.12, 26.49) --
	( 91.39, 27.97) --
	(147.65, 34.12) --
	(203.92, 77.20);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 35.12, 58.87) --
	( 91.39, 62.68) --
	(124.30, 68.55) --
	(147.65, 72.47);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 35.12, 60.44) --
	( 91.39, 64.58) --
	(147.65, 66.81) --
	(203.92, 70.73);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 35.12, 62.87) --
	( 91.39, 64.62) --
	(147.65, 67.25) --
	(203.92, 67.83);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 35.12, 58.10) --
	( 91.39, 59.23) --
	(147.65, 65.57) --
	(203.92, 79.66);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 35.12, 30.36) --
	( 91.39, 30.94) --
	(147.65, 35.55) --
	(203.92,165.70);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor,fill opacity=0.75] ( 32.63, 23.99) --
	( 37.62, 23.99) --
	( 37.62, 28.99) --
	( 32.63, 28.99) --
	cycle;

\path[fill=fillColor,fill opacity=0.75] ( 88.89, 25.47) --
	( 93.89, 25.47) --
	( 93.89, 30.46) --
	( 88.89, 30.46) --
	cycle;

\path[fill=fillColor,fill opacity=0.75] (145.16, 31.63) --
	(150.15, 31.63) --
	(150.15, 36.62) --
	(145.16, 36.62) --
	cycle;

\path[fill=fillColor,fill opacity=0.75] (201.42, 74.70) --
	(206.42, 74.70) --
	(206.42, 79.69) --
	(201.42, 79.69) --
	cycle;
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor,fill opacity=0.75] ( 35.12, 58.87) circle (  2.50);

\path[fill=fillColor,fill opacity=0.75] ( 91.39, 62.68) circle (  2.50);

\path[fill=fillColor,fill opacity=0.75] (124.30, 68.55) circle (  2.50);

\path[fill=fillColor,fill opacity=0.75] (147.65, 72.47) circle (  2.50);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor,fill opacity=0.75] ( 35.12, 64.32) --
	( 38.49, 58.50) --
	( 31.76, 58.50) --
	cycle;

\path[fill=fillColor,fill opacity=0.75] ( 91.39, 68.46) --
	( 94.75, 62.64) --
	( 88.03, 62.64) --
	cycle;

\path[fill=fillColor,fill opacity=0.75] (147.65, 70.70) --
	(151.02, 64.87) --
	(144.29, 64.87) --
	cycle;

\path[fill=fillColor,fill opacity=0.75] (203.92, 74.62) --
	(207.28, 68.79) --
	(200.56, 68.79) --
	cycle;
\definecolor{fillColor}{RGB}{231,41,138}

\path[fill=fillColor,fill opacity=0.75] ( 32.63, 62.87) --
	( 35.12, 65.37) --
	( 37.62, 62.87) --
	( 35.12, 60.37) --
	cycle;

\path[fill=fillColor,fill opacity=0.75] ( 88.89, 64.62) --
	( 91.39, 67.11) --
	( 93.89, 64.62) --
	( 91.39, 62.12) --
	cycle;

\path[fill=fillColor,fill opacity=0.75] (145.16, 67.25) --
	(147.65, 69.74) --
	(150.15, 67.25) --
	(147.65, 64.75) --
	cycle;

\path[fill=fillColor,fill opacity=0.75] (201.42, 67.83) --
	(203.92, 70.32) --
	(206.42, 67.83) --
	(203.92, 65.33) --
	cycle;
\definecolor{drawColor}{RGB}{102,166,30}
\definecolor{fillColor}{RGB}{102,166,30}

\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] ( 35.12, 58.10) circle (  2.50);

\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] ( 91.39, 59.23) circle (  2.50);

\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] (147.65, 65.57) circle (  2.50);

\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] (203.92, 79.66) circle (  2.50);
\definecolor{drawColor}{RGB}{230,171,2}
\definecolor{fillColor}{RGB}{230,171,2}

\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] ( 35.12, 30.36) circle (  1.67);

\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] ( 91.39, 30.94) circle (  1.67);

\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] (147.65, 35.55) circle (  1.67);

\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] (203.92,165.70) circle (  1.67);
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);

\path[] (216.56, 79.75) -- (203.92, 77.20);
\definecolor{drawColor}{RGB}{27,158,119}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (218.37, 74.87) --
	(228.37, 74.87) --
	(228.29, 74.88) --
	(228.58, 74.89) --
	(228.87, 74.94) --
	(229.14, 75.05) --
	(229.39, 75.19) --
	(229.62, 75.38) --
	(229.81, 75.60) --
	(229.97, 75.84) --
	(230.08, 76.11) --
	(230.15, 76.39) --
	(230.17, 76.68) --
	(230.17, 76.68) --
	(230.17, 83.01) --
	(230.17, 83.01) --
	(230.15, 83.30) --
	(230.08, 83.58) --
	(229.97, 83.85) --
	(229.81, 84.09) --
	(229.62, 84.31) --
	(229.39, 84.50) --
	(229.14, 84.64) --
	(228.87, 84.74) --
	(228.58, 84.80) --
	(228.37, 84.82) --
	(218.37, 84.82) --
	(218.59, 84.80) --
	(218.30, 84.81) --
	(218.01, 84.78) --
	(217.73, 84.70) --
	(217.47, 84.57) --
	(217.23, 84.41) --
	(217.02, 84.21) --
	(216.84, 83.97) --
	(216.71, 83.72) --
	(216.61, 83.44) --
	(216.57, 83.15) --
	(216.56, 83.01) --
	(216.56, 76.68) --
	(216.57, 76.83) --
	(216.57, 76.54) --
	(216.61, 76.25) --
	(216.71, 75.97) --
	(216.84, 75.71) --
	(217.02, 75.48) --
	(217.23, 75.28) --
	(217.47, 75.12) --
	(217.73, 74.99) --
	(218.01, 74.91) --
	(218.30, 74.88) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);
\definecolor{drawColor}{RGB}{27,158,119}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (223.37, 77.88) {$|\mathcal{P}|$};
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);

\path[] (217.03, 67.65) -- (203.92, 70.73);
\definecolor{drawColor}{RGB}{117,112,179}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (218.84, 62.52) --
	(228.37, 62.52) --
	(228.29, 62.52) --
	(228.58, 62.53) --
	(228.87, 62.59) --
	(229.14, 62.69) --
	(229.39, 62.84) --
	(229.62, 63.02) --
	(229.81, 63.24) --
	(229.97, 63.48) --
	(230.08, 63.75) --
	(230.15, 64.03) --
	(230.17, 64.32) --
	(230.17, 64.32) --
	(230.17, 70.65) --
	(230.17, 70.65) --
	(230.15, 70.94) --
	(230.08, 71.22) --
	(229.97, 71.49) --
	(229.81, 71.74) --
	(229.62, 71.95) --
	(229.39, 72.14) --
	(229.14, 72.28) --
	(228.87, 72.39) --
	(228.58, 72.44) --
	(228.37, 72.46) --
	(218.84, 72.46) --
	(219.06, 72.44) --
	(218.77, 72.46) --
	(218.48, 72.42) --
	(218.20, 72.34) --
	(217.94, 72.22) --
	(217.70, 72.05) --
	(217.49, 71.85) --
	(217.31, 71.62) --
	(217.18, 71.36) --
	(217.09, 71.08) --
	(217.04, 70.80) --
	(217.03, 70.65) --
	(217.03, 64.32) --
	(217.04, 64.47) --
	(217.04, 64.18) --
	(217.09, 63.89) --
	(217.18, 63.61) --
	(217.31, 63.36) --
	(217.49, 63.12) --
	(217.70, 62.92) --
	(217.94, 62.76) --
	(218.20, 62.63) --
	(218.48, 62.55) --
	(218.77, 62.52) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);
\definecolor{drawColor}{RGB}{117,112,179}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (223.60, 65.53) {$|\mathcal{V}|$};
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);

\path[] (217.66, 56.17) -- (203.92, 67.83);
\definecolor{drawColor}{RGB}{231,41,138}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (219.47, 50.14) --
	(228.37, 50.14) --
	(228.29, 50.14) --
	(228.58, 50.15) --
	(228.87, 50.21) --
	(229.14, 50.31) --
	(229.39, 50.46) --
	(229.62, 50.64) --
	(229.81, 50.86) --
	(229.97, 51.11) --
	(230.08, 51.37) --
	(230.15, 51.66) --
	(230.17, 51.95) --
	(230.17, 51.95) --
	(230.17, 58.27) --
	(230.17, 58.27) --
	(230.15, 58.56) --
	(230.08, 58.85) --
	(229.97, 59.11) --
	(229.81, 59.36) --
	(229.62, 59.58) --
	(229.39, 59.76) --
	(229.14, 59.91) --
	(228.87, 60.01) --
	(228.58, 60.07) --
	(228.37, 60.08) --
	(219.47, 60.08) --
	(219.68, 60.07) --
	(219.39, 60.08) --
	(219.11, 60.04) --
	(218.83, 59.96) --
	(218.56, 59.84) --
	(218.32, 59.67) --
	(218.11, 59.47) --
	(217.94, 59.24) --
	(217.80, 58.98) --
	(217.71, 58.71) --
	(217.67, 58.42) --
	(217.66, 58.27) --
	(217.66, 51.95) --
	(217.67, 52.09) --
	(217.67, 51.80) --
	(217.71, 51.51) --
	(217.80, 51.24) --
	(217.94, 50.98) --
	(218.11, 50.75) --
	(218.32, 50.55) --
	(218.56, 50.38) --
	(218.83, 50.26) --
	(219.11, 50.18) --
	(219.39, 50.14) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);
\definecolor{drawColor}{RGB}{231,41,138}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (223.92, 53.15) {$|\mathcal{C}|$};
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);

\path[] (206.06, 87.23) -- (203.92, 79.66);
\definecolor{drawColor}{RGB}{102,166,30}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (192.74, 87.23) --
	(219.48, 87.23) --
	(219.40, 87.23) --
	(219.70, 87.24) --
	(219.98, 87.30) --
	(220.25, 87.40) --
	(220.50, 87.54) --
	(220.73, 87.73) --
	(220.92, 87.95) --
	(221.08, 88.19) --
	(221.19, 88.46) --
	(221.26, 88.74) --
	(221.28, 89.03) --
	(221.28, 89.03) --
	(221.28, 95.36) --
	(221.28, 95.36) --
	(221.26, 95.65) --
	(221.19, 95.93) --
	(221.08, 96.20) --
	(220.92, 96.45) --
	(220.73, 96.66) --
	(220.50, 96.85) --
	(220.25, 96.99) --
	(219.98, 97.10) --
	(219.70, 97.15) --
	(219.48, 97.17) --
	(192.74, 97.17) --
	(192.95, 97.15) --
	(192.66, 97.17) --
	(192.37, 97.13) --
	(192.10, 97.05) --
	(191.83, 96.93) --
	(191.59, 96.76) --
	(191.38, 96.56) --
	(191.21, 96.33) --
	(191.07, 96.07) --
	(190.98, 95.79) --
	(190.94, 95.51) --
	(190.93, 95.36) --
	(190.93, 89.03) --
	(190.94, 89.18) --
	(190.94, 88.89) --
	(190.98, 88.60) --
	(191.07, 88.32) --
	(191.21, 88.07) --
	(191.38, 87.83) --
	(191.59, 87.63) --
	(191.83, 87.47) --
	(192.10, 87.34) --
	(192.37, 87.26) --
	(192.66, 87.23) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);
\definecolor{drawColor}{RGB}{102,166,30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (206.11, 90.24) {$\mathcal{M}_{\mathcal{C}}-|\mathcal{P}|$};
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);

\path[] (212.71,165.70) -- (203.92,165.70);
\definecolor{drawColor}{RGB}{230,171,2}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (214.51,160.73) --
	(228.37,160.73) --
	(228.29,160.73) --
	(228.58,160.74) --
	(228.87,160.80) --
	(229.14,160.90) --
	(229.39,161.05) --
	(229.62,161.23) --
	(229.81,161.45) --
	(229.97,161.69) --
	(230.08,161.96) --
	(230.15,162.24) --
	(230.17,162.53) --
	(230.17,162.53) --
	(230.17,168.86) --
	(230.17,168.86) --
	(230.15,169.15) --
	(230.08,169.43) --
	(229.97,169.70) --
	(229.81,169.95) --
	(229.62,170.16) --
	(229.39,170.35) --
	(229.14,170.49) --
	(228.87,170.60) --
	(228.58,170.66) --
	(228.37,170.67) --
	(214.51,170.67) --
	(214.73,170.66) --
	(214.44,170.67) --
	(214.15,170.63) --
	(213.87,170.55) --
	(213.61,170.43) --
	(213.37,170.26) --
	(213.16,170.06) --
	(212.99,169.83) --
	(212.85,169.57) --
	(212.76,169.29) --
	(212.71,169.01) --
	(212.71,168.86) --
	(212.71,162.53) --
	(212.71,162.68) --
	(212.71,162.39) --
	(212.76,162.10) --
	(212.85,161.82) --
	(212.99,161.57) --
	(213.16,161.34) --
	(213.37,161.13) --
	(213.61,160.97) --
	(213.87,160.84) --
	(214.15,160.76) --
	(214.44,160.73) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);
\definecolor{drawColor}{RGB}{230,171,2}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (221.44,163.74) {$\mathcal{M}_{\mathcal{N}}$};
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);
\definecolor{drawColor}{RGB}{217,95,2}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (141.06, 75.50) --
	(154.25, 75.50) --
	(154.17, 75.51) --
	(154.46, 75.52) --
	(154.75, 75.58) --
	(155.02, 75.68) --
	(155.27, 75.82) --
	(155.50, 76.01) --
	(155.69, 76.23) --
	(155.85, 76.47) --
	(155.96, 76.74) --
	(156.03, 77.02) --
	(156.05, 77.31) --
	(156.05, 77.31) --
	(156.05, 83.64) --
	(156.05, 83.64) --
	(156.03, 83.93) --
	(155.96, 84.21) --
	(155.85, 84.48) --
	(155.69, 84.73) --
	(155.50, 84.94) --
	(155.27, 85.13) --
	(155.02, 85.27) --
	(154.75, 85.38) --
	(154.46, 85.43) --
	(154.25, 85.45) --
	(141.06, 85.45) --
	(141.28, 85.43) --
	(140.99, 85.44) --
	(140.70, 85.41) --
	(140.42, 85.33) --
	(140.16, 85.20) --
	(139.92, 85.04) --
	(139.71, 84.84) --
	(139.54, 84.61) --
	(139.40, 84.35) --
	(139.31, 84.07) --
	(139.26, 83.79) --
	(139.26, 83.64) --
	(139.26, 77.31) --
	(139.26, 77.46) --
	(139.26, 77.17) --
	(139.31, 76.88) --
	(139.40, 76.60) --
	(139.54, 76.35) --
	(139.71, 76.11) --
	(139.92, 75.91) --
	(140.16, 75.75) --
	(140.42, 75.62) --
	(140.70, 75.54) --
	(140.99, 75.51) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);
\definecolor{drawColor}{RGB}{217,95,2}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (147.65, 78.52) {$\mathcal{M}_{\mathcal{A}}$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (234.88,176.16);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.56] at ( 22.63, 23.65) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.56] at ( 22.63, 74.65) {2000};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.56] at ( 22.63,125.64) {4000};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (234.88,176.16);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 24.03, 25.58) --
	( 25.78, 25.58);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 24.03, 76.58) --
	( 25.78, 76.58);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 24.03,127.57) --
	( 25.78,127.57);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (234.88,176.16);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.12, 17.78) --
	( 35.12, 19.53);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 91.39, 17.78) --
	( 91.39, 19.53);

\path[draw=drawColor,line width= 0.4pt,line join=round] (147.65, 17.78) --
	(147.65, 19.53);

\path[draw=drawColor,line width= 0.4pt,line join=round] (203.92, 17.78) --
	(203.92, 19.53);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (234.88,176.16);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at ( 35.12, 12.52) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at ( 91.39, 12.52) {2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at (147.65, 12.52) {4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at (203.92, 12.52) {8};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (234.88,176.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (128.58,  4.86) {Value of each parameter};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (234.88,176.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (  8.32, 96.09) {Mean number of nodes};
\end{scope}
\end{tikzpicture}

### 2020-01-21 paper/paper.tex
Another plot

@@
 
+\Crefname{constraint}{Constraint}{Constraints}
+\Crefname{clause}{Clause}{Clauses}
+\creflabelformat{clause}{#2(#1)#3}
+
 \usetikzlibrary{arrows.meta}
-\Crefname{constraint}{Constraint}{Constraints}
 \relpenalty=10000
@@
 % \end{table}
+
+% UAI format: section/subsection titles are in all caps, figure/table titles are
+% in TitleCase, table caption above the table
 
@@
   \end{tikzpicture}
-  \caption{A tree representation of the formula from \cref{example:formula}}
+  \caption{A Tree Representation of the Formula From \cref{example:formula}}
   \label{fig:example_tree}
@@
   \end{tikzpicture}
-  \caption{The tree representation of the body of Clause~\eqref{eq:example_clause}.}
+  \caption{A Tree Representation of the Body of \cref{eq:example_clause}}
   \label{fig:example_tree2}
@@
   \end{tikzpicture}
-  \caption{The predicate dependency graph of the program in \cref{ex:program}.
-    Positive edges are labeled with `$+$', and negative edges with `$-$'.}
+  \caption{The Predicate Dependency Graph of the Program In \cref{ex:program}.
+    Positive Edges Are Labelled with `$+$', and Negative Edges with `$-$'.}
   \label{fig:predicate_dependencies}
@@
     \mathsf{sibling}(X, Y) &\gets \mathsf{parent}(X, Z) \land \mathsf{parent}(Y, Z), \nonumber \\
-    \mathsf{father}(X, Y) &\gets \mathsf{parent}(X, Y) \land \neg\mathsf{mother}(X, Y). \label{eq:example_clause}
+    \mathsf{father}(X, Y) &\gets \mathsf{parent}(X, Y) \land \neg\mathsf{mother}(X, Y). \label[clause]{eq:example_clause}
   \end{align}
@@
   }
-  \caption{Propagation for independence}
+  \caption{Propagation for Independence}
   \label{alg:independence_propagation}
@@
   \Return{\textsc{undefined}}\;
-  \caption{Entailment for independence}
+  \caption{Entailment for Independence}
   \label{alg:independence_entailment}
@@
   }
-  \caption{Dependencies of a predicate}
+  \caption{Dependencies of a Predicate}
   \label{alg:dependencies}
@@
   \]
-  \caption{The adjacency matrix defined using \cref{def:adjacency_matrix} for
+  \caption{The Adjacency Matrix Defined Using \cref{def:adjacency_matrix} For
     \cref{example:independence}}
@@
 \end{figure}
-\begin{figure}
+\begin{figure}[t]
   \centering
@@
   \end{tikzpicture}
-  \caption{The predicate dependency graph that corresponds to
-    \cref{fig:dependencies_matrix}. Dashed edges are undetermined---they may
-    or may not exist.}
+  \caption{The Predicate Dependency Graph That Corresponds To
+    \cref{fig:dependencies_matrix}. Dashed Edges Are Undetermined---They May
+    Or May Not Exist.}
   \label{fig:dependencies2}
@@
   \Return{\textsc{undefined}}\;
-  \caption{Entailment check for negative cycles}
+  \caption{Entailment Check for Negative Cycles}
   \label{alg:negative_cycles}
@@
 % see Downloads/cp2019-wiggles.pdf for an example.
-
-\begin{figure*}[t]
-  \centering
-  \input{phase_transition.tex}
-  \caption{TODO}
-\end{figure*}
 
@@
 \item $|\predicates{}|$, $|\variables{}|$, $|\constants{}|$, $\maxNumNodes{}$,
-  the number of additional clauses are in $\{ 1, 2, 4, 8 \}$.
+  $\maxNumClauses{} - |\predicates{}|$ are in $\{ 1, 2, 4, 8 \}$.
 \item $\maxArity{} \in \{ 1, 2, 3, 4 \}$.
@@
 \begin{itemize}
-\item almost \num{400000} experiments.
+\item almost \num{400000} experiments, almost \num{300000} of which are with
+  $|\predicates{}| = 8$ (since the maximum number of independent pairs grows
+  with $|\predicates{}|$).
 \item \SI{97.7}{\percent} of total running times is less than \SI{1}{\second}
@@
   \end{itemize}
+\end{itemize}
+
+% TODO: describe the phase transition in this figure. still, almost 300k
+% data points. A phase transition in mean but not
+% median, i.e., some instances become really hard, but most remain easy.
+\begin{figure*}[t]
+  \centering
+  \input{phase_transition.tex}
+  \caption{The Distribution of the Number of Nodes in the Binary Search Tree as
+    a Function of the Number of Independent Pairs of Predicates for
+    $|\predicates| = 8$. Significant Outliers Are Hidden, The Dots Denote Mean
+    Values, and the Vertical Axis Is on a $\log_{10}$ Scale.}
+\end{figure*}
+
+\begin{figure}[t]
+  \centering
+  \input{impact.tex}
+  \caption{The Mean Number of Nodes in the Binary Search Tree for Each Value of
+    Each Experimental Parameter. Note That the Horizontal Axis Is on a $\log_2$
+    Scale.}
+  \label{fig:impact}
+\end{figure}
+
+Observations about \cref{fig:impact}:
+\begin{itemize}
+\item The same plot for the median is very similar.
+\item The growth of each curve suggest how well/poorly the model scales with
+  higher values of the parameter.
+\item It is clear that the number of nodes that can represent a body of a clause
+  is the limiting factor. A big tree significantly increases the search space,
+  and it becomes harder to ensure that there are no negative cycle and 
 \end{itemize}

### 2020-01-21 paper/phase_transition.tex
Another plot

@@
-% Created by tikzDevice version 0.12.3 on 2020-01-20 17:11:57
+% Created by tikzDevice version 0.12.3 on 2020-01-21 13:23:35
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (433.62,144.54);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( -0.00,  0.00) rectangle (433.62,144.54);
 \end{scope}
 \begin{scope}
-\path[clip] ( 34.79, 30.69) rectangle (428.12,139.04);
+\path[clip] ( 22.14, 19.53) rectangle (430.12,141.04);
 \definecolor{fillColor}{gray}{0.92}
 
-\path[fill=fillColor] ( 34.79, 30.69) rectangle (428.12,139.04);
+\path[fill=fillColor] ( 22.14, 19.53) rectangle (430.12,141.04);
 \definecolor{drawColor}{RGB}{255,255,255}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.79, 84.06) --
-	(428.12, 84.06);
+\path[draw=drawColor,line width= 0.2pt,line join=round] ( 22.14, 79.39) --
+	(430.12, 79.39);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.79,114.41) --
-	(428.12,114.41);
+\path[draw=drawColor,line width= 0.2pt,line join=round] ( 22.14,113.42) --
+	(430.12,113.42);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.79,122.88) --
-	(428.12,122.88);
+\path[draw=drawColor,line width= 0.2pt,line join=round] ( 22.14,122.92) --
+	(430.12,122.92);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.79, 30.69) --
-	(428.12, 30.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 22.14, 19.53) --
+	(430.12, 19.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.79,102.78) --
-	(428.12,102.78);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 22.14,100.38) --
+	(430.12,100.38);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 47.60, 30.69) --
-	( 47.60,139.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.42, 19.53) --
+	( 35.42,141.04);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 60.73, 30.69) --
-	( 60.73,139.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 49.04, 19.53) --
+	( 49.04,141.04);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.86, 30.69) --
-	( 73.86,139.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 62.67, 19.53) --
+	( 62.67,141.04);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 86.99, 30.69) --
-	( 86.99,139.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 76.29, 19.53) --
+	( 76.29,141.04);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (100.13, 30.69) --
-	(100.13,139.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 89.91, 19.53) --
+	( 89.91,141.04);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (113.26, 30.69) --
-	(113.26,139.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (103.53, 19.53) --
+	(103.53,141.04);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (126.39, 30.69) --
-	(126.39,139.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (117.15, 19.53) --
+	(117.15,141.04);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (139.53, 30.69) --
-	(139.53,139.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (130.78, 19.53) --
+	(130.78,141.04);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (152.66, 30.69) --
-	(152.66,139.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (144.40, 19.53) --
+	(144.40,141.04);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.79, 30.69) --
-	(165.79,139.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (158.02, 19.53) --
+	(158.02,141.04);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (178.92, 30.69) --
-	(178.92,139.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (171.64, 19.53) --
+	(171.64,141.04);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (192.06, 30.69) --
-	(192.06,139.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (185.26, 19.53) --
+	(185.26,141.04);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (205.19, 30.69) --
-	(205.19,139.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (198.89, 19.53) --
+	(198.89,141.04);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (218.32, 30.69) --
-	(218.32,139.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (212.51, 19.53) --
+	(212.51,141.04);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (231.46, 30.69) --
-	(231.46,139.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (226.13, 19.53) --
+	(226.13,141.04);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (244.59, 30.69) --
-	(244.59,139.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (239.75, 19.53) --
+	(239.75,141.04);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (257.72, 30.69) --
-	(257.72,139.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (253.37, 19.53) --
+	(253.37,141.04);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (270.85, 30.69) --
-	(270.85,139.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (267.00, 19.53) --
+	(267.00,141.04);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (283.99, 30.69) --
-	(283.99,139.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (280.62, 19.53) --
+	(280.62,141.04);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (297.12, 30.69) --
-	(297.12,139.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (294.24, 19.53) --
+	(294.24,141.04);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (310.25, 30.69) --
-	(310.25,139.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (307.86, 19.53) --
+	(307.86,141.04);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (323.39, 30.69) --
-	(323.39,139.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (321.48, 19.53) --
+	(321.48,141.04);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (336.52, 30.69) --
-	(336.52,139.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (335.11, 19.53) --
+	(335.11,141.04);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (349.65, 30.69) --
-	(349.65,139.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (348.73, 19.53) --
+	(348.73,141.04);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (362.78, 30.69) --
-	(362.78,139.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (362.35, 19.53) --
+	(362.35,141.04);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (375.92, 30.69) --
-	(375.92,139.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (375.97, 19.53) --
+	(375.97,141.04);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (389.05, 30.69) --
-	(389.05,139.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (389.59, 19.53) --
+	(389.59,141.04);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (402.18, 30.69) --
-	(402.18,139.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (403.22, 19.53) --
+	(403.22,141.04);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (415.32, 30.69) --
-	(415.32,139.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (416.84, 19.53) --
+	(416.84,141.04);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 47.60, 82.72) --
-	( 47.60,103.19);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.42, 77.89) --
+	( 35.42,100.83);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 47.60, 52.70) --
-	( 47.60, 41.88) --
-	( 47.60, 25.23) --
-	( 47.60,  0.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.42, 44.22) --
+	( 35.42, 32.09) --
+	( 35.42, 13.41) --
+	( 35.42,  0.00);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 42.67, 82.72) --
-	( 42.67, 52.70) --
-	( 47.60, 52.70) --
-	( 52.52, 52.70) --
-	( 52.52, 82.72) --
-	( 47.60, 82.72) --
-	( 42.67, 82.72) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 30.31, 77.89) --
+	( 30.31, 44.22) --
+	( 35.42, 44.22) --
+	( 40.53, 44.22) --
+	( 40.53, 77.89) --
+	( 35.42, 77.89) --
+	( 30.31, 77.89) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 42.67, 67.97) --
-	( 47.60, 67.97) --
-	( 52.52, 67.97);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 30.31, 61.34) --
+	( 35.42, 61.34) --
+	( 40.53, 61.34);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 60.73, 85.45) --
-	( 60.73,106.72);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 49.04, 80.95) --
+	( 49.04,104.79);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 60.73, 52.70) --
-	( 60.73, 36.00) --
-	( 60.73,  0.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 49.04, 44.22) --
+	( 49.04, 25.49) --
+	( 49.04,  0.00);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 55.80, 85.45) --
-	( 55.80, 52.70) --
-	( 60.73, 52.70) --
-	( 65.65, 52.70) --
-	( 65.65, 85.45) --
-	( 60.73, 85.45) --
-	( 55.80, 85.45) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 43.94, 80.95) --
+	( 43.94, 44.22) --
+	( 49.04, 44.22) --
+	( 54.15, 44.22) --
+	( 54.15, 80.95) --
+	( 49.04, 80.95) --
+	( 43.94, 80.95) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 55.80, 68.54) --
-	( 60.73, 68.54) --
-	( 65.65, 68.54);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 43.94, 61.98) --
+	( 49.04, 61.98) --
+	( 54.15, 61.98);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.86, 85.83) --
-	( 73.86,107.32);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.67, 81.37) --
+	( 62.67,105.47);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.86, 51.92) --
-	( 73.86, 34.23) --
-	( 73.86,  0.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.67, 43.33) --
+	( 62.67, 23.51) --
+	( 62.67,  0.00);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 68.94, 85.83) --
-	( 68.94, 51.92) --
-	( 73.86, 51.92) --
-	( 78.79, 51.92) --
-	( 78.79, 85.83) --
-	( 73.86, 85.83) --
-	( 68.94, 85.83) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 57.56, 81.37) --
+	( 57.56, 43.33) --
+	( 62.67, 43.33) --
+	( 67.77, 43.33) --
+	( 67.77, 81.37) --
+	( 62.67, 81.37) --
+	( 57.56, 81.37) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 68.94, 68.82) --
-	( 73.86, 68.82) --
-	( 78.79, 68.82);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 57.56, 62.29) --
+	( 62.67, 62.29) --
+	( 67.77, 62.29);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 86.99, 86.94) --
-	( 86.99,108.75);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 76.29, 82.62) --
+	( 76.29,107.07);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 86.99, 52.07) --
-	( 86.99, 34.79) --
-	( 86.99,  0.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 76.29, 43.51) --
+	( 76.29, 24.13) --
+	( 76.29,  0.00);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 82.07, 86.94) --
-	( 82.07, 52.07) --
-	( 86.99, 52.07) --
-	( 91.92, 52.07) --
-	( 91.92, 86.94) --
-	( 86.99, 86.94) --
-	( 82.07, 86.94) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 71.18, 82.62) --
+	( 71.18, 43.51) --
+	( 76.29, 43.51) --
+	( 81.40, 43.51) --
+	( 81.40, 82.62) --
+	( 76.29, 82.62) --
+	( 71.18, 82.62) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 82.07, 68.82) --
-	( 86.99, 68.82) --
-	( 91.92, 68.82);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 71.18, 62.29) --
+	( 76.29, 62.29) --
+	( 81.40, 62.29);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (100.13, 87.86) --
-	(100.13,109.89);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.91, 83.65) --
+	( 89.91,108.35);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (100.13, 52.07) --
-	(100.13, 34.79) --
-	(100.13,  0.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.91, 43.51) --
+	( 89.91, 24.13) --
+	( 89.91,  0.00);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 95.20, 87.86) --
-	( 95.20, 52.07) --
-	(100.13, 52.07) --
-	(105.05, 52.07) --
-	(105.05, 87.86) --
-	(100.13, 87.86) --
-	( 95.20, 87.86) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 84.80, 83.65) --
+	( 84.80, 43.51) --
+	( 89.91, 43.51) --
+	( 95.02, 43.51) --
+	( 95.02, 83.65) --
+	( 89.91, 83.65) --
+	( 84.80, 83.65) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 95.20, 69.46) --
-	(100.13, 69.46) --
-	(105.05, 69.46);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 84.80, 63.01) --
+	( 89.91, 63.01) --
+	( 95.02, 63.01);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (113.26, 88.21) --
-	(113.26,110.29);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (103.53, 84.04) --
+	(103.53,108.80);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (113.26, 52.23) --
-	(113.26, 34.65) --
-	(113.26,  0.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (103.53, 43.69) --
+	(103.53, 23.97) --
+	(103.53,  0.00);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (108.34, 88.21) --
-	(108.34, 52.23) --
-	(113.26, 52.23) --
-	(118.18, 52.23) --
-	(118.18, 88.21) --
-	(113.26, 88.21) --
-	(108.34, 88.21) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 98.42, 84.04) --
+	( 98.42, 43.69) --
+	(103.53, 43.69) --
+	(108.64, 43.69) --
+	(108.64, 84.04) --
+	(103.53, 84.04) --
+	( 98.42, 84.04) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (108.34, 69.19) --
-	(113.26, 69.19) --
-	(118.18, 69.19);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 98.42, 62.70) --
+	(103.53, 62.70) --
+	(108.64, 62.70);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (126.39, 87.91) --
-	(126.39,110.12);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.15, 83.71) --
+	(117.15,108.60);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (126.39, 51.43) --
-	(126.39, 34.23) --
-	(126.39,  0.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.15, 42.80) --
+	(117.15, 23.51) --
+	(117.15,  0.00);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (121.47, 87.91) --
-	(121.47, 51.43) --
-	(126.39, 51.43) --
-	(131.32, 51.43) --
-	(131.32, 87.91) --
-	(126.39, 87.91) --
-	(121.47, 87.91) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (112.05, 83.71) --
+	(112.05, 42.80) --
+	(117.15, 42.80) --
+	(122.26, 42.80) --
+	(122.26, 83.71) --
+	(117.15, 83.71) --
+	(112.05, 83.71) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (121.47, 68.82) --
-	(126.39, 68.82) --
-	(131.32, 68.82);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (112.05, 62.29) --
+	(117.15, 62.29) --
+	(122.26, 62.29);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (139.53, 89.24) --
-	(139.53,111.73);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (130.78, 85.20) --
+	(130.78,110.42);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (139.53, 51.43) --
-	(139.53, 34.51) --
-	(139.53,  0.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (130.78, 42.80) --
+	(130.78, 23.82) --
+	(130.78,  0.00);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (134.60, 89.24) --
-	(134.60, 51.43) --
-	(139.53, 51.43) --
-	(144.45, 51.43) --
-	(144.45, 89.24) --
-	(139.53, 89.24) --
-	(134.60, 89.24) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (125.67, 85.20) --
+	(125.67, 42.80) --
+	(130.78, 42.80) --
+	(135.88, 42.80) --
+	(135.88, 85.20) --
+	(130.78, 85.20) --
+	(125.67, 85.20) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (134.60, 69.28) --
-	(139.53, 69.28) --
-	(144.45, 69.28);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (125.67, 62.81) --
+	(130.78, 62.81) --
+	(135.88, 62.81);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (152.66, 88.81) --
-	(152.66,111.09);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (144.40, 84.71) --
+	(144.40,109.70);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (152.66, 51.92) --
-	(152.66, 35.33) --
-	(152.66,  0.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (144.40, 43.33) --
+	(144.40, 24.74) --
+	(144.40,  0.00);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (147.73, 88.81) --
-	(147.73, 51.92) --
-	(152.66, 51.92) --
-	(157.58, 51.92) --
-	(157.58, 88.81) --
-	(152.66, 88.81) --
-	(147.73, 88.81) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (139.29, 84.71) --
+	(139.29, 43.33) --
+	(144.40, 43.33) --
+	(149.51, 43.33) --
+	(149.51, 84.71) --
+	(144.40, 84.71) --
+	(139.29, 84.71) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (147.73, 69.37) --
-	(152.66, 69.37) --
-	(157.58, 69.37);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (139.29, 62.91) --
+	(144.40, 62.91) --
+	(149.51, 62.91);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.79, 89.53) --
-	(165.79,112.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (158.02, 85.52) --
+	(158.02,110.81);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.79, 51.43) --
-	(165.79, 34.09) --
-	(165.79,  0.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (158.02, 42.80) --
+	(158.02, 23.35) --
+	(158.02,  0.00);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (160.87, 89.53) --
-	(160.87, 51.43) --
-	(165.79, 51.43) --
-	(170.72, 51.43) --
-	(170.72, 89.53) --
-	(165.79, 89.53) --
-	(160.87, 89.53) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (152.91, 85.52) --
+	(152.91, 42.80) --
+	(158.02, 42.80) --
+	(163.13, 42.80) --
+	(163.13, 85.52) --
+	(158.02, 85.52) --
+	(152.91, 85.52) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (160.87, 69.19) --
-	(165.79, 69.19) --
-	(170.72, 69.19);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (152.91, 62.70) --
+	(158.02, 62.70) --
+	(163.13, 62.70);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (178.92, 89.53) --
-	(178.92,111.94);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (171.64, 85.52) --
+	(171.64,110.65);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (178.92, 51.60) --
-	(178.92, 40.77) --
-	(178.92, 24.09) --
-	(178.92,  0.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (171.64, 42.98) --
+	(171.64, 30.84) --
+	(171.64, 12.13) --
+	(171.64,  0.00);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (174.00, 89.53) --
-	(174.00, 51.60) --
-	(178.92, 51.60) --
-	(183.85, 51.60) --
-	(183.85, 89.53) --
-	(178.92, 89.53) --
-	(174.00, 89.53) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (166.53, 85.52) --
+	(166.53, 42.98) --
+	(171.64, 42.98) --
+	(176.75, 42.98) --
+	(176.75, 85.52) --
+	(171.64, 85.52) --
+	(166.53, 85.52) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (174.00, 69.64) --
-	(178.92, 69.64) --
-	(183.85, 69.64);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (166.53, 63.21) --
+	(171.64, 63.21) --
+	(176.75, 63.21);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (192.06, 89.63) --
-	(192.06,112.20);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (185.26, 85.63) --
+	(185.26,110.94);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (192.06, 51.43) --
-	(192.06, 34.51) --
-	(192.06,  0.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (185.26, 42.80) --
+	(185.26, 23.82) --
+	(185.26,  0.00);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (187.13, 89.63) --
-	(187.13, 51.43) --
-	(192.06, 51.43) --
-	(196.98, 51.43) --
-	(196.98, 89.63) --
-	(192.06, 89.63) --
-	(187.13, 89.63) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (180.16, 85.63) --
+	(180.16, 42.80) --
+	(185.26, 42.80) --
+	(190.37, 42.80) --
+	(190.37, 85.63) --
+	(185.26, 85.63) --
+	(180.16, 85.63) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (187.13, 69.64) --
-	(192.06, 69.64) --
-	(196.98, 69.64);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (180.16, 63.21) --
+	(185.26, 63.21) --
+	(190.37, 63.21);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (205.19, 90.11) --
-	(205.19,112.82);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (198.89, 86.17) --
+	(198.89,111.64);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (205.19, 51.27) --
-	(205.19, 33.95) --
-	(205.19,  0.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (198.89, 42.61) --
+	(198.89, 23.19) --
+	(198.89,  0.00);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (200.27, 90.11) --
-	(200.27, 51.27) --
-	(205.19, 51.27) --
-	(210.11, 51.27) --
-	(210.11, 90.11) --
-	(205.19, 90.11) --
-	(200.27, 90.11) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (193.78, 86.17) --
+	(193.78, 42.61) --
+	(198.89, 42.61) --
+	(203.99, 42.61) --
+	(203.99, 86.17) --
+	(198.89, 86.17) --
+	(193.78, 86.17) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (200.27, 69.37) --
-	(205.19, 69.37) --
-	(210.11, 69.37);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (193.78, 62.91) --
+	(198.89, 62.91) --
+	(203.99, 62.91);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (218.32, 90.05) --
-	(218.32,112.77);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (212.51, 86.11) --
+	(212.51,111.59);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (218.32, 51.11) --
-	(218.32, 34.09) --
-	(218.32,  0.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (212.51, 42.43) --
+	(212.51, 23.35) --
+	(212.51,  0.00);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (213.40, 90.05) --
-	(213.40, 51.11) --
-	(218.32, 51.11) --
-	(223.25, 51.11) --
-	(223.25, 90.05) --
-	(218.32, 90.05) --
-	(213.40, 90.05) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (207.40, 86.11) --
+	(207.40, 42.43) --
+	(212.51, 42.43) --
+	(217.62, 42.43) --
+	(217.62, 86.11) --
+	(212.51, 86.11) --
+	(207.40, 86.11) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (213.40, 69.00) --
-	(218.32, 69.00) --
-	(223.25, 69.00);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (207.40, 62.50) --
+	(212.51, 62.50) --
+	(217.62, 62.50);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (231.46, 90.34) --
-	(231.46,112.98);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (226.13, 86.42) --
+	(226.13,111.81);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (231.46, 51.27) --
-	(231.46, 34.51) --
-	(231.46,  0.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (226.13, 42.61) --
+	(226.13, 23.82) --
+	(226.13,  0.00);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (226.53, 90.34) --
-	(226.53, 51.27) --
-	(231.46, 51.27) --
-	(236.38, 51.27) --
-	(236.38, 90.34) --
-	(231.46, 90.34) --
-	(226.53, 90.34) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (221.02, 86.42) --
+	(221.02, 42.61) --
+	(226.13, 42.61) --
+	(231.24, 42.61) --
+	(231.24, 86.42) --
+	(226.13, 86.42) --
+	(221.02, 86.42) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (226.53, 69.37) --
-	(231.46, 69.37) --
-	(236.38, 69.37);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (221.02, 62.91) --
+	(226.13, 62.91) --
+	(231.24, 62.91);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (244.59, 90.24) --
-	(244.59,112.89);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (239.75, 86.32) --
+	(239.75,111.71);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (244.59, 51.60) --
-	(244.59, 34.79) --
-	(244.59,  0.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (239.75, 42.98) --
+	(239.75, 24.13) --
+	(239.75,  0.00);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (239.66, 90.24) --
-	(239.66, 51.60) --
-	(244.59, 51.60) --
-	(249.51, 51.60) --
-	(249.51, 90.24) --
-	(244.59, 90.24) --
-	(239.66, 90.24) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (234.64, 86.32) --
+	(234.64, 42.98) --
+	(239.75, 42.98) --
+	(244.86, 42.98) --
+	(244.86, 86.32) --
+	(239.75, 86.32) --
+	(234.64, 86.32) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (239.66, 69.64) --
-	(244.59, 69.64) --
-	(249.51, 69.64);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (234.64, 63.21) --
+	(239.75, 63.21) --
+	(244.86, 63.21);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (257.72, 90.95) --
-	(257.72,113.87);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (253.37, 87.11) --
+	(253.37,112.81);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (257.72, 51.11) --
-	(257.72, 33.95) --
-	(257.72,  0.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (253.37, 42.43) --
+	(253.37, 23.19) --
+	(253.37,  0.00);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (252.80, 90.95) --
-	(252.80, 51.11) --
-	(257.72, 51.11) --
-	(262.65, 51.11) --
-	(262.65, 90.95) --
-	(257.72, 90.95) --
-	(252.80, 90.95) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (248.27, 87.11) --
+	(248.27, 42.43) --
+	(253.37, 42.43) --
+	(258.48, 42.43) --
+	(258.48, 87.11) --
+	(253.37, 87.11) --
+	(248.27, 87.11) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (252.80, 69.69) --
-	(257.72, 69.69) --
-	(262.65, 69.69);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (248.27, 63.26) --
+	(253.37, 63.26) --
+	(258.48, 63.26);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (270.85, 90.86) --
-	(270.85,113.74);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (267.00, 87.00) --
+	(267.00,112.67);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (270.85, 50.95) --
-	(270.85, 34.51) --
-	(270.85,  0.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (267.00, 42.25) --
+	(267.00, 23.82) --
+	(267.00,  0.00);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (265.93, 90.86) --
-	(265.93, 50.95) --
-	(270.85, 50.95) --
-	(275.78, 50.95) --
-	(275.78, 90.86) --
-	(270.85, 90.86) --
-	(265.93, 90.86) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (261.89, 87.00) --
+	(261.89, 42.25) --
+	(267.00, 42.25) --
+	(272.10, 42.25) --
+	(272.10, 87.00) --
+	(267.00, 87.00) --
+	(261.89, 87.00) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (265.93, 69.37) --
-	(270.85, 69.37) --
-	(275.78, 69.37);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (261.89, 62.91) --
+	(267.00, 62.91) --
+	(272.10, 62.91);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (283.99, 91.13) --
-	(283.99,114.18);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (280.62, 87.31) --
+	(280.62,113.16);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (283.99, 50.62) --
-	(283.99, 33.67) --
-	(283.99,  0.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (280.62, 41.88) --
+	(280.62, 22.87) --
+	(280.62,  0.00);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (279.06, 91.13) --
-	(279.06, 50.62) --
-	(283.99, 50.62) --
-	(288.91, 50.62) --
-	(288.91, 91.13) --
-	(283.99, 91.13) --
-	(279.06, 91.13) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (275.51, 87.31) --
+	(275.51, 41.88) --
+	(280.62, 41.88) --
+	(285.73, 41.88) --
+	(285.73, 87.31) --
+	(280.62, 87.31) --
+	(275.51, 87.31) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (279.06, 69.28) --
-	(283.99, 69.28) --
-	(288.91, 69.28);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (275.51, 62.81) --
+	(280.62, 62.81) --
+	(285.73, 62.81);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (297.12, 91.84) --
-	(297.12,114.91);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (294.24, 88.10) --
+	(294.24,113.98);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (297.12, 50.95) --
-	(297.12, 33.95) --
-	(297.12,  0.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (294.24, 42.25) --
+	(294.24, 23.19) --
+	(294.24,  0.00);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (292.20, 91.84) --
-	(292.20, 50.95) --
-	(297.12, 50.95) --
-	(302.04, 50.95) --
-	(302.04, 91.84) --
-	(297.12, 91.84) --
-	(292.20, 91.84) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (289.13, 88.10) --
+	(289.13, 42.25) --
+	(294.24, 42.25) --
+	(299.35, 42.25) --
+	(299.35, 88.10) --
+	(294.24, 88.10) --
+	(289.13, 88.10) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (292.20, 69.46) --
-	(297.12, 69.46) --
-	(302.04, 69.46);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (289.13, 63.01) --
+	(294.24, 63.01) --
+	(299.35, 63.01);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (310.25, 91.71) --
-	(310.25,114.84);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (307.86, 87.97) --
+	(307.86,113.91);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (310.25, 50.62) --
-	(310.25, 33.24) --
-	(310.25,  0.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (307.86, 41.88) --
+	(307.86, 22.39) --
+	(307.86,  0.00);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (305.33, 91.71) --
-	(305.33, 50.62) --
-	(310.25, 50.62) --
-	(315.18, 50.62) --
-	(315.18, 91.71) --
-	(310.25, 91.71) --
-	(305.33, 91.71) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (302.75, 87.97) --
+	(302.75, 41.88) --
+	(307.86, 41.88) --
+	(312.97, 41.88) --
+	(312.97, 87.97) --
+	(307.86, 87.97) --
+	(302.75, 87.97) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (305.33, 69.28) --
-	(310.25, 69.28) --
-	(315.18, 69.28);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (302.75, 62.81) --
+	(307.86, 62.81) --
+	(312.97, 62.81);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (323.39, 92.36) --
-	(323.39,115.64);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (321.48, 88.70) --
+	(321.48,114.80);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (323.39, 50.45) --
-	(323.39, 33.24) --
-	(323.39,  0.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (321.48, 41.69) --
+	(321.48, 22.39) --
+	(321.48,  0.00);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (318.46, 92.36) --
-	(318.46, 50.45) --
-	(323.39, 50.45) --
-	(328.31, 50.45) --
-	(328.31, 92.36) --
-	(323.39, 92.36) --
-	(318.46, 92.36) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (316.38, 88.70) --
+	(316.38, 41.69) --
+	(321.48, 41.69) --
+	(326.59, 41.69) --
+	(326.59, 88.70) --
+	(321.48, 88.70) --
+	(316.38, 88.70) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (318.46, 69.28) --
-	(323.39, 69.28) --
-	(328.31, 69.28);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (316.38, 62.81) --
+	(321.48, 62.81) --
+	(326.59, 62.81);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (336.52, 91.48) --
-	(336.52,114.11);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (335.11, 87.70) --
+	(335.11,113.08);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (336.52, 50.78) --
-	(336.52, 33.95) --
-	(336.52,  0.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (335.11, 42.06) --
+	(335.11, 23.19) --
+	(335.11,  0.00);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (331.59, 91.48) --
-	(331.59, 50.78) --
-	(336.52, 50.78) --
-	(341.44, 50.78) --
-	(341.44, 91.48) --
-	(336.52, 91.48) --
-	(331.59, 91.48) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (330.00, 87.70) --
+	(330.00, 42.06) --
+	(335.11, 42.06) --
+	(340.21, 42.06) --
+	(340.21, 87.70) --
+	(335.11, 87.70) --
+	(330.00, 87.70) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (331.59, 69.09) --
-	(336.52, 69.09) --
-	(341.44, 69.09);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (330.00, 62.60) --
+	(335.11, 62.60) --
+	(340.21, 62.60);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (349.65, 92.41) --
-	(349.65,115.75);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (348.73, 88.75) --
+	(348.73,114.92);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (349.65, 50.28) --
-	(349.65, 33.38) --
-	(349.65,  0.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (348.73, 41.51) --
+	(348.73, 22.55) --
+	(348.73,  0.00);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (344.73, 92.41) --
-	(344.73, 50.28) --
-	(349.65, 50.28) --
-	(354.58, 50.28) --
-	(354.58, 92.41) --
-	(349.65, 92.41) --
-	(344.73, 92.41) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (343.62, 88.75) --
+	(343.62, 41.51) --
+	(348.73, 41.51) --
+	(353.84, 41.51) --
+	(353.84, 88.75) --
+	(348.73, 88.75) --
+	(343.62, 88.75) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (344.73, 68.54) --
-	(349.65, 68.54) --
-	(354.58, 68.54);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (343.62, 61.98) --
+	(348.73, 61.98) --
+	(353.84, 61.98);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (362.78, 92.67) --
-	(362.78,115.95);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (362.35, 89.04) --
+	(362.35,115.15);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (362.78, 50.12) --
-	(362.78, 33.24) --
-	(362.78,  0.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (362.35, 41.32) --
+	(362.35, 22.39) --
+	(362.35,  0.00);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (357.86, 92.67) --
-	(357.86, 50.12) --
-	(362.78, 50.12) --
-	(367.71, 50.12) --
-	(367.71, 92.67) --
-	(362.78, 92.67) --
-	(357.86, 92.67) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (357.24, 89.04) --
+	(357.24, 41.32) --
+	(362.35, 41.32) --
+	(367.46, 41.32) --
+	(367.46, 89.04) --
+	(362.35, 89.04) --
+	(357.24, 89.04) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (357.86, 68.91) --
-	(362.78, 68.91) --
-	(367.71, 68.91);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (357.24, 62.39) --
+	(362.35, 62.39) --
+	(367.46, 62.39);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (375.92, 93.23) --
-	(375.92,116.80);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (375.97, 89.66) --
+	(375.97,116.10);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (375.92, 49.78) --
-	(375.92, 33.67) --
-	(375.92,  0.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (375.97, 40.94) --
+	(375.97, 22.87) --
+	(375.97,  0.00);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (370.99, 93.23) --
-	(370.99, 78.50) --
-	(370.99, 49.78) --
-	(375.92, 49.78) --
-	(380.84, 49.78) --
-	(380.84, 78.50) --
-	(380.84, 93.23) --
-	(375.92, 93.23) --
-	(370.99, 93.23) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (370.86, 89.66) --
+	(370.86, 73.15) --
+	(370.86, 40.94) --
+	(375.97, 40.94) --
+	(381.08, 40.94) --
+	(381.08, 73.15) --
+	(381.08, 89.66) --
+	(375.97, 89.66) --
+	(370.86, 89.66) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (370.99, 68.54) --
-	(375.92, 68.54) --
-	(380.84, 68.54);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (370.86, 61.98) --
+	(375.97, 61.98) --
+	(381.08, 61.98);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (389.05, 93.35) --
-	(389.05,117.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.59, 89.81) --
+	(389.59,116.33);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (389.05, 49.44) --
-	(389.05, 32.36) --
-	(389.05,  0.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.59, 40.55) --
+	(389.59, 21.41) --
+	(389.59,  0.00);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (384.12, 93.35) --
-	(384.12, 78.54) --
-	(384.12, 49.44) --
-	(389.05, 49.44) --
-	(393.97, 49.44) --
-	(393.97, 78.54) --
-	(393.97, 93.35) --
-	(389.05, 93.35) --
-	(384.12, 93.35) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (384.49, 89.81) --
+	(384.49, 73.19) --
+	(384.49, 40.55) --
+	(389.59, 40.55) --
+	(394.70, 40.55) --
+	(394.70, 73.19) --
+	(394.70, 89.81) --
+	(389.59, 89.81) --
+	(384.49, 89.81) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (384.12, 68.35) --
-	(389.05, 68.35) --
-	(393.97, 68.35);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (384.49, 61.77) --
+	(389.59, 61.77) --
+	(394.70, 61.77);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (402.18, 94.07) --
-	(402.18,117.92);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (403.22, 90.61) --
+	(403.22,117.36);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (402.18, 49.09) --
-	(402.18, 32.51) --
-	(402.18,  0.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (403.22, 40.17) --
+	(403.22, 21.57) --
+	(403.22,  0.00);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (397.26, 94.07) --
-	(397.26, 79.05) --
-	(397.26, 49.09) --
-	(402.18, 49.09) --
-	(407.11, 49.09) --
-	(407.11, 79.05) --
-	(407.11, 94.07) --
-	(402.18, 94.07) --
-	(397.26, 94.07) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (398.11, 90.61) --
+	(398.11, 73.76) --
+	(398.11, 40.17) --
+	(403.22, 40.17) --
+	(408.32, 40.17) --
+	(408.32, 73.76) --
+	(408.32, 90.61) --
+	(403.22, 90.61) --
+	(398.11, 90.61) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (397.26, 67.01) --
-	(402.18, 67.01) --
-	(407.11, 67.01);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (398.11, 60.26) --
+	(403.22, 60.26) --
+	(408.32, 60.26);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (415.32, 95.91) --
-	(415.32,120.16);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (416.84, 92.67) --
+	(416.84,119.87);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (415.32, 48.56) --
-	(415.32, 31.76) --
-	(415.32,  0.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (416.84, 39.58) --
+	(416.84, 20.74) --
+	(416.84,  0.00);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (410.39, 95.91) --
-	(410.39, 80.45) --
-	(410.39, 48.56) --
-	(415.32, 48.56) --
-	(420.24, 48.56) --
-	(420.24, 80.45) --
-	(420.24, 95.91) --
-	(415.32, 95.91) --
-	(410.39, 95.91) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (411.73, 92.67) --
+	(411.73, 75.33) --
+	(411.73, 39.58) --
+	(416.84, 39.58) --
+	(421.95, 39.58) --
+	(421.95, 75.33) --
+	(421.95, 92.67) --
+	(416.84, 92.67) --
+	(411.73, 92.67) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (410.39, 65.50) --
-	(415.32, 65.50) --
-	(420.24, 65.50);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (411.73, 58.57) --
+	(416.84, 58.57) --
+	(421.95, 58.57);
 \definecolor{drawColor}{RGB}{0,0,0}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 47.60, 77.28) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 35.42, 71.78) circle (  1.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 60.73, 87.17) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 49.04, 82.87) circle (  1.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 73.86, 97.77) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 62.67, 94.76) circle (  1.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 86.99,102.29) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 76.29, 99.83) circle (  1.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (100.13,104.22) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.91,101.99) circle (  1.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.26,111.33) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.53,109.96) circle (  1.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.39,113.70) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.15,112.62) circle (  1.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.53,118.81) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.78,118.35) circle (  1.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.66,120.55) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.40,120.31) circle (  1.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.79,126.30) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.02,126.76) circle (  1.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (178.92,126.57) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (171.64,127.05) circle (  1.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (192.06,125.59) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (185.26,125.96) circle (  1.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (205.19,132.15) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (198.89,133.31) circle (  1.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (218.32,130.53) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (212.51,131.50) circle (  1.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (231.46,133.04) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (226.13,134.31) circle (  1.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (244.59,134.65) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (239.75,136.12) circle (  1.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (257.72,133.46) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (253.37,134.78) circle (  1.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (270.85,135.90) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (267.00,137.52) circle (  1.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (283.99,133.70) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (280.62,135.05) circle (  1.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (297.12,135.55) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (294.24,137.13) circle (  1.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (310.25,135.74) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (307.86,137.34) circle (  1.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (323.39,136.17) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (321.48,137.82) circle (  1.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (336.52,135.30) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (335.11,136.84) circle (  1.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (349.65,134.10) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (348.73,135.50) circle (  1.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (362.78,130.89) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (362.35,131.90) circle (  1.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (375.92,129.45) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (375.97,130.28) circle (  1.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (389.05,122.60) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (389.59,122.60) circle (  1.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (402.18,115.93) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (403.22,115.13) circle (  1.96);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (415.32,111.18) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (416.84,109.80) circle (  1.96);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96, 26.91) {10};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.56] at ( 11.43, 17.12) {10};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.62] at ( 26.76, 30.51) {2};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.39] at ( 17.03, 19.41) {2};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96, 99.01) {10};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.56] at ( 11.43, 97.98) {10};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.62] at ( 26.76,102.60) {3};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.39] at ( 17.03,100.27) {3};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.04, 30.69) --
-	( 34.79, 30.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 20.39, 19.53) --
+	( 22.14, 19.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.04,102.78) --
-	( 34.79,102.78);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 20.39,100.38) --
+	( 22.14,100.38);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 47.60, 27.94) --
-	( 47.60, 30.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.42, 17.78) --
+	( 35.42, 19.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 60.73, 27.94) --
-	( 60.73, 30.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 49.04, 17.78) --
+	( 49.04, 19.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.86, 27.94) --
-	( 73.86, 30.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 62.67, 17.78) --
+	( 62.67, 19.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 86.99, 27.94) --
-	( 86.99, 30.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 76.29, 17.78) --
+	( 76.29, 19.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (100.13, 27.94) --
-	(100.13, 30.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 89.91, 17.78) --
+	( 89.91, 19.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (113.26, 27.94) --
-	(113.26, 30.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (103.53, 17.78) --
+	(103.53, 19.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (126.39, 27.94) --
-	(126.39, 30.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (117.15, 17.78) --
+	(117.15, 19.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (139.53, 27.94) --
-	(139.53, 30.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (130.78, 17.78) --
+	(130.78, 19.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (152.66, 27.94) --
-	(152.66, 30.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (144.40, 17.78) --
+	(144.40, 19.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.79, 27.94) --
-	(165.79, 30.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (158.02, 17.78) --
+	(158.02, 19.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (178.92, 27.94) --
-	(178.92, 30.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (171.64, 17.78) --
+	(171.64, 19.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (192.06, 27.94) --
-	(192.06, 30.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (185.26, 17.78) --
+	(185.26, 19.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (205.19, 27.94) --
-	(205.19, 30.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (198.89, 17.78) --
+	(198.89, 19.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (218.32, 27.94) --
-	(218.32, 30.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (212.51, 17.78) --
+	(212.51, 19.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (231.46, 27.94) --
-	(231.46, 30.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (226.13, 17.78) --
+	(226.13, 19.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (244.59, 27.94) --
-	(244.59, 30.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (239.75, 17.78) --
+	(239.75, 19.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (257.72, 27.94) --
-	(257.72, 30.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (253.37, 17.78) --
+	(253.37, 19.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (270.85, 27.94) --
-	(270.85, 30.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (267.00, 17.78) --
+	(267.00, 19.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (283.99, 27.94) --
-	(283.99, 30.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (280.62, 17.78) --
+	(280.62, 19.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (297.12, 27.94) --
-	(297.12, 30.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (294.24, 17.78) --
+	(294.24, 19.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (310.25, 27.94) --
-	(310.25, 30.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (307.86, 17.78) --
+	(307.86, 19.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (323.39, 27.94) --
-	(323.39, 30.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (321.48, 17.78) --
+	(321.48, 19.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (336.52, 27.94) --
-	(336.52, 30.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (335.11, 17.78) --
+	(335.11, 19.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (349.65, 27.94) --
-	(349.65, 30.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (348.73, 17.78) --
+	(348.73, 19.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (362.78, 27.94) --
-	(362.78, 30.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (362.35, 17.78) --
+	(362.35, 19.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (375.92, 27.94) --
-	(375.92, 30.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (375.97, 17.78) --
+	(375.97, 19.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (389.05, 27.94) --
-	(389.05, 30.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (389.59, 17.78) --
+	(389.59, 19.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (402.18, 27.94) --
-	(402.18, 30.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (403.22, 17.78) --
+	(403.22, 19.53);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (415.32, 27.94) --
-	(415.32, 30.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (416.84, 17.78) --
+	(416.84, 19.53);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 47.60, 19.68) {0};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at ( 35.42, 12.52) {0};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 60.73, 19.68) {1};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at ( 49.04, 12.52) {1};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 73.86, 19.68) {2};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at ( 62.67, 12.52) {2};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 86.99, 19.68) {3};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at ( 76.29, 12.52) {3};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (100.13, 19.68) {4};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at ( 89.91, 12.52) {4};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (113.26, 19.68) {5};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at (103.53, 12.52) {5};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (126.39, 19.68) {6};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at (117.15, 12.52) {6};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (139.53, 19.68) {7};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at (130.78, 12.52) {7};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (152.66, 19.68) {8};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at (144.40, 12.52) {8};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (165.79, 19.68) {9};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at (158.02, 12.52) {9};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (178.92, 19.68) {10};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at (171.64, 12.52) {10};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (192.06, 19.68) {11};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at (185.26, 12.52) {11};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (205.19, 19.68) {12};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at (198.89, 12.52) {12};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (218.32, 19.68) {13};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at (212.51, 12.52) {13};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (231.46, 19.68) {14};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at (226.13, 12.52) {14};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (244.59, 19.68) {15};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at (239.75, 12.52) {15};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (257.72, 19.68) {16};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at (253.37, 12.52) {16};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (270.85, 19.68) {17};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at (267.00, 12.52) {17};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (283.99, 19.68) {18};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at (280.62, 12.52) {18};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (297.12, 19.68) {19};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at (294.24, 12.52) {19};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (310.25, 19.68) {20};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at (307.86, 12.52) {20};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (323.39, 19.68) {21};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at (321.48, 12.52) {21};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (336.52, 19.68) {22};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at (335.11, 12.52) {22};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (349.65, 19.68) {23};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at (348.73, 12.52) {23};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (362.78, 19.68) {24};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at (362.35, 12.52) {24};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (375.92, 19.68) {25};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at (375.97, 12.52) {25};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (389.05, 19.68) {26};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at (389.59, 12.52) {26};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (402.18, 19.68) {27};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at (403.22, 12.52) {27};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (415.32, 19.68) {28};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at (416.84, 12.52) {28};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (231.46,  7.64) {Independent pairs};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (226.13,  4.86) {Independent pairs};
 \end{scope}
@@
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08, 84.86) {Nodes};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (  8.32, 80.28) {Nodes};
 \end{scope}

### 2020-01-21 analyse_data.R

@@ -1,23 +1,22 @@
 library(ggplot2)
 library(tikzDevice)
+library(dplyr)
+library(ggrepel)
 
 df <- read.csv("src/runtime.csv", header = FALSE, sep = ";", skip = 1)
+df <- df[, colSums(is.na(df)) < nrow(df)]
 names(df) <- c("numPredicates", "maxArity", "numVariables", "numConstants", "numAdditionalClauses", "numIndependentPairs", "maxNumNodes",
                  "solutionCount", "buildingTime", "totalTime", "initTime", "nodes", "backtracks", "fails", "restarts")
 df$percentageIndependent <- round(ifelse(df$numIndependentPairs >= 2, df$numIndependentPairs / choose(df$numPredicates, 2), 0), 2)
+df$numClauses <- df$numPredicates + df$numAdditionalClauses
 
+# Numbers
 small <- df[df$totalTime < 1, ]
 nrow(small)/nrow(df)*100
 tail(sort(df$totalTime))
+df %>% group_by(df$numPredicates) %>% tally()
 
-boxplots <- function(df, x, y) {
-  ggplot(df, aes(factor(x), y, group = x)) +
-    geom_boxplot(outlier.shape = NA) +
-    coord_trans(y = "log10", limy = c(10, quantile(y, 0.92))) +
-    scale_y_continuous(breaks = c(1, 10, 100, 1000, 10000),
-                       labels = c("1", "10", expression(10^2), expression(10^3), expression(10^4)))
-}
-
+# Phase transition
 big <- df[df$numPredicates == 8, ]
 tikz(file = "paper/phase_transition.tex", width = 6, height = 2)
 ggplot(big, aes(factor(numIndependentPairs), nodes, group = numIndependentPairs)) +
@@ -27,38 +26,100 @@ ggplot(big, aes(factor(numIndependentPairs), nodes, group = numIndependentPairs)
                      labels = c("1", "20", expression(10^2), expression(10^3), expression(10^4))) +
   stat_summary(fun.y = mean, geom = "point") +
   xlab("Independent pairs") +
-  ylab("Nodes")
+  ylab("Nodes") +
+  theme_set(theme_gray(base_size = 7))
 dev.off()
 
-# Positive correlation
-cor.test(df$numVariables, df$totalTime)
-cor.test(df$numVariables, df$nodes)
-boxplots(df, df$numVariables, df$totalTime)
[…]

### 2020-01-22 paper/impact.tex
Writing about the experiments

@@
-% Created by tikzDevice version 0.12.3 on 2020-01-21 14:48:17
+% Created by tikzDevice version 0.12.3 on 2020-01-22 11:34:15
 % !TEX encoding = UTF-8 Unicode
@@
 \definecolor{fillColor}{RGB}{255,255,255}
-\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (234.88,176.16);
+\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (216.81,176.16);
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (234.88,176.16);
+\path[clip] (  0.00,  0.00) rectangle (216.81,176.16);
 \definecolor{drawColor}{RGB}{255,255,255}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (234.88,176.16);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (216.81,176.16);
 \end{scope}
 \begin{scope}
-\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);
+\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
 \definecolor{fillColor}{gray}{0.92}
 
-\path[fill=fillColor] ( 25.78, 19.53) rectangle (231.38,172.66);
+\path[fill=fillColor] ( 25.78, 19.53) rectangle (213.31,172.66);
 \definecolor{drawColor}{RGB}{255,255,255}
@@
 \path[draw=drawColor,line width= 0.2pt,line join=round] ( 25.78, 51.08) --
-	(231.38, 51.08);
+	(213.31, 51.08);
 
 \path[draw=drawColor,line width= 0.2pt,line join=round] ( 25.78,102.07) --
-	(231.38,102.07);
+	(213.31,102.07);
 
 \path[draw=drawColor,line width= 0.2pt,line join=round] ( 25.78,153.07) --
-	(231.38,153.07);
+	(213.31,153.07);
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] ( 63.26, 19.53) --
-	( 63.26,172.66);
+\path[draw=drawColor,line width= 0.2pt,line join=round] ( 59.96, 19.53) --
+	( 59.96,172.66);
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] (119.52, 19.53) --
-	(119.52,172.66);
+\path[draw=drawColor,line width= 0.2pt,line join=round] (111.28, 19.53) --
+	(111.28,172.66);
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] (175.79, 19.53) --
-	(175.79,172.66);
+\path[draw=drawColor,line width= 0.2pt,line join=round] (162.60, 19.53) --
+	(162.60,172.66);
 
 \path[draw=drawColor,line width= 0.4pt,line join=round] ( 25.78, 25.58) --
-	(231.38, 25.58);
+	(213.31, 25.58);
 
 \path[draw=drawColor,line width= 0.4pt,line join=round] ( 25.78, 76.58) --
-	(231.38, 76.58);
+	(213.31, 76.58);
 
 \path[draw=drawColor,line width= 0.4pt,line join=round] ( 25.78,127.57) --
-	(231.38,127.57);
+	(213.31,127.57);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.12, 19.53) --
-	( 35.12,172.66);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 34.30, 19.53) --
+	( 34.30,172.66);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 91.39, 19.53) --
-	( 91.39,172.66);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 85.62, 19.53) --
+	( 85.62,172.66);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] (147.65, 19.53) --
-	(147.65,172.66);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (136.94, 19.53) --
+	(136.94,172.66);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] (203.92, 19.53) --
-	(203.92,172.66);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (188.26, 19.53) --
+	(188.26,172.66);
 \definecolor{drawColor}{RGB}{27,158,119}
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 35.12, 26.49) --
-	( 91.39, 27.97) --
-	(147.65, 34.12) --
-	(203.92, 77.20);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 34.30, 26.49) --
+	( 85.62, 27.97) --
+	(136.94, 34.12) --
+	(188.26, 77.20);
 \definecolor{drawColor}{RGB}{217,95,2}
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 35.12, 58.87) --
-	( 91.39, 62.68) --
-	(124.30, 68.55) --
-	(147.65, 72.47);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 34.30, 58.87) --
+	( 85.62, 62.68) --
+	(115.64, 68.55) --
+	(136.94, 72.47);
 \definecolor{drawColor}{RGB}{117,112,179}
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 35.12, 60.44) --
-	( 91.39, 64.58) --
-	(147.65, 66.81) --
-	(203.92, 70.73);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 34.30, 60.44) --
+	( 85.62, 64.58) --
+	(136.94, 66.81) --
+	(188.26, 70.73);
 \definecolor{drawColor}{RGB}{231,41,138}
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 35.12, 62.87) --
-	( 91.39, 64.62) --
-	(147.65, 67.25) --
-	(203.92, 67.83);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 34.30, 62.87) --
+	( 85.62, 64.62) --
+	(136.94, 67.25) --
+	(188.26, 67.83);
 \definecolor{drawColor}{RGB}{102,166,30}
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 35.12, 58.10) --
-	( 91.39, 59.23) --
-	(147.65, 65.57) --
-	(203.92, 79.66);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 34.30, 58.10) --
+	( 85.62, 59.23) --
+	(136.94, 65.57) --
+	(188.26, 79.66);
 \definecolor{drawColor}{RGB}{230,171,2}
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 35.12, 30.36) --
-	( 91.39, 30.94) --
-	(147.65, 35.55) --
-	(203.92,165.70);
+\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 34.30, 30.36) --
+	( 85.62, 30.94) --
+	(136.94, 35.55) --
+	(188.26,165.70);
 \definecolor{fillColor}{RGB}{27,158,119}
 
-\path[fill=fillColor,fill opacity=0.75] ( 32.63, 23.99) --
-	( 37.62, 23.99) --
-	( 37.62, 28.99) --
-	( 32.63, 28.99) --
+\path[fill=fillColor,fill opacity=0.75] ( 31.81, 23.99) --
+	( 36.80, 23.99) --
+	( 36.80, 28.99) --
+	( 31.81, 28.99) --
 	cycle;
 
-\path[fill=fillColor,fill opacity=0.75] ( 88.89, 25.47) --
-	( 93.89, 25.47) --
-	( 93.89, 30.46) --
-	( 88.89, 30.46) --
+\path[fill=fillColor,fill opacity=0.75] ( 83.13, 25.47) --
+	( 88.12, 25.47) --
+	( 88.12, 30.46) --
+	( 83.13, 30.46) --
 	cycle;
 
-\path[fill=fillColor,fill opacity=0.75] (145.16, 31.63) --
-	(150.15, 31.63) --
-	(150.15, 36.62) --
-	(145.16, 36.62) --
+\path[fill=fillColor,fill opacity=0.75] (134.45, 31.63) --
+	(139.44, 31.63) --
+	(139.44, 36.62) --
+	(134.45, 36.62) --
 	cycle;
 
-\path[fill=fillColor,fill opacity=0.75] (201.42, 74.70) --
-	(206.42, 74.70) --
-	(206.42, 79.69) --
-	(201.42, 79.69) --
+\path[fill=fillColor,fill opacity=0.75] (185.77, 74.70) --
+	(190.76, 74.70) --
+	(190.76, 79.69) --
+	(185.77, 79.69) --
 	cycle;
@@
 
-\path[fill=fillColor,fill opacity=0.75] ( 35.12, 58.87) circle (  2.50);
+\path[fill=fillColor,fill opacity=0.75] ( 34.30, 58.87) circle (  2.50);
 
-\path[fill=fillColor,fill opacity=0.75] ( 91.39, 62.68) circle (  2.50);
+\path[fill=fillColor,fill opacity=0.75] ( 85.62, 62.68) circle (  2.50);
 
-\path[fill=fillColor,fill opacity=0.75] (124.30, 68.55) circle (  2.50);
+\path[fill=fillColor,fill opacity=0.75] (115.64, 68.55) circle (  2.50);
 
-\path[fill=fillColor,fill opacity=0.75] (147.65, 72.47) circle (  2.50);
+\path[fill=fillColor,fill opacity=0.75] (136.94, 72.47) circle (  2.50);
 \definecolor{fillColor}{RGB}{117,112,179}
 
-\path[fill=fillColor,fill opacity=0.75] ( 35.12, 64.32) --
-	( 38.49, 58.50) --
-	( 31.76, 58.50) --
+\path[fill=fillColor,fill opacity=0.75] ( 34.30, 64.32) --
+	( 37.67, 58.50) --
+	( 30.94, 58.50) --
 	cycle;
 
-\path[fill=fillColor,fill opacity=0.75] ( 91.39, 68.46) --
-	( 94.75, 62.64) --
-	( 88.03, 62.64) --
+\path[fill=fillColor,fill opacity=0.75] ( 85.62, 68.46) --
+	( 88.99, 62.64) --
+	( 82.26, 62.64) --
 	cycle;
 
-\path[fill=fillColor,fill opacity=0.75] (147.65, 70.70) --
-	(151.02, 64.87) --
-	(144.29, 64.87) --
+\path[fill=fillColor,fill opacity=0.75] (136.94, 70.70) --
+	(140.31, 64.87) --
+	(133.58, 64.87) --
 	cycle;
 
-\path[fill=fillColor,fill opacity=0.75] (203.92, 74.62) --
-	(207.28, 68.79) --
-	(200.56, 68.79) --
+\path[fill=fillColor,fill opacity=0.75] (188.26, 74.62) --
+	(191.63, 68.79) --
+	(184.90, 68.79) --
 	cycle;
@@
 
-\path[fill=fillColor,fill opacity=0.75] ( 32.63, 62.87) --
-	( 35.12, 65.37) --
-	( 37.62, 62.87) --
-	( 35.12, 60.37) --
+\path[fill=fillColor,fill opacity=0.75] ( 31.81, 62.87) --
+	( 34.30, 65.37) --
+	( 36.80, 62.87) --
+	( 34.30, 60.37) --
 	cycle;
 
-\path[fill=fillColor,fill opacity=0.75] ( 88.89, 64.62) --
-	( 91.39, 67.11) --
-	( 93.89, 64.62) --
-	( 91.39, 62.12) --
+\path[fill=fillColor,fill opacity=0.75] ( 83.13, 64.62) --
+	( 85.62, 67.11) --
+	( 88.12, 64.62) --
+	( 85.62, 62.12) --
 	cycle;
 
-\path[fill=fillColor,fill opacity=0.75] (145.16, 67.25) --
-	(147.65, 69.74) --
-	(150.15, 67.25) --
-	(147.65, 64.75) --
+\path[fill=fillColor,fill opacity=0.75] (134.45, 67.25) --
+	(136.94, 69.74) --
+	(139.44, 67.25) --
+	(136.94, 64.75) --
 	cycle;
 
-\path[fill=fillColor,fill opacity=0.75] (201.42, 67.83) --
-	(203.92, 70.32) --
-	(206.42, 67.83) --
-	(203.92, 65.33) --
+\path[fill=fillColor,fill opacity=0.75] (185.77, 67.83) --
+	(188.26, 70.32) --
+	(190.76, 67.83) --
+	(188.26, 65.33) --
 	cycle;
@@
 
-\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] ( 35.12, 58.10) circle (  2.50);
+\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] ( 34.30, 58.10) circle (  2.50);
 
-\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] ( 91.39, 59.23) circle (  2.50);
+\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] ( 85.62, 59.23) circle (  2.50);
 
-\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] (147.65, 65.57) circle (  2.50);
+\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] (136.94, 65.57) circle (  2.50);
 
-\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] (203.92, 79.66) circle (  2.50);
+\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] (188.26, 79.66) circle (  2.50);
 \definecolor{drawColor}{RGB}{230,171,2}
@@
 
-\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] ( 35.12, 30.36) circle (  1.67);
+\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] ( 34.30, 30.36) circle (  1.67);
 
-\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] ( 91.39, 30.94) circle (  1.67);
+\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] ( 85.62, 30.94) circle (  1.67);
 
-\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] (147.65, 35.55) circle (  1.67);
+\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] (136.94, 35.55) circle (  1.67);
 
-\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] (203.92,165.70) circle (  1.67);
+\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] (188.26,165.70) circle (  1.67);
 \end{scope}
 \begin{scope}
-\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);
+\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
 
-\path[] (216.56, 79.75) -- (203.92, 77.20);
+\path[] (198.49, 79.68) -- (188.26, 77.20);
 \definecolor{drawColor}{RGB}{27,158,119}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (218.37, 74.87) --
-	(228.37, 74.87) --
-	(228.29, 74.88) --
-	(228.58, 74.89) --
-	(228.87, 74.94) --
-	(229.14, 75.05) --
-	(229.39, 75.19) --
-	(229.62, 75.38) --
-	(229.81, 75.60) --
-	(229.97, 75.84) --
-	(230.08, 76.11) --
-	(230.15, 76.39) --
-	(230.17, 76.68) --
-	(230.17, 76.68) --
-	(230.17, 83.01) --
-	(230.17, 83.01) --
-	(230.15, 83.30) --
-	(230.08, 83.58) --
-	(229.97, 83.85) --
-	(229.81, 84.09) --
-	(229.62, 84.31) --
-	(229.39, 84.50) --
-	(229.14, 84.64) --
-	(228.87, 84.74) --
-	(228.58, 84.80) --
-	(228.37, 84.82) --
-	(218.37, 84.82) --
-	(218.59, 84.80) --
-	(218.30, 84.81) --
-	(218.01, 84.78) --
-	(217.73, 84.70) --
-	(217.47, 84.57) --
-	(217.23, 84.41) --
-	(217.02, 84.21) --
-	(216.84, 83.97) --
-	(216.71, 83.72) --
-	(216.61, 83.44) --
-	(216.57, 83.15) --
-	(216.56, 83.01) --
-	(216.56, 76.68) --
-	(216.57, 76.83) --
-	(216.57, 76.54) --
-	(216.61, 76.25) --
-	(216.71, 75.97) --
-	(216.84, 75.71) --
-	(217.02, 75.48) --
-	(217.23, 75.28) --
-	(217.47, 75.12) --
-	(217.73, 74.99) --
-	(218.01, 74.91) --
-	(218.30, 74.88) --
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (200.30, 74.83) --
+	(210.30, 74.83) --
+	(210.23, 74.83) --
+	(210.52, 74.84) --
+	(210.80, 74.90) --
+	(211.07, 75.00) --
+	(211.33, 75.15) --
+	(211.55, 75.33) --
+	(211.74, 75.55) --
+	(211.90, 75.80) --
+	(212.01, 76.06) --
+	(212.08, 76.35) --
+	(212.11, 76.63) --
+	(212.11, 76.63) --
+	(212.11, 82.96) --
+	(212.11, 82.96) --
+	(212.08, 83.25) --
+	(212.01, 83.54) --
+	(211.90, 83.80) --
+	(211.74, 84.05) --
+	(211.55, 84.27) --
+	(211.33, 84.45) --
+	(211.07, 84.60) --
+	(210.80, 84.70) --
+	(210.52, 84.76) --
+	(210.30, 84.77) --
+	(200.30, 84.77) --
+	(200.52, 84.76) --
+	(200.23, 84.77) --
+	(199.94, 84.73) --
+	(199.66, 84.65) --
+	(199.40, 84.53) --
+	(199.16, 84.36) --
+	(198.95, 84.16) --
+	(198.77, 83.93) --
+	(198.64, 83.67) --
+	(198.55, 83.40) --
+	(198.50, 83.11) --
+	(198.49, 82.96) --
+	(198.49, 76.63) --
+	(198.50, 76.78) --
+	(198.50, 76.49) --
+	(198.55, 76.20) --
+	(198.64, 75.93) --
+	(198.77, 75.67) --
+	(198.95, 75.44) --
+	(199.16, 75.24) --
+	(199.40, 75.07) --
+	(199.66, 74.95) --
+	(199.94, 74.86) --
+	(200.23, 74.83) --
 	cycle;
@@
 \begin{scope}
-\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);
+\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
 \definecolor{drawColor}{RGB}{27,158,119}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (223.37, 77.88) {$|\mathcal{P}|$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (205.30, 77.84) {$|\mathcal{P}|$};
 \end{scope}
 \begin{scope}
-\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);
+\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
 
-\path[] (217.03, 67.65) -- (203.92, 70.73);
+\path[] (198.97, 67.62) -- (188.26, 70.73);
 \definecolor{drawColor}{RGB}{117,112,179}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (218.84, 62.52) --
-	(228.37, 62.52) --
-	(228.29, 62.52) --
-	(228.58, 62.53) --
-	(228.87, 62.59) --
-	(229.14, 62.69) --
-	(229.39, 62.84) --
-	(229.62, 63.02) --
-	(229.81, 63.24) --
-	(229.97, 63.48) --
-	(230.08, 63.75) --
-	(230.15, 64.03) --
-	(230.17, 64.32) --
-	(230.17, 64.32) --
-	(230.17, 70.65) --
-	(230.17, 70.65) --
-	(230.15, 70.94) --
-	(230.08, 71.22) --
-	(229.97, 71.49) --
-	(229.81, 71.74) --
-	(229.62, 71.95) --
-	(229.39, 72.14) --
-	(229.14, 72.28) --
-	(228.87, 72.39) --
-	(228.58, 72.44) --
-	(228.37, 72.46) --
-	(218.84, 72.46) --
-	(219.06, 72.44) --
-	(218.77, 72.46) --
-	(218.48, 72.42) --
-	(218.20, 72.34) --
-	(217.94, 72.22) --
-	(217.70, 72.05) --
-	(217.49, 71.85) --
-	(217.31, 71.62) --
-	(217.18, 71.36) --
-	(217.09, 71.08) --
-	(217.04, 70.80) --
-	(217.03, 70.65) --
-	(217.03, 64.32) --
-	(217.04, 64.47) --
-	(217.04, 64.18) --
-	(217.09, 63.89) --
-	(217.18, 63.61) --
-	(217.31, 63.36) --
-	(217.49, 63.12) --
-	(217.70, 62.92) --
-	(217.94, 62.76) --
-	(218.20, 62.63) --
-	(218.48, 62.55) --
-	(218.77, 62.52) --
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (200.77, 62.43) --
+	(210.30, 62.43) --
+	(210.23, 62.43) --
+	(210.52, 62.44) --
+	(210.80, 62.50) --
+	(211.07, 62.60) --
+	(211.33, 62.75) --
+	(211.55, 62.93) --
+	(211.74, 63.15) --
+	(211.90, 63.39) --
+	(212.01, 63.66) --
+	(212.08, 63.94) --
+	(212.11, 64.23) --
+	(212.11, 64.23) --
+	(212.11, 70.56) --
+	(212.11, 70.56) --
+	(212.08, 70.85) --
+	(212.01, 71.13) --
+	(211.90, 71.40) --
+	(211.74, 71.65) --
+	(211.55, 71.87) --
+	(211.33, 72.05) --
+	(211.07, 72.19) --
+	(210.80, 72.30) --
+	(210.52, 72.36) --
+	(210.30, 72.37) --
+	(200.77, 72.37) --
+	(200.99, 72.36) --
+	(200.70, 72.37) --
+	(200.41, 72.33) --
+	(200.13, 72.25) --
+	(199.87, 72.13) --
+	(199.63, 71.96) --
+	(199.42, 71.76) --
+	(199.25, 71.53) --
+	(199.11, 71.27) --
+	(199.02, 71.00) --
+	(198.97, 70.71) --
+	(198.97, 70.56) --
+	(198.97, 64.23) --
+	(198.97, 64.38) --
+	(198.97, 64.09) --
+	(199.02, 63.80) --
+	(199.11, 63.53) --
+	(199.25, 63.27) --
+	(199.42, 63.04) --
+	(199.63, 62.83) --
+	(199.87, 62.67) --
+	(200.13, 62.54) --
+	(200.41, 62.46) --
+	(200.70, 62.43) --
 	cycle;
@@
 \begin{scope}
-\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);
+\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
 \definecolor{drawColor}{RGB}{117,112,179}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (223.60, 65.53) {$|\mathcal{V}|$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (205.54, 65.44) {$|\mathcal{V}|$};
 \end{scope}
 \begin{scope}
-\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);
+\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
 
-\path[] (217.66, 56.17) -- (203.92, 67.83);
+\path[] (199.59, 56.21) -- (188.26, 67.83);
 \definecolor{drawColor}{RGB}{231,41,138}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (219.47, 50.14) --
-	(228.37, 50.14) --
-	(228.29, 50.14) --
-	(228.58, 50.15) --
-	(228.87, 50.21) --
-	(229.14, 50.31) --
-	(229.39, 50.46) --
-	(229.62, 50.64) --
-	(229.81, 50.86) --
-	(229.97, 51.11) --
-	(230.08, 51.37) --
-	(230.15, 51.66) --
-	(230.17, 51.95) --
-	(230.17, 51.95) --
-	(230.17, 58.27) --
-	(230.17, 58.27) --
-	(230.15, 58.56) --
-	(230.08, 58.85) --
-	(229.97, 59.11) --
-	(229.81, 59.36) --
-	(229.62, 59.58) --
-	(229.39, 59.76) --
-	(229.14, 59.91) --
-	(228.87, 60.01) --
-	(228.58, 60.07) --
-	(228.37, 60.08) --
-	(219.47, 60.08) --
-	(219.68, 60.07) --
-	(219.39, 60.08) --
-	(219.11, 60.04) --
-	(218.83, 59.96) --
-	(218.56, 59.84) --
-	(218.32, 59.67) --
-	(218.11, 59.47) --
-	(217.94, 59.24) --
-	(217.80, 58.98) --
-	(217.71, 58.71) --
-	(217.67, 58.42) --
-	(217.66, 58.27) --
-	(217.66, 51.95) --
-	(217.67, 52.09) --
-	(217.67, 51.80) --
-	(217.71, 51.51) --
-	(217.80, 51.24) --
-	(217.94, 50.98) --
-	(218.11, 50.75) --
-	(218.32, 50.55) --
-	(218.56, 50.38) --
-	(218.83, 50.26) --
-	(219.11, 50.18) --
-	(219.39, 50.14) --
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (201.40, 50.08) --
+	(210.30, 50.08) --
+	(210.23, 50.08) --
+	(210.52, 50.10) --
+	(210.80, 50.15) --
+	(211.07, 50.26) --
+	(211.33, 50.40) --
+	(211.55, 50.59) --
+	(211.74, 50.80) --
+	(211.90, 51.05) --
+	(212.01, 51.32) --
+	(212.08, 51.60) --
+	(212.11, 51.89) --
+	(212.11, 51.89) --
+	(212.11, 58.22) --
+	(212.11, 58.22) --
+	(212.08, 58.51) --
+	(212.01, 58.79) --
+	(211.90, 59.06) --
+	(211.74, 59.30) --
+	(211.55, 59.52) --
+	(211.33, 59.71) --
+	(211.07, 59.85) --
+	(210.80, 59.95) --
+	(210.52, 60.01) --
+	(210.30, 60.02) --
+	(201.40, 60.02) --
+	(201.62, 60.01) --
+	(201.33, 60.02) --
+	(201.04, 59.99) --
+	(200.76, 59.91) --
+	(200.50, 59.78) --
+	(200.26, 59.62) --
+	(200.05, 59.42) --
+	(199.87, 59.18) --
+	(199.74, 58.93) --
+	(199.65, 58.65) --
+	(199.60, 58.36) --
+	(199.59, 58.22) --
+	(199.59, 51.89) --
+	(199.60, 52.03) --
+	(199.60, 51.74) --
+	(199.65, 51.46) --
+	(199.74, 51.18) --
+	(199.87, 50.92) --
+	(200.05, 50.69) --
+	(200.26, 50.49) --
+	(200.50, 50.32) --
+	(200.76, 50.20) --
+	(201.04, 50.12) --
+	(201.33, 50.08) --
 	cycle;
@@
 \begin{scope}
-\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);
+\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
 \definecolor{drawColor}{RGB}{231,41,138}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (223.92, 53.15) {$|\mathcal{C}|$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (205.85, 53.09) {$|\mathcal{C}|$};
 \end{scope}
 \begin{scope}
-\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);
+\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
 
-\path[] (206.06, 87.23) -- (203.92, 79.66);
+\path[] (189.92, 87.17) -- (188.26, 79.66);
 \definecolor{drawColor}{RGB}{102,166,30}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (192.74, 87.23) --
-	(219.48, 87.23) --
-	(219.40, 87.23) --
-	(219.70, 87.24) --
-	(219.98, 87.30) --
-	(220.25, 87.40) --
-	(220.50, 87.54) --
-	(220.73, 87.73) --
-	(220.92, 87.95) --
-	(221.08, 88.19) --
-	(221.19, 88.46) --
-	(221.26, 88.74) --
-	(221.28, 89.03) --
-	(221.28, 89.03) --
-	(221.28, 95.36) --
-	(221.28, 95.36) --
-	(221.26, 95.65) --
-	(221.19, 95.93) --
-	(221.08, 96.20) --
-	(220.92, 96.45) --
-	(220.73, 96.66) --
-	(220.50, 96.85) --
-	(220.25, 96.99) --
-	(219.98, 97.10) --
-	(219.70, 97.15) --
-	(219.48, 97.17) --
-	(192.74, 97.17) --
-	(192.95, 97.15) --
-	(192.66, 97.17) --
-	(192.37, 97.13) --
-	(192.10, 97.05) --
-	(191.83, 96.93) --
-	(191.59, 96.76) --
-	(191.38, 96.56) --
-	(191.21, 96.33) --
-	(191.07, 96.07) --
-	(190.98, 95.79) --
-	(190.94, 95.51) --
-	(190.93, 95.36) --
-	(190.93, 89.03) --
-	(190.94, 89.18) --
-	(190.94, 88.89) --
-	(190.98, 88.60) --
-	(191.07, 88.32) --
-	(191.21, 88.07) --
-	(191.38, 87.83) --
-	(191.59, 87.63) --
-	(191.83, 87.47) --
-	(192.10, 87.34) --
-	(192.37, 87.26) --
-	(192.66, 87.23) --
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (176.58, 87.17) --
+	(203.32, 87.17) --
+	(203.24, 87.17) --
+	(203.53, 87.19) --
+	(203.82, 87.24) --
+	(204.09, 87.35) --
+	(204.34, 87.49) --
+	(204.57, 87.68) --
+	(204.76, 87.89) --
+	(204.92, 88.14) --
+	(205.03, 88.41) --
+	(205.10, 88.69) --
+	(205.12, 88.98) --
+	(205.12, 88.98) --
+	(205.12, 95.31) --
+	(205.12, 95.31) --
+	(205.10, 95.60) --
+	(205.03, 95.88) --
+	(204.92, 96.15) --
+	(204.76, 96.39) --
+	(204.57, 96.61) --
+	(204.34, 96.79) --
+	(204.09, 96.94) --
+	(203.82, 97.04) --
+	(203.53, 97.10) --
+	(203.32, 97.11) --
+	(176.58, 97.11) --
+	(176.79, 97.10) --
+	(176.50, 97.11) --
+	(176.21, 97.08) --
+	(175.93, 97.00) --
+	(175.67, 96.87) --
+	(175.43, 96.71) --
+	(175.22, 96.51) --
+	(175.05, 96.27) --
+	(174.91, 96.02) --
+	(174.82, 95.74) --
+	(174.77, 95.45) --
+	(174.77, 95.31) --
+	(174.77, 88.98) --
+	(174.77, 89.12) --
+	(174.77, 88.83) --
+	(174.82, 88.55) --
+	(174.91, 88.27) --
+	(175.05, 88.01) --
+	(175.22, 87.78) --
+	(175.43, 87.58) --
+	(175.67, 87.41) --
+	(175.93, 87.29) --
+	(176.21, 87.21) --
+	(176.50, 87.17) --
 	cycle;
@@
 \begin{scope}
-\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);
+\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
 \definecolor{drawColor}{RGB}{102,166,30}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (206.11, 90.24) {$\mathcal{M}_{\mathcal{C}}-|\mathcal{P}|$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (189.95, 90.18) {$\mathcal{M}_{\mathcal{C}}-|\mathcal{P}|$};
 \end{scope}
 \begin{scope}
-\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);
+\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
 
-\path[] (212.71,165.70) -- (203.92,165.70);
+\path[] (194.64,165.70) -- (188.26,165.70);
 \definecolor{drawColor}{RGB}{230,171,2}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (214.51,160.73) --
-	(228.37,160.73) --
-	(228.29,160.73) --
-	(228.58,160.74) --
-	(228.87,160.80) --
-	(229.14,160.90) --
-	(229.39,161.05) --
-	(229.62,161.23) --
-	(229.81,161.45) --
-	(229.97,161.69) --
-	(230.08,161.96) --
-	(230.15,162.24) --
-	(230.17,162.53) --
-	(230.17,162.53) --
-	(230.17,168.86) --
-	(230.17,168.86) --
-	(230.15,169.15) --
-	(230.08,169.43) --
-	(229.97,169.70) --
-	(229.81,169.95) --
-	(229.62,170.16) --
-	(229.39,170.35) --
-	(229.14,170.49) --
-	(228.87,170.60) --
-	(228.58,170.66) --
-	(228.37,170.67) --
-	(214.51,170.67) --
-	(214.73,170.66) --
-	(214.44,170.67) --
-	(214.15,170.63) --
-	(213.87,170.55) --
-	(213.61,170.43) --
-	(213.37,170.26) --
-	(213.16,170.06) --
-	(212.99,169.83) --
-	(212.85,169.57) --
-	(212.76,169.29) --
-	(212.71,169.01) --
-	(212.71,168.86) --
-	(212.71,162.53) --
-	(212.71,162.68) --
-	(212.71,162.39) --
-	(212.76,162.10) --
-	(212.85,161.82) --
-	(212.99,161.57) --
-	(213.16,161.34) --
-	(213.37,161.13) --
-	(213.61,160.97) --
-	(213.87,160.84) --
-	(214.15,160.76) --
-	(214.44,160.73) --
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (196.44,160.73) --
+	(210.30,160.73) --
+	(210.23,160.73) --
+	(210.52,160.74) --
+	(210.80,160.80) --
+	(211.07,160.90) --
+	(211.33,161.05) --
+	(211.55,161.23) --
+	(211.74,161.45) --
+	(211.90,161.69) --
+	(212.01,161.96) --
+	(212.08,162.24) --
+	(212.11,162.53) --
+	(212.11,162.53) --
+	(212.11,168.86) --
+	(212.11,168.86) --
+	(212.08,169.15) --
+	(212.01,169.43) --
+	(211.90,169.70) --
+	(211.74,169.95) --
+	(211.55,170.16) --
+	(211.33,170.35) --
+	(211.07,170.49) --
+	(210.80,170.60) --
+	(210.52,170.66) --
+	(210.30,170.67) --
+	(196.44,170.67) --
+	(196.66,170.66) --
+	(196.37,170.67) --
+	(196.08,170.63) --
+	(195.80,170.55) --
+	(195.54,170.43) --
+	(195.30,170.26) --
+	(195.09,170.06) --
+	(194.92,169.83) --
+	(194.78,169.57) --
+	(194.69,169.29) --
+	(194.64,169.01) --
+	(194.64,168.86) --
+	(194.64,162.53) --
+	(194.64,162.68) --
+	(194.64,162.39) --
+	(194.69,162.10) --
+	(194.78,161.82) --
+	(194.92,161.57) --
+	(195.09,161.34) --
+	(195.30,161.13) --
+	(195.54,160.97) --
+	(195.80,160.84) --
+	(196.08,160.76) --
+	(196.37,160.73) --
 	cycle;
@@
 \begin{scope}
-\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);
+\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
 \definecolor{drawColor}{RGB}{230,171,2}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (221.44,163.74) {$\mathcal{M}_{\mathcal{N}}$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (203.37,163.74) {$\mathcal{M}_{\mathcal{N}}$};
 \end{scope}
 \begin{scope}
-\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);
+\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
 \definecolor{drawColor}{RGB}{217,95,2}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (141.06, 75.50) --
-	(154.25, 75.50) --
-	(154.17, 75.51) --
-	(154.46, 75.52) --
-	(154.75, 75.58) --
-	(155.02, 75.68) --
-	(155.27, 75.82) --
-	(155.50, 76.01) --
-	(155.69, 76.23) --
-	(155.85, 76.47) --
-	(155.96, 76.74) --
-	(156.03, 77.02) --
-	(156.05, 77.31) --
-	(156.05, 77.31) --
-	(156.05, 83.64) --
-	(156.05, 83.64) --
-	(156.03, 83.93) --
-	(155.96, 84.21) --
-	(155.85, 84.48) --
-	(155.69, 84.73) --
-	(155.50, 84.94) --
-	(155.27, 85.13) --
-	(155.02, 85.27) --
-	(154.75, 85.38) --
-	(154.46, 85.43) --
-	(154.25, 85.45) --
-	(141.06, 85.45) --
-	(141.28, 85.43) --
-	(140.99, 85.44) --
-	(140.70, 85.41) --
-	(140.42, 85.33) --
-	(140.16, 85.20) --
-	(139.92, 85.04) --
-	(139.71, 84.84) --
-	(139.54, 84.61) --
-	(139.40, 84.35) --
-	(139.31, 84.07) --
-	(139.26, 83.79) --
-	(139.26, 83.64) --
-	(139.26, 77.31) --
-	(139.26, 77.46) --
-	(139.26, 77.17) --
-	(139.31, 76.88) --
-	(139.40, 76.60) --
-	(139.54, 76.35) --
-	(139.71, 76.11) --
-	(139.92, 75.91) --
-	(140.16, 75.75) --
-	(140.42, 75.62) --
-	(140.70, 75.54) --
-	(140.99, 75.51) --
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (130.35, 75.50) --
+	(143.54, 75.50) --
+	(143.46, 75.51) --
+	(143.75, 75.52) --
+	(144.04, 75.58) --
+	(144.31, 75.68) --
+	(144.56, 75.82) --
+	(144.79, 76.01) --
+	(144.98, 76.23) --
+	(145.14, 76.47) --
+	(145.25, 76.74) --
+	(145.32, 77.02) --
+	(145.34, 77.31) --
+	(145.34, 77.31) --
+	(145.34, 83.64) --
+	(145.34, 83.64) --
+	(145.32, 83.93) --
+	(145.25, 84.21) --
+	(145.14, 84.48) --
+	(144.98, 84.73) --
+	(144.79, 84.94) --
+	(144.56, 85.13) --
+	(144.31, 85.27) --
+	(144.04, 85.38) --
+	(143.75, 85.43) --
+	(143.54, 85.45) --
+	(130.35, 85.45) --
+	(130.57, 85.43) --
+	(130.28, 85.44) --
+	(129.99, 85.41) --
+	(129.71, 85.33) --
+	(129.45, 85.20) --
+	(129.21, 85.04) --
+	(129.00, 84.84) --
+	(128.83, 84.61) --
+	(128.69, 84.35) --
+	(128.60, 84.07) --
+	(128.55, 83.79) --
+	(128.55, 83.64) --
+	(128.55, 77.31) --
+	(128.55, 77.46) --
+	(128.55, 77.17) --
+	(128.60, 76.88) --
+	(128.69, 76.60) --
+	(128.83, 76.35) --
+	(129.00, 76.11) --
+	(129.21, 75.91) --
+	(129.45, 75.75) --
+	(129.71, 75.62) --
+	(129.99, 75.54) --
+	(130.28, 75.51) --
 	cycle;
@@
 \begin{scope}
-\path[clip] ( 25.78, 19.53) rectangle (231.38,172.66);
+\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
 \definecolor{drawColor}{RGB}{217,95,2}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (147.65, 78.52) {$\mathcal{M}_{\mathcal{A}}$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (136.94, 78.52) {$\mathcal{M}_{\mathcal{A}}$};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (234.88,176.16);
+\path[clip] (  0.00,  0.00) rectangle (216.81,176.16);
 \definecolor{drawColor}{gray}{0.30}
@@
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (234.88,176.16);
+\path[clip] (  0.00,  0.00) rectangle (216.81,176.16);
 \definecolor{drawColor}{gray}{0.20}
@@
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (234.88,176.16);
+\path[clip] (  0.00,  0.00) rectangle (216.81,176.16);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.12, 17.78) --
-	( 35.12, 19.53);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 34.30, 17.78) --
+	( 34.30, 19.53);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 91.39, 17.78) --
-	( 91.39, 19.53);
+\path[draw=drawColor,line width= 0.4pt,line join=round] ( 85.62, 17.78) --
+	( 85.62, 19.53);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] (147.65, 17.78) --
-	(147.65, 19.53);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (136.94, 17.78) --
+	(136.94, 19.53);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] (203.92, 17.78) --
-	(203.92, 19.53);
+\path[draw=drawColor,line width= 0.4pt,line join=round] (188.26, 17.78) --
+	(188.26, 19.53);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (234.88,176.16);
+\path[clip] (  0.00,  0.00) rectangle (216.81,176.16);
 \definecolor{drawColor}{gray}{0.30}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at ( 35.12, 12.52) {1};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at ( 34.30, 12.52) {1};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at ( 91.39, 12.52) {2};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at ( 85.62, 12.52) {2};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at (147.65, 12.52) {4};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at (136.94, 12.52) {4};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at (203.92, 12.52) {8};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at (188.26, 12.52) {8};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (234.88,176.16);
+\path[clip] (  0.00,  0.00) rectangle (216.81,176.16);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (128.58,  4.86) {Value of each parameter};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (119.54,  4.86) {Value of each parameter};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (234.88,176.16);
+\path[clip] (  0.00,  0.00) rectangle (216.81,176.16);
 \definecolor{drawColor}{RGB}{0,0,0}

### 2020-01-22 paper/paper.tex
Writing about the experiments

--- 2020-01-20 paper/paper.tex
@@
 \usepackage[round]{natbib}
+\usepackage[inline]{enumitem}
 
@@
 
+% UAI format: section/subsection titles are in all caps, figure/table titles are
+% in TitleCase, table caption above the table
+
 \begin{document}
@@
 TODO: define all the relevant terminology from logic and constraint programming.
+% TODO: decide between 'argument' and 'gap' and be consistent.
 
@@
 
-\begin{example}
+\begin{example} \label{example:sibling}
   Let $\constants{} = \emptyset$, $\variables{} = \{ X, Y, Z \}$, $\maxArity{} =
@@
   \end{tikzpicture}
-  \caption{The tree representation of the body of Clause~\eqref{eq:example_clause}.}
+  \caption{A tree representation of the body of \cref{eq:example_clause}}
   \label{fig:example_tree2}
@@
   \caption{The predicate dependency graph of the program in \cref{ex:program}.
-    Positive edges are labeled with `$+$', and negative edges with `$-$'.}
+    Positive edges are labelled with `$+$', and negative edges with `$-$'.}
   \label{fig:predicate_dependencies}
@@
 \section{EMPIRICAL PERFORMANCE}
-% TODO: describe the experimental setup (variables), hardware/software (CPU, anything else?)
-% see Downloads/cp2019-wiggles.pdf for an example.
 
-\begin{figure*}[t]
+\begin{figure}
+  \centering
+  \input{impact.tex}
+  \caption{The mean number of nodes in the binary search tree for each value of
+    each experimental parameter. Note that the horizontal axis is on a $\log_2$
+    scale.}
+  \label{fig:impact}
+\end{figure}
+
+\begin{figure*}
   \centering
   \input{phase_transition.tex}
-  \caption{TODO}
+  \caption{The distribution of the number of nodes in the binary search tree as
+    a function of the number of independent pairs of predicates for
+    $|\predicates| = 8$. Significant outliers are hidden, the dots denote mean
+    values, and the vertical axis is on a $\log_{10}$ scale.}
+  \label{fig:phase_transition}
 \end{figure*}
 
-We split the decision variables into the following groups:
-\begin{enumerate}
-\item all head predicates,
-\item for each clause:
-  \begin{enumerate}
-  \item $\variable{structure}$,
+Along with constraints, variables, and their domains, two more design decisions
+are needed to complete the model: heuristics and restarts. By trial and error,
+the variable ordering heuristic was devised to eliminate sources of thrashing,
+i.e., situations where a contradiction is being `fixed' by making changes that
+have no hope to fix the contradiction. Thus, we partition all decision variables
+into an ordered list of groups, and require the values of all variables from one
+group to be determined before moving to the next group. Within each group, we
+use the `fail first' variable ordering heuristic. The first group consists of
+all head predicates. Afterwards, we handle all remaining decision variables from
+the first clause before proceeding to the next. The decision variables within
+each clause are divided into:
+\begin{enumerate*}
+\item the $\variable{structure}$ array,
 \item body predicates,
 \item head arguments,
-  \item (if $|\variables{}| > 1$) $\variable{intros}$,
+\item (if $|\variables{}| > 1$) the $\variable{intros}$ array,
 \item body arguments.
-  \end{enumerate}
-\end{enumerate}
-And use the `fail first' variable ordering heuristic within each group.
+\end{enumerate*}
+For instance, in the clause from \cref{example:sibling}, all visible parts of
+the clause would be decided in this order:
+\[
+  \overset{1}{\mathsf{sibling}}(\overset{3}{X}, \overset{3}{Y}) \gets
+  \overset{2}{\mathsf{parent}}(\overset{4}{X}, \overset{4}{Z})
+  \overset{2}{\land} \overset{2}{\mathsf{parent}}(\overset{4}{Y},
+  \overset{4}{Z}).
+\]
+We also employ a geometric restart policy, restarting after $10, 20, 40,
+80, \dots$ contradictions.
 
-We make no claim that this is optimal, but it does avoid major sources of
-thrashing.
-% Example of thrashing: P(X, a) <- ~P(X, b) contradicts the negative cycle
-% constrant. Let's try P(X, a) <- P(X, c) instead (and so on).
+We ran close to \num{400000} experiments, investigating whether the model is
+efficient enough to generate reasonably-sized programs and gaining insight into
+what parameter values make the constraint satisfaction problem harder. For these
+experiments, we use Choco~4.10.2 \citep{choco} with Java~8 on a personal
+computer with an Intel Core i5-8250U processor and Arch Linux 5.4.12-arch1-1
+operating system. For $|\predicates{}|$, $|\variables{}|$, $|\constants{}|$,
+$\maxNumNodes{}$, and $\maxNumClauses{} - |\predicates{}|$ (i.e., the number of
+clauses in addition to the mandatory $|\predicates{}|$ clauses), we assign all
+combinations of 1, 2, 4, 8. $\maxArity{}$ is assigned to values 1--4. For each
+$|\predicates{}|$, we also iterate over all possible numbers of independent
+pairs of predicates, ranging from 0 up to $\binom{|\predicates{}|}{2}$. For each
+combination of the above-mentioned parameters, we pick ten random pairs of:
+$\arities{}$ (such that $\maxArity{}$ occurs at least once) and the required
+number of independent pairs (without repetition). We then run the solver with a
+\SI{60}{\second} timeout.
 
-%If we're thrashing on the negative cycle constraint, there's not much I can do
-%about that.
+The vast majority (\SI{97.7}{\percent}) of runs finished in under
+\SI{1}{\second}, while four instances timed out: all with $|\predicates| =
+\maxNumClauses{} - |\predicates{}| = \maxNumNodes{} = 8$ and the remaining
+parameters all different. This suggests that---regardless of parameter
+values---most of the time a solution can be identified instantaneously while
+occasionally a series of wrong decisions can lead the solver into a part of the
+search space with no solutions.
 
-Value ordering heuristic is random (to make the results random).
+In \cref{fig:impact}, we plot how the mean number of nodes in the binary search
+tree grows as a function of each parameter (the plot for the median is very
+similar). The growth of each curve suggest how well/poorly the model scales with
+higher values of the parameter. From this plot, it is clear that
+$\maxNumNodes{}$ is the limiting factor. This is because some tree structures
+can be impossible to fill with predicates without creating either a negative
+cycle or a forbidden dependence, and such trees become more common as the number
+of nodes increases.
 
-We also employ a geometric restart policy, restarting after $10, 20, 40,\dots$
-failures (contradictions).
+\cref{fig:phase_transition} takes the data for $|\predicates{}| = 8$ (almost
+\num{300000} observations) and shows how the number of nodes in the search tree
+varies with the number of independent pairs of predicates. The box plots show
+that the median number of nodes stays about the same while the dots
+(representing the means) draw an arc. This suggests a type of phase transition,
+but only in mean rather than median, i.e., most problems remain easy, but with
+some parameter values hard problems become more likely. On the one hand, with
+few pairs of independent predicates, one can easily find the right combination
+of predicates to use in each clause. On the other hand, if most predicates must
+be independent, this leaves fewer predicates that can be used in the body of
+each clause (since all of them have to be independent with the head predicate),
+and we can either quickly find a solution or identify that there is none.
 
-% TODO: consider replacing \maxNumClauses{} with max_num_additional_clauses
-\begin{itemize}
-\item $|\predicates{}|$, $|\variables{}|$, $|\constants{}|$, $\maxNumNodes{}$,
-  the number of additional clauses are in $\{ 1, 2, 4, 8 \}$.
-\item $\maxArity{} \in \{ 1, 2, 3, 4 \}$.
-\item all possible numbers of independent pairs: $0, \dots,
-  \binom{|\predicates{}|}{2}$.
-\end{itemize}
-Repeat 10 times:
-\begin{itemize}
-\item Pick a random combination of $|\predicates{}|$ arities such that
-  $\maxArity{}$ is occurs at least once (in an ordered way, since order doesn't
-  matter).
-\item Pick the required number of independent pairs (without repetition).
-\item Run the solver with a \SI{60}{\second} timeout.
-\end{itemize}
-
-Results:
-\begin{itemize}
-\item almost \num{400000} experiments.
-\item \SI{97.7}{\percent} of total running times is less than \SI{1}{\second}
-\item 4 timeouts: all with 8 predicates, 8 additional clauses, and
-  $\maxNumNodes{} = 8$; the rest of the parameters differ.
-\item Running time (or number of nodes) as a function of various parameters:
-  \begin{itemize}
-  \item The number of clauses has a clear impact on time but not number of
-    nodes.
-  \item $\maxNumNodes{}$ has a huge impact on both.
-  \item The proportion of independent pairs of predicates is acting weird.
-    Investigate.
-  \end{itemize}
-\end{itemize}
+% TODO: talk about randomness. The value heuristic is random because we want
+% randomness. After finding one solution, one can continue the search for more,
+% but they will be similar (acceptable if the search space is small and we want
+% to find all solutions).
 

### 2020-01-23 paper/paper.tex
A bit of writing for the introduction

@@
 \section{INTRODUCTION}
+% TODO: import stuff (+references) from my proposal
 
@@
 \begin{itemize}
+\item Empirical testing of inference algorithms.
 \item Generating random programs that generate random data.
@@
 
-TODO: define all the relevant terminology from logic and constraint programming.
+%TODO: define all the relevant terminology from logic and constraint
+% programming: predicates ,arities, (logic) variables, constants, clauses, atoms,
+% heads, bodies,
+% CP: decision variables, constraints.
 % TODO: decide between 'argument' and 'gap' and be consistent.
+% TODO: need to introduce the idea of predicate independence
 
@@
 
-Parameters:
-\begin{itemize}
-\item a list of predicates $\predicates{}$,
-\item a list of their arities $\arities{}$ (including zero, but assuming that at
-  least one predicate has non-zero arity),
-  \begin{itemize}
-  \item \emph{maximum arity} $\maxArity{} \coloneqq \max \arities{}$.
-  \end{itemize}
-\item a list of variables $\variables{}$,
-\item and a list of constants $\constants{}$.
-  \begin{itemize}
-  \item Each of them can be empty, but $|\constants{}| + |\variables{}| > 0$.
-  \end{itemize}
-\item a list of probabilities that are randomly assigned to clauses,
-\item option to forbid all cycles or just negative cycles,
-\item $\maxNumNodes{} \ge 1$: maximum number of nodes in the tree representation
-  of a clause,
-\item $\maxNumClauses{} \ge |\predicates{}|$: maximum number of clauses in a
-  program,
-\end{itemize}
+We begin defining the parameters of our model by initialising sets and lists
+of the primitives used in constructing logic programs: a list of predicates
+$\predicates{}$, a list of their corresponding arities $\arities{}$ (so
+$|\arities{}|$ = $|\predicates{}|$), a set of variables $\variables{}$, and a
+set of constants $\constants{}$. Either $\variables{}$ or $\constants{}$ can be
+empty, but we assume that $|\constants{}| + |\variables{}| > 0$. Similarly, the
+model supports zero-arity predicates but requires at least one predicate to have
+non-zero arity. For notational convenience, we also set $\maxArity{} \coloneqq
+\max \arities{}$.
 
-We also define $\tokens{} = \{ \neg, \land, \lor, \top \}$. All decision
-variables of the model are contained in two arrays:
-$\arrayt{bodies}{\maxNumClauses{}}{Body}$ and
-$\arrayt{heads}{\maxNumClauses{}}{Head}$.
-
+We also define a measure of how complicated a body of a clause can become. As
+each body is represented by a tree (see \cref{sec:bodies}), we set
+$\maxNumNodes{} \ge 1$ to be the maximum number of nodes in the tree
+representation of any clause. We also set $\maxNumClauses{}$ to be the maximum
+number of clauses in a program. We must have that $\maxNumClauses{} \ge
+|\predicates{}|$ because we require each predicate to have at least one clause
+that defines it. The model supports eliminating either all cycles or just
+negative cycles (see \cref{sec:cycles}) and enforcing predicate independence
+(see \cref{sec:independence}), so a list of independent pairs of predicates is
+another parameter. Since this model can generate probabilistic as well as
+non-probabilistic programs, each clause is paired with a probability which is
+randomly selected from a given list (which is our last parameter). For
+generating non-probabilistic programs, one can set this list equal to $\{ 1 \}$.
+Finally, we define $\tokens{} = \{ \neg, \land, \lor, \top \}$ as the set of
+tokens that (together with atoms) form a clause. All decision variables of the
+model can now be divided into $2 \times \maxNumClauses{}$ separate groups,
+treating the body and the head of each clause separately. We say that the
+variables are contained in two arrays: $\arrayt{bodies}{\maxNumClauses{}}{Body}$
+and $\arrayt{heads}{\maxNumClauses{}}{Head}$. Since the order of the clauses
+does not change the meaning of the program, we can also state our first
+constraint:
 \begin{constraint}
@@
 \end{constraint}
-
-A random selection of probabilities is added at the end in case a
-probabilistic program is desired. Regular logic programs can be generated by
-setting the list of probabilities to $\{ 1 \}$.
+Here and henceforth, the exact ordering is immaterial: we only impose an order
+to eliminate permutation symmetries.
 
@@
 
-\section{BODIES OF CLAUSES}
+\section{BODIES OF CLAUSES} \label{sec:bodies}
 
@@
 \end{example}
-
-\subsection{NODES}
 
@@
 \end{align*}
-The first term is simply the number of ways to fill all $n$ gaps with
+The first term is the number of ways to fill all $n$ gaps with
 constants. The parameter $k$ is the number of variables used in the clause, and
@@
 
-\section{PREDICATE INDEPENDENCE}
+\section{PREDICATE INDEPENDENCE} \label{sec:independence}
 
@@
 
-\section{NEGATIVE CYCLES}
+\section{NEGATIVE CYCLES} \label{sec:cycles}
 % TODO: NB: the set of decision variables for this constraint must exclude all

### 2020-01-23 analyse_data.R

@@ -108,7 +108,7 @@ for (Variable in c('numPredicates', 'maxArity', 'numVariables', 'numConstants', 
 effects$label <- ifelse(effects$Value == 8, sapply(as.character(effects$Variable), mytolatex), "")
 effects$aritylabel[effects$Variable == "maxArity" & effects$Value == 4] <- "$\\mathcal{M}_{\\mathcal{A}}$"
 
-tikz(file = "paper/impact.tex", width = 3.25, height = 2.4375)
+tikz(file = "paper/impact.tex", width = 3, height = 2.4375)
 ggplot(effects, aes(Value, mean, color = factor(Variable))) +
   geom_line(alpha = 0.5) +
   geom_point(aes(shape = factor(Variable), size = 1), alpha = 0.75) +

### 2020-01-24 paper/paper.tex
Most of the writing

@@
 \documentclass[letterpaper]{article}
-\usepackage{uai2019}
+\usepackage{uai2020}
 \usepackage[margin=1in]{geometry}
+\usepackage{times}
+
 \usepackage[ruled,vlined]{algorithm2e}
@@
 \def\multiset#1#2{\ensuremath{\left(\kern-.3em\left(\genfrac{}{}{0pt}{}{#1}{#2}\right)\kern-.3em\right)}}
-
-% Set the typeface to Times Roman
-\usepackage{times}
 
@@
 % CP: decision variables, constraints.
-% TODO: decide between 'argument' and 'gap' and be consistent.
 % TODO: need to introduce the idea of predicate independence
 
-If a predicate has arity $n$ and it is as of yet undecided what $n$ terms will
-fill those spots, we will say that the predicate has $n$ \emph{gaps}. We say
-that a constraint variable is \emph{(fully) determined} if its domain (at the
-given moment in the execution) has exactly one value.
+We say that a constraint variable is \emph{(fully) determined} if its domain (at
+the given moment in the execution) has exactly one value.
 
@@
 \begin{definition}
-  The \emph{head} of a clause is composed of
-  \begin{itemize}
-  \item a $\variable{predicate} \in \predicates \cup \{ \Box \}$.
-  \item and $\arrayd{arguments}{\maxArity{}}{\constants{} \cup \variables{}}
-    \cup \{ \Box \}$
-  \end{itemize}
-\end{definition}
-The reason why $\Box$ must be a separate value will become clear in
-\cref{sec:variable_symmetry}.
+  The \emph{head} of a clause is composed of a $\variable{predicate} \in
+  \predicates \cup \{ \Box \}$, and
+  $\arrayd{arguments}{\maxArity{}}{\constants{} \cup \variables{}} \cup \{ \Box
+  \}$.
+\end{definition}
+Here, we use $\Box$ to denote either a disabled clause that we choose not to use
+or disabled arguments if the arity of the $\variable{predicate}$ is less than
+$\maxArity{}$. The reason why we need a separate value for the latter (i.e., why
+it is not enough to fix disabled arguments to a single already-existing value)
+will become clear in \cref{sec:variable_symmetry}.
 
@@
 
+Having defined arity, we can now fix the superfluous arguments:
+
 \begin{constraint} \label{constr:arity}
@@
 
+We can also add a constraint that each predicate $\mathsf{P} \in \predicates{}$
+should have at least one clause with $\mathsf{P}$ at its head:
+
 \begin{constraint}
-  Each predicate gets at least one clause. Let
+Let
   \[
@@
   \]
+\end{constraint}
+
 Here, $\variable{nValues}(P)$ counts the number of unique values in $P$.
-\end{constraint}
 
@@
 
+As was briefly mentioned before, the body of a clause is represented by a tree.
+
 \begin{definition}
-  The body of a clause is defined by:
-  \begin{itemize}
-  \item $\arrayd{structure}{\maxNumNodes{}}{[0, \maxNumNodes{} - 1]}$ such
-    that:
-    \begin{itemize}
-    \item $\variable{structure}[i] = i$: the $i$-th node is a root.
-    \item $\variable{structure}[i] = j$: the $i$-th node's parent is node $j$.
-    \end{itemize}
-  \item $\arrayt{values}{\maxNumNodes{}}{Node}$.
-  \end{itemize}
+  The \emph{body} of a clause has two parts. First, we have the
+  $\arrayd{structure}{\maxNumNodes{}}{[0, \maxNumNodes{} - 1]}$ array that
+  encodes the structure of the tree using the following two rules:
+  $\variable{structure}[i] = i$ means that the $i$-th node is a root, and
+  $\variable{structure}[i] = j$ (for $j \ne i$) means that the $i$-th node's
+  parent is node $j$. The second part is the array
+  $\arrayt{values}{\maxNumNodes{}}{Node}$ such that $\variable{values}[i]$ holds
+  the value of the $i$-th node.
+\end{definition}
+
+We can use the $\variable{tree}$ constraint \citep{DBLP:conf/cp/FagesL11} to
+forbid cycles in the $\variable{structure}$ array and simultaneously define
+$\variable{numTrees} \in \{ 1, \dots, \maxNumNodes{} \}$ to count the number of
+trees. We will view the tree rooted at the zeroth node as the main tree and
+restrict all other trees to single nodes. For this to work, we need to make sure
+that the zeroth node is indeed a root:
+
+\begin{constraint}
+  $\variable{structure}[0] = 0$.
+\end{constraint}
+
+\begin{definition}
+  For convenience, we also define $\variable{numNodes} \in \{ 1, \dots,
+  \maxNumNodes{} \}$ to count the number of nodes in the main tree. We define it
+  as
+  \[
+    \variable{numNodes} = \maxNumNodes{} - \variable{numTrees} + 1.
+  \]
 \end{definition}
@@
 \begin{example} \label{example:formula}
-  Let $\maxNumNodes{} = 8$. Then $\neg\mathsf{P}(X) \lor (\mathsf{Q}(X)
-  \land \mathsf{P}(X))$ corresponds to the tree in \cref{fig:example_tree} and
-  can be encoded as:
+  Let $\maxNumNodes{} = 8$. Then
+  \[
+    \neg\mathsf{P}(X) \lor (\mathsf{Q}(X) \land \mathsf{P}(X))
+  \]
+  corresponds to the tree in \cref{fig:example_tree} and can be encoded as:
   \begin{alignat*}{8}
@@
   \end{alignat*}
-  In the rest of this section, we will describe how the elements of
-  $\variable{values}$ are encoded and list a series of constraints that make
-  this representation unique.
 \end{example}
+
+Here, $\top$ is the value we use for the remaining one-node trees. The
+elements of the $\variable{values}$ array are \emph{nodes}.
 
@@
 
-We can use \cref{constr:arity} again to disable extra arguments.
+Furthermore, we can use \cref{constr:arity} again to disable the extra
+arguments.
 
 \begin{example}
-  Let $\maxArity{} = 2$, $\predicates{} = [\mathsf{P}, \dots]$, $\arities{}
-  = [1, \dots]$, and $X \in \variables{}$. Then the node representing atom
-  $\mathsf{P}(X)$ has:
+  Let $\maxArity{} = 2$, $X \in \variables{}$, and let $\mathsf{P}$ be a
+  predicate with arity 1. Then the node representing atom $\mathsf{P}(X)$ has:
   \begin{align*}
@@
 
-\subsection{CONSTRAINTS}
-
-\begin{definition}
-  Let $\variable{numTrees} \in \{ 1, \dots, \maxNumNodes{} \}$ be the number of
-  trees in $\variable{structure}$, defined using the $\variable{tree}$
-  constraint \citep{DBLP:conf/cp/FagesL11}.
-\end{definition}
-
-\begin{definition}
-  For convenience, we also define $\variable{numNodes} \in \{ 1, \dots,
-  \maxNumNodes{} \}$ to count the number of nodes in the main tree. We define it
-  as
-  \[
-    \variable{numNodes} = \maxNumNodes{} - \variable{numTrees} + 1.
-  \]
-\end{definition}
-
-\begin{constraint}
-  $\variable{structure}[0] = 0$.
-\end{constraint}
+It remains to constrain the forest represented by the $\variable{structure}$
+array together with its $\variable{values}$ to eliminate unnecessary symmetries
+and adhere to our desired format. First, we can recognise that the order of the
+elements in the $\variable{structure}$ array does not matter, i.e., the
+structure is only defined by how the elements link to each other, so we can add
+a constraint saying that:
 
@@
 
+Next, since we already have a variable that counts the number of nodes in the
+main tree, we can fix the structure and the values of the remaining trees to
+some constant values:
+
 \begin{constraint}
@@
 \end{constraint}
+
+The second part of this constraint states that every node in the main tree
+except the zeroth node cannot be a root and must have its parent located to
+the left of itself. Next, we classify all nodes into three classes: predicate
+(or empty) nodes, negation nodes, and conjunction/disjunction nodes based on the
+number of children (zero, one, and two, respectively).
 
@@
 \end{constraint}
-Each of the three equivalences in \cref{constraint:node_types} corresponds to
-node $i$ having no children, one child, and multiple children, respectively.
+
+The value $\top$ serves a twofold purpose: it is used as the fixed value for
+nodes outside the main tree, and, when located at the zeroth node, it can
+represent a clause with no body. Thus, we can say that only root nodes can have
+$\top$ as the value:
 
 \begin{constraint}
-  Only root nodes can have $\top$ as the value. For $i = 0, \dots,
-  \maxNumNodes{} - 1$,
+  For $i = 0, \dots, \maxNumNodes{} - 1$,
   \[
@@
 
-A way to `disable' a clause:
+Finally, we add a way to disable a clause by setting its head predicate to
+$\Box$:
+
 \begin{constraint}
@@
   $\variable{terms}[N] \in \constants{} \cup \variables{} \cup \{ \Box
-  \}$ be a flattened array of all gaps in a particular clause.
+  \}$ be a flattened array of all arguments in a particular clause.
 
@@
 
-The number of ways to fill $n$ gaps with terms can be expressed as
+The number of ways to select $n$ terms is
 \begin{align*}
@@
 \end{align*}
-The first term is the number of ways to fill all $n$ gaps with
-constants. The parameter $k$ is the number of variables used in the clause, and
-$s_1, \dots, s_k$ mark the first occurrence of each variable. For each gap
-between any two introductions (or before the first introduction, or after the last
-introduction), we have $s_{i+1}-s_i-1$ spaces to be filled with any of the
-$\constants{}$ constants or any of the $i$ already-introduced variables.
+The first term is the number of ways select $n$ constants. The parameter $k$ is
+the number of variables used in the clause, and $s_1, \dots, s_k$ mark the first
+occurrence of each variable. For each gap between any two introductions (or
+before the first introduction, or after the last introduction), we have
+$s_{i+1}-s_i-1$ spaces to be filled with any of the $|\constants{}|$ constants
+or any of the $i$ already-introduced variables.
 
@@
 possible arity $a$, and multiplying the number of `unfinished' clauses $C(a)$ by
-the number of ways to fill the $a+a_i$ gaps in the body and the head of the
-clause with terms.
+the number of ways to select the required $a+a_i$ terms in the body and the head
+of the clause.
 
@@
 
-\begin{definition}[Adjacency matrix representation] \label{def:adjacency_matrix}
+We can now add a constraint to define an adjacency matrix for the predicate
+dependency graph but without positivity/negativity.
+\begin{definition} \label{def:adjacency_matrix}
   An $|\predicates{}| \times |\predicates{}|$ adjacency matrix $\mathbf{A}$ with
@@
   if and only if, for all $k \in \{ 0, \dots, \maxNumClauses{} - 1 \}$, either
-$\variable{heads}[k].\variable{predicate} \ne j$ or $i \not\in \{
-a.\variable{name} \mid a \in \variable{bodies}[k].\variable{values} \}$.
+  \[
+    \variable{heads}[k].\variable{predicate} \ne j
+  \]
+  or
+  \[
+    i \not\in \{a.\variable{name} \mid a \in
+    \variable{bodies}[k].\variable{values} \}.
+  \]
 \end{definition}
@@
 \end{grammar}
-where $p \in \predicates{}$ is the name of the predicate which is the
-dependency of $\mathsf{P}$, and---in the case of $\AlmostDetermined$---$(s, t)
-\in \predicates{}^2$ is the one undetermined edge in $\mathbf{A}$ that prevents
-the dependency from being determined. For a dependency $d$---regardless of its
-exact type---we will refer to its predicate $p$ as $d.\variable{predicate}$. In
-describing the algorithms, we will use an underscore to replace any of $p$, $s$,
-$t$ in situations where the name is unimportant.
-
-\begin{algorithm}
-  \SetKwFunction{getDependencies}{deps}
-  \SetKwFunction{fail}{fail}
-  \SetKwFunction{removeValue}{removeValue}
-  \SetKwData{predicate}{predicate}
-  \SetKwData{source}{source}
-  \SetKwData{target}{target}
-  \KwData{predicates $p_1$, $p_2$; adjacency matrix $\mathbf{A}$}
-  \For{$(d_1, d_2) \in \getDependencies{$p_1$, 0} \times \getDependencies{$p_2$,
-      0}$ such that $d_1.\predicate = d_2.\predicate$}{
-    \lIf{$d_1$ {\bf is} $\Determined(\_)$ {\bf and} $d_2$ {\bf is}
-      $\Determined(\_)$}{\fail{}}
-    \If{$d_1$ {\bf is} $\Determined(\_)$ {\bf and} $d_2$ {\bf is}
-      $\AlmostDetermined(\_, s, t)$ {\bf or} \hspace{50pt} $d_2$ {\bf is}
-      $\Determined(\_)$ {\bf and} $d_1$ {\bf is} $\AlmostDetermined(\_, s, t)$}{
-      $\mathbf{A}[s][t]$.\removeValue{$1$}\;
-    }
-  }
-  \caption{Propagation for independence}
-  \label{alg:independence_propagation}
-\end{algorithm}
+where each alternative represents a determined, undetermined, and almost
+determined dependency, respectively. Here, $p \in \predicates{}$ is the name of
+the predicate which is the dependency of $\mathsf{P}$, and---in the case of
+$\AlmostDetermined$---$(s, t) \in \predicates{}^2$ is the one undetermined edge
+in $\mathbf{A}$ that prevents the dependency from being determined. For a
+dependency $d$---regardless of its exact type---we will refer to its predicate
+$p$ as $d.\mathsf{predicate}$. In describing the algorithms, we will use an
+underscore to replace any of $p$, $s$, $t$ in situations where the name is
+unimportant.
+
 \begin{algorithm}
@@
 \end{algorithm}
+
+Each entailment algorithm returns one out of three different values:
+\textsc{true} if the constraint is guaranteed to hold, \textsc{false} if the
+constraint is violated, and \textsc{undefined} if whether the constraint will be
+satisfied or not depends on the future decisions made by the solver.
+\cref{alg:independence_entailment} outlines a simple entailment algorithm for
+the independence of two predicates $p_1$ and $p_2$. First, we separately
+calculate all dependencies of $p_1$ and $p_2$, and look at the set $D$ of
+dependencies that $p_1$ and $p_2$ have in common. If there are none, then the
+predicates are clearly independent. If they have a dependency in common that is
+already fully determined ($\Determined$) for both predicates, then they cannot be
+independent. Otherwise, we return \textsc{undefined}.
+
+\begin{algorithm}
+  \LinesNumbered
+  \SetKwFunction{getDependencies}{deps}
+  \SetKwFunction{fail}{fail}
+  \SetKwFunction{removeValue}{removeValue}
+  \SetKwData{predicate}{predicate}
+  \SetKwData{source}{source}
+  \SetKwData{target}{target}
+  \KwData{predicates $p_1$, $p_2$; adjacency matrix $\mathbf{A}$}
+  \For{$(d_1, d_2) \in \getDependencies{$p_1$, 0} \times \getDependencies{$p_2$,
+      0}$ such that $d_1.\predicate = d_2.\predicate$}{
+    \lIf{$d_1$ {\bf is} $\Determined(\_)$ {\bf and} $d_2$ {\bf is}
+      $\Determined(\_)$}{\fail{}} \label{line:fail}
+    \If{$d_1$ {\bf is} $\Determined(\_)$ {\bf and} $d_2$ {\bf is}
+      $\AlmostDetermined(\_, s, t)$ {\bf or} \hspace{50pt} $d_2$ {\bf is}
+      $\Determined(\_)$ {\bf and} $d_1$ {\bf is} $\AlmostDetermined(\_, s,
+      t)$ \label{line:propagation_condition}}{
+      $\mathbf{A}[s][t]$.\removeValue{$1$}\; \label{line:propagation_result}
+    }
+  }
+  \caption{Propagation for independence}
+  \label{alg:independence_propagation}
+\end{algorithm}
+
+Propagation algorithms have two goals: causing a contradiction (failing) in
+situations where the corresponding entailment algorithm would return
+\textsc{false}, and eliminating values from domains of variables that are
+guaranteed to cause a contradiction. \cref{alg:independence_propagation} does
+the former on \cref{line:fail}. Furthermore, for any dependency shared between
+predicates $p_1$ and $p_2$, if it is determined ($\Determined$) for one
+predicate and almost determined ($\AlmostDetermined$) for another, then the edge
+that prevents the $\AlmostDetermined$ from becoming a $\Determined$ cannot
+exist--\cref{line:propagation_condition,line:propagation_result} take care of
+that.
+
 \begin{algorithm}
@@
   \SetKwData{all}{allDependencies}
-  \SetKwFunction{isDetermined}{isDetermined}
   \SetKwFunction{getDependencies}{deps}
@@
 \end{algorithm}
+
+The function $\getDependencies$ in \cref{alg:dependencies} calculates $D_p$ for
+any predicate $p$. It has two versions: $\getDependencies(p, 1)$ returns all
+dependencies, while $\getDependencies(p, 0)$ returns only determined and
+almost-determined dependencies. It starts by establishing the predicate $p$
+itself as a dependence and continues to add dependencies of dependencies until
+the set $D$ stabilises. For each dependency $d \in D$, we look at the in-links
+of $d$ in the predicate dependency graph. If the edge from some predicate $q$ to
+$d.\mathsf{predicate}$ is fully determined and $d$ is determined, then $q$ is
+another determined dependency of $p$. If the edge is determined but $d$ is
+almost determined, then $q$ is an almost-determined dependency. The same outcome
+applies if $d$ is fully determined but the edge is undetermined. Finally, if we
+are interested in collecting all dependencies regardless of their status, then
+$q$ is a dependency of $p$ as long as the edge from $q$ to
+$d.\mathsf{predicate}$ is possible. Note that if there are multiple paths in the
+dependency graph from $q$ to $p$, \cref{alg:dependencies} could include $q$ once
+for each possible type ($\Determined$, $\Undetermined$, and
+$\AlmostDetermined$), but
+\cref{alg:independence_propagation,alg:independence_entailment} would still work
+as intended.
+
 \begin{figure}
@@
   \[
-    \begin{blockarray}{ccccccc}
-      \begin{block}{ccc(cccc)}
-        \mathsf{father} & & & 0 & 0 & 0 & 0 \\
-        \mathsf{mother} & & & 1 & 0 & 0 & 0 \\
-        \mathsf{parent} & & & 1 & \fbox{\{ 0, 1 \}} & \{ 0, 1 \} & \{ 0, 1 \} \\
-        \mathsf{sibling} & & & 0 & 0 & 0 & 0 \\
+    \begin{blockarray}{ccccc}
+      \begin{block}{c(cccc)}
+        \mathsf{father} & 0 & 0 & 0 & 0 \\
+        \mathsf{mother} & 1 & 0 & 0 & 0 \\
+        \mathsf{parent} & 1 & \fbox{\{ 0, 1 \}} & \{ 0, 1 \} & \{ 0, 1 \} \\
+        \mathsf{sibling} & 0 & 0 & 0 & 0 \\
       \end{block}
@@
 \end{figure}
-\begin{figure}[t]
+
+\begin{figure}
   \centering
@@
 
-% TODO: start here
-% TODO: make sure my definitions and examples are consistent with loops
-% TODO: Discuss that the algorithms work in case there are multiple 'paths'
-% without any issues.
-
-Note that if there are multiple paths in the dependency graph from $\mathsf{Q}$
-to $\mathsf{P}$, when constructing $D_{\mathsf{P}}$, \cref{alg:dependencies}
-could include $\mathsf{Q}$ once for each possible type ($\Determined$,
-$\Undetermined$, and $\AlmostDetermined$). However,
-\cref{alg:independence_propagation,alg:independence_entailment}
-
 \begin{example} \label{example:independence}
@@
 \section{NEGATIVE CYCLES} \label{sec:cycles}
+% TODO: My paper has two slightly different graphs with the same name.
 % TODO: NB: the set of decision variables for this constraint must exclude all
 % arguments.
-% TODO: My paper has two slightly different graphs with the same name.
+% TODO: maybe move some of the definition 10 here.
+
+Having no negative cycles in the predicate dependency graph is a requirement for
+probabilistic logic programming language ProbLog \citep{kimmig2009trading},
+although it has been shown how the requirement can be alleviated by introducing
+negative probabilities \citep{DBLP:journals/ijar/BuchmanP17}. Ideally, we would
+like to design a constraint for that similar to the constraint for independence
+in the previous section. However, the difficulty with creating a propagation
+algorithm for negative cycles is that there seems to be no good way to extend
+\cref{def:adjacency_matrix} so that the adjacency matrix captures
+positivity/negativity. Thus, we settle for an entailment algorithm with no
+propagation.
 
@@
   and head fully determined\footnotemark\;
-  \lIf{$\mathscr{R} = \emptyset$}{\Return{\textsc{undefined}}}
   \If{\hasNegativeCycles($G_{\mathscr{R}}$)}{
@@
   \Return{\textsc{undefined}}\;
-  \caption{Entailment check for negative cycles}
+  \caption{Entailment for negative cycles}
   \label{alg:negative_cycles}
@@
 
-The \texttt{hasNegativeCycles} function is just a simple extension of the cycle
-detection algorithm that `travels' around the graph following edges and
-checking if each vertex has already been visited or not.
-
-The difficulty with creating a propagation algorithm for negative cycles is that
-there seems to be no good way to extend \cref{def:adjacency_matrix} so that the
-adjacency matrix captures positivity/negativity.
+The algorithm takes all clauses whose structure and predicates have been fully
+determined and uses them to construct a full dependency graph. In our
+implementation, \texttt{hasNegativeCycles} function is just a simple extension
+of the backtracking cycle detection algorithm that `travels' around the graph
+following edges and checking if each vertex has already been visited or not.
+Alternatively, one could assign weights to the edges (e.g., $1$ for positive
+and $-\infty$ for negative edges), thus reducing our negative cycle detection
+problem to what is typically known as the negative cycle detection problem in
+the literature, and use an algorithm such as Bellman-Ford
+\citep{shimbel1954structure}.
+
+If the algorithm finds a negative cycle in this fully-determined part of the
+program, then it is unavoidable and we must return \textsc{false}. If there was
+no negative cycle and the entire program is determined-enough to contribute to
+the graph, then there cannot be any negative cycles. In all other cases, it
+is too early to tell.
 

### 2020-01-24 paper/paper.tex
(Most of the) conclusion

@@
 
-% \begin{figure}[h]
-% \vspace{1in}
-% \caption{Sample Figure Caption}
-% \end{figure}
-
-% \begin{table}[h]
-% \caption{Sample Table Title}
-% \label{sample-table}
-% \begin{center}
-% \begin{tabular}{ll}
-% \multicolumn{1}{c}{\bf PART}  &\multicolumn{1}{c}{\bf DESCRIPTION} \\
-% \hline \\
-% Dendrite         &Input terminal \\
-% Axon             &Output terminal \\
-% Soma             &Cell body (contains cell nucleus) \\
-% \end{tabular}
-% \end{center}
-% \end{table}
-
-% UAI format: section/subsection titles are in all caps, figure/table titles are
-% in TitleCase, table caption above the table
-
 \begin{document}
@@
 % programming: predicates ,arities, (logic) variables, constants, clauses, atoms,
-% heads, bodies,
-% CP: decision variables, constraints.
+% heads, bodies, formulas.
+% CP: decision variables, constraints. So the word 'variable' has two meanings.
 % TODO: need to introduce the idea of predicate independence
@@
 constraint:
+
 \begin{constraint}
@@
 \end{constraint}
+
 Here and henceforth, the exact ordering is immaterial: we only impose an order
@@
 \end{definition}
+
 Here, we use $\Box$ to denote either a disabled clause that we choose not to use
@@
 \end{constraint}
+
 In simpler terms, \cref{constraint:potentialIntroductions} says that if a node
@@
 \end{align*}
-The first term here represents negation, i.e., negating an expression consumes
+The first term here represents negation, i.e., negating a formula consumes
 one node but otherwise leaves the task unchanged. If the first operation is not
@@
 dependency graph but without positivity/negativity.
+
 \begin{definition} \label{def:adjacency_matrix}
@@
 \end{figure}
-
 \begin{figure}
@@
 \section{EMPIRICAL PERFORMANCE}
-
-\begin{figure}
-  \centering
-  \input{impact.tex}
-  \caption{The mean number of nodes in the binary search tree for each value of
-    each experimental parameter. Note that the horizontal axis is on a $\log_2$
-    scale.}
-  \label{fig:impact}
-\end{figure}
-
-\begin{figure*}
-  \centering
-  \input{phase_transition.tex}
-  \caption{The distribution of the number of nodes in the binary search tree as
-    a function of the number of independent pairs of predicates for
-    $|\predicates| = 8$. Significant outliers are hidden, the dots denote mean
-    values, and the vertical axis is on a $\log_{10}$ scale.}
-  \label{fig:phase_transition}
-\end{figure*}
 
@@
 
+\begin{figure}
+  \centering
+  \input{impact.tex}
+  \caption{The mean number of nodes in the binary search tree for each value of
+    each experimental parameter. Note that the horizontal axis is on a $\log_2$
+    scale.}
+  \label{fig:impact}
+\end{figure}
+
 In \cref{fig:impact}, we plot how the mean number of nodes in the binary search
@@
 of nodes increases.
+
+\begin{figure*}
+  \centering
+  \input{phase_transition.tex}
+  \caption{The distribution of the number of nodes in the binary search tree as
+    a function of the number of independent pairs of predicates for
+    $|\predicates| = 8$. Significant outliers are hidden, the dots denote mean
+    values, and the vertical axis is on a $\log_{10}$ scale.}
+  \label{fig:phase_transition}
+\end{figure*}
 
@@
 % to find all solutions).
-
-\section{CONCLUSION \& FUTURE WORK}
-
-\begin{itemize}
-\item A constraint for logical equivalence. An algorithm to reduce each tree to
-  some kind of normal form. Not doing this on purpose. Leaving for further work.
-\item Could investigate how uniform the generated distribution of programs is.
-  Distributions of individual parameters will often favour larger values
-  because, e.g., there are more 5-tuples than 4-tuples.
-%\item Inference options to explore. Logspace vs normal space. Symbolic vs
-%  non-symbolic. Propagate evidence (might be irrelevant)? Propagate weights?
-%  Supported knowledge compilation techniques: sdd, sddx, bdd, nnf, ddnnf, kbest,
-%  fsdd, fbdd.
-\item Mention the random heuristic. Mention that restarting gives better
-  randomness, but duplicates become possible.
-\item Could add statistics about what constraints tend to conflict.
-\end{itemize}
+% Mention the random heuristic. Mention that restarting gives better randomness,
+% but duplicates become possible.
+% TODO: the number of predicates is also important.
+
+\section{CONCLUSIONS}
+
+% TODO: the positive side (what did we achieve?)
+
+One major question that was not addressed in this paper is that of logical
+equivalence. We eliminated permutation symmetries and constrained variable usage
+so that the same `functionality' is always assigned to the same variable, but
+syntactically different logical formulas are always treated as being different.
+For example, all three of these formulas are logically equivalent but
+syntactically different: $\neg(\mathsf{P}(X) \lor \mathsf{Q}(X))$,
+$\neg\mathsf{P}(X) \land \neg\mathsf{Q}(X)$, and $\neg\mathsf{Q}(X) \land
+\neg\mathsf{P}(X)$. While there are many situations where one would prefer to
+treat logically equivalent formulas as symmetries that should be eliminated,
+there are also situations where we do care about enumerating different ways to
+express the same probability distribution or knowledge base. For instance,
+one could look for the `best' logically equivalent formula, or investigate
+whether some formulas result in faster inference than others.
+
+Another issue worth discussing is that of randomness. Most random models sample
+from a well-defined probability distribution whereas a constraint model, while
+potentially sufficiently random, provides no such guarantees. In future work, it
+would be interesting to examine the probability distribution of logic programs
+as generated by our model, although it is not obvious how such a
+probability distribution could be characterised. One example of a clear bias
+exhibited by our model is that of complexity over simplicity, i.e., if a tree
+that represents the body of a clause can have up to $\maxNumNodes{}$
+nodes---because the number of possible trees with $n$ nodes grows with $n$---it
+is much more likely to have $\maxNumNodes{}$ or $\maxNumNodes{} - 1$ nodes than,
+e.g., one or two.
 

### 2020-01-24 paper/paper.tex
Making things more readable

@@
 
-\begin{abstract}
-The Abstract paragraph should be indented 0.25 inch (1.5 picas) on
-both left and right-hand margins. Use 10~point type, with a vertical
-spacing of 11~points.  {\bf Abstract} must be centered, bold, and in
-point size 12. Two line spaces precede the Abstract. The Abstract must
-be limited to one paragraph.
+\begin{abstract} % TODO: rewrite
+  We present a novel approach to generate random logic programs using constraint
+  programming. The constraint programming approach to the problem has a major
+  advantage in that one can easily add additional conditions for the generated
+  programs. Some of these conditions can be expressed using constraints native to
+  the constraint solver Choco \citep{choco}, while novel propagation and entailment
+  checking algorithms have been developed for ensuring independence and/or
+  conditional independence amongst predicates. A constraint programming approach
+  also benefits from many years of research into efficient constraint propagation
+  algorithms which makes it likely that our model can generate larger programs
+  relatively quickly.
 \end{abstract}
@@
 \section{INTRODUCTION}
-% TODO: import stuff (+references) from my proposal
+
+% TODO: import related work from my proposal
 
@@
 \begin{definition}
-  Let $N = \maxArity{} \times (\maxNumNodes{} + 1)$. Let
+  Let $N = \maxArity{} \times (\maxNumNodes{} + 1)$, and let
   $\variable{terms}[N] \in \constants{} \cup \variables{} \cup \{ \Box
@@
 
-We introduce an array that, for each variable, holds the position of its first
-occurrence.
+Next, we introduce an array that, for each variable, holds the position of its
+first occurrence:
+
 \begin{definition}
@@
 \end{definition}
+
 Here, a value of zero means that the variable does not occur in the clause. We
@@
 \cref{constraint:diffbutzero} later. Because of this choice, the definition of
-$\variable{intros}$ shifts all indices by one.
+$\variable{intros}$ shifts all indices by one. Lastly, we add the constraint
+that eliminates variable symmetries:
 
@@
 \end{constraint}
+
+In other words, we constrain the model so that the variable listed first in
+whatever order $\variables{}$ is presented in has to occur first in our
+representation of a clause.
 
@@
   \]
-  Then $\variable{terms} = [X, Y, \Box, \Box, X, Z, Y, Z]$ (the boxes represent
-  the conjunction node), $\variable{occ} = [\{ 0, 4 \}, \{ 1, 6 \},
-  \{ 5, 7 \}, \{ 2, 3 \}]$, and $\variable{intros} = [0, 1, 5]$.
+  Then
+  \begin{align*}
+    \variable{terms} &= [X, Y, \Box, \Box, X, Z, Y, Z], \\
+    \variable{occ} &= [\{ 0, 4 \}, \{ 1, 6 \}, \{ 5, 7 \}, \{ 2, 3 \}], \\
+    \variable{intros} &= [0, 1, 5],
+  \end{align*}
+  where the $\Box$'s correspond to the conjunction node.
 \end{example}
@@
 
-We add a number of redundant constraints to make search more efficient.
-
-\begin{constraint}
+We add a number of redundant constraints to make search more efficient. First,
+we can formally state that the positions occupied by different terms must be
+different:
+
+\begin{constraint} \label{constraint:all_diff}
   For $u \ne v \in \constants{} \cup \variables{} \cup \{ \Box \}$,
@@
 \end{constraint}
+
+The reason why we used zero to represent a variable not being introduced is so
+that we could efficiently rephrase \cref{constraint:all_diff} for the
+$\variable{intros}$ array:
 
@@
 
+We can also add another link between $\variable{intros}$ and $\variable{occ}$
+that essentially says that the smallest element of a set is an element of the
+set:
+
 \begin{constraint}
@@
 
+Finally, we define an auxiliary set variable to act as a set of possible values
+that $\variable{intros}$ can take:
+
 \begin{definition}
-  We define an auxiliary set variable
-  \[
-    \variable{potentialIntros} \subseteq \{ 0, \dots, N \}
-  \]
-  to act as a set of possible values that $\variable{intros}$ can take,
-  i.e., for $v \in \variables{}$, $\variable{intros}[v] \in
-  \variable{potentialIntros}$.
-\end{definition}
+  Let $\variable{potentials} \subseteq \{ 0, \dots, N \}$ be such that for $v
+  \in \variables{}$, $\variable{intros}[v] \in \variable{potentials}$.
+\end{definition}
+
+Using this new variable, we can easily add a constraint saying that
+non-predicate nodes in the tree representation of a clause cannot have variables
+as arguments:
 
@@
   \[
-    S = \{ \maxArity{} \times (i + 1) + j + 1 \mid j = 0, \dots, \maxArity{} - 1.
-    \}
+    S = \{ \maxArity{} \times (i + 1) + j + 1 \mid j = 0, \dots, \maxArity{} - 1
+    \}.
   \]
   If $\variable{values}[i].\variable{name} \not\in \predicates{}$, then
-  \[
-    \variable{potentialIntros} \cap S = \emptyset.
-  \]
-\end{constraint}
-
-In simpler terms, \cref{constraint:potentialIntroductions} says that if a node
-in the tree representation of a clause represents something other than a
-predicate, then a variable cannot be introduced as one of its `arguments'.
+  $\variable{potentials} \cap S = \emptyset$.
+\end{constraint}
 
@@
 \end{definition}
+
+Labelling the edges as positive/negative will be immaterial for predicate
+independence, but the same graph will play a crucial role in negative cycle
+detection in the next section.
 
@@
   \]
-  The predicate dependency graph (without positivity/negativity) defined by
-  \cref{def:adjacency_matrix} is represented in
+  The predicate dependency graph (without positivity/negativity)---as defined by
+  \cref{def:adjacency_matrix}---is represented in
   \cref{fig:dependencies_matrix,fig:dependencies2}.
@@
 \section{NEGATIVE CYCLES} \label{sec:cycles}
-% TODO: My paper has two slightly different graphs with the same name.
-% TODO: NB: the set of decision variables for this constraint must exclude all
-% arguments.
-% TODO: maybe move some of the definition 10 here.
 
@@
 % to find all solutions).
-% Mention the random heuristic. Mention that restarting gives better randomness,
-% but duplicates become possible.
-% TODO: the number of predicates is also important.
+% On the other hand, with restarts, duplicates become possible.
+% TODO: the number of predicates is also important for performance.
 

### 2020-01-25 paper/paper.tex
Freshly baked abstract

@@
 
-\begin{abstract} % TODO: rewrite
-  We present a novel approach to generate random logic programs using constraint
-  programming. The constraint programming approach to the problem has a major
+\begin{abstract}
+  We present a novel approach to generating random logic programs and
+  random probabilistic logic programs using constraint programming. The
+  generated programs are useful in empirical testing of inference algorithms,
+  random data generation, and program learning. This approach has a major
   advantage in that one can easily add additional conditions for the generated
-  programs. Some of these conditions can be expressed using constraints native to
-  the constraint solver Choco \citep{choco}, while novel propagation and entailment
-  checking algorithms have been developed for ensuring independence and/or
-  conditional independence amongst predicates. A constraint programming approach
-  also benefits from many years of research into efficient constraint propagation
-  algorithms which makes it likely that our model can generate larger programs
-  relatively quickly.
+  programs. As an example of this, we introduce a new constraint for predicate
+  independence with efficient propagation and entailment algorithms, allowing
+  one to generate programs that have a certain independence structure. In order
+  to generate valid probabilistic logic programs, we also present a new
+  constraint for negative cycle detection. Finally, we provide a combinatorial
+  argument for correctness and describe how the parameters of the model affect
+  the empirical difficulty of the program generation task.
 \end{abstract}
@@
 
-% TODO: import related work from my proposal
-
-Motivation:
-\begin{itemize}
-\item Empirical testing of inference algorithms.
-\item Generating random programs that generate random data.
-  %For example, enforcing that the decision is independent of gender.
-\item Learning: how this can be used for (targeted) learning, when (atomic)
-  probabilities can be assigned based on counting and we can have extra
-  constraints. A more primitive angle: generate structures, learn weights.
-\end{itemize}
-
-%TODO: define all the relevant terminology from logic and constraint
-% programming: predicates ,arities, (logic) variables, constants, clauses, atoms,
-% heads, bodies, formulas.
-% CP: decision variables, constraints. So the word 'variable' has two meanings.
-% TODO: need to introduce the idea of predicate independence
-
-We say that a constraint variable is \emph{(fully) determined} if its domain (at
-the given moment in the execution) has exactly one value.
-
-A \emph{(logic) program} is a multiset of clauses. Given a program
-$\mathscr{P}$, a \emph{subprogram} $\mathscr{R}$ of $\mathscr{P}$ is a subset of
-the clauses of $\mathscr{P}$ and is denoted by $\mathscr{R} \subseteq
+How confidently can we claim that an algorithm works well if it is only tested
+on a couple types of problems? Perhaps the `inferior' algorithm is actually
+better in some specific circumstances. Perhaps there are identifiable
+types of inputs that make every algorithm default to exponential behaviour
+that could be easily overcome with the right strategy. At present, most
+inference algorithms for probabilistic logic programs are only evaluated on 1--4
+different problems: sometimes just a single network
+\citep{DBLP:journals/tplp/KimmigDRCR11,DBLP:journals/corr/abs-1112-3785,DBLP:conf/iclp/KimmigCRDR08},
+sometimes two
+\citep{DBLP:journals/corr/abs-1009-3798,DBLP:conf/ecai/BruynoogheMKGVJR10} or
+four networks \citep{DBLP:conf/ijcai/VlasselaerBKMR15} coming from a range
+of areas such as social networks and citation/genetic/biological data sets. In
+order to better understand the strengths and weaknesses of these algorithms,
+along with real data they should also be evaluated on a range of synthetic
+problems that accurately represent the potential complexities that have to be
+handled by a well-designed inference algorithm. Furthermore, random logic
+program generators can be useful in combination with methods that generate
+random data with probabilistic logic programs \citep{DBLP:conf/soict/Dries15}
+and can be used as a component of learning.
+
+Most current approaches to generating random logic programs are quite
+restrictive, e.g., limited to clauses with only two literals
+\citep{DBLP:conf/lpnmr/NamasivayamT09}, or to clauses of the form $a \gets \neg
+b$ \citep{DBLP:journals/tocl/WenWSL16}, but others are more expressive, e.g.,
+defining a program only by the (maximum) number of atoms in the body and the
+total number of rules \citep{DBLP:conf/iclp/ZhaoL03,zhao2004answer}. We
+introduce a way to generate random logic programs using a constraint solver such
+as Choco \citep{choco}. The same model can generate both probabilistic programs
+directly in the syntax of ProbLog \citep{DBLP:conf/ijcai/RaedtKT07} as well as
+non-probabilistic Prolog programs. For generated probabilistic programs to be
+valid, we use a custom constraint to detect negative cycles (as described in
+\cref{sec:cycles}). A major advantage of our constraint-based approach is that
+one can easily add additional constraints to the model. To demonstrate that, in
+\cref{sec:independence} we present a custom constraint with propagation and
+entailment algorithms that can ensure predicate independence.
+\cref{sec:counting} also presents a combinatorial argument for correctness,
+where we produce combinatorial expressions that count the number of programs
+that the model should produce for various parameter values. Finally,
+\cref{sec:experiments} shows how the model scales when tasked with producing
+more complicated programs and identifies the relationships between parameter
+values and the empirical hardness of the program generation task.
+
+\subsection{PRELIMINARIES}
+
+The basic primitives of logic programs are \emph{constants}, \emph{(logic)
+  variables}, and \emph{predicates}. Each predicate has an \emph{arity} that
+defines the number of terms that it can applied to. A \emph{term} is either a
+variable or a constant, and an \emph{atom} is a predicate of arity $n$ applied
+to $n$ terms. A \emph{formula} is a grammatically-valid expression that connects
+atoms using conjunction ($\land$), disjunction ($\lor$), and negation ($\neg$).
+A \emph{clause} is a pair of a \emph{head} (which is an atom) and a \emph{body}
+(which is a formula). A \emph{(logic) program} is a multiset of clauses. Given a
+program $\mathscr{P}$, a \emph{subprogram} $\mathscr{R}$ of $\mathscr{P}$ is a
+subset of the clauses of $\mathscr{P}$ and is denoted by $\mathscr{R} \subseteq
 \mathscr{P}$.
 
-We will often use $\Box$ as a special domain value indicating a `disabled'
-(i.e., fixed and ignored) part of the model. We write $\arrayd{a}{b}{c}$ to mean
-that $\variable{a}$ is an array of variables of length $b$ such that each
-element of $\variable{a}$ has domain $c$. Similarly, we write $\arrayt{a}{b}{c}$
-to denote an array $\variable{a}$ of length $b$ such that each element of
-$\variable{a}$ has type $\variable{c}$. All constraint variables in the model
-are integer variables, but, e.g., if the integer $i$ refers to a logical
-variable $X$, we will use $i$ and $X$ interchangeably. All indices start at
+In the world of constraint satisfaction, we also have \emph{(constraint)
+  variables}, each with its own \emph{domain}, whose values are restricted using
+\emph{constraints}. All constraint variables in the model are integer or set
+variables, however, if an integer refers to a logical construct
+(e.g., a logical variable or a constant), we will make no distinction between
+the two and often use names of logical constructs to refer to the underlying
+integers. We say that a constraint variable is \emph{(fully) determined} if its
+domain (at the given moment in the execution) has exactly one value. We will
+often use $\Box$ as a special domain value to indicate a `disabled' (i.e., fixed
+and ignored) part of the model. We write $\arrayd{a}{b}{c}$ to mean that
+$\variable{a}$ is an array of variables of length $b$ such that each element of
+$\variable{a}$ has domain $c$. Similarly, we write $\arrayt{a}{b}{c}$ to denote
+an array $\variable{a}$ of length $b$ such that each element of $\variable{a}$
+has type $\variable{c}$. Finally, we assume that all arrays start with index
 zero.
-
-We also use Choco~4.10.2 \citep{choco}. This works with both Prolog
-\citep{DBLP:books/daglib/0041598} and ProbLog \citep{DBLP:conf/ijcai/RaedtKT07}.
-%Tested with SWI-Prolog \citep{DBLP:journals/tplp/WielemakerSTL12}.
 
@@
 
-\section{HEADS OF CLAUSES}
+\section{HEADS OF CLAUSES} \label{sec:heads}
 
@@
 
-\section{COUNTING PROGRAMS}
+\section{COUNTING PROGRAMS} \label{sec:counting}
 
@@
   \emph{dependencies} of $\mathsf{P}$ is the smallest set $D_{\mathsf{P}}$ such
-  that:
-  \begin{itemize}
-  \item $\mathsf{P} \in D_{\mathsf{P}}$,
-  \item for every $\mathsf{Q} \in D_{\mathsf{P}}$, all direct predecessors of
-    $\mathsf{Q}$ in $G_{\mathscr{P}}$ are in $D_{\mathsf{P}}$.
-  \end{itemize}
+  that $\mathsf{P} \in D_{\mathsf{P}}$, and, for every $\mathsf{Q} \in
+  D_{\mathsf{P}}$, all direct predecessors of $\mathsf{Q}$ in $G_{\mathscr{P}}$
+  are in $D_{\mathsf{P}}$.
 \end{definition}
@@
 
-\begin{algorithm}
+\begin{algorithm}[h]
   \LinesNumbered
@@
   \]
-  The predicate dependency graph (without positivity/negativity)---as defined by
-  \cref{def:adjacency_matrix}---is represented in
+  The predicate dependency graph without positivity/negativity (as defined in
+  \cref{def:adjacency_matrix}) is represented in
   \cref{fig:dependencies_matrix,fig:dependencies2}.
@@
 
-\section{EMPIRICAL PERFORMANCE}
+\section{EMPIRICAL PERFORMANCE} \label{sec:experiments}
+
+\begin{figure}
+  \centering
+  \input{impact.tex}
+  \caption{The mean number of nodes in the binary search tree for each value of
+    each experimental parameter. Note that the horizontal axis is on a $\log_2$
+    scale.}
+  \label{fig:impact}
+\end{figure}
+
+\begin{figure*}
+  \centering
+  \input{phase_transition.tex}
+  \caption{The distribution of the number of nodes in the binary search tree as
+    a function of the number of independent pairs of predicates for
+    $|\predicates| = 8$. Significant outliers are hidden, the dots denote mean
+    values, and the vertical axis is on a $\log_{10}$ scale.}
+  \label{fig:phase_transition}
+\end{figure*}
 
@@
 
-\begin{figure}
-  \centering
-  \input{impact.tex}
-  \caption{The mean number of nodes in the binary search tree for each value of
-    each experimental parameter. Note that the horizontal axis is on a $\log_2$
-    scale.}
-  \label{fig:impact}
-\end{figure}
-
 In \cref{fig:impact}, we plot how the mean number of nodes in the binary search
@@
 cycle or a forbidden dependence, and such trees become more common as the number
-of nodes increases.
-
-\begin{figure*}
-  \centering
-  \input{phase_transition.tex}
-  \caption{The distribution of the number of nodes in the binary search tree as
-    a function of the number of independent pairs of predicates for
-    $|\predicates| = 8$. Significant outliers are hidden, the dots denote mean
-    values, and the vertical axis is on a $\log_{10}$ scale.}
-  \label{fig:phase_transition}
-\end{figure*}
+of nodes increases. Likewise, a higher number of predicates complicates the
+situation as well.
 
@@
 % On the other hand, with restarts, duplicates become possible.
-% TODO: the number of predicates is also important for performance.
 
@@
 % TODO: the positive side (what did we achieve?)
+%We were able to design an efficient model
 
@@
 
+\newpage
+
 \renewcommand{\bibsection}{\subsubsection*{References}}

### 2020-01-29 paper/paper.tex
Finishing touches

@@
 
-\author{} % LEAVE BLANK FOR ORIGINAL SUBMISSION.
-          % UAI  reviewing is double-blind.
-
-% The author names and affiliations should appear only in the accepted paper.
-%
-%\author{ {\bf Harry Q.~Bovik\thanks{Footnote for author to give an
-%alternate address.}} \\
-%Computer Science Dept. \\
-%Cranberry University\\
-%Pittsburgh, PA 15213 \\
-%\And
-%{\bf Coauthor}  \\
-%Affiliation          \\
-%Address \\
-%\And
-%{\bf Coauthor}   \\
-%Affiliation \\
-%Address    \\
-%(if needed)\\
+\author{}
+
+%\author{ {\bf Paulius Dilkas} \\
+%School of Informatics \\
+%University of Edinburgh \\
+%Edinburgh, United Kingdom \\
 %}
@@
 
-\subsection{PRELIMINARIES}
+\section{PRELIMINARIES}
 
@@
 
-\subsection{PARAMETERS}
+\subsection{PARAMETERS OF THE MODEL}
 
@@
 non-probabilistic programs, each clause is paired with a probability which is
-randomly selected from a given list (which is our last parameter). For
+randomly selected from a given list (i.e., our last parameter). For
 generating non-probabilistic programs, one can set this list equal to $\{ 1 \}$.
@@
 Here, $\top$ is the value we use for the remaining one-node trees. The
-elements of the $\variable{values}$ array are \emph{nodes}.
+elements of the $\variable{values}$ array are nodes:
 
@@
 
-Furthermore, we can use \cref{constr:arity} again to disable the extra
+Furthermore, we can use \cref{constr:arity} to again disable the extra
 arguments.
@@
 
-Given any clause, we can permute the variables in it without changing the
-meaning of the clause or the entire program. Thus, we want to fix the order of
-variables to eliminate unnecessary symmetries. Informally, we can say that
-variable $X$ goes before variable $Y$ if its first occurrence in either the head
-or the body of the clause is before the first occurrence of $Y$. Note that the
-constrains described in this section only make sense if $|\variables| > 1$. Also
-note that all definitions and constraints here are on a per-clause basis.
+Given any clause, we can permute the variables in that clause without changing
+the meaning of the clause or the entire program. Thus, we want to fix the order
+of variables to eliminate unnecessary symmetries. Informally, we can say that
+variable $X$ goes before variable $Y$ if the first occurrence of $X$ in either
+the head or the body of the clause is before the first occurrence of $Y$. Note
+that the constrains described in this section only make sense if $|\variables| >
+1$. Also note that all definitions and constraints here are on a per-clause
+basis.
 
@@
 
-  Then we can use the $\variable{setsIntsChanneling}$ constraint
-  to define $\variable{occ}[|\constants{}| + |\variables{}| + 1]$ as an
-  array of subsets of $\{ 0, \dots, N-1 \}$ such that for all $i = 0, \dots, N
-  - 1$, and $t \in \constants{} \cup \variables{} \cup \{ \Box \}$,
+  Then we can use a channeling constraint to define
+  $\variable{occ}[|\constants{}| + |\variables{}| + 1]$ as an array of subsets
+  of $\{ 0, \dots, N-1 \}$ such that for all $i = 0, \dots, N - 1$, and $t \in
+  \constants{} \cup \variables{} \cup \{ \Box \}$,
   \[
@@
 
-Here, a value of zero means that the variable does not occur in the clause. We
-want to use specifically zero for this so that we could use
-\cref{constraint:diffbutzero} later. Because of this choice, the definition of
+Here, a value of zero means that the variable does not occur in the clause. The
+reason why we want to use specifically zero for this will become clear with
+\cref{constraint:diffbutzero}. Because of this choice, the definition of
 $\variable{intros}$ shifts all indices by one. Lastly, we add the constraint
@@
 
-The reason why we used zero to represent a variable not being introduced is so
-that we could efficiently rephrase \cref{constraint:all_diff} for the
-$\variable{intros}$ array:
+The reason why we used zero to represent an unused variable is so that we could
+efficiently rephrase \cref{constraint:all_diff} for the $\variable{intros}$
+array:
 
@@
 
-Using this new variable, we can easily add a constraint saying that
-non-predicate nodes in the tree representation of a clause cannot have variables
-as arguments:
+Using this new variable, we can add a constraint saying that non-predicate nodes
+in the tree representation of a clause cannot have variables as arguments:
 
@@
     \mathsf{sibling}(X, Y) &\gets \mathsf{parent}(X, Z) \land \mathsf{parent}(Y, Z), \nonumber \\
-    \mathsf{father}(X, Y) &\gets \mathsf{parent}(X, Y) \land \neg\mathsf{mother}(X, Y). \label[clause]{eq:example_clause}
+    \mathsf{father}(X, Y) &\gets \mathsf{parent}(X, Y) \land \neg\mathsf{mother}(X, Y) \label[clause]{eq:example_clause}
   \end{align}
@@
 We can now add a constraint to define an adjacency matrix for the predicate
-dependency graph but without positivity/negativity.
+dependency graph but without positivity/negativity:
 
@@
 the independence of two predicates $p_1$ and $p_2$. First, we separately
-calculate all dependencies of $p_1$ and $p_2$, and look at the set $D$ of
+calculate all dependencies of $p_1$ and $p_2$ and look at the set $D$ of
 dependencies that $p_1$ and $p_2$ have in common. If there are none, then the
@@
 that prevents the $\AlmostDetermined$ from becoming a $\Determined$ cannot
-exist--\cref{line:propagation_condition,line:propagation_result} take care of
-that.
+exist--\cref{line:propagation_condition,line:propagation_result} handle this
+possibility.
 
@@
 almost-determined dependencies. It starts by establishing the predicate $p$
-itself as a dependence and continues to add dependencies of dependencies until
+itself as a dependency and continues to add dependencies of dependencies until
 the set $D$ stabilises. For each dependency $d \in D$, we look at the in-links
@@
   \[
-    D = \{ \mathsf{father}, \mathsf{mother}, \mathsf{parent}, \mathsf{sibling}
-    \}.
+    D_\Box = \{ \mathsf{father}, \mathsf{mother}, \mathsf{parent},
+    \mathsf{sibling} \}.
   \]
@@
   zero, eliminating the potential edge from $\mathsf{parent}$ to
-  $\mathsf{mother}$. This also eliminates $\mathsf{mother}$ from $D$, and,
+  $\mathsf{mother}$. This also eliminates $\mathsf{mother}$ from $D_\Box$, and,
   although some undetermined variables remain, this is enough to make
@@
 negative probabilities \citep{DBLP:journals/ijar/BuchmanP17}. Ideally, we would
-like to design a constraint for that similar to the constraint for independence
-in the previous section. However, the difficulty with creating a propagation
-algorithm for negative cycles is that there seems to be no good way to extend
-\cref{def:adjacency_matrix} so that the adjacency matrix captures
+like to design a constraint for negative cycles similar to the constraint for
+independence in the previous section. However, the difficulty with creating a
+propagation algorithm for negative cycles is that there seems to be no good way
+to extend \cref{def:adjacency_matrix} so that the adjacency matrix captures
 positivity/negativity. Thus, we settle for an entailment algorithm with no
@@
 If the algorithm finds a negative cycle in this fully-determined part of the
-program, then it is unavoidable and we must return \textsc{false}. If there was
-no negative cycle and the entire program is determined-enough to contribute to
-the graph, then there cannot be any negative cycles. In all other cases, it
-is too early to tell.
+program, then we must return \textsc{false}. If there was no negative cycle and
+the entire program is (sufficiently) determined, then there cannot be any
+negative cycles. In all other cases, it is too early to tell.
 
@@
     a function of the number of independent pairs of predicates for
-    $|\predicates| = 8$. Significant outliers are hidden, the dots denote mean
-    values, and the vertical axis is on a $\log_{10}$ scale.}
+    $|\predicates| = 8$. Outliers are hidden, the dots denote mean values, and
+    the vertical axis is on a $\log_{10}$ scale.}
   \label{fig:phase_transition}
@@
 what parameter values make the constraint satisfaction problem harder. For these
-experiments, we use Choco~4.10.2 \citep{choco} with Java~8 on a personal
-computer with an Intel Core i5-8250U processor and Arch Linux 5.4.12-arch1-1
-operating system. For $|\predicates{}|$, $|\variables{}|$, $|\constants{}|$,
-$\maxNumNodes{}$, and $\maxNumClauses{} - |\predicates{}|$ (i.e., the number of
-clauses in addition to the mandatory $|\predicates{}|$ clauses), we assign all
-combinations of 1, 2, 4, 8. $\maxArity{}$ is assigned to values 1--4. For each
-$|\predicates{}|$, we also iterate over all possible numbers of independent
-pairs of predicates, ranging from 0 up to $\binom{|\predicates{}|}{2}$. For each
-combination of the above-mentioned parameters, we pick ten random pairs of:
-$\arities{}$ (such that $\maxArity{}$ occurs at least once) and the required
-number of independent pairs (without repetition). We then run the solver with a
-\SI{60}{\second} timeout.
+experiments, we use Choco~4.10.2 \citep{choco} with Java~8 on a computer with an
+Intel Core i5-8250U processor. For $|\predicates{}|$, $|\variables{}|$,
+$|\constants{}|$, $\maxNumNodes{}$, and $\maxNumClauses{} - |\predicates{}|$
+(i.e., the number of clauses in addition to the mandatory $|\predicates{}|$
+clauses), we assign all combinations of 1, 2, 4, 8. $\maxArity{}$ is assigned to
+values 1--4. For each $|\predicates{}|$, we also iterate over all possible
+numbers of independent pairs of predicates, ranging from 0 up to
+$\binom{|\predicates{}|}{2}$. For each combination of the above-mentioned
+parameters, we pick ten random ways to assign arities to predicates (such that
+$\maxArity{}$ occurs at least once) and ten random combinations of independent
+pairs. We then run the solver with a \SI{60}{\second} timeout.
 
@@
 can be impossible to fill with predicates without creating either a negative
-cycle or a forbidden dependence, and such trees become more common as the number
+cycle or a forbidden dependency, and such trees become more common as the number
 of nodes increases. Likewise, a higher number of predicates complicates the
@@
 
-% TODO: the positive side (what did we achieve?)
-%We were able to design an efficient model
-
-One major question that was not addressed in this paper is that of logical
-equivalence. We eliminated permutation symmetries and constrained variable usage
-so that the same `functionality' is always assigned to the same variable, but
-syntactically different logical formulas are always treated as being different.
-For example, all three of these formulas are logically equivalent but
-syntactically different: $\neg(\mathsf{P}(X) \lor \mathsf{Q}(X))$,
-$\neg\mathsf{P}(X) \land \neg\mathsf{Q}(X)$, and $\neg\mathsf{Q}(X) \land
-\neg\mathsf{P}(X)$. While there are many situations where one would prefer to
-treat logically equivalent formulas as symmetries that should be eliminated,
-there are also situations where we do care about enumerating different ways to
-express the same probability distribution or knowledge base. For instance,
-one could look for the `best' logically equivalent formula, or investigate
-whether some formulas result in faster inference than others.
+We were able to design an efficient model for generating both logic programs and
+probabilistic logic programs. The model avoids unnecessary symmetries, generates
+valid programs, and can ensure predicate independence. Note that there is one
+kind of symmetries not handled by our model, i.e., logical equivalence. For
+example, all three of these formulas are logically equivalent but syntactically
+different: $\neg(\mathsf{P}(X) \lor \mathsf{Q}(X))$, $\neg\mathsf{P}(X) \land
+\neg\mathsf{Q}(X)$, and $\neg\mathsf{Q}(X) \land \neg\mathsf{P}(X)$. While there
+are many situations where one would prefer to treat logically equivalent
+formulas as symmetries that should be eliminated, there are also situations
+where we do care about enumerating different ways to express the same
+probability distribution or knowledge base. For instance, one could look for the
+`best' logically equivalent formula, or investigate whether some formulas result
+in faster inference than others.
 
@@
 as generated by our model, although it is not obvious how such a
-probability distribution could be characterised. One example of a clear bias
-exhibited by our model is that of complexity over simplicity, i.e., if a tree
-that represents the body of a clause can have up to $\maxNumNodes{}$
-nodes---because the number of possible trees with $n$ nodes grows with $n$---it
-is much more likely to have $\maxNumNodes{}$ or $\maxNumNodes{} - 1$ nodes than,
-e.g., one or two.
-
-\subsubsection*{Acknowledgements}
+probability distribution could be characterised.% One example of a clear bias
+%exhibited by our model is that of complexity over simplicity, i.e., if a tree
+%that represents the body of a clause can have up to $\maxNumNodes{}$
+%nodes---because the number of possible trees with $n$ nodes grows with $n$---it
+%is much more likely to have $\maxNumNodes{}$ or $\maxNumNodes{} - 1$ nodes than,
+%e.g., one or two.
+
+%\subsubsection*{Acknowledgements}
 
 % The author would like to thank Vaishak Belle for his comments.
-This work was supported by the EPSRC Centre for Doctoral Training in Robotics
-and Autonomous Systems, funded by the UK Engineering and Physical Sciences
-Research Council (grant EP/S023208/1).
-
-\newpage
+%This work was supported by the EPSRC Centre for Doctoral Training in Robotics
+%and Autonomous Systems, funded by the UK Engineering and Physical Sciences
+%Research Council (grant EP/S023208/1).
 

### 2020-01-29 paper/phase_transition.tex
Finishing touches

@@
-% Created by tikzDevice version 0.12.3 on 2020-01-21 13:23:35
+% Created by tikzDevice version 0.12.3 on 2020-01-25 19:15:40
 % !TEX encoding = UTF-8 Unicode
@@
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (433.62,144.54);
-\definecolor{drawColor}{RGB}{255,255,255}
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( -0.00,  0.00) rectangle (433.62,144.54);
-\end{scope}
-\begin{scope}
 \path[clip] ( 22.14, 19.53) rectangle (430.12,141.04);
-\definecolor{fillColor}{gray}{0.92}
-
-\path[fill=fillColor] ( 22.14, 19.53) rectangle (430.12,141.04);
-\definecolor{drawColor}{RGB}{255,255,255}
+\definecolor{drawColor}{gray}{0.92}
 
@@
 \path[clip] (  0.00,  0.00) rectangle (433.62,144.54);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 20.39, 19.53) --
-	( 22.14, 19.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 20.39,100.38) --
-	( 22.14,100.38);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (433.62,144.54);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.42, 17.78) --
-	( 35.42, 19.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 49.04, 17.78) --
-	( 49.04, 19.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 62.67, 17.78) --
-	( 62.67, 19.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 76.29, 17.78) --
-	( 76.29, 19.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 89.91, 17.78) --
-	( 89.91, 19.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] (103.53, 17.78) --
-	(103.53, 19.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] (117.15, 17.78) --
-	(117.15, 19.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] (130.78, 17.78) --
-	(130.78, 19.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] (144.40, 17.78) --
-	(144.40, 19.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] (158.02, 17.78) --
-	(158.02, 19.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] (171.64, 17.78) --
-	(171.64, 19.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] (185.26, 17.78) --
-	(185.26, 19.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] (198.89, 17.78) --
-	(198.89, 19.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] (212.51, 17.78) --
-	(212.51, 19.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] (226.13, 17.78) --
-	(226.13, 19.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] (239.75, 17.78) --
-	(239.75, 19.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] (253.37, 17.78) --
-	(253.37, 19.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] (267.00, 17.78) --
-	(267.00, 19.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] (280.62, 17.78) --
-	(280.62, 19.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] (294.24, 17.78) --
-	(294.24, 19.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] (307.86, 17.78) --
-	(307.86, 19.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] (321.48, 17.78) --
-	(321.48, 19.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] (335.11, 17.78) --
-	(335.11, 19.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] (348.73, 17.78) --
-	(348.73, 19.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] (362.35, 17.78) --
-	(362.35, 19.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] (375.97, 17.78) --
-	(375.97, 19.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] (389.59, 17.78) --
-	(389.59, 19.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] (403.22, 17.78) --
-	(403.22, 19.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] (416.84, 17.78) --
-	(416.84, 19.53);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (433.62,144.54);
 \definecolor{drawColor}{gray}{0.30}

### 2020-02-11 paper/paper.tex
An appendix with example programs

@@
 \newcommand{\arrayd}[3]{\variable{{#1}[}{#2}\variable{]} \in {#3}}
-\newcommand{\arrayt}[3]{\variable{{#3}[}{#2}\variable{] {#1}}}
+
+% 1=name, 2=length, 3=type
+\newcommand{\arrayt}[3]{\variable{{#3}} : \variable{{#1}[}{#2}\variable{]}}
 
@@
 \DeclareMathOperator{\AlmostDetermined}{\Gamma}
+\DeclareMathOperator{\getss}{\mathtt{:-}}
 
@@
 How confidently can we claim that an algorithm works well if it is only tested
-on a couple types of problems? Perhaps the `inferior' algorithm is actually
-better in some specific circumstances. Perhaps there are identifiable
+on a few types of problems? Perhaps the `inferior' algorithm is actually
+better in some specific circumstances. Maybe there are identifiable
 types of inputs that make every algorithm default to exponential behaviour
 that could be easily overcome with the right strategy. At present, most
-inference algorithms for probabilistic logic programs are only evaluated on 1--4
-different problems: sometimes just a single network
+inference algorithms for probabilistic logic programs are only evaluated on at
+most four different problems: sometimes just a single network
 \citep{DBLP:journals/tplp/KimmigDRCR11,DBLP:journals/corr/abs-1112-3785,DBLP:conf/iclp/KimmigCRDR08},
@@
 \citep{DBLP:journals/corr/abs-1009-3798,DBLP:conf/ecai/BruynoogheMKGVJR10} or
-four networks \citep{DBLP:conf/ijcai/VlasselaerBKMR15} coming from a range
-of areas such as social networks and citation/genetic/biological data sets. In
+four networks \citep{DBLP:conf/ijcai/VlasselaerBKMR15} coming from a range of
+areas such as social networks and citation/genetic/biological data sets. In
 order to better understand the strengths and weaknesses of these algorithms,
@@
 
-Most current approaches to generating random logic programs are quite
-restrictive, e.g., limited to clauses with only two literals
+Most current approaches to generating random logic programs are restrictive,
+e.g., limited to clauses with only two literals
 \citep{DBLP:conf/lpnmr/NamasivayamT09}, or to clauses of the form $a \gets \neg
@@
 defining a program only by the (maximum) number of atoms in the body and the
-total number of rules \citep{DBLP:conf/iclp/ZhaoL03,zhao2004answer}. We
-introduce a way to generate random logic programs using a constraint solver such
-as Choco \citep{choco}. The same model can generate both probabilistic programs
-directly in the syntax of ProbLog \citep{DBLP:conf/ijcai/RaedtKT07} as well as
+total number of rules \citep{DBLP:conf/iclp/ZhaoL03}. We introduce a way to
+generate random logic programs using a constraint solver such as Choco
+\citep{choco}. The same model can generate both probabilistic programs directly
+in the syntax of ProbLog \citep{DBLP:conf/ijcai/RaedtKT07} as well as
 non-probabilistic Prolog programs. For generated probabilistic programs to be
@@
 values and the empirical hardness of the program generation task.
+ % TODO (Fazl): % Could you provide a motivating example? It % might be useful to engage readers.
+
+% TODO (Vaishak):
+Overall, [main] contributions are concerned purely with logic programming-based
+languages and frameworks, which capture a major fragment of statistical
+relational learning \citep{DBLP:series/synthesis/2016Raedt}.
+However, since probabilistic logic programming [languages] are closely related
+to other [endeavours] in machine learning, including (imperative) probabilistic
+programming (e.g., see discussions in \citep{DBLP:journals/ml/RaedtK15}), our
+results [may] provide the [footing] to explore broader questiosn on generating
+and testing programs/algorithms in machine learning.
 
@@
 negative cycles (see \cref{sec:cycles}) and enforcing predicate independence
-(see \cref{sec:independence}), so a list of independent pairs of predicates is
+(see \cref{sec:independence}), so a set of independent pairs of predicates is
 another parameter. Since this model can generate probabilistic as well as
 non-probabilistic programs, each clause is paired with a probability which is
-randomly selected from a given list (i.e., our last parameter). For
+randomly selected from a given multiset (i.e., our last parameter). For
 generating non-probabilistic programs, one can set this list equal to $\{ 1 \}$.
@@
 \end{constraint}
+% TODO (Fazl): explain what h is.
 
@@
 
+% TODO (Fazl): the first four words sound odd. Rephrase.
 It remains to constrain the forest represented by the $\variable{structure}$
@@
 a body of a clause is the sum total of arities of all predicates in the body.
+% TODO (Vaishak, last sentence): move to footnote and add "Since the [details] of
+% this empirical investigation are not crucial to the thrust of this paper, we
+% will [detail] this in an extendedd technical report."
 
@@
 
+% TODO (Vaishak):
+% Now we add a theorem that states that the programs generated by the algorithm,
+% regardless of whether they involve negative cycles or not, are well-defined?
+% That is, in the non-probabilistic case, they are satisfiable, and, in the
+% probabilistic case, for both negative cycles & without, they induce programs
+% that are satisfiable + well-defined measure on the set of satisfying
+% assignments [proofs in the appendix?]
+
 \section{EMPIRICAL PERFORMANCE} \label{sec:experiments}
@@
 \section{CONCLUSIONS}
+% TODO (Fazl): equations and 'provides no such guarantees' sound more like
+% future work / limitation section. Make it sound more positive.
 
@@
 
+% TODO: We can do the same thing for predicates within the body of a clause that
+% we do with variables, i.e., predicates within a clause are permutable (except
+% for the head predicate), so we can have a set of 'allowed' predicates.
+
 %\subsubsection*{Acknowledgements}
 
-% The author would like to thank Vaishak Belle for his comments.
-%This work was supported by the EPSRC Centre for Doctoral Training in Robotics
-%and Autonomous Systems, funded by the UK Engineering and Physical Sciences
-%Research Council (grant EP/S023208/1).
+%This work was supported by the EPSRC Centre for Doctoral Training in
+%Robotics and Autonomous Systems, funded by the UK Engineering and Physical
+%Sciences Research Council (grant EP/S023208/1).
 
@@
 \bibliography{paper}
+% TODO: logic programs don't have disjunctions. Is there an easy way to
+% eliminate them?
+
+\appendix
+\section{EXAMPLE PROGRAMS}
+
+In this appendix, we provide examples of probabilistic logic programs generated
+by various combinations of parameters. In all cases, we use $\{ 0.1, 0.2, \dots,
+0.9, 1, 1, 1, 1, 1\}$ as the multiset of probabilities. Each clause is written
+on a separate line and ends with a full stop. The head and the body of each
+clause are separated with \texttt{:-} (instead of $\gets$). The probability of
+each clause is prepended to the clause, using \texttt{::} as a separator.
+Probabilities equal to one and empty bodies of clauses can be omitted.
+Conjunction, disjunction, and negation are denoted by commas, semicolons, and
+`\texttt{\textbackslash+}', respectively. Parentheses are used to demonstrate
+precedence, although many of them are redundant.
+
+By setting $\predicates{} = [\texttt{p}]$, $\arities{} = [1]$, $\variables{} =
+\{ \texttt{X} \}$, $\constants{} = \emptyset$, $\maxNumNodes{} = 4$, and
+$\maxNumClauses{} = 1$, we get fifteen one-line programs, five of which are
+without negative cycles (denoted by `+'). Only the last program has no cycles at
+all.
+
+\begin{itemize}
+\item
+\begin{verbatim}
+0.5 :: p(X) :- (\+(p(X))), (p(X)).
+\end{verbatim}
+\item
+\begin{verbatim}
+0.8 :: p(X) :- (\+(p(X))); (p(X)).
+\end{verbatim}
+\item[+]
+\begin{verbatim}
+0.8 :: p(X) :- (p(X)); (p(X)).
+\end{verbatim}
+\item[+]
+\begin{verbatim}
+0.7 :: p(X) :- (p(X)), (p(X)).
+\end{verbatim}
+\item
+\begin{verbatim}
+0.6 :: p(X) :- (p(X)), (\+(p(X))).
+\end{verbatim}
+\item
+\begin{verbatim}
+p(X) :- (p(X)); (\+(p(X))).
+\end{verbatim}
+\item[+]
+\begin{verbatim}
+0.1 :: p(X) :- (p(X)); (p(X)); (p(X)).
+\end{verbatim}
+\item[+]
+\begin{verbatim}
+0.8 :: p(X) :- (p(X)), (p(X)), (p(X)).
+\end{verbatim}
+\item
+\begin{verbatim}
+p(X) :- \+(p(X)).
+\end{verbatim}
+\item
+\begin{verbatim}
+0.1 :: p(X) :- \+(\+(p(X))).
+\end{verbatim}
+\item
+\begin{verbatim}
+p(X) :- \+((p(X)); (p(X))).
+\end{verbatim}
+\item
+\begin{verbatim}
+0.4 :: p(X) :- \+((p(X)), (p(X))).
+\end{verbatim}
+\item
+\begin{verbatim}
+0.4 :: p(X) :- \+(\+(\+(p(X)))).
+\end{verbatim}
+\item[+]
+\begin{verbatim}
+0.7 :: p(X) :- p(X).
+\end{verbatim}
+\item[+]
+\begin{verbatim}
+p(X).
+\end{verbatim}
+\end{itemize}
+
+To demonstrate variable symmetry reduction in action, we set $\predicates{} =
+[\texttt{p}]$, $\arities{} = [3]$, $\variables{} = \{\texttt{X}, \texttt{Y},
+\texttt{Z} \}$, $\constants{} = \emptyset$, $\maxNumNodes{} = 1$,
+$\maxNumClauses{} = 1$, and forbid all cycles. This gives us the following five
+programs:
+
+\begin{itemize}
+\item
+\begin{verbatim}
+0.8 :: p(Z, Z, Z).
+\end{verbatim}
+\item
+\begin{verbatim}
+p(Y, Y, Z).
+\end{verbatim}
+\item
+\begin{verbatim}
+p(Y, Z, Z).
+\end{verbatim}
+\item
+\begin{verbatim}
+p(Y, Z, Y).
+\end{verbatim}
+\item
+\begin{verbatim}
+0.1 :: p(X, Y, Z).
+\end{verbatim}
+\end{itemize}
+
+This is one of many possible programs with $\predicates{} = [\texttt{p},
+\texttt{q}, \texttt{r}]$, $\arities{} = [1, 2, 3]$, $\variables{} =
+\{\texttt{X}, \texttt{Y}, \texttt{Z} \}$, $\constants{} = \{ \texttt{a},
+\texttt{b}, \texttt{c} \}$, $\maxNumNodes{} = 5$, $\maxNumClauses{} = 5$, and
+without negative cycles:
+
+\begin{verbatim}
+p(b) :- \+((q(a, b)), (q(X, Y)), (q(Z, X))).
+0.4 :: q(X, X) :- \+(r(Y, Z, a)).
+q(X, a) :- r(Y, Y, Z).
+q(X, a) :- r(Y, b, Z).
+r(Y, b, Z).
+\end{verbatim}
+
+Finally, we set
+$\predicates{} = [\texttt{p}, \texttt{q}, \texttt{r}]$, $\arities{} = [1, 1,
+1]$, $\variables{} = \emptyset$, $\constants{} = \{ \texttt{a} \}$,
+$\maxNumNodes{} = 3$, $\maxNumClauses{} = 3$, forbid negative cycles, and
+constrain predicates \texttt{p} and \texttt{q} to be independent. The resulting
+search space contains thousands of programs such as:
+
+\begin{itemize}
+\item
+\begin{verbatim}
+0.5 :: p(a) :- (p(a)); (p(a)).
+0.2 :: q(a) :- (q(a)), (q(a)).
+0.4 :: r(a) :- \+(q(a)).
+\end{verbatim}
+\item
+\begin{verbatim}
+p(a) :- p(a).
+0.5 :: q(a) :- (r(a)); (q(a)).
+r(a) :- (r(a)); (r(a)).
+\end{verbatim}
+\item
+\begin{verbatim}
+p(a) :- (p(a)); (p(a)).
+0.6 :: q(a) :- q(a).
+0.7 :: r(a) :- \+(q(a)).
+\end{verbatim}
+\end{itemize}
+
 \end{document}

### 2020-02-11 src/main/GeneratePrograms.java

@@ -234,12 +234,12 @@ class GeneratePrograms {
     public static void main(String[] args) throws IOException {
         //checkNumPrograms();
         //generateSmallPrograms();
-        generateBigPrograms(Arrays.asList(1, 2, 4, 8));
+        //generateBigPrograms(Arrays.asList(1, 2, 4, 8));
 
-        /*String[] predicates = new String[]{"p"};
-        Program p = new Program(16, 2,
-                ForbidCycles.NEGATIVE, DEFAULT_PROBABILITIES, predicates, new int[]{1}, new String[]{"X"},
-                new String[]{"a"}, new PredicatePair[0]);
-        p.saveProgramsToFiles(1000, "../programs/");*/
+        String[] predicates = new String[]{"p", "q", "r"};
+        Program p = new Program(3, 3,
+                ForbidCycles.NONE, DEFAULT_PROBABILITIES, predicates, new int[]{1, 1, 1}, new String[0],
+                new String[]{"a"}, new PredicatePair[]{new PredicatePair(predicates, "p", "q")});
+        p.saveProgramsToFiles(1000, "../programs/");
     }
 }

### 2020-02-11 src/main/Program.java

@@ -311,7 +311,7 @@ public class Program {
 
         String body = bodies[i].toString();
         String head = clauseHeads[i].toString();
-        if (body.equals("T."))
+        if (body.equals("."))
             return probabilityString + head+ ".\n";
         return probabilityString + head + " :- " + body + "\n";
     }

### 2020-02-11 paper/paper.tex
Rearranging stuff

@@
 values and the empirical hardness of the program generation task.
- % TODO (Fazl): % Could you provide a motivating example? It % might be useful to engage readers.
 
@@
 \end{constraint}
-% TODO (Fazl): explain what h is.
 
@@
 
-% TODO (Fazl): the first four words sound odd. Rephrase.
 It remains to constrain the forest represented by the $\variable{structure}$
@@
 $\maxNumNodes{}$ nodes per clause, and arbitrary $\predicates{}$,
-$\arities{}$, $\variables{}$, and $\constants{}$. To simplify the task, we only
-consider clauses without probabilities and disable (negative) cycle elimination.
-It was experimentally confirmed that the model agrees with the combinatorial
-formula from this section in 985 different scenarios. The \emph{total arity} of
-a body of a clause is the sum total of arities of all predicates in the body.
-% TODO (Vaishak, last sentence): move to footnote and add "Since the [details] of
-% this empirical investigation are not crucial to the thrust of this paper, we
-% will [detail] this in an extendedd technical report."
+$\arities{}$, $\variables{}$, and $\constants{}$\footnote{We checked that the
+  our model agrees with the derived combinatorial formula in close to a thousand
+  different scenarios. The details of this empirical investigation are omitted
+  as they are not crucial to the thrust of this paper.}. To simplify the task,
+we only consider clauses without probabilities and disable (negative) cycle
+elimination. We also introduce the term \emph{total arity} of a body of a clause
+to refer to the sum total of arities of all predicates in the body.
 
@@
 
-% TODO: talk about randomness. The value heuristic is random because we want
-% randomness. After finding one solution, one can continue the search for more,
-% but they will be similar (acceptable if the search space is small and we want
-% to find all solutions).
-% On the other hand, with restarts, duplicates become possible.
+% TODO: Extra notes.
+% 1. Randomness. The value heuristic is random because we want randomness. After
+% finding one solution, one can continue the search for more, but they will be
+% similar (acceptable if the search space is small and we want to find all
+% solutions).
+% 2. Logic programs don't have disjunctions and parentheses. Is there an easy
+% way to eliminate them?
+% 3. We can do the same thing for predicates within the body of a clause that we
+% do with variables, i.e., predicates within a clause are permutable (except for
+% the head predicate), so we can have a set of 'allowed' predicates.
+% 4. One example of a clear bias exhibited by our model is that of complexity
+% over simplicity, i.e., if a tree that represents the body of a clause can have
+% up to $\maxNumNodes{}$ nodes---because the number of possible trees with $n$
+% nodes grows with $n$---it is much more likely to have $\maxNumNodes{}$ or
+% $\maxNumNodes{} - 1$ nodes than, e.g., one or two.
 
@@
 as generated by our model, although it is not obvious how such a
-probability distribution could be characterised.% One example of a clear bias
-%exhibited by our model is that of complexity over simplicity, i.e., if a tree
-%that represents the body of a clause can have up to $\maxNumNodes{}$
-%nodes---because the number of possible trees with $n$ nodes grows with $n$---it
-%is much more likely to have $\maxNumNodes{}$ or $\maxNumNodes{} - 1$ nodes than,
-%e.g., one or two.
-
-% TODO: We can do the same thing for predicates within the body of a clause that
-% we do with variables, i.e., predicates within a clause are permutable (except
-% for the head predicate), so we can have a set of 'allowed' predicates.
+probability distribution could be characterised.
 
@@
 \bibliography{paper}
-% TODO: logic programs don't have disjunctions. Is there an easy way to
-% eliminate them?
 

### 2020-02-13 paper/paper.tex
Editing

@@
 most four different problems: sometimes just a single network
-\citep{DBLP:journals/tplp/KimmigDRCR11,DBLP:journals/corr/abs-1112-3785,DBLP:conf/iclp/KimmigCRDR08},
+\citep{DBLP:journals/tplp/KimmigDRCR11,DBLP:journals/corr/abs-1112-3785},
 sometimes two
 \citep{DBLP:journals/corr/abs-1009-3798,DBLP:conf/ecai/BruynoogheMKGVJR10} or
-four networks \citep{DBLP:conf/ijcai/VlasselaerBKMR15} coming from a range of
-areas such as social networks and citation/genetic/biological data sets. In
-order to better understand the strengths and weaknesses of these algorithms,
-along with real data they should also be evaluated on a range of synthetic
-problems that accurately represent the potential complexities that have to be
-handled by a well-designed inference algorithm. Furthermore, random logic
-program generators can be useful in combination with methods that generate
-random data with probabilistic logic programs \citep{DBLP:conf/soict/Dries15}
-and can be used as a component of learning.
+four networks \citep{DBLP:conf/ijcai/VlasselaerBKMR15}, all coming from a range
+of areas such as social networks and citation/genetic/biological data sets. To
+better understand the strengths and weaknesses of these algorithms, along with
+real data they should also be evaluated on a range of synthetic problems that
+accurately represent the potential complexities that have to be handled by a
+well-designed inference algorithm. Furthermore, random logic program generators
+can be useful in combination with methods that generate random data with
+probabilistic logic programs \citep{DBLP:conf/soict/Dries15} and can be used as
+a component of learning.
 
@@
 total number of rules \citep{DBLP:conf/iclp/ZhaoL03}. We introduce a way to
-generate random logic programs using a constraint solver such as Choco
-\citep{choco}. The same model can generate both probabilistic programs directly
-in the syntax of ProbLog \citep{DBLP:conf/ijcai/RaedtKT07} as well as
-non-probabilistic Prolog programs. For generated probabilistic programs to be
-valid, we use a custom constraint to detect negative cycles (as described in
-\cref{sec:cycles}). A major advantage of our constraint-based approach is that
-one can easily add additional constraints to the model. To demonstrate that, in
-\cref{sec:independence} we present a custom constraint with propagation and
-entailment algorithms that can ensure predicate independence.
-\cref{sec:counting} also presents a combinatorial argument for correctness,
-where we produce combinatorial expressions that count the number of programs
-that the model should produce for various parameter values. Finally,
-\cref{sec:experiments} shows how the model scales when tasked with producing
-more complicated programs and identifies the relationships between parameter
-values and the empirical hardness of the program generation task.
-
-% TODO (Vaishak):
-Overall, [main] contributions are concerned purely with logic programming-based
+generate random logic programs using a constraint model. The same model can
+generate both probabilistic programs directly in the syntax of ProbLog
+\citep{DBLP:conf/ijcai/RaedtKT07} as well as non-probabilistic Prolog programs.
+For generated probabilistic programs to be valid, we use a custom constraint to
+detect negative cycles (as described in \cref{sec:cycles}). A major advantage of
+our constraint-based approach is that one can easily add additional constraints
+to the model. To demonstrate that, in \cref{sec:independence} we present a
+custom constraint with propagation and entailment algorithms that can ensure
+predicate independence. \cref{sec:counting} also presents a combinatorial
+argument for correctness, where we produce combinatorial expressions that count
+the number of programs that the model should produce for various parameter
+values. Finally, \cref{sec:experiments} shows how the model scales when tasked
+with producing more complicated programs and identifies the relationships
+between parameter values and the empirical hardness of the program generation
+task.
+
+Overall, our main contributions are concerned purely with logic programming-based
 languages and frameworks, which capture a major fragment of statistical
 relational learning \citep{DBLP:series/synthesis/2016Raedt}.
-However, since probabilistic logic programming [languages] are closely related
-to other [endeavours] in machine learning, including (imperative) probabilistic
-programming (e.g., see discussions in \citep{DBLP:journals/ml/RaedtK15}), our
-results [may] provide the [footing] to explore broader questiosn on generating
-and testing programs/algorithms in machine learning.
+However, since probabilistic logic programming languages are closely related
+to other areas of machine learning, including (imperative) probabilistic
+programming \citep{DBLP:journals/ml/RaedtK15}, our results can lay the
+foundations for exploring broader questions on generating and testing
+programs/algorithms in machine learning.
 
@@
 
-It remains to constrain the forest represented by the $\variable{structure}$
+We need to constrain the forest represented by the $\variable{structure}$
 array together with its $\variable{values}$ to eliminate unnecessary symmetries
@@
 
-% TODO (Vaishak):
-% Now we add a theorem that states that the programs generated by the algorithm,
-% regardless of whether they involve negative cycles or not, are well-defined?
-% That is, in the non-probabilistic case, they are satisfiable, and, in the
-% probabilistic case, for both negative cycles & without, they induce programs
-% that are satisfiable + well-defined measure on the set of satisfying
-% assignments [proofs in the appendix?]
-
 \section{EMPIRICAL PERFORMANCE} \label{sec:experiments}
@@
 i.e., situations where a contradiction is being `fixed' by making changes that
-have no hope to fix the contradiction. Thus, we partition all decision variables
-into an ordered list of groups, and require the values of all variables from one
-group to be determined before moving to the next group. Within each group, we
-use the `fail first' variable ordering heuristic. The first group consists of
-all head predicates. Afterwards, we handle all remaining decision variables from
-the first clause before proceeding to the next. The decision variables within
-each clause are divided into:
+have no hope of fixing the contradiction. Thus, we partition all decision
+variables into an ordered list of groups, and require the values of all
+variables from one group to be determined before moving to the next group.
+Within each group, we use the `fail first' variable ordering heuristic. The
+first group consists of all head predicates. Afterwards, we handle all remaining
+decision variables from the first clause before proceeding to the next. The
+decision variables within each clause are divided into:
 \begin{enumerate*}
@@
 what parameter values make the constraint satisfaction problem harder. For these
-experiments, we use Choco~4.10.2 \citep{choco} with Java~8 on a computer with an
-Intel Core i5-8250U processor. For $|\predicates{}|$, $|\variables{}|$,
-$|\constants{}|$, $\maxNumNodes{}$, and $\maxNumClauses{} - |\predicates{}|$
-(i.e., the number of clauses in addition to the mandatory $|\predicates{}|$
-clauses), we assign all combinations of 1, 2, 4, 8. $\maxArity{}$ is assigned to
-values 1--4. For each $|\predicates{}|$, we also iterate over all possible
-numbers of independent pairs of predicates, ranging from 0 up to
-$\binom{|\predicates{}|}{2}$. For each combination of the above-mentioned
-parameters, we pick ten random ways to assign arities to predicates (such that
-$\maxArity{}$ occurs at least once) and ten random combinations of independent
-pairs. We then run the solver with a \SI{60}{\second} timeout.
+experiments, we use Choco~4.10.2 \citep{choco} with Java~8. For
+$|\predicates{}|$, $|\variables{}|$, $|\constants{}|$, $\maxNumNodes{}$, and
+$\maxNumClauses{} - |\predicates{}|$ (i.e., the number of clauses in addition to
+the mandatory $|\predicates{}|$ clauses), we assign all combinations of 1, 2, 4,
+8. $\maxArity{}$ is assigned to values 1--4. For each $|\predicates{}|$, we also
+iterate over all possible numbers of independent pairs of predicates, ranging
+from 0 up to $\binom{|\predicates{}|}{2}$. For each combination of the
+above-mentioned parameters, we pick ten random ways to assign arities to
+predicates (such that $\maxArity{}$ occurs at least once) and ten random
+combinations of independent pairs. We then run the solver with a
+\SI{60}{\second} timeout.
 
@@
 
-\section{CONCLUSIONS}
-% TODO (Fazl): equations and 'provides no such guarantees' sound more like
-% future work / limitation section. Make it sound more positive.
+\section{CONCLUSIONS \& FUTURE WORK}
 
@@
 probabilistic logic programs. The model avoids unnecessary symmetries, generates
-valid programs, and can ensure predicate independence. Note that there is one
-kind of symmetries not handled by our model, i.e., logical equivalence. For
-example, all three of these formulas are logically equivalent but syntactically
-different: $\neg(\mathsf{P}(X) \lor \mathsf{Q}(X))$, $\neg\mathsf{P}(X) \land
-\neg\mathsf{Q}(X)$, and $\neg\mathsf{Q}(X) \land \neg\mathsf{P}(X)$. While there
-are many situations where one would prefer to treat logically equivalent
-formulas as symmetries that should be eliminated, there are also situations
-where we do care about enumerating different ways to express the same
-probability distribution or knowledge base. For instance, one could look for the
-`best' logically equivalent formula, or investigate whether some formulas result
-in faster inference than others.
-
-Another issue worth discussing is that of randomness. Most random models sample
-from a well-defined probability distribution whereas a constraint model, while
-potentially sufficiently random, provides no such guarantees. In future work, it
-would be interesting to examine the probability distribution of logic programs
-as generated by our model, although it is not obvious how such a
-probability distribution could be characterised.
+valid programs, and can ensure predicate independence. Note that our model
+treats logically equivalent but syntactically different formulas as different.
+While there are many situations where one would prefer to eliminate them like
+symmetries, there are also situations where we do care about enumerating
+different ways to express the same probability distribution or knowledge base.
+For instance, one could look for the `best' logically equivalent formula, or
+investigate whether some formulas result in faster inference than others.
+
+Another topic worth mentioning is randomness. Most random models sample from a
+well-defined probability distribution whereas a constraint model, while
+sufficiently random, provides no such guarantees. In future work, it would be
+interesting to examine the probability distribution of logic programs as
+generated by our model, although it is not obvious how such a probability
+distribution could be characterised.
 

### 2020-02-13 paper/paper.tex
Update the appendix

@@
 
+\usepackage[dvipsnames]{xcolor}
 \usepackage[ruled,vlined]{algorithm2e}
@@
 \renewcommand\fbox{\fcolorbox{red}{white}}
+\newcommand{\hilight}[1]{\setlength{\fboxsep}{1pt}\colorbox{SpringGreen}{#1}}
+\newcommand{\hlitem}{\stepcounter{enumi}\item[\hilight{\theenumi}]}
 
@@
 \{ \texttt{X} \}$, $\constants{} = \emptyset$, $\maxNumNodes{} = 4$, and
-$\maxNumClauses{} = 1$, we get fifteen one-line programs, five of which are
-without negative cycles (denoted by `+'). Only the last program has no cycles at
-all.
-
+$\maxNumClauses{} = 1$, we get fifteen one-line programs, six of which are
+without negative cycles (as highlighted below). Only the last program has no
+cycles at all.
+
+\begin{enumerate}[label=\arabic*.]
+\item
+\begin{verbatim}
+0.5 :: p(X) :- (\+(p(X))), (p(X)).
+\end{verbatim}
+\item
+\begin{verbatim}
+0.8 :: p(X) :- (\+(p(X))); (p(X)).
+\end{verbatim}
+\hlitem
+\begin{verbatim}
+0.8 :: p(X) :- (p(X)); (p(X)).
+\end{verbatim}
+\hlitem
+\begin{verbatim}
+0.7 :: p(X) :- (p(X)), (p(X)).
+\end{verbatim}
+\item
+\begin{verbatim}
+0.6 :: p(X) :- (p(X)), (\+(p(X))).
+\end{verbatim}
+\item
+\begin{verbatim}
+p(X) :- (p(X)); (\+(p(X))).
+\end{verbatim}
+\hlitem
+\begin{verbatim}
+0.1 :: p(X) :- (p(X)); (p(X)); (p(X)).
+\end{verbatim}
+\hlitem
+\begin{verbatim}
+0.8 :: p(X) :- (p(X)), (p(X)), (p(X)).
+\end{verbatim}
+\item
+\begin{verbatim}
+p(X) :- \+(p(X)).
+\end{verbatim}
+\item
+\begin{verbatim}
+0.1 :: p(X) :- \+(\+(p(X))).
+\end{verbatim}
+\item
+\begin{verbatim}
+p(X) :- \+((p(X)); (p(X))).
+\end{verbatim}
+\item
+\begin{verbatim}
+0.4 :: p(X) :- \+((p(X)), (p(X))).
+\end{verbatim}
+\item
+\begin{verbatim}
+0.4 :: p(X) :- \+(\+(\+(p(X)))).
+\end{verbatim}
+\hlitem
+\begin{verbatim}
+0.7 :: p(X) :- p(X).
+\end{verbatim}
+\hlitem
+\begin{verbatim}
+p(X).
+\end{verbatim}
+\end{enumerate}
+
+Note that:
 \begin{itemize}
-\item
-\begin{verbatim}
-0.5 :: p(X) :- (\+(p(X))), (p(X)).
-\end{verbatim}
-\item
-\begin{verbatim}
-0.8 :: p(X) :- (\+(p(X))); (p(X)).
-\end{verbatim}
-\item[+]
-\begin{verbatim}
-0.8 :: p(X) :- (p(X)); (p(X)).
-\end{verbatim}
-\item[+]
-\begin{verbatim}
-0.7 :: p(X) :- (p(X)), (p(X)).
-\end{verbatim}
-\item
-\begin{verbatim}
-0.6 :: p(X) :- (p(X)), (\+(p(X))).
-\end{verbatim}
-\item
-\begin{verbatim}
-p(X) :- (p(X)); (\+(p(X))).
-\end{verbatim}
-\item[+]
-\begin{verbatim}
-0.1 :: p(X) :- (p(X)); (p(X)); (p(X)).
-\end{verbatim}
-\item[+]
-\begin{verbatim}
-0.8 :: p(X) :- (p(X)), (p(X)), (p(X)).
-\end{verbatim}
-\item
-\begin{verbatim}
-p(X) :- \+(p(X)).
-\end{verbatim}
-\item
-\begin{verbatim}
-0.1 :: p(X) :- \+(\+(p(X))).
-\end{verbatim}
-\item
-\begin{verbatim}
-p(X) :- \+((p(X)); (p(X))).
-\end{verbatim}
-\item
-\begin{verbatim}
-0.4 :: p(X) :- \+((p(X)), (p(X))).
-\end{verbatim}
-\item
-\begin{verbatim}
-0.4 :: p(X) :- \+(\+(\+(p(X)))).
-\end{verbatim}
-\item[+]
-\begin{verbatim}
-0.7 :: p(X) :- p(X).
-\end{verbatim}
-\item[+]
-\begin{verbatim}
-p(X).
-\end{verbatim}
+\item A program such as Program~14, because of its cyclic definition, defines a
+  predicate that has probability zero across all constants. This can more easily
+  be seen as solving equation $0.7x = x$.
+\item Programs 10 and 14 are not equivalent (i.e., double negation does not
+  cancel out) because Program 10 has a negative cycle and is thus considered to
+  be ill-defined.
 \end{itemize}

### 2020-02-17 paper/paper.tex
Heavy editing

@@
 
-\usepackage[dvipsnames]{xcolor}
 \usepackage[ruled,vlined]{algorithm2e}
@@
 \renewcommand\fbox{\fcolorbox{red}{white}}
-\newcommand{\hilight}[1]{\setlength{\fboxsep}{1pt}\colorbox{SpringGreen}{#1}}
+\newcommand{\hilight}[1]{\setlength{\fboxsep}{1pt}\colorbox{lightgray}{#1}}
 \newcommand{\hlitem}{\stepcounter{enumi}\item[\hilight{\theenumi}]}
@@
 \begin{document}
-\bibliographystyle{plainnat}
+\bibliographystyle{abbrvnat}
 \maketitle
@@
   independence with efficient propagation and entailment algorithms, allowing
-  one to generate programs that have a certain independence structure. In order
-  to generate valid probabilistic logic programs, we also present a new
-  constraint for negative cycle detection. Finally, we provide a combinatorial
-  argument for correctness and describe how the parameters of the model affect
-  the empirical difficulty of the program generation task.
+  one to generate programs that have a certain independence structure. To
+  generate valid probabilistic logic programs, we also present a new constraint
+  for negative cycle detection. Finally, we provide a combinatorial argument for
+  correctness and describe how the parameters of the model affect the empirical
+  difficulty of the program generation task.
 \end{abstract}
@@
 
-How confidently can we claim that an algorithm works well if it is only tested
-on a few types of problems? Perhaps the `inferior' algorithm is actually
-better in some specific circumstances. Maybe there are identifiable
-types of inputs that make every algorithm default to exponential behaviour
-that could be easily overcome with the right strategy. At present, most
-inference algorithms for probabilistic logic programs are only evaluated on at
-most four different problems: sometimes just a single network
-\citep{DBLP:journals/tplp/KimmigDRCR11,DBLP:journals/corr/abs-1112-3785},
-sometimes two
-\citep{DBLP:journals/corr/abs-1009-3798,DBLP:conf/ecai/BruynoogheMKGVJR10} or
-four networks \citep{DBLP:conf/ijcai/VlasselaerBKMR15}, all coming from a range
-of areas such as social networks and citation/genetic/biological data sets. To
-better understand the strengths and weaknesses of these algorithms, along with
-real data they should also be evaluated on a range of synthetic problems that
-accurately represent the potential complexities that have to be handled by a
-well-designed inference algorithm. Furthermore, random logic program generators
-can be useful in combination with methods that generate random data with
-probabilistic logic programs \citep{DBLP:conf/soict/Dries15} and can be used as
-a component of learning.
-
-Most current approaches to generating random logic programs are restrictive,
-e.g., limited to clauses with only two literals
-\citep{DBLP:conf/lpnmr/NamasivayamT09}, or to clauses of the form $a \gets \neg
-b$ \citep{DBLP:journals/tocl/WenWSL16}, but others are more expressive, e.g.,
-defining a program only by the (maximum) number of atoms in the body and the
-total number of rules \citep{DBLP:conf/iclp/ZhaoL03}. We introduce a way to
-generate random logic programs using a constraint model. The same model can
-generate both probabilistic programs directly in the syntax of ProbLog
-\citep{DBLP:conf/ijcai/RaedtKT07} as well as non-probabilistic Prolog programs.
-For generated probabilistic programs to be valid, we use a custom constraint to
-detect negative cycles (as described in \cref{sec:cycles}). A major advantage of
-our constraint-based approach is that one can easily add additional constraints
-to the model. To demonstrate that, in \cref{sec:independence} we present a
-custom constraint with propagation and entailment algorithms that can ensure
-predicate independence. \cref{sec:counting} also presents a combinatorial
-argument for correctness, where we produce combinatorial expressions that count
-the number of programs that the model should produce for various parameter
-values. Finally, \cref{sec:experiments} shows how the model scales when tasked
-with producing more complicated programs and identifies the relationships
-between parameter values and the empirical hardness of the program generation
-task.
-
-Overall, our main contributions are concerned purely with logic programming-based
-languages and frameworks, which capture a major fragment of statistical
-relational learning \citep{DBLP:series/synthesis/2016Raedt}.
-However, since probabilistic logic programming languages are closely related
-to other areas of machine learning, including (imperative) probabilistic
-programming \citep{DBLP:journals/ml/RaedtK15}, our results can lay the
-foundations for exploring broader questions on generating and testing
-programs/algorithms in machine learning.
+% Notes on papers that test ProbLog inference algorithms:
+% - On the Implementation: published, one biological network
+% -(removed) Nesting Probabilistic Inference: NOT published, one Alzheimer
+% network
+% -(removed) DNF Sampling: NOT published, two networks: a family tree and the
+% Alzheimer network
+% -ProbLog Technology: published, two networks: a custom theory with randomly
+% generated data, and citation data
+% -Anytime Inference: published, four networks: the Smokers social network,
+% Alzheimer data, biological network of genetic data, data about the world wide
+% web
+
+%Interestingly, in the [???] of
+%probabilistic logic programming, random logic program generators can be useful
+%in combination with methods that generate random data with probabilistic logic
+%programs \citep{DBLP:conf/soict/Dries15} and can be used as a component of
+%learning.
+
+Unifying logic and probability is a long-standing challenge in artificial
+intelligence \citep{DBLP:journals/cacm/Russell15}, and, in that regard,
+statistical relational learning (SRL) has developed into an exciting area that
+mixes machine learning and symbolic (logical and relational) structures. In
+particular, logic programs and probabilistic logic programs---including
+languages such as PRISM \citep{DBLP:conf/ijcai/SatoK97}, ICL
+\citep{DBLP:journals/ai/Poole97}, and ProbLog
+\citep{DBLP:conf/ijcai/RaedtKT07}---are promising frameworks for codifying
+complex SRL models. With the enhanced structure, however, inference becomes more
+challenging as algorithms have to correctly handle hard and soft logical
+constraints. At the moment, we have no precise way of evaluating and comparing
+different inference algorithms. Incidentally, if one were to survey the
+literature, one often finds that an inference algorithm is only tested on 1--4
+data sets
+\citep{DBLP:journals/tplp/KimmigDRCR11,DBLP:conf/ecai/BruynoogheMKGVJR10,DBLP:conf/ijcai/VlasselaerBKMR15},
+originating from areas such as social networks, citation patterns, and
+biological data. But how confidently can we claim that an algorithm works well
+if it is only tested on a few types of problems?
+
+About thirty years ago, SAT solving technology was dealing with a similar lack
+of clarity \citep{DBLP:journals/ai/SelmanML96}. This changed with the study of
+generation of random SAT instances against different input parameters (e.g.,
+clause length and total number of variables) to better understand the behaviour
+of algorithms and their ability to solve random synthetic problems.
+Unfortunately, in the context of probabilistic logic programming, most current
+approaches to random instance generation are very restrictive, e.g., limited to
+clauses with only two literals \citep{DBLP:conf/lpnmr/NamasivayamT09}, or to
+clauses of the form $a \gets \neg b$ \citep{DBLP:journals/tocl/WenWSL16},
+although some are more expressive, e.g., defining a program only by the
+(maximum) number of atoms in the body and the total number of rules
+\citep{DBLP:conf/iclp/ZhaoL03}.
+
+In this work, we introduce a constraint model for generating random logic
+programs according to a number of user-specified parameters on the structure of
+the program. In fact, the same model can generate both probabilistic programs
+directly in the syntax of ProbLog \citep{DBLP:conf/ijcai/RaedtKT07} and
+non-probabilistic Prolog programs. For generated probabilistic programs to be
+valid, we use a custom constraint to detect negative cycles. A major advantage
+of our constraint-based approach is that one can easily add additional
+constraints to the model. To demonstrate that, we present a custom constraint
+with propagation and entailment algorithms that can ensure predicate
+independence. We also present a combinatorial argument for correctness, counting
+the number of programs that the model produces for various parameter values.
+Finally, we show how the model scales when tasked with producing more
+complicated programs and identify the relationships between parameter values and
+the empirical hardness of the program generation task.
+
+Overall, our main contributions are concerned with logic programming-based
+languages and frameworks, which capture a major fragment of SRL
+\citep{DBLP:series/synthesis/2016Raedt}. However, since probabilistic logic
+programming languages are closely related to other areas of machine learning,
+including (imperative) probabilistic programming
+\citep{DBLP:journals/ml/RaedtK15}, our results can lay the foundations for
+exploring broader questions on generating models and testing algorithms in
+machine learning.
 
@@
   variables}, and \emph{predicates}. Each predicate has an \emph{arity} that
-defines the number of terms that it can applied to. A \emph{term} is either a
+defines the number of terms that it can be applied to. A \emph{term} is either a
 variable or a constant, and an \emph{atom} is a predicate of arity $n$ applied
@@
   \]
-  Then
-  \[
-    \variable{nValues}(P) =
-    \begin{cases}
-      |\predicates{}| + 1 & \text{if } \variable{count}(\Box, P) > 0 \\
-      |\predicates{}| & \text{otherwise.}
-    \end{cases}
-  \]
+  Then $\variable{nValues}(P) = |\predicates{}|$ if $\variable{count}(\Box, P) =
+  0$ and $|\predicates{}| + 1$ otherwise, where $\variable{nValues}(P)$ counts
+  the number of unique values in $P$.
 \end{constraint}
-
-Here, $\variable{nValues}(P)$ counts the number of unique values in $P$.
 
@@
 the head or the body of the clause is before the first occurrence of $Y$. Note
-that the constrains described in this section only make sense if $|\variables| >
-1$. Also note that all definitions and constraints here are on a per-clause
+that the constraints described in this section only make sense if $|\variables| >
+1$. Also, note that all definitions and constraints here are on a per-clause
 basis.
@@
 We add a number of redundant constraints to make search more efficient. First,
-we can formally state that the positions occupied by different terms must be
-different:
+we can state that the positions occupied by different terms must be different:
 
@@
 
-In order to demonstrate the correctness of the model and explain it in more
+To demonstrate the correctness of the model and explain it in more
 detail, in this section we are going to derive combinatorial expressions for
@@
 $\maxNumNodes{}$ nodes per clause, and arbitrary $\predicates{}$,
-$\arities{}$, $\variables{}$, and $\constants{}$\footnote{We checked that the
+$\arities{}$, $\variables{}$, and $\constants{}$\footnote{We checked that
   our model agrees with the derived combinatorial formula in close to a thousand
@@
   from the root to the $\mathsf{P}$ node in the tree representation of the
-  clause passes through at least one negation node. Otherwise it is
+  clause passes through at least one negation node. Otherwise, it is
   \emph{positive}. We say that $\mathscr{P}$ (or $G_{\mathscr{P}}$) has a
@@
   Hence, we have two pairs of independent predicates, i.e., $\mathsf{mother}$ is
-  independent from $\mathsf{parent}$ and $\mathsf{sibling}$.
+  independent of $\mathsf{parent}$ and $\mathsf{sibling}$.
 \end{example}
@@
   \]
-  or
-  \[
-    i \not\in \{a.\variable{name} \mid a \in
-    \variable{bodies}[k].\variable{values} \}.
-  \]
+  or $ i \not\in \{a.\variable{name} \mid a \in
+  \variable{bodies}[k].\variable{values} \}$.
 \end{definition}
@@
 \section{NEGATIVE CYCLES} \label{sec:cycles}
-
-Having no negative cycles in the predicate dependency graph is a requirement for
-probabilistic logic programming language ProbLog \citep{kimmig2009trading},
-although it has been shown how the requirement can be alleviated by introducing
-negative probabilities \citep{DBLP:journals/ijar/BuchmanP17}. Ideally, we would
-like to design a constraint for negative cycles similar to the constraint for
-independence in the previous section. However, the difficulty with creating a
-propagation algorithm for negative cycles is that there seems to be no good way
-to extend \cref{def:adjacency_matrix} so that the adjacency matrix captures
-positivity/negativity. Thus, we settle for an entailment algorithm with no
-propagation.
+% although some work has been done in overcoming this limitation
+% \citep{DBLP:journals/ijar/BuchmanP17}
+
+Having no negative cycles in the predicate dependency graph is a requirement of
+ProbLog that makes the program well-defined \citep{kimmig2009trading}. Ideally,
+we would like to design a constraint for negative cycles similar to the
+constraint for independence in the previous section. However, the difficulty
+with creating a propagation algorithm for negative cycles is that there seems to
+be no good way to extend \cref{def:adjacency_matrix} so that the adjacency
+matrix captures positivity/negativity. Thus, we settle for an entailment
+algorithm with no propagation.
 
@@
 
-The vast majority (\SI{97.7}{\percent}) of runs finished in under
-\SI{1}{\second}, while four instances timed out: all with $|\predicates| =
-\maxNumClauses{} - |\predicates{}| = \maxNumNodes{} = 8$ and the remaining
-parameters all different. This suggests that---regardless of parameter
-values---most of the time a solution can be identified instantaneously while
-occasionally a series of wrong decisions can lead the solver into a part of the
-search space with no solutions.
+The majority (\SI{97.7}{\percent}) of runs finished in under \SI{1}{\second},
+while four instances timed out: all with $|\predicates| = \maxNumClauses{} -
+|\predicates{}| = \maxNumNodes{} = 8$ and the remaining parameters all
+different. This suggests that---regardless of parameter values---most of the
+time a solution can be identified instantaneously while occasionally a series of
+wrong decisions can lead the solver into a part of the search space with no
+solutions.
 
@@
 % $\maxNumNodes{} - 1$ nodes than, e.g., one or two.
-
-\section{CONCLUSIONS \& FUTURE WORK}
+% 5. It can easily be shown that all generated logic programs are satisfiable
+% 6. Logic programs typically only have a single conjunction with literals, but
+% we can easily adapt the model to handle that.
+
+\section{CONCLUSIONS}
 
@@
 probabilistic logic programs. The model avoids unnecessary symmetries, generates
-valid programs, and can ensure predicate independence. Note that our model
-treats logically equivalent but syntactically different formulas as different.
-While there are many situations where one would prefer to eliminate them like
-symmetries, there are also situations where we do care about enumerating
-different ways to express the same probability distribution or knowledge base.
-For instance, one could look for the `best' logically equivalent formula, or
-investigate whether some formulas result in faster inference than others.
-
-Another topic worth mentioning is randomness. Most random models sample from a
-well-defined probability distribution whereas a constraint model, while
-sufficiently random, provides no such guarantees. In future work, it would be
-interesting to examine the probability distribution of logic programs as
-generated by our model, although it is not obvious how such a probability
-distribution could be characterised.
+valid programs, and can ensure predicate independence. Our constraint-driven
+approach is advantageous in that one can easily add additional conditions on the
+structure and properties of the program, although the main disadvantage is
+that there are no guarantees about the underlying probability distribution from
+which programs are sampled.
+
+In addition, note that our model treats logically equivalent but syntactically
+different formulas as different. This is so in part because designing a
+constraint for logical equivalence fell outside the scope of this work and in
+part because in some situations one might want to enumerate all ways to express
+the same probability distribution or knowledge base, e.g., to investigate
+whether inference algorithms are robust to changes in representation.
 

### 2020-02-19 conditional_independence_notes/paper.tex
Entailment for conditional independence: version 1

\documentclass{article}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{xfrac}

\theoremstyle{definition}
\newtheorem{definition}{Definition}

\newcommand{\maxNumNodes}{\mathcal{M}_{\mathcal{N}}}
\newcommand{\maxNumClauses}{\mathcal{M}_{\mathcal{C}}}
\newcommand{\maybe}{\sfrac{1}{2}}

\author{Paulius Dilkas}
\title{A Constraint for Conditional Independence}

\begin{document}
\maketitle
% TODO: predicates should always be the first dimension, indices the second

Goal: conditional independence of two predicates conditioned on a
conjunction/disjunction of any number of predicates or a negation of a
predicate.

Central question: does this clause contain this predicate (filtering out
the possibility that the predicate is mentioned in the conditioning part)? We
can answer this question by iterating over each position and answering two other
questions:
\begin{itemize}
\item Does this position contain this predicate? Yes/No/Maybe.
\item Is this position part of the structure we are conditioning on? Yes/No/Maybe.
\end{itemize}

For each clause, we have two position x predicate matrices. One of them says (in
a yes/no/maybe fashion) whether this predicate can be in this position (that's
A). The other says whether this predicate is masked in this position
(yes/no/maybe).

The propagation algorithm for independence is extended with masks that are
either potential or definite. Masking happens in two stages: first, we mask
expressions within formulas, and then predicates. Masking algorithm uses an
algorithm for perfect bipartite matching.

For any integer $n$, let $[n] = \{ 0, 1, \dots, n-1 \}$.

\begin{definition}[Conditional independence]
  When assigning edges to the graph, mask off all possible instances of the
  expression we're conditioning on. For example, if we're conditioning on $a
  \land b$, then $c \gets a \land a \land b$ should produce no edges.
\end{definition}

\begin{definition}
  A predicate is \emph{definitely masked} if all instances are definitely
  masked. A predicate is \emph{potentially masked} if all instances are
  definitely/potentially masked.
\end{definition}

\begin{definition}[Primitives]
  For each clause, let $\mathbf{P}$ be a $\maxNumNodes{} \times |\mathcal{P}
  \cup \{ \land, \lor, \neg \}|$ matrix defined as
  \[
    P_{p,i} = \begin{cases}
      1 & \text{if } \mathtt{values}[i] = \{ p \} \\
      0 & \text{otherwise.}
    \end{cases}
  \]
  This matrix shows what symbol can (or must) be in what position.

  Likewise, let $\mathbf{C}$ be a $\maxNumNodes{} \times \maxNumNodes{}$ matrix
  defined as
  \[
    C_{i,j} = \begin{cases}
      1 & \text{if } \mathtt{structure}[i] = \{ j \} \\
      0 & \text{otherwise.}
    \end{cases}
  \]
  The $(i,j)$-th element shows whether node $i$ can be a child of node $j$.
\end{definition}

\begin{table}
  \centering
  \caption{Combining $\mathbf{M}$ and $\mathbf{P}$. The $\#$ stands for `impossible'.}
  \begin{tabular}{lll}
    \toprule
    & $P = 1$ & $P = 0$ \\
    \midrule
    $M = 1$ & $0$ & $\#$ \\
    $M = 0$ & $1$ & $0$ \\
    \bottomrule
  \end{tabular}
\end{table}
% P and C could be functions instead

\begin{algorithm}
  \caption{Constructing the adjacency matrix $\mathbf{A}$}
  \SetKwFunction{constructMask}{constructMask}
  \SetKwFunction{upgradeTo}{upgradeTo}
  $\mathbf{A} \gets \mathbf{0}_{|\mathcal{P}|, |\mathcal{P}|}$\;
  \ForEach{clause $c$}{
    Construct $\mathbf{P}$ and $\mathbf{C}$\;
    $\mathbf{M} \gets \constructMask{$\odot$, $\mathcal{C}$} $\;
    Let $\mathbf{A'} \in \{ 0, \maybe{}, 1 \}^{|\mathcal{P}| \times
      \maxNumNodes{}}$ be such that $A'_{i,j} = \begin{cases}
      0 & \text{if } P_{i,j} = M_{i,j} \ne \maybe{} \\
      1 & \text{if } P_{i,j} = 1 \text{ and } M_{i,j} = 0 \\
      \maybe{} & \text{otherwise}
    \end{cases}$\;
    \For{$h \in \mathtt{head}[c]$}{
      \For{$p \in \mathcal{P}$}{
        \For{$i \in [\maxNumNodes{}]$}{
          \uIf{$|\mathtt{head}[c]| = 1$ {\bf and } $A'_{p,i} = 1$}{
            $A_{h \gets p}.\upgradeTo{$1$}$\;
          }
          \ElseIf{$|\mathtt{head}[c]| = 1$ {\bf and} $A'_{p,i} = \maybe{}$}{
            $A_{h \gets p}.\upgradeTo{$\maybe{}$}$\;
          }
        }
      }
    }
  }
\end{algorithm}

The adjacency matrix $\mathbf{A} \in \{ 0, \maybe{}, 1 \}^{|\mathcal{P}| \times
  |\mathcal{P}|}$ is defined as:
\[
  A[h \gets p] = \begin{cases}
    1 & \text{if } \exists c \in [\maxNumClauses{}]: \mathtt{head}[c] = \{ h
    \} \text{ and } \exists i \in [\maxNumNodes{}]: A_{c;p,i} = 1 \\
    0 & \text{otherwise}
  \end{cases}\;
\]

How does this propagate back to the variables? Each `maybe' edge should hold a
set of (variable, value) pairs that can be eliminated if the propagation
algorithm decides that it cannot exist. Problem: propagating through
$\mathbf{A'}$ would mean propagating through $\mathbf{M}$ and $\mathbf{P}$. If
they're both uncertain, then we can't do anything. If $\mathbf{P}$ is uncertain,
we can remove the predicate, but if $\mathbf{M}$ is uncertain, there might be
multiple ways to complete the mask.

Essentially, we have three layers, i.e., we build two layers of abstraction on
top of the CP model. We make a decision on the top layer, and propagate the
changes to the bottom layers. A weakness is that some high-level problems can
have multiple solutions in the bottom layers, in which case we can't commit to
any particular solution and so can't do anything.

\begin{algorithm}
  \caption{Construct the mask matrix $\mathbf{M}$}
  \SetKwProg{Fn}{Function}{:}{}
  \SetKwFunction{markIndices}{markIndices}
  \SetKwFunction{constructMask}{constructMask}
  \KwData{the expression we are conditioning on: $\bigodot_{\mathsf{p} \in
      \mathcal{C}} \mathsf{p}$}
  \Fn{\constructMask{$\odot$, $\mathcal{C}$}}{
    $\mathbf{M} = \mathbf{0}_{|\mathcal{P}|, \maxNumNodes{}}$\;
    \For(\tcp*[h]{for each possible root}){$r \in [\maxNumNodes{}]$ such that
      $P_{r,\odot} \ne 0$}{
      $E \gets \{ \{p, i\} \mid p \in \mathcal{P}, i \in [\maxNumNodes{}],
      C_{i,r} \ne 0, P_{i,p} \ne 0 \}$\;
      $\mathbf{M'} \gets \markIndices{$(\mathcal{P}, [\maxNumNodes{}], E)$,
        $\maybe{}$}$\tcp*[l]{potential positions}
      $\mathbf{M} \gets \max\{ \mathbf{M}, \mathbf{M'}\}$\;
      \If{$P_{r,\odot} = 1$ {\bf and} $\mathbf{M'} \ne \mathbf{0}$}{
        $E \gets \{ \{p, i\} \mid p \in \mathcal{P}, i \in [\maxNumNodes{}],
        C_{i,r} = 1, P_{i,p} = 1, M'_{p,i} \ne 0 \}$\;
        % Because this M is a subset of the previous M
        $\mathbf{M} \gets \max \{ \mathbf{M}, \markIndices{$(\mathcal{P},
          [\maxNumNodes{}], E)$, $1$} \}$\tcp*[l]{determined positions}
      }
    }
    \Return{$\mathbf{M}$}\;
  }
\end{algorithm}

\begin{algorithm}
  \caption{Predicate-perfect bipartite matching}
  \SetKwProg{Fn}{Function}{:}{}
  \SetKwFunction{markIndices}{markIndices}
  \KwData{a bipartite graph $G = (\mathcal{P}, \mathcal{I}, E)$
    (predicates and indices) and the value $v$ to use for the matrix ($1$ or
    $\maybe{}$)}
  \KwResult{a $|\mathcal{P}| \times |\mathcal{I}|$ mask matrix $\mathbf{M}$}
  \Fn{\markIndices{$G$, $v$}}{
    $\mathbf{M} \gets \mathbf{0}_{|\mathcal{P}|,\maxNumNodes{}}$\;
    \lIf{$|\mathcal{I}| < |\mathcal{P}|$}{\Return{$\mathbf{M}$}}
    \While{true}{
      Let $(p, i) \in E$ be such that $M_{p,i} = 0$\;
      \lIf{there is none}{break}
      Let $G'$ be $G$ without vertices $p$, $i$ and all the incident edges\;
      Use alternating paths to find a $\mathcal{P}$-perfect matching $P$ in $G'$\;
      \uIf{found}{
        \lForEach{edge $(p', i') \in P$}{$M_{p',i'} = v$}
      }
      \Else{
        remove $e$ from $G$\;
        \lIf{this leaves an isolated vertex}{break}
      }
    }
    \Return{$\mathbf{M}$}\;
  }
\end{algorithm}

% TODO: need a way to prove the correctness of the algorithm. I'm not sure how I
% would approach empirical testing, so maybe do a proof instead.

% \begin{algorithm}
%   \SetKwProg{Fn}{Function}{:}{}
%   \SetKwFunction{potentialRoots}{potentialRoots}
%   \SetKwFunction{getTreeValues}{getTreeValues}
%   \SetKwFunction{getTreeStructureDomainValues}{getTreeStructureDomainValues}
%   \SetKwData{clause}{clause}
%   \KwData{connective $c$, a set of predicates $P$}
%   \Fn{\potentialRoots{\clause, $i$}} {
%     $R \gets \emptyset$\;
%     $V \gets \clause.\getTreeValues{$i$}$\;
%     \For{$v \in V$}{
%       \uIf{$v = c$}{
%         $R \gets R \cup \{ (i, |V| = 1) \}$\;
%       }
%       \ElseIf{$v \in P$}{
%         $R' \gets \clause.\getTreeStructureDomainValues{$i$}$\;
%         $R \gets R \cup \{ (r, |R'| = 1) \mid r \in R' \}$\;
%       }
%     }
%     \Return{$R$}\;
%   }
%   \caption{Potential root nodes of the required expression, assuming that the
%     node at index $i$ is part of the expression}
% \end{algorithm}

\end{document}

### 2020-02-19 src/main/Body.java

@@ -97,7 +97,7 @@ public class Body {
         return arguments;
     }
 
-    IntVar[] getPredicates() {
+    public IntVar[] getPredicates() {
         IntVar[] predicates = new IntVar[treeValues.length];
         for (int i = 0; i < treeValues.length; i++)
             predicates[i] = treeValues[i].getPredicate();
@@ -115,11 +115,21 @@ public class Body {
         return variables;
     }
 
-    IntVar[] getTreeStructure() {
+    public IntVar[] getTreeStructure() {
         return treeStructure;
     }
 
     // ======================================== OTHER GETTERS ========================================
+
+    public boolean allDetermined() {
+        for (IntVar v : treeStructure)
+            if (v.getDomainSize() != 1)
+                return false;
+        for (Node node : treeValues)
+            if (node.getPredicate().getDomainSize() != 1)
+                return false;
+        return true;
+    }
 
     /** A list of predicates featured in this clause. The sign of each predicate denotes whether the predicate is
      * negated or not (after unfolding all the logical connectives). */
@@ -174,6 +184,12 @@ public class Body {
 
     // ================================================== OUTPUT ==================================================
 
+    /** For fully-determined bodies */
+    @Override
+    public String toString() {
+        return treeToString(0) + ".";
+    }
+
     private String treeToString(int i) {
         int value = treeValues[i].getPredicate().getValue();
         if (value >= Token.TRUE.ordinal())
@@ -197,8 +213,49 @@ public class Body {
         return output.toString();
     }
 
-    @Override
-    public String toString() {
-        return treeToString(0) + ".";
+    /** For partially-determined bodies */
+    void basicToString() {
+        System.out.println("Structure: " + structureToString());
+        System.out.println("Values:    " + valuesToString());
+    }
+
+    private String structureToString() {
+        StringBuilder builder = new StringBuilder();
+        builder.append("{");
+        for (int i = 0; i < treeStructure.length; i++) {
+            if (i > 0)
+                builder.append(" ");
+            if (treeStructure[i].getDomainSize() == 1) {
+                builder.append(treeStructure[i].getValue());
+            } else {
+                builder.append("?");
+            }
+        }
+        builder.append("}");
+        return builder.toString();
+    }
+
+    private String valuesToString() {
+        StringBuilder builder = new StringBuilder();
+        builder.append("{");
+        for (int i = 0; i < treeValues.length; i++) {
+            if (i > 0)
+                builder.append(" ");
[…]

### 2020-02-19 src/main/GeneratePrograms.java

@@ -4,6 +4,7 @@ import java.io.*;
 import java.util.*;
 
 import org.chocosolver.util.tools.ArrayUtils;
+import propagators.Condition;
 
 import static java.util.stream.Collectors.toList;
 
@@ -236,10 +237,11 @@ class GeneratePrograms {
         //generateSmallPrograms();
         //generateBigPrograms(Arrays.asList(1, 2, 4, 8));
 
-        String[] predicates = new String[]{"p", "q", "r"};
-        Program p = new Program(3, 3,
-                ForbidCycles.NONE, DEFAULT_PROBABILITIES, predicates, new int[]{1, 1, 1}, new String[0],
-                new String[]{"a"}, new PredicatePair[]{new PredicatePair(predicates, "p", "q")});
+        String[] predicates = new String[]{"p", "q", "r", "s"};
+        Program p = new Program(3, 4,
+                ForbidCycles.NONE, DEFAULT_PROBABILITIES, predicates, new int[]{1, 1, 1, 1}, new String[]{"X"},
+                new String[]{}, new PredicatePair[]{new PredicatePair(predicates, "p", "q",
+                new Condition(Token.AND, new String[]{"r", "s"}, predicates))});
         p.saveProgramsToFiles(1000, "../programs/");
     }
 }

### 2020-02-19 src/main/Program.java

@@ -3,6 +3,7 @@ package main;
 import org.chocosolver.solver.Model;
 import org.chocosolver.solver.Solver;
 import org.chocosolver.solver.constraints.Constraint;
+import org.chocosolver.solver.constraints.Propagator;
 import org.chocosolver.solver.constraints.extension.Tuples;
 import org.chocosolver.solver.search.limits.FailCounter;
 import org.chocosolver.solver.search.strategy.Search;
@@ -13,6 +14,7 @@ import org.chocosolver.solver.search.strategy.strategy.StrategiesSequencer;
 import org.chocosolver.solver.variables.IntVar;
 import org.chocosolver.solver.variables.SetVar;
 import org.chocosolver.util.tools.ArrayUtils;
+import propagators.ConditionalIndependencePropagator;
 import propagators.IndependencePropagator;
 import propagators.NegativeCyclePropagator;
 
@@ -32,16 +34,17 @@ public class Program {
 
     int maxNumNodes;
     int maxArity;
-    String[] predicates;
+    public String[] predicates;
     String[] variables;
     String[] constants;
 
     Tuples aritiesTable; // used in defining constraints
 
+    public IntVar[] clauseAssignments; // an array of predicates occurring at the heads of clauses
+    public Body[] bodies; // the body of each clause
+
     private Model model;
-    private IntVar[] clauseAssignments; // an array of predicates occurring at the heads of clauses
     private Head[] clauseHeads; // full heads (predicates, variables, constants)
-    private Body[] bodies; // the body of each clause
     private IntVar[][] introductions; // for eliminating variable symmetries
     private java.util.Random rng;
 
@@ -59,6 +62,7 @@ public class Program {
         maxArity = Arrays.stream(arities).max().getAsInt();
 
         // Set up constraints
+        assert(maxNumClauses >= predicates.length);
         setUpMainConstraints();
         setUpVariableSymmetryElimination();
         setUpIndependenceConstraints();
@@ -221,10 +225,17 @@ public class Program {
                 model.ifOnlyIf(noEdge, model.and(clausesAssignedToJHaveNoI));
             }
         }
-        for (int i = 0; i < independentPairs.length; i++)
-            new Constraint("independence " + i,
-                    new IndependencePropagator(adjacencyMatrix, independentPairs[i].getFirst(),
-                            independentPairs[i].getSecond())).post();
+        for (int i = 0; i < independentPairs.length; i++) {
+            Propagator<IntVar> propagator;
[…]

### 2020-02-23 paper_extension/paper.tex
A description of the 'required formula' constraint

\documentclass{article}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\usepackage{mathtools}
\usepackage[capitalise]{cleveref}

\newcommand{\maxNumNodes}{\mathcal{M}_{\mathcal{N}}}
\newcommand{\maxNumClauses}{\mathcal{M}_{\mathcal{C}}}

\Crefname{subformula}{Subformula}{Subformulae}
\creflabelformat{subformula}{#2(#1)#3}

\begin{document}

\section{A Required Subformula}
% also note that /\ = max, and \/ = min

We describe how to add constraints to the model in order to guarantee that a
particular subformula appears somewhere in the program. In this section, a
\emph{subformula} is a formula of the form
\begin{equation} \label[subformula]{eq:subformula}
  \bigodot_{i=1}^n \mathsf{p}_i,
\end{equation}
where $\odot \in \{ \land, \lor \}$, and $(\mathsf{p}_i)_{i=1}^n$ is a finite
sequence of predicates, arguments of which are immaterial. Let
\cref{eq:subformula} be precisely the required subformula.

We say that a clause has \cref{eq:subformula} if we can find indices
$i_0, i_1, \dots, i_n \in \{0, \dots, \maxNumNodes{} - 1 \}$ such that
\[
  \mathtt{values}[i_0] = \odot,
\]
and, for each $j = 1, \dots, n$,
\[
  \mathtt{structure}[i_j] = i_0,
\]
and
\[
  \mathtt{values}[i_j] = \mathsf{p}_j.
\]
We use this idea to define several data structures for each clause, gradually
building up to a Boolean indicator for whether the clause has
\cref{eq:subformula}. First, let $\mathbf{A}$ be an $\maxNumNodes{} \times
\maxNumNodes{}$ Boolean matrix defined as
\[
  A_{i,j} \coloneqq (\mathtt{values}[i] = \odot) \land (\mathtt{structure}[j] = i),
\]
i.e., the $(i,j)$-th element is true if node $i$ is the root node of the
subformula, and node $j$ is its child. Next, let $\mathbf{B}$ be an
$\maxNumNodes{} \times n$ Boolean matrix defined as
\[
  B_{i,j} \coloneqq (\mathtt{values}[i] = \mathsf{p}_j),
\]
where the $(i,j)$-th element indicates whether node $i$ contains predicate
$\mathsf{p}_j$. We can then use $\mathbf{A}$ and $\mathbf{B}$ to define an
$\maxNumNodes{} \times n$ Boolean matrix $\mathbf{C}$ where the $(i,j)$-th
element shows whether node $i$ is a parent of a node that contains predicate
$\mathsf{p}_j$. We then have that $\mathbf{C} \coloneqq \mathbf{A} \mathbf{B}$,
i.e.,
\[
  C_{i,j} \coloneqq \bigvee_k A_{i,k} \land B_{k,j}.
\]
The Boolean variable $f_i$ that indicates whether the $i$-th clause has the
required subformula (for $i = 0, \dots, \maxNumClauses{} - 1$) can then be
expressed as
\[
  f_i \coloneqq \bigvee_j \bigwedge_k C_{j,k},
\]
i.e., the clause has \cref{eq:subformula} if there is a suitable parent node
that has all $n$ predicates as its children. Note that this allows for the
parent node to have more than $n$ children, and the order of children is
inconsequential. Finally, we can require the program to have the subformula
simply by asking for
\[
  \bigvee_i f_i
\]
to be satisfied.

\end{document}

### 2020-04-19 paper2/impact.tex
Second publication attempt

--- 2020-01-22 paper/impact.tex
@@
-% Created by tikzDevice version 0.12.3 on 2020-01-22 11:34:15
+% Created by tikzDevice version 0.12.3 on 2020-01-25 19:17:02
 % !TEX encoding = UTF-8 Unicode
@@
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (216.81,176.16);
-\definecolor{drawColor}{RGB}{255,255,255}
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (216.81,176.16);
-\end{scope}
-\begin{scope}
 \path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
-\definecolor{fillColor}{gray}{0.92}
-
-\path[fill=fillColor] ( 25.78, 19.53) rectangle (213.31,172.66);
-\definecolor{drawColor}{RGB}{255,255,255}
+\definecolor{drawColor}{gray}{0.92}
 
@@
 
-\path[] (198.49, 79.68) -- (188.26, 77.20);
+\path[] (198.49, 79.80) -- (188.26, 77.20);
 \definecolor{drawColor}{RGB}{27,158,119}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (200.30, 74.83) --
-	(210.30, 74.83) --
-	(210.23, 74.83) --
-	(210.52, 74.84) --
-	(210.80, 74.90) --
-	(211.07, 75.00) --
-	(211.33, 75.15) --
-	(211.55, 75.33) --
-	(211.74, 75.55) --
-	(211.90, 75.80) --
-	(212.01, 76.06) --
-	(212.08, 76.35) --
-	(212.11, 76.63) --
-	(212.11, 76.63) --
-	(212.11, 82.96) --
-	(212.11, 82.96) --
-	(212.08, 83.25) --
-	(212.01, 83.54) --
-	(211.90, 83.80) --
-	(211.74, 84.05) --
-	(211.55, 84.27) --
-	(211.33, 84.45) --
-	(211.07, 84.60) --
-	(210.80, 84.70) --
-	(210.52, 84.76) --
-	(210.30, 84.77) --
-	(200.30, 84.77) --
-	(200.52, 84.76) --
-	(200.23, 84.77) --
-	(199.94, 84.73) --
-	(199.66, 84.65) --
-	(199.40, 84.53) --
-	(199.16, 84.36) --
-	(198.95, 84.16) --
-	(198.77, 83.93) --
-	(198.64, 83.67) --
-	(198.55, 83.40) --
-	(198.50, 83.11) --
-	(198.49, 82.96) --
-	(198.49, 76.63) --
-	(198.50, 76.78) --
-	(198.50, 76.49) --
-	(198.55, 76.20) --
-	(198.64, 75.93) --
-	(198.77, 75.67) --
-	(198.95, 75.44) --
-	(199.16, 75.24) --
-	(199.40, 75.07) --
-	(199.66, 74.95) --
-	(199.94, 74.86) --
-	(200.23, 74.83) --
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (200.30, 74.97) --
+	(210.30, 74.97) --
+	(210.23, 74.97) --
+	(210.52, 74.98) --
+	(210.80, 75.04) --
+	(211.07, 75.14) --
+	(211.33, 75.29) --
+	(211.55, 75.47) --
+	(211.74, 75.69) --
+	(211.90, 75.94) --
+	(212.01, 76.20) --
+	(212.08, 76.49) --
+	(212.11, 76.78) --
+	(212.11, 76.78) --
+	(212.11, 83.11) --
+	(212.11, 83.11) --
+	(212.08, 83.40) --
+	(212.01, 83.68) --
+	(211.90, 83.94) --
+	(211.74, 84.19) --
+	(211.55, 84.41) --
+	(211.33, 84.59) --
+	(211.07, 84.74) --
+	(210.80, 84.84) --
+	(210.52, 84.90) --
+	(210.30, 84.91) --
+	(200.30, 84.91) --
+	(200.52, 84.90) --
+	(200.23, 84.91) --
+	(199.94, 84.88) --
+	(199.66, 84.79) --
+	(199.40, 84.67) --
+	(199.16, 84.50) --
+	(198.95, 84.30) --
+	(198.77, 84.07) --
+	(198.64, 83.81) --
+	(198.55, 83.54) --
+	(198.50, 83.25) --
+	(198.49, 83.11) --
+	(198.49, 76.78) --
+	(198.50, 76.92) --
+	(198.50, 76.63) --
+	(198.55, 76.34) --
+	(198.64, 76.07) --
+	(198.77, 75.81) --
+	(198.95, 75.58) --
+	(199.16, 75.38) --
+	(199.40, 75.21) --
+	(199.66, 75.09) --
+	(199.94, 75.01) --
+	(200.23, 74.97) --
 	cycle;
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (205.30, 77.84) {$|\mathcal{P}|$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (205.30, 77.98) {$|\mathcal{P}|$};
 \end{scope}
@@
 
-\path[] (198.97, 67.62) -- (188.26, 70.73);
+\path[] (198.97, 67.74) -- (188.26, 70.73);
 \definecolor{drawColor}{RGB}{117,112,179}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (200.77, 62.43) --
-	(210.30, 62.43) --
-	(210.23, 62.43) --
-	(210.52, 62.44) --
-	(210.80, 62.50) --
-	(211.07, 62.60) --
-	(211.33, 62.75) --
-	(211.55, 62.93) --
-	(211.74, 63.15) --
-	(211.90, 63.39) --
-	(212.01, 63.66) --
-	(212.08, 63.94) --
-	(212.11, 64.23) --
-	(212.11, 64.23) --
-	(212.11, 70.56) --
-	(212.11, 70.56) --
-	(212.08, 70.85) --
-	(212.01, 71.13) --
-	(211.90, 71.40) --
-	(211.74, 71.65) --
-	(211.55, 71.87) --
-	(211.33, 72.05) --
-	(211.07, 72.19) --
-	(210.80, 72.30) --
-	(210.52, 72.36) --
-	(210.30, 72.37) --
-	(200.77, 72.37) --
-	(200.99, 72.36) --
-	(200.70, 72.37) --
-	(200.41, 72.33) --
-	(200.13, 72.25) --
-	(199.87, 72.13) --
-	(199.63, 71.96) --
-	(199.42, 71.76) --
-	(199.25, 71.53) --
-	(199.11, 71.27) --
-	(199.02, 71.00) --
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (200.77, 62.58) --
+	(210.30, 62.58) --
+	(210.23, 62.58) --
+	(210.52, 62.59) --
+	(210.80, 62.65) --
+	(211.07, 62.75) --
+	(211.33, 62.90) --
+	(211.55, 63.08) --
+	(211.74, 63.30) --
+	(211.90, 63.54) --
+	(212.01, 63.81) --
+	(212.08, 64.09) --
+	(212.11, 64.38) --
+	(212.11, 64.38) --
+	(212.11, 70.71) --
+	(212.11, 70.71) --
+	(212.08, 71.00) --
+	(212.01, 71.29) --
+	(211.90, 71.55) --
+	(211.74, 71.80) --
+	(211.55, 72.02) --
+	(211.33, 72.20) --
+	(211.07, 72.35) --
+	(210.80, 72.45) --
+	(210.52, 72.51) --
+	(210.30, 72.52) --
+	(200.77, 72.52) --
+	(200.99, 72.51) --
+	(200.70, 72.52) --
+	(200.41, 72.48) --
+	(200.13, 72.40) --
+	(199.87, 72.28) --
+	(199.63, 72.11) --
+	(199.42, 71.91) --
+	(199.25, 71.68) --
+	(199.11, 71.42) --
+	(199.02, 71.15) --
+	(198.97, 70.86) --
 	(198.97, 70.71) --
-	(198.97, 70.56) --
-	(198.97, 64.23) --
 	(198.97, 64.38) --
-	(198.97, 64.09) --
-	(199.02, 63.80) --
-	(199.11, 63.53) --
-	(199.25, 63.27) --
-	(199.42, 63.04) --
-	(199.63, 62.83) --
-	(199.87, 62.67) --
-	(200.13, 62.54) --
-	(200.41, 62.46) --
-	(200.70, 62.43) --
+	(198.97, 64.53) --
+	(198.97, 64.24) --
+	(199.02, 63.95) --
+	(199.11, 63.68) --
+	(199.25, 63.42) --
+	(199.42, 63.19) --
+	(199.63, 62.99) --
+	(199.87, 62.82) --
+	(200.13, 62.70) --
+	(200.41, 62.61) --
+	(200.70, 62.58) --
 	cycle;
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (205.54, 65.44) {$|\mathcal{V}|$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (205.54, 65.59) {$|\mathcal{V}|$};
 \end{scope}
@@
 
-\path[] (199.59, 56.21) -- (188.26, 67.83);
+\path[] (199.59, 56.31) -- (188.26, 67.83);
 \definecolor{drawColor}{RGB}{231,41,138}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (201.40, 50.08) --
-	(210.30, 50.08) --
-	(210.23, 50.08) --
-	(210.52, 50.10) --
-	(210.80, 50.15) --
-	(211.07, 50.26) --
-	(211.33, 50.40) --
-	(211.55, 50.59) --
-	(211.74, 50.80) --
-	(211.90, 51.05) --
-	(212.01, 51.32) --
-	(212.08, 51.60) --
-	(212.11, 51.89) --
-	(212.11, 51.89) --
-	(212.11, 58.22) --
-	(212.11, 58.22) --
-	(212.08, 58.51) --
-	(212.01, 58.79) --
-	(211.90, 59.06) --
-	(211.74, 59.30) --
-	(211.55, 59.52) --
-	(211.33, 59.71) --
-	(211.07, 59.85) --
-	(210.80, 59.95) --
-	(210.52, 60.01) --
-	(210.30, 60.02) --
-	(201.40, 60.02) --
-	(201.62, 60.01) --
-	(201.33, 60.02) --
-	(201.04, 59.99) --
-	(200.76, 59.91) --
-	(200.50, 59.78) --
-	(200.26, 59.62) --
-	(200.05, 59.42) --
-	(199.87, 59.18) --
-	(199.74, 58.93) --
-	(199.65, 58.65) --
-	(199.60, 58.36) --
-	(199.59, 58.22) --
-	(199.59, 51.89) --
-	(199.60, 52.03) --
-	(199.60, 51.74) --
-	(199.65, 51.46) --
-	(199.74, 51.18) --
-	(199.87, 50.92) --
-	(200.05, 50.69) --
-	(200.26, 50.49) --
-	(200.50, 50.32) --
-	(200.76, 50.20) --
-	(201.04, 50.12) --
-	(201.33, 50.08) --
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (201.40, 50.18) --
+	(210.30, 50.18) --
+	(210.23, 50.18) --
+	(210.52, 50.19) --
+	(210.80, 50.25) --
+	(211.07, 50.35) --
+	(211.33, 50.50) --
+	(211.55, 50.68) --
+	(211.74, 50.90) --
+	(211.90, 51.15) --
+	(212.01, 51.41) --
+	(212.08, 51.70) --
+	(212.11, 51.99) --
+	(212.11, 51.99) --
+	(212.11, 58.31) --
+	(212.11, 58.31) --
+	(212.08, 58.60) --
+	(212.01, 58.89) --
+	(211.90, 59.15) --
+	(211.74, 59.40) --
+	(211.55, 59.62) --
+	(211.33, 59.80) --
+	(211.07, 59.95) --
+	(210.80, 60.05) --
+	(210.52, 60.11) --
+	(210.30, 60.12) --
+	(201.40, 60.12) --
+	(201.62, 60.11) --
+	(201.33, 60.12) --
+	(201.04, 60.08) --
+	(200.76, 60.00) --
+	(200.50, 59.88) --
+	(200.26, 59.71) --
+	(200.05, 59.51) --
+	(199.87, 59.28) --
+	(199.74, 59.02) --
+	(199.65, 58.75) --
+	(199.60, 58.46) --
+	(199.59, 58.31) --
+	(199.59, 51.99) --
+	(199.60, 52.13) --
+	(199.60, 51.84) --
+	(199.65, 51.55) --
+	(199.74, 51.28) --
+	(199.87, 51.02) --
+	(200.05, 50.79) --
+	(200.26, 50.59) --
+	(200.50, 50.42) --
+	(200.76, 50.30) --
+	(201.04, 50.22) --
+	(201.33, 50.18) --
 	cycle;
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (205.85, 53.09) {$|\mathcal{C}|$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (205.85, 53.19) {$|\mathcal{C}|$};
 \end{scope}
@@
 
-\path[] (189.92, 87.17) -- (188.26, 79.66);
+\path[] (189.67, 87.32) -- (188.26, 79.66);
 \definecolor{drawColor}{RGB}{102,166,30}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (176.58, 87.17) --
-	(203.32, 87.17) --
-	(203.24, 87.17) --
-	(203.53, 87.19) --
-	(203.82, 87.24) --
-	(204.09, 87.35) --
-	(204.34, 87.49) --
-	(204.57, 87.68) --
-	(204.76, 87.89) --
-	(204.92, 88.14) --
-	(205.03, 88.41) --
-	(205.10, 88.69) --
-	(205.12, 88.98) --
-	(205.12, 88.98) --
-	(205.12, 95.31) --
-	(205.12, 95.31) --
-	(205.10, 95.60) --
-	(205.03, 95.88) --
-	(204.92, 96.15) --
-	(204.76, 96.39) --
-	(204.57, 96.61) --
-	(204.34, 96.79) --
-	(204.09, 96.94) --
-	(203.82, 97.04) --
-	(203.53, 97.10) --
-	(203.32, 97.11) --
-	(176.58, 97.11) --
-	(176.79, 97.10) --
-	(176.50, 97.11) --
-	(176.21, 97.08) --
-	(175.93, 97.00) --
-	(175.67, 96.87) --
-	(175.43, 96.71) --
-	(175.22, 96.51) --
-	(175.05, 96.27) --
-	(174.91, 96.02) --
-	(174.82, 95.74) --
-	(174.77, 95.45) --
-	(174.77, 95.31) --
-	(174.77, 88.98) --
-	(174.77, 89.12) --
-	(174.77, 88.83) --
-	(174.82, 88.55) --
-	(174.91, 88.27) --
-	(175.05, 88.01) --
-	(175.22, 87.78) --
-	(175.43, 87.58) --
-	(175.67, 87.41) --
-	(175.93, 87.29) --
-	(176.21, 87.21) --
-	(176.50, 87.17) --
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (176.31, 87.32) --
+	(203.05, 87.32) --
+	(202.98, 87.32) --
+	(203.27, 87.33) --
+	(203.56, 87.39) --
+	(203.83, 87.49) --
+	(204.08, 87.64) --
+	(204.31, 87.82) --
+	(204.50, 88.04) --
+	(204.65, 88.28) --
+	(204.77, 88.55) --
+	(204.84, 88.83) --
+	(204.86, 89.12) --
+	(204.86, 89.12) --
+	(204.86, 95.45) --
+	(204.86, 95.45) --
+	(204.84, 95.74) --
+	(204.77, 96.03) --
+	(204.65, 96.29) --
+	(204.50, 96.54) --
+	(204.31, 96.76) --
+	(204.08, 96.94) --
+	(203.83, 97.09) --
+	(203.56, 97.19) --
+	(203.27, 97.25) --
+	(203.05, 97.26) --
+	(176.31, 97.26) --
+	(176.53, 97.25) --
+	(176.24, 97.26) --
+	(175.95, 97.22) --
+	(175.67, 97.14) --
+	(175.41, 97.02) --
+	(175.17, 96.85) --
+	(174.96, 96.65) --
+	(174.79, 96.42) --
+	(174.65, 96.16) --
+	(174.56, 95.89) --
+	(174.51, 95.60) --
+	(174.51, 95.45) --
+	(174.51, 89.12) --
+	(174.51, 89.27) --
+	(174.51, 88.98) --
+	(174.56, 88.69) --
+	(174.65, 88.42) --
+	(174.79, 88.16) --
+	(174.96, 87.93) --
+	(175.17, 87.72) --
+	(175.41, 87.56) --
+	(175.67, 87.44) --
+	(175.95, 87.35) --
+	(176.24, 87.32) --
 	cycle;
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (189.95, 90.18) {$\mathcal{M}_{\mathcal{C}}-|\mathcal{P}|$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (189.68, 90.33) {$\mathcal{M}_{\mathcal{C}}-|\mathcal{P}|$};
 \end{scope}
@@
 	(145.14, 84.48) --
-	(144.98, 84.73) --
+	(144.98, 84.72) --
 	(144.79, 84.94) --
@@
 	(144.31, 85.27) --
-	(144.04, 85.38) --
+	(144.04, 85.37) --
 	(143.75, 85.43) --
@@
 	(128.60, 84.07) --
-	(128.55, 83.79) --
+	(128.55, 83.78) --
 	(128.55, 83.64) --
@@
 \path[clip] (  0.00,  0.00) rectangle (216.81,176.16);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 24.03, 25.58) --
-	( 25.78, 25.58);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 24.03, 76.58) --
-	( 25.78, 76.58);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 24.03,127.57) --
-	( 25.78,127.57);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (216.81,176.16);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 34.30, 17.78) --
-	( 34.30, 19.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 85.62, 17.78) --
-	( 85.62, 19.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] (136.94, 17.78) --
-	(136.94, 19.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round] (188.26, 17.78) --
-	(188.26, 19.53);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (216.81,176.16);
 \definecolor{drawColor}{gray}{0.30}

### 2020-04-19 paper2/paper.tex
Second publication attempt

--- 2020-02-17 paper/paper.tex
@@
-\documentclass[letterpaper]{article}
-\usepackage{uai2020}
-\usepackage[margin=1in]{geometry}
-\usepackage{times}
-
+\documentclass[runningheads]{llncs}
 \usepackage[ruled,vlined]{algorithm2e}
@@
 \usepackage{siunitx}
-\usepackage{amsthm}
-\usepackage[round]{natbib}
 \usepackage[inline]{enumitem}
-
-\newtheorem{constraint}{Constraint}
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
-\newtheorem{example}{Example}
+\usepackage{capt-of}
+\usepackage[caption=false]{subfig}
+
+\captionsetup[subfigure]{width=\linewidth}
 
@@
 
-\makeatletter
-\newcommand{\nosemic}{\renewcommand{\@endalgocfline}{\relax}}% Drop semi-colon ;
-\newcommand{\dosemic}{\renewcommand{\@endalgocfline}{\algocf@endline}}% Reinstate semi-colon ;
-\newcommand{\pushline}{\Indp}% Indent
-\newcommand{\popline}{\Indm\dosemic}% Undent
-\makeatother
-
 \newcommand{\logical}[1]{{\normalfont \texttt{#1}}}
@@
 \newcommand{\arrayd}[3]{\variable{{#1}[}{#2}\variable{]} \in {#3}}
-
 % 1=name, 2=length, 3=type
@@
 
+\makeatletter
+\newcommand{\nosemic}{\renewcommand{\@endalgocfline}{\relax}}% Drop semi-colon ;
+\newcommand{\dosemic}{\renewcommand{\@endalgocfline}{\algocf@endline}}% Reinstate semi-colon ;
+\newcommand{\pushline}{\Indp}% Indent
+\newcommand{\popline}{\Indm\dosemic}% Undent
+\makeatother
+
+\spnewtheorem{constraint}{Constraint}{\bfseries}{\itshape}
+
 \DeclareMathOperator{\Determined}{\Delta}
@@
 \Crefname{constraint}{Constraint}{Constraints}
-\Crefname{clause}{Clause}{Clauses}
-\creflabelformat{clause}{#2(#1)#3}
+\crefname{section}{Sect.}{Sects.}
 
 \usetikzlibrary{arrows.meta}
-\relpenalty=10000
-\binoppenalty=10000
+%\relpenalty=10000
+%\binoppenalty=10000
 \def\multiset#1#2{\ensuremath{\left(\kern-.3em\left(\genfrac{}{}{0pt}{}{#1}{#2}\right)\kern-.3em\right)}}
 
+\begin{document}
+
 \title{Generating Random Logic Programs Using Constraint Programming}
-
-\author{}
-
-%\author{ {\bf Paulius Dilkas} \\
-%School of Informatics \\
-%University of Edinburgh \\
-%Edinburgh, United Kingdom \\
-%}
-
-\begin{document}
-\bibliographystyle{abbrvnat}
+%\author{Paulius Dilkas\inst{1} \and
+%Vaishak Belle\inst{1,2}}
+%\authorrunning{P. Dilkas and V. Belle}
+%\institute{University of Edinburgh, Edinburgh, UK \email{\{p.dilkas@sms.,vaishak@\}ed.ac.uk} \and Alan Turing Institute, London, UK}
+
 \maketitle
 
+%The abstract should briefly summarize the contents of the paper in
+%150--250 words.
 \begin{abstract}
@@
   difficulty of the program generation task.
+
+  \keywords{Probabilistic logic programming \and Logic programming \and
+    Predicate independence.}
 \end{abstract}
 
-\section{INTRODUCTION}
-
-% Notes on papers that test ProbLog inference algorithms:
-% - On the Implementation: published, one biological network
-% -(removed) Nesting Probabilistic Inference: NOT published, one Alzheimer
-% network
-% -(removed) DNF Sampling: NOT published, two networks: a family tree and the
-% Alzheimer network
-% -ProbLog Technology: published, two networks: a custom theory with randomly
-% generated data, and citation data
-% -Anytime Inference: published, four networks: the Smokers social network,
-% Alzheimer data, biological network of genetic data, data about the world wide
-% web
-
-%Interestingly, in the [???] of
-%probabilistic logic programming, random logic program generators can be useful
-%in combination with methods that generate random data with probabilistic logic
-%programs \citep{DBLP:conf/soict/Dries15} and can be used as a component of
-%learning.
+% TODO (for later)
+% 1) First keyword should be the category that I'm submitting for
+% 2) Use American English
+% 3) Avoid the Definition environment (to save space)
+% 4) Make sure that figures and algorithms are placed in good positions
+
+\section{Introduction}
 
 Unifying logic and probability is a long-standing challenge in artificial
-intelligence \citep{DBLP:journals/cacm/Russell15}, and, in that regard,
+intelligence \cite{DBLP:journals/cacm/Russell15}, and, in that regard,
 statistical relational learning (SRL) has developed into an exciting area that
@@
 particular, logic programs and probabilistic logic programs---including
-languages such as PRISM \citep{DBLP:conf/ijcai/SatoK97}, ICL
-\citep{DBLP:journals/ai/Poole97}, and ProbLog
-\citep{DBLP:conf/ijcai/RaedtKT07}---are promising frameworks for codifying
+languages such as PRISM \cite{DBLP:conf/ijcai/SatoK97}, ICL
+\cite{DBLP:journals/ai/Poole97}, and ProbLog
+\cite{DBLP:conf/ijcai/RaedtKT07}---are promising frameworks for codifying
 complex SRL models. With the enhanced structure, however, inference becomes more
@@
 data sets
-\citep{DBLP:journals/tplp/KimmigDRCR11,DBLP:conf/ecai/BruynoogheMKGVJR10,DBLP:conf/ijcai/VlasselaerBKMR15},
+\cite{DBLP:conf/ecai/BruynoogheMKGVJR10,DBLP:journals/tplp/KimmigDRCR11,DBLP:conf/ijcai/VlasselaerBKMR15},
 originating from areas such as social networks, citation patterns, and
@@
 About thirty years ago, SAT solving technology was dealing with a similar lack
-of clarity \citep{DBLP:journals/ai/SelmanML96}. This changed with the study of
+of clarity \cite{DBLP:journals/ai/SelmanML96}. This changed with the study of
 generation of random SAT instances against different input parameters (e.g.,
@@
 approaches to random instance generation are very restrictive, e.g., limited to
-clauses with only two literals \citep{DBLP:conf/lpnmr/NamasivayamT09}, or to
-clauses of the form $a \gets \neg b$ \citep{DBLP:journals/tocl/WenWSL16},
+clauses with only two literals \cite{DBLP:conf/lpnmr/NamasivayamT09}, or to
+clauses of the form $a \gets \neg b$ \cite{DBLP:journals/tocl/WenWSL16},
 although some are more expressive, e.g., defining a program only by the
 (maximum) number of atoms in the body and the total number of rules
-\citep{DBLP:conf/iclp/ZhaoL03}.
+\cite{DBLP:conf/iclp/ZhaoL03}.
 
@@
 the program. In fact, the same model can generate both probabilistic programs
-directly in the syntax of ProbLog \citep{DBLP:conf/ijcai/RaedtKT07} and
+directly in the syntax of ProbLog \cite{DBLP:conf/ijcai/RaedtKT07} and
 non-probabilistic Prolog programs. For generated probabilistic programs to be
@@
 languages and frameworks, which capture a major fragment of SRL
-\citep{DBLP:series/synthesis/2016Raedt}. However, since probabilistic logic
+\cite{DBLP:series/synthesis/2016Raedt}. However, since probabilistic logic
 programming languages are closely related to other areas of machine learning,
 including (imperative) probabilistic programming
-\citep{DBLP:journals/ml/RaedtK15}, our results can lay the foundations for
+\cite{DBLP:journals/ml/RaedtK15}, our results can lay the foundations for
 exploring broader questions on generating models and testing algorithms in
@@
 
-\section{PRELIMINARIES}
+\section{Preliminaries}
 
@@
 
-\subsection{PARAMETERS OF THE MODEL}
+\subsection{Parameters of the Model}
 
@@
 
-\section{HEADS OF CLAUSES} \label{sec:heads}
+\section{Heads of Clauses} \label{sec:heads}
 
@@
 \begin{constraint} \label{constr:arity}
-  For $i = 0, \dots, \maxArity{} - 1$,
-  \[
-    \variable{arguments}[i] = \Box \iff i \ge \variable{arity}.
-  \]
+  For $i = 0, \dots, \maxArity{} - 1$, $\variable{arguments}[i] = \Box \iff i
+  \ge \variable{arity}$.
 \end{constraint}
@@
 \begin{constraint}
-Let
-  \[
-    P = \{ h.\variable{predicate} \mid h \in \variable{heads} \}.
-  \]
-  Then $\variable{nValues}(P) = |\predicates{}|$ if $\variable{count}(\Box, P) =
-  0$ and $|\predicates{}| + 1$ otherwise, where $\variable{nValues}(P)$ counts
-  the number of unique values in $P$.
-\end{constraint}
-
-\section{BODIES OF CLAUSES} \label{sec:bodies}
+  Let $P = \{ h.\variable{predicate} \mid h \in \variable{heads} \}$. Then
+  \[
+    \variable{nValues}(P) = \begin{cases}
+      |\predicates{}| & \text{if } \variable{count}(\Box, P) = 0 \\
+      |\predicates{}| + 1 & \text{otherwise,}
+    \end{cases}
+  \]
+  where $\variable{nValues}(P)$ counts the number of unique values in $P$.
+\end{constraint}
+
+\section{Bodies of Clauses} \label{sec:bodies}
 
@@
 
+% TODO: fix the formatting issue
 \begin{definition}
@@
 
-We can use the $\variable{tree}$ constraint \citep{DBLP:conf/cp/FagesL11} to
+We can use the $\variable{tree}$ constraint \cite{DBLP:conf/cp/FagesL11} to
 forbid cycles in the $\variable{structure}$ array and simultaneously define
@@
 \end{definition}
+
+\begin{example} \label{example:formula}
+  Let $\maxNumNodes{} = 8$. Then
+  \[
+    \neg\mathsf{P}(X) \lor (\mathsf{Q}(X) \land \mathsf{P}(X))
+  \]
+  corresponds to the tree in \cref{fig:example_tree} and can be encoded as:
+  \begin{alignat*}{8}
+    \variable{structure} &= [0, &&0, &&0, &&1, &&2, &&2, &&6, &&7],\\
+    \variable{values} &= [{\lor}, &&{\neg}, &&{\land}, \mathsf{P}(&&X),
+    \mathsf{Q}(&&X), \mathsf{P}(&&X), &&\top, &&\top],\\
+    \variable{numNodes} &= 6, && && && && && && &&\\
+    \variable{numTrees} &= 3. && && && && && && &&
+  \end{alignat*}
+\end{example}
 
@@
 
-\begin{example} \label{example:formula}
-  Let $\maxNumNodes{} = 8$. Then
-  \[
-    \neg\mathsf{P}(X) \lor (\mathsf{Q}(X) \land \mathsf{P}(X))
-  \]
-  corresponds to the tree in \cref{fig:example_tree} and can be encoded as:
-  \begin{alignat*}{8}
-    \variable{structure} &= [0, &&0, &&0, &&1, &&2, &&2, &&6, &&7],\\
-    \variable{values} &= [{\lor}, &&{\neg}, &&{\land}, \mathsf{P}(&&X), \mathsf{Q}(&&X), \mathsf{P}(&&X), &&\top, &&\top],\\
-    \variable{numNodes} &= 6, && && && && && && &&\\
-    \variable{numTrees} &= 3. && && && && && && &&
-  \end{alignat*}
-\end{example}
-
 Here, $\top$ is the value we use for the remaining one-node trees. The
@@
   For $i = 0, \dots, \maxNumNodes{} - 1$, let $C_i$ be the number of times $i$
-  appears in the \variable{struture} array with index greater than $i$. Then
+  appears in the \variable{structure} array with index greater than $i$. Then
   \begin{align*}
@@
   \[
-    \variable{bodies}[i].\variable{numNodes} = 1,
-  \]
-  and
-  \[
-    \variable{bodies}[i].\variable{values}[0].\variable{name} =
-    \top.
-  \]
-\end{constraint}
-
-\section{VARIABLE SYMMETRIES} \label{sec:variable_symmetry}
+    \variable{bodies}[i].\variable{numNodes} = 1, \quad \text{and}
+    \quad \variable{bodies}[i].\variable{values}[0].\variable{name} = \top.
+  \]
+\end{constraint}
+
+\section{Variable Symmetries} \label{sec:variable_symmetry}
 
@@
     i \in \variable{occ}[t] \quad \iff \quad
-    \variable{terms}[i] = t
+    \variable{terms}[i] = t.
   \]
@@
 
-\subsection{REDUNDANT CONSTRAINTS}
+\subsection{Redundant Constraints}
 
@@
   For $u \ne v \in \constants{} \cup \variables{} \cup \{ \Box \}$,
-  \[
-    \variable{occ}[u] \cap \variable{occ}[v] = \emptyset.
-  \]
+  $\variable{occ}[u] \cap \variable{occ}[v] = \emptyset$.
 \end{constraint}
@@
 
-\section{COUNTING PROGRAMS} \label{sec:counting}
+\section{Counting Programs} \label{sec:counting}
+
+\setcounter{footnote}{0}
 
@@
 definition can be applied for $n > 1$:
-\begin{align*}
-  T(n, a) = T(n-1, a) + 2&\sum_{\substack{c_1 + \dots + c_k = n - 1,\\
-      2 \le k \le \frac{a}{\min \arities{}},\\
-  c_i \ge 1 \text{ for all } i}}\\
-  &\sum_{\substack{d_1 + \dots + d_k = a,\\
-  d_i \ge \min \arities{} \text{ for all } i}} \prod_{i=1}^k T(c_i, d_i).
-\end{align*}
+\[
+  T(n, a) = T(n-1, a) + 2\sum_{\substack{c_1 + \dots + c_k = n - 1,\\ 2 \le k
+      \le \frac{a}{\min \arities{}},\\ c_i \ge 1 \text{ for all } i}}
+  \sum_{\substack{d_1 + \dots + d_k = a,\\ d_i \ge \min \arities{} \text{ for
+        all } i}} \prod_{i=1}^k T(c_i, d_i).
+\]
 The first term here represents negation, i.e., negating a formula consumes
@@
 The number of ways to select $n$ terms is
-\begin{align*}
-  P(n) = |\constants{}|^n + &\sum_{\substack{1 \le k \le |\variables{}|, \\ 0 =
-      s_0 < s_1 < \dots < s_k < s_{k+1} = n+1}}\\
-  &\prod_{i=0}^k (|\constants{}| + i)^{s_{i+1} - s_i - 1}.
-\end{align*}
+\[
+  P(n) = |\constants{}|^n + \sum_{\substack{1 \le k \le |\variables{}|, \\ 0 =
+      s_0 < s_1 < \dots < s_k < s_{k+1} = n+1}} \prod_{i=0}^k (|\constants{}| +
+  i)^{s_{i+1} - s_i - 1}.
+\]
 The first term is the number of ways select $n$ constants. The parameter $k$ is
@@
 
-\section{PREDICATE INDEPENDENCE} \label{sec:independence}
+\section{Predicate Independence} \label{sec:independence}
 
@@
 
+\begin{example} \label{ex:program}
+  Consider the following (fragment of a) program:
+  \begin{align}
+    \mathsf{sibling}(X, Y) &\gets \mathsf{parent}(X, Z) \land \mathsf{parent}(Y, Z), \nonumber \\
+    \mathsf{father}(X, Y) &\gets \mathsf{parent}(X, Y) \land \neg\mathsf{mother}(X, Y). \label[clause]{eq:example_clause}
+  \end{align}
+  Its predicate dependency graph is in \cref{fig:predicate_dependencies}.
+  Because of the negation in \eqref{eq:example_clause} (as seen in
+  \cref{fig:example_tree2}), the edge from $\mathsf{mother}$ to
+  $\mathsf{father}$ is negative, while the other two edges are positive.
+
 \begin{figure}
+  \centering
+  \begin{minipage}{.49\textwidth}
     \centering
@@
     \end{tikzpicture}
-  \caption{A tree representation of the body of \cref{eq:example_clause}}
+    \captionof{figure}{A tree representation of the body of \eqref{eq:example_clause}}
     \label{fig:example_tree2}
-\end{figure}
-\begin{figure}
+  \end{minipage}
+  \begin{minipage}{.49\textwidth}
     \centering
@@
     \end{tikzpicture}
-  \caption{The predicate dependency graph of the program in \cref{ex:program}.
-    Positive edges are labelled with `$+$', and negative edges with `$-$'.}
+    \captionof{figure}{The predicate dependency graph of the program in
+      \cref{ex:program}. Positive edges are labelled with `$+$', and negative
+      edges with `$-$'.}
     \label{fig:predicate_dependencies}
+  \end{minipage}
 \end{figure}
-
-\begin{example} \label{ex:program}
-  Consider the following (fragment of a) program:
-  \begin{align}
-    \mathsf{sibling}(X, Y) &\gets \mathsf{parent}(X, Z) \land \mathsf{parent}(Y, Z), \nonumber \\
-    \mathsf{father}(X, Y) &\gets \mathsf{parent}(X, Y) \land \neg\mathsf{mother}(X, Y) \label[clause]{eq:example_clause}
-  \end{align}
-  Its predicate dependency graph is in \cref{fig:predicate_dependencies}.
-  Because of the negation in \cref{eq:example_clause} (as seen in
-  \cref{fig:example_tree2}), the edge from $\mathsf{mother}$ to
-  $\mathsf{father}$ is negative, while the other two edges are positive.
 
@@
   \begin{alignat*}{3}
-    D_{\mathsf{parent}} &= \{ \mathsf{parent} \}, && D_{\mathsf{sibling}}
+    D_{\mathsf{parent}} &= \{ \mathsf{parent} \}, \quad && D_{\mathsf{sibling}}
     &&= \{\mathsf{sibling}, \mathsf{parent} \},\\
-    D_{\mathsf{mother}} &= \{ \mathsf{mother} \}, && D_{\mathsf{father}}
+    D_{\mathsf{mother}} &= \{ \mathsf{mother} \}, \quad && D_{\mathsf{father}}
     &&= \{ \mathsf{father}, \mathsf{mother}, \mathsf{parent} \}.
@@
   if and only if, for all $k \in \{ 0, \dots, \maxNumClauses{} - 1 \}$, either
-  \[
-    \variable{heads}[k].\variable{predicate} \ne j
-  \]
-  or $ i \not\in \{a.\variable{name} \mid a \in
-  \variable{bodies}[k].\variable{values} \}$.
+  $\variable{heads}[k].\variable{predicate} \ne j$ or $ i \not\in
+  \{a.\variable{name} \mid a \in \variable{bodies}[k].\variable{values} \}$.
 \end{definition}
@@
   \KwData{predicates $p_1$, $p_2$}
-  \nosemic $D \gets \{ (d_1, d_2) \in \getDependencies{$p_1$, 1} \times \getDependencies{$p_2$, 1}$\;
-  \hspace{27pt}\dosemic $\mid d_1.\predicate = d_2.\predicate \}$\;
+  $D \gets \{ (d_1, d_2) \in \getDependencies{$p_1$, 1} \times
+  \getDependencies{$p_2$, 1} \mid d_1.\predicate = d_2.\predicate \}$\;
   \lIf{$D = \emptyset$}{\Return{\textsc{true}}}
-  \lIf{$\exists (\Determined \_, \Determined \_) \in D$}{\Return{\textsc{false}}}
-  \Return{\textsc{undefined}}\;
+  \leIf{$\exists (\Determined \_, \Determined \_) \in
+    D$}{\Return{\textsc{false}}}{\Return{\textsc{undefined}}}
   \caption{Entailment for independence}
@@
 satisfied or not depends on the future decisions made by the solver.
-\cref{alg:independence_entailment} outlines a simple entailment algorithm for
+\Cref{alg:independence_entailment} outlines a simple entailment algorithm for
 the independence of two predicates $p_1$ and $p_2$. First, we separately
@@
   \For{$(d_1, d_2) \in \getDependencies{$p_1$, 0} \times \getDependencies{$p_2$,
-      0}$ such that $d_1.\predicate = d_2.\predicate$}{
+      0}$ s.t. $d_1.\predicate = d_2.\predicate$}{
     \lIf{$d_1$ {\bf is} $\Determined(\_)$ {\bf and} $d_2$ {\bf is}
@@
     \If{$d_1$ {\bf is} $\Determined(\_)$ {\bf and} $d_2$ {\bf is}
-      $\AlmostDetermined(\_, s, t)$ {\bf or} \hspace{50pt} $d_2$ {\bf is}
-      $\Determined(\_)$ {\bf and} $d_1$ {\bf is} $\AlmostDetermined(\_, s,
+      $\AlmostDetermined(\_, s, t)$ {\bf or} $d_2$ {\bf is} $\Determined(\_)$
+      {\bf and} $d_1$ {\bf is} $\AlmostDetermined(\_, s,
       t)$ \label{line:propagation_condition}}{
@@
 
+\begin{example} \label{example:independence}
+  Consider this partially determined (fragment of a) program:
+  \begin{align*}
+    \Box(X, Y) &\gets \mathsf{parent}(X, Z) \land \mathsf{parent}(Y, Z),\\
+    \mathsf{father}(X, Y) &\gets \mathsf{parent}(X, Y) \land \neg\mathsf{mother}(X, Y),
+  \end{align*}
+  where $\Box$ indicates an unknown predicate with domain
+  \[
+    D_\Box = \{ \mathsf{father}, \mathsf{mother}, \mathsf{parent},
+    \mathsf{sibling} \}.
+  \]
+  The predicate dependency graph without positivity/negativity (as defined in
+  \cref{def:adjacency_matrix}) is represented in
+  \cref{fig:dependencies_matrix,fig:dependencies2}.
+
+  % TODO: labels on the inside (check if they work)
   \begin{figure}
+    \begin{minipage}{.49\textwidth}
       \centering
-  \[
-    \begin{blockarray}{ccccc}
-      \begin{block}{c(cccc)}
+      \subfloat[The adjacency matrix defined using \cref{def:adjacency_matrix} for
+      \cref{example:independence}\label{fig:dependencies_matrix}]{
+        $\begin{blockarray}{lcccc}
+          \begin{block}{l!{\quad}(cccc)}
             \mathsf{father} & 0 & 0 & 0 & 0 \\
@@
           \end{block}
-    \end{blockarray}
-  \]
-  \caption{The adjacency matrix defined using \cref{def:adjacency_matrix} for
-    \cref{example:independence}}
-  \label{fig:dependencies_matrix}
-\end{figure}
-\begin{figure}
+        \end{blockarray}$
+      }
+    \end{minipage}
+    \hfill
+    \begin{minipage}{.49\textwidth}
       \centering
+      \subfloat[The predicate dependency graph that corresponds to
+      \cref{fig:dependencies_matrix}. Dashed edges are undetermined---they may or
+      may not exist.\label{fig:dependencies2}]{
+        \centering
+        \makebox[\linewidth]{
           \begin{tikzpicture}
@@
           \end{tikzpicture}
-  \caption{The predicate dependency graph that corresponds to
-    \cref{fig:dependencies_matrix}. Dashed edges are undetermined---they may
-    or may not exist.}
-  \label{fig:dependencies2}
+        }
+      }
+    \end{minipage}
+    \caption{TODO}
   \end{figure}
-
-\begin{example} \label{example:independence}
-  Consider this partially determined (fragment of a) program:
-  \begin{align*}
-    \Box(X, Y) &\gets \mathsf{parent}(X, Z) \land \mathsf{parent}(Y, Z),\\
-    \mathsf{father}(X, Y) &\gets \mathsf{parent}(X, Y) \land \neg\mathsf{mother}(X, Y)
-  \end{align*}
-  where $\Box$ indicates an unknown predicate with domain
-  \[
-    D_\Box = \{ \mathsf{father}, \mathsf{mother}, \mathsf{parent},
-    \mathsf{sibling} \}.
-  \]
-  The predicate dependency graph without positivity/negativity (as defined in
-  \cref{def:adjacency_matrix}) is represented in
-  \cref{fig:dependencies_matrix,fig:dependencies2}.
 
@@
 
-\section{NEGATIVE CYCLES} \label{sec:cycles}
+\section{Negative Cycles} \label{sec:cycles}
 % although some work has been done in overcoming this limitation
-% \citep{DBLP:journals/ijar/BuchmanP17}
+% \cite{DBLP:journals/ijar/BuchmanP17}
 
 Having no negative cycles in the predicate dependency graph is a requirement of
-ProbLog that makes the program well-defined \citep{kimmig2009trading}. Ideally,
+ProbLog that makes the program well-defined \cite{kimmig2009trading}. Ideally,
 we would like to design a constraint for negative cycles similar to the
@@
 the literature, and use an algorithm such as Bellman-Ford
-\citep{shimbel1954structure}.
+\cite{shimbel1954structure}.
 
@@
 
-\section{EMPIRICAL PERFORMANCE} \label{sec:experiments}
-
-\begin{figure}
-  \centering
-  \input{impact.tex}
-  \caption{The mean number of nodes in the binary search tree for each value of
-    each experimental parameter. Note that the horizontal axis is on a $\log_2$
-    scale.}
-  \label{fig:impact}
-\end{figure}
-
-\begin{figure*}
-  \centering
-  \input{phase_transition.tex}
-  \caption{The distribution of the number of nodes in the binary search tree as
-    a function of the number of independent pairs of predicates for
-    $|\predicates| = 8$. Outliers are hidden, the dots denote mean values, and
-    the vertical axis is on a $\log_{10}$ scale.}
-  \label{fig:phase_transition}
-\end{figure*}
+\section{Empirical Performance} \label{sec:experiments}
 
@@
 what parameter values make the constraint satisfaction problem harder. For these
-experiments, we use Choco~4.10.2 \citep{choco} with Java~8. For
+experiments, we use Choco~4.10.2 \cite{choco} with Java~8. For
 $|\predicates{}|$, $|\variables{}|$, $|\constants{}|$, $\maxNumNodes{}$, and
@@
 
-\cref{fig:phase_transition} takes the data for $|\predicates{}| = 8$ (almost
-\num{300000} observations) and shows how the number of nodes in the search tree
-varies with the number of independent pairs of predicates. The box plots show
-that the median number of nodes stays about the same while the dots
-(representing the means) draw an arc. This suggests a type of phase transition,
-but only in mean rather than median, i.e., most problems remain easy, but with
-some parameter values hard problems become more likely. On the one hand, with
-few pairs of independent predicates, one can easily find the right combination
-of predicates to use in each clause. On the other hand, if most predicates must
-be independent, this leaves fewer predicates that can be used in the body of
-each clause (since all of them have to be independent with the head predicate),
-and we can either quickly find a solution or identify that there is none.
-
-% TODO: Extra notes.
+\begin{figure}
+  \centering
+  \input{impact.tex}
+  \caption{The mean number of nodes in the binary search tree for each value of
+    each experimental parameter. Note that the horizontal axis is on a $\log_2$
+    scale.}
+  \label{fig:impact}
+\end{figure}
+
+\section{Conclusions}
+
+We were able to design an efficient model for generating both logic programs and
+probabilistic logic programs. The model avoids unnecessary symmetries, generates
+valid programs, and can ensure predicate independence. Our constraint-driven
+approach is advantageous in that one can easily add additional conditions on the
+structure and properties of the program, although the main disadvantage is
+that there are no guarantees about the underlying probability distribution from
+which programs are sampled.
+
+In addition, note that our model treats logically equivalent but syntactically
+different formulas as different. This is so in part because designing a
+constraint for logical equivalence fell outside the scope of this work and in
+part because in some situations one might want to enumerate all ways to express
+the same probability distribution or knowledge base, e.g., to investigate
+whether inference algorithms are robust to changes in representation.
+
+%\subsubsection*{Acknowledgments.}
+%This work was supported by the EPSRC Centre for Doctoral Training in Robotics
+%and Autonomous Systems, funded by the UK Engineering and Physical Sciences
+%Research Council (grant EP/S023208/1).
+
+% ==============================================================================
+%                                   NOTES
+% ==============================================================================
+
+% Notes on papers that test ProbLog inference algorithms:
+% - On the Implementation: published, one biological network
+% -(removed) Nesting Probabilistic Inference: NOT published, one Alzheimer
+% network
+% -(removed) DNF Sampling: NOT published, two networks: a family tree and the
+% Alzheimer network
+% -ProbLog Technology: published, two networks: a custom theory with randomly
+% generated data, and citation data
+% -Anytime Inference: published, four networks: the Smokers social network,
+% Alzheimer data, biological network of genetic data, data about the world wide
+% web
+
+%Interestingly, in the [???] of
+%probabilistic logic programming, random logic program generators can be useful
+%in combination with methods that generate random data with probabilistic logic
+%programs \cite{DBLP:conf/soict/Dries15} and can be used as a component of
+%learning.
+
+%\cref{fig:phase_transition} takes the data for $|\predicates{}| = 8$ (almost
+%\num{300000} observations) and shows how the number of nodes in the search tree
+%varies with the number of independent pairs of predicates. The box plots show
+%that the median number of nodes stays about the same while the dots
+%(representing the means) draw an arc. This suggests a type of phase transition,
+%but only in mean rather than median, i.e., most problems remain easy, but with
+%some parameter values hard problems become more likely. On the one hand, with
+%few pairs of independent predicates, one can easily find the right combination
+%of predicates to use in each clause. On the other hand, if most predicates must
+%be independent, this leaves fewer predicates that can be used in the body of
+%each clause (since all of them have to be independent with the head predicate),
+%and we can either quickly find a solution or identify that there is none.
+
+%\begin{figure*}
+%  \centering
+%  \input{phase_transition.tex}
+%  \caption{The distribution of the number of nodes in the binary search tree as
+%    a function of the number of independent pairs of predicates for
+%    $|\predicates| = 8$. Outliers are hidden, the dots denote mean values, and
+%    the vertical axis is on a $\log_{10}$ scale.}
+%  \label{fig:phase_transition}
+%\end{figure*}
+
+% Extra notes.
 % 1. Randomness. The value heuristic is random because we want randomness. After
@@
 
-\section{CONCLUSIONS}
-
-We were able to design an efficient model for generating both logic programs and
-probabilistic logic programs. The model avoids unnecessary symmetries, generates
-valid programs, and can ensure predicate independence. Our constraint-driven
-approach is advantageous in that one can easily add additional conditions on the
-structure and properties of the program, although the main disadvantage is
-that there are no guarantees about the underlying probability distribution from
-which programs are sampled.
-
-In addition, note that our model treats logically equivalent but syntactically
-different formulas as different. This is so in part because designing a
-constraint for logical equivalence fell outside the scope of this work and in
-part because in some situations one might want to enumerate all ways to express
-the same probability distribution or knowledge base, e.g., to investigate
-whether inference algorithms are robust to changes in representation.
-
-%\subsubsection*{Acknowledgements}
-
-%This work was supported by the EPSRC Centre for Doctoral Training in
-%Robotics and Autonomous Systems, funded by the UK Engineering and Physical
-%Sciences Research Council (grant EP/S023208/1).
-
-\renewcommand{\bibsection}{\subsubsection*{References}}
-\bibliography{paper}
-
-\appendix
-\section{EXAMPLE PROGRAMS}
-
-In this appendix, we provide examples of probabilistic logic programs generated
-by various combinations of parameters. In all cases, we use $\{ 0.1, 0.2, \dots,
-0.9, 1, 1, 1, 1, 1\}$ as the multiset of probabilities. Each clause is written
-on a separate line and ends with a full stop. The head and the body of each
-clause are separated with \texttt{:-} (instead of $\gets$). The probability of
-each clause is prepended to the clause, using \texttt{::} as a separator.
-Probabilities equal to one and empty bodies of clauses can be omitted.
-Conjunction, disjunction, and negation are denoted by commas, semicolons, and
-`\texttt{\textbackslash+}', respectively. Parentheses are used to demonstrate
-precedence, although many of them are redundant.
-
-By setting $\predicates{} = [\texttt{p}]$, $\arities{} = [1]$, $\variables{} =
-\{ \texttt{X} \}$, $\constants{} = \emptyset$, $\maxNumNodes{} = 4$, and
-$\maxNumClauses{} = 1$, we get fifteen one-line programs, six of which are
-without negative cycles (as highlighted below). Only the last program has no
-cycles at all.
-
-\begin{enumerate}[label=\arabic*.]
-\item
-\begin{verbatim}
-0.5 :: p(X) :- (\+(p(X))), (p(X)).
-\end{verbatim}
-\item
-\begin{verbatim}
-0.8 :: p(X) :- (\+(p(X))); (p(X)).
-\end{verbatim}
-\hlitem
-\begin{verbatim}
-0.8 :: p(X) :- (p(X)); (p(X)).
-\end{verbatim}
-\hlitem
-\begin{verbatim}
-0.7 :: p(X) :- (p(X)), (p(X)).
-\end{verbatim}
-\item
-\begin{verbatim}
-0.6 :: p(X) :- (p(X)), (\+(p(X))).
-\end{verbatim}
-\item
-\begin{verbatim}
-p(X) :- (p(X)); (\+(p(X))).
-\end{verbatim}
-\hlitem
-\begin{verbatim}
-0.1 :: p(X) :- (p(X)); (p(X)); (p(X)).
-\end{verbatim}
-\hlitem
-\begin{verbatim}
-0.8 :: p(X) :- (p(X)), (p(X)), (p(X)).
-\end{verbatim}
-\item
-\begin{verbatim}
-p(X) :- \+(p(X)).
-\end{verbatim}
-\item
-\begin{verbatim}
-0.1 :: p(X) :- \+(\+(p(X))).
-\end{verbatim}
-\item
-\begin{verbatim}
-p(X) :- \+((p(X)); (p(X))).
-\end{verbatim}
-\item
-\begin{verbatim}
-0.4 :: p(X) :- \+((p(X)), (p(X))).
-\end{verbatim}
-\item
-\begin{verbatim}
-0.4 :: p(X) :- \+(\+(\+(p(X)))).
-\end{verbatim}
-\hlitem
-\begin{verbatim}
-0.7 :: p(X) :- p(X).
-\end{verbatim}
-\hlitem
-\begin{verbatim}
-p(X).
-\end{verbatim}
-\end{enumerate}
-
-Note that:
-\begin{itemize}
-\item A program such as Program~14, because of its cyclic definition, defines a
-  predicate that has probability zero across all constants. This can more easily
-  be seen as solving equation $0.7x = x$.
-\item Programs 10 and 14 are not equivalent (i.e., double negation does not
-  cancel out) because Program 10 has a negative cycle and is thus considered to
-  be ill-defined.
-\end{itemize}
-
-To demonstrate variable symmetry reduction in action, we set $\predicates{} =
-[\texttt{p}]$, $\arities{} = [3]$, $\variables{} = \{\texttt{X}, \texttt{Y},
-\texttt{Z} \}$, $\constants{} = \emptyset$, $\maxNumNodes{} = 1$,
-$\maxNumClauses{} = 1$, and forbid all cycles. This gives us the following five
-programs:
-
-\begin{itemize}
-\item
-\begin{verbatim}
-0.8 :: p(Z, Z, Z).
-\end{verbatim}
-\item
-\begin{verbatim}
-p(Y, Y, Z).
-\end{verbatim}
-\item
-\begin{verbatim}
-p(Y, Z, Z).
-\end{verbatim}
-\item
-\begin{verbatim}
-p(Y, Z, Y).
-\end{verbatim}
-\item
-\begin{verbatim}
-0.1 :: p(X, Y, Z).
-\end{verbatim}
-\end{itemize}
-
-This is one of many possible programs with $\predicates{} = [\texttt{p},
-\texttt{q}, \texttt{r}]$, $\arities{} = [1, 2, 3]$, $\variables{} =
-\{\texttt{X}, \texttt{Y}, \texttt{Z} \}$, $\constants{} = \{ \texttt{a},
-\texttt{b}, \texttt{c} \}$, $\maxNumNodes{} = 5$, $\maxNumClauses{} = 5$, and
-without negative cycles:
-
-\begin{verbatim}
-p(b) :- \+((q(a, b)), (q(X, Y)), (q(Z, X))).
-0.4 :: q(X, X) :- \+(r(Y, Z, a)).
-q(X, a) :- r(Y, Y, Z).
-q(X, a) :- r(Y, b, Z).
-r(Y, b, Z).
-\end{verbatim}
-
-Finally, we set
-$\predicates{} = [\texttt{p}, \texttt{q}, \texttt{r}]$, $\arities{} = [1, 1,
-1]$, $\variables{} = \emptyset$, $\constants{} = \{ \texttt{a} \}$,
-$\maxNumNodes{} = 3$, $\maxNumClauses{} = 3$, forbid negative cycles, and
-constrain predicates \texttt{p} and \texttt{q} to be independent. The resulting
-search space contains thousands of programs such as:
-
-\begin{itemize}
-\item
-\begin{verbatim}
-0.5 :: p(a) :- (p(a)); (p(a)).
-0.2 :: q(a) :- (q(a)), (q(a)).
-0.4 :: r(a) :- \+(q(a)).
-\end{verbatim}
-\item
-\begin{verbatim}
-p(a) :- p(a).
-0.5 :: q(a) :- (r(a)); (q(a)).
-r(a) :- (r(a)); (r(a)).
-\end{verbatim}
-\item
-\begin{verbatim}
-p(a) :- (p(a)); (p(a)).
-0.6 :: q(a) :- q(a).
-0.7 :: r(a) :- \+(q(a)).
-\end{verbatim}
-\end{itemize}
+\bibliographystyle{splncs04}
+\bibliography{bibliography}
 

### 2020-04-19 paper2/papertemp.tex
Second publication attempt

--- 2020-02-17 paper/paper.tex
@@
 
-\author{}
-
-%\author{ {\bf Paulius Dilkas} \\
-%School of Informatics \\
-%University of Edinburgh \\
-%Edinburgh, United Kingdom \\
-%}
+%\author{}
+
+\author{ {\bf Paulius Dilkas} \\
+University of Edinburgh, UK
+\And
+{\bf Vaishak Belle} \\
+University of Edinburgh, UK \\
+Alan Turing Institute, UK
+}
 
@@
 
-%\subsubsection*{Acknowledgements}
-
-%This work was supported by the EPSRC Centre for Doctoral Training in
-%Robotics and Autonomous Systems, funded by the UK Engineering and Physical
-%Sciences Research Council (grant EP/S023208/1).
+\subsubsection*{Acknowledgements}
+
+This work was supported by the EPSRC Centre for Doctoral Training in
+Robotics and Autonomous Systems, funded by the UK Engineering and Physical
+Sciences Research Council (grant EP/S023208/1). The authors would like to thank
+Fazl Barez for his comments.
 
@@
 
+\newpage
 \appendix

### 2020-05-05 paper2/paper.tex
Improve the explanation of acyclicity

@@
 \maketitle
+
+% TODO (for later)
+% 1) First keyword should be the category that I'm submitting for (add a new one)
+% 2) Use American English
+% 3) Avoid the Definition environment (to save space)
+% 4) Make sure that figures and algorithms are placed in good positions
+% 5) Check the grammar
+
+% Empirical tasks:
+% 1) make the CP model faster: apply the redundant constraints to predicates
+% (not just variables). Check if everything works out.
+% 2) motivate either for benchmarking or by comparing parameter learning with
+% ProbFOIL
+% New things I could talk about:
+% 1) entailment for conditional independence
+% 2) the 'required formula' part of the model
 
@@
 
-  \keywords{Probabilistic logic programming \and Logic programming \and
-    Predicate independence.}
+  \keywords{Probabilistic logic programming \and Statistical relational
+    artificial intelligence.}
 \end{abstract}
-
-% TODO (for later)
-% 1) First keyword should be the category that I'm submitting for
-% 2) Use American English
-% 3) Avoid the Definition environment (to save space)
-% 4) Make sure that figures and algorithms are placed in good positions
 
@@
 
+% TODO: Review: I’m not convinced that paragraph 2 follows from paragraph 1. Has
+% generation of random SAT problems really solved the problem of establishing
+% that one inference algorithm is better than another? I thought it led to the
+% opposite–a discovery that randomly generated instances are a different kind of
+% problem than real-world benchmarks. For example, a recent SAT competition
+% shows now overlap in the top three solvers for the random vs non-random
+% tracks.
+
 About thirty years ago, SAT solving technology was dealing with a similar lack
@@
 the program. In fact, the same model can generate both probabilistic programs
-directly in the syntax of ProbLog \cite{DBLP:conf/ijcai/RaedtKT07} and
-non-probabilistic Prolog programs. For generated probabilistic programs to be
-valid, we use a custom constraint to detect negative cycles. A major advantage
-of our constraint-based approach is that one can easily add additional
-constraints to the model. To demonstrate that, we present a custom constraint
-with propagation and entailment algorithms that can ensure predicate
-independence. We also present a combinatorial argument for correctness, counting
-the number of programs that the model produces for various parameter values.
-Finally, we show how the model scales when tasked with producing more
-complicated programs and identify the relationships between parameter values and
-the empirical hardness of the program generation task.
+in the syntax of ProbLog \cite{DBLP:conf/ijcai/RaedtKT07} and
+non-probabilistic Prolog programs. A major advantage of our constraint-based
+approach is that one can easily add additional constraints to the model. To
+demonstrate that, we present a custom constraint with propagation and entailment
+algorithms that can ensure predicate independence. We also present a
+combinatorial argument for correctness, counting the number of programs that the
+model produces for various parameter values. Finally, we show how the model
+scales when tasked with producing more complicated programs.
+
+A common restriction put on both logic programs and probabilistic logic programs
+in order to ensure that there is a unique answer to every query is known as
+\emph{stratification}
+\cite{DBLP:journals/jlp/BalbinPRM91,DBLP:conf/padl/MantadelisR17}. We extend
+this idea to programs that have arbitrary well-formed formulas in clause bodies
+(as ProbLog supports this) and describe a custom constraint that ensures
+stratification by checking for negative cycles in the predicate dependency
+graph.
+
+% TODO: Review: I would have appreciated a definition of 
+% predicate independence instead of just a forward pointer to sections 7 and 8.
 
@@
 
+% TODO: Answer to a review: The main benefit of a constraint-based approach is
+% the ability to add additional constraints as needed, and to do that
+% efficiently (compared to generate-and-test approaches). Specifically, we can
+% regulate what parts of the program must be independent, require certain
+% formulas to be included, etc.
+
+% TODO: Review: The paper fails to provide explanation of critical parts: for
+% example, how is a set of constraints going to be turned into a random logic
+% program? We don’t find out until section 9.
+
 \section{Preliminaries}
@@
 variable or a constant, and an \emph{atom} is a predicate of arity $n$ applied
-to $n$ terms. A \emph{formula} is a grammatically-valid expression that connects
+to $n$ terms. A \emph{formula} is any well-formed expression that connects
 atoms using conjunction ($\land$), disjunction ($\lor$), and negation ($\neg$).
@@
 \mathscr{P}$.
+% TODO: Review: The use of disjunction and arbitrary negation in the body is
+% also uncommon
 
@@
 |\predicates{}|$ because we require each predicate to have at least one clause
-that defines it. The model supports eliminating either all cycles or just
-negative cycles (see \cref{sec:cycles}) and enforcing predicate independence
-(see \cref{sec:independence}), so a set of independent pairs of predicates is
-another parameter. Since this model can generate probabilistic as well as
+that defines it.
+
+% TODO: make the first sentence clear
+The model supports enforcing predicate independence (see
+\cref{sec:independence}), so a set of independent pairs of predicates is another
+parameter. Since this model can generate probabilistic as well as
 non-probabilistic programs, each clause is paired with a probability which is
@@
 \begin{constraint}
-  Clauses are sorted.
-\end{constraint}
-
-Here and henceforth, the exact ordering is immaterial: we only impose an order
-to eliminate permutation symmetries.
+  Clauses are sorted according to a lexicographic increasing order\footnote{The
+    exact order is immaterial: we only impose an order to eliminate duplicates
+    and permutation symmetries.}.
+\end{constraint}
 
@@
 
-\begin{definition}
-  The \emph{head} of a clause is composed of a $\variable{predicate} \in
-  \predicates \cup \{ \Box \}$, and
-  $\arrayd{arguments}{\maxArity{}}{\constants{} \cup \variables{}} \cup \{ \Box
-  \}$.
-\end{definition}
-
-Here, we use $\Box$ to denote either a disabled clause that we choose not to use
-or disabled arguments if the arity of the $\variable{predicate}$ is less than
-$\maxArity{}$. The reason why we need a separate value for the latter (i.e., why
-it is not enough to fix disabled arguments to a single already-existing value)
-will become clear in \cref{sec:variable_symmetry}.
-
-\begin{definition} \label{def:arity}
-  The \variable{predicate}'s $\variable{arity} \in [0, \maxArity{}]$ can then be
-  defined using the \variable{table} constraint as the arity of the
-  $\variable{predicate}$ if $\variable{predicate} \in \predicates{}$, and zero
-  otherwise.
-\end{definition}
-
+We define the \emph{head} of a clause as a $\variable{predicate} \in \predicates
+\cup \{ \Box \}$ and $\arrayd{arguments}{\maxArity{}}{\constants{} \cup
+  \variables{}} \cup \{ \Box \}$. Here, we use $\Box$ to denote either a
+disabled clause that we choose not to use or disabled arguments if the arity of
+the $\variable{predicate}$ is less than $\maxArity{}$. The reason why we need a
+separate value for the latter (i.e., why it is not enough to fix disabled
+arguments to a single already-existing value) will become clear in
+\cref{sec:variable_symmetry}.
+
+This $\variable{predicate}$ variable has a corresponding arity that depends on
+the value of $\variable{predicate}$. We can define $\variable{arity} \in [0,
+\maxArity{}]$ as the arity of the $\variable{predicate}$ if
+$\variable{predicate} \in \predicates{}$ and zero otherwise using the table
+constraint \cite{DBLP:conf/cpaior/MairyDL15}. This constraint uses a set of
+pairs of the form $(p, a)$, where $p$ ranges over all possible values of
+$\variable{predicate}$, and $a$ is either the arity of predicate $p$ or zero.
 Having defined arity, we can now fix the superfluous arguments:
@@
 \begin{constraint}
-  Let $P = \{ h.\variable{predicate} \mid h \in \variable{heads} \}$. Then
+  Let $P = \{ h.\variable{predicate} \mid h \in \variable{heads} \}$ be a
+  multiset. Then
   \[
@@
   \]
-  where $\variable{nValues}(P)$ counts the number of unique values in $P$.
+  where $\variable{nValues}(P)$ counts the number of unique values in $P$, and
+  $\variable{count}(\Box, P)$ counts how many times $\Box$ appears in $P$.
 \end{constraint}
@@
 
-As was briefly mentioned before, the body of a clause is represented by a tree.
-
-% TODO: fix the formatting issue
-\begin{definition}
-  The \emph{body} of a clause has two parts. First, we have the
-  $\arrayd{structure}{\maxNumNodes{}}{[0, \maxNumNodes{} - 1]}$ array that
-  encodes the structure of the tree using the following two rules:
+As was briefly mentioned before, the \emph{body} of a clause is represented by a
+tree. It has two parts. First, there is the
+$\arrayd{structure}{\maxNumNodes{}}{[0, \maxNumNodes{} - 1]}$ array that encodes
+the structure of the tree using the following two rules:
 $\variable{structure}[i] = i$ means that the $i$-th node is a root, and
@@
 the value of the $i$-th node.
-\end{definition}
+% TODO: explain what Node is.
 
@@
 
-\begin{definition}
 For convenience, we also define $\variable{numNodes} \in \{ 1, \dots,
@@
 \]
-\end{definition}
 
 \begin{example} \label{example:formula}
-  Let $\maxNumNodes{} = 8$. Then
-  \[
-    \neg\mathsf{P}(X) \lor (\mathsf{Q}(X) \land \mathsf{P}(X))
-  \]
-  corresponds to the tree in \cref{fig:example_tree} and can be encoded as:
-  \begin{alignat*}{8}
+  Let $\maxNumNodes{} = 8$. Then $\neg\mathsf{P}(X) \lor (\mathsf{Q}(X) \land
+  \mathsf{P}(X))$ corresponds to the tree in \cref{fig:example_tree} and can be
+  encoded as:
+  \begin{gather*}
+    \begin{alignedat}{8}
       \variable{structure} &= [0, &&0, &&0, &&1, &&2, &&2, &&6, &&7],\\
       \variable{values} &= [{\lor}, &&{\neg}, &&{\land}, \mathsf{P}(&&X),
-    \mathsf{Q}(&&X), \mathsf{P}(&&X), &&\top, &&\top],\\
-    \variable{numNodes} &= 6, && && && && && && &&\\
-    \variable{numTrees} &= 3. && && && && && && &&
-  \end{alignat*}
+      \mathsf{Q}(&&X), \mathsf{P}(&&X), &&\top, &&\top],
+    \end{alignedat} \\
+    \variable{numNodes} = 6, \quad \variable{numTrees} = 3.
+  \end{gather*}
 \end{example}
@@
 Here, $\top$ is the value we use for the remaining one-node trees. The
-elements of the $\variable{values}$ array are nodes:
-
-\begin{definition} \label{def:node}
-  A \emph{node} has a $\variable{name} \in \tokens{} \cup \predicates{}$ and
+elements of the $\variable{values}$ array are nodes. A \emph{node} has a
+$\variable{name} \in \tokens{} \cup \predicates{}$ and
 $\arrayd{arguments}{\maxArity{}}{\variables{} \cup \constants{} \cup \{ \Box
-    \}}$. The node's $\variable{arity}$ can then be
-  defined analogously to \cref{def:arity}.
-\end{definition}
-
-Furthermore, we can use \cref{constr:arity} to again disable the extra
-arguments.
+  \}}$. The node's $\variable{arity}$ can then be defined in the same way as in
+\cref{sec:heads}. Furthermore, we can use \cref{constr:arity} to again disable
+the extra arguments.
 
@@
   predicate with arity 1. Then the node representing atom $\mathsf{P}(X)$ has:
-  \begin{align*}
-    \variable{name} &= \mathsf{P},\\
-    \variable{arguments} &= [X, \Box],\\
-    \variable{arity} &= 1.
-  \end{align*}
+    $\variable{name} = \mathsf{P}$, $\variable{arguments} = [X, \Box]$,
+    $\variable{arity} = 1$.
 \end{example}
@@
 
+% TODO: Response to a review: Symmetry removal is important for two reasons.
+% First, if we want to generate all programs that match a certain description,
+% we would rather not generate the same program multiple times. Second, symmetry
+% removal makes the constraint solving task much simpler by significantly
+% reducing the search space that needs to be explored, often turning an
+% intractable problem into an easy one.
+
 Given any clause, we can permute the variables in that clause without changing
@@
   $\variable{terms}[N] \in \constants{} \cup \variables{} \cup \{ \Box
-  \}$ be a flattened array of all arguments in a particular clause.
-
-  Then we can use a channeling constraint to define
-  $\variable{occ}[|\constants{}| + |\variables{}| + 1]$ as an array of subsets
-  of $\{ 0, \dots, N-1 \}$ such that for all $i = 0, \dots, N - 1$, and $t \in
-  \constants{} \cup \variables{} \cup \{ \Box \}$,
+  \}$ be a flattened array of all arguments in a particular clause. Then we can
+  use a channeling constraint to define $\variable{occ}[|\constants{}| +
+  |\variables{}| + 1]$ as an array of subsets of $\{ 0, \dots, N-1 \}$ such that
+  for all $i = 0, \dots, N - 1$, and $t \in \constants{} \cup \variables{} \cup
+  \{ \Box \}$,
   \[
@@
 Finally, we define an auxiliary set variable to act as a set of possible values
-that $\variable{intros}$ can take:
-
-\begin{definition}
-  Let $\variable{potentials} \subseteq \{ 0, \dots, N \}$ be such that for $v
-  \in \variables{}$, $\variable{intros}[v] \in \variable{potentials}$.
-\end{definition}
-
-Using this new variable, we can add a constraint saying that non-predicate nodes
-in the tree representation of a clause cannot have variables as arguments:
+that $\variable{intros}$ can take. Let $\variable{potentials} \subseteq \{ 0,
+\dots, N \}$ be such that for $v \in \variables{}$, $\variable{intros}[v] \in
+\variable{potentials}$. Using this new variable, we can add a constraint saying
+that non-predicate nodes in the tree representation of a clause cannot have
+variables as arguments:
 
@@
 \section{Counting Programs} \label{sec:counting}
+% TODO: Does this section still work if I don't allow duplicates?
 
 \setcounter{footnote}{0}
+
+% TODO: Review: Finally, regarding correctness of the proposal, I don´t
+% understand "the combinatorial argument for correctness" result, how does the
+% provided analysis show correctness relative to the properties? I was expecting
+% a proof that would show the relationship between the formalized constraint and
+% the desired property, to chow for instance that if such constraint is taken
+% into account in the construction of the program then it is impossible that the
+% program does not satisfy the property. Is there something I do not understand
+% from this? I find the proposal lacking in this terms, not finding the
+% arguments for validity strong enough, unless I misunderstood the analysis.
+% Answer: 
+% Regarding correctness, we decided against including proofs that a constraint for
+% a property ensures the property because the discussed properties are all
+% syntactic, and the constraint model itself is a representation of the same
+% syntax so the proofs would not be particularly revealing. We can nonetheless add
+% them if necessary.
+%
+% Instead, Section 6 shows correctness in a sense that if two methods generate the
+% same numbers (i.e., numbers of programs with certain properties and parameters),
+% then they describe the same thing, and we gain confidence that the constraint
+% description (which matches the combinatorial description) accurately matches our
+% intentions. This method helped us debug many aspects of the model and can be
+% particularly revealing when both the model and the combinatorial argument become
+% more intricate.
 
@@
 
+% TODO: Review: Section 7 defined predicate (in)dependence. It is done using the
+% constraint model, but given a logic program, it could just as well be
+% extracted from the logic program (construct body tree from each clause).
+% Answer: Motivate why we need this.
+
+% TODO: Answer to a review: All constraints have propagation and entailment
+% procedures behind them. When designing a new constraint, unless it can be
+% composed of already-existing constraints, designing these algorithms is, in
+% fact, completely in the spirit of constraint programming.
+
 In this section, we define a notion of predicate independence as a way to
@@
 also describe efficient algorithms for propagation and entailment checking.
-
-\begin{definition}
 Let $\mathscr{P}$ be a probabilistic logic program. Its \emph{predicate
-    dependency graph} is a directed graph $G_{\mathscr{P}} = (V, E)$ with the
-  set of nodes $V$ consisting of all predicates in $\mathscr{P}$. For any two
+  dependency graph} is a directed graph $G_{\mathscr{P}} = (V, E)$ with the set
+of nodes $V$ consisting of all predicates in $\mathscr{P}$. For any two
 different predicates $\mathsf{P}$ and $\mathsf{Q}$, we add an edge from
 $\mathsf{P}$ to $\mathsf{Q}$ if there is a clause in $\mathscr{P}$ with
-  $\mathsf{Q}$ as the head and $\mathsf{P}$ mentioned in the body. We say that
-  the edge is \emph{negative} if there exists a clause with $\mathsf{Q}$ as the
-  head and at least one instance of $\mathsf{P}$ at the body such that the path
-  from the root to the $\mathsf{P}$ node in the tree representation of the
-  clause passes through at least one negation node. Otherwise, it is
-  \emph{positive}. We say that $\mathscr{P}$ (or $G_{\mathscr{P}}$) has a
-  \emph{negative cycle} if $G_{\mathscr{P}}$ has a cycle with at least one
-  negative edge.
-\end{definition}
-
-Labelling the edges as positive/negative will be immaterial for predicate
-independence, but the same graph will play a crucial role in negative cycle
-detection in the next section.
+$\mathsf{Q}$ as the head and $\mathsf{P}$ mentioned in the body. We say that the
+edge is \emph{negative} if there exists a clause with $\mathsf{Q}$ as the head
+and at least one instance of $\mathsf{P}$ at the body such that the path from
+the root to the $\mathsf{P}$ node in the tree representation of the clause
+passes through at least one negation node. Otherwise, it is \emph{positive}. We
+say that $\mathscr{P}$ (or $G_{\mathscr{P}}$) has a \emph{negative cycle} if
+$G_{\mathscr{P}}$ has a cycle with at least one negative edge. Labelling the
+edges as positive/negative will be immaterial for predicate independence, but
+the same graph will play a crucial role in designing a constraint for
+stratification in the next section. In fact, a program $\mathscr{P}$ is
+\emph{stratified} if $G_{\mathscr{P}}$ has no negative cycles.
 
@@
   D_{\mathsf{P}}$, all direct predecessors of $\mathsf{Q}$ in $G_{\mathscr{P}}$
-  are in $D_{\mathsf{P}}$.
-\end{definition}
-
-\begin{definition}
-  Two predicates $\mathsf{P}$ and $\mathsf{Q}$ are \emph{independent} if
-  $D_{\mathsf{P}} \cap D_{\mathsf{Q}} = \emptyset$.
+  are in $D_{\mathsf{P}}$. Two predicates $\mathsf{P}$ and $\mathsf{Q}$ are
+  \emph{independent} if $D_{\mathsf{P}} \cap D_{\mathsf{Q}} = \emptyset$.
 \end{definition}
@@
 
-\begin{figure}
+\begin{figure}[t]
   \centering
@@
   The predicate dependency graph without positivity/negativity (as defined in
-  \cref{def:adjacency_matrix}) is represented in
-  \cref{fig:dependencies_matrix,fig:dependencies2}.
-
-  % TODO: labels on the inside (check if they work)
+  \cref{def:adjacency_matrix}) is represented in \cref{fig:example}.
+
   \begin{figure}
@@
       \centering
-      \subfloat[The adjacency matrix defined using \cref{def:adjacency_matrix} for
-      \cref{example:independence}\label{fig:dependencies_matrix}]{
+      \subfloat[The adjacency matrix of the graph. The boxed value is the
+      decision variable that will be propagated by
+      \cref{alg:independence_propagation}.\label{fig:dependencies_matrix}]{
         $\begin{blockarray}{lcccc}
@@
       \centering
-      \subfloat[The predicate dependency graph that corresponds to
-      \cref{fig:dependencies_matrix}. Dashed edges are undetermined---they may or
-      may not exist.\label{fig:dependencies2}]{
+      \subfloat[A drawing of the graph. Dashed edges are undetermined---they may
+      or may not exist.\label{fig:dependencies2}]{
         \centering
@@
     \end{minipage}
-    \caption{TODO}
+    \caption{The predicate dependency graph of \cref{example:independence}}
+    \label{fig:example}
   \end{figure}
@@
 \section{Negative Cycles} \label{sec:cycles}
-% although some work has been done in overcoming this limitation
-% \cite{DBLP:journals/ijar/BuchmanP17}
-
-Having no negative cycles in the predicate dependency graph is a requirement of
-ProbLog that makes the program well-defined \cite{kimmig2009trading}. Ideally,
-we would like to design a constraint for negative cycles similar to the
+
+Ideally, we would like to design a constraint for negative cycles similar to the
 constraint for independence in the previous section. However, the difficulty
@@
 
+% TODO: Review: From section 9 it seems that this language has a very special
+% handcrafted (heuristic) solution procedure that is not guaranteed to find a
+% solution if one exists.
+% Answer: Adding a restart policy helps with efficiency when generating larger
+% programs, but if we want to find all possible programs, restarts can be
+% disabled (and this is likely to only be relevant with low parameter values,
+% where the number of possible programs is in thousands rather than millions).
+% Note that combinations of parameter values that have no solutions (or are
+% unlikely to have solutions) are unlikely to occur in practice (i.e., be of
+% interest).
+
 \section{Conclusions}
@@
 \bibliographystyle{splncs04}
-\bibliography{bibliography}
+\bibliography{paper}
 

### 2020-05-06 text/paper2/paper.tex
Minor changes

--- 2020-05-05 paper2/paper.tex
@@
 %\binoppenalty=10000
-\def\multiset#1#2{\ensuremath{\left(\kern-.3em\left(\genfrac{}{}{0pt}{}{#1}{#2}\right)\kern-.3em\right)}}
 
@@
 % TODO (for later)
-% 1) First keyword should be the category that I'm submitting for (add a new one)
-% 2) Use American English
-% 3) Avoid the Definition environment (to save space)
-% 4) Make sure that figures and algorithms are placed in good positions
-% 5) Check the grammar
+% 1) Use American English
+% 2) Avoid the Definition environment (to save space)
+% 3) Check the grammar
+% 4) Update the abstract
 
@@
 
-  \keywords{Probabilistic logic programming \and Statistical relational
-    artificial intelligence.}
+  \keywords{Constraint programming \and Probabilistic logic programming \and
+    Statistical relational learning.}
 \end{abstract}
@@
 mixes machine learning and symbolic (logical and relational) structures. In
-particular, logic programs and probabilistic logic programs---including
-languages such as PRISM \cite{DBLP:conf/ijcai/SatoK97}, ICL
-\cite{DBLP:journals/ai/Poole97}, and ProbLog
+particular, probabilistic logic programs---including languages such as PRISM
+\cite{DBLP:conf/ijcai/SatoK97}, ICL \cite{DBLP:journals/ai/Poole97}, and ProbLog
 \cite{DBLP:conf/ijcai/RaedtKT07}---are promising frameworks for codifying
@@
 if it is only tested on a few types of problems?
-
-% TODO: Review: I’m not convinced that paragraph 2 follows from paragraph 1. Has
-% generation of random SAT problems really solved the problem of establishing
-% that one inference algorithm is better than another? I thought it led to the
-% opposite–a discovery that randomly generated instances are a different kind of
-% problem than real-world benchmarks. For example, a recent SAT competition
-% shows now overlap in the top three solvers for the random vs non-random
-% tracks.
 
@@
 in the syntax of ProbLog \cite{DBLP:conf/ijcai/RaedtKT07} and
-non-probabilistic Prolog programs. A major advantage of our constraint-based
-approach is that one can easily add additional constraints to the model. To
-demonstrate that, we present a custom constraint with propagation and entailment
-algorithms that can ensure predicate independence. We also present a
-combinatorial argument for correctness, counting the number of programs that the
-model produces for various parameter values. Finally, we show how the model
-scales when tasked with producing more complicated programs.
+non-probabilistic Prolog programs. A major advantage of a constraint-based
+approach is the ability to add additional constraints as needed, and to do that
+efficiently (compared to generate-and-test approaches). As an example of this,
+we develop a custom constraint (with propagation and entailment algorithms)
+that, given two predicates $\mathsf{P}$ and $\mathsf{Q}$, ensures that any
+ground atom with predicate $\mathsf{P}$ is independent of any ground atom
+with predicate $\mathsf{Q}$. In this way, we can easily regulate the
+independence structure of the underlying probability distribution. We also
+present a combinatorial argument for correctness, counting the number of
+programs that the model produces for various parameter values. Finally, we show
+how the model scales when tasked with producing more complicated programs.
+
+% TODO: these two paragraphs aren't connected
 
@@
 
-% TODO: Review: I would have appreciated a definition of 
-% predicate independence instead of just a forward pointer to sections 7 and 8.
-
 Overall, our main contributions are concerned with logic programming-based
@@
 
-% TODO: Answer to a review: The main benefit of a constraint-based approach is
-% the ability to add additional constraints as needed, and to do that
-% efficiently (compared to generate-and-test approaches). Specifically, we can
-% regulate what parts of the program must be independent, require certain
-% formulas to be included, etc.
-
 % TODO: Review: The paper fails to provide explanation of critical parts: for
@@
 % program? We don’t find out until section 9.
+
+%We develop a constraint-based representation for valid logic programs based on
+%some simple parameters that describe the program's size, what predicates and
+%constants it uses, etc. This representation takes the form of a constraint
+%satisfaction problem, i.e., a set of discrete variables and restrictions on what
+%values they can take. After a constraint solver provides valid values for these
+%variables, they directly translate into a logic program.
 
@@
 to $n$ terms. A \emph{formula} is any well-formed expression that connects
-atoms using conjunction ($\land$), disjunction ($\lor$), and negation ($\neg$).
+atoms using conjunction $\land$, disjunction $\lor$, and negation
+$\neg$\footnote{One can add a couple extra constraints to restrict the
+  generated programs to logic programs that only allow a single disjunction with
+  positive and negative literals.}.
 A \emph{clause} is a pair of a \emph{head} (which is an atom) and a \emph{body}
-(which is a formula). A \emph{(logic) program} is a multiset of clauses. Given a
+(which is a formula). A \emph{(logic) program} is a set of clauses. Given a
 program $\mathscr{P}$, a \emph{subprogram} $\mathscr{R}$ of $\mathscr{P}$ is a
@@
 \mathscr{P}$.
-% TODO: Review: The use of disjunction and arbitrary negation in the body is
-% also uncommon
 
@@
 
-\subsection{Parameters of the Model}
-
-We begin defining the parameters of our model by initialising sets and lists
-of the primitives used in constructing logic programs: a list of predicates
-$\predicates{}$, a list of their corresponding arities $\arities{}$ (so
-$|\arities{}|$ = $|\predicates{}|$), a set of variables $\variables{}$, and a
-set of constants $\constants{}$. Either $\variables{}$ or $\constants{}$ can be
-empty, but we assume that $|\constants{}| + |\variables{}| > 0$. Similarly, the
-model supports zero-arity predicates but requires at least one predicate to have
-non-zero arity. For notational convenience, we also set $\maxArity{} \coloneqq
-\max \arities{}$.
-
-We also define a measure of how complicated a body of a clause can become. As
-each body is represented by a tree (see \cref{sec:bodies}), we set
-$\maxNumNodes{} \ge 1$ to be the maximum number of nodes in the tree
-representation of any clause. We also set $\maxNumClauses{}$ to be the maximum
-number of clauses in a program. We must have that $\maxNumClauses{} \ge
-|\predicates{}|$ because we require each predicate to have at least one clause
-that defines it.
-
-% TODO: make the first sentence clear
-The model supports enforcing predicate independence (see
-\cref{sec:independence}), so a set of independent pairs of predicates is another
-parameter. Since this model can generate probabilistic as well as
-non-probabilistic programs, each clause is paired with a probability which is
-randomly selected from a given multiset (i.e., our last parameter). For
-generating non-probabilistic programs, one can set this list equal to $\{ 1 \}$.
-Finally, we define $\tokens{} = \{ \neg, \land, \lor, \top \}$ as the set of
-tokens that (together with atoms) form a clause. All decision variables of the
-model can now be divided into $2 \times \maxNumClauses{}$ separate groups,
-treating the body and the head of each clause separately. We say that the
-variables are contained in two arrays: $\arrayt{bodies}{\maxNumClauses{}}{Body}$
-and $\arrayt{heads}{\maxNumClauses{}}{Head}$. Since the order of the clauses
-does not change the meaning of the program, we can also state our first
-constraint:
-
-\begin{constraint}
-  Clauses are sorted according to a lexicographic increasing order\footnote{The
-    exact order is immaterial: we only impose an order to eliminate duplicates
-    and permutation symmetries.}.
-\end{constraint}
+\paragraph{Parameters of the Model.} We begin defining the parameters of our
+model by initialising sets and lists of the primitives used in constructing
+logic programs: a list of predicates $\predicates{}$, a list of their
+corresponding arities $\arities{}$ (so $|\arities{}|$ = $|\predicates{}|$), a
+set of variables $\variables{}$, and a set of constants $\constants{}$. Either
+$\variables{}$ or $\constants{}$ can be empty, but we assume that
+$|\constants{}| + |\variables{}| > 0$. Similarly, the model supports zero-arity
+predicates but requires at least one predicate to have non-zero arity. For
+notational convenience, we also set $\maxArity{} = \max \arities{}$. Next, we
+need a measure of how complex a body of a clause can be. As each body is
+represented by a tree (see \cref{sec:bodies}), we set $\maxNumNodes{} \ge 1$ to
+be the maximum number of nodes in the tree representation of any clause. We also
+set $\maxNumClauses{}$ to be the maximum number of clauses in a program. We must
+have that $\maxNumClauses{} \ge |\predicates{}|$ because we require each
+predicate to have at least one clause that defines it. The model supports
+enforcing predicate independence (see \cref{sec:independence}), so a set of
+independent pairs of predicates is another parameter. Since this model can
+generate probabilistic as well as non-probabilistic programs, each clause is
+paired with a probability which is randomly selected from a given list---our
+last parameter. For generating non-probabilistic programs, one can set this list
+to $[1]$. Finally, we define $\tokens{} = \{ \neg, \land, \lor, \top \}$ as the
+set of tokens that (together with atoms) form a clause. All decision variables
+of the model can now be divided into $2 \times \maxNumClauses{}$ separate
+groups, treating the body and the head of each clause separately. We say that
+the variables are contained in two arrays:
+$\arrayt{bodies}{\maxNumClauses{}}{Body}$ and
+$\arrayt{heads}{\maxNumClauses{}}{Head}$.
 
@@
 
-We define the \emph{head} of a clause as a $\variable{predicate} \in \predicates
+We define the \emph{head} of a clause as a $\variable{predicate} \in \predicates{}
 \cup \{ \Box \}$ and $\arrayd{arguments}{\maxArity{}}{\constants{} \cup
@@
 arguments to a single already-existing value) will become clear in
-\cref{sec:variable_symmetry}.
-
-This $\variable{predicate}$ variable has a corresponding arity that depends on
-the value of $\variable{predicate}$. We can define $\variable{arity} \in [0,
-\maxArity{}]$ as the arity of the $\variable{predicate}$ if
-$\variable{predicate} \in \predicates{}$ and zero otherwise using the table
-constraint \cite{DBLP:conf/cpaior/MairyDL15}. This constraint uses a set of
-pairs of the form $(p, a)$, where $p$ ranges over all possible values of
-$\variable{predicate}$, and $a$ is either the arity of predicate $p$ or zero.
-Having defined arity, we can now fix the superfluous arguments:
-
+\cref{sec:variable_symmetry}. This $\variable{predicate}$ variable has a
+corresponding arity that depends on the value of $\variable{predicate}$. We can
+define $\variable{arity} \in [0, \maxArity{}]$ as the arity of the
+$\variable{predicate}$ if $\variable{predicate} \in \predicates{}$ and zero
+otherwise using the table constraint \cite{DBLP:conf/cpaior/MairyDL15}. This
+constraint uses a set of pairs of the form $(p, a)$, where $p$ ranges over all
+possible values of $\variable{predicate}$, and $a$ is either the arity of
+predicate $p$ or zero. Having defined arity, we can now fix the superfluous
+arguments.
 \begin{constraint} \label{constr:arity}
@@
 \end{constraint}
-
 We can also add a constraint that each predicate $\mathsf{P} \in \predicates{}$
-should have at least one clause with $\mathsf{P}$ at its head:
-
+should have at least one clause with $\mathsf{P}$ at its head.
 \begin{constraint}
@@
   $\variable{count}(\Box, P)$ counts how many times $\Box$ appears in $P$.
+\end{constraint}
+Finally, clauses are supposed to constitute a set but with one important
+exception: there may be more than one disabled clause, i.e., a clause with head
+$\variable{predicate} = \Box$. Assuming a lexicographic order over entire
+clauses such that $\Box > \mathsf{P}$ for all $\mathsf{P} \in \predicates{}$, and
+the head predicate is the `first digit' of this representation, we get the
+following constraint.
+\begin{constraint}
+  For $i = 1, \dots, \maxNumClauses{} - 1$, if $\variable{heads}[i].\variable{predicate}
+  \ne \Box$, then
+  \[
+    (\variable{heads}[i-1], \variable{bodies}[i-1]) < (\variable{heads}[i],
+    \variable{bodies}[i]).
+  \]
 \end{constraint}
@@
 $\arrayt{values}{\maxNumNodes{}}{Node}$ such that $\variable{values}[i]$ holds
-the value of the $i$-th node.
-% TODO: explain what Node is.
+the value of the $i$-th node, i.e., a representation of the atom or logical
+operator.
 
@@
 restrict all other trees to single nodes. For this to work, we need to make sure
-that the zeroth node is indeed a root:
-
+that the zeroth node is indeed a root.
 \begin{constraint}
@@
 \end{constraint}
-
 For convenience, we also define $\variable{numNodes} \in \{ 1, \dots,
 \maxNumNodes{} \}$ to count the number of nodes in the main tree. We define it
-as
-\[
-  \variable{numNodes} = \maxNumNodes{} - \variable{numTrees} + 1.
-\]
+as $\variable{numNodes} = \maxNumNodes{} - \variable{numTrees} + 1$.
 
@@
   encoded as:
-  \begin{gather*}
-    \begin{alignedat}{8}
-      \variable{structure} &= [0, &&0, &&0, &&1, &&2, &&2, &&6, &&7],\\
+  \begin{alignat*}{9}
+    \variable{structure} &= [0, &&0, &&0, &&1, &&2, &&2, &&6, &&7], \quad
+    &&\variable{numNodes} = 6, \\
     \variable{values} &= [{\lor}, &&{\neg}, &&{\land}, \mathsf{P}(&&X),
-      \mathsf{Q}(&&X), \mathsf{P}(&&X), &&\top, &&\top],
-    \end{alignedat} \\
-    \variable{numNodes} = 6, \quad \variable{numTrees} = 3.
-  \end{gather*}
+    \mathsf{Q}(&&X), \mathsf{P}(&&X), &&\top, &&\top], \quad
+    &&\variable{numTrees} = 3.
+  \end{alignat*}
 \end{example}
 
-\begin{figure}
+\begin{figure}[t]
   \centering
@@
 We need to constrain the forest represented by the $\variable{structure}$
-array together with its $\variable{values}$ to eliminate unnecessary symmetries
-and adhere to our desired format. First, we can recognise that the order of the
-elements in the $\variable{structure}$ array does not matter, i.e., the
-structure is only defined by how the elements link to each other, so we can add
-a constraint saying that:
-
+array together with its $\variable{values}$ to eliminate symmetries and adhere
+to our desired format. First, we can recognise that the order of the elements in
+the $\variable{structure}$ array does not matter, i.e., the structure is only
+defined by how the elements link to each other, so we can add a constraint
+saying that
 \begin{constraint}
@@
 \end{constraint}
-
 Next, since we already have a variable that counts the number of nodes in the
 main tree, we can fix the structure and the values of the remaining trees to
-some constant values:
-
+some constant values.
 \begin{constraint}
@@
 \end{constraint}
-
 The second part of this constraint states that every node in the main tree
@@
 number of children (zero, one, and two, respectively).
-
 \begin{constraint} \label{constraint:node_types}
@@
 \end{constraint}
-
 The value $\top$ serves a twofold purpose: it is used as the fixed value for
@@
 $\top$ as the value:
-
 \begin{constraint}
@@
 \end{constraint}
-
 Finally, we add a way to disable a clause by setting its head predicate to
 $\Box$:
-
 \begin{constraint}
@@
 
-\section{Variable Symmetries} \label{sec:variable_symmetry}
-
-% TODO: Response to a review: Symmetry removal is important for two reasons.
-% First, if we want to generate all programs that match a certain description,
-% we would rather not generate the same program multiple times. Second, symmetry
-% removal makes the constraint solving task much simpler by significantly
-% reducing the search space that needs to be explored, often turning an
-% intractable problem into an easy one.
-
-Given any clause, we can permute the variables in that clause without changing
-the meaning of the clause or the entire program. Thus, we want to fix the order
-of variables to eliminate unnecessary symmetries. Informally, we can say that
-variable $X$ goes before variable $Y$ if the first occurrence of $X$ in either
-the head or the body of the clause is before the first occurrence of $Y$. Note
-that the constraints described in this section only make sense if $|\variables| >
-1$. Also, note that all definitions and constraints here are on a per-clause
-basis.
-
+\section{Variable Symmetry Breaking} \label{sec:variable_symmetry}
+
+Ideally, we want to avoid generating programs that are equivalent in a sense
+that they produce the same answers to all queries. Even more importantly, we
+want to avoid generating multiple internal representations that ultimately
+result in the same program. This is the purpose of \emph{symmetry-breaking
+  constraints}, another important benefit of which is that the constraint
+solving task becomes easier \cite{DBLP:conf/cp/Walsh06}. Given any clause, we
+can permute the variables in that clause without changing the meaning of the
+clause or the entire program. Thus, we want to fix the order of variables.
+Informally, we can say that variable $X$ goes before variable $Y$ if the first
+occurrence of $X$ in either the head or the body of the clause is before the
+first occurrence of $Y$. Note that the constraints described in this section
+only make sense if $|\variables{}| > 1$ and that all definitions and constraints
+here are on a per-clause basis.
 \begin{definition}
@@
 \end{definition}
-
-Next, we introduce an array that, for each variable, holds the position of its
-first occurrence:
-
+Next, we introduce an array that holds the first occurrence of each variable.
 \begin{definition}
@@
 \end{definition}
-
 Here, a value of zero means that the variable does not occur in the clause. The
@@
 \cref{constraint:diffbutzero}. Because of this choice, the definition of
-$\variable{intros}$ shifts all indices by one. Lastly, we add the constraint
-that eliminates variable symmetries:
-
+$\variable{intros}$ shifts all indices by one. Lastly, we add the variable
+symmetry-breaking constraint.
 \begin{constraint}
@@
 \end{constraint}
-
-In other words, we constrain the model so that the variable listed first in
-whatever order $\variables{}$ is presented in has to occur first in our
+In other words, we constrain the model so that the variable listed first (in
+whatever order $\variables{}$ is presented in) has to occur first in our
 representation of a clause.
@@
   Let $\constants{} = \emptyset$, $\variables{} = \{ X, Y, Z \}$, $\maxArity{} =
-  2$, $\maxNumNodes{} = 3$, and consider the clause
-  \[
-    \mathsf{sibling}(X, Y) \gets \mathsf{parent}(X, Z) \land
-    \mathsf{parent}(Y, Z).
-  \]
-  Then
+  2$, $\maxNumNodes{} = 3$, and consider the clause $\mathsf{sibling}(X, Y)
+  \gets \mathsf{parent}(X, Z) \land \mathsf{parent}(Y, Z)$. Then
   \begin{align*}
@@
 We add a number of redundant constraints to make search more efficient. First,
-we can state that the positions occupied by different terms must be different:
-
+we can state that the positions occupied by different terms must be different.
 \begin{constraint} \label{constraint:all_diff}
@@
 \end{constraint}
-
 The reason why we used zero to represent an unused variable is so that we could
 efficiently rephrase \cref{constraint:all_diff} for the $\variable{intros}$
-array:
-
+array.
 \begin{constraint} \label{constraint:diffbutzero}
@@
 \end{constraint}
-
 We can also add another link between $\variable{intros}$ and $\variable{occ}$
 that essentially says that the smallest element of a set is an element of the
-set:
-
+set.
 \begin{constraint}
-  For $v \in \variables{}$,
-  \[
-    \variable{intros}[v] \ne 0 \quad \iff \quad
-    \variable{intros}[v] - 1 \in \variable{occ}[v].
-  \]
-\end{constraint}
-
+  For $v \in \variables{}$, $\variable{intros}[v] \ne 0 \iff
+  \variable{intros}[v] - 1 \in \variable{occ}[v]$.
+\end{constraint}
 Finally, we define an auxiliary set variable to act as a set of possible values
@@
 that non-predicate nodes in the tree representation of a clause cannot have
-variables as arguments:
-
+variables as arguments.
 \begin{constraint} \label{constraint:potentialIntroductions}
@@
   different scenarios. The details of this empirical investigation are omitted
-  as they are not crucial to the thrust of this paper.}. To simplify the task,
-we only consider clauses without probabilities and disable (negative) cycle
+  as they are not crucial to the thrust of this paper.}. Being able to establish
+two ways to generate the same sequence of numbers (i.e., numbers of programs
+with certain properties and parameters) allows us to gain confidence that the
+constraint model accurately matches our intentions. To simplify the task, we
+only consider clauses without probabilities and disable (negative) cycle
 elimination. We also introduce the term \emph{total arity} of a body of a clause
@@
 
-We will first consider clauses with gaps, i.e., without taking variables and
-constants into account. Let $T(n, a)$ denote the number of possible clause
+We will first consider clauses with \emph{gaps}, i.e., without taking variables
+and constants into account. Let $T(n, a)$ denote the number of possible clause
 bodies with $n$ nodes and total arity $a$. Then $T(1, a)$ is the number of
@@
 nodes. Similarly, the second sum considers every possible way to partition the
-total arity $a$ across the $k$ children nodes.
-
-We can then count the number of possible clause bodies with total arity $a$ (and
-any number of nodes) as
+total arity $a$ across the $k$ children nodes. We can then count the number of
+possible clause bodies with total arity $a$ (and any number of nodes) as
 \[
@@
   \sum_{\substack{ \sum_{i=1}^{|\predicates{}|} h_i = n,\\
-      |\predicates{}| \le n \le \maxNumClauses,\\
+      |\predicates{}| \le n \le \maxNumClauses{},\\
       h_i \ge 1 \text{ for all } i}} \prod_{i=1}^{|\predicates{}|}
-  \multiset{\sum_{a=0}^{\maxArity{} \times \maxNumNodes{}} C(a) P(a+a_i)}{h_i},
-\]
-where
-\[
-  \multiset{n}{k} = \binom{n+k-1}{k}
-\]
-counts the number of ways to select $k$ out of $n$ items with repetition (and
-without ordering). Here, we sum over all possible ways to distribute
-$|\predicates{}| \le n \le \maxNumClauses{}$ clauses among $|\predicates{}|$
-predicates so that each predicate gets at least one clause. For each predicate,
-we can then count the number of ways to select its clauses out of all possible
-clauses. The number of possible clauses can be computed by considering each
-possible arity $a$, and multiplying the number of `unfinished' clauses $C(a)$ by
-the number of ways to select the required $a+a_i$ terms in the body and the head
-of the clause.
+  \binom{\sum_{a=0}^{\maxArity{} \times \maxNumNodes{}} C(a) P(a+a_i)}{h_i},
+\]
+Here, we sum over all possible ways to distribute $|\predicates{}| \le n \le
+\maxNumClauses{}$ clauses among $|\predicates{}|$ predicates so that each
+predicate gets at least one clause. For each predicate, we can then count the
+number of ways to select its clauses out of all possible clauses. The number of
+possible clauses can be computed by considering each possible arity $a$, and
+multiplying the number of `unfinished' clauses $C(a)$ by the number of ways to
+select the required $a+a_i$ terms in the body and the head of the clause.
 
 \section{Predicate Independence} \label{sec:independence}
-
-% TODO: Review: Section 7 defined predicate (in)dependence. It is done using the
-% constraint model, but given a logic program, it could just as well be
-% extracted from the logic program (construct body tree from each clause).
-% Answer: Motivate why we need this.
 
@@
 \emph{stratified} if $G_{\mathscr{P}}$ has no negative cycles.
-
 \begin{definition}
@@
   $\mathsf{father}$ is negative, while the other two edges are positive.
-
+  The dependencies of each predicate are:
+  \begin{alignat*}{3}
+    D_{\mathsf{parent}} &= \{ \mathsf{parent} \}, \quad && D_{\mathsf{sibling}}
+    &&= \{\mathsf{sibling}, \mathsf{parent} \},\\
+    D_{\mathsf{mother}} &= \{ \mathsf{mother} \}, \quad && D_{\mathsf{father}}
+    &&= \{ \mathsf{father}, \mathsf{mother}, \mathsf{parent} \}.
+  \end{alignat*}
+  Hence, we have two pairs of independent predicates, i.e., $\mathsf{mother}$ is
+  independent of $\mathsf{parent}$ and $\mathsf{sibling}$.
+\end{example}
 \begin{figure}[t]
@@
 
-  We can now list the dependencies of each predicate:
-  \begin{alignat*}{3}
-    D_{\mathsf{parent}} &= \{ \mathsf{parent} \}, \quad && D_{\mathsf{sibling}}
-    &&= \{\mathsf{sibling}, \mathsf{parent} \},\\
-    D_{\mathsf{mother}} &= \{ \mathsf{mother} \}, \quad && D_{\mathsf{father}}
-    &&= \{ \mathsf{father}, \mathsf{mother}, \mathsf{parent} \}.
-  \end{alignat*}
-  Hence, we have two pairs of independent predicates, i.e., $\mathsf{mother}$ is
-  independent of $\mathsf{parent}$ and $\mathsf{sibling}$.
-\end{example}
-
-We can now add a constraint to define an adjacency matrix for the predicate
+Next, we add a constraint that defines an adjacency matrix for the predicate
 dependency graph but without positivity/negativity:
-
 \begin{definition} \label{def:adjacency_matrix}
@@
 \end{definition}
-
 Given an undetermined model, we can classify all dependencies of a predicate
@@
 
-  \begin{figure}
+  \begin{figure}[t]
     \begin{minipage}{.49\textwidth}
@@
 are needed to complete the model: heuristics and restarts. By trial and error,
-the variable ordering heuristic was devised to eliminate sources of thrashing,
-i.e., situations where a contradiction is being `fixed' by making changes that
-have no hope of fixing the contradiction. Thus, we partition all decision
-variables into an ordered list of groups, and require the values of all
-variables from one group to be determined before moving to the next group.
+the variable ordering heuristic was devised to eliminate sources of
+\emph{thrashing}, i.e., situations where a contradiction is being `fixed' by
+making changes that have no hope of fixing the contradiction. Thus, we partition
+all decision variables into an ordered list of groups, and require the values of
+all variables from one group to be determined before moving to the next group.
 Within each group, we use the `fail first' variable ordering heuristic. The
@@
 We also employ a geometric restart policy, restarting after $10, 20, 40,
-80, \dots$ contradictions.
+80, \dots$ contradictions\footnote{Restarts are helpful in overcoming early
+  mistakes in the search process, but can be disabled if one wants to find all
+  solutions, in which case search is complete regardless of the variable
+  ordering heuristic.}.
 
@@
 The majority (\SI{97.7}{\percent}) of runs finished in under \SI{1}{\second},
-while four instances timed out: all with $|\predicates| = \maxNumClauses{} -
+while four instances timed out: all with $|\predicates{}| = \maxNumClauses{} -
 |\predicates{}| = \maxNumNodes{} = 8$ and the remaining parameters all
@@
 \end{figure}
-
-% TODO: Review: From section 9 it seems that this language has a very special
-% handcrafted (heuristic) solution procedure that is not guaranteed to find a
-% solution if one exists.
-% Answer: Adding a restart policy helps with efficiency when generating larger
-% programs, but if we want to find all possible programs, restarts can be
-% disabled (and this is likely to only be relevant with low parameter values,
-% where the number of possible programs is in thousands rather than millions).
-% Note that combinations of parameter values that have no solutions (or are
-% unlikely to have solutions) are unlikely to occur in practice (i.e., be of
-% interest).
 
@@
 %    a function of the number of independent pairs of predicates for
-%    $|\predicates| = 8$. Outliers are hidden, the dots denote mean values, and
+%    $|\predicates{}| = 8$. Outliers are hidden, the dots denote mean values, and
 %    the vertical axis is on a $\log_{10}$ scale.}
@@
 % 5. It can easily be shown that all generated logic programs are satisfiable
-% 6. Logic programs typically only have a single conjunction with literals, but
-% we can easily adapt the model to handle that.
 

### 2020-05-06 text/paper2/impact.tex
Minor grammar and readability adjustments

--- 2020-04-19 paper2/impact.tex
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (205.30, 77.98) {$|\mathcal{P}|$};
+\node[text=black,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (205.30, 77.98) {$|\mathcal{P}|$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (205.54, 65.59) {$|\mathcal{V}|$};
+\node[text=black,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (205.54, 65.59) {$|\mathcal{V}|$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (205.85, 53.19) {$|\mathcal{C}|$};
+\node[text=black,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (205.85, 53.19) {$|\mathcal{C}|$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (189.68, 90.33) {$\mathcal{M}_{\mathcal{C}}-|\mathcal{P}|$};
+\node[text=black,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (189.68, 90.33) {$\mathcal{M}_{\mathcal{C}}-|\mathcal{P}|$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (203.37,163.74) {$\mathcal{M}_{\mathcal{N}}$};
+\node[text=black,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (203.37,163.74) {$\mathcal{M}_{\mathcal{N}}$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (136.94, 78.52) {$\mathcal{M}_{\mathcal{A}}$};
+\node[text=black,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (136.94, 78.52) {$\mathcal{M}_{\mathcal{A}}$};
 \end{scope}

### 2020-05-06 text/paper2/paper.tex
Minor grammar and readability adjustments

@@
 % 2) Avoid the Definition environment (to save space)
-% 3) Check the grammar
-% 4) Update the abstract
 
@@
   for negative cycle detection. Finally, we provide a combinatorial argument for
-  correctness and describe how the parameters of the model affect the empirical
-  difficulty of the program generation task.
+  the correctness of the model and describe how the parameters of the model
+  affect the empirical difficulty of the program generation task.
 
@@
 of clarity \cite{DBLP:journals/ai/SelmanML96}. This changed with the study of
-generation of random SAT instances against different input parameters (e.g.,
-clause length and total number of variables) to better understand the behaviour
-of algorithms and their ability to solve random synthetic problems.
+generating random SAT instances against different input parameters (e.g.,
+clause length and the total number of variables) to better understand the
+behaviour of algorithms and their ability to solve random synthetic problems.
 Unfortunately, in the context of probabilistic logic programming, most current
 approaches to random instance generation are very restrictive, e.g., limited to
-clauses with only two literals \cite{DBLP:conf/lpnmr/NamasivayamT09}, or to
-clauses of the form $a \gets \neg b$ \cite{DBLP:journals/tocl/WenWSL16},
-although some are more expressive, e.g., defining a program only by the
-(maximum) number of atoms in the body and the total number of rules
-\cite{DBLP:conf/iclp/ZhaoL03}.
-
-In this work, we introduce a constraint model for generating random logic
-programs according to a number of user-specified parameters on the structure of
-the program. In fact, the same model can generate both probabilistic programs
-in the syntax of ProbLog \cite{DBLP:conf/ijcai/RaedtKT07} and
-non-probabilistic Prolog programs. A major advantage of a constraint-based
-approach is the ability to add additional constraints as needed, and to do that
-efficiently (compared to generate-and-test approaches). As an example of this,
-we develop a custom constraint (with propagation and entailment algorithms)
-that, given two predicates $\mathsf{P}$ and $\mathsf{Q}$, ensures that any
-ground atom with predicate $\mathsf{P}$ is independent of any ground atom
-with predicate $\mathsf{Q}$. In this way, we can easily regulate the
-independence structure of the underlying probability distribution. We also
-present a combinatorial argument for correctness, counting the number of
-programs that the model produces for various parameter values. Finally, we show
-how the model scales when tasked with producing more complicated programs.
-
-% TODO: these two paragraphs aren't connected
+clauses with only two literals \cite{DBLP:conf/lpnmr/NamasivayamT09}, or clauses
+of the form $a \gets \neg b$ \cite{DBLP:journals/tocl/WenWSL16}, although some
+are more expressive, e.g., defining a program only by the (maximum) number of
+atoms in the body and the total number of rules \cite{DBLP:conf/iclp/ZhaoL03}.
+
+In this work, we introduce a constraint-based representation for logic programs
+based on some simple parameters that describe the program's size, what
+predicates and constants it uses, etc. This representation takes the form of a
+constraint satisfaction problem, i.e., a set of discrete variables and
+restrictions on what values they can take. Every solution to this problem (as
+output by a constraint solver) directly translates into a logic program. One can
+either use random value-ordering heuristics and restarts to generate random
+programs or find all (sufficiently small) programs that satisfy the given
+requirements. In fact, the same model can generate both probabilistic programs
+in the syntax of ProbLog \cite{DBLP:conf/ijcai/RaedtKT07} and non-probabilistic
+Prolog programs.
+
+A major advantage of a constraint-based approach is the ability to add
+additional constraints as needed, and to do that efficiently (compared to
+generate-and-test approaches). As an example of this, we develop a custom
+constraint (with propagation and entailment algorithms) that, given two
+predicates $\mathsf{P}$ and $\mathsf{Q}$, ensures that any ground atom with
+predicate $\mathsf{P}$ is independent of any ground atom with predicate
+$\mathsf{Q}$. In this way, we can easily regulate the independence structure of
+the underlying probability distribution. We also present a combinatorial
+argument for correctness, counting the number of programs that the model
+produces for various parameter values and show how the model scales when tasked
+with producing more complicated programs.
 
 A common restriction put on both logic programs and probabilistic logic programs
-in order to ensure that there is a unique answer to every query is known as
+to ensure that there is a unique answer to every query is known as
 \emph{stratification}
@@
 
-% TODO: Review: The paper fails to provide explanation of critical parts: for
-% example, how is a set of constraints going to be turned into a random logic
-% program? We don’t find out until section 9.
-
-%We develop a constraint-based representation for valid logic programs based on
-%some simple parameters that describe the program's size, what predicates and
-%constants it uses, etc. This representation takes the form of a constraint
-%satisfaction problem, i.e., a set of discrete variables and restrictions on what
-%values they can take. After a constraint solver provides valid values for these
-%variables, they directly translate into a logic program.
-
 \section{Preliminaries}
@@
 atoms using conjunction $\land$, disjunction $\lor$, and negation
-$\neg$\footnote{One can add a couple extra constraints to restrict the
+$\neg$\footnote{One can add a couple of extra constraints to restrict the
   generated programs to logic programs that only allow a single disjunction with
@@
 In the world of constraint satisfaction, we also have \emph{(constraint)
-  variables}, each with its own \emph{domain}, whose values are restricted using
+  variables}, each with a \emph{domain}, whose values are restricted using
 \emph{constraints}. All constraint variables in the model are integer or set
@@
 $\variable{predicate} = \Box$. Assuming a lexicographic order over entire
-clauses such that $\Box > \mathsf{P}$ for all $\mathsf{P} \in \predicates{}$, and
+clauses such that $\Box > \mathsf{P}$ for all $\mathsf{P} \in \predicates{}$ and
 the head predicate is the `first digit' of this representation, we get the
@@
 
-Ideally, we want to avoid generating programs that are equivalent in a sense
+Ideally, we want to avoid generating programs that are equivalent in the sense
 that they produce the same answers to all queries. Even more importantly, we
@@
 
-We add a number of redundant constraints to make search more efficient. First,
+We add several redundant constraints to make search more efficient. First,
 we can state that the positions occupied by different terms must be different.
@@
 \section{Counting Programs} \label{sec:counting}
-% TODO: Does this section still work if I don't allow duplicates?
-
-\setcounter{footnote}{0}
-
-% TODO: Review: Finally, regarding correctness of the proposal, I don´t
-% understand "the combinatorial argument for correctness" result, how does the
-% provided analysis show correctness relative to the properties? I was expecting
-% a proof that would show the relationship between the formalized constraint and
-% the desired property, to chow for instance that if such constraint is taken
-% into account in the construction of the program then it is impossible that the
-% program does not satisfy the property. Is there something I do not understand
-% from this? I find the proposal lacking in this terms, not finding the
-% arguments for validity strong enough, unless I misunderstood the analysis.
-% Answer: 
-% Regarding correctness, we decided against including proofs that a constraint for
-% a property ensures the property because the discussed properties are all
-% syntactic, and the constraint model itself is a representation of the same
-% syntax so the proofs would not be particularly revealing. We can nonetheless add
-% them if necessary.
-%
-% Instead, Section 6 shows correctness in a sense that if two methods generate the
-% same numbers (i.e., numbers of programs with certain properties and parameters),
-% then they describe the same thing, and we gain confidence that the constraint
-% description (which matches the combinatorial description) accurately matches our
-% intentions. This method helped us debug many aspects of the model and can be
-% particularly revealing when both the model and the combinatorial argument become
-% more intricate.
 
@@
 \section{Predicate Independence} \label{sec:independence}
-
-% TODO: Answer to a review: All constraints have propagation and entailment
-% procedures behind them. When designing a new constraint, unless it can be
-% composed of already-existing constraints, designing these algorithms is, in
-% fact, completely in the spirit of constraint programming.
 
@@
 We also employ a geometric restart policy, restarting after $10, 20, 40,
-80, \dots$ contradictions\footnote{Restarts are helpful in overcoming early
-  mistakes in the search process, but can be disabled if one wants to find all
-  solutions, in which case search is complete regardless of the variable
-  ordering heuristic.}.
+80, \dots$ contradictions\footnote{Restarts help overcome early mistakes in the
+  search process but can be disabled if one wants to find all solutions, in
+  which case search is complete regardless of the variable ordering heuristic.}.
 
@@
 
-In addition, note that our model treats logically equivalent but syntactically
+Also, note that our model treats logically equivalent but syntactically
 different formulas as different. This is so in part because designing a

### 2020-05-07 scripts/parse_problog_output.py
Move config variables to the Config class

@@ -1,0 +1,33 @@
+import csv
+import os
+
+DIR = '../generated/problog_output/'
+
+data = []
+for filename in os.listdir(DIR):
+    d = {'instance': filename[:filename.index('.')]}
+    if not filename.endswith('.pl'):
+        continue
+    with open(DIR + filename, 'r') as f:
+        for line in f:
+            if line.startswith('[INFO]'):
+                if line.startswith('[INFO] Output level'):
+                    continue
+                name = line[(line.index(' ')+1):line.index(':')]
+                time = line[(line.rindex(' ')+1):line.rindex('s')]
+                d[name] = time
+            elif line.startswith('NonGroundProbabilisticClause'):
+                d['answer'] = None
+            else:
+                d['answer'] = ''.join([c for c in line if c.isdigit() or c == '.'])
+    data.append(d)
+
+fieldnames = set()
+for d in data:
+    fieldnames.update(d.keys())
+
+with open('../data/output.csv', 'w', newline='') as csvfile:
+    writer = csv.DictWriter(csvfile, fieldnames=fieldnames)
+    writer.writeheader()
+    for d in data:
+        writer.writerow(d)

### 2020-05-07 src/main/java/model/Config.java

@@ -4,6 +4,11 @@ import java.util.ArrayList;
 import java.util.List;
 
 public class Config {
+
+    public final boolean allowEmptyBodies = true;
+    public final boolean defineEachPredicate = true;
+    public final boolean printDebugInfo = false;
+
     public int maxNumNodes;
     public int maxNumClauses;
     public String forbidCycles;

### 2020-05-07 scripts/generate_programs.py
Refactoring

@@ -14,14 +14,15 @@ OUTPUT_DIR = '../generated/problog_output/'
 TIMEOUT = '60' # in seconds
 FORBID_CYCLES = 'NEGATIVE'
 NUM_THREADS = 1
+REPEAT = 10
 
 class Config:
     def __init__(self, max_num_nodes, max_num_clauses, num_predicates, max_arity, num_variables, num_constants,
-                 num_independent_pairs, required_formula=None):
+                 num_independent_pairs, count, required_formula=None):
         self.forbidCycles = FORBID_CYCLES
         self.timeout = TIMEOUT + 's'
         self.prefix = '_'.join(str(x) for x in [num_predicates, num_variables, max_num_nodes, max_arity,
-                                                num_independent_pairs]) + '_'
+                                                num_independent_pairs, count])
 
         self.maxNumNodes = max_num_nodes
         self.maxNumClauses = max_num_clauses
@@ -61,13 +62,13 @@ def run_problog():
 
 def generate_programs(args):
     num_predicates, num_variables, max_num_nodes, max_arity, num_independent_pairs = args
-    time.sleep(0.1)
-    config = Config(max_num_nodes, num_predicates, num_predicates, max_arity, num_variables, 0, num_independent_pairs)
-    config.save()
-    time.sleep(0.1)
-    generator = subprocess.Popen(['mvn',  'exec:java', '-Dexec.mainClass=model.GeneratePrograms',
-                                  '-Dexec.classpathScope=runtime', '-Dexec.args="normal"'], cwd="../")
-    generator.wait()
+    for i in range(REPEAT):
+        config = Config(max_num_nodes, num_predicates, num_predicates,
+                        max_arity, num_variables, 0, num_independent_pairs, i)
+        config.save()
+        generator = subprocess.Popen(['mvn',  'exec:java', '-Dexec.mainClass=model.GeneratePrograms',
+                                      '-Dexec.classpathScope=runtime', '-Dexec.args="normal"'], cwd="../")
+        generator.wait()
 
 arguments = [(num_predicates, num_variables, max_num_nodes, max_arity, num_independent_pairs)
              for num_predicates, num_variables, max_num_nodes in itertools.product([2, 4, 8], repeat=3)

### 2020-05-07 src/main/java/model/Config.java

@@ -13,12 +13,13 @@ public class Config {
     public static final String FILENAME = "config.yaml";
     public static final String PROGRAM_COUNTS_FILENAME = "data/program_counts.csv";
 
-    public final boolean allowEmptyBodies = true;
+    public final boolean allowEmptyBodies = false;
     public final boolean defineEachPredicate = true;
     public final boolean printDebugInfo = false;
     public final boolean printProgramsWhileCounting = false;
-    public final int numSolutions = 10;
+    public final int numSolutions = 1;
     public final String outputDirectory = "generated/programs/";
+    public double[] probabilities = {0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9};
 
     public int maxNumNodes;
     public int maxNumClauses;

### 2020-05-07 src/main/java/modes/CountingMode.java

@@ -49,7 +49,8 @@ public class CountingMode {
 
             Config config = new Config(Integer.parseInt(data[4]), Integer.parseInt(data[5]), "NONE", "60s",
                     predicates, arities, variables, constants, new LinkedList<>(), null);
-            Program p = new Program(config, new double[]{1});
+            config.probabilities = new double[]{1};
+            Program p = new Program(config);
 
             // Count the number of solutions
             int i = 0;

### 2020-05-08 scripts/generate_strings.py
Integrate program generation and fact generation

@@ -1,0 +1,23 @@
+def next_name(name):
+    'Generate an infinite sequence of strings'
+    if (name[-1] != 'z'):
+        return name[:-1] + chr(ord(name[-1]) + 1)
+
+    i = len(name) - 1
+    while (i >= 0 and name[i] == 'z'):
+        i -= 1
+    first_z = i + 1
+
+    count_z = len(name) - first_z
+    if first_z >= 1:
+        return name[:(first_z-1)] + chr(ord(name[first_z-1]) + 1) + 'a' * count_z
+    return 'a' * (count_z + 1)
+
+def generate_constants(n, prefix='c'):
+    'Generate n constants'
+    if (n == 0):
+        return []
+    s = ['a']
+    for _ in range(n - 1):
+        s.append(next_name(s[-1]))
+    return [prefix + x for x in s]

### 2020-05-10 scripts/analyse_data.R
Gathering experimental data

@@ -1,125 +1,0 @@
-library(ggplot2)
-library(tikzDevice)
-library(dplyr)
-library(ggrepel)
-
-df <- read.csv("src/runtime.csv", header = FALSE, sep = ";", skip = 1)
-df <- df[, colSums(is.na(df)) < nrow(df)]
-names(df) <- c("numPredicates", "maxArity", "numVariables", "numConstants", "numAdditionalClauses", "numIndependentPairs", "maxNumNodes",
-                 "solutionCount", "buildingTime", "totalTime", "initTime", "nodes", "backtracks", "fails", "restarts")
-df$percentageIndependent <- round(ifelse(df$numIndependentPairs >= 2, df$numIndependentPairs / choose(df$numPredicates, 2), 0), 2)
-df$numClauses <- df$numPredicates + df$numAdditionalClauses
-
-# Numbers
-small <- df[df$totalTime < 1, ]
-nrow(small)/nrow(df)*100
-tail(sort(df$totalTime))
-df %>% group_by(df$numPredicates) %>% tally()
-
-# Phase transition
-big <- df[df$numPredicates == 8, ]
-tikz(file = "paper/phase_transition.tex", width = 6, height = 2)
-ggplot(big, aes(factor(numIndependentPairs), nodes, group = numIndependentPairs)) +
-  geom_boxplot(outlier.shape = NA) +
-  coord_trans(y = "log10", limy = c(100, quantile(big$nodes, 0.91))) +
-  scale_y_continuous(breaks = c(1, 20, 100, 1000, 10000),
-                     labels = c("1", "20", expression(10^2), expression(10^3), expression(10^4))) +
-  stat_summary(fun.y = mean, geom = "point") +
-  xlab("Independent pairs") +
-  ylab("Nodes") +
-  theme_set(theme_minimal(base_size = 7))
-dev.off()
-
-# Extra stuff to investigate the phase transition
-bigs <- big %>% group_by(numIndependentPairs) %>% slice(which.max(nodes))
-ggplot(bigs, aes(numIndependentPairs, nodes)) + geom_point()
-ggplot(big, aes(factor(numIndependentPairs), totalTime, group = numIndependentPairs)) +
-  geom_boxplot(outlier.shape = NA) +
-  coord_trans(y = "log10") +
-  scale_y_continuous(breaks = c(1, 20, 100, 1000, 10000),
[…]

### 2020-05-10 scripts/analyse_model.R

@@ -1,0 +1,126 @@
+library(ggplot2)
+library(tikzDevice)
+library(dplyr)
+library(ggrepel)
+
+# This is all for the runtime data of the CP model
+
+df <- read.csv("src/runtime.csv", header = FALSE, sep = ";", skip = 1)
+df <- df[, colSums(is.na(df)) < nrow(df)]
+names(df) <- c("numPredicates", "maxArity", "numVariables", "numConstants", "numAdditionalClauses", "numIndependentPairs", "maxNumNodes",
+                 "solutionCount", "buildingTime", "totalTime", "initTime", "nodes", "backtracks", "fails", "restarts")
+df$percentageIndependent <- round(ifelse(df$numIndependentPairs >= 2, df$numIndependentPairs / choose(df$numPredicates, 2), 0), 2)
+df$numClauses <- df$numPredicates + df$numAdditionalClauses
+
+# Numbers
+small <- df[df$totalTime < 1, ]
+nrow(small)/nrow(df)*100
+tail(sort(df$totalTime))
+df %>% group_by(df$numPredicates) %>% tally()
+
+# Phase transition
+big <- df[df$numPredicates == 8, ]
+tikz(file = "paper/phase_transition.tex", width = 6, height = 2)
+ggplot(big, aes(factor(numIndependentPairs), nodes, group = numIndependentPairs)) +
+  geom_boxplot(outlier.shape = NA) +
+  coord_trans(y = "log10", limy = c(100, quantile(big$nodes, 0.91))) +
+  scale_y_continuous(breaks = c(1, 20, 100, 1000, 10000),
+                     labels = c("1", "20", expression(10^2), expression(10^3), expression(10^4))) +
+  stat_summary(fun.y = mean, geom = "point") +
+  xlab("Independent pairs") +
+  ylab("Nodes") +
+  theme_set(theme_minimal(base_size = 7))
+dev.off()
+
+# Extra stuff to investigate the phase transition
+bigs <- big %>% group_by(numIndependentPairs) %>% slice(which.max(nodes))
+ggplot(bigs, aes(numIndependentPairs, nodes)) + geom_point()
+ggplot(big, aes(factor(numIndependentPairs), totalTime, group = numIndependentPairs)) +
+  geom_boxplot(outlier.shape = NA) +
+  coord_trans(y = "log10") +
+  scale_y_continuous(breaks = c(1, 20, 100, 1000, 10000),
[…]

### 2020-05-10 scripts/analyse_problog.R

@@ -1,0 +1,130 @@
+require(reshape2)
+require(ggplot2)
+require(dplyr)
+require(gridExtra)
+require(scales)
+require(grid)
+require(tidyr)
+
+# TODO: reject all instances where at least one algorithm failed
+
+only_relevant_columns <- c("number.of.predicates", "number.of.variables",
+                           "maximum.number.of.nodes", "maximum.arity",
+                           "number.of.independent.pairs", "domain.size",
+                           "number.of.facts", "proportion.probabilistic",
+                           "proportion.listed", "proportion.independent.pairs", "universe.size", "instance")
+relevant_columns <- c("number.of.predicates", "number.of.variables",
+                      "maximum.number.of.nodes", "maximum.arity",
+                      "number.of.independent.pairs", "domain.size",
+                      "number.of.facts", "proportion.probabilistic",
+                      "proportion.listed", "proportion.independent.pairs", "universe.size", "Total.time")
+pretty_names <- c("The number of predicates", "The number of variables",
+                  "Maximum number of nodes", "Maximum arity",
+                  "The number of independent pairs", "Domain size",
+                  "The number of facts", "The proportion of probabilistic facts",
+                  "The proportion of listed facts", "The proportion of independent pairs",
+                  "The number of possible facts")
+
+prepare.csv <- function(filename) {
+  df <- read.csv(filename, header = TRUE, sep = ",")
+  print(mean(is.na(df$answer)))
+  df <- df[!is.na(df$answer),]
+  #df <- df[df$number.of.predicates == 8,]
+  df$proportion.listed <- df$number.of.facts / df$universe.size
+  df$total.pairs <- df$number.of.predicates * (df$number.of.predicates - 1) / 2
+  df$proportion.independent.pairs <- df$number.of.independent.pairs / df$total.pairs
+  df
+}
+
+sdd <- prepare.csv("../data/problog_sdd.csv")
+nnf <- prepare.csv("../data/problog_nnf.csv")
+symbolic <- prepare.csv("../data/problog_symbolic.csv")
+melted.sdd <- melt(sdd[, relevant_columns], id.var = "Total.time")
[…]

### 2020-05-10 scripts/generate_facts.py

@@ -12,28 +12,32 @@ PROBABILITIES = [x/10 for x in range(1, 10)]
 INPUT_DIR = '../generated/programs/'
 OUTPUT_DIR = '../generated/full_programs/'
 CONFIG_FILENAME = '../config.yaml'
+MAX_PROPORTION_LISTED = 0.75
 
 def facts_to_string(facts, proportion_probabilistic, query):
     'Turn a fact sheet into a string'
     num_probabilistic = int(round(proportion_probabilistic * len(facts), 0))
     factsheet = []
     for i, fact in enumerate(facts):
-        if i < num_probabilistic:
-            factsheet.append(str(random.choice(PROBABILITIES)) + ' :: ' + fact + '.')
-        else:
-            factsheet.append(fact + '.')
-
+        factsheet.append(str(random.choice(PROBABILITIES)) + ' :: ' + fact + '.'
+                         if i < num_probabilistic else fact + '.')
     return '\n'.join(factsheet) + '\n' + 'query({}).\n'.format(query)
 
-def generate_universe(predicates_and_arities, domain):
-    return [predicate + '(' + ','.join(arguments) + ')'
-            for predicate, arity in predicates_and_arities
-            for arguments in itertools.product(domain, repeat=arity)]
-
-def generate_factsheet(predicates_and_arities, proportion_listed, domain):
-    universe = generate_universe(predicates_and_arities, domain)
-    s = random.sample(universe, int(len(universe) * proportion_listed))
-    return s[:-1], s[-1]
+def generate_factsheet(predicates_and_arities, num_facts, domain):
+    facts = set()
+    total = 0
+    correct = 0
+    while len(facts) < num_facts + 1:
+        predicate, arity = random.choice(predicates_and_arities)
+        constants = random.choices(domain, k=arity)
+        previous_len = len(facts)
+        facts.add(predicate + '(' + ','.join(constants) + ')')
+        if len(facts) > previous_len:
+            correct += 1
+        total += 1
+    query = random.sample(facts, 1)[0]
+    print('{:.2f}%'.format(100*correct/total))
+    return facts.difference(set(query)), query
 
 def generate_filename(config, count):
     return '_'.join(str(x) for x in [len(config.predicates),
@@ -43,23 +47,27 @@ def generate_filename(config, count):
                                      len(config.independentPairs), count]
     ) + '.pl'
 
-def generate_new_filename(config, count, domain_size, proportion_listed, proportion_probabilistic):
[…]

### 2020-05-10 scripts/generate_programs.py

@@ -51,14 +51,20 @@ def remove_programs(d):
 
 def generate_programs(args):
     num_predicates, num_variables, max_num_nodes, max_arity, num_independent_pairs = args
+    print('''number of predicates: {}, number of variables: {}, maximum number of
+          nodes: {}, maximum arity: {}, number of independent pairs: {}'''.
+          format(num_predicates, num_variables, max_num_nodes, max_arity, num_independent_pairs))
     for i in range(REPEAT):
         config = Config(max_num_nodes, num_predicates, num_predicates,
                         max_arity, num_variables, 0, num_independent_pairs, i)
+        if os.path.exists(PROGRAMS_DIR + config.prefix + '.pl'):
+            continue
         config.save()
         generator = subprocess.Popen(['mvn',  'exec:java', '-Dexec.mainClass=model.GeneratePrograms',
                                       '-Dexec.classpathScope=runtime', '-Dexec.args="normal"'], cwd="../")
         generator.wait()
         append_factsheets(config, i)
+        time.sleep(0.1)
 
 arguments = [(num_predicates, num_variables, max_num_nodes, max_arity, num_independent_pairs)
              for num_predicates, num_variables, max_num_nodes in itertools.product([2, 4, 8], repeat=3)
@@ -66,5 +72,6 @@ arguments = [(num_predicates, num_variables, max_num_nodes, max_arity, num_indep
              for num_independent_pairs in range(int(num_predicates * (num_predicates - 1) / 2) + 1)]
 remove_programs(PROGRAMS_DIR)
 remove_programs(FULL_PROGRAMS_DIR)
+random.shuffle(arguments)
 for args in arguments:
     generate_programs(args)

### 2020-05-10 scripts/parse_problog_output.py

@@ -3,9 +3,17 @@ import os
 
 DIR = '../generated/problog_output/'
 
+def extract_parameters_from_filename(filename):
+    values = filename[:filename.rindex('.')].split('_')
+    names = ['number.of.predicates', 'number.of.variables',
+             'maximum.number.of.nodes', 'maximum.arity',
+             'number.of.independent.pairs', 'instance', 'domain.size',
+             'number.of.facts', 'proportion.probabilistic', 'universe.size']
+    return dict(zip(names, values))
+
 data = []
 for filename in os.listdir(DIR):
-    d = {'instance': filename[:filename.index('.')]}
+    d = extract_parameters_from_filename(filename)
     if not filename.endswith('.pl'):
         continue
     with open(DIR + filename, 'r') as f:

### 2020-05-10 scripts/run_problog.py

@@ -8,15 +8,18 @@ OUTPUT_DIR = '../generated/problog_output/'
 TIMEOUT = '60'
 
 def run_one(filename):
+    output_filename = OUTPUT_DIR + filename
+    if os.path.exists(output_filename):
+        return
     sys.stdout.write('.')
     sys.stdout.flush()
-    output = subprocess.Popen(['problog', '-v', PROGRAMS_DIR + filename, '-t', TIMEOUT],
+    output = subprocess.Popen(['problog', '-v', PROGRAMS_DIR + filename, '-t', TIMEOUT, '--symbolic'],
                               stdout=subprocess.PIPE)
     output_str = output.communicate()[0][:-1].decode('utf-8')
-    with open(OUTPUT_DIR + filename, 'w+') as f:
+    with open(output_filename, 'w+') as f:
         f.write(output_str)
 
 
 files = [f for f in os.listdir(PROGRAMS_DIR) if f.endswith('.pl')]
-with multiprocessing.Pool(7) as p:
+with multiprocessing.Pool(6) as p:
     p.map(run_one, files)

### 2020-05-10 src/main/java/modes/NormalMode.java

@@ -3,6 +3,7 @@ package modes;
 import model.Config;
 import model.Program;
 import org.chocosolver.solver.Solver;
+import org.chocosolver.solver.search.limits.FailCounter;
 
 import java.io.BufferedWriter;
 import java.io.FileWriter;
@@ -13,12 +14,14 @@ public class NormalMode {
     public static void run() throws IOException {
         Program p = new Program(Config.initialiseFromFile());
         Solver solver = p.model.getSolver();
+        solver.setGeometricalRestart(10, 1.1, new FailCounter(p.model, 1), 100);
         if (p.config.timeout != null)
             solver.limitTime(p.config.timeout);
         if (p.config.printDebugInfo) {
             solver.showDecisions();
             solver.showContradiction();
         }
+
         for (int i = 0; i < p.config.numSolutions && solver.solve(); i++) {
             String suffix = "";
             if (p.config.numSolutions > 1)

### 2020-05-11 text/paper2/bars.tex
Some new plots

% Created by tikzDevice version 0.12.3 on 2020-05-11 12:49:46
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (173.45,130.09);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (173.45,130.09);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( -0.00,  0.00) rectangle (173.45,130.09);
\end{scope}
\begin{scope}
\path[clip] ( 31.71, 30.69) rectangle ( 97.08,108.01);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 31.71, 30.69) rectangle ( 97.08,108.01);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 36.29) --
	( 97.08, 36.29);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 62.99) --
	( 97.08, 62.99);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 89.69) --
	( 97.08, 89.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71, 49.64) --
	( 97.08, 49.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71, 76.34) --
	( 97.08, 76.34);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71,103.05) --
	( 97.08,103.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 49.54, 30.69) --
	( 49.54,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 79.25, 30.69) --
	( 79.25,108.01);
\definecolor{drawColor}{RGB}{51,51,51}

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.97) -- ( 51.50, 75.90);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.90) -- ( 51.50, 71.97);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.07) -- ( 51.50, 74.99);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.99) -- ( 51.50, 71.07);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 80.47) -- ( 51.50, 84.39);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 84.39) -- ( 51.50, 80.47);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.71) -- ( 51.50, 79.64);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 79.64) -- ( 51.50, 75.71);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.51) -- ( 51.50, 77.44);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.44) -- ( 51.50, 73.51);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.96) -- ( 51.50, 75.88);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.88) -- ( 51.50, 71.96);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.26) -- ( 51.50, 78.19);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.19) -- ( 51.50, 74.26);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.50) -- ( 51.50, 74.42);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.42) -- ( 51.50, 70.50);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.45) -- ( 51.50, 78.37);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.37) -- ( 51.50, 74.45);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.60) -- ( 51.50, 75.53);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.53) -- ( 51.50, 71.60);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.07) -- ( 51.50, 77.99);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.99) -- ( 51.50, 74.07);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 72.86) -- ( 51.50, 76.78);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.78) -- ( 51.50, 72.86);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.26) -- ( 51.50, 75.18);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.18) -- ( 51.50, 71.26);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.60) -- ( 51.50, 75.53);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.53) -- ( 51.50, 71.60);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.53) -- ( 51.50, 75.46);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.46) -- ( 51.50, 71.53);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.17) -- ( 51.50, 78.09);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.09) -- ( 51.50, 74.17);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 72.05) -- ( 51.50, 75.98);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.98) -- ( 51.50, 72.05);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.59) -- ( 51.50, 74.51);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.51) -- ( 51.50, 70.59);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.60) -- ( 51.50, 75.53);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.53) -- ( 51.50, 71.60);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.73) -- ( 51.50, 75.65);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.65) -- ( 51.50, 71.73);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.27) -- ( 51.50, 75.19);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.19) -- ( 51.50, 71.27);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.86) -- ( 51.50, 74.79);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.79) -- ( 51.50, 70.86);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 72.78) -- ( 51.50, 76.70);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.70) -- ( 51.50, 72.78);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.08) -- ( 51.50, 77.01);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.01) -- ( 51.50, 73.08);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.27) -- ( 51.50, 74.19);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.19) -- ( 51.50, 70.27);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.09) -- ( 51.50, 79.01);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 79.01) -- ( 51.50, 75.09);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.26) -- ( 51.50, 78.18);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.18) -- ( 51.50, 74.26);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.92) -- ( 51.50, 75.84);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.84) -- ( 51.50, 71.92);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.89) -- ( 51.50, 74.82);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.82) -- ( 51.50, 70.89);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.81) -- ( 51.50, 74.73);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.73) -- ( 51.50, 70.81);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.32) -- ( 51.50, 75.24);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.24) -- ( 51.50, 71.32);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.51) -- ( 51.50, 77.43);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.43) -- ( 51.50, 73.51);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 72.68) -- ( 51.50, 76.60);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.60) -- ( 51.50, 72.68);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.68) -- ( 51.50, 79.61);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 79.61) -- ( 51.50, 75.68);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.08) -- ( 51.50, 74.01);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.01) -- ( 51.50, 70.08);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 72.32) -- ( 51.50, 76.24);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.24) -- ( 51.50, 72.32);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.44) -- ( 51.50, 74.37);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.37) -- ( 51.50, 70.44);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.61) -- ( 51.50, 74.54);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.54) -- ( 51.50, 70.61);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 69.97) -- ( 51.50, 73.89);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.89) -- ( 51.50, 69.97);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.26) -- ( 51.50, 82.18);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 82.18) -- ( 51.50, 78.26);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.73) -- ( 51.50, 78.66);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.66) -- ( 51.50, 74.73);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.06) -- ( 51.50, 74.99);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.99) -- ( 51.50, 71.06);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58,101.49) -- ( 51.50,105.41);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58,105.41) -- ( 51.50,101.49);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58,102.54) -- ( 51.50,106.46);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58,106.46) -- ( 51.50,102.54);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.11) -- ( 51.50, 81.03);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 81.03) -- ( 51.50, 77.11);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58,101.45) -- ( 51.50,105.38);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58,105.38) -- ( 51.50,101.45);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58,101.49) -- ( 51.50,105.41);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58,105.41) -- ( 51.50,101.49);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 98.71) -- ( 51.50,102.64);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58,102.64) -- ( 51.50, 98.71);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 85.70) -- ( 51.50, 89.62);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 89.62) -- ( 51.50, 85.70);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.59) -- ( 51.50, 74.52);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.52) -- ( 51.50, 70.59);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 69.91) -- ( 51.50, 73.84);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.84) -- ( 51.50, 69.91);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.65) -- ( 51.50, 74.58);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.58) -- ( 51.50, 70.65);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.71) -- ( 51.50, 74.63);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.63) -- ( 51.50, 70.71);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.41) -- ( 51.50, 74.33);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.33) -- ( 51.50, 70.41);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.48) -- ( 51.50, 81.41);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 81.41) -- ( 51.50, 77.48);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 80.61) -- ( 51.50, 84.53);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 84.53) -- ( 51.50, 80.61);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 87.23) -- ( 51.50, 91.16);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 91.16) -- ( 51.50, 87.23);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.91) -- ( 51.50, 77.83);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.83) -- ( 51.50, 73.91);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 49.54, 57.22) -- ( 49.54, 71.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 49.54, 47.48) -- ( 49.54, 34.20);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 38.40, 57.22) --
	( 38.40, 47.48) --
	( 60.68, 47.48) --
	( 60.68, 57.22) --
	( 38.40, 57.22) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 38.40, 52.13) -- ( 60.68, 52.13);
\definecolor{drawColor}{RGB}{51,51,51}

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.78) -- ( 81.21, 85.71);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.71) -- ( 81.21, 81.78);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.35) -- ( 81.21, 86.27);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.27) -- ( 81.21, 82.35);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.08) -- ( 81.21, 83.00);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.00) -- ( 81.21, 79.08);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.03) -- ( 81.21, 82.96);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.96) -- ( 81.21, 79.03);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.81) -- ( 81.21, 86.73);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.73) -- ( 81.21, 82.81);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.76) -- ( 81.21, 84.68);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.68) -- ( 81.21, 80.76);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.46) -- ( 81.21, 84.39);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.39) -- ( 81.21, 80.46);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.59) -- ( 81.21, 91.52);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.52) -- ( 81.21, 87.59);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.62) -- ( 81.21, 84.55);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.55) -- ( 81.21, 80.62);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.17) -- ( 81.21, 87.09);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.09) -- ( 81.21, 83.17);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.21) -- ( 81.21, 83.13);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.13) -- ( 81.21, 79.21);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.27) -- ( 81.21, 83.20);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.20) -- ( 81.21, 79.27);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.26) -- ( 81.21, 83.19);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.19) -- ( 81.21, 79.26);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.88) -- ( 81.21, 90.81);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.81) -- ( 81.21, 86.88);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.48) -- ( 81.21, 82.41);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.41) -- ( 81.21, 78.48);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.54) -- ( 81.21, 88.47);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.47) -- ( 81.21, 84.54);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.09) -- ( 81.21, 91.01);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.01) -- ( 81.21, 87.09);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.58) -- ( 81.21, 86.51);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.51) -- ( 81.21, 82.58);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.17) -- ( 81.21, 90.09);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.09) -- ( 81.21, 86.17);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.00) -- ( 81.21, 89.93);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.93) -- ( 81.21, 86.00);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.62) -- ( 81.21, 85.54);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.54) -- ( 81.21, 81.62);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.72) -- ( 81.21, 93.64);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 93.64) -- ( 81.21, 89.72);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.29) -- ( 81.21, 88.21);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.21) -- ( 81.21, 84.29);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.16) -- ( 81.21, 87.08);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.08) -- ( 81.21, 83.16);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.29) -- ( 81.21, 84.22);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.22) -- ( 81.21, 80.29);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.56) -- ( 81.21, 82.49);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.49) -- ( 81.21, 78.56);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.11) -- ( 81.21, 94.04);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 94.04) -- ( 81.21, 90.11);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.43) -- ( 81.21, 87.35);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.35) -- ( 81.21, 83.43);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.66) -- ( 81.21, 86.58);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.58) -- ( 81.21, 82.66);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.00) -- ( 81.21, 86.93);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.93) -- ( 81.21, 83.00);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.39) -- ( 81.21, 83.31);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.31) -- ( 81.21, 79.39);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.28) -- ( 81.21, 87.20);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.20) -- ( 81.21, 83.28);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.34) -- ( 81.21, 83.26);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.26) -- ( 81.21, 79.34);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.21) -- ( 81.21, 91.14);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.14) -- ( 81.21, 87.21);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.88) -- ( 81.21, 82.80);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.80) -- ( 81.21, 78.88);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.19) -- ( 81.21, 86.12);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.12) -- ( 81.21, 82.19);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.96) -- ( 81.21, 82.89);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.89) -- ( 81.21, 78.96);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.84) -- ( 81.21, 85.77);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.77) -- ( 81.21, 81.84);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.45) -- ( 81.21, 84.37);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.37) -- ( 81.21, 80.45);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.23) -- ( 81.21, 83.16);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.16) -- ( 81.21, 79.23);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.89) -- ( 81.21, 85.82);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.82) -- ( 81.21, 81.89);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.83) -- ( 81.21, 82.75);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.75) -- ( 81.21, 78.83);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.26) -- ( 81.21, 86.19);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.19) -- ( 81.21, 82.26);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.31) -- ( 81.21, 89.24);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.24) -- ( 81.21, 85.31);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.51) -- ( 81.21, 82.43);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.43) -- ( 81.21, 78.51);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.59) -- ( 81.21, 85.52);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.52) -- ( 81.21, 81.59);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.56) -- ( 81.21, 85.49);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.49) -- ( 81.21, 81.56);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.08) -- ( 81.21, 84.01);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.01) -- ( 81.21, 80.08);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.36) -- ( 81.21, 85.29);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.29) -- ( 81.21, 81.36);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.54) -- ( 81.21, 85.47);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.47) -- ( 81.21, 81.54);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.19) -- ( 81.21, 83.11);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.11) -- ( 81.21, 79.19);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.87) -- ( 81.21, 89.79);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.79) -- ( 81.21, 85.87);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.50) -- ( 81.21, 82.42);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.42) -- ( 81.21, 78.50);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.66) -- ( 81.21, 83.59);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.59) -- ( 81.21, 79.66);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.79) -- ( 81.21, 84.71);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.71) -- ( 81.21, 80.79);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.63) -- ( 81.21, 87.55);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.55) -- ( 81.21, 83.63);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.11) -- ( 81.21, 85.03);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.03) -- ( 81.21, 81.11);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.05) -- ( 81.21, 88.97);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.97) -- ( 81.21, 85.05);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.98) -- ( 81.21, 89.90);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.90) -- ( 81.21, 85.98);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.03) -- ( 81.21, 83.96);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.96) -- ( 81.21, 80.03);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.65) -- ( 81.21, 82.58);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.58) -- ( 81.21, 78.65);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.50) -- ( 81.21, 87.43);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.43) -- ( 81.21, 83.50);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.41) -- ( 81.21, 82.33);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.33) -- ( 81.21, 78.41);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.91) -- ( 81.21, 87.84);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.84) -- ( 81.21, 83.91);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.23) -- ( 81.21, 87.15);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.15) -- ( 81.21, 83.23);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.91) -- ( 81.21, 89.83);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.83) -- ( 81.21, 85.91);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.55) -- ( 81.21, 85.47);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.47) -- ( 81.21, 81.55);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.78) -- ( 81.21, 83.71);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.71) -- ( 81.21, 79.78);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.03) -- ( 81.21, 82.95);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.95) -- ( 81.21, 79.03);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.87) -- ( 81.21, 82.80);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.80) -- ( 81.21, 78.87);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.19) -- ( 81.21, 84.11);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.11) -- ( 81.21, 80.19);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.94) -- ( 81.21, 83.86);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.86) -- ( 81.21, 79.94);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.19) -- ( 81.21, 85.12);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.12) -- ( 81.21, 81.19);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.21) -- ( 81.21, 85.14);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.14) -- ( 81.21, 81.21);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.32) -- ( 81.21, 85.24);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.24) -- ( 81.21, 81.32);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.16) -- ( 81.21, 84.08);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.08) -- ( 81.21, 80.16);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.04) -- ( 81.21, 86.96);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.96) -- ( 81.21, 83.04);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.20) -- ( 81.21, 85.13);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.13) -- ( 81.21, 81.20);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.88) -- ( 81.21, 87.80);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.80) -- ( 81.21, 83.88);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.26) -- ( 81.21, 85.18);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.18) -- ( 81.21, 81.26);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.69) -- ( 81.21, 82.62);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.62) -- ( 81.21, 78.69);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.78) -- ( 81.21, 85.71);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.71) -- ( 81.21, 81.78);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.05) -- ( 81.21, 86.97);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.97) -- ( 81.21, 83.05);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.98) -- ( 81.21, 82.91);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.91) -- ( 81.21, 78.98);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.90) -- ( 81.21, 85.83);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.83) -- ( 81.21, 81.90);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.97) -- ( 81.21, 83.90);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.90) -- ( 81.21, 79.97);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.54) -- ( 81.21, 85.46);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.46) -- ( 81.21, 81.54);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.33) -- ( 81.21, 90.25);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.25) -- ( 81.21, 86.33);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.99) -- ( 81.21, 86.91);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.91) -- ( 81.21, 82.99);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.08) -- ( 81.21, 83.00);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.00) -- ( 81.21, 79.08);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.06) -- ( 81.21, 91.99);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.99) -- ( 81.21, 88.06);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.88) -- ( 81.21, 84.81);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.81) -- ( 81.21, 80.88);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.96) -- ( 81.21, 89.89);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.89) -- ( 81.21, 85.96);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.65) -- ( 81.21, 84.57);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.57) -- ( 81.21, 80.65);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.79) -- ( 81.21, 88.72);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.72) -- ( 81.21, 84.79);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.85) -- ( 81.21, 83.78);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.78) -- ( 81.21, 79.85);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.99) -- ( 81.21, 86.91);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.91) -- ( 81.21, 82.99);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.51) -- ( 81.21, 86.44);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.44) -- ( 81.21, 82.51);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.82) -- ( 81.21, 86.74);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.74) -- ( 81.21, 82.82);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.26) -- ( 81.21, 84.18);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.18) -- ( 81.21, 80.26);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.22) -- ( 81.21, 90.14);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.14) -- ( 81.21, 86.22);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.27) -- ( 81.21, 83.19);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.19) -- ( 81.21, 79.27);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.16) -- ( 81.21, 83.08);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.08) -- ( 81.21, 79.16);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.77) -- ( 81.21, 88.69);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.69) -- ( 81.21, 84.77);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.23) -- ( 81.21, 84.16);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.16) -- ( 81.21, 80.23);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.04) -- ( 81.21, 82.96);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.96) -- ( 81.21, 79.04);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.14) -- ( 81.21, 91.07);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.07) -- ( 81.21, 87.14);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.88) -- ( 81.21, 82.80);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.80) -- ( 81.21, 78.88);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.54) -- ( 81.21, 86.46);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.46) -- ( 81.21, 82.54);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.43) -- ( 81.21, 88.36);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.36) -- ( 81.21, 84.43);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.01) -- ( 81.21, 85.93);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.93) -- ( 81.21, 82.01);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.55) -- ( 81.21, 87.47);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.47) -- ( 81.21, 83.55);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.19) -- ( 81.21, 85.12);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.12) -- ( 81.21, 81.19);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 97.06) -- ( 81.21,100.99);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29,100.99) -- ( 81.21, 97.06);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.13) -- ( 81.21, 90.06);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.06) -- ( 81.21, 86.13);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.28) -- ( 81.21, 86.21);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.21) -- ( 81.21, 82.28);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.75) -- ( 81.21, 88.68);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.68) -- ( 81.21, 84.75);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.14) -- ( 81.21, 90.06);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.06) -- ( 81.21, 86.14);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.28) -- ( 81.21, 83.21);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.21) -- ( 81.21, 79.28);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.35) -- ( 81.21, 85.28);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.28) -- ( 81.21, 81.35);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.95) -- ( 81.21, 83.87);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.87) -- ( 81.21, 79.95);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.73) -- ( 81.21, 84.66);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.66) -- ( 81.21, 80.73);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 92.83) -- ( 81.21, 96.76);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 96.76) -- ( 81.21, 92.83);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.59) -- ( 81.21, 84.52);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.52) -- ( 81.21, 80.59);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.31) -- ( 81.21, 92.24);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 92.24) -- ( 81.21, 88.31);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.07) -- ( 81.21, 84.00);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.00) -- ( 81.21, 80.07);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.24) -- ( 81.21, 89.16);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.16) -- ( 81.21, 85.24);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 95.70) -- ( 81.21, 99.63);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 99.63) -- ( 81.21, 95.70);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.55) -- ( 81.21, 86.47);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.47) -- ( 81.21, 82.55);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.29) -- ( 81.21, 84.21);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.21) -- ( 81.21, 80.29);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.62) -- ( 81.21, 83.55);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.55) -- ( 81.21, 79.62);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.78) -- ( 81.21, 82.70);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.70) -- ( 81.21, 78.78);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.17) -- ( 81.21, 83.10);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.10) -- ( 81.21, 79.17);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.00) -- ( 81.21, 82.92);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.92) -- ( 81.21, 79.00);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.09) -- ( 81.21, 91.01);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.01) -- ( 81.21, 87.09);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.15) -- ( 81.21, 88.08);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.08) -- ( 81.21, 84.15);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.74) -- ( 81.21, 84.66);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.66) -- ( 81.21, 80.74);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.67) -- ( 81.21, 90.59);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.59) -- ( 81.21, 86.67);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.53) -- ( 81.21, 82.45);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.45) -- ( 81.21, 78.53);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.85) -- ( 81.21, 84.77);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.77) -- ( 81.21, 80.85);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.25) -- ( 81.21, 84.18);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.18) -- ( 81.21, 80.25);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 92.97) -- ( 81.21, 96.90);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 96.90) -- ( 81.21, 92.97);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.45) -- ( 81.21, 93.38);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 93.38) -- ( 81.21, 89.45);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.27) -- ( 81.21, 83.19);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.19) -- ( 81.21, 79.27);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.86) -- ( 81.21, 82.79);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.79) -- ( 81.21, 78.86);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.53) -- ( 81.21, 87.45);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.45) -- ( 81.21, 83.53);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.02) -- ( 81.21, 90.94);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.94) -- ( 81.21, 87.02);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.13) -- ( 81.21, 89.06);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.06) -- ( 81.21, 85.13);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.62) -- ( 81.21, 88.55);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.55) -- ( 81.21, 84.62);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 97.62) -- ( 81.21,101.54);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29,101.54) -- ( 81.21, 97.62);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.91) -- ( 81.21, 90.83);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.83) -- ( 81.21, 86.91);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.65) -- ( 81.21, 87.58);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.58) -- ( 81.21, 83.65);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.14) -- ( 81.21, 92.07);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 92.07) -- ( 81.21, 88.14);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.09) -- ( 81.21, 95.02);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 95.02) -- ( 81.21, 91.09);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.39) -- ( 81.21, 82.32);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.32) -- ( 81.21, 78.39);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.95) -- ( 81.21, 85.87);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.87) -- ( 81.21, 81.95);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.34) -- ( 81.21, 86.27);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.27) -- ( 81.21, 82.34);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.97) -- ( 81.21, 85.89);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.89) -- ( 81.21, 81.97);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.45) -- ( 81.21, 92.37);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 92.37) -- ( 81.21, 88.45);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.38) -- ( 81.21, 90.30);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.30) -- ( 81.21, 86.38);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 98.06) -- ( 81.21,101.98);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29,101.98) -- ( 81.21, 98.06);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.07) -- ( 81.21, 84.00);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.00) -- ( 81.21, 80.07);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.75) -- ( 81.21, 84.67);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.67) -- ( 81.21, 80.75);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.06) -- ( 81.21, 82.98);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.98) -- ( 81.21, 79.06);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.07) -- ( 81.21, 83.00);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.00) -- ( 81.21, 79.07);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29,101.47) -- ( 81.21,105.40);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29,105.40) -- ( 81.21,101.47);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29,101.45) -- ( 81.21,105.37);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29,105.37) -- ( 81.21,101.45);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 97.62) -- ( 81.21,101.54);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29,101.54) -- ( 81.21, 97.62);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.30) -- ( 81.21, 95.22);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 95.22) -- ( 81.21, 91.30);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.28) -- ( 81.21, 93.21);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 93.21) -- ( 81.21, 89.28);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.70) -- ( 81.21, 93.63);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 93.63) -- ( 81.21, 89.70);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 95.64) -- ( 81.21, 99.56);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 99.56) -- ( 81.21, 95.64);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.38) -- ( 81.21, 91.31);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.31) -- ( 81.21, 87.38);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.67) -- ( 81.21, 85.60);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.60) -- ( 81.21, 81.67);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.60) -- ( 81.21, 82.53);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.53) -- ( 81.21, 78.60);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.22) -- ( 81.21, 83.14);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.14) -- ( 81.21, 79.22);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.50) -- ( 81.21, 85.43);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.43) -- ( 81.21, 81.50);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.62) -- ( 81.21, 87.54);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.54) -- ( 81.21, 83.62);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.82) -- ( 81.21, 83.74);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.74) -- ( 81.21, 79.82);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.50) -- ( 81.21, 86.42);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.42) -- ( 81.21, 82.50);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.97) -- ( 81.21, 82.90);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.90) -- ( 81.21, 78.97);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.86) -- ( 81.21, 83.79);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.79) -- ( 81.21, 79.86);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.38) -- ( 81.21, 83.30);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.30) -- ( 81.21, 79.38);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.21) -- ( 81.21, 88.13);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.13) -- ( 81.21, 84.21);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.65) -- ( 81.21, 86.57);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.57) -- ( 81.21, 82.65);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.56) -- ( 81.21, 82.48);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.48) -- ( 81.21, 78.56);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.88) -- ( 81.21, 82.80);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.80) -- ( 81.21, 78.88);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.24) -- ( 81.21, 84.17);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.17) -- ( 81.21, 80.24);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.20) -- ( 81.21, 84.12);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.12) -- ( 81.21, 80.20);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.69) -- ( 81.21, 85.62);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.62) -- ( 81.21, 81.69);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.98) -- ( 81.21, 91.91);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.91) -- ( 81.21, 87.98);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.45) -- ( 81.21, 83.37);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.37) -- ( 81.21, 79.45);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.11) -- ( 81.21, 91.03);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.03) -- ( 81.21, 87.11);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 95.98) -- ( 81.21, 99.90);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 99.90) -- ( 81.21, 95.98);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.69) -- ( 81.21, 84.61);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.61) -- ( 81.21, 80.69);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.22) -- ( 81.21, 84.14);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.14) -- ( 81.21, 80.22);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.07) -- ( 81.21, 87.00);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.00) -- ( 81.21, 83.07);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.35) -- ( 81.21, 83.28);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.28) -- ( 81.21, 79.35);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.70) -- ( 81.21, 84.62);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.62) -- ( 81.21, 80.70);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.19) -- ( 81.21, 84.12);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.12) -- ( 81.21, 80.19);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.84) -- ( 81.21, 84.76);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.76) -- ( 81.21, 80.84);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 93.44) -- ( 81.21, 97.37);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 97.37) -- ( 81.21, 93.44);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.39) -- ( 81.21, 82.32);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.32) -- ( 81.21, 78.39);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.63) -- ( 81.21, 86.55);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.55) -- ( 81.21, 82.63);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.52) -- ( 81.21, 82.44);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.44) -- ( 81.21, 78.52);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 79.25, 63.16) -- ( 79.25, 80.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 79.25, 51.75) -- ( 79.25, 36.04);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 68.11, 63.16) --
	( 68.11, 51.75) --
	( 90.39, 51.75) --
	( 90.39, 63.16) --
	( 68.11, 63.16) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 68.11, 57.40) -- ( 90.39, 57.40);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.71, 30.69) rectangle ( 97.08,108.01);
\end{scope}
\begin{scope}
\path[clip] (102.58, 30.69) rectangle (167.95,108.01);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (102.58, 30.69) rectangle (167.95,108.01);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (102.58, 36.29) --
	(167.95, 36.29);

\path[draw=drawColor,line width= 0.3pt,line join=round] (102.58, 62.99) --
	(167.95, 62.99);

\path[draw=drawColor,line width= 0.3pt,line join=round] (102.58, 89.69) --
	(167.95, 89.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (102.58, 49.64) --
	(167.95, 49.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (102.58, 76.34) --
	(167.95, 76.34);

\path[draw=drawColor,line width= 0.6pt,line join=round] (102.58,103.05) --
	(167.95,103.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.84, 30.69) --
	(114.84,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (135.26, 30.69) --
	(135.26,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (155.69, 30.69) --
	(155.69,108.01);
\definecolor{drawColor}{RGB}{51,51,51}

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 72.46) -- (116.80, 76.39);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.39) -- (116.80, 72.46);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 72.15) -- (116.80, 76.07);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.07) -- (116.80, 72.15);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.39) -- (116.80, 80.31);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 80.31) -- (116.80, 76.39);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.62) -- (116.80, 77.55);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.55) -- (116.80, 73.62);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.92) -- (116.80, 77.85);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.85) -- (116.80, 73.92);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 71.37) -- (116.80, 75.29);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.29) -- (116.80, 71.37);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.50) -- (116.80, 79.43);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 79.43) -- (116.80, 75.50);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 72.53) -- (116.80, 76.45);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.45) -- (116.80, 72.53);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 71.61) -- (116.80, 75.53);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.53) -- (116.80, 71.61);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 71.50) -- (116.80, 75.42);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.42) -- (116.80, 71.50);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.66) -- (116.80, 77.58);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.58) -- (116.80, 73.66);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 72.62) -- (116.80, 76.55);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.55) -- (116.80, 72.62);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 72.05) -- (116.80, 75.98);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.98) -- (116.80, 72.05);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.89) -- (116.80, 79.81);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 79.81) -- (116.80, 75.89);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.08) -- (116.80, 77.01);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.01) -- (116.80, 73.08);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 71.47) -- (116.80, 75.40);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.40) -- (116.80, 71.47);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 72.42) -- (116.80, 76.34);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.34) -- (116.80, 72.42);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.83) -- (116.80, 81.75);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 81.75) -- (116.80, 77.83);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.04) -- (116.80, 76.96);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.96) -- (116.80, 73.04);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.17) -- (116.80, 77.09);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.09) -- (116.80, 73.17);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 72.88) -- (116.80, 76.80);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.80) -- (116.80, 72.88);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.74) -- (116.80, 77.67);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.67) -- (116.80, 73.74);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.35) -- (116.80, 77.28);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.28) -- (116.80, 73.35);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.52) -- (116.80, 77.45);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.45) -- (116.80, 73.52);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 72.78) -- (116.80, 76.70);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.70) -- (116.80, 72.78);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.82) -- (116.80, 77.75);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.75) -- (116.80, 73.82);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.48) -- (116.80, 77.40);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.40) -- (116.80, 73.48);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.85) -- (116.80, 77.78);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.78) -- (116.80, 73.85);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 72.02) -- (116.80, 75.95);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.95) -- (116.80, 72.02);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 74.08) -- (116.80, 78.00);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.00) -- (116.80, 74.08);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.24) -- (116.80, 77.16);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.16) -- (116.80, 73.24);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.28) -- (116.80, 77.21);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.21) -- (116.80, 73.28);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.03) -- (116.80, 76.95);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.95) -- (116.80, 73.03);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.08) -- (116.80, 81.00);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 81.00) -- (116.80, 77.08);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 71.55) -- (116.80, 75.47);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.47) -- (116.80, 71.55);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 74.72) -- (116.80, 78.65);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.65) -- (116.80, 74.72);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 80.73) -- (116.80, 84.66);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 84.66) -- (116.80, 80.73);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 71.57) -- (116.80, 75.49);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.49) -- (116.80, 71.57);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 85.24) -- (116.80, 89.16);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 89.16) -- (116.80, 85.24);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 71.68) -- (116.80, 75.60);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.60) -- (116.80, 71.68);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 74.38) -- (116.80, 78.31);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.31) -- (116.80, 74.38);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 74.54) -- (116.80, 78.46);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.46) -- (116.80, 74.54);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.71) -- (116.80, 77.63);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.63) -- (116.80, 73.71);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 79.27) -- (116.80, 83.19);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 83.19) -- (116.80, 79.27);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 72.00) -- (116.80, 75.93);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.93) -- (116.80, 72.00);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.60) -- (116.80, 81.53);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 81.53) -- (116.80, 77.60);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 85.13) -- (116.80, 89.06);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 89.06) -- (116.80, 85.13);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 72.58) -- (116.80, 76.50);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.50) -- (116.80, 72.58);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.33) -- (116.80, 77.25);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.25) -- (116.80, 73.33);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 81.97) -- (116.80, 85.89);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 85.89) -- (116.80, 81.97);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 71.96) -- (116.80, 75.89);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.89) -- (116.80, 71.96);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.11) -- (116.80, 81.03);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 81.03) -- (116.80, 77.11);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 97.62) -- (116.80,101.54);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87,101.54) -- (116.80, 97.62);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 98.71) -- (116.80,102.64);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87,102.64) -- (116.80, 98.71);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 95.64) -- (116.80, 99.56);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 99.56) -- (116.80, 95.64);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.08) -- (116.80, 80.01);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 80.01) -- (116.80, 76.08);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 74.91) -- (116.80, 78.83);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.83) -- (116.80, 74.91);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 72.31) -- (116.80, 76.23);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.23) -- (116.80, 72.31);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 72.31) -- (116.80, 76.23);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.23) -- (116.80, 72.31);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 72.63) -- (116.80, 76.56);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.56) -- (116.80, 72.63);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 72.25) -- (116.80, 76.17);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.17) -- (116.80, 72.25);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.54) -- (116.80, 77.47);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.47) -- (116.80, 73.54);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 80.20) -- (116.80, 84.12);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 84.12) -- (116.80, 80.20);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.14) -- (116.80, 82.06);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 82.06) -- (116.80, 78.14);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 81.69) -- (116.80, 85.62);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 85.62) -- (116.80, 81.69);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.79) -- (116.80, 80.71);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 80.71) -- (116.80, 76.79);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.97) -- (116.80, 81.89);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 81.89) -- (116.80, 77.97);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 87.11) -- (116.80, 91.03);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 91.03) -- (116.80, 87.11);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 95.98) -- (116.80, 99.90);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 99.90) -- (116.80, 95.98);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 80.22) -- (116.80, 84.14);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 84.14) -- (116.80, 80.22);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 71.47) -- (116.80, 75.39);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.39) -- (116.80, 71.47);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 87.23) -- (116.80, 91.16);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 91.16) -- (116.80, 87.23);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 80.84) -- (116.80, 84.76);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 84.76) -- (116.80, 80.84);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.05) -- (116.80, 79.97);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 79.97) -- (116.80, 76.05);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 72.00) -- (116.80, 75.92);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.92) -- (116.80, 72.00);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.84, 58.20) -- (114.84, 73.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.84, 48.16) -- (114.84, 34.20);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (107.18, 58.20) --
	(107.18, 48.16) --
	(122.50, 48.16) --
	(122.50, 58.20) --
	(107.18, 58.20) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (107.18, 53.11) -- (122.50, 53.11);
\definecolor{drawColor}{RGB}{51,51,51}

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 79.03) -- (137.23, 82.96);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.96) -- (137.23, 79.03);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.81) -- (137.23, 86.73);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 86.73) -- (137.23, 82.81);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.76) -- (137.23, 84.68);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.68) -- (137.23, 80.76);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.46) -- (137.23, 84.39);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.39) -- (137.23, 80.46);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 77.23) -- (137.23, 81.16);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.16) -- (137.23, 77.23);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 76.48) -- (137.23, 80.40);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.40) -- (137.23, 76.48);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 76.86) -- (137.23, 80.78);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.78) -- (137.23, 76.86);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 77.23) -- (137.23, 81.15);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.15) -- (137.23, 77.23);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 78.16) -- (137.23, 82.09);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.09) -- (137.23, 78.16);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 77.85) -- (137.23, 81.78);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.78) -- (137.23, 77.85);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.66) -- (137.23, 86.58);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 86.58) -- (137.23, 82.66);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 77.03) -- (137.23, 80.95);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.95) -- (137.23, 77.03);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 79.34) -- (137.23, 83.26);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.26) -- (137.23, 79.34);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 79.23) -- (137.23, 83.16);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.16) -- (137.23, 79.23);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 78.51) -- (137.23, 82.43);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.43) -- (137.23, 78.51);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 76.55) -- (137.23, 80.48);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.48) -- (137.23, 76.55);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 77.98) -- (137.23, 81.91);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.91) -- (137.23, 77.98);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 78.50) -- (137.23, 82.42);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.42) -- (137.23, 78.50);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.79) -- (137.23, 84.71);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.71) -- (137.23, 80.79);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 77.79) -- (137.23, 81.71);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.71) -- (137.23, 77.79);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 78.41) -- (137.23, 82.33);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.33) -- (137.23, 78.41);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.55) -- (137.23, 85.47);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 85.47) -- (137.23, 81.55);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 77.37) -- (137.23, 81.29);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.29) -- (137.23, 77.37);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.19) -- (137.23, 85.12);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 85.12) -- (137.23, 81.19);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.32) -- (137.23, 85.24);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 85.24) -- (137.23, 81.32);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.04) -- (137.23, 86.96);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 86.96) -- (137.23, 83.04);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.20) -- (137.23, 85.13);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 85.13) -- (137.23, 81.20);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.26) -- (137.23, 85.18);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 85.18) -- (137.23, 81.26);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 77.66) -- (137.23, 81.58);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.58) -- (137.23, 77.66);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.90) -- (137.23, 85.83);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 85.83) -- (137.23, 81.90);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 79.97) -- (137.23, 83.90);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.90) -- (137.23, 79.97);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 77.88) -- (137.23, 81.81);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.81) -- (137.23, 77.88);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 76.54) -- (137.23, 80.46);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.46) -- (137.23, 76.54);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 78.21) -- (137.23, 82.14);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.14) -- (137.23, 78.21);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.88) -- (137.23, 84.81);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.81) -- (137.23, 80.88);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.65) -- (137.23, 84.57);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.57) -- (137.23, 80.65);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.82) -- (137.23, 86.74);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 86.74) -- (137.23, 82.82);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 78.07) -- (137.23, 81.99);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.99) -- (137.23, 78.07);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 79.16) -- (137.23, 83.08);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.08) -- (137.23, 79.16);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 78.16) -- (137.23, 82.08);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.08) -- (137.23, 78.16);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.23) -- (137.23, 84.16);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.16) -- (137.23, 80.23);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 79.04) -- (137.23, 82.96);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.96) -- (137.23, 79.04);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 78.88) -- (137.23, 82.80);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.80) -- (137.23, 78.88);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 76.59) -- (137.23, 80.51);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.51) -- (137.23, 76.59);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 79.28) -- (137.23, 83.21);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.21) -- (137.23, 79.28);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 78.28) -- (137.23, 82.20);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.20) -- (137.23, 78.28);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 77.75) -- (137.23, 81.68);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.68) -- (137.23, 77.75);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 76.82) -- (137.23, 80.74);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.74) -- (137.23, 76.82);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 95.70) -- (137.23, 99.63);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 99.63) -- (137.23, 95.70);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.74) -- (137.23, 84.66);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.66) -- (137.23, 80.74);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 78.53) -- (137.23, 82.45);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.45) -- (137.23, 78.53);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.25) -- (137.23, 84.18);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.18) -- (137.23, 80.25);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 92.97) -- (137.23, 96.90);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 96.90) -- (137.23, 92.97);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 89.45) -- (137.23, 93.38);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 93.38) -- (137.23, 89.45);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 87.02) -- (137.23, 90.94);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 90.94) -- (137.23, 87.02);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.62) -- (137.23, 88.55);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 88.55) -- (137.23, 84.62);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 86.91) -- (137.23, 90.83);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 90.83) -- (137.23, 86.91);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.65) -- (137.23, 87.58);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 87.58) -- (137.23, 83.65);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 88.14) -- (137.23, 92.07);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 92.07) -- (137.23, 88.14);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 78.39) -- (137.23, 82.32);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.32) -- (137.23, 78.39);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.95) -- (137.23, 85.87);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 85.87) -- (137.23, 81.95);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 88.45) -- (137.23, 92.37);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 92.37) -- (137.23, 88.45);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 86.38) -- (137.23, 90.30);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 90.30) -- (137.23, 86.38);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.75) -- (137.23, 84.67);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.67) -- (137.23, 80.75);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.65) -- (137.23, 86.57);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 86.57) -- (137.23, 82.65);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.69) -- (137.23, 84.61);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.61) -- (137.23, 80.69);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 77.07) -- (137.23, 80.99);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.99) -- (137.23, 77.07);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.07) -- (137.23, 87.00);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 87.00) -- (137.23, 83.07);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.61) -- (137.23, 84.53);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.53) -- (137.23, 80.61);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.19) -- (137.23, 84.12);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.12) -- (137.23, 80.19);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 78.39) -- (137.23, 82.32);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.32) -- (137.23, 78.39);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.63) -- (137.23, 86.55);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 86.55) -- (137.23, 82.63);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (135.26, 61.60) -- (135.26, 78.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (135.26, 50.39) -- (135.26, 35.20);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (127.60, 61.60) --
	(127.60, 50.39) --
	(142.92, 50.39) --
	(142.92, 61.60) --
	(127.60, 61.60) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (127.60, 56.00) -- (142.92, 56.00);
\definecolor{drawColor}{RGB}{51,51,51}

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 81.78) -- (157.65, 85.71);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.71) -- (157.65, 81.78);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 82.35) -- (157.65, 86.27);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.27) -- (157.65, 82.35);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.59) -- (157.65, 91.52);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.52) -- (157.65, 87.59);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 80.62) -- (157.65, 84.55);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.55) -- (157.65, 80.62);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 83.17) -- (157.65, 87.09);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.09) -- (157.65, 83.17);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 80.47) -- (157.65, 84.39);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.39) -- (157.65, 80.47);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.88) -- (157.65, 90.81);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.81) -- (157.65, 86.88);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.54) -- (157.65, 88.47);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.47) -- (157.65, 84.54);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.09) -- (157.65, 91.01);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.01) -- (157.65, 87.09);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 82.58) -- (157.65, 86.51);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.51) -- (157.65, 82.58);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.17) -- (157.65, 90.09);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.09) -- (157.65, 86.17);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.00) -- (157.65, 89.93);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.93) -- (157.65, 86.00);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 81.62) -- (157.65, 85.54);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.54) -- (157.65, 81.62);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.72) -- (157.65, 93.64);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 93.64) -- (157.65, 89.72);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.29) -- (157.65, 88.21);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.21) -- (157.65, 84.29);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 83.16) -- (157.65, 87.08);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.08) -- (157.65, 83.16);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 80.29) -- (157.65, 84.22);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.22) -- (157.65, 80.29);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.11) -- (157.65, 94.04);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 94.04) -- (157.65, 90.11);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 83.43) -- (157.65, 87.35);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.35) -- (157.65, 83.43);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 83.00) -- (157.65, 86.93);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.93) -- (157.65, 83.00);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 83.28) -- (157.65, 87.20);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.20) -- (157.65, 83.28);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.21) -- (157.65, 91.14);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.14) -- (157.65, 87.21);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 82.19) -- (157.65, 86.12);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.12) -- (157.65, 82.19);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 81.84) -- (157.65, 85.77);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.77) -- (157.65, 81.84);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 80.45) -- (157.65, 84.37);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.37) -- (157.65, 80.45);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 81.89) -- (157.65, 85.82);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.82) -- (157.65, 81.89);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 82.26) -- (157.65, 86.19);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.19) -- (157.65, 82.26);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.31) -- (157.65, 89.24);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.24) -- (157.65, 85.31);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 81.59) -- (157.65, 85.52);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.52) -- (157.65, 81.59);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 81.56) -- (157.65, 85.49);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.49) -- (157.65, 81.56);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 81.36) -- (157.65, 85.29);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.29) -- (157.65, 81.36);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 81.54) -- (157.65, 85.47);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.47) -- (157.65, 81.54);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.87) -- (157.65, 89.79);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.79) -- (157.65, 85.87);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 83.63) -- (157.65, 87.55);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.55) -- (157.65, 83.63);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 81.11) -- (157.65, 85.03);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.03) -- (157.65, 81.11);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.05) -- (157.65, 88.97);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.97) -- (157.65, 85.05);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.98) -- (157.65, 89.90);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.90) -- (157.65, 85.98);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 83.50) -- (157.65, 87.43);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.43) -- (157.65, 83.50);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 83.91) -- (157.65, 87.84);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.84) -- (157.65, 83.91);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 83.23) -- (157.65, 87.15);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.15) -- (157.65, 83.23);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.91) -- (157.65, 89.83);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.83) -- (157.65, 85.91);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 80.19) -- (157.65, 84.11);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.11) -- (157.65, 80.19);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 81.21) -- (157.65, 85.14);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.14) -- (157.65, 81.21);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 83.88) -- (157.65, 87.80);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.80) -- (157.65, 83.88);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 81.78) -- (157.65, 85.71);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.71) -- (157.65, 81.78);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 83.05) -- (157.65, 86.97);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.97) -- (157.65, 83.05);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 81.54) -- (157.65, 85.46);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.46) -- (157.65, 81.54);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.33) -- (157.65, 90.25);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.25) -- (157.65, 86.33);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 82.99) -- (157.65, 86.91);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.91) -- (157.65, 82.99);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.06) -- (157.65, 91.99);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.99) -- (157.65, 88.06);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.96) -- (157.65, 89.89);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.89) -- (157.65, 85.96);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.79) -- (157.65, 88.72);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.72) -- (157.65, 84.79);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 82.99) -- (157.65, 86.91);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.91) -- (157.65, 82.99);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 82.51) -- (157.65, 86.44);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.44) -- (157.65, 82.51);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 80.26) -- (157.65, 84.18);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.18) -- (157.65, 80.26);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.22) -- (157.65, 90.14);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.14) -- (157.65, 86.22);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.77) -- (157.65, 88.69);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.69) -- (157.65, 84.77);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.14) -- (157.65, 91.07);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.07) -- (157.65, 87.14);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 82.54) -- (157.65, 86.46);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.46) -- (157.65, 82.54);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.43) -- (157.65, 88.36);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.36) -- (157.65, 84.43);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 82.01) -- (157.65, 85.93);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.93) -- (157.65, 82.01);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 83.55) -- (157.65, 87.47);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.47) -- (157.65, 83.55);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 81.19) -- (157.65, 85.12);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.12) -- (157.65, 81.19);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 97.06) -- (157.65,100.99);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,100.99) -- (157.65, 97.06);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.13) -- (157.65, 90.06);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.06) -- (157.65, 86.13);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 82.28) -- (157.65, 86.21);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.21) -- (157.65, 82.28);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.75) -- (157.65, 88.68);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.68) -- (157.65, 84.75);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.14) -- (157.65, 90.06);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.06) -- (157.65, 86.14);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 81.35) -- (157.65, 85.28);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.28) -- (157.65, 81.35);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 92.83) -- (157.65, 96.76);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 96.76) -- (157.65, 92.83);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 80.59) -- (157.65, 84.52);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.52) -- (157.65, 80.59);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.31) -- (157.65, 92.24);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 92.24) -- (157.65, 88.31);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 82.55) -- (157.65, 86.47);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.47) -- (157.65, 82.55);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 80.29) -- (157.65, 84.21);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.21) -- (157.65, 80.29);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.09) -- (157.65, 91.01);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.01) -- (157.65, 87.09);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.15) -- (157.65, 88.08);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.08) -- (157.65, 84.15);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.67) -- (157.65, 90.59);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.59) -- (157.65, 86.67);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 80.85) -- (157.65, 84.77);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.77) -- (157.65, 80.85);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 83.53) -- (157.65, 87.45);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.45) -- (157.65, 83.53);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 97.62) -- (157.65,101.54);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,101.54) -- (157.65, 97.62);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.09) -- (157.65, 95.02);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 95.02) -- (157.65, 91.09);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 82.34) -- (157.65, 86.27);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.27) -- (157.65, 82.34);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 98.06) -- (157.65,101.98);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,101.98) -- (157.65, 98.06);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,101.49) -- (157.65,105.41);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,105.41) -- (157.65,101.49);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,102.54) -- (157.65,106.46);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,106.46) -- (157.65,102.54);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,101.45) -- (157.65,105.38);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,105.38) -- (157.65,101.45);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,101.49) -- (157.65,105.41);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,105.41) -- (157.65,101.49);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,101.47) -- (157.65,105.40);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,105.40) -- (157.65,101.47);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,101.45) -- (157.65,105.37);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,105.37) -- (157.65,101.45);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.30) -- (157.65, 95.22);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 95.22) -- (157.65, 91.30);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.28) -- (157.65, 93.21);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 93.21) -- (157.65, 89.28);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.70) -- (157.65, 93.63);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 93.63) -- (157.65, 89.70);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.70) -- (157.65, 89.62);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.62) -- (157.65, 85.70);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.38) -- (157.65, 91.31);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.31) -- (157.65, 87.38);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 81.67) -- (157.65, 85.60);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.60) -- (157.65, 81.67);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 81.50) -- (157.65, 85.43);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.43) -- (157.65, 81.50);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 83.62) -- (157.65, 87.54);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.54) -- (157.65, 83.62);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 82.50) -- (157.65, 86.42);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.42) -- (157.65, 82.50);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.21) -- (157.65, 88.13);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.13) -- (157.65, 84.21);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 80.24) -- (157.65, 84.17);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.17) -- (157.65, 80.24);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.98) -- (157.65, 91.91);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.91) -- (157.65, 87.98);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 80.70) -- (157.65, 84.62);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.62) -- (157.65, 80.70);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 93.44) -- (157.65, 97.37);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 97.37) -- (157.65, 93.44);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (155.69, 64.76) -- (155.69, 82.12);

\path[draw=drawColor,line width= 0.6pt,line join=round] (155.69, 53.18) -- (155.69, 39.70);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (148.03, 64.76) --
	(148.03, 53.18) --
	(163.35, 53.18) --
	(163.35, 64.76) --
	(148.03, 64.76) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (148.03, 58.96) -- (163.35, 58.96);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (102.58, 30.69) rectangle (167.95,108.01);
\end{scope}
\begin{scope}
\path[clip] ( 31.71,108.01) rectangle ( 97.08,124.59);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,108.01) rectangle ( 97.08,124.59);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 64.40,113.27) {Maximum arity};
\end{scope}
\begin{scope}
\path[clip] (102.58,108.01) rectangle (167.95,124.59);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (102.58,108.01) rectangle (167.95,124.59);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (135.26,113.27) {Probabilistic};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (173.45,130.09);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 49.54, 27.94) --
	( 49.54, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 79.25, 27.94) --
	( 79.25, 30.69);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (173.45,130.09);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 49.54, 19.68) {2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 79.25, 19.68) {3};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (173.45,130.09);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.84, 27.94) --
	(114.84, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (135.26, 27.94) --
	(135.26, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (155.69, 27.94) --
	(155.69, 30.69);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (173.45,130.09);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (114.84, 19.68) {0.25};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (135.26, 19.68) {0.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (155.69, 19.68) {0.75};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (173.45,130.09);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76, 46.61) {20};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76, 73.31) {40};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76,100.01) {60};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (173.45,130.09);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96, 49.64) --
	( 31.71, 49.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96, 76.34) --
	( 31.71, 76.34);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,103.05) --
	( 31.71,103.05);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (173.45,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08, 69.35) {Inference time (s)};
\end{scope}
\end{tikzpicture}

### 2020-05-11 text/paper2/impact.tex
Some new plots

@@
-% Created by tikzDevice version 0.12.3 on 2020-01-25 19:17:02
+% Created by tikzDevice version 0.12.3 on 2020-05-11 12:44:46
 % !TEX encoding = UTF-8 Unicode
@@
 \definecolor{fillColor}{RGB}{255,255,255}
-\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (216.81,176.16);
+\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (173.45,130.09);
 \begin{scope}
-\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
+\path[clip] (  0.00,  0.00) rectangle (173.45,130.09);
+\definecolor{drawColor}{RGB}{255,255,255}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (173.45,130.09);
+\end{scope}
+\begin{scope}
+\path[clip] ( 40.51, 30.69) rectangle (167.95,124.59);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 40.51, 30.69) rectangle (167.95,124.59);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] ( 25.78, 51.08) --
-	(213.31, 51.08);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51, 50.03) --
+	(167.95, 50.03);
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] ( 25.78,102.07) --
-	(213.31,102.07);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51, 81.30) --
+	(167.95, 81.30);
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] ( 25.78,153.07) --
-	(213.31,153.07);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51,112.57) --
+	(167.95,112.57);
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] ( 59.96, 19.53) --
-	( 59.96,172.66);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 63.74, 30.69) --
+	( 63.74,124.59);
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] (111.28, 19.53) --
-	(111.28,172.66);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 98.62, 30.69) --
+	( 98.62,124.59);
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] (162.60, 19.53) --
-	(162.60,172.66);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (133.49, 30.69) --
+	(133.49,124.59);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 25.78, 25.58) --
-	(213.31, 25.58);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.51, 34.40) --
+	(167.95, 34.40);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 25.78, 76.58) --
-	(213.31, 76.58);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.51, 65.67) --
+	(167.95, 65.67);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 25.78,127.57) --
-	(213.31,127.57);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.51, 96.94) --
+	(167.95, 96.94);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 34.30, 19.53) --
-	( 34.30,172.66);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.30, 30.69) --
+	( 46.30,124.59);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] ( 85.62, 19.53) --
-	( 85.62,172.66);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.18, 30.69) --
+	( 81.18,124.59);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] (136.94, 19.53) --
-	(136.94,172.66);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (116.05, 30.69) --
+	(116.05,124.59);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round] (188.26, 19.53) --
-	(188.26,172.66);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (150.93, 30.69) --
+	(150.93,124.59);
 \definecolor{drawColor}{RGB}{27,158,119}
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 34.30, 26.49) --
-	( 85.62, 27.97) --
-	(136.94, 34.12) --
-	(188.26, 77.20);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.30, 34.95) --
+	( 81.18, 35.86) --
+	(116.05, 39.64) --
+	(150.93, 66.05);
 \definecolor{drawColor}{RGB}{217,95,2}
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 34.30, 58.87) --
-	( 85.62, 62.68) --
-	(115.64, 68.55) --
-	(136.94, 72.47);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 46.30, 54.81) --
+	( 81.18, 57.14) --
+	(101.58, 60.74) --
+	(116.05, 63.15);
 \definecolor{drawColor}{RGB}{117,112,179}
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 34.30, 60.44) --
-	( 85.62, 64.58) --
-	(136.94, 66.81) --
-	(188.26, 70.73);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 46.30, 55.77) --
+	( 81.18, 58.31) --
+	(116.05, 59.68) --
+	(150.93, 62.08);
 \definecolor{drawColor}{RGB}{231,41,138}
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 34.30, 62.87) --
-	( 85.62, 64.62) --
-	(136.94, 67.25) --
-	(188.26, 67.83);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 46.30, 57.27) --
+	( 81.18, 58.33) --
+	(116.05, 59.95) --
+	(150.93, 60.30);
 \definecolor{drawColor}{RGB}{102,166,30}
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 34.30, 58.10) --
-	( 85.62, 59.23) --
-	(136.94, 65.57) --
-	(188.26, 79.66);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round] ( 46.30, 54.34) --
+	( 81.18, 55.03) --
+	(116.05, 58.92) --
+	(150.93, 67.56);
 \definecolor{drawColor}{RGB}{230,171,2}
 
-\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,line join=round] ( 34.30, 30.36) --
-	( 85.62, 30.94) --
-	(136.94, 35.55) --
-	(188.26,165.70);
-\definecolor{fillColor}{RGB}{27,158,119}
-
-\path[fill=fillColor,fill opacity=0.75] ( 31.81, 23.99) --
-	( 36.80, 23.99) --
-	( 36.80, 28.99) --
-	( 31.81, 28.99) --
-	cycle;
-
-\path[fill=fillColor,fill opacity=0.75] ( 83.13, 25.47) --
-	( 88.12, 25.47) --
-	( 88.12, 30.46) --
-	( 83.13, 30.46) --
-	cycle;
-
-\path[fill=fillColor,fill opacity=0.75] (134.45, 31.63) --
-	(139.44, 31.63) --
-	(139.44, 36.62) --
-	(134.45, 36.62) --
-	cycle;
-
-\path[fill=fillColor,fill opacity=0.75] (185.77, 74.70) --
-	(190.76, 74.70) --
-	(190.76, 79.69) --
-	(185.77, 79.69) --
-	cycle;
-\definecolor{fillColor}{RGB}{217,95,2}
-
-\path[fill=fillColor,fill opacity=0.75] ( 34.30, 58.87) circle (  2.50);
-
-\path[fill=fillColor,fill opacity=0.75] ( 85.62, 62.68) circle (  2.50);
-
-\path[fill=fillColor,fill opacity=0.75] (115.64, 68.55) circle (  2.50);
-
-\path[fill=fillColor,fill opacity=0.75] (136.94, 72.47) circle (  2.50);
-\definecolor{fillColor}{RGB}{117,112,179}
-
-\path[fill=fillColor,fill opacity=0.75] ( 34.30, 64.32) --
-	( 37.67, 58.50) --
-	( 30.94, 58.50) --
-	cycle;
-
-\path[fill=fillColor,fill opacity=0.75] ( 85.62, 68.46) --
-	( 88.99, 62.64) --
-	( 82.26, 62.64) --
-	cycle;
-
-\path[fill=fillColor,fill opacity=0.75] (136.94, 70.70) --
-	(140.31, 64.87) --
-	(133.58, 64.87) --
-	cycle;
-
-\path[fill=fillColor,fill opacity=0.75] (188.26, 74.62) --
-	(191.63, 68.79) --
-	(184.90, 68.79) --
-	cycle;
-\definecolor{fillColor}{RGB}{231,41,138}
-
-\path[fill=fillColor,fill opacity=0.75] ( 31.81, 62.87) --
-	( 34.30, 65.37) --
-	( 36.80, 62.87) --
-	( 34.30, 60.37) --
-	cycle;
-
-\path[fill=fillColor,fill opacity=0.75] ( 83.13, 64.62) --
-	( 85.62, 67.11) --
-	( 88.12, 64.62) --
-	( 85.62, 62.12) --
-	cycle;
-
-\path[fill=fillColor,fill opacity=0.75] (134.45, 67.25) --
-	(136.94, 69.74) --
-	(139.44, 67.25) --
-	(136.94, 64.75) --
-	cycle;
-
-\path[fill=fillColor,fill opacity=0.75] (185.77, 67.83) --
-	(188.26, 70.32) --
-	(190.76, 67.83) --
-	(188.26, 65.33) --
-	cycle;
-\definecolor{drawColor}{RGB}{102,166,30}
-\definecolor{fillColor}{RGB}{102,166,30}
-
-\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] ( 34.30, 58.10) circle (  2.50);
-
-\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] ( 85.62, 59.23) circle (  2.50);
-
-\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] (136.94, 65.57) circle (  2.50);
-
-\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] (188.26, 79.66) circle (  2.50);
-\definecolor{drawColor}{RGB}{230,171,2}
-\definecolor{fillColor}{RGB}{230,171,2}
-
-\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] ( 34.30, 30.36) circle (  1.67);
-
-\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] ( 85.62, 30.94) circle (  1.67);
-
-\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] (136.94, 35.55) circle (  1.67);
-
-\path[draw=drawColor,draw opacity=0.75,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.75] (188.26,165.70) circle (  1.67);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt on 4pt off 3pt ,line join=round] ( 46.30, 37.33) --
+	( 81.18, 37.69) --
+	(116.05, 40.51) --
+	(150.93,120.32);
 \end{scope}
 \begin{scope}
-\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
+\path[clip] ( 40.51, 30.69) rectangle (167.95,124.59);
 
-\path[] (198.49, 79.80) -- (188.26, 77.20);
+\path[] (158.55, 74.38) -- (150.93, 66.05);
 \definecolor{drawColor}{RGB}{27,158,119}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (200.30, 74.97) --
-	(210.30, 74.97) --
-	(210.23, 74.97) --
-	(210.52, 74.98) --
-	(210.80, 75.04) --
-	(211.07, 75.14) --
-	(211.33, 75.29) --
-	(211.55, 75.47) --
-	(211.74, 75.69) --
-	(211.90, 75.94) --
-	(212.01, 76.20) --
-	(212.08, 76.49) --
-	(212.11, 76.78) --
-	(212.11, 76.78) --
-	(212.11, 83.11) --
-	(212.11, 83.11) --
-	(212.08, 83.40) --
-	(212.01, 83.68) --
-	(211.90, 83.94) --
-	(211.74, 84.19) --
-	(211.55, 84.41) --
-	(211.33, 84.59) --
-	(211.07, 84.74) --
-	(210.80, 84.84) --
-	(210.52, 84.90) --
-	(210.30, 84.91) --
-	(200.30, 84.91) --
-	(200.52, 84.90) --
-	(200.23, 84.91) --
-	(199.94, 84.88) --
-	(199.66, 84.79) --
-	(199.40, 84.67) --
-	(199.16, 84.50) --
-	(198.95, 84.30) --
-	(198.77, 84.07) --
-	(198.64, 83.81) --
-	(198.55, 83.54) --
-	(198.50, 83.25) --
-	(198.49, 83.11) --
-	(198.49, 76.78) --
-	(198.50, 76.92) --
-	(198.50, 76.63) --
-	(198.55, 76.34) --
-	(198.64, 76.07) --
-	(198.77, 75.81) --
-	(198.95, 75.58) --
-	(199.16, 75.38) --
-	(199.40, 75.21) --
-	(199.66, 75.09) --
-	(199.94, 75.01) --
-	(200.23, 74.97) --
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (154.94, 74.38) --
+	(164.94, 74.38) --
+	(164.86, 74.38) --
+	(165.15, 74.39) --
+	(165.44, 74.45) --
+	(165.71, 74.55) --
+	(165.96, 74.70) --
+	(166.19, 74.88) --
+	(166.38, 75.10) --
+	(166.54, 75.34) --
+	(166.65, 75.61) --
+	(166.72, 75.89) --
+	(166.74, 76.18) --
+	(166.74, 76.18) --
+	(166.74, 82.51) --
+	(166.74, 82.51) --
+	(166.72, 82.80) --
+	(166.65, 83.08) --
+	(166.54, 83.35) --
+	(166.38, 83.60) --
+	(166.19, 83.81) --
+	(165.96, 84.00) --
+	(165.71, 84.14) --
+	(165.44, 84.25) --
+	(165.15, 84.30) --
+	(164.94, 84.32) --
+	(154.94, 84.32) --
+	(155.16, 84.30) --
+	(154.87, 84.32) --
+	(154.58, 84.28) --
+	(154.30, 84.20) --
+	(154.04, 84.08) --
+	(153.80, 83.91) --
+	(153.59, 83.71) --
+	(153.41, 83.48) --
+	(153.28, 83.22) --
+	(153.19, 82.94) --
+	(153.14, 82.66) --
+	(153.13, 82.51) --
+	(153.13, 76.18) --
+	(153.14, 76.33) --
+	(153.14, 76.04) --
+	(153.19, 75.75) --
+	(153.28, 75.47) --
+	(153.41, 75.22) --
+	(153.59, 74.98) --
+	(153.80, 74.78) --
+	(154.04, 74.62) --
+	(154.30, 74.49) --
+	(154.58, 74.41) --
+	(154.87, 74.38) --
 	cycle;
@@
 \begin{scope}
-\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
+\path[clip] ( 40.51, 30.69) rectangle (167.95,124.59);
 \definecolor{drawColor}{RGB}{27,158,119}
 
-\node[text=black,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (205.30, 77.98) {$|\mathcal{P}|$};
+\node[text=black,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (159.94, 77.39) {$|\mathcal{P}|$};
 \end{scope}
 \begin{scope}
-\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
-
-\path[] (198.97, 67.74) -- (188.26, 70.73);
+\path[clip] ( 40.51, 30.69) rectangle (167.95,124.59);
 \definecolor{drawColor}{RGB}{117,112,179}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (200.77, 62.58) --
-	(210.30, 62.58) --
-	(210.23, 62.58) --
-	(210.52, 62.59) --
-	(210.80, 62.65) --
-	(211.07, 62.75) --
-	(211.33, 62.90) --
-	(211.55, 63.08) --
-	(211.74, 63.30) --
-	(211.90, 63.54) --
-	(212.01, 63.81) --
-	(212.08, 64.09) --
-	(212.11, 64.38) --
-	(212.11, 64.38) --
-	(212.11, 70.71) --
-	(212.11, 70.71) --
-	(212.08, 71.00) --
-	(212.01, 71.29) --
-	(211.90, 71.55) --
-	(211.74, 71.80) --
-	(211.55, 72.02) --
-	(211.33, 72.20) --
-	(211.07, 72.35) --
-	(210.80, 72.45) --
-	(210.52, 72.51) --
-	(210.30, 72.52) --
-	(200.77, 72.52) --
-	(200.99, 72.51) --
-	(200.70, 72.52) --
-	(200.41, 72.48) --
-	(200.13, 72.40) --
-	(199.87, 72.28) --
-	(199.63, 72.11) --
-	(199.42, 71.91) --
-	(199.25, 71.68) --
-	(199.11, 71.42) --
-	(199.02, 71.15) --
-	(198.97, 70.86) --
-	(198.97, 70.71) --
-	(198.97, 64.38) --
-	(198.97, 64.53) --
-	(198.97, 64.24) --
-	(199.02, 63.95) --
-	(199.11, 63.68) --
-	(199.25, 63.42) --
-	(199.42, 63.19) --
-	(199.63, 62.99) --
-	(199.87, 62.82) --
-	(200.13, 62.70) --
-	(200.41, 62.61) --
-	(200.70, 62.58) --
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (155.41, 62.03) --
+	(164.94, 62.03) --
+	(164.86, 62.03) --
+	(165.15, 62.04) --
+	(165.44, 62.10) --
+	(165.71, 62.20) --
+	(165.96, 62.35) --
+	(166.19, 62.53) --
+	(166.38, 62.75) --
+	(166.53, 63.00) --
+	(166.65, 63.26) --
+	(166.72, 63.55) --
+	(166.74, 63.84) --
+	(166.74, 63.84) --
+	(166.74, 70.16) --
+	(166.74, 70.16) --
+	(166.72, 70.45) --
+	(166.65, 70.74) --
+	(166.53, 71.00) --
+	(166.38, 71.25) --
+	(166.19, 71.47) --
+	(165.96, 71.65) --
+	(165.71, 71.80) --
+	(165.44, 71.90) --
+	(165.15, 71.96) --
+	(164.94, 71.97) --
+	(155.41, 71.97) --
+	(155.63, 71.96) --
+	(155.34, 71.97) --
+	(155.05, 71.93) --
+	(154.77, 71.85) --
+	(154.51, 71.73) --
+	(154.27, 71.56) --
+	(154.06, 71.36) --
+	(153.88, 71.13) --
+	(153.75, 70.87) --
+	(153.65, 70.60) --
+	(153.61, 70.31) --
+	(153.60, 70.16) --
+	(153.60, 63.84) --
+	(153.61, 63.98) --
+	(153.61, 63.69) --
+	(153.65, 63.40) --
+	(153.75, 63.13) --
+	(153.88, 62.87) --
+	(154.06, 62.64) --
+	(154.27, 62.44) --
+	(154.51, 62.27) --
+	(154.77, 62.15) --
+	(155.05, 62.07) --
+	(155.34, 62.03) --
 	cycle;
@@
 \begin{scope}
-\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
+\path[clip] ( 40.51, 30.69) rectangle (167.95,124.59);
 \definecolor{drawColor}{RGB}{117,112,179}
 
-\node[text=black,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (205.54, 65.59) {$|\mathcal{V}|$};
+\node[text=black,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (160.17, 65.04) {$|\mathcal{V}|$};
 \end{scope}
 \begin{scope}
-\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
-
-\path[] (199.59, 56.31) -- (188.26, 67.83);
+\path[clip] ( 40.51, 30.69) rectangle (167.95,124.59);
 \definecolor{drawColor}{RGB}{231,41,138}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (201.40, 50.18) --
-	(210.30, 50.18) --
-	(210.23, 50.18) --
-	(210.52, 50.19) --
-	(210.80, 50.25) --
-	(211.07, 50.35) --
-	(211.33, 50.50) --
-	(211.55, 50.68) --
-	(211.74, 50.90) --
-	(211.90, 51.15) --
-	(212.01, 51.41) --
-	(212.08, 51.70) --
-	(212.11, 51.99) --
-	(212.11, 51.99) --
-	(212.11, 58.31) --
-	(212.11, 58.31) --
-	(212.08, 58.60) --
-	(212.01, 58.89) --
-	(211.90, 59.15) --
-	(211.74, 59.40) --
-	(211.55, 59.62) --
-	(211.33, 59.80) --
-	(211.07, 59.95) --
-	(210.80, 60.05) --
-	(210.52, 60.11) --
-	(210.30, 60.12) --
-	(201.40, 60.12) --
-	(201.62, 60.11) --
-	(201.33, 60.12) --
-	(201.04, 60.08) --
-	(200.76, 60.00) --
-	(200.50, 59.88) --
-	(200.26, 59.71) --
-	(200.05, 59.51) --
-	(199.87, 59.28) --
-	(199.74, 59.02) --
-	(199.65, 58.75) --
-	(199.60, 58.46) --
-	(199.59, 58.31) --
-	(199.59, 51.99) --
-	(199.60, 52.13) --
-	(199.60, 51.84) --
-	(199.65, 51.55) --
-	(199.74, 51.28) --
-	(199.87, 51.02) --
-	(200.05, 50.79) --
-	(200.26, 50.59) --
-	(200.50, 50.42) --
-	(200.76, 50.30) --
-	(201.04, 50.22) --
-	(201.33, 50.18) --
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (156.04, 49.68) --
+	(164.94, 49.68) --
+	(164.86, 49.68) --
+	(165.15, 49.69) --
+	(165.44, 49.75) --
+	(165.71, 49.85) --
+	(165.96, 50.00) --
+	(166.19, 50.18) --
+	(166.38, 50.40) --
+	(166.54, 50.65) --
+	(166.65, 50.91) --
+	(166.72, 51.20) --
+	(166.74, 51.49) --
+	(166.74, 51.49) --
+	(166.74, 57.81) --
+	(166.74, 57.81) --
+	(166.72, 58.10) --
+	(166.65, 58.39) --
+	(166.54, 58.65) --
+	(166.38, 58.90) --
+	(166.19, 59.12) --
+	(165.96, 59.30) --
+	(165.71, 59.45) --
+	(165.44, 59.55) --
+	(165.15, 59.61) --
+	(164.94, 59.62) --
+	(156.04, 59.62) --
+	(156.26, 59.61) --
+	(155.96, 59.62) --
+	(155.68, 59.58) --
+	(155.40, 59.50) --
+	(155.13, 59.38) --
+	(154.89, 59.21) --
+	(154.69, 59.01) --
+	(154.51, 58.78) --
+	(154.38, 58.52) --
+	(154.28, 58.25) --
+	(154.24, 57.96) --
+	(154.23, 57.81) --
+	(154.23, 51.49) --
+	(154.24, 51.63) --
+	(154.24, 51.34) --
+	(154.28, 51.05) --
+	(154.38, 50.78) --
+	(154.51, 50.52) --
+	(154.69, 50.29) --
+	(154.89, 50.09) --
+	(155.13, 49.92) --
+	(155.40, 49.80) --
+	(155.68, 49.72) --
+	(155.96, 49.68) --
 	cycle;
@@
 \begin{scope}
-\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
+\path[clip] ( 40.51, 30.69) rectangle (167.95,124.59);
 \definecolor{drawColor}{RGB}{231,41,138}
 
-\node[text=black,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (205.85, 53.19) {$|\mathcal{C}|$};
+\node[text=black,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (160.49, 52.69) {$|\mathcal{C}|$};
 \end{scope}
 \begin{scope}
-\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
+\path[clip] ( 40.51, 30.69) rectangle (167.95,124.59);
 
-\path[] (189.67, 87.32) -- (188.26, 79.66);
+\path[] (139.49, 80.12) -- (150.93, 67.56);
 \definecolor{drawColor}{RGB}{102,166,30}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (176.31, 87.32) --
-	(203.05, 87.32) --
-	(202.98, 87.32) --
-	(203.27, 87.33) --
-	(203.56, 87.39) --
-	(203.83, 87.49) --
-	(204.08, 87.64) --
-	(204.31, 87.82) --
-	(204.50, 88.04) --
-	(204.65, 88.28) --
-	(204.77, 88.55) --
-	(204.84, 88.83) --
-	(204.86, 89.12) --
-	(204.86, 89.12) --
-	(204.86, 95.45) --
-	(204.86, 95.45) --
-	(204.84, 95.74) --
-	(204.77, 96.03) --
-	(204.65, 96.29) --
-	(204.50, 96.54) --
-	(204.31, 96.76) --
-	(204.08, 96.94) --
-	(203.83, 97.09) --
-	(203.56, 97.19) --
-	(203.27, 97.25) --
-	(203.05, 97.26) --
-	(176.31, 97.26) --
-	(176.53, 97.25) --
-	(176.24, 97.26) --
-	(175.95, 97.22) --
-	(175.67, 97.14) --
-	(175.41, 97.02) --
-	(175.17, 96.85) --
-	(174.96, 96.65) --
-	(174.79, 96.42) --
-	(174.65, 96.16) --
-	(174.56, 95.89) --
-	(174.51, 95.60) --
-	(174.51, 95.45) --
-	(174.51, 89.12) --
-	(174.51, 89.27) --
-	(174.51, 88.98) --
-	(174.56, 88.69) --
-	(174.65, 88.42) --
-	(174.79, 88.16) --
-	(174.96, 87.93) --
-	(175.17, 87.72) --
-	(175.41, 87.56) --
-	(175.67, 87.44) --
-	(175.95, 87.35) --
-	(176.24, 87.32) --
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (122.22, 80.12) --
+	(148.97, 80.12) --
+	(148.89, 80.12) --
+	(149.18, 80.13) --
+	(149.47, 80.19) --
+	(149.74, 80.29) --
+	(149.99, 80.44) --
+	(150.22, 80.62) --
+	(150.41, 80.84) --
+	(150.57, 81.08) --
+	(150.68, 81.35) --
+	(150.75, 81.63) --
+	(150.77, 81.92) --
+	(150.77, 81.92) --
+	(150.77, 88.25) --
+	(150.77, 88.25) --
+	(150.75, 88.54) --
+	(150.68, 88.82) --
+	(150.57, 89.09) --
+	(150.41, 89.34) --
+	(150.22, 89.55) --
+	(149.99, 89.74) --
+	(149.74, 89.88) --
+	(149.47, 89.99) --
+	(149.18, 90.05) --
+	(148.97, 90.06) --
+	(122.22, 90.06) --
+	(122.44, 90.05) --
+	(122.15, 90.06) --
+	(121.86, 90.02) --
+	(121.58, 89.94) --
+	(121.32, 89.82) --
+	(121.08, 89.65) --
+	(120.87, 89.45) --
+	(120.70, 89.22) --
+	(120.56, 88.96) --
+	(120.47, 88.68) --
+	(120.42, 88.40) --
+	(120.42, 88.25) --
+	(120.42, 81.92) --
+	(120.42, 82.07) --
+	(120.42, 81.78) --
+	(120.47, 81.49) --
+	(120.56, 81.21) --
+	(120.70, 80.96) --
+	(120.87, 80.72) --
+	(121.08, 80.52) --
+	(121.32, 80.36) --
+	(121.58, 80.23) --
+	(121.86, 80.15) --
+	(122.15, 80.12) --
 	cycle;
@@
 \begin{scope}
-\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
+\path[clip] ( 40.51, 30.69) rectangle (167.95,124.59);
 \definecolor{drawColor}{RGB}{102,166,30}
 
-\node[text=black,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (189.68, 90.33) {$\mathcal{M}_{\mathcal{C}}-|\mathcal{P}|$};
+\node[text=black,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (135.59, 83.13) {$\mathcal{M}_{\mathcal{C}}-|\mathcal{P}|$};
 \end{scope}
 \begin{scope}
-\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
-
-\path[] (194.64,165.70) -- (188.26,165.70);
+\path[clip] ( 40.51, 30.69) rectangle (167.95,124.59);
 \definecolor{drawColor}{RGB}{230,171,2}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (196.44,160.73) --
-	(210.30,160.73) --
-	(210.23,160.73) --
-	(210.52,160.74) --
-	(210.80,160.80) --
-	(211.07,160.90) --
-	(211.33,161.05) --
-	(211.55,161.23) --
-	(211.74,161.45) --
-	(211.90,161.69) --
-	(212.01,161.96) --
-	(212.08,162.24) --
-	(212.11,162.53) --
-	(212.11,162.53) --
-	(212.11,168.86) --
-	(212.11,168.86) --
-	(212.08,169.15) --
-	(212.01,169.43) --
-	(211.90,169.70) --
-	(211.74,169.95) --
-	(211.55,170.16) --
-	(211.33,170.35) --
-	(211.07,170.49) --
-	(210.80,170.60) --
-	(210.52,170.66) --
-	(210.30,170.67) --
-	(196.44,170.67) --
-	(196.66,170.66) --
-	(196.37,170.67) --
-	(196.08,170.63) --
-	(195.80,170.55) --
-	(195.54,170.43) --
-	(195.30,170.26) --
-	(195.09,170.06) --
-	(194.92,169.83) --
-	(194.78,169.57) --
-	(194.69,169.29) --
-	(194.64,169.01) --
-	(194.64,168.86) --
-	(194.64,162.53) --
-	(194.64,162.68) --
-	(194.64,162.39) --
-	(194.69,162.10) --
-	(194.78,161.82) --
-	(194.92,161.57) --
-	(195.09,161.34) --
-	(195.30,161.13) --
-	(195.54,160.97) --
-	(195.80,160.84) --
-	(196.08,160.76) --
-	(196.37,160.73) --
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (151.08,109.18) --
+	(164.94,109.18) --
+	(164.86,109.18) --
+	(165.15,109.19) --
+	(165.44,109.25) --
+	(165.71,109.36) --
+	(165.96,109.50) --
+	(166.19,109.68) --
+	(166.38,109.90) --
+	(166.54,110.15) --
+	(166.65,110.42) --
+	(166.72,110.70) --
+	(166.74,110.99) --
+	(166.74,110.99) --
+	(166.74,117.32) --
+	(166.74,117.32) --
+	(166.72,117.61) --
+	(166.65,117.89) --
+	(166.54,118.16) --
+	(166.38,118.40) --
+	(166.19,118.62) --
+	(165.96,118.80) --
+	(165.71,118.95) --
+	(165.44,119.05) --
+	(165.15,119.11) --
+	(164.94,119.12) --
+	(151.08,119.12) --
+	(151.30,119.11) --
+	(151.01,119.12) --
+	(150.72,119.09) --
+	(150.44,119.01) --
+	(150.18,118.88) --
+	(149.94,118.72) --
+	(149.73,118.51) --
+	(149.56,118.28) --
+	(149.42,118.02) --
+	(149.33,117.75) --
+	(149.28,117.46) --
+	(149.28,117.32) --
+	(149.28,110.99) --
+	(149.28,111.13) --
+	(149.28,110.84) --
+	(149.33,110.56) --
+	(149.42,110.28) --
+	(149.56,110.02) --
+	(149.73,109.79) --
+	(149.94,109.59) --
+	(150.18,109.42) --
+	(150.44,109.30) --
+	(150.72,109.22) --
+	(151.01,109.18) --
 	cycle;
@@
 \begin{scope}
-\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
+\path[clip] ( 40.51, 30.69) rectangle (167.95,124.59);
 \definecolor{drawColor}{RGB}{230,171,2}
 
-\node[text=black,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (203.37,163.74) {$\mathcal{M}_{\mathcal{N}}$};
+\node[text=black,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (158.01,112.19) {$\mathcal{M}_{\mathcal{N}}$};
 \end{scope}
 \begin{scope}
-\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
+\path[clip] ( 40.51, 30.69) rectangle (167.95,124.59);
 \definecolor{drawColor}{RGB}{217,95,2}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (130.35, 75.50) --
-	(143.54, 75.50) --
-	(143.46, 75.51) --
-	(143.75, 75.52) --
-	(144.04, 75.58) --
-	(144.31, 75.68) --
-	(144.56, 75.82) --
-	(144.79, 76.01) --
-	(144.98, 76.23) --
-	(145.14, 76.47) --
-	(145.25, 76.74) --
-	(145.32, 77.02) --
-	(145.34, 77.31) --
-	(145.34, 77.31) --
-	(145.34, 83.64) --
-	(145.34, 83.64) --
-	(145.32, 83.93) --
-	(145.25, 84.21) --
-	(145.14, 84.48) --
-	(144.98, 84.72) --
-	(144.79, 84.94) --
-	(144.56, 85.13) --
-	(144.31, 85.27) --
-	(144.04, 85.37) --
-	(143.75, 85.43) --
-	(143.54, 85.45) --
-	(130.35, 85.45) --
-	(130.57, 85.43) --
-	(130.28, 85.44) --
-	(129.99, 85.41) --
-	(129.71, 85.33) --
-	(129.45, 85.20) --
-	(129.21, 85.04) --
-	(129.00, 84.84) --
-	(128.83, 84.61) --
-	(128.69, 84.35) --
-	(128.60, 84.07) --
-	(128.55, 83.78) --
-	(128.55, 83.64) --
-	(128.55, 77.31) --
-	(128.55, 77.46) --
-	(128.55, 77.17) --
-	(128.60, 76.88) --
-	(128.69, 76.60) --
-	(128.83, 76.35) --
-	(129.00, 76.11) --
-	(129.21, 75.91) --
-	(129.45, 75.75) --
-	(129.71, 75.62) --
-	(129.99, 75.54) --
-	(130.28, 75.51) --
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (109.46, 66.16) --
+	(122.64, 66.16) --
+	(122.57, 66.16) --
+	(122.86, 66.17) --
+	(123.15, 66.23) --
+	(123.42, 66.33) --
+	(123.67, 66.48) --
+	(123.90, 66.66) --
+	(124.09, 66.88) --
+	(124.24, 67.12) --
+	(124.36, 67.39) --
+	(124.43, 67.67) --
+	(124.45, 67.96) --
+	(124.45, 67.96) --
+	(124.45, 74.29) --
+	(124.45, 74.29) --
+	(124.43, 74.58) --
+	(124.36, 74.86) --
+	(124.24, 75.13) --
+	(124.09, 75.38) --
+	(123.90, 75.60) --
+	(123.67, 75.78) --
+	(123.42, 75.92) --
+	(123.15, 76.03) --
+	(122.86, 76.09) --
+	(122.64, 76.10) --
+	(109.46, 76.10) --
+	(109.68, 76.09) --
+	(109.39, 76.10) --
+	(109.10, 76.06) --
+	(108.82, 75.98) --
+	(108.56, 75.86) --
+	(108.32, 75.69) --
+	(108.11, 75.49) --
+	(107.93, 75.26) --
+	(107.80, 75.00) --
+	(107.71, 74.72) --
+	(107.66, 74.44) --
+	(107.65, 74.29) --
+	(107.65, 67.96) --
+	(107.66, 68.11) --
+	(107.66, 67.82) --
+	(107.71, 67.53) --
+	(107.80, 67.26) --
+	(107.93, 67.00) --
+	(108.11, 66.77) --
+	(108.32, 66.56) --
+	(108.56, 66.40) --
+	(108.82, 66.27) --
+	(109.10, 66.19) --
+	(109.39, 66.16) --
 	cycle;
@@
 \begin{scope}
-\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
+\path[clip] ( 40.51, 30.69) rectangle (167.95,124.59);
 \definecolor{drawColor}{RGB}{217,95,2}
 
-\node[text=black,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (136.94, 78.52) {$\mathcal{M}_{\mathcal{A}}$};
+\node[text=black,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (116.05, 69.17) {$\mathcal{M}_{\mathcal{A}}$};
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 30.69) rectangle (167.95,124.59);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (216.81,176.16);
+\path[clip] (  0.00,  0.00) rectangle (173.45,130.09);
 \definecolor{drawColor}{gray}{0.30}
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.56] at ( 22.63, 23.65) {0};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56, 31.37) {0};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.56] at ( 22.63, 74.65) {2000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56, 62.64) {2000};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.56] at ( 22.63,125.64) {4000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56, 93.91) {4000};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (216.81,176.16);
+\path[clip] (  0.00,  0.00) rectangle (173.45,130.09);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 37.76, 34.40) --
+	( 40.51, 34.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 37.76, 65.67) --
+	( 40.51, 65.67);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 37.76, 96.94) --
+	( 40.51, 96.94);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (173.45,130.09);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.30, 27.94) --
+	( 46.30, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.18, 27.94) --
+	( 81.18, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (116.05, 27.94) --
+	(116.05, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (150.93, 27.94) --
+	(150.93, 30.69);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (173.45,130.09);
 \definecolor{drawColor}{gray}{0.30}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at ( 34.30, 12.52) {1};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 46.30, 19.68) {1};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at ( 85.62, 12.52) {2};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 81.18, 19.68) {2};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at (136.94, 12.52) {4};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (116.05, 19.68) {4};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.56] at (188.26, 12.52) {8};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (150.93, 19.68) {8};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (216.81,176.16);
+\path[clip] (  0.00,  0.00) rectangle (173.45,130.09);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (119.54,  4.86) {Value of each parameter};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (104.23,  7.64) {The value of each parameter};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (216.81,176.16);
+\path[clip] (  0.00,  0.00) rectangle (173.45,130.09);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (  8.32, 96.09) {Mean number of nodes};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08, 77.64) {Mean number of nodes};
 \end{scope}

### 2020-05-11 text/paper2/line_plots.tex
Some new plots

% Created by tikzDevice version 0.12.3 on 2020-05-11 12:49:51
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (346.90,130.09);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (346.90,130.09);
\end{scope}
\begin{scope}
\path[clip] ( 31.71, 30.69) rectangle (145.35,108.01);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 31.71, 30.69) rectangle (145.35,108.01);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 46.03) --
	(145.35, 46.03);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 69.81) --
	(145.35, 69.81);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 93.59) --
	(145.35, 93.59);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 49.66, 30.69) --
	( 49.66,108.01);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 75.52, 30.69) --
	( 75.52,108.01);

\path[draw=drawColor,line width= 0.3pt,line join=round] (101.39, 30.69) --
	(101.39,108.01);

\path[draw=drawColor,line width= 0.3pt,line join=round] (127.25, 30.69) --
	(127.25,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71, 34.14) --
	(145.35, 34.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71, 57.92) --
	(145.35, 57.92);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71, 81.70) --
	(145.35, 81.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71,105.48) --
	(145.35,105.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 36.72, 30.69) --
	( 36.72,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.59, 30.69) --
	( 62.59,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.46, 30.69) --
	( 88.46,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.32, 30.69) --
	(114.32,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (140.19, 30.69) --
	(140.19,108.01);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 36.88, 34.20) --
	( 37.03, 34.26) --
	( 37.34, 34.43) --
	( 37.76, 34.78) --
	( 37.96, 34.89) --
	( 39.21, 35.94) --
	( 44.56, 37.96) --
	( 44.72, 37.05) --
	( 45.03, 37.14) --
	( 47.07, 39.24) --
	( 52.24, 42.35) --
	( 52.40, 40.98) --
	( 52.71, 41.86) --
	( 60.08, 44.75) --
	( 60.39, 44.97) --
	( 67.76, 48.70) --
	( 67.92, 47.86) --
	( 68.07, 47.05) --
	( 68.23, 47.32) --
	( 68.85, 49.64) --
	( 75.75, 52.22) --
	( 83.44, 55.11) --
	( 91.12, 58.33) --
	( 98.80, 75.16) --
	( 99.11, 59.59) --
	( 99.73, 62.82) --
	(130.00, 75.17) --
	(130.62, 78.87) --
	(140.19, 88.26);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 36.88, 34.22) --
	( 37.03, 34.33) --
	( 37.34, 37.18) --
	( 37.76, 37.64) --
	( 37.96, 43.41) --
	( 39.21, 42.20) --
	( 44.56, 57.46) --
	( 44.72, 36.84) --
	( 45.03, 37.68) --
	( 47.07, 40.19) --
	( 52.24, 42.81) --
	( 52.40, 41.77) --
	( 52.71, 40.98) --
	( 60.08, 45.16) --
	( 60.39, 49.30) --
	( 67.76, 47.31) --
	( 67.92, 55.25) --
	( 68.07, 48.59) --
	( 68.23, 46.96) --
	( 68.85, 47.72) --
	( 75.75, 52.99) --
	( 83.44, 57.55) --
	( 91.12, 56.42) --
	( 98.80, 71.23) --
	( 99.11, 62.93) --
	( 99.73, 67.49) --
	(130.00, 79.80) --
	(130.62, 85.06) --
	(140.19, 91.20);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 36.88, 34.22) --
	( 37.03, 34.29) --
	( 37.34, 34.49) --
	( 37.76, 34.88) --
	( 37.96, 35.00) --
	( 39.21, 36.19) --
	( 44.56, 38.30) --
	( 44.72, 37.18) --
	( 45.03, 37.98) --
	( 47.07, 40.27) --
	( 52.24, 44.88) --
	( 52.40, 42.06) --
	( 52.71, 40.35) --
	( 60.08, 45.65) --
	( 60.39, 47.17) --
	( 67.76, 51.25) --
	( 67.92, 52.15) --
	( 68.07, 51.25) --
	( 68.23, 52.79) --
	( 68.85, 51.87) --
	( 75.75, 54.08) --
	( 83.44, 57.97) --
	( 91.12, 61.03) --
	( 98.80, 76.47) --
	( 99.11, 65.20) --
	( 99.73, 59.83) --
	(130.00, 84.23) --
	(130.62, 85.33) --
	(140.19, 99.28);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 36.88, 34.24) --
	( 37.03, 34.31) --
	( 37.34, 34.50) --
	( 37.76, 34.90) --
	( 37.96, 35.05) --
	( 39.21, 36.07) --
	( 44.56, 38.21) --
	( 44.72, 38.54) --
	( 45.03, 38.69) --
	( 47.07, 40.00) --
	( 52.24, 42.70) --
	( 52.40, 41.93) --
	( 52.71, 41.20) --
	( 60.08, 46.14) --
	( 60.39, 46.70) --
	( 67.76, 50.70) --
	( 67.92, 48.30) --
	( 68.07, 50.28) --
	( 68.23, 47.98) --
	( 68.85, 52.07) --
	( 75.75, 55.24) --
	( 83.44, 59.51) --
	( 91.12, 61.81) --
	( 98.80, 82.15) --
	( 99.11, 68.77) --
	( 99.73, 67.98) --
	(130.00, 80.96) --
	(130.62, 80.15) --
	(140.19, 97.28);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round] ( 36.88, 34.20) --
	( 37.03, 34.32) --
	( 37.34, 34.48) --
	( 37.76, 34.84) --
	( 37.96, 34.97) --
	( 39.21, 35.75) --
	( 44.56, 37.97) --
	( 44.72, 36.07) --
	( 45.03, 38.73) --
	( 47.07, 40.22) --
	( 52.24, 44.23) --
	( 52.40, 43.29) --
	( 52.71, 40.97) --
	( 60.08, 46.70) --
	( 60.39, 47.27) --
	( 67.76, 50.76) --
	( 67.92, 53.24) --
	( 68.07, 51.86) --
	( 68.23, 53.84) --
	( 68.85, 51.03) --
	( 75.75, 54.08) --
	( 83.44, 59.44) --
	( 91.12, 63.01) --
	( 98.80, 79.72) --
	( 99.11, 66.18) --
	( 99.73, 66.97) --
	(130.00, 83.43) --
	(130.62, 87.45) --
	(140.19, 98.97);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt on 4pt off 3pt ,line join=round] ( 36.88, 34.23) --
	( 37.03, 34.28) --
	( 37.34, 34.44) --
	( 37.76, 34.80) --
	( 37.96, 34.97) --
	( 39.21, 36.01) --
	( 44.56, 37.80) --
	( 44.72, 36.11) --
	( 45.03, 37.78) --
	( 47.07, 39.38) --
	( 52.24, 43.57) --
	( 52.40, 41.73) --
	( 52.71, 43.60) --
	( 60.08, 45.48) --
	( 60.39, 45.53) --
	( 67.76, 46.06) --
	( 67.92, 48.49) --
	( 68.07, 47.82) --
	( 68.23, 50.65) --
	( 68.85, 47.58) --
	( 75.75, 51.59) --
	( 83.44, 56.58) --
	( 91.12, 55.51) --
	( 98.80, 75.37) --
	( 99.11, 65.39) --
	( 99.73, 59.41) --
	(130.00, 80.88) --
	(130.62, 80.85) --
	(140.19, 91.13);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.71, 30.69) rectangle (145.35,108.01);
\end{scope}
\begin{scope}
\path[clip] (150.85, 30.69) rectangle (264.49,108.01);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (150.85, 30.69) rectangle (264.49,108.01);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (150.85, 46.03) --
	(264.49, 46.03);

\path[draw=drawColor,line width= 0.3pt,line join=round] (150.85, 69.81) --
	(264.49, 69.81);

\path[draw=drawColor,line width= 0.3pt,line join=round] (150.85, 93.59) --
	(264.49, 93.59);

\path[draw=drawColor,line width= 0.3pt,line join=round] (168.93, 30.69) --
	(168.93,108.01);

\path[draw=drawColor,line width= 0.3pt,line join=round] (194.76, 30.69) --
	(194.76,108.01);

\path[draw=drawColor,line width= 0.3pt,line join=round] (220.59, 30.69) --
	(220.59,108.01);

\path[draw=drawColor,line width= 0.3pt,line join=round] (246.42, 30.69) --
	(246.42,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (150.85, 34.14) --
	(264.49, 34.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (150.85, 57.92) --
	(264.49, 57.92);

\path[draw=drawColor,line width= 0.6pt,line join=round] (150.85, 81.70) --
	(264.49, 81.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] (150.85,105.48) --
	(264.49,105.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] (156.02, 30.69) --
	(156.02,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (181.85, 30.69) --
	(181.85,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (207.67, 30.69) --
	(207.67,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (233.50, 30.69) --
	(233.50,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (259.33, 30.69) --
	(259.33,108.01);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (156.02, 82.69) --
	(159.71, 86.86) --
	(167.09, 90.51) --
	(170.78, 84.86) --
	(173.24, 90.95) --
	(185.54, 87.17) --
	(189.23, 82.10) --
	(200.29, 86.31) --
	(211.36, 91.58) --
	(215.05, 82.04) --
	(218.74, 87.00) --
	(224.89, 82.36) --
	(226.12, 81.20) --
	(229.81, 82.46) --
	(233.50, 88.61) --
	(237.19, 93.14) --
	(240.88, 91.31) --
	(251.95, 83.85) --
	(255.64, 86.37) --
	(259.33, 89.25);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (156.02, 91.65) --
	(159.71, 90.13) --
	(167.09, 92.54) --
	(170.78, 85.10) --
	(173.24, 93.89) --
	(185.54, 91.81) --
	(189.23, 87.37) --
	(200.29, 88.45) --
	(211.36, 94.07) --
	(215.05, 85.46) --
	(218.74, 89.07) --
	(224.89, 81.32) --
	(226.12, 84.81) --
	(229.81, 85.30) --
	(233.50, 90.02) --
	(237.19, 93.14) --
	(240.88, 94.41) --
	(251.95, 85.94) --
	(255.64, 89.62) --
	(259.33, 93.56);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (156.02, 96.40) --
	(159.71, 96.07) --
	(167.09,104.50) --
	(170.78, 94.79) --
	(173.24,102.91) --
	(185.54,101.57) --
	(189.23, 94.35) --
	(200.29, 98.68) --
	(211.36,103.55) --
	(215.05, 88.61) --
	(218.74, 97.59) --
	(224.89, 89.92) --
	(226.12, 91.22) --
	(229.81, 87.06) --
	(233.50, 98.75) --
	(237.19,102.58) --
	(240.88,102.50) --
	(251.95, 90.37) --
	(255.64, 96.15) --
	(259.33,100.82);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (156.02, 90.92) --
	(159.71,100.08) --
	(167.09, 97.34) --
	(170.78, 90.63) --
	(173.24, 99.99) --
	(185.54, 96.84) --
	(189.23, 91.32) --
	(200.29, 97.00) --
	(211.36,100.90) --
	(215.05, 88.00) --
	(218.74, 94.45) --
	(224.89, 92.66) --
	(226.12, 90.99) --
	(229.81, 92.19) --
	(233.50, 96.98) --
	(237.19, 99.26) --
	(240.88,100.29) --
	(251.95, 92.01) --
	(255.64, 93.41) --
	(259.33, 99.52);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round] (156.02, 91.47) --
	(159.71, 96.45) --
	(167.09,104.39) --
	(170.78, 90.59) --
	(173.24,102.58) --
	(185.54,100.46) --
	(189.23, 95.50) --
	(200.29, 97.48) --
	(211.36,103.31) --
	(215.05, 90.65) --
	(218.74, 97.90) --
	(224.89, 87.48) --
	(226.12, 91.85) --
	(229.81, 91.08) --
	(233.50, 98.02) --
	(237.19,100.29) --
	(240.88,102.81) --
	(251.95, 90.81) --
	(255.64, 95.58) --
	(259.33,101.07);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt on 4pt off 3pt ,line join=round] (156.02, 81.98) --
	(159.71, 88.47) --
	(167.09, 93.40) --
	(170.78, 85.56) --
	(173.24, 94.47) --
	(185.54, 91.91) --
	(189.23, 83.83) --
	(200.29, 92.87) --
	(211.36, 94.86) --
	(215.05, 82.23) --
	(218.74, 90.48) --
	(224.89, 86.23) --
	(226.12, 82.27) --
	(229.81, 80.81) --
	(233.50, 91.75) --
	(237.19, 92.55) --
	(240.88, 93.28) --
	(251.95, 85.59) --
	(255.64, 87.94) --
	(259.33, 93.81);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (150.85, 30.69) rectangle (264.49,108.01);
\end{scope}
\begin{scope}
\path[clip] ( 31.71,108.01) rectangle (145.35,124.59);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,108.01) rectangle (145.35,124.59);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 88.53,113.27) {The number of facts ($\times 10^3$)};
\end{scope}
\begin{scope}
\path[clip] (150.85,108.01) rectangle (264.49,124.59);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (150.85,108.01) rectangle (264.49,124.59);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (207.67,113.27) {Proportion of independent pairs};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 36.72, 27.94) --
	( 36.72, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.59, 27.94) --
	( 62.59, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.46, 27.94) --
	( 88.46, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.32, 27.94) --
	(114.32, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (140.19, 27.94) --
	(140.19, 30.69);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 36.72, 19.68) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 62.59, 19.68) {25};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 88.46, 19.68) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (114.32, 19.68) {75};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (140.19, 19.68) {100};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (156.02, 27.94) --
	(156.02, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (181.85, 27.94) --
	(181.85, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (207.67, 27.94) --
	(207.67, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (233.50, 27.94) --
	(233.50, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (259.33, 27.94) --
	(259.33, 30.69);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (156.02, 19.68) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (181.85, 19.68) {0.25};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (207.67, 19.68) {0.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (233.50, 19.68) {0.75};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (259.33, 19.68) {1};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76, 31.11) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76, 54.89) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76, 78.67) {20};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76,102.45) {30};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96, 34.14) --
	( 31.71, 34.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96, 57.92) --
	( 31.71, 57.92);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96, 81.70) --
	( 31.71, 81.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,105.48) --
	( 31.71,105.48);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08, 69.35) {Mean inference time (s)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (275.49, 12.88) rectangle (341.40,125.82);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at (280.99,111.67) {Algorithm};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (280.99, 90.65) rectangle (295.45,105.10);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (282.44, 97.88) -- (294.00, 97.88);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (280.99, 76.20) rectangle (295.45, 90.65);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (282.44, 83.42) -- (294.00, 83.42);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (280.99, 61.74) rectangle (295.45, 76.20);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (282.44, 68.97) -- (294.00, 68.97);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (280.99, 47.29) rectangle (295.45, 61.74);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (282.44, 54.52) -- (294.00, 54.52);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (280.99, 32.83) rectangle (295.45, 47.29);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round] (282.44, 40.06) -- (294.00, 40.06);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (280.99, 18.38) rectangle (295.45, 32.83);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt on 4pt off 3pt ,line join=round] (282.44, 25.61) -- (294.00, 25.61);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (300.95, 94.85) {dDNNF};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (300.95, 80.39) {K-Best};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (300.95, 65.94) {NNF};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (300.95, 51.49) {SDD};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (300.95, 37.03) {SDDX};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (300.95, 22.58) {Symbolic};
\end{scope}
\end{tikzpicture}

### 2020-05-11 text/paper2/paper.tex
Move config variables to the Config class
Refactoring
Integrate program generation and fact generation
Gathering experimental data
Some new plots

@@
 
+% TODO: does the restart policy still matter? If so, update the numbers.
 % TODO (for later)
@@
 
+% Description of experimental options
+% Old options: (<600k experiments)
+% number of predicates (2, 4, 8)
+% number of variables (2, 4, 8)
+% max number of nodes (2, 4, 8)
+% max arity (1, 2, 3)
+% number of constants (0)
+% number of additional clauses (0)
+% number of independent pairs (all options)
+% New options:
+% define each predicate: true
+% allow empty bodies: false
+% timeout = 60s (for both?)
+% disable negative cycles
+% probabilities = [0.1, ..., 0.9]
+% generate 10 programs (with restarts, restarting arities and independent pairs)
+% domain size: 100, 200, 400
+% proportion probabilistic: 0.25, 0.5, 0.75
+% number of facts: 1k, 10k, 100k
+% DERIVATIVE: average spots per constant
+% DERIVATIVES: universe size, proportion listed
+% NOTE: The distribution of facts is uniformly distributed across predicates
+% (because it's easier this way)
+% NOTE: number of facts goes up to 75% of the universe
+
 % Empirical tasks:
@@
 % (not just variables). Check if everything works out.
-% 2) motivate either for benchmarking or by comparing parameter learning with
-% ProbFOIL
+% 2) motivate either for benchmarking or by comparing parameter learning with ProbFOIL
+% 3) create a constraint for groundedness (see the ProbLog FAQ)
 % New things I could talk about:
@@
   \centering
+  \begin{minipage}[t]{.49\textwidth}
+    \centering
     \input{impact.tex}
-  \caption{The mean number of nodes in the binary search tree for each value of
-    each experimental parameter. Note that the horizontal axis is on a $\log_2$
-    scale.}
+    \captionof{figure}{The mean number of nodes in the binary search tree for
+      each value of each experimental parameter. Note that the horizontal axis
+      is on a $\log_2$ scale.}
     \label{fig:impact}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[t]{.49\textwidth}
+    \centering
+    \input{bars.tex}
+    \captionof{figure}{Inference time for different values of $\maxArity{}$ and
+      proportions of facts that are probabilistic. The total number of facts is
+      fixed at $10^5$.}
+    \label{fig:bars}
+  \end{minipage}
 \end{figure}
+
+\begin{figure}[t]
+  \centering
+  \input{line_plots.tex}
+  \caption{Mean inference time for a range of ProbLog inference algorithms as
+    a function of the total number of facts in the program and the proportion of
+    independent pairs of predicates. For the second plot, the number of facts is
+    fixed at $10^5$.}
+  \label{fig:line_plots}
+\end{figure} % TODO: describe in the text
 

### 2020-05-11 scripts/analyse_model.R

@@ -5,12 +5,14 @@ library(ggrepel)
 
 # This is all for the runtime data of the CP model
 
-df <- read.csv("src/runtime.csv", header = FALSE, sep = ";", skip = 1)
+df <- read.csv("../data/runtime.csv", header = FALSE, sep = ";", skip = 1)
 df <- df[, colSums(is.na(df)) < nrow(df)]
 names(df) <- c("numPredicates", "maxArity", "numVariables", "numConstants", "numAdditionalClauses", "numIndependentPairs", "maxNumNodes",
                  "solutionCount", "buildingTime", "totalTime", "initTime", "nodes", "backtracks", "fails", "restarts")
 df$percentageIndependent <- round(ifelse(df$numIndependentPairs >= 2, df$numIndependentPairs / choose(df$numPredicates, 2), 0), 2)
 df$numClauses <- df$numPredicates + df$numAdditionalClauses
+
+# =========================================================
 
 # Numbers
 small <- df[df$totalTime < 1, ]
@@ -75,6 +77,8 @@ boxplots(df, df$numIndependentPairs, df$nodes)
 cor.test(df$percentageIndependent, df$nodes)
 boxplots(df, df$percentageIndependent, df$nodes)
 
+# ================================================================
+
 # Each parameter is a colour
 # 1, 2, 4, 8 on the x-axis
 # Something that represents the distribution of nodes on the y-axis. Start with a mean or median.
@@ -99,28 +103,29 @@ mytolatex <- function(name) {
 
 # reformat the table to have 3 columns: parameter_name, value (1, 2, 4, 8), and mean of nodes
 effects <- data.frame(Variable = factor(), Value = integer(), mean = numeric(), aritylabel = character())
-for (Variable in c('numPredicates', 'maxArity', 'numVariables', 'numConstants', 'numAdditionalClauses', 'maxNumNodes')) {
+factors <- c('numPredicates', 'maxArity', 'numVariables', 'numConstants', 'numAdditionalClauses', 'maxNumNodes')
+labels <- c("$|\\mathcal{P}|$", "$\\mathcal{M}_{\\mathcal{A}}$", "$|\\mathcal{V}|$", "$|\\mathcal{C}|$", "$\\mathcal{M}_{\\mathcal{C}}-|\\mathcal{P}|$", "$\\mathcal{M}_{\\mathcal{N}}$")
+for (Variable in factors) {
[…]

### 2020-05-11 scripts/analyse_problog.R

@@ -5,8 +5,7 @@ require(gridExtra)
 require(scales)
 require(grid)
 require(tidyr)
-
-# TODO: reject all instances where at least one algorithm failed
+require(tikzDevice)
 
 only_relevant_columns <- c("number.of.predicates", "number.of.variables",
                            "maximum.number.of.nodes", "maximum.arity",
@@ -29,24 +28,42 @@ prepare.csv <- function(filename) {
   df <- read.csv(filename, header = TRUE, sep = ",")
   print(mean(is.na(df$answer)))
   df <- df[!is.na(df$answer),]
-  #df <- df[df$number.of.predicates == 8,]
   df$proportion.listed <- df$number.of.facts / df$universe.size
   df$total.pairs <- df$number.of.predicates * (df$number.of.predicates - 1) / 2
   df$proportion.independent.pairs <- df$number.of.independent.pairs / df$total.pairs
-  df
+  df %>% unite("ID", only_relevant_columns, remove = F)
 }
 
-sdd <- prepare.csv("../data/problog_sdd.csv")
-nnf <- prepare.csv("../data/problog_nnf.csv")
-symbolic <- prepare.csv("../data/problog_symbolic.csv")
-melted.sdd <- melt(sdd[, relevant_columns], id.var = "Total.time")
-melted.nnf <- melt(nnf[, relevant_columns], id.var = "Total.time")
-melted.symbolic <- melt(symbolic[, relevant_columns], id.var = "Total.time")
+# ==================== Data wrangling ========================
 
-combined <- rbind(cbind(melted.sdd, Algorithm = "sdd"), cbind(melted.nnf, Algorithm = "nnf"),
-                  cbind(melted.symbolic, Algorithm = "symbolic"))
+sdd <- prepare.csv("../data/problog/sdd.csv")
+nnf <- prepare.csv("../data/problog/nnf.csv")
+symbolic <- prepare.csv("../data/problog/symbolic.csv")
+kbest <- prepare.csv("../data/problog/kbest.csv")
+sddx <- prepare.csv("../data/problog/sddx.csv")
+ddnnf <- prepare.csv("../data/problog/ddnnf.csv")
+
+sdd <- sdd[sdd$ID %in% nnf$ID,]
+sdd <- sdd[sdd$ID %in% symbolic$ID,]
[…]

### 2020-05-11 scripts/run_problog.py

@@ -13,7 +13,7 @@ def run_one(filename):
         return
     sys.stdout.write('.')
     sys.stdout.flush()
-    output = subprocess.Popen(['problog', '-v', PROGRAMS_DIR + filename, '-t', TIMEOUT, '--symbolic'],
+    output = subprocess.Popen(['problog', '-v', PROGRAMS_DIR + filename, '-t', TIMEOUT, '-k', 'bdd'],
                               stdout=subprocess.PIPE)
     output_str = output.communicate()[0][:-1].decode('utf-8')
     with open(output_filename, 'w+') as f:

### 2020-05-15 text/paper2/bars.tex
Description of the experiments

@@
-% Created by tikzDevice version 0.12.3 on 2020-05-11 12:49:46
+% Created by tikzDevice version 0.12.3 on 2020-05-14 17:55:45
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 36.29) --
-	( 97.08, 36.29);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 62.99) --
-	( 97.08, 62.99);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 89.69) --
-	( 97.08, 89.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71, 49.64) --
-	( 97.08, 49.64);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71, 76.34) --
-	( 97.08, 76.34);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71,103.05) --
-	( 97.08,103.05);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 36.97) --
+	( 97.08, 36.97);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 64.98) --
+	( 97.08, 64.98);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 92.98) --
+	( 97.08, 92.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71, 50.98) --
+	( 97.08, 50.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71, 78.98) --
+	( 97.08, 78.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71,106.99) --
+	( 97.08,106.99);
 
@@
 
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.97) -- ( 51.50, 75.90);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.90) -- ( 51.50, 71.97);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.07) -- ( 51.50, 74.99);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.99) -- ( 51.50, 71.07);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 80.47) -- ( 51.50, 84.39);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 84.39) -- ( 51.50, 80.47);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.71) -- ( 51.50, 79.64);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 79.64) -- ( 51.50, 75.71);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.51) -- ( 51.50, 77.44);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.44) -- ( 51.50, 73.51);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.96) -- ( 51.50, 75.88);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.88) -- ( 51.50, 71.96);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.26) -- ( 51.50, 78.19);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.19) -- ( 51.50, 74.26);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.50) -- ( 51.50, 74.42);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.42) -- ( 51.50, 70.50);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.45) -- ( 51.50, 78.37);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.37) -- ( 51.50, 74.45);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.60) -- ( 51.50, 75.53);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.53) -- ( 51.50, 71.60);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.07) -- ( 51.50, 77.99);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.99) -- ( 51.50, 74.07);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 72.86) -- ( 51.50, 76.78);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.78) -- ( 51.50, 72.86);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.26) -- ( 51.50, 75.18);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.18) -- ( 51.50, 71.26);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.60) -- ( 51.50, 75.53);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.53) -- ( 51.50, 71.60);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.53) -- ( 51.50, 75.46);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.46) -- ( 51.50, 71.53);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.17) -- ( 51.50, 78.09);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.09) -- ( 51.50, 74.17);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 72.05) -- ( 51.50, 75.98);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.98) -- ( 51.50, 72.05);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.59) -- ( 51.50, 74.51);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.51) -- ( 51.50, 70.59);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.60) -- ( 51.50, 75.53);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.53) -- ( 51.50, 71.60);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.73) -- ( 51.50, 75.65);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.65) -- ( 51.50, 71.73);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.27) -- ( 51.50, 75.19);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.19) -- ( 51.50, 71.27);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.86) -- ( 51.50, 74.79);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.79) -- ( 51.50, 70.86);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 72.78) -- ( 51.50, 76.70);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.70) -- ( 51.50, 72.78);
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.50) -- ( 51.50, 78.42);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.42) -- ( 51.50, 74.50);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.55) -- ( 51.50, 77.47);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.47) -- ( 51.50, 73.55);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 83.41) -- ( 51.50, 87.33);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 87.33) -- ( 51.50, 83.41);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.42) -- ( 51.50, 82.34);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 82.34) -- ( 51.50, 78.42);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.11) -- ( 51.50, 80.03);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 80.03) -- ( 51.50, 76.11);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.48) -- ( 51.50, 78.40);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.40) -- ( 51.50, 74.48);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.90) -- ( 51.50, 80.82);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 80.82) -- ( 51.50, 76.90);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 72.95) -- ( 51.50, 76.87);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.87) -- ( 51.50, 72.95);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.09) -- ( 51.50, 81.02);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 81.02) -- ( 51.50, 77.09);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.11) -- ( 51.50, 78.03);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.03) -- ( 51.50, 74.11);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.69) -- ( 51.50, 80.62);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 80.62) -- ( 51.50, 76.69);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.42) -- ( 51.50, 79.34);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 79.34) -- ( 51.50, 75.42);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.74) -- ( 51.50, 77.67);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.67) -- ( 51.50, 73.74);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.11) -- ( 51.50, 78.03);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.03) -- ( 51.50, 74.11);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.03) -- ( 51.50, 77.96);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.96) -- ( 51.50, 74.03);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.80) -- ( 51.50, 80.72);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 80.72) -- ( 51.50, 76.80);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.58) -- ( 51.50, 78.50);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.50) -- ( 51.50, 74.58);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.04) -- ( 51.50, 76.96);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.96) -- ( 51.50, 73.04);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.11) -- ( 51.50, 78.03);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.03) -- ( 51.50, 74.11);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.24) -- ( 51.50, 78.16);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.16) -- ( 51.50, 74.24);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.75) -- ( 51.50, 77.68);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.68) -- ( 51.50, 73.75);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.33) -- ( 51.50, 77.25);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.25) -- ( 51.50, 73.33);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.34) -- ( 51.50, 79.26);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 79.26) -- ( 51.50, 75.34);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.66) -- ( 51.50, 79.58);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 79.58) -- ( 51.50, 75.66);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 72.71) -- ( 51.50, 76.63);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.63) -- ( 51.50, 72.71);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.76) -- ( 51.50, 81.69);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 81.69) -- ( 51.50, 77.76);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.89) -- ( 51.50, 80.82);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 80.82) -- ( 51.50, 76.89);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.43) -- ( 51.50, 78.36);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.36) -- ( 51.50, 74.43);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.36) -- ( 51.50, 77.29);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.29) -- ( 51.50, 73.36);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.28) -- ( 51.50, 77.20);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.20) -- ( 51.50, 73.28);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.81) -- ( 51.50, 77.73);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.73) -- ( 51.50, 73.81);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.10) -- ( 51.50, 80.03);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 80.03) -- ( 51.50, 76.10);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.24) -- ( 51.50, 79.16);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 79.16) -- ( 51.50, 75.24);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.38) -- ( 51.50, 82.31);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 82.31) -- ( 51.50, 78.38);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 72.51) -- ( 51.50, 76.43);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.43) -- ( 51.50, 72.51);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.85) -- ( 51.50, 78.78);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.78) -- ( 51.50, 74.85);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 72.89) -- ( 51.50, 76.82);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.82) -- ( 51.50, 72.89);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.54) -- ( 51.50, 77.46);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.46) -- ( 51.50, 73.54);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 79.88) -- ( 51.50, 83.81);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 83.81) -- ( 51.50, 79.88);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58,102.54) -- ( 51.50,106.46);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58,106.46) -- ( 51.50,102.54);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 88.89) -- ( 51.50, 92.81);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 92.81) -- ( 51.50, 88.89);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.05) -- ( 51.50, 76.97);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.97) -- ( 51.50, 73.05);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.11) -- ( 51.50, 77.03);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.03) -- ( 51.50, 73.11);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.17) -- ( 51.50, 77.09);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.09) -- ( 51.50, 73.17);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 72.85) -- ( 51.50, 76.77);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.77) -- ( 51.50, 72.85);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 80.27) -- ( 51.50, 84.20);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 84.20) -- ( 51.50, 80.27);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 83.55) -- ( 51.50, 87.47);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 87.47) -- ( 51.50, 83.55);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 90.50) -- ( 51.50, 94.42);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 94.42) -- ( 51.50, 90.50);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.52) -- ( 51.50, 80.45);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 80.45) -- ( 51.50, 76.52);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.93) -- ( 51.50, 79.85);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 79.85) -- ( 51.50, 75.93);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.09) -- ( 51.50, 77.02);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.02) -- ( 51.50, 73.09);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.21) -- ( 51.50, 77.13);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.13) -- ( 51.50, 73.21);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.77) -- ( 51.50, 81.69);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 81.69) -- ( 51.50, 77.77);
 
@@
 
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.27) -- ( 51.50, 74.19);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.19) -- ( 51.50, 70.27);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.09) -- ( 51.50, 79.01);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 79.01) -- ( 51.50, 75.09);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.26) -- ( 51.50, 78.18);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.18) -- ( 51.50, 74.26);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.92) -- ( 51.50, 75.84);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.84) -- ( 51.50, 71.92);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.89) -- ( 51.50, 74.82);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.82) -- ( 51.50, 70.89);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.81) -- ( 51.50, 74.73);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.73) -- ( 51.50, 70.81);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.32) -- ( 51.50, 75.24);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.24) -- ( 51.50, 71.32);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.51) -- ( 51.50, 77.43);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.43) -- ( 51.50, 73.51);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 72.68) -- ( 51.50, 76.60);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.60) -- ( 51.50, 72.68);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.68) -- ( 51.50, 79.61);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 79.61) -- ( 51.50, 75.68);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.08) -- ( 51.50, 74.01);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.01) -- ( 51.50, 70.08);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 72.32) -- ( 51.50, 76.24);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.24) -- ( 51.50, 72.32);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.44) -- ( 51.50, 74.37);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.37) -- ( 51.50, 70.44);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.61) -- ( 51.50, 74.54);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.54) -- ( 51.50, 70.61);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 69.97) -- ( 51.50, 73.89);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.89) -- ( 51.50, 69.97);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.26) -- ( 51.50, 82.18);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 82.18) -- ( 51.50, 78.26);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.73) -- ( 51.50, 78.66);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.66) -- ( 51.50, 74.73);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.06) -- ( 51.50, 74.99);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.99) -- ( 51.50, 71.06);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58,101.49) -- ( 51.50,105.41);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58,105.41) -- ( 51.50,101.49);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58,102.54) -- ( 51.50,106.46);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58,106.46) -- ( 51.50,102.54);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.11) -- ( 51.50, 81.03);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 81.03) -- ( 51.50, 77.11);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58,101.45) -- ( 51.50,105.38);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58,105.38) -- ( 51.50,101.45);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58,101.49) -- ( 51.50,105.41);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58,105.41) -- ( 51.50,101.49);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 98.71) -- ( 51.50,102.64);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58,102.64) -- ( 51.50, 98.71);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 85.70) -- ( 51.50, 89.62);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 89.62) -- ( 51.50, 85.70);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.59) -- ( 51.50, 74.52);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.52) -- ( 51.50, 70.59);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 69.91) -- ( 51.50, 73.84);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.84) -- ( 51.50, 69.91);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.65) -- ( 51.50, 74.58);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.58) -- ( 51.50, 70.65);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.71) -- ( 51.50, 74.63);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.63) -- ( 51.50, 70.71);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.41) -- ( 51.50, 74.33);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.33) -- ( 51.50, 70.41);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.48) -- ( 51.50, 81.41);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 81.41) -- ( 51.50, 77.48);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 80.61) -- ( 51.50, 84.53);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 84.53) -- ( 51.50, 80.61);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 87.23) -- ( 51.50, 91.16);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 91.16) -- ( 51.50, 87.23);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.91) -- ( 51.50, 77.83);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.83) -- ( 51.50, 73.91);
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 90.09) -- ( 51.50, 94.01);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 94.01) -- ( 51.50, 90.09);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.16) -- ( 51.50, 78.08);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.08) -- ( 51.50, 74.16);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 79.84) -- ( 51.50, 83.77);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 83.77) -- ( 51.50, 79.84);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.15) -- ( 51.50, 82.08);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 82.08) -- ( 51.50, 78.15);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 93.27) -- ( 51.50, 97.19);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 97.19) -- ( 51.50, 93.27);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 49.54, 57.22) -- ( 49.54, 71.81);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 49.54, 47.48) -- ( 49.54, 34.20);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 38.40, 57.22) --
-	( 38.40, 47.48) --
-	( 60.68, 47.48) --
-	( 60.68, 57.22) --
-	( 38.40, 57.22) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 49.54, 58.91) -- ( 49.54, 74.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 49.54, 48.64) -- ( 49.54, 34.20);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 38.40, 58.91) --
+	( 38.40, 48.64) --
+	( 60.68, 48.64) --
+	( 60.68, 58.91) --
+	( 38.40, 58.91) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 38.40, 52.13) -- ( 60.68, 52.13);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 38.40, 53.42) -- ( 60.68, 53.42);
 \definecolor{drawColor}{RGB}{51,51,51}
 
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.78) -- ( 81.21, 85.71);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.71) -- ( 81.21, 81.78);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.35) -- ( 81.21, 86.27);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.27) -- ( 81.21, 82.35);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.08) -- ( 81.21, 83.00);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.00) -- ( 81.21, 79.08);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.03) -- ( 81.21, 82.96);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.96) -- ( 81.21, 79.03);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.81) -- ( 81.21, 86.73);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.73) -- ( 81.21, 82.81);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.76) -- ( 81.21, 84.68);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.68) -- ( 81.21, 80.76);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.46) -- ( 81.21, 84.39);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.39) -- ( 81.21, 80.46);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.59) -- ( 81.21, 91.52);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.52) -- ( 81.21, 87.59);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.62) -- ( 81.21, 84.55);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.55) -- ( 81.21, 80.62);
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.78) -- ( 81.21, 88.71);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.71) -- ( 81.21, 84.78);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.38) -- ( 81.21, 89.30);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.30) -- ( 81.21, 85.38);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.95) -- ( 81.21, 85.87);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.87) -- ( 81.21, 81.95);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.90) -- ( 81.21, 85.82);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.82) -- ( 81.21, 81.90);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.85) -- ( 81.21, 89.78);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.78) -- ( 81.21, 85.85);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.71) -- ( 81.21, 87.63);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.63) -- ( 81.21, 83.71);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.40) -- ( 81.21, 87.32);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.32) -- ( 81.21, 83.40);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.88) -- ( 81.21, 94.80);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 94.80) -- ( 81.21, 90.88);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.57) -- ( 81.21, 87.49);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.49) -- ( 81.21, 83.57);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.24) -- ( 81.21, 90.16);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.16) -- ( 81.21, 86.24);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.08) -- ( 81.21, 86.01);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.01) -- ( 81.21, 82.08);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.15) -- ( 81.21, 86.08);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.08) -- ( 81.21, 82.15);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.14) -- ( 81.21, 86.07);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.07) -- ( 81.21, 82.14);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.13) -- ( 81.21, 94.06);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 94.06) -- ( 81.21, 90.13);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.67) -- ( 81.21, 91.60);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.60) -- ( 81.21, 87.67);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.35) -- ( 81.21, 94.27);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 94.27) -- ( 81.21, 90.35);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.62) -- ( 81.21, 89.55);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.55) -- ( 81.21, 85.62);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.38) -- ( 81.21, 93.30);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 93.30) -- ( 81.21, 89.38);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.21) -- ( 81.21, 93.13);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 93.13) -- ( 81.21, 89.21);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.61) -- ( 81.21, 88.53);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.53) -- ( 81.21, 84.61);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 93.10) -- ( 81.21, 97.03);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 97.03) -- ( 81.21, 93.10);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.41) -- ( 81.21, 91.33);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.33) -- ( 81.21, 87.41);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.23) -- ( 81.21, 90.15);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.15) -- ( 81.21, 86.23);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.22) -- ( 81.21, 87.15);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.15) -- ( 81.21, 83.22);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 93.52) -- ( 81.21, 97.44);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 97.44) -- ( 81.21, 93.52);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.51) -- ( 81.21, 90.43);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.43) -- ( 81.21, 86.51);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.70) -- ( 81.21, 89.63);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.63) -- ( 81.21, 85.70);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.06) -- ( 81.21, 89.98);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.98) -- ( 81.21, 86.06);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.27) -- ( 81.21, 86.19);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.19) -- ( 81.21, 82.27);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.35) -- ( 81.21, 90.28);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.28) -- ( 81.21, 86.35);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.22) -- ( 81.21, 86.14);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.14) -- ( 81.21, 82.22);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.48) -- ( 81.21, 94.40);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 94.40) -- ( 81.21, 90.48);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.74) -- ( 81.21, 85.66);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.66) -- ( 81.21, 81.74);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.21) -- ( 81.21, 89.14);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.14) -- ( 81.21, 85.21);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.82) -- ( 81.21, 85.75);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.75) -- ( 81.21, 81.82);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.84) -- ( 81.21, 88.77);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.77) -- ( 81.21, 84.84);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.38) -- ( 81.21, 87.31);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.31) -- ( 81.21, 83.38);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.11) -- ( 81.21, 86.03);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.03) -- ( 81.21, 82.11);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.90) -- ( 81.21, 88.82);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.82) -- ( 81.21, 84.90);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.68) -- ( 81.21, 85.61);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.61) -- ( 81.21, 81.68);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.29) -- ( 81.21, 89.21);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.21) -- ( 81.21, 85.29);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.48) -- ( 81.21, 92.41);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 92.41) -- ( 81.21, 88.48);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.59) -- ( 81.21, 88.51);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.51) -- ( 81.21, 84.59);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.55) -- ( 81.21, 88.47);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.47) -- ( 81.21, 84.55);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.00) -- ( 81.21, 86.92);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.92) -- ( 81.21, 83.00);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.34) -- ( 81.21, 88.27);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.27) -- ( 81.21, 84.34);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.53) -- ( 81.21, 88.45);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.45) -- ( 81.21, 84.53);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.06) -- ( 81.21, 85.98);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.98) -- ( 81.21, 82.06);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.07) -- ( 81.21, 92.99);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 92.99) -- ( 81.21, 89.07);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.56) -- ( 81.21, 86.48);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.48) -- ( 81.21, 82.56);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.74) -- ( 81.21, 87.66);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.66) -- ( 81.21, 83.74);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.71) -- ( 81.21, 90.64);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.64) -- ( 81.21, 86.71);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.08) -- ( 81.21, 88.00);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.00) -- ( 81.21, 84.08);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.21) -- ( 81.21, 92.13);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 92.13) -- ( 81.21, 88.21);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.18) -- ( 81.21, 93.10);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 93.10) -- ( 81.21, 89.18);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.95) -- ( 81.21, 86.87);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.87) -- ( 81.21, 82.95);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.59) -- ( 81.21, 90.51);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.51) -- ( 81.21, 86.59);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.02) -- ( 81.21, 90.94);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.94) -- ( 81.21, 87.02);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.30) -- ( 81.21, 90.22);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.22) -- ( 81.21, 86.30);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.11) -- ( 81.21, 93.03);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 93.03) -- ( 81.21, 89.11);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.54) -- ( 81.21, 88.46);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.46) -- ( 81.21, 84.54);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.69) -- ( 81.21, 86.61);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.61) -- ( 81.21, 82.69);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.89) -- ( 81.21, 85.82);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.82) -- ( 81.21, 81.89);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.73) -- ( 81.21, 85.66);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.66) -- ( 81.21, 81.73);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.11) -- ( 81.21, 87.03);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.03) -- ( 81.21, 83.11);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.85) -- ( 81.21, 86.77);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.77) -- ( 81.21, 82.85);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.16) -- ( 81.21, 88.09);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.09) -- ( 81.21, 84.16);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.18) -- ( 81.21, 88.11);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.11) -- ( 81.21, 84.18);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.30) -- ( 81.21, 88.22);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.22) -- ( 81.21, 84.30);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.08) -- ( 81.21, 87.00);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.00) -- ( 81.21, 83.08);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.10) -- ( 81.21, 90.02);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.02) -- ( 81.21, 86.10);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.17) -- ( 81.21, 88.10);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.10) -- ( 81.21, 84.17);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.98) -- ( 81.21, 90.90);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.90) -- ( 81.21, 86.98);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.23) -- ( 81.21, 88.16);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.16) -- ( 81.21, 84.23);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.78) -- ( 81.21, 88.70);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.70) -- ( 81.21, 84.78);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.11) -- ( 81.21, 90.04);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.04) -- ( 81.21, 86.11);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.85) -- ( 81.21, 85.77);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.77) -- ( 81.21, 81.85);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.91) -- ( 81.21, 88.83);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.83) -- ( 81.21, 84.91);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.89) -- ( 81.21, 86.81);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.81) -- ( 81.21, 82.89);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.53) -- ( 81.21, 88.45);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.45) -- ( 81.21, 84.53);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.55) -- ( 81.21, 93.47);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 93.47) -- ( 81.21, 89.55);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.05) -- ( 81.21, 89.97);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.97) -- ( 81.21, 86.05);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.94) -- ( 81.21, 85.87);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.87) -- ( 81.21, 81.94);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.37) -- ( 81.21, 95.29);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 95.29) -- ( 81.21, 91.37);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.84) -- ( 81.21, 87.76);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.76) -- ( 81.21, 83.84);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.17) -- ( 81.21, 93.09);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 93.09) -- ( 81.21, 89.17);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.59) -- ( 81.21, 87.52);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.52) -- ( 81.21, 83.59);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.94) -- ( 81.21, 91.87);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.87) -- ( 81.21, 87.94);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.76) -- ( 81.21, 86.68);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.68) -- ( 81.21, 82.76);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.05) -- ( 81.21, 89.97);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.97) -- ( 81.21, 86.05);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.55) -- ( 81.21, 89.47);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.47) -- ( 81.21, 85.55);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.87) -- ( 81.21, 89.79);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.79) -- ( 81.21, 85.87);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.18) -- ( 81.21, 87.11);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.11) -- ( 81.21, 83.18);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.44) -- ( 81.21, 93.36);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 93.36) -- ( 81.21, 89.44);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.14) -- ( 81.21, 86.07);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.07) -- ( 81.21, 82.14);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.03) -- ( 81.21, 85.95);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.95) -- ( 81.21, 82.03);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.91) -- ( 81.21, 91.84);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.84) -- ( 81.21, 87.91);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.16) -- ( 81.21, 87.08);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.08) -- ( 81.21, 83.16);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.90) -- ( 81.21, 85.83);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.83) -- ( 81.21, 81.90);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.40) -- ( 81.21, 94.33);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 94.33) -- ( 81.21, 90.40);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.74) -- ( 81.21, 85.66);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.66) -- ( 81.21, 81.74);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.58) -- ( 81.21, 89.50);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.50) -- ( 81.21, 85.58);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.56) -- ( 81.21, 91.49);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.49) -- ( 81.21, 87.56);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.02) -- ( 81.21, 88.94);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.94) -- ( 81.21, 85.02);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.63) -- ( 81.21, 90.55);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.55) -- ( 81.21, 86.63);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.16) -- ( 81.21, 88.09);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.09) -- ( 81.21, 84.16);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29,100.81) -- ( 81.21,104.73);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29,104.73) -- ( 81.21,100.81);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.34) -- ( 81.21, 93.27);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 93.27) -- ( 81.21, 89.34);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.30) -- ( 81.21, 89.23);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.23) -- ( 81.21, 85.30);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.90) -- ( 81.21, 91.82);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.82) -- ( 81.21, 87.90);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.35) -- ( 81.21, 93.27);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 93.27) -- ( 81.21, 89.35);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.16) -- ( 81.21, 86.09);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.09) -- ( 81.21, 82.16);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.33) -- ( 81.21, 88.25);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.25) -- ( 81.21, 84.33);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.86) -- ( 81.21, 86.78);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.78) -- ( 81.21, 82.86);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.68) -- ( 81.21, 87.61);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.61) -- ( 81.21, 83.68);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 96.37) -- ( 81.21,100.29);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29,100.29) -- ( 81.21, 96.37);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.53) -- ( 81.21, 87.46);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.46) -- ( 81.21, 83.53);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.63) -- ( 81.21, 95.55);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 95.55) -- ( 81.21, 91.63);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.99) -- ( 81.21, 86.92);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.92) -- ( 81.21, 82.99);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.40) -- ( 81.21, 92.33);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 92.33) -- ( 81.21, 88.40);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 99.38) -- ( 81.21,103.31);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29,103.31) -- ( 81.21, 99.38);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.59) -- ( 81.21, 89.51);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.51) -- ( 81.21, 85.59);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.21) -- ( 81.21, 87.14);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.14) -- ( 81.21, 83.21);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.52) -- ( 81.21, 86.44);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.44) -- ( 81.21, 82.52);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.63) -- ( 81.21, 85.56);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.56) -- ( 81.21, 81.63);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.05) -- ( 81.21, 85.97);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.97) -- ( 81.21, 82.05);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.99) -- ( 81.21, 86.91);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.91) -- ( 81.21, 82.99);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.70) -- ( 81.21, 87.62);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.62) -- ( 81.21, 83.70);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.92) -- ( 81.21, 85.85);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.85) -- ( 81.21, 81.92);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.94) -- ( 81.21, 85.87);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.87) -- ( 81.21, 81.94);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29,101.39) -- ( 81.21,105.31);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29,105.31) -- ( 81.21,101.39);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 94.76) -- ( 81.21, 98.69);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 98.69) -- ( 81.21, 94.76);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 92.65) -- ( 81.21, 96.57);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 96.57) -- ( 81.21, 92.65);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 93.09) -- ( 81.21, 97.01);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 97.01) -- ( 81.21, 93.09);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 99.31) -- ( 81.21,103.23);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29,103.23) -- ( 81.21, 99.31);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.65) -- ( 81.21, 94.58);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 94.58) -- ( 81.21, 90.65);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.67) -- ( 81.21, 88.59);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.59) -- ( 81.21, 84.67);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.09) -- ( 81.21, 86.01);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.01) -- ( 81.21, 82.09);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.49) -- ( 81.21, 88.41);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.41) -- ( 81.21, 84.49);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.70) -- ( 81.21, 90.63);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.63) -- ( 81.21, 86.70);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.72) -- ( 81.21, 86.65);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.65) -- ( 81.21, 82.72);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.53) -- ( 81.21, 89.46);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.46) -- ( 81.21, 85.53);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.84) -- ( 81.21, 85.76);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.76) -- ( 81.21, 81.84);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.77) -- ( 81.21, 86.69);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.69) -- ( 81.21, 82.77);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.26) -- ( 81.21, 86.18);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.18) -- ( 81.21, 82.26);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.33) -- ( 81.21, 91.25);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.25) -- ( 81.21, 87.33);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.69) -- ( 81.21, 89.61);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.61) -- ( 81.21, 85.69);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.73) -- ( 81.21, 85.66);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.66) -- ( 81.21, 81.73);
 
@@
 
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.21) -- ( 81.21, 83.13);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.13) -- ( 81.21, 79.21);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.27) -- ( 81.21, 83.20);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.20) -- ( 81.21, 79.27);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.26) -- ( 81.21, 83.19);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.19) -- ( 81.21, 79.26);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.88) -- ( 81.21, 90.81);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.81) -- ( 81.21, 86.88);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.48) -- ( 81.21, 82.41);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.41) -- ( 81.21, 78.48);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.54) -- ( 81.21, 88.47);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.47) -- ( 81.21, 84.54);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.09) -- ( 81.21, 91.01);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.01) -- ( 81.21, 87.09);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.58) -- ( 81.21, 86.51);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.51) -- ( 81.21, 82.58);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.17) -- ( 81.21, 90.09);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.09) -- ( 81.21, 86.17);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.00) -- ( 81.21, 89.93);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.93) -- ( 81.21, 86.00);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.62) -- ( 81.21, 85.54);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.54) -- ( 81.21, 81.62);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.72) -- ( 81.21, 93.64);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 93.64) -- ( 81.21, 89.72);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.29) -- ( 81.21, 88.21);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.21) -- ( 81.21, 84.29);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.16) -- ( 81.21, 87.08);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.08) -- ( 81.21, 83.16);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.29) -- ( 81.21, 84.22);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.22) -- ( 81.21, 80.29);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.56) -- ( 81.21, 82.49);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.49) -- ( 81.21, 78.56);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.11) -- ( 81.21, 94.04);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 94.04) -- ( 81.21, 90.11);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.43) -- ( 81.21, 87.35);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.35) -- ( 81.21, 83.43);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.66) -- ( 81.21, 86.58);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.58) -- ( 81.21, 82.66);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.00) -- ( 81.21, 86.93);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.93) -- ( 81.21, 83.00);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.39) -- ( 81.21, 83.31);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.31) -- ( 81.21, 79.39);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.28) -- ( 81.21, 87.20);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.20) -- ( 81.21, 83.28);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.34) -- ( 81.21, 83.26);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.26) -- ( 81.21, 79.34);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.21) -- ( 81.21, 91.14);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.14) -- ( 81.21, 87.21);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.88) -- ( 81.21, 82.80);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.80) -- ( 81.21, 78.88);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.19) -- ( 81.21, 86.12);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.12) -- ( 81.21, 82.19);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.96) -- ( 81.21, 82.89);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.89) -- ( 81.21, 78.96);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.84) -- ( 81.21, 85.77);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.77) -- ( 81.21, 81.84);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.45) -- ( 81.21, 84.37);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.37) -- ( 81.21, 80.45);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.23) -- ( 81.21, 83.16);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.16) -- ( 81.21, 79.23);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.89) -- ( 81.21, 85.82);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.82) -- ( 81.21, 81.89);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.83) -- ( 81.21, 82.75);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.75) -- ( 81.21, 78.83);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.26) -- ( 81.21, 86.19);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.19) -- ( 81.21, 82.26);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.31) -- ( 81.21, 89.24);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.24) -- ( 81.21, 85.31);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.51) -- ( 81.21, 82.43);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.43) -- ( 81.21, 78.51);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.59) -- ( 81.21, 85.52);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.52) -- ( 81.21, 81.59);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.56) -- ( 81.21, 85.49);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.49) -- ( 81.21, 81.56);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.08) -- ( 81.21, 84.01);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.01) -- ( 81.21, 80.08);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.36) -- ( 81.21, 85.29);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.29) -- ( 81.21, 81.36);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.54) -- ( 81.21, 85.47);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.47) -- ( 81.21, 81.54);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.19) -- ( 81.21, 83.11);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.11) -- ( 81.21, 79.19);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.87) -- ( 81.21, 89.79);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.79) -- ( 81.21, 85.87);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.50) -- ( 81.21, 82.42);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.42) -- ( 81.21, 78.50);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.66) -- ( 81.21, 83.59);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.59) -- ( 81.21, 79.66);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.79) -- ( 81.21, 84.71);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.71) -- ( 81.21, 80.79);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.63) -- ( 81.21, 87.55);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.55) -- ( 81.21, 83.63);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.11) -- ( 81.21, 85.03);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.03) -- ( 81.21, 81.11);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.05) -- ( 81.21, 88.97);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.97) -- ( 81.21, 85.05);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.98) -- ( 81.21, 89.90);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.90) -- ( 81.21, 85.98);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.03) -- ( 81.21, 83.96);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.96) -- ( 81.21, 80.03);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.65) -- ( 81.21, 82.58);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.58) -- ( 81.21, 78.65);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.50) -- ( 81.21, 87.43);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.43) -- ( 81.21, 83.50);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.41) -- ( 81.21, 82.33);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.33) -- ( 81.21, 78.41);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.91) -- ( 81.21, 87.84);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.84) -- ( 81.21, 83.91);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.23) -- ( 81.21, 87.15);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.15) -- ( 81.21, 83.23);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.91) -- ( 81.21, 89.83);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.83) -- ( 81.21, 85.91);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.55) -- ( 81.21, 85.47);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.47) -- ( 81.21, 81.55);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.78) -- ( 81.21, 83.71);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.71) -- ( 81.21, 79.78);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.03) -- ( 81.21, 82.95);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.95) -- ( 81.21, 79.03);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.87) -- ( 81.21, 82.80);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.80) -- ( 81.21, 78.87);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.19) -- ( 81.21, 84.11);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.11) -- ( 81.21, 80.19);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.94) -- ( 81.21, 83.86);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.86) -- ( 81.21, 79.94);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.19) -- ( 81.21, 85.12);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.12) -- ( 81.21, 81.19);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.21) -- ( 81.21, 85.14);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.14) -- ( 81.21, 81.21);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.32) -- ( 81.21, 85.24);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.24) -- ( 81.21, 81.32);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.16) -- ( 81.21, 84.08);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.08) -- ( 81.21, 80.16);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.04) -- ( 81.21, 86.96);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.96) -- ( 81.21, 83.04);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.20) -- ( 81.21, 85.13);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.13) -- ( 81.21, 81.20);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.88) -- ( 81.21, 87.80);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.80) -- ( 81.21, 83.88);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.26) -- ( 81.21, 85.18);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.18) -- ( 81.21, 81.26);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.69) -- ( 81.21, 82.62);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.62) -- ( 81.21, 78.69);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.78) -- ( 81.21, 85.71);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.71) -- ( 81.21, 81.78);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.05) -- ( 81.21, 86.97);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.97) -- ( 81.21, 83.05);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.98) -- ( 81.21, 82.91);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.91) -- ( 81.21, 78.98);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.90) -- ( 81.21, 85.83);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.83) -- ( 81.21, 81.90);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.97) -- ( 81.21, 83.90);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.90) -- ( 81.21, 79.97);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.54) -- ( 81.21, 85.46);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.46) -- ( 81.21, 81.54);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.33) -- ( 81.21, 90.25);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.25) -- ( 81.21, 86.33);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.99) -- ( 81.21, 86.91);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.91) -- ( 81.21, 82.99);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.08) -- ( 81.21, 83.00);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.00) -- ( 81.21, 79.08);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.06) -- ( 81.21, 91.99);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.99) -- ( 81.21, 88.06);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.88) -- ( 81.21, 84.81);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.81) -- ( 81.21, 80.88);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.96) -- ( 81.21, 89.89);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.89) -- ( 81.21, 85.96);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.65) -- ( 81.21, 84.57);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.57) -- ( 81.21, 80.65);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.79) -- ( 81.21, 88.72);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.72) -- ( 81.21, 84.79);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.85) -- ( 81.21, 83.78);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.78) -- ( 81.21, 79.85);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.99) -- ( 81.21, 86.91);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.91) -- ( 81.21, 82.99);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.51) -- ( 81.21, 86.44);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.44) -- ( 81.21, 82.51);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.82) -- ( 81.21, 86.74);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.74) -- ( 81.21, 82.82);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.26) -- ( 81.21, 84.18);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.18) -- ( 81.21, 80.26);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.22) -- ( 81.21, 90.14);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.14) -- ( 81.21, 86.22);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.27) -- ( 81.21, 83.19);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.19) -- ( 81.21, 79.27);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.16) -- ( 81.21, 83.08);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.08) -- ( 81.21, 79.16);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.77) -- ( 81.21, 88.69);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.69) -- ( 81.21, 84.77);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.23) -- ( 81.21, 84.16);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.16) -- ( 81.21, 80.23);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.04) -- ( 81.21, 82.96);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.96) -- ( 81.21, 79.04);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.14) -- ( 81.21, 91.07);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.07) -- ( 81.21, 87.14);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.88) -- ( 81.21, 82.80);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.80) -- ( 81.21, 78.88);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.54) -- ( 81.21, 86.46);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.46) -- ( 81.21, 82.54);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.43) -- ( 81.21, 88.36);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.36) -- ( 81.21, 84.43);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.01) -- ( 81.21, 85.93);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.93) -- ( 81.21, 82.01);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.55) -- ( 81.21, 87.47);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.47) -- ( 81.21, 83.55);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.19) -- ( 81.21, 85.12);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.12) -- ( 81.21, 81.19);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 97.06) -- ( 81.21,100.99);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29,100.99) -- ( 81.21, 97.06);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.13) -- ( 81.21, 90.06);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.06) -- ( 81.21, 86.13);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.28) -- ( 81.21, 86.21);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.21) -- ( 81.21, 82.28);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.75) -- ( 81.21, 88.68);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.68) -- ( 81.21, 84.75);
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.12) -- ( 81.21, 87.04);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.04) -- ( 81.21, 83.12);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.69) -- ( 81.21, 88.61);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.61) -- ( 81.21, 84.69);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.28) -- ( 81.21, 95.21);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 95.21) -- ( 81.21, 91.28);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.34) -- ( 81.21, 86.26);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.26) -- ( 81.21, 82.34);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.37) -- ( 81.21, 94.29);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 94.29) -- ( 81.21, 90.37);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 99.67) -- ( 81.21,103.59);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29,103.59) -- ( 81.21, 99.67);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.63) -- ( 81.21, 87.56);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.56) -- ( 81.21, 83.63);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.14) -- ( 81.21, 87.07);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.07) -- ( 81.21, 83.14);
 
@@
 
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.28) -- ( 81.21, 83.21);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.21) -- ( 81.21, 79.28);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.35) -- ( 81.21, 85.28);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.28) -- ( 81.21, 81.35);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.95) -- ( 81.21, 83.87);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.87) -- ( 81.21, 79.95);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.73) -- ( 81.21, 84.66);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.66) -- ( 81.21, 80.73);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 92.83) -- ( 81.21, 96.76);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 96.76) -- ( 81.21, 92.83);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.59) -- ( 81.21, 84.52);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.52) -- ( 81.21, 80.59);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.31) -- ( 81.21, 92.24);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 92.24) -- ( 81.21, 88.31);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.07) -- ( 81.21, 84.00);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.00) -- ( 81.21, 80.07);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.24) -- ( 81.21, 89.16);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.16) -- ( 81.21, 85.24);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 95.70) -- ( 81.21, 99.63);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 99.63) -- ( 81.21, 95.70);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.55) -- ( 81.21, 86.47);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.47) -- ( 81.21, 82.55);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.29) -- ( 81.21, 84.21);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.21) -- ( 81.21, 80.29);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.62) -- ( 81.21, 83.55);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.55) -- ( 81.21, 79.62);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.78) -- ( 81.21, 82.70);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.70) -- ( 81.21, 78.78);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.17) -- ( 81.21, 83.10);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.10) -- ( 81.21, 79.17);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.00) -- ( 81.21, 82.92);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.92) -- ( 81.21, 79.00);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.09) -- ( 81.21, 91.01);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.01) -- ( 81.21, 87.09);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.15) -- ( 81.21, 88.08);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.08) -- ( 81.21, 84.15);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.74) -- ( 81.21, 84.66);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.66) -- ( 81.21, 80.74);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.67) -- ( 81.21, 90.59);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.59) -- ( 81.21, 86.67);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.53) -- ( 81.21, 82.45);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.45) -- ( 81.21, 78.53);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.85) -- ( 81.21, 84.77);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.77) -- ( 81.21, 80.85);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.25) -- ( 81.21, 84.18);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.18) -- ( 81.21, 80.25);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 92.97) -- ( 81.21, 96.90);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 96.90) -- ( 81.21, 92.97);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.45) -- ( 81.21, 93.38);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 93.38) -- ( 81.21, 89.45);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.27) -- ( 81.21, 83.19);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.19) -- ( 81.21, 79.27);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.86) -- ( 81.21, 82.79);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.79) -- ( 81.21, 78.86);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.53) -- ( 81.21, 87.45);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.45) -- ( 81.21, 83.53);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.02) -- ( 81.21, 90.94);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.94) -- ( 81.21, 87.02);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.13) -- ( 81.21, 89.06);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.06) -- ( 81.21, 85.13);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.62) -- ( 81.21, 88.55);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.55) -- ( 81.21, 84.62);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 97.62) -- ( 81.21,101.54);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29,101.54) -- ( 81.21, 97.62);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.91) -- ( 81.21, 90.83);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.83) -- ( 81.21, 86.91);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.65) -- ( 81.21, 87.58);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.58) -- ( 81.21, 83.65);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.14) -- ( 81.21, 92.07);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 92.07) -- ( 81.21, 88.14);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.09) -- ( 81.21, 95.02);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 95.02) -- ( 81.21, 91.09);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.39) -- ( 81.21, 82.32);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.32) -- ( 81.21, 78.39);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.95) -- ( 81.21, 85.87);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.87) -- ( 81.21, 81.95);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.34) -- ( 81.21, 86.27);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.27) -- ( 81.21, 82.34);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.97) -- ( 81.21, 85.89);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.89) -- ( 81.21, 81.97);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.45) -- ( 81.21, 92.37);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 92.37) -- ( 81.21, 88.45);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.38) -- ( 81.21, 90.30);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.30) -- ( 81.21, 86.38);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 98.06) -- ( 81.21,101.98);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29,101.98) -- ( 81.21, 98.06);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.07) -- ( 81.21, 84.00);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.00) -- ( 81.21, 80.07);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.75) -- ( 81.21, 84.67);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.67) -- ( 81.21, 80.75);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.06) -- ( 81.21, 82.98);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.98) -- ( 81.21, 79.06);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.07) -- ( 81.21, 83.00);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.00) -- ( 81.21, 79.07);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29,101.47) -- ( 81.21,105.40);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29,105.40) -- ( 81.21,101.47);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29,101.45) -- ( 81.21,105.37);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29,105.37) -- ( 81.21,101.45);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 97.62) -- ( 81.21,101.54);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29,101.54) -- ( 81.21, 97.62);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.30) -- ( 81.21, 95.22);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 95.22) -- ( 81.21, 91.30);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.28) -- ( 81.21, 93.21);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 93.21) -- ( 81.21, 89.28);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.70) -- ( 81.21, 93.63);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 93.63) -- ( 81.21, 89.70);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 95.64) -- ( 81.21, 99.56);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 99.56) -- ( 81.21, 95.64);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.38) -- ( 81.21, 91.31);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.31) -- ( 81.21, 87.38);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.67) -- ( 81.21, 85.60);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.60) -- ( 81.21, 81.67);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.60) -- ( 81.21, 82.53);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.53) -- ( 81.21, 78.60);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.22) -- ( 81.21, 83.14);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.14) -- ( 81.21, 79.22);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.50) -- ( 81.21, 85.43);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.43) -- ( 81.21, 81.50);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.62) -- ( 81.21, 87.54);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.54) -- ( 81.21, 83.62);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.82) -- ( 81.21, 83.74);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.74) -- ( 81.21, 79.82);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.50) -- ( 81.21, 86.42);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.42) -- ( 81.21, 82.50);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.97) -- ( 81.21, 82.90);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.90) -- ( 81.21, 78.97);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.86) -- ( 81.21, 83.79);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.79) -- ( 81.21, 79.86);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.38) -- ( 81.21, 83.30);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.30) -- ( 81.21, 79.38);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.21) -- ( 81.21, 88.13);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.13) -- ( 81.21, 84.21);
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.23) -- ( 81.21, 86.16);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.16) -- ( 81.21, 82.23);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.64) -- ( 81.21, 87.57);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.57) -- ( 81.21, 83.64);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.12) -- ( 81.21, 87.04);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.04) -- ( 81.21, 83.12);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.79) -- ( 81.21, 87.71);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.71) -- ( 81.21, 83.79);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 97.01) -- ( 81.21,100.93);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29,100.93) -- ( 81.21, 97.01);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.67) -- ( 81.21, 89.59);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.59) -- ( 81.21, 85.67);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.04) -- ( 81.21, 93.97);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 93.97) -- ( 81.21, 90.04);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.39) -- ( 81.21, 93.32);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 93.32) -- ( 81.21, 89.39);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.02) -- ( 81.21, 85.94);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.94) -- ( 81.21, 82.02);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.59) -- ( 81.21, 92.51);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 92.51) -- ( 81.21, 88.59);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.22) -- ( 81.21, 93.15);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 93.15) -- ( 81.21, 89.22);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 92.53) -- ( 81.21, 96.45);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 96.45) -- ( 81.21, 92.53);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.87) -- ( 81.21, 91.79);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.79) -- ( 81.21, 87.87);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.02) -- ( 81.21, 85.94);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.94) -- ( 81.21, 82.02);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.38) -- ( 81.21, 95.30);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 95.30) -- ( 81.21, 91.38);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.33) -- ( 81.21, 92.25);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 92.25) -- ( 81.21, 88.33);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.83) -- ( 81.21, 92.75);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 92.75) -- ( 81.21, 88.83);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.10) -- ( 81.21, 91.03);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.03) -- ( 81.21, 87.10);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 90.05) -- ( 81.21, 93.98);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 93.98) -- ( 81.21, 90.05);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.15) -- ( 81.21, 89.07);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.07) -- ( 81.21, 85.15);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.87) -- ( 81.21, 88.79);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.79) -- ( 81.21, 84.87);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.64) -- ( 81.21, 85.56);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.56) -- ( 81.21, 81.64);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.16) -- ( 81.21, 86.08);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.08) -- ( 81.21, 82.16);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.79) -- ( 81.21, 87.72);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.72) -- ( 81.21, 83.79);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.15) -- ( 81.21, 95.08);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 95.08) -- ( 81.21, 91.15);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.79) -- ( 81.21, 87.72);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.72) -- ( 81.21, 83.79);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.70) -- ( 81.21, 85.63);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.63) -- ( 81.21, 81.70);
 
@@
 \path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.57) -- ( 81.21, 82.65);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.56) -- ( 81.21, 82.48);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.48) -- ( 81.21, 78.56);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.88) -- ( 81.21, 82.80);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.80) -- ( 81.21, 78.88);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.24) -- ( 81.21, 84.17);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.17) -- ( 81.21, 80.24);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.20) -- ( 81.21, 84.12);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.12) -- ( 81.21, 80.20);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.69) -- ( 81.21, 85.62);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.62) -- ( 81.21, 81.69);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.98) -- ( 81.21, 91.91);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.91) -- ( 81.21, 87.98);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.45) -- ( 81.21, 83.37);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.37) -- ( 81.21, 79.45);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.11) -- ( 81.21, 91.03);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 91.03) -- ( 81.21, 87.11);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 95.98) -- ( 81.21, 99.90);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 99.90) -- ( 81.21, 95.98);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.69) -- ( 81.21, 84.61);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.61) -- ( 81.21, 80.69);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.22) -- ( 81.21, 84.14);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.14) -- ( 81.21, 80.22);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.07) -- ( 81.21, 87.00);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.00) -- ( 81.21, 83.07);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 79.35) -- ( 81.21, 83.28);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.28) -- ( 81.21, 79.35);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.70) -- ( 81.21, 84.62);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.62) -- ( 81.21, 80.70);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.19) -- ( 81.21, 84.12);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.12) -- ( 81.21, 80.19);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 80.84) -- ( 81.21, 84.76);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.76) -- ( 81.21, 80.84);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 93.44) -- ( 81.21, 97.37);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 97.37) -- ( 81.21, 93.44);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.39) -- ( 81.21, 82.32);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.32) -- ( 81.21, 78.39);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.63) -- ( 81.21, 86.55);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 86.55) -- ( 81.21, 82.63);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 78.52) -- ( 81.21, 82.44);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 82.44) -- ( 81.21, 78.52);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 79.25, 63.16) -- ( 79.25, 80.24);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 79.25, 51.75) -- ( 79.25, 36.04);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 68.11, 63.16) --
-	( 68.11, 51.75) --
-	( 90.39, 51.75) --
-	( 90.39, 63.16) --
-	( 68.11, 63.16) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 79.25, 65.34) -- ( 79.25, 83.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 79.25, 53.18) -- ( 79.25, 36.71);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 68.11, 65.34) --
+	( 68.11, 53.18) --
+	( 90.39, 53.18) --
+	( 90.39, 65.34) --
+	( 68.11, 65.34) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 68.11, 57.40) -- ( 90.39, 57.40);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 68.11, 59.03) -- ( 90.39, 59.03);
 
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (102.58, 36.29) --
-	(167.95, 36.29);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (102.58, 62.99) --
-	(167.95, 62.99);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (102.58, 89.69) --
-	(167.95, 89.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (102.58, 49.64) --
-	(167.95, 49.64);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (102.58, 76.34) --
-	(167.95, 76.34);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (102.58,103.05) --
-	(167.95,103.05);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (102.58, 36.97) --
+	(167.95, 36.97);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (102.58, 64.98) --
+	(167.95, 64.98);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (102.58, 92.98) --
+	(167.95, 92.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (102.58, 50.98) --
+	(167.95, 50.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (102.58, 78.98) --
+	(167.95, 78.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (102.58,106.99) --
+	(167.95,106.99);
 
@@
 
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 72.46) -- (116.80, 76.39);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.39) -- (116.80, 72.46);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 72.15) -- (116.80, 76.07);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.07) -- (116.80, 72.15);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.39) -- (116.80, 80.31);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 80.31) -- (116.80, 76.39);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.62) -- (116.80, 77.55);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.55) -- (116.80, 73.62);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.92) -- (116.80, 77.85);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.85) -- (116.80, 73.92);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 71.37) -- (116.80, 75.29);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.29) -- (116.80, 71.37);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.50) -- (116.80, 79.43);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 79.43) -- (116.80, 75.50);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 72.53) -- (116.80, 76.45);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.45) -- (116.80, 72.53);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 71.61) -- (116.80, 75.53);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.53) -- (116.80, 71.61);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 71.50) -- (116.80, 75.42);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.42) -- (116.80, 71.50);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.66) -- (116.80, 77.58);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.58) -- (116.80, 73.66);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 72.62) -- (116.80, 76.55);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.55) -- (116.80, 72.62);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 72.05) -- (116.80, 75.98);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.98) -- (116.80, 72.05);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.89) -- (116.80, 79.81);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 79.81) -- (116.80, 75.89);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.08) -- (116.80, 77.01);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.01) -- (116.80, 73.08);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 71.47) -- (116.80, 75.40);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.40) -- (116.80, 71.47);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 72.42) -- (116.80, 76.34);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.34) -- (116.80, 72.42);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.83) -- (116.80, 81.75);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 81.75) -- (116.80, 77.83);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.04) -- (116.80, 76.96);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.96) -- (116.80, 73.04);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.17) -- (116.80, 77.09);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.09) -- (116.80, 73.17);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 72.88) -- (116.80, 76.80);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.80) -- (116.80, 72.88);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.74) -- (116.80, 77.67);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.67) -- (116.80, 73.74);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.35) -- (116.80, 77.28);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.28) -- (116.80, 73.35);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.52) -- (116.80, 77.45);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.45) -- (116.80, 73.52);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 72.78) -- (116.80, 76.70);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.70) -- (116.80, 72.78);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.82) -- (116.80, 77.75);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.75) -- (116.80, 73.82);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.48) -- (116.80, 77.40);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.40) -- (116.80, 73.48);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.85) -- (116.80, 77.78);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.78) -- (116.80, 73.85);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 72.02) -- (116.80, 75.95);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.95) -- (116.80, 72.02);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 74.08) -- (116.80, 78.00);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.00) -- (116.80, 74.08);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.24) -- (116.80, 77.16);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.16) -- (116.80, 73.24);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.28) -- (116.80, 77.21);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.21) -- (116.80, 73.28);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.03) -- (116.80, 76.95);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.95) -- (116.80, 73.03);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.08) -- (116.80, 81.00);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 81.00) -- (116.80, 77.08);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 71.55) -- (116.80, 75.47);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.47) -- (116.80, 71.55);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 74.72) -- (116.80, 78.65);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.65) -- (116.80, 74.72);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 80.73) -- (116.80, 84.66);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 84.66) -- (116.80, 80.73);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 71.57) -- (116.80, 75.49);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.49) -- (116.80, 71.57);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 85.24) -- (116.80, 89.16);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 89.16) -- (116.80, 85.24);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 71.68) -- (116.80, 75.60);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.60) -- (116.80, 71.68);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 74.38) -- (116.80, 78.31);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.31) -- (116.80, 74.38);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 74.54) -- (116.80, 78.46);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.46) -- (116.80, 74.54);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.71) -- (116.80, 77.63);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.63) -- (116.80, 73.71);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 79.27) -- (116.80, 83.19);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 83.19) -- (116.80, 79.27);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 72.00) -- (116.80, 75.93);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.93) -- (116.80, 72.00);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.60) -- (116.80, 81.53);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 81.53) -- (116.80, 77.60);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 85.13) -- (116.80, 89.06);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 89.06) -- (116.80, 85.13);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 72.58) -- (116.80, 76.50);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.50) -- (116.80, 72.58);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.33) -- (116.80, 77.25);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.25) -- (116.80, 73.33);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 81.97) -- (116.80, 85.89);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 85.89) -- (116.80, 81.97);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 71.96) -- (116.80, 75.89);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.89) -- (116.80, 71.96);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.11) -- (116.80, 81.03);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 81.03) -- (116.80, 77.11);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 97.62) -- (116.80,101.54);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87,101.54) -- (116.80, 97.62);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 98.71) -- (116.80,102.64);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87,102.64) -- (116.80, 98.71);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 95.64) -- (116.80, 99.56);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 99.56) -- (116.80, 95.64);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.08) -- (116.80, 80.01);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 80.01) -- (116.80, 76.08);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 74.91) -- (116.80, 78.83);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.83) -- (116.80, 74.91);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 72.31) -- (116.80, 76.23);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.23) -- (116.80, 72.31);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 72.31) -- (116.80, 76.23);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.23) -- (116.80, 72.31);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 72.63) -- (116.80, 76.56);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.56) -- (116.80, 72.63);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 72.25) -- (116.80, 76.17);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.17) -- (116.80, 72.25);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 73.54) -- (116.80, 77.47);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.47) -- (116.80, 73.54);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 80.20) -- (116.80, 84.12);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 84.12) -- (116.80, 80.20);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.14) -- (116.80, 82.06);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 82.06) -- (116.80, 78.14);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 81.69) -- (116.80, 85.62);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 85.62) -- (116.80, 81.69);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.79) -- (116.80, 80.71);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 80.71) -- (116.80, 76.79);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.97) -- (116.80, 81.89);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 81.89) -- (116.80, 77.97);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 87.11) -- (116.80, 91.03);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 91.03) -- (116.80, 87.11);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 95.98) -- (116.80, 99.90);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 99.90) -- (116.80, 95.98);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 80.22) -- (116.80, 84.14);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 84.14) -- (116.80, 80.22);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 71.47) -- (116.80, 75.39);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.39) -- (116.80, 71.47);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 87.23) -- (116.80, 91.16);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 91.16) -- (116.80, 87.23);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 80.84) -- (116.80, 84.76);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 84.76) -- (116.80, 80.84);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.05) -- (116.80, 79.97);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 79.97) -- (116.80, 76.05);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 72.00) -- (116.80, 75.92);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.92) -- (116.80, 72.00);
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.01) -- (116.80, 78.93);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.93) -- (116.80, 75.01);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 74.68) -- (116.80, 78.60);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.60) -- (116.80, 74.68);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 79.12) -- (116.80, 83.05);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 83.05) -- (116.80, 79.12);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.22) -- (116.80, 80.15);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 80.15) -- (116.80, 76.22);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.54) -- (116.80, 80.46);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 80.46) -- (116.80, 76.54);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.20) -- (116.80, 82.12);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 82.12) -- (116.80, 78.20);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.08) -- (116.80, 79.00);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 79.00) -- (116.80, 75.08);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 74.11) -- (116.80, 78.03);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.03) -- (116.80, 74.11);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.26) -- (116.80, 80.19);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 80.19) -- (116.80, 76.26);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.17) -- (116.80, 79.10);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 79.10) -- (116.80, 75.17);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 74.58) -- (116.80, 78.50);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.50) -- (116.80, 74.58);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.60) -- (116.80, 82.53);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 82.53) -- (116.80, 78.60);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.66) -- (116.80, 79.58);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 79.58) -- (116.80, 75.66);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 74.96) -- (116.80, 78.89);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.89) -- (116.80, 74.96);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 80.63) -- (116.80, 84.56);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 84.56) -- (116.80, 80.63);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.61) -- (116.80, 79.54);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 79.54) -- (116.80, 75.61);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.75) -- (116.80, 79.67);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 79.67) -- (116.80, 75.75);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.44) -- (116.80, 79.36);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 79.36) -- (116.80, 75.44);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.35) -- (116.80, 80.27);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 80.27) -- (116.80, 76.35);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.94) -- (116.80, 79.87);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 79.87) -- (116.80, 75.94);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.12) -- (116.80, 80.05);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 80.05) -- (116.80, 76.12);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.34) -- (116.80, 79.26);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 79.26) -- (116.80, 75.34);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.44) -- (116.80, 80.36);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 80.36) -- (116.80, 76.44);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.07) -- (116.80, 80.00);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 80.00) -- (116.80, 76.07);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.47) -- (116.80, 80.39);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 80.39) -- (116.80, 76.47);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 74.55) -- (116.80, 78.47);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.47) -- (116.80, 74.55);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.70) -- (116.80, 80.63);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 80.63) -- (116.80, 76.70);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.82) -- (116.80, 79.74);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 79.74) -- (116.80, 75.82);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.87) -- (116.80, 79.79);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 79.79) -- (116.80, 75.87);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.60) -- (116.80, 79.52);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 79.52) -- (116.80, 75.60);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 79.85) -- (116.80, 83.77);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 83.77) -- (116.80, 79.85);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.38) -- (116.80, 81.30);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 81.30) -- (116.80, 77.38);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 83.68) -- (116.80, 87.61);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 87.61) -- (116.80, 83.68);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 88.40) -- (116.80, 92.33);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 92.33) -- (116.80, 88.40);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 74.19) -- (116.80, 78.11);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.11) -- (116.80, 74.19);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 74.48) -- (116.80, 78.41);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.41) -- (116.80, 74.48);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 79.88) -- (116.80, 83.81);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 83.81) -- (116.80, 79.88);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87,101.39) -- (116.80,105.31);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87,105.31) -- (116.80,101.39);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87,102.54) -- (116.80,106.46);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87,106.46) -- (116.80,102.54);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 99.31) -- (116.80,103.23);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87,103.23) -- (116.80, 99.31);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.81) -- (116.80, 82.73);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 82.73) -- (116.80, 78.81);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.57) -- (116.80, 81.50);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 81.50) -- (116.80, 77.57);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 74.85) -- (116.80, 78.77);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.77) -- (116.80, 74.85);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 74.84) -- (116.80, 78.77);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.77) -- (116.80, 74.84);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.19) -- (116.80, 79.11);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 79.11) -- (116.80, 75.19);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 74.78) -- (116.80, 78.70);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.70) -- (116.80, 74.78);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.14) -- (116.80, 80.06);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 80.06) -- (116.80, 76.14);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 83.12) -- (116.80, 87.04);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 87.04) -- (116.80, 83.12);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 80.96) -- (116.80, 84.89);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 84.89) -- (116.80, 80.96);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 84.69) -- (116.80, 88.61);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 88.61) -- (116.80, 84.69);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 79.54) -- (116.80, 83.47);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 83.47) -- (116.80, 79.54);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 80.78) -- (116.80, 84.71);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 84.71) -- (116.80, 80.78);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 90.37) -- (116.80, 94.29);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 94.29) -- (116.80, 90.37);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 99.67) -- (116.80,103.59);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87,103.59) -- (116.80, 99.67);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 83.14) -- (116.80, 87.07);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 87.07) -- (116.80, 83.14);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 90.50) -- (116.80, 94.42);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 94.42) -- (116.80, 90.50);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 83.79) -- (116.80, 87.71);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 87.71) -- (116.80, 83.79);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.77) -- (116.80, 82.70);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 82.70) -- (116.80, 78.77);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 74.52) -- (116.80, 78.45);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.45) -- (116.80, 74.52);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 74.78) -- (116.80, 78.71);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.71) -- (116.80, 74.78);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.33) -- (116.80, 79.25);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 79.25) -- (116.80, 75.33);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.24) -- (116.80, 82.17);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 82.17) -- (116.80, 78.24);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.25) -- (116.80, 79.18);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 79.18) -- (116.80, 75.25);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.55) -- (116.80, 79.48);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 79.48) -- (116.80, 75.55);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.18) -- (116.80, 79.11);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 79.11) -- (116.80, 75.18);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.22) -- (116.80, 82.14);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 82.14) -- (116.80, 78.22);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 77.74) -- (116.80, 81.67);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 81.67) -- (116.80, 77.74);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 75.24) -- (116.80, 79.16);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 79.16) -- (116.80, 75.24);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 85.15) -- (116.80, 89.07);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 89.07) -- (116.80, 85.15);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 76.03) -- (116.80, 79.96);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 79.96) -- (116.80, 76.03);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.69) -- (116.80, 82.61);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 82.61) -- (116.80, 78.69);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 91.15) -- (116.80, 95.08);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 95.08) -- (116.80, 91.15);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 78.15) -- (116.80, 82.08);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (112.87, 82.08) -- (116.80, 78.15);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (114.84, 58.20) -- (114.84, 73.24);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (114.84, 48.16) -- (114.84, 34.20);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (107.18, 58.20) --
-	(107.18, 48.16) --
-	(122.50, 48.16) --
-	(122.50, 58.20) --
-	(107.18, 58.20) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] (114.84, 60.05) -- (114.84, 76.03);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (114.84, 49.37) -- (114.84, 34.20);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (107.18, 60.05) --
+	(107.18, 49.37) --
+	(122.50, 49.37) --
+	(122.50, 60.05) --
+	(107.18, 60.05) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (107.18, 53.11) -- (122.50, 53.11);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (107.18, 54.57) -- (122.50, 54.57);
 \definecolor{drawColor}{RGB}{51,51,51}
 
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 79.03) -- (137.23, 82.96);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.96) -- (137.23, 79.03);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.81) -- (137.23, 86.73);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 86.73) -- (137.23, 82.81);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.76) -- (137.23, 84.68);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.68) -- (137.23, 80.76);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.46) -- (137.23, 84.39);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.39) -- (137.23, 80.46);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 77.23) -- (137.23, 81.16);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.16) -- (137.23, 77.23);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 76.48) -- (137.23, 80.40);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.40) -- (137.23, 76.48);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 76.86) -- (137.23, 80.78);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.78) -- (137.23, 76.86);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 77.23) -- (137.23, 81.15);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.15) -- (137.23, 77.23);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 78.16) -- (137.23, 82.09);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.09) -- (137.23, 78.16);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 77.85) -- (137.23, 81.78);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.78) -- (137.23, 77.85);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.66) -- (137.23, 86.58);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 86.58) -- (137.23, 82.66);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 77.03) -- (137.23, 80.95);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.95) -- (137.23, 77.03);
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.90) -- (137.23, 85.82);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 85.82) -- (137.23, 81.90);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 85.85) -- (137.23, 89.78);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 89.78) -- (137.23, 85.85);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.71) -- (137.23, 87.63);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 87.63) -- (137.23, 83.71);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.40) -- (137.23, 87.32);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 87.32) -- (137.23, 83.40);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.01) -- (137.23, 83.94);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.94) -- (137.23, 80.01);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 79.22) -- (137.23, 83.14);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.14) -- (137.23, 79.22);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 79.62) -- (137.23, 83.54);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.54) -- (137.23, 79.62);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.00) -- (137.23, 83.93);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.93) -- (137.23, 80.00);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.99) -- (137.23, 84.91);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.91) -- (137.23, 80.99);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.66) -- (137.23, 84.59);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.59) -- (137.23, 80.66);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 85.70) -- (137.23, 89.63);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 89.63) -- (137.23, 85.70);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 79.80) -- (137.23, 83.72);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.72) -- (137.23, 79.80);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.22) -- (137.23, 86.14);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 86.14) -- (137.23, 82.22);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.11) -- (137.23, 86.03);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 86.03) -- (137.23, 82.11);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.35) -- (137.23, 85.27);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 85.27) -- (137.23, 81.35);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 79.30) -- (137.23, 83.22);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.22) -- (137.23, 79.30);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.80) -- (137.23, 84.72);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.72) -- (137.23, 80.80);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.34) -- (137.23, 85.26);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 85.26) -- (137.23, 81.34);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 79.00) -- (137.23, 82.92);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.92) -- (137.23, 79.00);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.74) -- (137.23, 87.66);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 87.66) -- (137.23, 83.74);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.59) -- (137.23, 84.52);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.52) -- (137.23, 80.59);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.24) -- (137.23, 85.17);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 85.17) -- (137.23, 81.24);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.54) -- (137.23, 88.46);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 88.46) -- (137.23, 84.54);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.15) -- (137.23, 84.07);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.07) -- (137.23, 80.15);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.16) -- (137.23, 88.09);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 88.09) -- (137.23, 84.16);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.30) -- (137.23, 88.22);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 88.22) -- (137.23, 84.30);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 86.10) -- (137.23, 90.02);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 90.02) -- (137.23, 86.10);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.17) -- (137.23, 88.10);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 88.10) -- (137.23, 84.17);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.23) -- (137.23, 88.16);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 88.16) -- (137.23, 84.23);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.45) -- (137.23, 84.38);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.38) -- (137.23, 80.45);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.91) -- (137.23, 88.83);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 88.83) -- (137.23, 84.91);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.89) -- (137.23, 86.81);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 86.81) -- (137.23, 82.89);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.69) -- (137.23, 84.62);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.62) -- (137.23, 80.69);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 79.28) -- (137.23, 83.20);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.20) -- (137.23, 79.28);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.04) -- (137.23, 84.96);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.96) -- (137.23, 81.04);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.84) -- (137.23, 87.76);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 87.76) -- (137.23, 83.84);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.59) -- (137.23, 87.52);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 87.52) -- (137.23, 83.59);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 85.87) -- (137.23, 89.79);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 89.79) -- (137.23, 85.87);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.89) -- (137.23, 84.81);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.81) -- (137.23, 80.89);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.03) -- (137.23, 85.95);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 85.95) -- (137.23, 82.03);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.98) -- (137.23, 84.90);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.90) -- (137.23, 80.98);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.16) -- (137.23, 87.08);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 87.08) -- (137.23, 83.16);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.90) -- (137.23, 85.83);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 85.83) -- (137.23, 81.90);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.74) -- (137.23, 85.66);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 85.66) -- (137.23, 81.74);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 79.12) -- (137.23, 83.05);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.05) -- (137.23, 79.12);
 
@@
 
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 79.23) -- (137.23, 83.16);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.16) -- (137.23, 79.23);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 78.51) -- (137.23, 82.43);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.43) -- (137.23, 78.51);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 76.55) -- (137.23, 80.48);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.48) -- (137.23, 76.55);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 77.98) -- (137.23, 81.91);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.91) -- (137.23, 77.98);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 78.50) -- (137.23, 82.42);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.42) -- (137.23, 78.50);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.79) -- (137.23, 84.71);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.71) -- (137.23, 80.79);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 77.79) -- (137.23, 81.71);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.71) -- (137.23, 77.79);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 78.41) -- (137.23, 82.33);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.33) -- (137.23, 78.41);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.55) -- (137.23, 85.47);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 85.47) -- (137.23, 81.55);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 77.37) -- (137.23, 81.29);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.29) -- (137.23, 77.37);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.19) -- (137.23, 85.12);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 85.12) -- (137.23, 81.19);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.32) -- (137.23, 85.24);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 85.24) -- (137.23, 81.32);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.04) -- (137.23, 86.96);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 86.96) -- (137.23, 83.04);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.20) -- (137.23, 85.13);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 85.13) -- (137.23, 81.20);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.26) -- (137.23, 85.18);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 85.18) -- (137.23, 81.26);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 77.66) -- (137.23, 81.58);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.58) -- (137.23, 77.66);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.90) -- (137.23, 85.83);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 85.83) -- (137.23, 81.90);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 79.97) -- (137.23, 83.90);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.90) -- (137.23, 79.97);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 77.88) -- (137.23, 81.81);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.81) -- (137.23, 77.88);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 76.54) -- (137.23, 80.46);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.46) -- (137.23, 76.54);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 78.21) -- (137.23, 82.14);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.14) -- (137.23, 78.21);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.88) -- (137.23, 84.81);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.81) -- (137.23, 80.88);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.65) -- (137.23, 84.57);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.57) -- (137.23, 80.65);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.82) -- (137.23, 86.74);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 86.74) -- (137.23, 82.82);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 78.07) -- (137.23, 81.99);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.99) -- (137.23, 78.07);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 79.16) -- (137.23, 83.08);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.08) -- (137.23, 79.16);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 78.16) -- (137.23, 82.08);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.08) -- (137.23, 78.16);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.23) -- (137.23, 84.16);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.16) -- (137.23, 80.23);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 79.04) -- (137.23, 82.96);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.96) -- (137.23, 79.04);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 78.88) -- (137.23, 82.80);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.80) -- (137.23, 78.88);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 76.59) -- (137.23, 80.51);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.51) -- (137.23, 76.59);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 79.28) -- (137.23, 83.21);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.21) -- (137.23, 79.28);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 78.28) -- (137.23, 82.20);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.20) -- (137.23, 78.28);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 77.75) -- (137.23, 81.68);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.68) -- (137.23, 77.75);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 76.82) -- (137.23, 80.74);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.74) -- (137.23, 76.82);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 95.70) -- (137.23, 99.63);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 99.63) -- (137.23, 95.70);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.74) -- (137.23, 84.66);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.66) -- (137.23, 80.74);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 78.53) -- (137.23, 82.45);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.45) -- (137.23, 78.53);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.25) -- (137.23, 84.18);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.18) -- (137.23, 80.25);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 92.97) -- (137.23, 96.90);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 96.90) -- (137.23, 92.97);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 89.45) -- (137.23, 93.38);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 93.38) -- (137.23, 89.45);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 87.02) -- (137.23, 90.94);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 90.94) -- (137.23, 87.02);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.62) -- (137.23, 88.55);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 88.55) -- (137.23, 84.62);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 86.91) -- (137.23, 90.83);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 90.83) -- (137.23, 86.91);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.65) -- (137.23, 87.58);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 87.58) -- (137.23, 83.65);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 88.14) -- (137.23, 92.07);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 92.07) -- (137.23, 88.14);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 78.39) -- (137.23, 82.32);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.32) -- (137.23, 78.39);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.95) -- (137.23, 85.87);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 85.87) -- (137.23, 81.95);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 88.45) -- (137.23, 92.37);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 92.37) -- (137.23, 88.45);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 86.38) -- (137.23, 90.30);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 90.30) -- (137.23, 86.38);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.75) -- (137.23, 84.67);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.67) -- (137.23, 80.75);
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.16) -- (137.23, 86.09);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 86.09) -- (137.23, 82.16);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.11) -- (137.23, 85.03);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 85.03) -- (137.23, 81.11);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.56) -- (137.23, 84.48);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.48) -- (137.23, 80.56);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 79.58) -- (137.23, 83.50);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.50) -- (137.23, 79.58);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 99.38) -- (137.23,103.31);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30,103.31) -- (137.23, 99.38);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 79.19) -- (137.23, 83.11);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.11) -- (137.23, 79.19);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.70) -- (137.23, 87.62);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 87.62) -- (137.23, 83.70);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 85.69) -- (137.23, 89.61);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 89.61) -- (137.23, 85.69);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.63) -- (137.23, 87.56);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 87.56) -- (137.23, 83.63);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 79.84) -- (137.23, 83.76);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.76) -- (137.23, 79.84);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 86.14) -- (137.23, 90.06);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 90.06) -- (137.23, 86.14);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.55) -- (137.23, 87.47);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 87.47) -- (137.23, 83.55);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.12) -- (137.23, 87.04);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 87.04) -- (137.23, 83.12);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.23) -- (137.23, 85.15);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 85.15) -- (137.23, 81.23);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 85.67) -- (137.23, 89.59);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 89.59) -- (137.23, 85.67);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.56) -- (137.23, 85.49);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 85.49) -- (137.23, 81.56);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.35) -- (137.23, 84.28);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.28) -- (137.23, 80.35);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 90.09) -- (137.23, 94.01);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 94.01) -- (137.23, 90.09);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 79.84) -- (137.23, 83.77);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.77) -- (137.23, 79.84);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 81.70) -- (137.23, 85.63);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 85.63) -- (137.23, 81.70);
 
@@
 \path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 86.57) -- (137.23, 82.65);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.69) -- (137.23, 84.61);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.61) -- (137.23, 80.69);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 77.07) -- (137.23, 80.99);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.99) -- (137.23, 77.07);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 83.07) -- (137.23, 87.00);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 87.00) -- (137.23, 83.07);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.61) -- (137.23, 84.53);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.53) -- (137.23, 80.61);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 80.19) -- (137.23, 84.12);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 84.12) -- (137.23, 80.19);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 78.39) -- (137.23, 82.32);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.32) -- (137.23, 78.39);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 82.63) -- (137.23, 86.55);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (133.30, 86.55) -- (137.23, 82.63);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (135.26, 61.60) -- (135.26, 78.41);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (135.26, 50.39) -- (135.26, 35.20);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (127.60, 61.60) --
-	(127.60, 50.39) --
-	(142.92, 50.39) --
-	(142.92, 61.60) --
-	(127.60, 61.60) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] (135.26, 63.50) -- (135.26, 80.88);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (135.26, 51.90) -- (135.26, 35.59);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (127.60, 63.50) --
+	(127.60, 51.90) --
+	(142.92, 51.90) --
+	(142.92, 63.50) --
+	(127.60, 63.50) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (127.60, 56.00) -- (142.92, 56.00);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (127.60, 57.67) -- (142.92, 57.67);
 \definecolor{drawColor}{RGB}{51,51,51}
 
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 81.78) -- (157.65, 85.71);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.71) -- (157.65, 81.78);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 82.35) -- (157.65, 86.27);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.27) -- (157.65, 82.35);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.59) -- (157.65, 91.52);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.52) -- (157.65, 87.59);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 80.62) -- (157.65, 84.55);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.55) -- (157.65, 80.62);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 83.17) -- (157.65, 87.09);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.09) -- (157.65, 83.17);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 80.47) -- (157.65, 84.39);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.39) -- (157.65, 80.47);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.88) -- (157.65, 90.81);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.81) -- (157.65, 86.88);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.54) -- (157.65, 88.47);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.47) -- (157.65, 84.54);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.09) -- (157.65, 91.01);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.01) -- (157.65, 87.09);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 82.58) -- (157.65, 86.51);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.51) -- (157.65, 82.58);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.17) -- (157.65, 90.09);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.09) -- (157.65, 86.17);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.00) -- (157.65, 89.93);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.93) -- (157.65, 86.00);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 81.62) -- (157.65, 85.54);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.54) -- (157.65, 81.62);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.72) -- (157.65, 93.64);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 93.64) -- (157.65, 89.72);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.29) -- (157.65, 88.21);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.21) -- (157.65, 84.29);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 83.16) -- (157.65, 87.08);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.08) -- (157.65, 83.16);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 80.29) -- (157.65, 84.22);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.22) -- (157.65, 80.29);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.11) -- (157.65, 94.04);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 94.04) -- (157.65, 90.11);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 83.43) -- (157.65, 87.35);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.35) -- (157.65, 83.43);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 83.00) -- (157.65, 86.93);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.93) -- (157.65, 83.00);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 83.28) -- (157.65, 87.20);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.20) -- (157.65, 83.28);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.21) -- (157.65, 91.14);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.14) -- (157.65, 87.21);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 82.19) -- (157.65, 86.12);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.12) -- (157.65, 82.19);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 81.84) -- (157.65, 85.77);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.77) -- (157.65, 81.84);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 80.45) -- (157.65, 84.37);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.37) -- (157.65, 80.45);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 81.89) -- (157.65, 85.82);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.82) -- (157.65, 81.89);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 82.26) -- (157.65, 86.19);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.19) -- (157.65, 82.26);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.31) -- (157.65, 89.24);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.24) -- (157.65, 85.31);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 81.59) -- (157.65, 85.52);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.52) -- (157.65, 81.59);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 81.56) -- (157.65, 85.49);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.49) -- (157.65, 81.56);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 81.36) -- (157.65, 85.29);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.29) -- (157.65, 81.36);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 81.54) -- (157.65, 85.47);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.47) -- (157.65, 81.54);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.87) -- (157.65, 89.79);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.79) -- (157.65, 85.87);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 83.63) -- (157.65, 87.55);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.55) -- (157.65, 83.63);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 81.11) -- (157.65, 85.03);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.03) -- (157.65, 81.11);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.05) -- (157.65, 88.97);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.97) -- (157.65, 85.05);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.98) -- (157.65, 89.90);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.90) -- (157.65, 85.98);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 83.50) -- (157.65, 87.43);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.43) -- (157.65, 83.50);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 83.91) -- (157.65, 87.84);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.84) -- (157.65, 83.91);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 83.23) -- (157.65, 87.15);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.15) -- (157.65, 83.23);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.91) -- (157.65, 89.83);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.83) -- (157.65, 85.91);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 80.19) -- (157.65, 84.11);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.11) -- (157.65, 80.19);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 81.21) -- (157.65, 85.14);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.14) -- (157.65, 81.21);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 83.88) -- (157.65, 87.80);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.80) -- (157.65, 83.88);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 81.78) -- (157.65, 85.71);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.71) -- (157.65, 81.78);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 83.05) -- (157.65, 86.97);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.97) -- (157.65, 83.05);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 81.54) -- (157.65, 85.46);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.46) -- (157.65, 81.54);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.33) -- (157.65, 90.25);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.25) -- (157.65, 86.33);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 82.99) -- (157.65, 86.91);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.91) -- (157.65, 82.99);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.06) -- (157.65, 91.99);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.99) -- (157.65, 88.06);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.96) -- (157.65, 89.89);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.89) -- (157.65, 85.96);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.79) -- (157.65, 88.72);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.72) -- (157.65, 84.79);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 82.99) -- (157.65, 86.91);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.91) -- (157.65, 82.99);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 82.51) -- (157.65, 86.44);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.44) -- (157.65, 82.51);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 80.26) -- (157.65, 84.18);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.18) -- (157.65, 80.26);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.22) -- (157.65, 90.14);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.14) -- (157.65, 86.22);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.77) -- (157.65, 88.69);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.69) -- (157.65, 84.77);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.14) -- (157.65, 91.07);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.07) -- (157.65, 87.14);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 82.54) -- (157.65, 86.46);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.46) -- (157.65, 82.54);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.43) -- (157.65, 88.36);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.36) -- (157.65, 84.43);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 82.01) -- (157.65, 85.93);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.93) -- (157.65, 82.01);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 83.55) -- (157.65, 87.47);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.47) -- (157.65, 83.55);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 81.19) -- (157.65, 85.12);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.12) -- (157.65, 81.19);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 97.06) -- (157.65,100.99);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,100.99) -- (157.65, 97.06);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.13) -- (157.65, 90.06);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.06) -- (157.65, 86.13);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 82.28) -- (157.65, 86.21);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.21) -- (157.65, 82.28);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.75) -- (157.65, 88.68);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.68) -- (157.65, 84.75);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.14) -- (157.65, 90.06);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.06) -- (157.65, 86.14);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 81.35) -- (157.65, 85.28);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.28) -- (157.65, 81.35);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 92.83) -- (157.65, 96.76);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 96.76) -- (157.65, 92.83);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 80.59) -- (157.65, 84.52);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.52) -- (157.65, 80.59);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.31) -- (157.65, 92.24);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 92.24) -- (157.65, 88.31);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 82.55) -- (157.65, 86.47);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.47) -- (157.65, 82.55);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 80.29) -- (157.65, 84.21);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.21) -- (157.65, 80.29);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.09) -- (157.65, 91.01);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.01) -- (157.65, 87.09);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.15) -- (157.65, 88.08);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.08) -- (157.65, 84.15);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.67) -- (157.65, 90.59);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.59) -- (157.65, 86.67);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 80.85) -- (157.65, 84.77);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.77) -- (157.65, 80.85);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 83.53) -- (157.65, 87.45);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.45) -- (157.65, 83.53);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 97.62) -- (157.65,101.54);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,101.54) -- (157.65, 97.62);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.09) -- (157.65, 95.02);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 95.02) -- (157.65, 91.09);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 82.34) -- (157.65, 86.27);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.27) -- (157.65, 82.34);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 98.06) -- (157.65,101.98);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,101.98) -- (157.65, 98.06);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,101.49) -- (157.65,105.41);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,105.41) -- (157.65,101.49);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,102.54) -- (157.65,106.46);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,106.46) -- (157.65,102.54);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,101.45) -- (157.65,105.38);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,105.38) -- (157.65,101.45);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,101.49) -- (157.65,105.41);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,105.41) -- (157.65,101.49);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,101.47) -- (157.65,105.40);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,105.40) -- (157.65,101.47);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,101.45) -- (157.65,105.37);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,105.37) -- (157.65,101.45);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.30) -- (157.65, 95.22);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 95.22) -- (157.65, 91.30);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.28) -- (157.65, 93.21);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 93.21) -- (157.65, 89.28);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.70) -- (157.65, 93.63);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 93.63) -- (157.65, 89.70);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.70) -- (157.65, 89.62);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.62) -- (157.65, 85.70);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.38) -- (157.65, 91.31);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.31) -- (157.65, 87.38);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 81.67) -- (157.65, 85.60);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.60) -- (157.65, 81.67);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 81.50) -- (157.65, 85.43);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.43) -- (157.65, 81.50);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 83.62) -- (157.65, 87.54);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.54) -- (157.65, 83.62);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 82.50) -- (157.65, 86.42);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.42) -- (157.65, 82.50);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.21) -- (157.65, 88.13);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.13) -- (157.65, 84.21);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 80.24) -- (157.65, 84.17);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.17) -- (157.65, 80.24);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.98) -- (157.65, 91.91);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.91) -- (157.65, 87.98);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 80.70) -- (157.65, 84.62);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.62) -- (157.65, 80.70);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 93.44) -- (157.65, 97.37);
-
-\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 97.37) -- (157.65, 93.44);
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.78) -- (157.65, 88.71);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.71) -- (157.65, 84.78);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.38) -- (157.65, 89.30);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.30) -- (157.65, 85.38);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.88) -- (157.65, 94.80);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 94.80) -- (157.65, 90.88);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.24) -- (157.65, 90.16);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.16) -- (157.65, 86.24);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.13) -- (157.65, 94.06);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 94.06) -- (157.65, 90.13);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.67) -- (157.65, 91.60);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.60) -- (157.65, 87.67);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.35) -- (157.65, 94.27);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 94.27) -- (157.65, 90.35);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.62) -- (157.65, 89.55);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.55) -- (157.65, 85.62);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.38) -- (157.65, 93.30);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 93.30) -- (157.65, 89.38);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.21) -- (157.65, 93.13);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 93.13) -- (157.65, 89.21);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.61) -- (157.65, 88.53);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.53) -- (157.65, 84.61);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 93.10) -- (157.65, 97.03);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 97.03) -- (157.65, 93.10);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.41) -- (157.65, 91.33);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.33) -- (157.65, 87.41);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.23) -- (157.65, 90.15);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.15) -- (157.65, 86.23);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 93.52) -- (157.65, 97.44);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 97.44) -- (157.65, 93.52);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.51) -- (157.65, 90.43);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.43) -- (157.65, 86.51);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.06) -- (157.65, 89.98);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.98) -- (157.65, 86.06);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.35) -- (157.65, 90.28);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.28) -- (157.65, 86.35);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.48) -- (157.65, 94.40);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 94.40) -- (157.65, 90.48);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.21) -- (157.65, 89.14);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.14) -- (157.65, 85.21);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.84) -- (157.65, 88.77);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.77) -- (157.65, 84.84);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.90) -- (157.65, 88.82);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.82) -- (157.65, 84.90);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.29) -- (157.65, 89.21);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.21) -- (157.65, 85.29);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.48) -- (157.65, 92.41);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 92.41) -- (157.65, 88.48);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.59) -- (157.65, 88.51);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.51) -- (157.65, 84.59);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.55) -- (157.65, 88.47);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.47) -- (157.65, 84.55);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.34) -- (157.65, 88.27);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.27) -- (157.65, 84.34);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.53) -- (157.65, 88.45);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.45) -- (157.65, 84.53);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.07) -- (157.65, 92.99);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 92.99) -- (157.65, 89.07);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.71) -- (157.65, 90.64);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.64) -- (157.65, 86.71);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.08) -- (157.65, 88.00);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.00) -- (157.65, 84.08);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.21) -- (157.65, 92.13);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 92.13) -- (157.65, 88.21);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.18) -- (157.65, 93.10);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 93.10) -- (157.65, 89.18);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.59) -- (157.65, 90.51);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.51) -- (157.65, 86.59);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.02) -- (157.65, 90.94);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.94) -- (157.65, 87.02);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.30) -- (157.65, 90.22);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.22) -- (157.65, 86.30);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.11) -- (157.65, 93.03);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 93.03) -- (157.65, 89.11);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.18) -- (157.65, 88.11);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.11) -- (157.65, 84.18);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.98) -- (157.65, 90.90);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.90) -- (157.65, 86.98);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.78) -- (157.65, 88.70);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.70) -- (157.65, 84.78);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.11) -- (157.65, 90.04);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.04) -- (157.65, 86.11);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.53) -- (157.65, 88.45);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.45) -- (157.65, 84.53);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.55) -- (157.65, 93.47);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 93.47) -- (157.65, 89.55);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.05) -- (157.65, 89.97);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.97) -- (157.65, 86.05);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.37) -- (157.65, 95.29);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 95.29) -- (157.65, 91.37);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.17) -- (157.65, 93.09);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 93.09) -- (157.65, 89.17);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.94) -- (157.65, 91.87);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.87) -- (157.65, 87.94);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.05) -- (157.65, 89.97);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.97) -- (157.65, 86.05);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.55) -- (157.65, 89.47);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.47) -- (157.65, 85.55);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.44) -- (157.65, 93.36);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 93.36) -- (157.65, 89.44);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.91) -- (157.65, 91.84);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.84) -- (157.65, 87.91);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.40) -- (157.65, 94.33);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 94.33) -- (157.65, 90.40);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.58) -- (157.65, 89.50);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.50) -- (157.65, 85.58);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.56) -- (157.65, 91.49);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.49) -- (157.65, 87.56);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.02) -- (157.65, 88.94);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.94) -- (157.65, 85.02);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.63) -- (157.65, 90.55);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.55) -- (157.65, 86.63);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.16) -- (157.65, 88.09);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.09) -- (157.65, 84.16);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,100.81) -- (157.65,104.73);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,104.73) -- (157.65,100.81);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.34) -- (157.65, 93.27);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 93.27) -- (157.65, 89.34);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.30) -- (157.65, 89.23);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.23) -- (157.65, 85.30);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.90) -- (157.65, 91.82);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.82) -- (157.65, 87.90);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.35) -- (157.65, 93.27);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 93.27) -- (157.65, 89.35);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.33) -- (157.65, 88.25);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.25) -- (157.65, 84.33);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 96.37) -- (157.65,100.29);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,100.29) -- (157.65, 96.37);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.63) -- (157.65, 95.55);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 95.55) -- (157.65, 91.63);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.59) -- (157.65, 89.51);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.51) -- (157.65, 85.59);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 94.76) -- (157.65, 98.69);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 98.69) -- (157.65, 94.76);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 92.65) -- (157.65, 96.57);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 96.57) -- (157.65, 92.65);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 93.09) -- (157.65, 97.01);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 97.01) -- (157.65, 93.09);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.89) -- (157.65, 92.81);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 92.81) -- (157.65, 88.89);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.65) -- (157.65, 94.58);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 94.58) -- (157.65, 90.65);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.67) -- (157.65, 88.59);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.59) -- (157.65, 84.67);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.49) -- (157.65, 88.41);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.41) -- (157.65, 84.49);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 86.70) -- (157.65, 90.63);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.63) -- (157.65, 86.70);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 85.53) -- (157.65, 89.46);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.46) -- (157.65, 85.53);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.33) -- (157.65, 91.25);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.25) -- (157.65, 87.33);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.28) -- (157.65, 95.21);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 95.21) -- (157.65, 91.28);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 97.01) -- (157.65,100.93);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73,100.93) -- (157.65, 97.01);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.04) -- (157.65, 93.97);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 93.97) -- (157.65, 90.04);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.39) -- (157.65, 93.32);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 93.32) -- (157.65, 89.39);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.59) -- (157.65, 92.51);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 92.51) -- (157.65, 88.59);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 89.22) -- (157.65, 93.15);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 93.15) -- (157.65, 89.22);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 92.53) -- (157.65, 96.45);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 96.45) -- (157.65, 92.53);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.87) -- (157.65, 91.79);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.79) -- (157.65, 87.87);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.38) -- (157.65, 95.30);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 95.30) -- (157.65, 91.38);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.33) -- (157.65, 92.25);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 92.25) -- (157.65, 88.33);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.83) -- (157.65, 92.75);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 92.75) -- (157.65, 88.83);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 87.10) -- (157.65, 91.03);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 91.03) -- (157.65, 87.10);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 90.05) -- (157.65, 93.98);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 93.98) -- (157.65, 90.05);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 84.87) -- (157.65, 88.79);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 88.79) -- (157.65, 84.87);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 93.27) -- (157.65, 97.19);
+
+\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] (153.73, 97.19) -- (157.65, 93.27);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (155.69, 64.76) -- (155.69, 82.12);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (155.69, 53.18) -- (155.69, 39.70);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (148.03, 64.76) --
-	(148.03, 53.18) --
-	(163.35, 53.18) --
-	(163.35, 64.76) --
-	(148.03, 64.76) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] (155.69, 67.06) -- (155.69, 85.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (155.69, 54.45) -- (155.69, 41.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (148.03, 67.06) --
+	(148.03, 54.45) --
+	(163.35, 54.45) --
+	(163.35, 67.06) --
+	(148.03, 67.06) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (148.03, 58.96) -- (163.35, 58.96);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (148.03, 60.57) -- (163.35, 60.57);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76, 46.61) {20};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76, 73.31) {40};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76,100.01) {60};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76, 47.95) {20};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76, 75.95) {40};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76,103.95) {60};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96, 49.64) --
-	( 31.71, 49.64);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96, 76.34) --
-	( 31.71, 76.34);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,103.05) --
-	( 31.71,103.05);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96, 50.98) --
+	( 31.71, 50.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96, 78.98) --
+	( 31.71, 78.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,106.99) --
+	( 31.71,106.99);
 \end{scope}

### 2020-05-15 text/paper2/line_plots.tex
Description of the experiments

@@
-% Created by tikzDevice version 0.12.3 on 2020-05-11 12:49:51
+% Created by tikzDevice version 0.12.3 on 2020-05-15 17:19:15
 % !TEX encoding = UTF-8 Unicode
@@
 \begin{scope}
-\path[clip] ( 31.71, 30.69) rectangle (145.35,108.01);
+\path[clip] ( 31.71, 30.69) rectangle (146.09,108.01);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 31.71, 30.69) rectangle (145.35,108.01);
+\path[fill=fillColor] ( 31.71, 30.69) rectangle (146.09,108.01);
 \definecolor{drawColor}{gray}{0.92}
@@
 \path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 46.03) --
-	(145.35, 46.03);
+	(146.09, 46.03);
 
 \path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 69.81) --
-	(145.35, 69.81);
+	(146.09, 69.81);
 
 \path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 93.59) --
-	(145.35, 93.59);
+	(146.09, 93.59);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 49.66, 30.69) --
-	( 49.66,108.01);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 49.77, 30.69) --
+	( 49.77,108.01);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 75.52, 30.69) --
-	( 75.52,108.01);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 75.80, 30.69) --
+	( 75.80,108.01);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (101.39, 30.69) --
-	(101.39,108.01);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (101.84, 30.69) --
+	(101.84,108.01);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (127.25, 30.69) --
-	(127.25,108.01);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (127.87, 30.69) --
+	(127.87,108.01);
 
 \path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71, 34.14) --
-	(145.35, 34.14);
+	(146.09, 34.14);
 
 \path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71, 57.92) --
-	(145.35, 57.92);
+	(146.09, 57.92);
 
 \path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71, 81.70) --
-	(145.35, 81.70);
+	(146.09, 81.70);
 
 \path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71,105.48) --
-	(145.35,105.48);
+	(146.09,105.48);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 36.72, 30.69) --
-	( 36.72,108.01);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 36.75, 30.69) --
+	( 36.75,108.01);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.59, 30.69) --
-	( 62.59,108.01);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.79, 30.69) --
+	( 62.79,108.01);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.46, 30.69) --
-	( 88.46,108.01);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.82, 30.69) --
+	( 88.82,108.01);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (114.32, 30.69) --
-	(114.32,108.01);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (114.85, 30.69) --
+	(114.85,108.01);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (140.19, 30.69) --
-	(140.19,108.01);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (140.89, 30.69) --
+	(140.89,108.01);
 \definecolor{drawColor}{RGB}{27,158,119}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 36.88, 34.20) --
-	( 37.03, 34.26) --
-	( 37.34, 34.43) --
-	( 37.76, 34.78) --
-	( 37.96, 34.89) --
-	( 39.21, 35.94) --
-	( 44.56, 37.96) --
-	( 44.72, 37.05) --
-	( 45.03, 37.14) --
-	( 47.07, 39.24) --
-	( 52.24, 42.35) --
-	( 52.40, 40.98) --
-	( 52.71, 41.86) --
-	( 60.08, 44.75) --
-	( 60.39, 44.97) --
-	( 67.76, 48.70) --
-	( 67.92, 47.86) --
-	( 68.07, 47.05) --
-	( 68.23, 47.32) --
-	( 68.85, 49.64) --
-	( 75.75, 52.22) --
-	( 83.44, 55.11) --
-	( 91.12, 58.33) --
-	( 98.80, 75.16) --
-	( 99.11, 59.59) --
-	( 99.73, 62.82) --
-	(130.00, 75.17) --
-	(130.62, 78.87) --
-	(140.19, 88.26);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 36.91, 34.22) --
+	( 37.07, 34.28) --
+	( 37.38, 34.45) --
+	( 37.80, 34.74) --
+	( 38.00, 34.74) --
+	( 39.25, 35.27) --
+	( 44.64, 37.45) --
+	( 44.80, 36.38) --
+	( 45.11, 37.84) --
+	( 47.17, 39.46) --
+	( 52.37, 41.24) --
+	( 52.53, 41.31) --
+	( 52.84, 41.51) --
+	( 60.26, 45.33) --
+	( 60.58, 45.62) --
+	( 67.99, 50.08) --
+	( 68.15, 47.64) --
+	( 68.31, 50.15) --
+	( 68.46, 46.59) --
+	( 69.09, 54.70) --
+	( 76.04, 53.02) --
+	( 83.77, 56.41) --
+	( 91.50, 57.95) --
+	( 99.23, 74.63) --
+	( 99.55, 65.78) --
+	(100.17, 64.84) --
+	(130.63, 79.54) --
+	(131.26, 78.48) --
+	(140.89, 91.54);
 \definecolor{drawColor}{RGB}{217,95,2}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 36.88, 34.22) --
-	( 37.03, 34.33) --
-	( 37.34, 37.18) --
-	( 37.76, 37.64) --
-	( 37.96, 43.41) --
-	( 39.21, 42.20) --
-	( 44.56, 57.46) --
-	( 44.72, 36.84) --
-	( 45.03, 37.68) --
-	( 47.07, 40.19) --
-	( 52.24, 42.81) --
-	( 52.40, 41.77) --
-	( 52.71, 40.98) --
-	( 60.08, 45.16) --
-	( 60.39, 49.30) --
-	( 67.76, 47.31) --
-	( 67.92, 55.25) --
-	( 68.07, 48.59) --
-	( 68.23, 46.96) --
-	( 68.85, 47.72) --
-	( 75.75, 52.99) --
-	( 83.44, 57.55) --
-	( 91.12, 56.42) --
-	( 98.80, 71.23) --
-	( 99.11, 62.93) --
-	( 99.73, 67.49) --
-	(130.00, 79.80) --
-	(130.62, 85.06) --
-	(140.19, 91.20);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 36.91, 34.20) --
+	( 37.07, 34.26) --
+	( 37.38, 34.41) --
+	( 37.80, 34.70) --
+	( 38.00, 34.68) --
+	( 39.25, 35.23) --
+	( 44.64, 37.74) --
+	( 44.80, 37.05) --
+	( 45.11, 37.14) --
+	( 47.17, 39.19) --
+	( 52.37, 42.35) --
+	( 52.53, 40.98) --
+	( 52.84, 41.86) --
+	( 60.26, 44.75) --
+	( 60.58, 45.01) --
+	( 67.99, 48.70) --
+	( 68.15, 46.51) --
+	( 68.31, 47.05) --
+	( 68.46, 47.32) --
+	( 69.09, 49.64) --
+	( 76.04, 52.22) --
+	( 83.77, 55.11) --
+	( 91.50, 58.33) --
+	( 99.23, 75.16) --
+	( 99.55, 59.59) --
+	(100.17, 62.82) --
+	(130.63, 75.24) --
+	(131.26, 79.11) --
+	(140.89, 88.23);
 \definecolor{drawColor}{RGB}{117,112,179}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 36.88, 34.22) --
-	( 37.03, 34.29) --
-	( 37.34, 34.49) --
-	( 37.76, 34.88) --
-	( 37.96, 35.00) --
-	( 39.21, 36.19) --
-	( 44.56, 38.30) --
-	( 44.72, 37.18) --
-	( 45.03, 37.98) --
-	( 47.07, 40.27) --
-	( 52.24, 44.88) --
-	( 52.40, 42.06) --
-	( 52.71, 40.35) --
-	( 60.08, 45.65) --
-	( 60.39, 47.17) --
-	( 67.76, 51.25) --
-	( 67.92, 52.15) --
-	( 68.07, 51.25) --
-	( 68.23, 52.79) --
-	( 68.85, 51.87) --
-	( 75.75, 54.08) --
-	( 83.44, 57.97) --
-	( 91.12, 61.03) --
-	( 98.80, 76.47) --
-	( 99.11, 65.20) --
-	( 99.73, 59.83) --
-	(130.00, 84.23) --
-	(130.62, 85.33) --
-	(140.19, 99.28);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 36.91, 34.22) --
+	( 37.07, 34.33) --
+	( 37.38, 34.49) --
+	( 37.80, 34.77) --
+	( 38.00, 34.77) --
+	( 39.25, 35.37) --
+	( 44.64, 37.40) --
+	( 44.80, 36.84) --
+	( 45.11, 37.68) --
+	( 47.17, 39.58) --
+	( 52.37, 42.81) --
+	( 52.53, 41.77) --
+	( 52.84, 40.98) --
+	( 60.26, 45.16) --
+	( 60.58, 45.74) --
+	( 67.99, 47.31) --
+	( 68.15, 46.52) --
+	( 68.31, 48.59) --
+	( 68.46, 46.96) --
+	( 69.09, 47.72) --
+	( 76.04, 52.99) --
+	( 83.77, 57.55) --
+	( 91.50, 56.42) --
+	( 99.23, 71.23) --
+	( 99.55, 62.93) --
+	(100.17, 67.49) --
+	(130.63, 75.36) --
+	(131.26, 79.09) --
+	(140.89, 90.92);
 \definecolor{drawColor}{RGB}{231,41,138}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 36.88, 34.24) --
-	( 37.03, 34.31) --
-	( 37.34, 34.50) --
-	( 37.76, 34.90) --
-	( 37.96, 35.05) --
-	( 39.21, 36.07) --
-	( 44.56, 38.21) --
-	( 44.72, 38.54) --
-	( 45.03, 38.69) --
-	( 47.07, 40.00) --
-	( 52.24, 42.70) --
-	( 52.40, 41.93) --
-	( 52.71, 41.20) --
-	( 60.08, 46.14) --
-	( 60.39, 46.70) --
-	( 67.76, 50.70) --
-	( 67.92, 48.30) --
-	( 68.07, 50.28) --
-	( 68.23, 47.98) --
-	( 68.85, 52.07) --
-	( 75.75, 55.24) --
-	( 83.44, 59.51) --
-	( 91.12, 61.81) --
-	( 98.80, 82.15) --
-	( 99.11, 68.77) --
-	( 99.73, 67.98) --
-	(130.00, 80.96) --
-	(130.62, 80.15) --
-	(140.19, 97.28);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 36.91, 34.22) --
+	( 37.07, 34.29) --
+	( 37.38, 34.48) --
+	( 37.80, 34.79) --
+	( 38.00, 34.74) --
+	( 39.25, 35.45) --
+	( 44.64, 37.64) --
+	( 44.80, 37.18) --
+	( 45.11, 37.98) --
+	( 47.17, 40.20) --
+	( 52.37, 44.88) --
+	( 52.53, 42.06) --
+	( 52.84, 40.35) --
+	( 60.26, 45.65) --
+	( 60.58, 47.25) --
+	( 67.99, 51.25) --
+	( 68.15, 51.16) --
+	( 68.31, 51.25) --
+	( 68.46, 52.79) --
+	( 69.09, 51.87) --
+	( 76.04, 54.08) --
+	( 83.77, 57.97) --
+	( 91.50, 61.03) --
+	( 99.23, 76.47) --
+	( 99.55, 65.20) --
+	(100.17, 59.83) --
+	(130.63, 84.66) --
+	(131.26, 85.31) --
+	(140.89, 99.29);
 \definecolor{drawColor}{RGB}{102,166,30}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round] ( 36.88, 34.20) --
-	( 37.03, 34.32) --
-	( 37.34, 34.48) --
-	( 37.76, 34.84) --
-	( 37.96, 34.97) --
-	( 39.21, 35.75) --
-	( 44.56, 37.97) --
-	( 44.72, 36.07) --
-	( 45.03, 38.73) --
-	( 47.07, 40.22) --
-	( 52.24, 44.23) --
-	( 52.40, 43.29) --
-	( 52.71, 40.97) --
-	( 60.08, 46.70) --
-	( 60.39, 47.27) --
-	( 67.76, 50.76) --
-	( 67.92, 53.24) --
-	( 68.07, 51.86) --
-	( 68.23, 53.84) --
-	( 68.85, 51.03) --
-	( 75.75, 54.08) --
-	( 83.44, 59.44) --
-	( 91.12, 63.01) --
-	( 98.80, 79.72) --
-	( 99.11, 66.18) --
-	( 99.73, 66.97) --
-	(130.00, 83.43) --
-	(130.62, 87.45) --
-	(140.19, 98.97);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round] ( 36.91, 34.24) --
+	( 37.07, 34.31) --
+	( 37.38, 34.48) --
+	( 37.80, 34.81) --
+	( 38.00, 34.77) --
+	( 39.25, 35.45) --
+	( 44.64, 37.88) --
+	( 44.80, 38.54) --
+	( 45.11, 38.69) --
+	( 47.17, 39.95) --
+	( 52.37, 42.70) --
+	( 52.53, 41.93) --
+	( 52.84, 41.20) --
+	( 60.26, 46.14) --
+	( 60.58, 46.43) --
+	( 67.99, 50.70) --
+	( 68.15, 47.87) --
+	( 68.31, 50.28) --
+	( 68.46, 47.98) --
+	( 69.09, 52.07) --
+	( 76.04, 55.24) --
+	( 83.77, 59.51) --
+	( 91.50, 61.81) --
+	( 99.23, 82.15) --
+	( 99.55, 68.77) --
+	(100.17, 67.98) --
+	(130.63, 80.43) --
+	(131.26, 80.51) --
+	(140.89, 97.30);
 \definecolor{drawColor}{RGB}{230,171,2}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt on 4pt off 3pt ,line join=round] ( 36.88, 34.23) --
-	( 37.03, 34.28) --
-	( 37.34, 34.44) --
-	( 37.76, 34.80) --
-	( 37.96, 34.97) --
-	( 39.21, 36.01) --
-	( 44.56, 37.80) --
-	( 44.72, 36.11) --
-	( 45.03, 37.78) --
-	( 47.07, 39.38) --
-	( 52.24, 43.57) --
-	( 52.40, 41.73) --
-	( 52.71, 43.60) --
-	( 60.08, 45.48) --
-	( 60.39, 45.53) --
-	( 67.76, 46.06) --
-	( 67.92, 48.49) --
-	( 68.07, 47.82) --
-	( 68.23, 50.65) --
-	( 68.85, 47.58) --
-	( 75.75, 51.59) --
-	( 83.44, 56.58) --
-	( 91.12, 55.51) --
-	( 98.80, 75.37) --
-	( 99.11, 65.39) --
-	( 99.73, 59.41) --
-	(130.00, 80.88) --
-	(130.62, 80.85) --
-	(140.19, 91.13);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt on 4pt off 3pt ,line join=round] ( 36.91, 34.20) --
+	( 37.07, 34.32) --
+	( 37.38, 34.47) --
+	( 37.80, 34.80) --
+	( 38.00, 34.78) --
+	( 39.25, 35.44) --
+	( 44.64, 37.83) --
+	( 44.80, 36.07) --
+	( 45.11, 38.73) --
+	( 47.17, 40.20) --
+	( 52.37, 44.23) --
+	( 52.53, 43.29) --
+	( 52.84, 40.97) --
+	( 60.26, 46.70) --
+	( 60.58, 47.28) --
+	( 67.99, 50.76) --
+	( 68.15, 52.81) --
+	( 68.31, 51.86) --
+	( 68.46, 53.84) --
+	( 69.09, 51.03) --
+	( 76.04, 54.08) --
+	( 83.77, 59.44) --
+	( 91.50, 63.01) --
+	( 99.23, 79.72) --
+	( 99.55, 66.18) --
+	(100.17, 66.97) --
+	(130.63, 83.22) --
+	(131.26, 87.08) --
+	(140.89, 98.99);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.71, 30.69) rectangle (145.35,108.01);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.71, 30.69) rectangle (146.09,108.01);
 \end{scope}
 \begin{scope}
-\path[clip] (150.85, 30.69) rectangle (264.49,108.01);
+\path[clip] (151.59, 30.69) rectangle (265.96,108.01);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (150.85, 30.69) rectangle (264.49,108.01);
+\path[fill=fillColor] (151.59, 30.69) rectangle (265.96,108.01);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (150.85, 46.03) --
-	(264.49, 46.03);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (151.59, 46.03) --
+	(265.96, 46.03);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (150.85, 69.81) --
-	(264.49, 69.81);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (151.59, 69.81) --
+	(265.96, 69.81);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (150.85, 93.59) --
-	(264.49, 93.59);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (151.59, 93.59) --
+	(265.96, 93.59);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (168.93, 30.69) --
-	(168.93,108.01);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (169.78, 30.69) --
+	(169.78,108.01);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (194.76, 30.69) --
-	(194.76,108.01);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (195.78, 30.69) --
+	(195.78,108.01);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (220.59, 30.69) --
-	(220.59,108.01);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (221.77, 30.69) --
+	(221.77,108.01);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (246.42, 30.69) --
-	(246.42,108.01);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (247.77, 30.69) --
+	(247.77,108.01);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (150.85, 34.14) --
-	(264.49, 34.14);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (151.59, 34.14) --
+	(265.96, 34.14);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (150.85, 57.92) --
-	(264.49, 57.92);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (151.59, 57.92) --
+	(265.96, 57.92);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (150.85, 81.70) --
-	(264.49, 81.70);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (151.59, 81.70) --
+	(265.96, 81.70);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (150.85,105.48) --
-	(264.49,105.48);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (151.59,105.48) --
+	(265.96,105.48);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (156.02, 30.69) --
-	(156.02,108.01);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (156.79, 30.69) --
+	(156.79,108.01);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (181.85, 30.69) --
-	(181.85,108.01);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (182.78, 30.69) --
+	(182.78,108.01);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (207.67, 30.69) --
-	(207.67,108.01);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (208.77, 30.69) --
+	(208.77,108.01);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (233.50, 30.69) --
-	(233.50,108.01);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (234.77, 30.69) --
+	(234.77,108.01);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (259.33, 30.69) --
-	(259.33,108.01);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (260.76, 30.69) --
+	(260.76,108.01);
 \definecolor{drawColor}{RGB}{27,158,119}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (156.02, 82.69) --
-	(159.71, 86.86) --
-	(167.09, 90.51) --
-	(170.78, 84.86) --
-	(173.24, 90.95) --
-	(185.54, 87.17) --
-	(189.23, 82.10) --
-	(200.29, 86.31) --
-	(211.36, 91.58) --
-	(215.05, 82.04) --
-	(218.74, 87.00) --
-	(224.89, 82.36) --
-	(226.12, 81.20) --
-	(229.81, 82.46) --
-	(233.50, 88.61) --
-	(237.19, 93.14) --
-	(240.88, 91.31) --
-	(251.95, 83.85) --
-	(255.64, 86.37) --
-	(259.33, 89.25);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (156.79, 87.17) --
+	(160.50, 93.17) --
+	(167.93, 93.97) --
+	(171.64, 85.86) --
+	(174.11, 95.63) --
+	(186.49, 90.99) --
+	(190.21, 86.16) --
+	(201.35, 88.72) --
+	(212.49, 93.71) --
+	(216.20, 85.21) --
+	(219.91, 88.26) --
+	(226.10, 81.94) --
+	(227.34, 84.46) --
+	(231.05, 82.43) --
+	(234.77, 92.42) --
+	(238.48, 95.04) --
+	(242.19, 93.76) --
+	(253.34, 84.82) --
+	(257.05, 89.64) --
+	(260.76, 94.51);
 \definecolor{drawColor}{RGB}{217,95,2}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (156.02, 91.65) --
-	(159.71, 90.13) --
-	(167.09, 92.54) --
-	(170.78, 85.10) --
-	(173.24, 93.89) --
-	(185.54, 91.81) --
-	(189.23, 87.37) --
-	(200.29, 88.45) --
-	(211.36, 94.07) --
-	(215.05, 85.46) --
-	(218.74, 89.07) --
-	(224.89, 81.32) --
-	(226.12, 84.81) --
-	(229.81, 85.30) --
-	(233.50, 90.02) --
-	(237.19, 93.14) --
-	(240.88, 94.41) --
-	(251.95, 85.94) --
-	(255.64, 89.62) --
-	(259.33, 93.56);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (156.79, 81.98) --
+	(160.50, 87.03) --
+	(167.93, 90.51) --
+	(171.64, 84.86) --
+	(174.11, 90.95) --
+	(186.49, 87.07) --
+	(190.21, 82.10) --
+	(201.35, 86.31) --
+	(212.49, 91.58) --
+	(216.20, 81.17) --
+	(219.91, 86.92) --
+	(226.10, 82.36) --
+	(227.34, 81.20) --
+	(231.05, 82.46) --
+	(234.77, 88.61) --
+	(238.48, 93.14) --
+	(242.19, 91.31) --
+	(253.34, 83.85) --
+	(257.05, 86.37) --
+	(260.76, 89.25);
 \definecolor{drawColor}{RGB}{117,112,179}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (156.02, 96.40) --
-	(159.71, 96.07) --
-	(167.09,104.50) --
-	(170.78, 94.79) --
-	(173.24,102.91) --
-	(185.54,101.57) --
-	(189.23, 94.35) --
-	(200.29, 98.68) --
-	(211.36,103.55) --
-	(215.05, 88.61) --
-	(218.74, 97.59) --
-	(224.89, 89.92) --
-	(226.12, 91.22) --
-	(229.81, 87.06) --
-	(233.50, 98.75) --
-	(237.19,102.58) --
-	(240.88,102.50) --
-	(251.95, 90.37) --
-	(255.64, 96.15) --
-	(259.33,100.82);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (156.79, 88.97) --
+	(160.50, 89.35) --
+	(167.93, 92.54) --
+	(171.64, 85.10) --
+	(174.11, 93.89) --
+	(186.49, 90.38) --
+	(190.21, 87.37) --
+	(201.35, 88.45) --
+	(212.49, 94.07) --
+	(216.20, 82.90) --
+	(219.91, 88.35) --
+	(226.10, 81.32) --
+	(227.34, 84.81) --
+	(231.05, 85.30) --
+	(234.77, 90.02) --
+	(238.48, 93.14) --
+	(242.19, 94.41) --
+	(253.34, 85.94) --
+	(257.05, 89.62) --
+	(260.76, 93.56);
 \definecolor{drawColor}{RGB}{231,41,138}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (156.02, 90.92) --
-	(159.71,100.08) --
-	(167.09, 97.34) --
-	(170.78, 90.63) --
-	(173.24, 99.99) --
-	(185.54, 96.84) --
-	(189.23, 91.32) --
-	(200.29, 97.00) --
-	(211.36,100.90) --
-	(215.05, 88.00) --
-	(218.74, 94.45) --
-	(224.89, 92.66) --
-	(226.12, 90.99) --
-	(229.81, 92.19) --
-	(233.50, 96.98) --
-	(237.19, 99.26) --
-	(240.88,100.29) --
-	(251.95, 92.01) --
-	(255.64, 93.41) --
-	(259.33, 99.52);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (156.79, 95.74) --
+	(160.50, 96.35) --
+	(167.93,104.50) --
+	(171.64, 94.79) --
+	(174.11,102.91) --
+	(186.49,101.65) --
+	(190.21, 94.35) --
+	(201.35, 98.68) --
+	(212.49,103.55) --
+	(216.20, 88.20) --
+	(219.91, 97.47) --
+	(226.10, 89.92) --
+	(227.34, 91.22) --
+	(231.05, 87.06) --
+	(234.77, 98.75) --
+	(238.48,102.58) --
+	(242.19,102.50) --
+	(253.34, 90.37) --
+	(257.05, 96.15) --
+	(260.76,100.82);
 \definecolor{drawColor}{RGB}{102,166,30}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round] (156.02, 91.47) --
-	(159.71, 96.45) --
-	(167.09,104.39) --
-	(170.78, 90.59) --
-	(173.24,102.58) --
-	(185.54,100.46) --
-	(189.23, 95.50) --
-	(200.29, 97.48) --
-	(211.36,103.31) --
-	(215.05, 90.65) --
-	(218.74, 97.90) --
-	(224.89, 87.48) --
-	(226.12, 91.85) --
-	(229.81, 91.08) --
-	(233.50, 98.02) --
-	(237.19,100.29) --
-	(240.88,102.81) --
-	(251.95, 90.81) --
-	(255.64, 95.58) --
-	(259.33,101.07);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round] (156.79, 90.34) --
+	(160.50,100.33) --
+	(167.93, 97.34) --
+	(171.64, 90.63) --
+	(174.11, 99.99) --
+	(186.49, 96.75) --
+	(190.21, 91.32) --
+	(201.35, 97.00) --
+	(212.49,100.90) --
+	(216.20, 88.11) --
+	(219.91, 94.51) --
+	(226.10, 92.66) --
+	(227.34, 90.99) --
+	(231.05, 92.19) --
+	(234.77, 96.98) --
+	(238.48, 99.26) --
+	(242.19,100.29) --
+	(253.34, 92.01) --
+	(257.05, 93.41) --
+	(260.76, 99.52);
 \definecolor{drawColor}{RGB}{230,171,2}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt on 4pt off 3pt ,line join=round] (156.02, 81.98) --
-	(159.71, 88.47) --
-	(167.09, 93.40) --
-	(170.78, 85.56) --
-	(173.24, 94.47) --
-	(185.54, 91.91) --
-	(189.23, 83.83) --
-	(200.29, 92.87) --
-	(211.36, 94.86) --
-	(215.05, 82.23) --
-	(218.74, 90.48) --
-	(224.89, 86.23) --
-	(226.12, 82.27) --
-	(229.81, 80.81) --
-	(233.50, 91.75) --
-	(237.19, 92.55) --
-	(240.88, 93.28) --
-	(251.95, 85.59) --
-	(255.64, 87.94) --
-	(259.33, 93.81);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt on 4pt off 3pt ,line join=round] (156.79, 90.96) --
+	(160.50, 96.67) --
+	(167.93,104.39) --
+	(171.64, 90.59) --
+	(174.11,102.58) --
+	(186.49,100.48) --
+	(190.21, 95.50) --
+	(201.35, 97.48) --
+	(212.49,103.31) --
+	(216.20, 90.87) --
+	(219.91, 97.96) --
+	(226.10, 87.48) --
+	(227.34, 91.85) --
+	(231.05, 91.08) --
+	(234.77, 98.02) --
+	(238.48,100.29) --
+	(242.19,102.81) --
+	(253.34, 90.81) --
+	(257.05, 95.58) --
+	(260.76,101.07);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (150.85, 30.69) rectangle (264.49,108.01);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (151.59, 30.69) rectangle (265.96,108.01);
 \end{scope}
 \begin{scope}
-\path[clip] ( 31.71,108.01) rectangle (145.35,124.59);
+\path[clip] ( 31.71,108.01) rectangle (146.09,124.59);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,108.01) rectangle (145.35,124.59);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,108.01) rectangle (146.09,124.59);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 88.53,113.27) {The number of facts ($\times 10^3$)};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 88.90,113.27) {The number of facts ($\times 10^3$)};
 \end{scope}
 \begin{scope}
-\path[clip] (150.85,108.01) rectangle (264.49,124.59);
+\path[clip] (151.59,108.01) rectangle (265.96,124.59);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (150.85,108.01) rectangle (264.49,124.59);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (151.59,108.01) rectangle (265.96,124.59);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (207.67,113.27) {Proportion of independent pairs};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (208.77,113.27) {Proportion of independent pairs};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 36.72, 27.94) --
-	( 36.72, 30.69);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 36.75, 27.94) --
+	( 36.75, 30.69);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.59, 27.94) --
-	( 62.59, 30.69);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.79, 27.94) --
+	( 62.79, 30.69);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.46, 27.94) --
-	( 88.46, 30.69);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.82, 27.94) --
+	( 88.82, 30.69);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (114.32, 27.94) --
-	(114.32, 30.69);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (114.85, 27.94) --
+	(114.85, 30.69);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (140.19, 27.94) --
-	(140.19, 30.69);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (140.89, 27.94) --
+	(140.89, 30.69);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 36.72, 19.68) {0};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 36.75, 19.68) {0};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 62.59, 19.68) {25};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 62.79, 19.68) {25};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 88.46, 19.68) {50};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 88.82, 19.68) {50};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (114.32, 19.68) {75};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (114.85, 19.68) {75};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (140.19, 19.68) {100};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (140.89, 19.68) {100};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (156.02, 27.94) --
-	(156.02, 30.69);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (156.79, 27.94) --
+	(156.79, 30.69);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (181.85, 27.94) --
-	(181.85, 30.69);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (182.78, 27.94) --
+	(182.78, 30.69);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (207.67, 27.94) --
-	(207.67, 30.69);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (208.77, 27.94) --
+	(208.77, 30.69);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (233.50, 27.94) --
-	(233.50, 30.69);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (234.77, 27.94) --
+	(234.77, 30.69);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (259.33, 27.94) --
-	(259.33, 30.69);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (260.76, 27.94) --
+	(260.76, 30.69);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (156.02, 19.68) {0};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (156.79, 19.68) {0};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (181.85, 19.68) {0.25};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (182.78, 19.68) {0.25};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (207.67, 19.68) {0.5};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (208.77, 19.68) {0.5};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (233.50, 19.68) {0.75};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (234.77, 19.68) {0.75};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (259.33, 19.68) {1};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (260.76, 19.68) {1};
 \end{scope}
@@
 
-\path[fill=fillColor] (275.49, 12.88) rectangle (341.40,125.82);
+\path[fill=fillColor] (276.96, 12.88) rectangle (341.40,125.82);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at (280.99,111.67) {Algorithm};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.46,111.67) {Algorithm};
 \end{scope}
@@
 
-\path[fill=fillColor] (280.99, 90.65) rectangle (295.45,105.10);
+\path[fill=fillColor] (282.46, 90.65) rectangle (296.92,105.10);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (282.44, 97.88) -- (294.00, 97.88);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (283.91, 97.88) -- (295.47, 97.88);
 \end{scope}
@@
 
-\path[fill=fillColor] (280.99, 76.20) rectangle (295.45, 90.65);
+\path[fill=fillColor] (282.46, 76.20) rectangle (296.92, 90.65);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (282.44, 83.42) -- (294.00, 83.42);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (283.91, 83.42) -- (295.47, 83.42);
 \end{scope}
@@
 
-\path[fill=fillColor] (280.99, 61.74) rectangle (295.45, 76.20);
+\path[fill=fillColor] (282.46, 61.74) rectangle (296.92, 76.20);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (282.44, 68.97) -- (294.00, 68.97);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (283.91, 68.97) -- (295.47, 68.97);
 \end{scope}
@@
 
-\path[fill=fillColor] (280.99, 47.29) rectangle (295.45, 61.74);
+\path[fill=fillColor] (282.46, 47.29) rectangle (296.92, 61.74);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (282.44, 54.52) -- (294.00, 54.52);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (283.91, 54.52) -- (295.47, 54.52);
 \end{scope}
@@
 
-\path[fill=fillColor] (280.99, 32.83) rectangle (295.45, 47.29);
+\path[fill=fillColor] (282.46, 32.83) rectangle (296.92, 47.29);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round] (282.44, 40.06) -- (294.00, 40.06);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round] (283.91, 40.06) -- (295.47, 40.06);
 \end{scope}
@@
 
-\path[fill=fillColor] (280.99, 18.38) rectangle (295.45, 32.83);
+\path[fill=fillColor] (282.46, 18.38) rectangle (296.92, 32.83);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt on 4pt off 3pt ,line join=round] (282.44, 25.61) -- (294.00, 25.61);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt on 4pt off 3pt ,line join=round] (283.91, 25.61) -- (295.47, 25.61);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (300.95, 94.85) {dDNNF};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (302.42, 94.85) {BDD};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (300.95, 80.39) {K-Best};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (302.42, 80.39) {d-DNNF};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (300.95, 65.94) {NNF};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (302.42, 65.94) {K-Best};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (300.95, 51.49) {SDD};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (302.42, 51.49) {NNF};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (300.95, 37.03) {SDDX};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (302.42, 37.03) {SDD};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (300.95, 22.58) {Symbolic};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (302.42, 22.58) {SDDX};
 \end{scope}

### 2020-05-15 text/paper2/paper.tex
Description of the experiments

--- 2020-05-06 text/paper2/paper.tex
@@
 \usepackage{blkarray}
-\usepackage{siunitx}
+\usepackage[binary-units]{siunitx}
 \usepackage[inline]{enumitem}
@@
 \maketitle
-
-% TODO (for later)
-% 1) Use American English
-% 2) Avoid the Definition environment (to save space)
-
-% Empirical tasks:
-% 1) make the CP model faster: apply the redundant constraints to predicates
-% (not just variables). Check if everything works out.
-% 2) motivate either for benchmarking or by comparing parameter learning with
-% ProbFOIL
-% New things I could talk about:
-% 1) entailment for conditional independence
-% 2) the 'required formula' part of the model
 
@@
   independence with efficient propagation and entailment algorithms, allowing
-  one to generate programs that have a certain independence structure. To
-  generate valid probabilistic logic programs, we also present a new constraint
-  for negative cycle detection. Finally, we provide a combinatorial argument for
-  the correctness of the model and describe how the parameters of the model
-  affect the empirical difficulty of the program generation task.
+  one to generate programs that have a certain independence structure. Finally,
+  we provide a combinatorial argument for the correctness of the model and
+  describe how the parameters of the model affect the empirical difficulty of
+  the program generation task.
 
@@
 \end{abstract}
+% TODO: update the introduction and the abstract
 
@@
 generate-and-test approaches). As an example of this, we develop a custom
-constraint (with propagation and entailment algorithms) that, given two
-predicates $\mathsf{P}$ and $\mathsf{Q}$, ensures that any ground atom with
-predicate $\mathsf{P}$ is independent of any ground atom with predicate
-$\mathsf{Q}$. In this way, we can easily regulate the independence structure of
-the underlying probability distribution. We also present a combinatorial
-argument for correctness, counting the number of programs that the model
-produces for various parameter values and show how the model scales when tasked
-with producing more complicated programs.
-
-A common restriction put on both logic programs and probabilistic logic programs
-to ensure that there is a unique answer to every query is known as
-\emph{stratification}
-\cite{DBLP:journals/jlp/BalbinPRM91,DBLP:conf/padl/MantadelisR17}. We extend
-this idea to programs that have arbitrary well-formed formulas in clause bodies
-(as ProbLog supports this) and describe a custom constraint that ensures
-stratification by checking for negative cycles in the predicate dependency
-graph.
+constraint that, given two predicates $\mathsf{P}$ and $\mathsf{Q}$, ensures
+that any ground atom with predicate $\mathsf{P}$ is independent of any ground
+atom with predicate $\mathsf{Q}$. In this way, we can easily regulate the
+independence structure of the underlying probability distribution. We also
+present a combinatorial argument for correctness, counting the number of
+programs that the model produces for various parameter values and show how the
+model scales when tasked with producing more complicated programs.
 
@@
 A \emph{clause} is a pair of a \emph{head} (which is an atom) and a \emph{body}
-(which is a formula). A \emph{(logic) program} is a set of clauses. Given a
-program $\mathscr{P}$, a \emph{subprogram} $\mathscr{R}$ of $\mathscr{P}$ is a
-subset of the clauses of $\mathscr{P}$ and is denoted by $\mathscr{R} \subseteq
-\mathscr{P}$.
+(which is a formula). A \emph{(logic) program} is a set of clauses, and a
+\emph{ProbLog program} is a set of clause-probability pairs.
 
@@
 restrict all other trees to single nodes. For this to work, we need to make sure
-that the zeroth node is indeed a root.
-\begin{constraint}
-  $\variable{structure}[0] = 0$.
-\end{constraint}
+that the zeroth node is indeed a root, i.e., fix $\variable{structure}[0] = 0$.
 For convenience, we also define $\variable{numNodes} \in \{ 1, \dots,
@@
   Let $\maxNumNodes{} = 8$. Then $\neg\mathsf{P}(X) \lor (\mathsf{Q}(X) \land
-  \mathsf{P}(X))$ corresponds to the tree in \cref{fig:example_tree} and can be
-  encoded as:
+  \mathsf{P}(X))$ can be encoded as:
   \begin{alignat*}{9}
@@
 
-\begin{figure}[t]
-  \centering
-  \begin{tikzpicture}
-    \node[draw,circle,gray,text=black] (or) at (-0.375, 0) {$\lor$};
-    \node[draw,circle,gray,text=black] (not) at (-1.5, -1) {$\neg$};
-    \node[draw,circle,gray,text=black] (and) at (0.75, -1) {$\land$};
-    \node[draw,gray,text=black] (P) at (-1.5, -2) {$\mathsf{P}(X)$};
-    \node[draw,gray,text=black] (Q) at (0, -2) {$\mathsf{Q}(X)$};
-    \node[draw,gray,text=black] (R) at (1.5, -2) {$\mathsf{P}(X)$};
-    \draw[gray] (or) -- (not);
-    \draw[gray] (or) -- (and);
-    \draw[gray] (not) -- (P);
-    \draw[gray] (and) -- (Q);
-    \draw[gray] (and) -- (R);
-  \end{tikzpicture}
-  \caption{A tree representation of the formula from \cref{example:formula}}
-  \label{fig:example_tree}
-\end{figure}
-
 Here, $\top$ is the value we use for the remaining one-node trees. The
@@
 defined by how the elements link to each other, so we can add a constraint
-saying that
+saying that $\variable{structure}$ is sorted. Next, since we already have a
+variable that counts the number of nodes in the main tree, we can fix the
+structure and the values of the remaining trees to some constant values.
 \begin{constraint}
-  \variable{structure} is sorted.
-\end{constraint}
-Next, since we already have a variable that counts the number of nodes in the
-main tree, we can fix the structure and the values of the remaining trees to
-some constant values.
-\begin{constraint}
-  For $i = 1, \dots, \maxNumNodes{} - 1$, if $i \ge \variable{numNodes}$, then
+  For $i = 1, \dots, \maxNumNodes{} - 1$, if $i < \variable{numNodes}$, then
   \[
@@
 \end{definition}
-Here, a value of zero means that the variable does not occur in the clause. The
-reason why we want to use specifically zero for this will become clear with
-\cref{constraint:diffbutzero}. Because of this choice, the definition of
-$\variable{intros}$ shifts all indices by one. Lastly, we add the variable
-symmetry-breaking constraint.
-\begin{constraint}
-  $\variable{intros}$ are sorted.
-\end{constraint}
-In other words, we constrain the model so that the variable listed first (in
-whatever order $\variables{}$ is presented in) has to occur first in our
-representation of a clause.
+Here, a value of zero means that the variable does not occur in the clause (this
+choice is motivated by subsequent constraints). This means that the definition
+of $\variable{intros}$ shifts all indices by one. Lastly, we add the variable
+symmetry-breaking constraint for sorting $\variable{intros}$. In other words, we
+constrain the model so that the variable listed first (in whatever order
+$\variables{}$ is presented in) has to occur first in our representation of a
+clause.
 
@@
 
-\subsection{Redundant Constraints}
-
-We add several redundant constraints to make search more efficient. First,
-we can state that the positions occupied by different terms must be different.
+We end the section with several redundant constraints. First, we can state that
+the positions occupied by different terms must be different.
 \begin{constraint} \label{constraint:all_diff}
@@
 The reason why we used zero to represent an unused variable is so that we could
-efficiently rephrase \cref{constraint:all_diff} for the $\variable{intros}$
-array.
-\begin{constraint} \label{constraint:diffbutzero}
-  $\variable{allDifferentExcept0}(\variable{intros})$.
-\end{constraint}
-We can also add another link between $\variable{intros}$ and $\variable{occ}$
-that essentially says that the smallest element of a set is an element of the
-set.
+now use the `all different except zero' constraint for the $\variable{intros}$
+array. We can also add another link between $\variable{intros}$ and
+$\variable{occ}$ that essentially says that the smallest element of a set is an
+element of the set.
 \begin{constraint}
@@
 with certain properties and parameters) allows us to gain confidence that the
-constraint model accurately matches our intentions. To simplify the task, we
-only consider clauses without probabilities and disable (negative) cycle
-elimination. We also introduce the term \emph{total arity} of a body of a clause
-to refer to the sum total of arities of all predicates in the body.
+constraint model accurately matches our intentions. For this section, we
+introduce the term \emph{total arity} of a body of a clause to refer to the sum
+total of arities of all predicates in the body.
 
@@
 
-\section{Predicate Independence} \label{sec:independence}
-
-In this section, we define a notion of predicate independence as a way to
-constrain the probability distributions defined by the generated programs. We
-also describe efficient algorithms for propagation and entailment checking.
+\section{Stratification and Independence} \label{sec:independence}
+
+% TODO: explain about entailment and propagation
+
+A ProbLog program has to be stratified in order to ensure a unique
+solution to every query
+\cite{DBLP:journals/jlp/BalbinPRM91,DBLP:conf/padl/MantadelisR17}. Independence
+is a fundamental concept in probability theory that imposes structure on the
+probability distribution and makes probabilistic inference easier. In the
+context of probabilistic logic programming languages, these two seemingly
+disparate concepts can be defined using the same building block, i.e., a
+predicate dependency graph. In this section, we define both notions and describe
+custom constraints meant to ensure that our generated programs are valid and
+have the desired independence structure. A new constraint is usually presented
+with two algorithms: one for \emph{entailment} checking, i.e., checking if the
+(partially solved) constraint model satisfies the constraint or not, and one for
+\emph{propagation}, i.e., removing values from domains that are incompatible
+with the current state of the model.
+
 Let $\mathscr{P}$ be a probabilistic logic program. Its \emph{predicate
@@
 say that $\mathscr{P}$ (or $G_{\mathscr{P}}$) has a \emph{negative cycle} if
-$G_{\mathscr{P}}$ has a cycle with at least one negative edge. Labelling the
-edges as positive/negative will be immaterial for predicate independence, but
-the same graph will play a crucial role in designing a constraint for
-stratification in the next section. In fact, a program $\mathscr{P}$ is
-\emph{stratified} if $G_{\mathscr{P}}$ has no negative cycles.
-\begin{definition}
+$G_{\mathscr{P}}$ has a cycle with at least one negative edge. A program
+$\mathscr{P}$ is \emph{stratified} if $G_{\mathscr{P}}$ has no negative cycles.
+Thus a simple entailment algorithm for stratification can be constructed by
+selecting all clauses, all predicates of which are fully determined, and looking
+for negative cycles in the dependency graph constructed based on those clauses
+using an algorithm such as Bellman-Ford.
+
 Let $\mathsf{P}$ be a predicate in a program $\mathscr{P}$. The set of
@@
 \emph{independent} if $D_{\mathsf{P}} \cap D_{\mathsf{Q}} = \emptyset$.
-\end{definition}
 
@@
       \draw[gray] (not) -- (mother);
-    \end{tikzpicture}
+    \end{tikzpicture}%
     \captionof{figure}{A tree representation of the body of \eqref{eq:example_clause}}
@@
       \draw[-{Stealth[scale=1.5]}] (mother) edge node[below] {$-$} (father);
-    \end{tikzpicture}
+    \end{tikzpicture}%
     \captionof{figure}{The predicate dependency graph of the program in
@@
 
-Next, we add a constraint that defines an adjacency matrix for the predicate
-dependency graph but without positivity/negativity:
-\begin{definition} \label{def:adjacency_matrix}
-  An $|\predicates{}| \times |\predicates{}|$ adjacency matrix $\mathbf{A}$ with
-  $\{ 0, 1 \}$ as its domain is defined by stating that $\mathbf{A}[i][j] = 0$
-  if and only if, for all $k \in \{ 0, \dots, \maxNumClauses{} - 1 \}$, either
+Next, we can define a $|\predicates{}| \times |\predicates{}|$ adjacency matrix
+$\mathbf{A}$ with a binary domain (i.e., without positivity/negativity). It can
+be defined element-wise by stating that $\mathbf{A}[i][j] = 0$ if and only if,
+for all $k \in \{ 0, \dots, \maxNumClauses{} - 1 \}$, either
 $\variable{heads}[k].\variable{predicate} \ne j$ or $ i \not\in
 \{a.\variable{name} \mid a \in \variable{bodies}[k].\variable{values} \}$.
-\end{definition}
+
 Given an undetermined model, we can classify all dependencies of a predicate
@@
 of propagation and entailment algorithms, we define a \emph{dependency} as the
-sum type:
-\begin{grammar}
-  <dependency> ::= $\Determined(p)$ | $\Undetermined(p)$ | $\AlmostDetermined(p,
-  s, t)$
-\end{grammar}
-where each alternative represents a determined, undetermined, and almost
-determined dependency, respectively. Here, $p \in \predicates{}$ is the name of
-the predicate which is the dependency of $\mathsf{P}$, and---in the case of
-$\AlmostDetermined$---$(s, t) \in \predicates{}^2$ is the one undetermined edge
-in $\mathbf{A}$ that prevents the dependency from being determined. For a
-dependency $d$---regardless of its exact type---we will refer to its predicate
-$p$ as $d.\mathsf{predicate}$. In describing the algorithms, we will use an
-underscore to replace any of $p$, $s$, $t$ in situations where the name is
-unimportant.
-
-\begin{algorithm}
+sum type: \syntax{<dependency> ::= $\Determined(p)$ | $\Undetermined(p)$ |
+  $\AlmostDetermined(p, s, t)$}. Each alternative represents a determined,
+undetermined, and almost determined dependency, respectively. Here, $p \in
+\predicates{}$ is the name of the predicate which is the dependency of
+$\mathsf{P}$, and---in the case of $\AlmostDetermined$---$(s, t) \in
+\predicates{}^2$ is the one undetermined edge in $\mathbf{A}$ that prevents the
+dependency from being determined. For a dependency $d$---regardless of its exact
+type---we will refer to its predicate $p$ as $d.\mathsf{predicate}$. In
+describing the algorithms, we will use an underscore to replace any of $p$, $s$,
+$t$ in situations where the name is unimportant.
+
+\begin{algorithm}[t]
   \SetKwFunction{getDependencies}{deps}
@@
 
-\begin{algorithm}[h]
+\begin{algorithm}[t]
   \LinesNumbered
@@
 
-\begin{algorithm}
+\begin{algorithm}[t]
   \SetKwData{edgeExists}{edge}
@@
   \SetKwData{target}{target}
-  \SetKwData{all}{allDependencies}
+  \SetKwData{all}{allDeps}
   \SetKwFunction{getDependencies}{deps}
@@
         $\edgeExists \gets \mathbf{A}[q][d.\predicate] = \{ 1 \}$\;
-        \uIf{$\edgeExists$ {\bf and} $d$ {\bf is} $\Determined(\_)$}{
-          $D' \gets D' \cup \{ \Determined(q) \}$
-        }
-        \uElseIf{$\edgeExists$ {\bf and} $d$ {\bf is} $\AlmostDetermined(\_, s,
-          t)$}{
-          $D' \gets D' \cup \{ \AlmostDetermined(q, s, t) \}$\;
-        }
+        \lIf{$\edgeExists$ {\bf and} $d$ {\bf is} $\Determined(\_)$}{$D' \gets
+          D' \cup \{ \Determined(q) \}$}
+        \lElseIf{$\edgeExists$ {\bf and} $d$ {\bf is} $\AlmostDetermined(\_, s,
+          t)$}{$D' \gets D' \cup \{ \AlmostDetermined(q, s, t) \}$}
         \uElseIf{$|\mathbf{A}[q][d.\predicate]| > 1$ {\bf and} $d$~{\bf is}~$\Determined(r)$}{
@@
         }
-        \ElseIf{$|\mathbf{A}[q][d.\predicate]| > 1$ {\bf and} \all}{
-          $D' \gets D' \cup \{ \Undetermined(q) \}$\;
+        \lElseIf{$|\mathbf{A}[q][d.\predicate]| > 1$ {\bf and} \all}{$D' \gets
+          D' \cup \{ \Undetermined(q) \}$}
       }
-      }
-      \lIf{$D' = D$}{\Return{$D$}}
-      $D \gets D'$\;
+      \leIf{$D' = D$}{\Return{$D$}}{$D \gets D'$}
     }
@@
   \]
-  The predicate dependency graph without positivity/negativity (as defined in
-  \cref{def:adjacency_matrix}) is represented in \cref{fig:example}.
+  The predicate dependency graph is pictured in \cref{fig:example}. Suppose we
+  have a constraint that $\mathsf{mother}$ and $\mathsf{parent}$ must be
+  independent. The lists of potential dependencies for both predicates are:
+  \begin{align*}
+    D_{\mathsf{mother}} &= \{ \Determined(\mathsf{mother}), \AlmostDetermined(\mathsf{parent}, \mathsf{parent}, \mathsf{mother}) \}, \\
+    D_{\mathsf{parent}} &= \{ \Determined(\mathsf{parent}) \}.
+  \end{align*}
+  An entailment check at this stage would produce \textsc{undefined}, but
+  propagation replaces the boxed value in \cref{fig:dependencies_matrix} with
+  zero, eliminating the potential edge from $\mathsf{parent}$ to
+  $\mathsf{mother}$. This also eliminates $\mathsf{mother}$ from $D_\Box$, and
+  this is enough to make \cref{alg:independence_entailment} return
+  \textsc{true}.
+\end{example}
 
@@
 
-  Suppose we have a constraint that $\mathsf{mother}$ and $\mathsf{parent}$ must
-  be independent. The lists of potential dependencies for both predicates are:
-  \begin{align*}
-    D_{\mathsf{mother}} &= \{ \Determined(\mathsf{mother}), \AlmostDetermined(\mathsf{parent}, \mathsf{parent}, \mathsf{mother}) \}, \\
-    D_{\mathsf{parent}} &= \{ \Determined(\mathsf{parent}) \}.
-  \end{align*}
-  An entailment check at this stage would produce \textsc{undefined}, but
-  propagation replaces the boxed value in \cref{fig:dependencies_matrix} with
-  zero, eliminating the potential edge from $\mathsf{parent}$ to
-  $\mathsf{mother}$. This also eliminates $\mathsf{mother}$ from $D_\Box$, and,
-  although some undetermined variables remain, this is enough to make
-  \cref{alg:independence_entailment} return \textsc{true}.
-\end{example}
-
-\section{Negative Cycles} \label{sec:cycles}
-
-Ideally, we would like to design a constraint for negative cycles similar to the
-constraint for independence in the previous section. However, the difficulty
-with creating a propagation algorithm for negative cycles is that there seems to
-be no good way to extend \cref{def:adjacency_matrix} so that the adjacency
-matrix captures positivity/negativity. Thus, we settle for an entailment
-algorithm with no propagation.
-
-\begin{algorithm}
-  \KwData{a program $\mathscr{P}$}
-  \SetKwFunction{hasNegativeCycles}{hasNegativeCycles}
-  Let $\mathscr{R} \subseteq \mathscr{P}$ be the largest subprogram of
-  $\mathscr{P}$ with its $\variable{structure}$ and predicates in both body
-  and head fully determined\footnotemark\;
-  \If{\hasNegativeCycles($G_{\mathscr{R}}$)}{
-    \Return{\textsc{false}}\;
-  }
-  \lIf{$\mathscr{R} = \mathscr{P}$}{\Return{\textsc{true}}}
-  \Return{\textsc{undefined}}\;
-  \caption{Entailment for negative cycles}
-  \label{alg:negative_cycles}
-\end{algorithm}
-\footnotetext{The arguments (whether variables or constants) are irrelevant to
-  our definition of independence.}
-
-The algorithm takes all clauses whose structure and predicates have been fully
-determined and uses them to construct a full dependency graph. In our
-implementation, \texttt{hasNegativeCycles} function is just a simple extension
-of the backtracking cycle detection algorithm that `travels' around the graph
-following edges and checking if each vertex has already been visited or not.
-Alternatively, one could assign weights to the edges (e.g., $1$ for positive
-and $-\infty$ for negative edges), thus reducing our negative cycle detection
-problem to what is typically known as the negative cycle detection problem in
-the literature, and use an algorithm such as Bellman-Ford
-\cite{shimbel1954structure}.
-
-If the algorithm finds a negative cycle in this fully-determined part of the
-program, then we must return \textsc{false}. If there was no negative cycle and
-the entire program is (sufficiently) determined, then there cannot be any
-negative cycles. In all other cases, it is too early to tell.
-
-\section{Empirical Performance} \label{sec:experiments}
+\section{Experimental Results}
+
+This section presents two empirical investigations: in \cref{sec:experiment1} we
+examine the scalability of our constraint model with respect to its parameters
+and in \cref{sec:experiment2} we demonstrate how the model can be used to
+compare inference algorithms and describe their behaviour across a wide range of
+programs---something that has not been done before. The experiments were run on
+a system with Intel Core i5-8250U processor, \SI{8}{\giga\byte} RAM, and Arch
+Linux~5.6.11-arch1-1 operating system. The constraint model was implemented in
+Java~8 with Choco~4.10.2. All inference algorithms are implemented in
+ProbLog~2.1.0.39 and were run using Python~3.8.2 with PySDD~0.2.10 and
+PyEDA~0.28.0. For both sets of experiments, we generate programs without
+negative cycles and use a \SI{60}{\second} timeout.
+
+\subsection{Empirical Performance of the Model} \label{sec:experiment1}
 
@@
 \]
-We also employ a geometric restart policy, restarting after $10, 20, 40,
-80, \dots$ contradictions\footnote{Restarts help overcome early mistakes in the
-  search process but can be disabled if one wants to find all solutions, in
-  which case search is complete regardless of the variable ordering heuristic.}.
-
-We ran close to \num{400000} experiments, investigating whether the model is
-efficient enough to generate reasonably-sized programs and gaining insight into
-what parameter values make the constraint satisfaction problem harder. For these
-experiments, we use Choco~4.10.2 \cite{choco} with Java~8. For
-$|\predicates{}|$, $|\variables{}|$, $|\constants{}|$, $\maxNumNodes{}$, and
-$\maxNumClauses{} - |\predicates{}|$ (i.e., the number of clauses in addition to
-the mandatory $|\predicates{}|$ clauses), we assign all combinations of 1, 2, 4,
-8. $\maxArity{}$ is assigned to values 1--4. For each $|\predicates{}|$, we also
-iterate over all possible numbers of independent pairs of predicates, ranging
-from 0 up to $\binom{|\predicates{}|}{2}$. For each combination of the
-above-mentioned parameters, we pick ten random ways to assign arities to
-predicates (such that $\maxArity{}$ occurs at least once) and ten random
-combinations of independent pairs. We then run the solver with a
-\SI{60}{\second} timeout.
+We also employ a geometric restart policy, restarting after $10, 10 \times 1.1,
+10 \times 1.1^2, \dots$ contradictions\footnote{Restarts help overcome early
+  mistakes in the search process but can be disabled if one wants to find all
+  solutions, in which case search is complete regardless of the variable
+  ordering heuristic.}. We ran close to \num{400000} experiments, investigating
+whether the model is efficient enough to generate reasonably-sized programs and
+gaining insight into what parameter values make the constraint satisfaction
+problem harder. For $|\predicates{}|$, $|\variables{}|$, $|\constants{}|$,
+$\maxNumNodes{}$, and $\maxNumClauses{} - |\predicates{}|$ (i.e., the number of
+clauses in addition to the mandatory $|\predicates{}|$ clauses), we assign all
+combinations of 1, 2, 4, 8. $\maxArity{}$ is assigned to values 1--4. For each
+$|\predicates{}|$, we also iterate over all possible numbers of independent
+pairs of predicates, ranging from 0 up to $\binom{|\predicates{}|}{2}$. For each
+combination of the above-mentioned parameters, we pick ten random ways to assign
+arities to predicates (such that $\maxArity{}$ occurs at least once) and ten
+random combinations of independent pairs.
 
@@
   \centering
-  \input{impact.tex}
-  \caption{The mean number of nodes in the binary search tree for each value of
-    each experimental parameter. Note that the horizontal axis is on a $\log_2$
-    scale.}
+  \begin{minipage}[t]{.49\textwidth}
+    \centering
+    \input{impact.tex}%
+    \captionof{figure}{The mean number of nodes in the binary search tree for
+      each value of each experimental parameter. Note that the horizontal axis
+      is on a $\log_2$ scale.}
     \label{fig:impact}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[t]{.49\textwidth}
+    \centering
+    \input{bars.tex}%
+    \captionof{figure}{Inference time for different values of $\maxArity{}$ and
+      proportions of facts that are probabilistic. The total number of facts is
+      fixed at $10^5$.}
+    \label{fig:bars}
+  \end{minipage}
 \end{figure}
 
-\section{Conclusions}
-
-We were able to design an efficient model for generating both logic programs and
-probabilistic logic programs. The model avoids unnecessary symmetries, generates
-valid programs, and can ensure predicate independence. Our constraint-driven
-approach is advantageous in that one can easily add additional conditions on the
-structure and properties of the program, although the main disadvantage is
-that there are no guarantees about the underlying probability distribution from
-which programs are sampled.
-
-Also, note that our model treats logically equivalent but syntactically
+\subsection{Experimental Comparison of Inference Algorithms} \label{sec:experiment2}
+
+For this experiment, we consider clauses of two types: \emph{rules} are clauses
+such that the head atom has at least one variable, and \emph{facts} are clauses
+with no bodies and no variables. We use our constraint model to generate the
+rules according to the following parameter values: $|\predicates{}|,
+|\variables{}|, \maxNumNodes{} \in \{ 2, 4, 8 \}$, $\maxArity{} \in \{ 1, 2, 3
+\}$, $\maxNumClauses{} = |\predicates{}|$, $\constants{} = \emptyset$. Just like
+before, we explore all possible numbers of independent predicate pairs. We also
+add a constraint that forbids empty bodies. For both rules and facts,
+probabilities are uniformly sampled from $\{ 0.1, 0.2, \dots, 0.9 \}$.
+Furthermore, all rules are probabilistic, while we vary the proportion of
+probabilistic facts among \SI{25}{\percent}, \SI{50}{\percent}, and
+\SI{75}{\percent}. For generating facts, we consider $|\constants{}| \in \{100,
+200, 400 \}$ and vary the number of facts among $10^3$, $10^4$, and $10^5$ but
+with one exception: the number of facts is not allowed to exceed
+\SI{75}{\percent} of all possible facts with the given values of
+$\predicates{}$, $\arities{}$, and $\constants{}$. Facts are generated using a
+simple procedure that randomly selects a predicate, combines it with the right
+number of constants, and checks whether the generated atom is already included
+or not. We randomly select configurations from the description above and
+generate ten programs with a complete restart of the constraint solver before
+the generation of each program, including choosing different arities and
+independent pairs. Finally, we set the query of each program to a random fact
+not explicitly included in the program and consider six natively supported
+algorithms and knowledge compilation techniques: binary decision diagrams (BDDs)
+\cite{DBLP:journals/tc/Bryant86}, negation normal form (NNF), deterministic
+decomposable NNF (d-DNNF) \cite{DBLP:journals/jair/DarwicheM02}, K-Best
+\cite{DBLP:conf/pkdd/GutmannKKR08}, and two encodings based on sentential
+decision diagrams \cite{DBLP:conf/ijcai/Darwiche11}, one of which encodes the
+entire program (SDDX), while the other one encodes only the part of the program
+relevant to the query (SDD)\footnote{Forward SDDs (FSDDs) and forward BDDs
+  (FBDDs)
+  \cite{DBLP:journals/corr/abs-1911-07750,DBLP:conf/ijcai/VlasselaerBKMR15} are
+  omitted because the former uses too much memory and the implementation of the
+  latter seems to be broken at the time of writing.}.
+
+Out of \num{11310} generated problem instances, about \SI{35}{\percent} were
+discarded because one or more algorithms were not able to ground the instance in
+an unambiguous way. The first observation (pictured in \cref{fig:line_plots}) is
+that the algorithms are remarkably similar, i.e., the differences in performance
+are small and consistent across all parameter values (including parameters not
+shown in the figure). Unsurprisingly, the most important predictor of inference
+time is the number of facts. However, after fixing the number of facts to a
+constant value, we can still observe that inference becomes harder with higher
+arity predicates as well as when facts are mostly probabilistic (see
+\cref{fig:bars}). Finally, according to \cref{fig:line_plots}, the independence
+structure of a program does not affect inference time, i.e., state-of-the-art
+inference algorithms---although they are supposed to
+\cite{DBLP:conf/uai/FierensBTGR11}---do not exploit situations where separate
+parts of a program can be handled independently.
+
+\begin{figure}[t]
+  \centering
+  \input{line_plots.tex}%
+  \caption{Mean inference time for a range of ProbLog inference algorithms as
+    a function of the total number of facts in the program and the proportion of
+    independent pairs of predicates. For the second plot, the number of facts is
+    fixed at $10^5$.}
+  \label{fig:line_plots}
+\end{figure}
+
+\section{Conclusion}
+
+We presented a constraint model for generating both logic programs and
+probabilistic logic programs. The model avoids unnecessary symmetries, is
+reasonably efficient and supports additional constraints such as predicate
+independence. The advantages of this approach lie in customisability and speed,
+although the main disadvantage is that there are no guarantees about the
+underlying probability distribution from which programs are sampled.
+
+Also note that our model treats logically equivalent but syntactically
 different formulas as different. This is so in part because designing a
@@
 
+Finally, our experimental results provide the first comparison of inference
+algorithms for probabilistic logic programming languages that generalises over
+programs, i.e., is not restricted to just a few programs and data sets. While
+the results did not reveal any significant differences among the algorithms,
+they did reveal a shared weakness, i.e., the inability to ignore the part of a
+program that is easily seen to be irrelevant to the given query. We hope that
+our work can facilitate the development of inference (as well as learning)
+algorithms and provide a better understanding of the strengths and weaknesses of
+current approaches.
+
 %\subsubsection*{Acknowledgments.}
@@
 % ==============================================================================
+
+% Empirical tasks:
+% 1) make the CP model faster: apply the redundant constraints to predicates
+% (not just variables). Check if everything works out.
+% 2) compare to parameter learning with ProbFOIL
+% 3) create a constraint for groundedness (see the ProbLog FAQ)
+% New things I could talk about:
+% 1) entailment for conditional independence
+% 2) the 'required formula' part of the model
+% 3) how linear models can predict inference time
 
@@
 %\end{figure*}
+
+%\begin{figure}[t]
+%  \centering
+%  \begin{tikzpicture}
+%    \node[draw,circle,gray,text=black] (or) at (-0.375, 0) {$\lor$};
+%    \node[draw,circle,gray,text=black] (not) at (-1.5, -1) {$\neg$};
+%    \node[draw,circle,gray,text=black] (and) at (0.75, -1) {$\land$};
+%    \node[draw,gray,text=black] (P) at (-1.5, -2) {$\mathsf{P}(X)$};
+%    \node[draw,gray,text=black] (Q) at (0, -2) {$\mathsf{Q}(X)$};
+%    \node[draw,gray,text=black] (R) at (1.5, -2) {$\mathsf{P}(X)$};
+%    \draw[gray] (or) -- (not);
+%    \draw[gray] (or) -- (and);
+%    \draw[gray] (not) -- (P);
+%    \draw[gray] (and) -- (Q);
+%    \draw[gray] (and) -- (R);
+%  \end{tikzpicture}
+%  \caption{A tree representation of the formula from \cref{example:formula}}
+%  \label{fig:example_tree}
+%\end{figure}
 
@@
 
+% \section{Entailment Checking of Negative Cycles} \label{sec:cycles}
+
+% Ideally, we would like to design a constraint for negative cycles similar to the
+% constraint for independence in the previous section. However, the difficulty
+% with creating a propagation algorithm for negative cycles is that there seems to
+% be no good way to extend \cref{def:adjacency_matrix} so that the adjacency
+% matrix captures positivity/negativity. Thus, we settle for an entailment
+% algorithm with no propagation.
+
+%\begin{algorithm}
+%  \KwData{a program $\mathscr{P}$}
+%  \SetKwFunction{hasNegativeCycles}{hasNegativeCycles}
+%  Let $\mathscr{R} \subseteq \mathscr{P}$ be the largest subprogram of
+%  $\mathscr{P}$ with its $\variable{structure}$ and predicates in both body
+%  and head fully determined\footnotemark\;
+%  \lIf{\hasNegativeCycles($G_{\mathscr{R}}$)}{\Return{\textsc{false}}}
+%  \leIf{$\mathscr{R} = \mathscr{P}$}{\Return{\textsc{true}}}{\Return{\textsc{undefined}}}
+%  \caption{Entailment for negative cycles}
+%  \label{alg:negative_cycles}
+%\end{algorithm}
+%\footnotetext{Variables and constants are irrelevant to our definition of
+%  independence.}
+
+% The algorithm takes all clauses whose structure and predicates have been fully
+% determined and uses them to construct a full dependency graph. In our
+% implementation, \texttt{hasNegativeCycles} function is just a simple extension
+% of the backtracking cycle detection algorithm that `travels' around the graph
+% following edges and checking if each vertex has already been visited or not.
+% Alternatively, one could assign weights to the edges (e.g., $1$ for positive
+% and $-\infty$ for negative edges), thus reducing our negative cycle detection
+% problem to what is typically known as the negative cycle detection problem in
+% the literature, and use an algorithm such as Bellman-Ford
+% \cite{shimbel1954structure}.
+
+% If the algorithm finds a negative cycle in this fully-determined part of the
+% program, then we must return \textsc{false}. If there was no negative cycle and
+% the entire program is (sufficiently) determined, then there cannot be any
+% negative cycles. In all other cases, it is too early to tell.
+
 \bibliographystyle{splncs04}

### 2020-05-15 scripts/analyse_problog.R

@@ -38,28 +38,28 @@ prepare.csv <- function(filename) {
 
 sdd <- prepare.csv("../data/problog/sdd.csv")
 nnf <- prepare.csv("../data/problog/nnf.csv")
-symbolic <- prepare.csv("../data/problog/symbolic.csv")
 kbest <- prepare.csv("../data/problog/kbest.csv")
 sddx <- prepare.csv("../data/problog/sddx.csv")
 ddnnf <- prepare.csv("../data/problog/ddnnf.csv")
+bdd <- prepare.csv("../data/problog/bdd.csv")
 
 sdd <- sdd[sdd$ID %in% nnf$ID,]
-sdd <- sdd[sdd$ID %in% symbolic$ID,]
 sdd <- sdd[sdd$ID %in% kbest$ID,]
 sdd <- sdd[sdd$ID %in% sddx$ID,]
 sdd <- sdd[sdd$ID %in% ddnnf$ID,]
+sdd <- sdd[sdd$ID %in% bdd$ID,]
 nnf <- nnf[nnf$ID %in% sdd$ID,]
-symbolic <- symbolic[symbolic$ID %in% sdd$ID,]
 kbest <- kbest[kbest$ID %in% sdd$ID,]
 sddx <- sddx[sddx$ID %in% sdd$ID,]
 ddnnf <- ddnnf[ddnnf$ID %in% sdd$ID,]
+bdd <- bdd[bdd$ID %in% sdd$ID,]
 
 combined <- rbind(cbind(melt(sdd[, relevant_columns], id.var = "Total.time"), Algorithm = "SDD"),
                   cbind(melt(nnf[, relevant_columns], id.var = "Total.time"), Algorithm = "NNF"),
-                  cbind(melt(symbolic[, relevant_columns], id.var = "Total.time"), Algorithm = "Symbolic"),
                   cbind(melt(kbest[, relevant_columns], id.var = "Total.time"), Algorithm = "K-Best"),
                   cbind(melt(sddx[, relevant_columns], id.var = "Total.time"), Algorithm = "SDDX"),
-                  cbind(melt(ddnnf[, relevant_columns], id.var = "Total.time"), Algorithm = "dDNNF"))
+                  cbind(melt(ddnnf[, relevant_columns], id.var = "Total.time"), Algorithm = "d-DNNF"),
+                  cbind(melt(bdd[, relevant_columns], id.var = "Total.time"), Algorithm = "BDD"))
[…]

### 2020-05-15 scripts/run_problog.py

@@ -13,7 +13,7 @@ def run_one(filename):
         return
     sys.stdout.write('.')
     sys.stdout.flush()
-    output = subprocess.Popen(['problog', '-v', PROGRAMS_DIR + filename, '-t', TIMEOUT, '-k', 'bdd'],
+    output = subprocess.Popen(['problog', '-v', PROGRAMS_DIR + filename, '-t', TIMEOUT, '-k', 'fbdd'],
                               stdout=subprocess.PIPE)
     output_str = output.communicate()[0][:-1].decode('utf-8')
     with open(output_filename, 'w+') as f:

### 2020-05-16 text/paper2/paper.tex
Edit the section on custom constraints

@@
 \usepackage[caption=false]{subfig}
+\usepackage{booktabs}
 
@@
 \section{Introduction}
+
+TODO: Review \cite{DBLP:journals/tplp/WangWM15,DBLP:conf/ijcai/AmendolaRT17,DBLP:journals/ai/AmendolaRT20}
 
@@
 
-% TODO: explain about entailment and propagation
-
-A ProbLog program has to be stratified in order to ensure a unique
-solution to every query
-\cite{DBLP:journals/jlp/BalbinPRM91,DBLP:conf/padl/MantadelisR17}. Independence
-is a fundamental concept in probability theory that imposes structure on the
-probability distribution and makes probabilistic inference easier. In the
+In this section, we present custom constraints for stratification and
+independence. Stratification is a condition that both logic programs and
+probabilistic logic programs need to satisfy to ensure a unique answer
+to every query
+\cite{DBLP:journals/jlp/BalbinPRM91,DBLP:conf/padl/MantadelisR17}, while
+independence is a fundamental concept in probability theory that imposes
+structure on the probability distribution and simplifies inference. In the
 context of probabilistic logic programming languages, these two seemingly
 disparate concepts can be defined using the same building block, i.e., a
-predicate dependency graph. In this section, we define both notions and describe
-custom constraints meant to ensure that our generated programs are valid and
-have the desired independence structure. A new constraint is usually presented
-with two algorithms: one for \emph{entailment} checking, i.e., checking if the
-(partially solved) constraint model satisfies the constraint or not, and one for
+predicate dependency graph. Constraints are usually presented with two
+algorithms: one for \emph{entailment} checking, i.e., checking if the (partially
+solved) constraint model satisfies the constraint or not, and one for
 \emph{propagation}, i.e., removing values from domains that are incompatible
-with the current state of the model.
-
-Let $\mathscr{P}$ be a probabilistic logic program. Its \emph{predicate
-  dependency graph} is a directed graph $G_{\mathscr{P}} = (V, E)$ with the set
-of nodes $V$ consisting of all predicates in $\mathscr{P}$. For any two
-different predicates $\mathsf{P}$ and $\mathsf{Q}$, we add an edge from
-$\mathsf{P}$ to $\mathsf{Q}$ if there is a clause in $\mathscr{P}$ with
+with the current state of the model. We present both algorithms for independence
+while settling for a short description of entailment for stratification.
+
+Let $\mathscr{P}$ be a probabilistic logic program with predicates
+$\predicates{}$. Its \emph{(predicate) dependency graph} is a directed graph
+$G_{\mathscr{P}}$ with $\predicates{}$ as nodes and an edge between $\mathsf{P},
+\mathsf{Q} \in \predicates{}$ if there is a clause in $\mathscr{P}$ with
 $\mathsf{Q}$ as the head and $\mathsf{P}$ mentioned in the body. We say that the
@@
 the root to the $\mathsf{P}$ node in the tree representation of the clause
-passes through at least one negation node. Otherwise, it is \emph{positive}. We
+passes through at least one negation node; otherwise, it is \emph{positive}. We
 say that $\mathscr{P}$ (or $G_{\mathscr{P}}$) has a \emph{negative cycle} if
@@
 
-Let $\mathsf{P}$ be a predicate in a program $\mathscr{P}$. The set of
-\emph{dependencies} of $\mathsf{P}$ is the smallest set $D_{\mathsf{P}}$ such
-that $\mathsf{P} \in D_{\mathsf{P}}$, and, for every $\mathsf{Q} \in
-D_{\mathsf{P}}$, all direct predecessors of $\mathsf{Q}$ in $G_{\mathscr{P}}$
-are in $D_{\mathsf{P}}$. Two predicates $\mathsf{P}$ and $\mathsf{Q}$ are
-\emph{independent} if $D_{\mathsf{P}} \cap D_{\mathsf{Q}} = \emptyset$.
+For any predicate $\mathsf{P} \in \predicates{}$, the set of \emph{dependencies}
+of $\mathsf{P}$ is the smallest set $D_{\mathsf{P}}$ such that $\mathsf{P} \in
+D_{\mathsf{P}}$, and, for every $\mathsf{Q} \in D_{\mathsf{P}}$, all direct
+predecessors of $\mathsf{Q}$ in $G_{\mathscr{P}}$ are in $D_{\mathsf{P}}$. Two
+predicates $\mathsf{P}$ and $\mathsf{Q}$ are \emph{independent} if
+$D_{\mathsf{P}} \cap D_{\mathsf{Q}} = \emptyset$.
 
@@
   Its predicate dependency graph is in \cref{fig:predicate_dependencies}.
-  Because of the negation in \eqref{eq:example_clause} (as seen in
-  \cref{fig:example_tree2}), the edge from $\mathsf{mother}$ to
-  $\mathsf{father}$ is negative, while the other two edges are positive.
-  The dependencies of each predicate are:
+  Because of the negation in \eqref{eq:example_clause}, the edge from
+  $\mathsf{mother}$ to $\mathsf{father}$ is negative, while the other two edges
+  are positive. The dependencies of each predicate are:
   \begin{alignat*}{3}
@@
 \end{example}
+
 \begin{figure}[t]
   \centering
-  \begin{minipage}{.49\textwidth}
-    \centering
-    \begin{tikzpicture}
-      \node[draw,circle,gray,text=black] (and) at (0, 0) {$\land$};
-      \node[draw,circle,gray,text=black] (not) at (1.5, -1) {$\neg$};
-      \node[draw,gray,text=black] (parent) at (-1.5, -1) {$\mathsf{parent}(X, Y)$};
-      \node[draw,gray,text=black] (mother) at (1.5, -2) {$\mathsf{mother}(X, Y)$};
-      \draw[gray] (and) -- (parent);
-      \draw[gray] (and) -- (not);
-      \draw[gray] (not) -- (mother);
-    \end{tikzpicture}%
-    \captionof{figure}{A tree representation of the body of \eqref{eq:example_clause}}
-    \label{fig:example_tree2}
-  \end{minipage}
   \begin{minipage}{.49\textwidth}
@@
   \end{minipage}
+  \begin{minipage}{.49\textwidth}
+    \centering
+    \captionof{table}{Types of (potential) dependencies of a predicate
+      $\mathsf{P}$ based on the number of undetermined edges on the path from
+      the dependency to $\mathsf{P}$}
+    \label{tbl:dependencies}
+    \begin{tabular}{clc}
+      \toprule
+      Edges & Name & Notation \\
+      \midrule
+      $0$ & determined & $\Determined(p)$ \\
+      $1$ & almost determined & $\AlmostDetermined(p, s, t)$ \\
+      $>1$ & undetermined & $\Undetermined(p)$ \\
+      \bottomrule
+    \end{tabular}
+  \end{minipage}
 \end{figure}
 
-Next, we can define a $|\predicates{}| \times |\predicates{}|$ adjacency matrix
-$\mathbf{A}$ with a binary domain (i.e., without positivity/negativity). It can
-be defined element-wise by stating that $\mathbf{A}[i][j] = 0$ if and only if,
-for all $k \in \{ 0, \dots, \maxNumClauses{} - 1 \}$, either
+Since the definition of independence relies on the dependency graph, we can
+represent this graph as an adjacency matrix constructed as part of the model.
+Let $\mathbf{A}$ be a $|\predicates{}| \times |\predicates{}|$ binary matrix
+defined element-wise by stating that $\mathbf{A}[i][j] = 0$ if and only if, for
+all $k = 0, \dots, \maxNumClauses{} - 1$, either
 $\variable{heads}[k].\variable{predicate} \ne j$ or $ i \not\in
@@
 
-Given an undetermined model, we can classify all dependencies of a predicate
-$\mathsf{P}$ into three categories based on how many of the edges on the path
-from the dependency to $\mathsf{P}$ are undetermined. In the case of zero, we
-call the dependency \emph{determined}. In the case of one, we call it
-\emph{almost determined}. Otherwise, it is \emph{undetermined}. In the context
-of propagation and entailment algorithms, we define a \emph{dependency} as the
-sum type: \syntax{<dependency> ::= $\Determined(p)$ | $\Undetermined(p)$ |
-  $\AlmostDetermined(p, s, t)$}. Each alternative represents a determined,
-undetermined, and almost determined dependency, respectively. Here, $p \in
-\predicates{}$ is the name of the predicate which is the dependency of
-$\mathsf{P}$, and---in the case of $\AlmostDetermined$---$(s, t) \in
-\predicates{}^2$ is the one undetermined edge in $\mathbf{A}$ that prevents the
-dependency from being determined. For a dependency $d$---regardless of its exact
-type---we will refer to its predicate $p$ as $d.\mathsf{predicate}$. In
-describing the algorithms, we will use an underscore to replace any of $p$, $s$,
-$t$ in situations where the name is unimportant.
+Given a partially-solved model with its predicate dependency graph, let us pick
+an arbitrary path from $\mathsf{Q}$ to $\mathsf{P}$ (for some $\mathsf{P},
+\mathsf{Q} \in \predicates{}$) that consists of determined edges that are
+denoted by $1$ in $\mathbf{A}$ and potential/undetermined edges that are
+denoted by $\{ 0, 1 \}$. Each such path characterises a \emph{(potential)
+  dependency} $\mathsf{Q}$ for $\mathsf{P}$. We can put each such dependency
+into one out of three classes depending on the number of undetermined edges on
+the path. These classes are outlined in \cref{tbl:dependencies}, where $p$
+represents the dependency predicate $\mathsf{Q}$, and, in the case of
+$\AlmostDetermined{}$, $(s, t) \in \predicates{}^2$ is the one undetermined edge
+on the path. For a dependency $d$---regardless of its exact type---we will refer
+to its predicate $p$ as $d.\mathsf{predicate}$. In describing the algorithms, we
+will use an underscore to replace any of $p$, $s$, $t$ in situations where the
+name is unimportant.
 
@@
       $\Determined(\_)$}{\fail{}} \label{line:fail}
-    \If{$d_1$ {\bf is} $\Determined(\_)$ {\bf and} $d_2$ {\bf is}
-      $\AlmostDetermined(\_, s, t)$ {\bf or} $d_2$ {\bf is} $\Determined(\_)$
-      {\bf and} $d_1$ {\bf is} $\AlmostDetermined(\_, s,
-      t)$ \label{line:propagation_condition}}{
-      $\mathbf{A}[s][t]$.\removeValue{$1$}\; \label{line:propagation_result}
-    }
+    \lIf{$\{ d_1, d_2 \} = \{ \Determined(\_), \AlmostDetermined(\_, s, t)
+      \}$ \label{line:propagation_condition}}{$\mathbf{A}[s][t]$.\removeValue{$1$}}
   }
@@
 that prevents the $\AlmostDetermined$ from becoming a $\Determined$ cannot
-exist--\cref{line:propagation_condition,line:propagation_result} handle this
-possibility.
+exist---\cref{line:propagation_condition} handles this possibility.
 
@@
 
+%    \begin{tikzpicture}
+%      \node[draw,circle,gray,text=black] (and) at (0, 0) {$\land$};
+%      \node[draw,circle,gray,text=black] (not) at (1.5, -1) {$\neg$};
+%      \node[draw,gray,text=black] (parent) at (-1.5, -1) {$\mathsf{parent}(X, Y)$};
+%      \node[draw,gray,text=black] (mother) at (1.5, -2) {$\mathsf{mother}(X, Y)$};
+%      \draw[gray] (and) -- (parent);
+%      \draw[gray] (and) -- (not);
+%      \draw[gray] (not) -- (mother);
+%    \end{tikzpicture}%
+%    \captionof{figure}{A tree representation of the body of \eqref{eq:example_clause}}
+%    \label{fig:example_tree2}
+
 \bibliographystyle{splncs04}

### 2020-05-16 text/paper2/paper.tex
Improve introduction

@@
   one to generate programs that have a certain independence structure. Finally,
-  we provide a combinatorial argument for the correctness of the model and
+  we provide a combinatorial argument for the correctness of the model,
   describe how the parameters of the model affect the empirical difficulty of
-  the program generation task.
+  the program generation task, and use the model to compare probabilistic
+  inference algorithms across a range of synthetic problems.
 
@@
 \end{abstract}
-% TODO: update the introduction and the abstract
+
+% TODO: proofread, run a grammar checker on everything
 
 \section{Introduction}
-
-TODO: Review \cite{DBLP:journals/tplp/WangWM15,DBLP:conf/ijcai/AmendolaRT17,DBLP:journals/ai/AmendolaRT20}
 
@@
 mixes machine learning and symbolic (logical and relational) structures. In
-particular, probabilistic logic programs---including languages such as PRISM
-\cite{DBLP:conf/ijcai/SatoK97}, ICL \cite{DBLP:journals/ai/Poole97}, and ProbLog
+particular, probabilistic logic programs---including languages such as
+\textsc{PRISM} \cite{DBLP:conf/ijcai/SatoK97}, \textsc{ICL}
+\cite{DBLP:journals/ai/Poole97}, and \textsc{ProbLog}
 \cite{DBLP:conf/ijcai/RaedtKT07}---are promising frameworks for codifying
@@
 behaviour of algorithms and their ability to solve random synthetic problems.
-Unfortunately, in the context of probabilistic logic programming, most current
-approaches to random instance generation are very restrictive, e.g., limited to
-clauses with only two literals \cite{DBLP:conf/lpnmr/NamasivayamT09}, or clauses
-of the form $a \gets \neg b$ \cite{DBLP:journals/tocl/WenWSL16}, although some
-are more expressive, e.g., defining a program only by the (maximum) number of
-atoms in the body and the total number of rules \cite{DBLP:conf/iclp/ZhaoL03}.
-
-In this work, we introduce a constraint-based representation for logic programs
-based on some simple parameters that describe the program's size, what
-predicates and constants it uses, etc. This representation takes the form of a
-constraint satisfaction problem, i.e., a set of discrete variables and
-restrictions on what values they can take. Every solution to this problem (as
-output by a constraint solver) directly translates into a logic program. One can
-either use random value-ordering heuristics and restarts to generate random
-programs or find all (sufficiently small) programs that satisfy the given
-requirements. In fact, the same model can generate both probabilistic programs
-in the syntax of ProbLog \cite{DBLP:conf/ijcai/RaedtKT07} and non-probabilistic
-Prolog programs.
+Unfortunately, when it comes to generating random logic programs, all approaches
+so far focused exclusively on propositional programs
+\cite{DBLP:conf/ijcai/AmendolaRT17,DBLP:journals/ai/AmendolaRT20,DBLP:journals/tplp/WangWM15,DBLP:conf/iclp/ZhaoL03},
+often with severely limiting conditions such as two-literal clauses
+\cite{DBLP:conf/iclp/Namasivayam09,DBLP:conf/lpnmr/NamasivayamT09} or clauses of
+the form $a \gets \neg b$.
+
+In \cref{sec:heads,sec:bodies,sec:variable_symmetry}, we introduce a
+constraint-based representation for logic programs based on simple parameters
+that describe the program's size, what predicates and constants it uses, etc.
+This representation takes the form of a \emph{constraint satisfaction problem}
+(CSP), i.e., a set of discrete variables and restrictions on what values they
+can take. Every solution to this problem (as output by a constraint solver)
+directly translates into a logic program. One can either output all
+(sufficiently small) programs that satisfy the given conditions or use random
+value-ordering heuristics and restarts to generate random programs. For sampling
+from a uniform distribution, the CSP can be transformed into a belief network
+\cite{DBLP:conf/aaai/DechterKBE02}. In fact, the same model can generate both
+probabilistic programs in the syntax of \textsc{ProbLog}
+\cite{DBLP:conf/ijcai/RaedtKT07} and non-probabilistic \textsc{Prolog} programs.
+This is both the first time the problem of generating random logic programs has
+been approached in its full generality (i.e., including first-order clauses with
+variables) and the first time inference algorithms for probabilistic logic
+programs can be evaluated on more than a handful of instances.
 
@@
 additional constraints as needed, and to do that efficiently (compared to
-generate-and-test approaches). As an example of this, we develop a custom
-constraint that, given two predicates $\mathsf{P}$ and $\mathsf{Q}$, ensures
-that any ground atom with predicate $\mathsf{P}$ is independent of any ground
-atom with predicate $\mathsf{Q}$. In this way, we can easily regulate the
-independence structure of the underlying probability distribution. We also
-present a combinatorial argument for correctness, counting the number of
-programs that the model produces for various parameter values and show how the
-model scales when tasked with producing more complicated programs.
+generate-and-test approaches). As an example of this, in \cref{sec:independence}
+we develop a custom constraint that, given two predicates $\mathsf{P}$ and
+$\mathsf{Q}$, ensures that any ground atom with predicate $\mathsf{P}$ is
+independent of any ground atom with predicate $\mathsf{Q}$. In this way, we can
+easily regulate the independence structure of the underlying probability
+distribution. In \cref{sec:counting} we also present a combinatorial argument
+for correctness that counts the number of programs that the model produces for
+various parameter values. We end the paper with two experimental results in
+\cref{sec:experiments}: one investigating how the constraint model scales when
+tasked with producing more complex programs, and one showing how the model can
+be used to evaluate and compare probabilistic inference algorithms.
 
@@
 (which is a formula). A \emph{(logic) program} is a set of clauses, and a
-\emph{ProbLog program} is a set of clause-probability pairs.
-
-In the world of constraint satisfaction, we also have \emph{(constraint)
-  variables}, each with a \emph{domain}, whose values are restricted using
-\emph{constraints}. All constraint variables in the model are integer or set
-variables, however, if an integer refers to a logical construct
-(e.g., a logical variable or a constant), we will make no distinction between
-the two and often use names of logical constructs to refer to the underlying
-integers. We say that a constraint variable is \emph{(fully) determined} if its
-domain (at the given moment in the execution) has exactly one value. We will
-often use $\Box$ as a special domain value to indicate a `disabled' (i.e., fixed
-and ignored) part of the model. We write $\arrayd{a}{b}{c}$ to mean that
-$\variable{a}$ is an array of variables of length $b$ such that each element of
-$\variable{a}$ has domain $c$. Similarly, we write $\arrayt{a}{b}{c}$ to denote
-an array $\variable{a}$ of length $b$ such that each element of $\variable{a}$
-has type $\variable{c}$. Finally, we assume that all arrays start with index
-zero.
+\emph{\textsc{ProbLog} program} is a set of clause-probability pairs.
+
+In the world of CSPs, we also have \emph{(constraint) variables}, each with a
+\emph{domain}, whose values are restricted using \emph{constraints}. All
+constraint variables in the model are integer or set variables, however, if an
+integer refers to a logical construct (e.g., a logical variable or a constant),
+we will make no distinction between the two and often use names of logical
+constructs to refer to the underlying integers. We say that a constraint
+variable is \emph{(fully) determined} if its domain (at the given moment in the
+execution) has exactly one value. We will often use $\Box$ as a special domain
+value to indicate a `disabled' (i.e., fixed and ignored) part of the model. We
+write $\arrayd{a}{b}{c}$ to mean that $\variable{a}$ is an array of variables of
+length $b$ such that each element of $\variable{a}$ has domain $c$. Similarly,
+we write $\arrayt{a}{b}{c}$ to denote an array $\variable{a}$ of length $b$ such
+that each element of $\variable{a}$ has type $\variable{c}$. Finally, we assume
+that all arrays start with index zero.
 
@@
 In this section, we present custom constraints for stratification and
-independence. Stratification is a condition that both logic programs and
-probabilistic logic programs need to satisfy to ensure a unique answer
-to every query
-\cite{DBLP:journals/jlp/BalbinPRM91,DBLP:conf/padl/MantadelisR17}, while
-independence is a fundamental concept in probability theory that imposes
-structure on the probability distribution and simplifies inference. In the
-context of probabilistic logic programming languages, these two seemingly
-disparate concepts can be defined using the same building block, i.e., a
-predicate dependency graph. Constraints are usually presented with two
+independence. Stratification is a condition necessary for probabilistic logic
+programs \cite{DBLP:conf/padl/MantadelisR17} and often enforced on logic
+programs \cite{DBLP:journals/tcs/Bidoit91} that helps to ensure a unique answer
+to every query, while independence is a fundamental concept in probability
+theory that imposes structure on the probability distribution and simplifies
+inference. In the context of probabilistic logic programming languages, these
+two seemingly disparate concepts can be defined using the same building block,
+i.e., a predicate dependency graph. Constraints are usually presented with two
 algorithms: one for \emph{entailment} checking, i.e., checking if the (partially
@@
 $G_{\mathscr{P}}$ has a cycle with at least one negative edge. A program
-$\mathscr{P}$ is \emph{stratified} if $G_{\mathscr{P}}$ has no negative cycles.
-Thus a simple entailment algorithm for stratification can be constructed by
-selecting all clauses, all predicates of which are fully determined, and looking
-for negative cycles in the dependency graph constructed based on those clauses
-using an algorithm such as Bellman-Ford.
+$\mathscr{P}$ is \emph{stratified} if $G_{\mathscr{P}}$ has no negative
+cycles\footnote{This definition is an extension of a well-known result for logic
+programs \cite{DBLP:journals/jlp/BalbinPRM91} to probabilistic logic programs
+with arbitrary complex clause bodies.}. Thus a simple entailment algorithm for
+stratification can be constructed by selecting all clauses, all predicates of
+which are fully determined, and looking for negative cycles in the dependency
+graph constructed based on those clauses using an algorithm such as
+Bellman-Ford.
 
@@
 
-\section{Experimental Results}
-
-This section presents two empirical investigations: in \cref{sec:experiment1} we
-examine the scalability of our constraint model with respect to its parameters
-and in \cref{sec:experiment2} we demonstrate how the model can be used to
-compare inference algorithms and describe their behaviour across a wide range of
+\section{Experimental Results} \label{sec:experiments}
+
+This section presents two experiments: in \cref{sec:experiment1} we examine the
+scalability of our constraint model with respect to its parameters and in
+\cref{sec:experiment2} we demonstrate how the model can be used to compare
+inference algorithms and describe their behaviour across a wide range of
 programs---something that has not been done before. The experiments were run on
@@
 Linux~5.6.11-arch1-1 operating system. The constraint model was implemented in
-Java~8 with Choco~4.10.2. All inference algorithms are implemented in
-ProbLog~2.1.0.39 and were run using Python~3.8.2 with PySDD~0.2.10 and
-PyEDA~0.28.0. For both sets of experiments, we generate programs without
-negative cycles and use a \SI{60}{\second} timeout.
+Java~8 with \textsc{Choco}~4.10.2 \cite{choco}. All inference algorithms are
+implemented in \textsc{ProbLog}~2.1.0.39 and were run using Python~3.8.2 with
+PySDD~0.2.10 and PyEDA~0.28.0. For both sets of experiments, we generate
+programs without negative cycles and use a \SI{60}{\second} timeout.
 
@@
 whether the model is efficient enough to generate reasonably-sized programs and
-gaining insight into what parameter values make the constraint satisfaction
-problem harder. For $|\predicates{}|$, $|\variables{}|$, $|\constants{}|$,
-$\maxNumNodes{}$, and $\maxNumClauses{} - |\predicates{}|$ (i.e., the number of
-clauses in addition to the mandatory $|\predicates{}|$ clauses), we assign all
-combinations of 1, 2, 4, 8. $\maxArity{}$ is assigned to values 1--4. For each
-$|\predicates{}|$, we also iterate over all possible numbers of independent
-pairs of predicates, ranging from 0 up to $\binom{|\predicates{}|}{2}$. For each
-combination of the above-mentioned parameters, we pick ten random ways to assign
-arities to predicates (such that $\maxArity{}$ occurs at least once) and ten
-random combinations of independent pairs.
+gaining insight into what parameter values make the CSP harder. For
+$|\predicates{}|$, $|\variables{}|$, $|\constants{}|$, $\maxNumNodes{}$, and
+$\maxNumClauses{} - |\predicates{}|$ (i.e., the number of clauses in addition to
+the mandatory $|\predicates{}|$ clauses), we assign all combinations of 1, 2, 4,
+8. $\maxArity{}$ is assigned to values 1--4. For each $|\predicates{}|$, we also
+iterate over all possible numbers of independent pairs of predicates, ranging
+from 0 up to $\binom{|\predicates{}|}{2}$. For each combination of the
+above-mentioned parameters, we pick ten random ways to assign arities to
+predicates (such that $\maxArity{}$ occurs at least once) and ten random
+combinations of independent pairs.
 
@@
   \input{line_plots.tex}%
-  \caption{Mean inference time for a range of ProbLog inference algorithms as
-    a function of the total number of facts in the program and the proportion of
-    independent pairs of predicates. For the second plot, the number of facts is
-    fixed at $10^5$.}
+  \caption{Mean inference time for a range of \textsc{ProbLog} inference
+    algorithms as a function of the total number of facts in the program and the
+    proportion of independent pairs of predicates. For the second plot, the
+    number of facts is fixed at $10^5$.}
   \label{fig:line_plots}

### 2020-05-18 text/paper2/paper.tex
Editing

@@
 \cite{DBLP:conf/iclp/Namasivayam09,DBLP:conf/lpnmr/NamasivayamT09} or clauses of
-the form $a \gets \neg b$.
+the form $a \gets \neg b$ \cite{DBLP:journals/tocl/WenWSL16}.
 
@@
 atoms using conjunction $\land$, disjunction $\lor$, and negation
-$\neg$\footnote{One can add a couple of extra constraints to restrict the
-  generated programs to logic programs that only allow a single disjunction with
-  positive and negative literals.}.
-A \emph{clause} is a pair of a \emph{head} (which is an atom) and a \emph{body}
-(which is a formula). A \emph{(logic) program} is a set of clauses, and a
-\emph{\textsc{ProbLog} program} is a set of clause-probability pairs.
+$\neg$. A \emph{clause} is a pair of a \emph{head} (which is an atom) and a
+\emph{body} (which is a formula\footnote{Our model supports arbitrarily complex
+  bodies of clauses because \textsc{ProbLog} does too. However, one can easily
+  restrict our representation of a body to a single disjunction of literals by
+  adding a couple of additional constraints.}). A \emph{(logic) program} is a
+set of clauses, and a \emph{\textsc{ProbLog} program} is a set of
+clause-probability pairs.
 
@@
 
-\paragraph{Parameters of the Model.} We begin defining the parameters of our
+\paragraph{Parameters of the model.} We begin defining the parameters of our
 model by initialising sets and lists of the primitives used in constructing
@@
 notational convenience, we also set $\maxArity{} = \max \arities{}$. Next, we
-need a measure of how complex a body of a clause can be. As each body is
-represented by a tree (see \cref{sec:bodies}), we set $\maxNumNodes{} \ge 1$ to
+need a measure of how complex a body of a clause can be. As we represent each
+body by a tree (see \cref{sec:bodies}), we set $\maxNumNodes{} \ge 1$ to
 be the maximum number of nodes in the tree representation of any clause. We also
@@
 \cref{sec:variable_symmetry}. This $\variable{predicate}$ variable has a
-corresponding arity that depends on the value of $\variable{predicate}$. We can
+corresponding arity that depends on the $\variable{predicate}$. We can
 define $\variable{arity} \in [0, \maxArity{}]$ as the arity of the
@@
 constraint uses a set of pairs of the form $(p, a)$, where $p$ ranges over all
-possible values of $\variable{predicate}$, and $a$ is either the arity of
+possible values of the $\variable{predicate}$, and $a$ is either the arity of
 predicate $p$ or zero. Having defined arity, we can now fix the superfluous
@@
 the structure of the tree using the following two rules:
-$\variable{structure}[i] = i$ means that the $i$-th node is a root, and
-$\variable{structure}[i] = j$ (for $j \ne i$) means that the $i$-th node's
+$\variable{structure}[i] = i$ means that the $i$th node is a root, and
+$\variable{structure}[i] = j$ (for $j \ne i$) means that the $i$th node's
 parent is node $j$. The second part is the array
 $\arrayt{values}{\maxNumNodes{}}{Node}$ such that $\variable{values}[i]$ holds
-the value of the $i$-th node, i.e., a representation of the atom or logical
+the value of the $i$th node, i.e., a representation of the atom or logical
 operator.
@@
 nodes outside the main tree, and, when located at the zeroth node, it can
-represent a clause with no body. Thus, we can say that only root nodes can have
-$\top$ as the value:
+represent a clause with an empty body. Thus, we can say that only root nodes can
+have $\top$ as the value.
 \begin{constraint}
@@
 Finally, we add a way to disable a clause by setting its head predicate to
-$\Box$:
+$\Box$.
 \begin{constraint}
@@
 Here, a value of zero means that the variable does not occur in the clause (this
-choice is motivated by subsequent constraints). This means that the definition
-of $\variable{intros}$ shifts all indices by one. Lastly, we add the variable
-symmetry-breaking constraint for sorting $\variable{intros}$. In other words, we
-constrain the model so that the variable listed first (in whatever order
-$\variables{}$ is presented in) has to occur first in our representation of a
-clause.
+choice is motivated by subsequent constraints). As a consequence, all other
+indices are shifted by one. Having set this up, we can now eliminate variable
+symmetries simply by sorting $\variable{intros}$. In other words, we constrain
+the model so that the variable listed first (in whatever order $\variables{}$ is
+presented in) has to occur first in our representation of a clause.
 
@@
 \end{constraint}
-The reason why we used zero to represent an unused variable is so that we could
+The reason why we use zero to represent an unused variable is so that we could
 now use the `all different except zero' constraint for the $\variable{intros}$
@@
 $\arities{}$, $\variables{}$, and $\constants{}$\footnote{We checked that
-  our model agrees with the derived combinatorial formula in close to a thousand
+  our model agrees with the derived combinatorial formula in up to a thousand
   different scenarios. The details of this empirical investigation are omitted
@@
 one node but otherwise leaves the task unchanged. If the first operation is not
-negation, then it must be either conjunction or disjunction (hence the
+a negation, then it must be either conjunction or disjunction (hence the
 coefficient `2'). In the first sum, $k$ represents the number of children of the
@@
 \]
-Here, the empty clause is considered separately.
 
@@
 \]
-The first term is the number of ways select $n$ constants. The parameter $k$ is
-the number of variables used in the clause, and $s_1, \dots, s_k$ mark the first
-occurrence of each variable. For each gap between any two introductions (or
-before the first introduction, or after the last introduction), we have
+The first term is the number of ways to select $n$ constants. The parameter $k$
+is the number of variables used in the clause, and $s_1, \dots, s_k$ mark the
+first occurrence of each variable. For each gap between any two introductions
+(or before the first introduction, or after the last introduction), we have
 $s_{i+1}-s_i-1$ spaces to be filled with any of the $|\constants{}|$ constants
@@
 Let us order the elements of $\predicates{}$, and let $a_i$ be the arity of the
-$i$-th predicate. The number of programs is then:
+$i$th predicate. The number of programs is then:
 \[
@@
 
-Let $\mathscr{P}$ be a probabilistic logic program with predicates
+Let $\mathscr{P}$ be a probabilistic logic program with its set of predicates
 $\predicates{}$. Its \emph{(predicate) dependency graph} is a directed graph
-$G_{\mathscr{P}}$ with $\predicates{}$ as nodes and an edge between $\mathsf{P},
-\mathsf{Q} \in \predicates{}$ if there is a clause in $\mathscr{P}$ with
-$\mathsf{Q}$ as the head and $\mathsf{P}$ mentioned in the body. We say that the
-edge is \emph{negative} if there exists a clause with $\mathsf{Q}$ as the head
-and at least one instance of $\mathsf{P}$ at the body such that the path from
-the root to the $\mathsf{P}$ node in the tree representation of the clause
-passes through at least one negation node; otherwise, it is \emph{positive}. We
-say that $\mathscr{P}$ (or $G_{\mathscr{P}}$) has a \emph{negative cycle} if
-$G_{\mathscr{P}}$ has a cycle with at least one negative edge. A program
-$\mathscr{P}$ is \emph{stratified} if $G_{\mathscr{P}}$ has no negative
-cycles\footnote{This definition is an extension of a well-known result for logic
-programs \cite{DBLP:journals/jlp/BalbinPRM91} to probabilistic logic programs
-with arbitrary complex clause bodies.}. Thus a simple entailment algorithm for
-stratification can be constructed by selecting all clauses, all predicates of
-which are fully determined, and looking for negative cycles in the dependency
-graph constructed based on those clauses using an algorithm such as
-Bellman-Ford.
+$G_{\mathscr{P}}$ with elements of $\predicates{}$ as nodes and an edge between
+$\mathsf{P}, \mathsf{Q} \in \predicates{}$ if there is a clause in $\mathscr{P}$
+with $\mathsf{Q}$ as the head and $\mathsf{P}$ mentioned in the body. We say
+that the edge is \emph{negative} if there exists a clause with $\mathsf{Q}$ as
+the head and at least one instance of $\mathsf{P}$ at the body such that the
+path from the root to the $\mathsf{P}$ node in the tree representation of the
+clause passes through at least one negation node; otherwise, it is
+\emph{positive}. We say that $\mathscr{P}$ (or $G_{\mathscr{P}}$) has a
+\emph{negative cycle} if $G_{\mathscr{P}}$ has a cycle with at least one
+negative edge. A program $\mathscr{P}$ is \emph{stratified} if $G_{\mathscr{P}}$
+has no negative cycles\footnote{This definition is an extension of a well-known
+  result for logic programs \cite{DBLP:journals/jlp/BalbinPRM91} to
+  probabilistic logic programs with arbitrary complex clause bodies.}. Thus a
+simple entailment algorithm for stratification can be constructed by selecting
+all clauses, all predicates of which are fully determined, and looking for
+negative cycles in the dependency graph constructed based on those clauses using
+an algorithm such as Bellman-Ford.
 
@@
     \end{tikzpicture}%
-    \captionof{figure}{The predicate dependency graph of the program in
+    \captionof{figure}{The predicate dependency graph of the program from
       \cref{ex:program}. Positive edges are labelled with `$+$', and negative
@@
 denoted by $\{ 0, 1 \}$. Each such path characterises a \emph{(potential)
-  dependency} $\mathsf{Q}$ for $\mathsf{P}$. We can put each such dependency
-into one out of three classes depending on the number of undetermined edges on
-the path. These classes are outlined in \cref{tbl:dependencies}, where $p$
-represents the dependency predicate $\mathsf{Q}$, and, in the case of
-$\AlmostDetermined{}$, $(s, t) \in \predicates{}^2$ is the one undetermined edge
-on the path. For a dependency $d$---regardless of its exact type---we will refer
-to its predicate $p$ as $d.\mathsf{predicate}$. In describing the algorithms, we
-will use an underscore to replace any of $p$, $s$, $t$ in situations where the
-name is unimportant.
+  dependency} $\mathsf{Q}$ for $\mathsf{P}$. We classify all such dependencies
+into three classes depending on the number of undetermined edges on the path.
+These classes are outlined in \cref{tbl:dependencies}, where $p$ represents the
+dependency predicate $\mathsf{Q}$, and, in the case of $\AlmostDetermined{}$,
+$(s, t) \in \predicates{}^2$ is the one undetermined edge on the path. For a
+dependency $d$---regardless of its exact type---we will refer to its predicate
+$p$ as $d.\mathsf{predicate}$. In describing the algorithms, we will use `$\_$'
+to replace any of $p$, $s$, $t$ in situations where the name is unimportant.
 
@@
 
-Each entailment algorithm returns one out of three different values:
+Each entailment algorithm returns one out of three values:
 \textsc{true} if the constraint is guaranteed to hold, \textsc{false} if the
@@
 
-This section presents two experiments: in \cref{sec:experiment1} we examine the
-scalability of our constraint model with respect to its parameters and in
-\cref{sec:experiment2} we demonstrate how the model can be used to compare
-inference algorithms and describe their behaviour across a wide range of
-programs---something that has not been done before. The experiments were run on
-a system with Intel Core i5-8250U processor, \SI{8}{\giga\byte} RAM, and Arch
-Linux~5.6.11-arch1-1 operating system. The constraint model was implemented in
-Java~8 with \textsc{Choco}~4.10.2 \cite{choco}. All inference algorithms are
-implemented in \textsc{ProbLog}~2.1.0.39 and were run using Python~3.8.2 with
-PySDD~0.2.10 and PyEDA~0.28.0. For both sets of experiments, we generate
-programs without negative cycles and use a \SI{60}{\second} timeout.
+We now present the results of two experiments: in \cref{sec:experiment1} we
+examine the scalability of our constraint model with respect to its parameters
+and in \cref{sec:experiment2} we demonstrate how the model can be used to
+compare inference algorithms and describe their behaviour across a wide range of
+programs. The experiments were run on a system with Intel Core i5-8250U
+processor, \SI{8}{\giga\byte} RAM, and Arch Linux~5.6.11-arch1-1 operating
+system. The constraint model was implemented in Java~8 with
+Choco~4.10.2 \cite{choco}. All inference algorithms are implemented in
+\textsc{ProbLog}~2.1.0.39 and were run using Python~3.8.2 with PySDD~0.2.10 and
+PyEDA~0.28.0. For both sets of experiments, we generate programs without
+negative cycles and use a \SI{60}{\second} timeout.
 
@@
 making changes that have no hope of fixing the contradiction. Thus, we partition
-all decision variables into an ordered list of groups, and require the values of
+all decision variables into an ordered list of groups and require the values of
 all variables from one group to be determined before moving to the next group.
@@
 decision variables from the first clause before proceeding to the next. The
-decision variables within each clause are divided into:
+decision variables within each clause are divided into
 \begin{enumerate*}
@@
 tree grows as a function of each parameter (the plot for the median is very
-similar). The growth of each curve suggest how well/poorly the model scales with
-higher values of the parameter. From this plot, it is clear that
-$\maxNumNodes{}$ is the limiting factor. This is because some tree structures
-can be impossible to fill with predicates without creating either a negative
-cycle or a forbidden dependency, and such trees become more common as the number
-of nodes increases. Likewise, a higher number of predicates complicates the
-situation as well.
+similar). The growth of each curve suggests how the model scales with higher
+values of the parameter. From this plot, it is clear that $\maxNumNodes{}$ is
+the limiting factor. This is because some tree structures can be impossible to
+fill with predicates without creating either a negative cycle or a forbidden
+dependency, and such trees become more common as the number of nodes increases.
+Likewise, a higher number of predicates complicates the situation as well.
 
@@
 such that the head atom has at least one variable, and \emph{facts} are clauses
-with no bodies and no variables. We use our constraint model to generate the
+with empty bodies and no variables. We use our constraint model to generate the
 rules according to the following parameter values: $|\predicates{}|,
@@
 
-Out of \num{11310} generated problem instances, about \SI{35}{\percent} were
-discarded because one or more algorithms were not able to ground the instance in
-an unambiguous way. The first observation (pictured in \cref{fig:line_plots}) is
-that the algorithms are remarkably similar, i.e., the differences in performance
-are small and consistent across all parameter values (including parameters not
-shown in the figure). Unsurprisingly, the most important predictor of inference
-time is the number of facts. However, after fixing the number of facts to a
-constant value, we can still observe that inference becomes harder with higher
-arity predicates as well as when facts are mostly probabilistic (see
-\cref{fig:bars}). Finally, according to \cref{fig:line_plots}, the independence
-structure of a program does not affect inference time, i.e., state-of-the-art
-inference algorithms---although they are supposed to
+Out of over \num{11000} generated problem instances, about \SI{35}{\percent} were
+discarded because one or more algorithms were not able to ground the instance
+unambiguously. The first observation (pictured in \cref{fig:line_plots}) is that
+the algorithms are remarkably similar, i.e., the differences in performance are
+small and consistent across all parameter values (including parameters not shown
+in the figure). Unsurprisingly, the most important predictor of inference time
+is the number of facts. However, after fixing the number of facts to a constant
+value, we can still observe that inference becomes harder with higher arity
+predicates as well as when facts are mostly probabilistic (see \cref{fig:bars}).
+Finally, according to \cref{fig:line_plots}, the independence structure of a
+program does not affect inference time, i.e., state-of-the-art inference
+algorithms---although they are supposed to
 \cite{DBLP:conf/uai/FierensBTGR11}---do not exploit situations where separate
@@
 
-We presented a constraint model for generating both logic programs and
+We described a constraint model for generating both logic programs and
 probabilistic logic programs. The model avoids unnecessary symmetries, is
@@
 
-Also note that our model treats logically equivalent but syntactically
+As a side note, our model treats logically equivalent but syntactically
 different formulas as different. This is so in part because designing a

### 2020-05-21 text/paper2/paper.tex
Incorporating some feedback

@@
 \usepackage[binary-units]{siunitx}
-\usepackage[inline]{enumitem}
+\usepackage[inline,shortlabels]{enumitem}
 \usepackage{capt-of}
@@
 
-%The abstract should briefly summarize the contents of the paper in
-%150--250 words.
 \begin{abstract}
-  We present a novel approach to generating random logic programs and
-  random probabilistic logic programs using constraint programming. The
-  generated programs are useful in empirical testing of inference algorithms,
-  random data generation, and program learning. This approach has a major
-  advantage in that one can easily add additional conditions for the generated
-  programs. As an example of this, we introduce a new constraint for predicate
-  independence with efficient propagation and entailment algorithms, allowing
-  one to generate programs that have a certain independence structure. Finally,
-  we provide a combinatorial argument for the correctness of the model,
-  describe how the parameters of the model affect the empirical difficulty of
-  the program generation task, and use the model to compare probabilistic
-  inference algorithms across a range of synthetic problems.
+  Testing algorithms across a wide range of problem instances is crucial to
+  ensure the validity of any claim about one algorithm's superiority over
+  another. However, when it comes to inference algorithms for probabilistic
+  logic programs, experimental evaluations are limited to only a few programs.
+  Existing methods to generate random logic programs are limited to
+  propositional programs and often impose stringent syntactic restrictions. We
+  present a novel approach to generating random logic programs and random
+  probabilistic logic programs using constraint programming, introducing a new
+  constraint to control the independence structure of the underlying probability
+  distribution. We also provide a combinatorial argument for the correctness of
+  the model, show how the model scales with parameter values, and use the model
+  to compare probabilistic inference algorithms across a range of synthetic
+  problems. Our model allows inference algorithm developers to evaluate and
+  compare the algorithms across a wide range of instances, providing a detailed
+  picture of their (comparative) strengths and weaknesses.
 
@@
 \end{abstract}
-
-% TODO: proofread, run a grammar checker on everything
 
@@
 complex SRL models. With the enhanced structure, however, inference becomes more
-challenging as algorithms have to correctly handle hard and soft logical
-constraints. At the moment, we have no precise way of evaluating and comparing
-different inference algorithms. Incidentally, if one were to survey the
-literature, one often finds that an inference algorithm is only tested on 1--4
-data sets
+challenging. At the moment, we have no precise way of evaluating and comparing
+inference algorithms. Incidentally, if one were to survey the literature, one
+often finds that an inference algorithm is only tested on a small number (1--4)
+of data sets
 \cite{DBLP:conf/ecai/BruynoogheMKGVJR10,DBLP:journals/tplp/KimmigDRCR11,DBLP:conf/ijcai/VlasselaerBKMR15},
 originating from areas such as social networks, citation patterns, and
-biological data. But how confidently can we claim that an algorithm works well
-if it is only tested on a few types of problems?
+biological data. But how confident can we be that an algorithm works well if it
+is only tested on a few problems?
 
@@
 
-In \cref{sec:heads,sec:bodies,sec:variable_symmetry}, we introduce a
+In this work (\cref{sec:heads,sec:bodies,sec:variable_symmetry}), we introduce a
 constraint-based representation for logic programs based on simple parameters
@@
 \cite{DBLP:conf/ijcai/RaedtKT07} and non-probabilistic \textsc{Prolog} programs.
-This is both the first time the problem of generating random logic programs has
-been approached in its full generality (i.e., including first-order clauses with
-variables) and the first time inference algorithms for probabilistic logic
-programs can be evaluated on more than a handful of instances.
+To the best of our knowledge, this is the first work that
+\begin{enumerate*}[(a)]
+\item addresses the problem of generating random logic programs in its full
+  generality (i.e., including first-order clauses with variables), and
+\item compares and evaluates inference algorithms for probabilistic logic
+  programs on more than a handful of instances.
+\end{enumerate*}
 
@@
 The basic primitives of logic programs are \emph{constants}, \emph{(logic)
-  variables}, and \emph{predicates}. Each predicate has an \emph{arity} that
-defines the number of terms that it can be applied to. A \emph{term} is either a
-variable or a constant, and an \emph{atom} is a predicate of arity $n$ applied
-to $n$ terms. A \emph{formula} is any well-formed expression that connects
-atoms using conjunction $\land$, disjunction $\lor$, and negation
+  variables}, and \emph{predicates} with their \emph{arities}. A \emph{term} is
+either a variable or a constant, and an \emph{atom} is a predicate of arity $n$
+applied to $n$ terms. A \emph{formula} is any well-formed expression that
+connects atoms using conjunction $\land$, disjunction $\lor$, and negation
 $\neg$. A \emph{clause} is a pair of a \emph{head} (which is an atom) and a
 \emph{body} (which is a formula\footnote{Our model supports arbitrarily complex
-  bodies of clauses because \textsc{ProbLog} does too. However, one can easily
-  restrict our representation of a body to a single disjunction of literals by
-  adding a couple of additional constraints.}). A \emph{(logic) program} is a
-set of clauses, and a \emph{\textsc{ProbLog} program} is a set of
-clause-probability pairs.
+  bodies of clauses (e.g., $\neg\mathsf{P}(X) \lor (\mathsf{Q}(X) \land
+  \mathsf{P}(X))$) because \textsc{ProbLog} does too. However, one can easily
+  restrict our representation of a body to a single conjunction of literals
+  (e.g., $\mathsf{Q}(X) \land \neg\mathsf{P}(X))$) by adding a couple of
+  additional constraints.}). A \emph{(logic) program} is a set of clauses, and a
+\emph{\textsc{ProbLog} program} is a set of clause-probability pairs
+\cite{DBLP:journals/tplp/FierensBRSGTJR15}.
 
@@
 the $\variable{structure}$ array does not matter, i.e., the structure is only
-defined by how the elements link to each other, so we can add a constraint
-saying that $\variable{structure}$ is sorted. Next, since we already have a
+defined by how the elements link to each other, so we can add a constraint for
+sorting the $\variable{structure}$ array. Next, since we already have a
 variable that counts the number of nodes in the main tree, we can fix the
@@
 
-We end the section with several redundant constraints. First, we can state that
-the positions occupied by different terms must be different.
+We end the section with several redundant constraints that make the CSP easier
+to solve. First, we can state that the positions occupied by different terms
+must be different.
 \begin{constraint} \label{constraint:all_diff}
@@
 
-To demonstrate the correctness of the model and explain it in more
-detail, in this section we are going to derive combinatorial expressions for
-counting the number of programs with up to $\maxNumClauses{}$ clauses and up to
-$\maxNumNodes{}$ nodes per clause, and arbitrary $\predicates{}$,
-$\arities{}$, $\variables{}$, and $\constants{}$\footnote{We checked that
-  our model agrees with the derived combinatorial formula in up to a thousand
-  different scenarios. The details of this empirical investigation are omitted
-  as they are not crucial to the thrust of this paper.}. Being able to establish
-two ways to generate the same sequence of numbers (i.e., numbers of programs
-with certain properties and parameters) allows us to gain confidence that the
-constraint model accurately matches our intentions. For this section, we
-introduce the term \emph{total arity} of a body of a clause to refer to the sum
-total of arities of all predicates in the body.
+To demonstrate the correctness of the model, in this section we are going to
+derive combinatorial expressions for counting the number of programs with up to
+$\maxNumClauses{}$ clauses and up to $\maxNumNodes{}$ nodes per clause, and
+arbitrary $\predicates{}$, $\arities{}$, $\variables{}$, and $\constants{}$.
+Being able to establish two ways to generate the same sequence of numbers (i.e.,
+numbers of programs with certain properties and parameters) allows us to gain
+confidence that the constraint model accurately matches our intentions. For this
+section, we introduce the term \emph{total arity} of a body of a clause to refer
+to the sum total of arities of all predicates in the body.
 
@@
 negative edge. A program $\mathscr{P}$ is \emph{stratified} if $G_{\mathscr{P}}$
-has no negative cycles\footnote{This definition is an extension of a well-known
+has no negative cycles.\footnote{This definition is an extension of a well-known
   result for logic programs \cite{DBLP:journals/jlp/BalbinPRM91} to
-  probabilistic logic programs with arbitrary complex clause bodies.}. Thus a
+  probabilistic logic programs with arbitrary complex clause bodies.} Thus a
 simple entailment algorithm for stratification can be constructed by selecting
@@
 decision variables within each clause are divided into
-\begin{enumerate*}
+\begin{enumerate*}[(a)]
 \item the $\variable{structure}$ array,
@@
 We also employ a geometric restart policy, restarting after $10, 10 \times 1.1,
-10 \times 1.1^2, \dots$ contradictions\footnote{Restarts help overcome early
+10 \times 1.1^2, \dots$ contradictions.\footnote{Restarts help overcome early
   mistakes in the search process but can be disabled if one wants to find all
   solutions, in which case search is complete regardless of the variable
-  ordering heuristic.}. We ran close to \num{400000} experiments, investigating
+  ordering heuristic.} We ran close to \num{400000} experiments, investigating
 whether the model is efficient enough to generate reasonably-sized programs and
@@
 entire program (SDDX), while the other one encodes only the part of the program
-relevant to the query (SDD)\footnote{Forward SDDs (FSDDs) and forward BDDs
+relevant to the query (SDD).\footnote{Forward SDDs (FSDDs) and forward BDDs
   (FBDDs)
@@
   omitted because the former uses too much memory and the implementation of the
-  latter seems to be broken at the time of writing.}.
+  latter seems to be broken at the time of writing.}
 
@@
 
+% We checked that our model agrees with the derived combinatorial formula in up
+% to a thousand different scenarios. The details of this empirical investigation
+% are omitted as they are not crucial to the thrust of this paper.
+
 \bibliographystyle{splncs04}

### 2020-05-30 text/paper2/algorithms.tex
New plots

% Created by tikzDevice version 0.12.3 on 2020-05-30 13:08:25
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (346.90,346.90);
\begin{scope}
\path[clip] ( 12.91,260.17) rectangle (124.24,346.90);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 12.91,260.17) rectangle (124.24,346.90);
\end{scope}
\begin{scope}
\path[clip] ( 34.60,290.86) rectangle (118.74,341.40);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 34.60,290.86) rectangle (118.74,341.40);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.60,295.44) --
	(118.74,295.44);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.60,307.95) --
	(118.74,307.95);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.60,320.47) --
	(118.74,320.47);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.60,332.98) --
	(118.74,332.98);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 51.17,290.86) --
	( 51.17,341.40);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 76.67,290.86) --
	( 76.67,341.40);

\path[draw=drawColor,line width= 0.3pt,line join=round] (102.17,290.86) --
	(102.17,341.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.60,301.70) --
	(118.74,301.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.60,314.21) --
	(118.74,314.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.60,326.72) --
	(118.74,326.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.60,339.24) --
	(118.74,339.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 38.43,290.86) --
	( 38.43,341.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 63.92,290.86) --
	( 63.92,341.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.42,290.86) --
	( 89.42,341.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.91,290.86) --
	(114.91,341.40);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 38.43,313.83) --
	( 63.92,305.69) --
	(114.91,313.71);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 38.43,295.89) --
	( 63.92,293.16) --
	(114.91,303.91);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 38.43,305.50) --
	( 63.92,302.49) --
	(114.91,313.03);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 38.43,328.83) --
	( 63.92,329.45) --
	(114.91,339.10);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round] ( 38.43,320.24) --
	( 63.92,323.43) --
	(114.91,332.99);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt on 4pt off 3pt ,line join=round] ( 38.43,330.32) --
	( 63.92,328.96) --
	(114.91,338.63);
\definecolor{drawColor}{RGB}{27,158,119}
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 38.43,313.83) circle (  1.96);
\definecolor{drawColor}{RGB}{217,95,2}
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 38.43,295.89) circle (  1.96);
\definecolor{drawColor}{RGB}{117,112,179}
\definecolor{fillColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 38.43,305.50) circle (  1.96);
\definecolor{drawColor}{RGB}{231,41,138}
\definecolor{fillColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 38.43,328.83) circle (  1.96);
\definecolor{drawColor}{RGB}{102,166,30}
\definecolor{fillColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 38.43,320.24) circle (  1.96);
\definecolor{drawColor}{RGB}{230,171,2}
\definecolor{fillColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 38.43,330.32) circle (  1.96);
\definecolor{drawColor}{RGB}{27,158,119}
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 63.92,305.69) circle (  1.96);
\definecolor{drawColor}{RGB}{217,95,2}
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 63.92,293.16) circle (  1.96);
\definecolor{drawColor}{RGB}{117,112,179}
\definecolor{fillColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 63.92,302.49) circle (  1.96);
\definecolor{drawColor}{RGB}{231,41,138}
\definecolor{fillColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 63.92,329.45) circle (  1.96);
\definecolor{drawColor}{RGB}{102,166,30}
\definecolor{fillColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 63.92,323.43) circle (  1.96);
\definecolor{drawColor}{RGB}{230,171,2}
\definecolor{fillColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 63.92,328.96) circle (  1.96);
\definecolor{drawColor}{RGB}{27,158,119}
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.91,313.71) circle (  1.96);
\definecolor{drawColor}{RGB}{217,95,2}
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.91,303.91) circle (  1.96);
\definecolor{drawColor}{RGB}{117,112,179}
\definecolor{fillColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.91,313.03) circle (  1.96);
\definecolor{drawColor}{RGB}{231,41,138}
\definecolor{fillColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.91,339.10) circle (  1.96);
\definecolor{drawColor}{RGB}{102,166,30}
\definecolor{fillColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.91,332.99) circle (  1.96);
\definecolor{drawColor}{RGB}{230,171,2}
\definecolor{fillColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.91,338.63) circle (  1.96);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 34.60,290.86) rectangle (118.74,341.40);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.65,298.67) {7.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.65,311.18) {7.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.65,323.69) {8.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.65,336.21) {8.5};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.85,301.70) --
	( 34.60,301.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.85,314.21) --
	( 34.60,314.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.85,326.72) --
	( 34.60,326.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.85,339.24) --
	( 34.60,339.24);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 38.43,288.11) --
	( 38.43,290.86);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 63.92,288.11) --
	( 63.92,290.86);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.42,288.11) --
	( 89.42,290.86);

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.91,288.11) --
	(114.91,290.86);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 38.43,279.85) {2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 63.92,279.85) {4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 89.42,279.85) {6};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (114.91,279.85) {8};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 76.67,267.81) {Predicates};
\end{scope}
\begin{scope}
\path[clip] (124.24,260.17) rectangle (235.57,346.90);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (124.24,260.17) rectangle (235.57,346.90);
\end{scope}
\begin{scope}
\path[clip] (145.93,290.86) rectangle (230.07,341.40);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (145.93,290.86) rectangle (230.07,341.40);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (145.93,298.88) --
	(230.07,298.88);

\path[draw=drawColor,line width= 0.3pt,line join=round] (145.93,309.45) --
	(230.07,309.45);

\path[draw=drawColor,line width= 0.3pt,line join=round] (145.93,320.03) --
	(230.07,320.03);

\path[draw=drawColor,line width= 0.3pt,line join=round] (145.93,330.60) --
	(230.07,330.60);

\path[draw=drawColor,line width= 0.3pt,line join=round] (145.93,341.17) --
	(230.07,341.17);

\path[draw=drawColor,line width= 0.3pt,line join=round] (162.50,290.86) --
	(162.50,341.40);

\path[draw=drawColor,line width= 0.3pt,line join=round] (188.00,290.86) --
	(188.00,341.40);

\path[draw=drawColor,line width= 0.3pt,line join=round] (213.49,290.86) --
	(213.49,341.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (145.93,293.59) --
	(230.07,293.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (145.93,304.16) --
	(230.07,304.16);

\path[draw=drawColor,line width= 0.6pt,line join=round] (145.93,314.74) --
	(230.07,314.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (145.93,325.31) --
	(230.07,325.31);

\path[draw=drawColor,line width= 0.6pt,line join=round] (145.93,335.89) --
	(230.07,335.89);

\path[draw=drawColor,line width= 0.6pt,line join=round] (149.75,290.86) --
	(149.75,341.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (175.25,290.86) --
	(175.25,341.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (200.75,290.86) --
	(200.75,341.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (226.24,290.86) --
	(226.24,341.40);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (149.75,319.74) --
	(175.25,314.24) --
	(226.24,300.18);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (149.75,309.41) --
	(175.25,305.28) --
	(226.24,293.16);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (149.75,316.71) --
	(175.25,313.05) --
	(226.24,301.69);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (149.75,336.45) --
	(175.25,339.10) --
	(226.24,320.12);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round] (149.75,333.77) --
	(175.25,329.89) --
	(226.24,317.60);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt on 4pt off 3pt ,line join=round] (149.75,337.33) --
	(175.25,336.51) --
	(226.24,322.03);
\definecolor{drawColor}{RGB}{27,158,119}
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (149.75,319.74) circle (  1.96);
\definecolor{drawColor}{RGB}{217,95,2}
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (149.75,309.41) circle (  1.96);
\definecolor{drawColor}{RGB}{117,112,179}
\definecolor{fillColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (149.75,316.71) circle (  1.96);
\definecolor{drawColor}{RGB}{231,41,138}
\definecolor{fillColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (149.75,336.45) circle (  1.96);
\definecolor{drawColor}{RGB}{102,166,30}
\definecolor{fillColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (149.75,333.77) circle (  1.96);
\definecolor{drawColor}{RGB}{230,171,2}
\definecolor{fillColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (149.75,337.33) circle (  1.96);
\definecolor{drawColor}{RGB}{27,158,119}
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.25,314.24) circle (  1.96);
\definecolor{drawColor}{RGB}{217,95,2}
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.25,305.28) circle (  1.96);
\definecolor{drawColor}{RGB}{117,112,179}
\definecolor{fillColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.25,313.05) circle (  1.96);
\definecolor{drawColor}{RGB}{231,41,138}
\definecolor{fillColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.25,339.10) circle (  1.96);
\definecolor{drawColor}{RGB}{102,166,30}
\definecolor{fillColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.25,329.89) circle (  1.96);
\definecolor{drawColor}{RGB}{230,171,2}
\definecolor{fillColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.25,336.51) circle (  1.96);
\definecolor{drawColor}{RGB}{27,158,119}
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (226.24,300.18) circle (  1.96);
\definecolor{drawColor}{RGB}{217,95,2}
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (226.24,293.16) circle (  1.96);
\definecolor{drawColor}{RGB}{117,112,179}
\definecolor{fillColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (226.24,301.69) circle (  1.96);
\definecolor{drawColor}{RGB}{231,41,138}
\definecolor{fillColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (226.24,320.12) circle (  1.96);
\definecolor{drawColor}{RGB}{102,166,30}
\definecolor{fillColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (226.24,317.60) circle (  1.96);
\definecolor{drawColor}{RGB}{230,171,2}
\definecolor{fillColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (226.24,322.03) circle (  1.96);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (145.93,290.86) rectangle (230.07,341.40);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (140.98,290.56) {6.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (140.98,301.13) {7.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (140.98,311.71) {7.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (140.98,322.28) {8.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (140.98,332.86) {8.5};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (143.18,293.59) --
	(145.93,293.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (143.18,304.16) --
	(145.93,304.16);

\path[draw=drawColor,line width= 0.6pt,line join=round] (143.18,314.74) --
	(145.93,314.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (143.18,325.31) --
	(145.93,325.31);

\path[draw=drawColor,line width= 0.6pt,line join=round] (143.18,335.89) --
	(145.93,335.89);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (149.75,288.11) --
	(149.75,290.86);

\path[draw=drawColor,line width= 0.6pt,line join=round] (175.25,288.11) --
	(175.25,290.86);

\path[draw=drawColor,line width= 0.6pt,line join=round] (200.75,288.11) --
	(200.75,290.86);

\path[draw=drawColor,line width= 0.6pt,line join=round] (226.24,288.11) --
	(226.24,290.86);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (149.75,279.85) {2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (175.25,279.85) {4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (200.75,279.85) {6};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (226.24,279.85) {8};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (188.00,267.81) {Variables};
\end{scope}
\begin{scope}
\path[clip] (235.57,260.17) rectangle (346.90,346.90);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (235.57,260.17) rectangle (346.90,346.90);
\end{scope}
\begin{scope}
\path[clip] (250.42,290.86) rectangle (341.40,341.40);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (250.42,290.86) rectangle (341.40,341.40);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (250.42,301.05) --
	(341.40,301.05);

\path[draw=drawColor,line width= 0.3pt,line join=round] (250.42,314.08) --
	(341.40,314.08);

\path[draw=drawColor,line width= 0.3pt,line join=round] (250.42,327.12) --
	(341.40,327.12);

\path[draw=drawColor,line width= 0.3pt,line join=round] (250.42,340.15) --
	(341.40,340.15);

\path[draw=drawColor,line width= 0.3pt,line join=round] (268.34,290.86) --
	(268.34,341.40);

\path[draw=drawColor,line width= 0.3pt,line join=round] (295.91,290.86) --
	(295.91,341.40);

\path[draw=drawColor,line width= 0.3pt,line join=round] (323.48,290.86) --
	(323.48,341.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (250.42,294.53) --
	(341.40,294.53);

\path[draw=drawColor,line width= 0.6pt,line join=round] (250.42,307.57) --
	(341.40,307.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] (250.42,320.60) --
	(341.40,320.60);

\path[draw=drawColor,line width= 0.6pt,line join=round] (250.42,333.64) --
	(341.40,333.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.55,290.86) --
	(254.55,341.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (282.12,290.86) --
	(282.12,341.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (309.69,290.86) --
	(309.69,341.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (337.26,290.86) --
	(337.26,341.40);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.55,313.91) --
	(282.12,324.40) --
	(337.26,297.39);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (254.55,307.70) --
	(282.12,318.43) --
	(337.26,293.16);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (254.55,313.15) --
	(282.12,322.72) --
	(337.26,297.68);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (254.55,325.94) --
	(282.12,339.01) --
	(337.26,308.68);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round] (254.55,322.23) --
	(282.12,334.34) --
	(337.26,307.90);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt on 4pt off 3pt ,line join=round] (254.55,326.00) --
	(282.12,339.10) --
	(337.26,307.80);
\definecolor{drawColor}{RGB}{27,158,119}
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (254.55,313.91) circle (  1.96);
\definecolor{drawColor}{RGB}{217,95,2}
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (254.55,307.70) circle (  1.96);
\definecolor{drawColor}{RGB}{117,112,179}
\definecolor{fillColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (254.55,313.15) circle (  1.96);
\definecolor{drawColor}{RGB}{231,41,138}
\definecolor{fillColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (254.55,325.94) circle (  1.96);
\definecolor{drawColor}{RGB}{102,166,30}
\definecolor{fillColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (254.55,322.23) circle (  1.96);
\definecolor{drawColor}{RGB}{230,171,2}
\definecolor{fillColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (254.55,326.00) circle (  1.96);
\definecolor{drawColor}{RGB}{27,158,119}
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (282.12,324.40) circle (  1.96);
\definecolor{drawColor}{RGB}{217,95,2}
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (282.12,318.43) circle (  1.96);
\definecolor{drawColor}{RGB}{117,112,179}
\definecolor{fillColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (282.12,322.72) circle (  1.96);
\definecolor{drawColor}{RGB}{231,41,138}
\definecolor{fillColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (282.12,339.01) circle (  1.96);
\definecolor{drawColor}{RGB}{102,166,30}
\definecolor{fillColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (282.12,334.34) circle (  1.96);
\definecolor{drawColor}{RGB}{230,171,2}
\definecolor{fillColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (282.12,339.10) circle (  1.96);
\definecolor{drawColor}{RGB}{27,158,119}
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (337.26,297.39) circle (  1.96);
\definecolor{drawColor}{RGB}{217,95,2}
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (337.26,293.16) circle (  1.96);
\definecolor{drawColor}{RGB}{117,112,179}
\definecolor{fillColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (337.26,297.68) circle (  1.96);
\definecolor{drawColor}{RGB}{231,41,138}
\definecolor{fillColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (337.26,308.68) circle (  1.96);
\definecolor{drawColor}{RGB}{102,166,30}
\definecolor{fillColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (337.26,307.90) circle (  1.96);
\definecolor{drawColor}{RGB}{230,171,2}
\definecolor{fillColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (337.26,307.80) circle (  1.96);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (250.42,290.86) rectangle (341.40,341.40);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (245.47,291.50) {6};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (245.47,304.53) {7};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (245.47,317.57) {8};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (245.47,330.61) {9};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (247.67,294.53) --
	(250.42,294.53);

\path[draw=drawColor,line width= 0.6pt,line join=round] (247.67,307.57) --
	(250.42,307.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] (247.67,320.60) --
	(250.42,320.60);

\path[draw=drawColor,line width= 0.6pt,line join=round] (247.67,333.64) --
	(250.42,333.64);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.55,288.11) --
	(254.55,290.86);

\path[draw=drawColor,line width= 0.6pt,line join=round] (282.12,288.11) --
	(282.12,290.86);

\path[draw=drawColor,line width= 0.6pt,line join=round] (309.69,288.11) --
	(309.69,290.86);

\path[draw=drawColor,line width= 0.6pt,line join=round] (337.26,288.11) --
	(337.26,290.86);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (254.55,279.85) {2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (282.12,279.85) {4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (309.69,279.85) {6};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (337.26,279.85) {8};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (295.91,267.81) {Nodes};
\end{scope}
\begin{scope}
\path[clip] ( 12.91,173.45) rectangle (124.24,260.17);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 12.91,173.45) rectangle (124.24,260.17);
\end{scope}
\begin{scope}
\path[clip] ( 27.76,204.13) rectangle (118.74,254.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 27.76,204.13) rectangle (118.74,254.67);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 27.76,211.92) --
	(118.74,211.92);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 27.76,224.78) --
	(118.74,224.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 27.76,237.63) --
	(118.74,237.63);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 27.76,250.49) --
	(118.74,250.49);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 52.57,204.13) --
	( 52.57,254.67);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 93.93,204.13) --
	( 93.93,254.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 27.76,205.49) --
	(118.74,205.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 27.76,218.35) --
	(118.74,218.35);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 27.76,231.21) --
	(118.74,231.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 27.76,244.06) --
	(118.74,244.06);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.89,204.13) --
	( 31.89,254.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.25,204.13) --
	( 73.25,254.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.60,204.13) --
	(114.60,254.67);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.89,206.50) --
	( 73.25,232.39) --
	(114.60,246.53);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 31.89,206.43) --
	( 73.25,230.60) --
	(114.60,244.33);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 31.89,206.59) --
	( 73.25,232.14) --
	(114.60,246.19);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 31.89,206.63) --
	( 73.25,235.27) --
	(114.60,252.37);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round] ( 31.89,206.61) --
	( 73.25,234.81) --
	(114.60,250.70);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt on 4pt off 3pt ,line join=round] ( 31.89,206.61) --
	( 73.25,235.71) --
	(114.60,251.98);
\definecolor{drawColor}{RGB}{27,158,119}
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 31.89,206.50) circle (  1.96);
\definecolor{drawColor}{RGB}{217,95,2}
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 31.89,206.43) circle (  1.96);
\definecolor{drawColor}{RGB}{117,112,179}
\definecolor{fillColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 31.89,206.59) circle (  1.96);
\definecolor{drawColor}{RGB}{231,41,138}
\definecolor{fillColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 31.89,206.63) circle (  1.96);
\definecolor{drawColor}{RGB}{102,166,30}
\definecolor{fillColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 31.89,206.61) circle (  1.96);
\definecolor{drawColor}{RGB}{230,171,2}
\definecolor{fillColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 31.89,206.61) circle (  1.96);
\definecolor{drawColor}{RGB}{27,158,119}
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 73.25,232.39) circle (  1.96);
\definecolor{drawColor}{RGB}{217,95,2}
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 73.25,230.60) circle (  1.96);
\definecolor{drawColor}{RGB}{117,112,179}
\definecolor{fillColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 73.25,232.14) circle (  1.96);
\definecolor{drawColor}{RGB}{231,41,138}
\definecolor{fillColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 73.25,235.27) circle (  1.96);
\definecolor{drawColor}{RGB}{102,166,30}
\definecolor{fillColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 73.25,234.81) circle (  1.96);
\definecolor{drawColor}{RGB}{230,171,2}
\definecolor{fillColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 73.25,235.71) circle (  1.96);
\definecolor{drawColor}{RGB}{27,158,119}
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.60,246.53) circle (  1.96);
\definecolor{drawColor}{RGB}{217,95,2}
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.60,244.33) circle (  1.96);
\definecolor{drawColor}{RGB}{117,112,179}
\definecolor{fillColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.60,246.19) circle (  1.96);
\definecolor{drawColor}{RGB}{231,41,138}
\definecolor{fillColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.60,252.37) circle (  1.96);
\definecolor{drawColor}{RGB}{102,166,30}
\definecolor{fillColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.60,250.70) circle (  1.96);
\definecolor{drawColor}{RGB}{230,171,2}
\definecolor{fillColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.60,251.98) circle (  1.96);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 27.76,204.13) rectangle (118.74,254.67);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.81,202.46) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.81,215.32) {3};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.81,228.17) {6};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.81,241.03) {9};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.01,205.49) --
	( 27.76,205.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.01,218.35) --
	( 27.76,218.35);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.01,231.21) --
	( 27.76,231.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.01,244.06) --
	( 27.76,244.06);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.89,201.38) --
	( 31.89,204.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.25,201.38) --
	( 73.25,204.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.60,201.38) --
	(114.60,204.13);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 31.89,193.12) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 73.25,193.12) {2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (114.60,193.12) {3};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 73.25,181.09) {Maximum arity};
\end{scope}
\begin{scope}
\path[clip] (124.24,173.45) rectangle (235.57,260.17);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (124.24,173.45) rectangle (235.57,260.17);
\end{scope}
\begin{scope}
\path[clip] (139.09,204.13) rectangle (230.07,254.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (139.09,204.13) rectangle (230.07,254.67);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (139.09,211.84) --
	(230.07,211.84);

\path[draw=drawColor,line width= 0.3pt,line join=round] (139.09,228.56) --
	(230.07,228.56);

\path[draw=drawColor,line width= 0.3pt,line join=round] (139.09,245.29) --
	(230.07,245.29);

\path[draw=drawColor,line width= 0.3pt,line join=round] (157.01,204.13) --
	(157.01,254.67);

\path[draw=drawColor,line width= 0.3pt,line join=round] (184.58,204.13) --
	(184.58,254.67);

\path[draw=drawColor,line width= 0.3pt,line join=round] (212.15,204.13) --
	(212.15,254.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.09,220.20) --
	(230.07,220.20);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.09,236.93) --
	(230.07,236.93);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.09,253.65) --
	(230.07,253.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] (143.22,204.13) --
	(143.22,254.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (170.79,204.13) --
	(170.79,254.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (198.36,204.13) --
	(198.36,254.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (225.93,204.13) --
	(225.93,254.67);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (143.22,214.12) --
	(170.79,232.73) --
	(225.93,234.71);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (143.22,206.43) --
	(170.79,225.85) --
	(225.93,227.75);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (143.22,211.87) --
	(170.79,232.76) --
	(225.93,233.78);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (143.22,228.34) --
	(170.79,250.01) --
	(225.93,252.21);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round] (143.22,225.19) --
	(170.79,244.09) --
	(225.93,248.77);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt on 4pt off 3pt ,line join=round] (143.22,228.37) --
	(170.79,249.10) --
	(225.93,252.37);
\definecolor{drawColor}{RGB}{27,158,119}
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.22,214.12) circle (  1.96);
\definecolor{drawColor}{RGB}{217,95,2}
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.22,206.43) circle (  1.96);
\definecolor{drawColor}{RGB}{117,112,179}
\definecolor{fillColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.22,211.87) circle (  1.96);
\definecolor{drawColor}{RGB}{231,41,138}
\definecolor{fillColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.22,228.34) circle (  1.96);
\definecolor{drawColor}{RGB}{102,166,30}
\definecolor{fillColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.22,225.19) circle (  1.96);
\definecolor{drawColor}{RGB}{230,171,2}
\definecolor{fillColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.22,228.37) circle (  1.96);
\definecolor{drawColor}{RGB}{27,158,119}
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.79,232.73) circle (  1.96);
\definecolor{drawColor}{RGB}{217,95,2}
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.79,225.85) circle (  1.96);
\definecolor{drawColor}{RGB}{117,112,179}
\definecolor{fillColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.79,232.76) circle (  1.96);
\definecolor{drawColor}{RGB}{231,41,138}
\definecolor{fillColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.79,250.01) circle (  1.96);
\definecolor{drawColor}{RGB}{102,166,30}
\definecolor{fillColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.79,244.09) circle (  1.96);
\definecolor{drawColor}{RGB}{230,171,2}
\definecolor{fillColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.79,249.10) circle (  1.96);
\definecolor{drawColor}{RGB}{27,158,119}
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (225.93,234.71) circle (  1.96);
\definecolor{drawColor}{RGB}{217,95,2}
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (225.93,227.75) circle (  1.96);
\definecolor{drawColor}{RGB}{117,112,179}
\definecolor{fillColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (225.93,233.78) circle (  1.96);
\definecolor{drawColor}{RGB}{231,41,138}
\definecolor{fillColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (225.93,252.21) circle (  1.96);
\definecolor{drawColor}{RGB}{102,166,30}
\definecolor{fillColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (225.93,248.77) circle (  1.96);
\definecolor{drawColor}{RGB}{230,171,2}
\definecolor{fillColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (225.93,252.37) circle (  1.96);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (139.09,204.13) rectangle (230.07,254.67);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (134.14,217.17) {7};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (134.14,233.90) {8};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (134.14,250.62) {9};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (136.34,220.20) --
	(139.09,220.20);

\path[draw=drawColor,line width= 0.6pt,line join=round] (136.34,236.93) --
	(139.09,236.93);

\path[draw=drawColor,line width= 0.6pt,line join=round] (136.34,253.65) --
	(139.09,253.65);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (143.22,201.38) --
	(143.22,204.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] (170.79,201.38) --
	(170.79,204.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] (198.36,201.38) --
	(198.36,204.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] (225.93,201.38) --
	(225.93,204.13);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (143.22,193.12) {100};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (170.79,193.12) {200};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (198.36,193.12) {300};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (225.93,193.12) {400};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (184.58,181.09) {Domain size};
\end{scope}
\begin{scope}
\path[clip] (235.57,173.45) rectangle (346.90,260.17);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (235.57,173.45) rectangle (346.90,260.17);
\end{scope}
\begin{scope}
\path[clip] (250.42,204.13) rectangle (341.40,254.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (250.42,204.13) rectangle (341.40,254.67);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (250.42,207.43) --
	(341.40,207.43);

\path[draw=drawColor,line width= 0.3pt,line join=round] (250.42,223.92) --
	(341.40,223.92);

\path[draw=drawColor,line width= 0.3pt,line join=round] (250.42,240.40) --
	(341.40,240.40);

\path[draw=drawColor,line width= 0.3pt,line join=round] (254.55,204.13) --
	(254.55,254.67);

\path[draw=drawColor,line width= 0.3pt,line join=round] (271.09,204.13) --
	(271.09,254.67);

\path[draw=drawColor,line width= 0.3pt,line join=round] (287.64,204.13) --
	(287.64,254.67);

\path[draw=drawColor,line width= 0.3pt,line join=round] (304.18,204.13) --
	(304.18,254.67);

\path[draw=drawColor,line width= 0.3pt,line join=round] (320.72,204.13) --
	(320.72,254.67);

\path[draw=drawColor,line width= 0.3pt,line join=round] (337.26,204.13) --
	(337.26,254.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (250.42,215.67) --
	(341.40,215.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (250.42,232.16) --
	(341.40,232.16);

\path[draw=drawColor,line width= 0.6pt,line join=round] (250.42,248.64) --
	(341.40,248.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (262.82,204.13) --
	(262.82,254.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (279.36,204.13) --
	(279.36,254.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (295.91,204.13) --
	(295.91,254.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (312.45,204.13) --
	(312.45,254.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (328.99,204.13) --
	(328.99,254.67);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.55,212.10) --
	(295.91,221.05) --
	(337.26,235.32);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (254.55,206.43) --
	(295.91,214.71) --
	(337.26,226.12);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (254.55,210.56) --
	(295.91,221.30) --
	(337.26,233.56);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (254.55,227.18) --
	(295.91,238.03) --
	(337.26,251.65);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round] (254.55,223.69) --
	(295.91,232.98) --
	(337.26,247.85);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt on 4pt off 3pt ,line join=round] (254.55,226.85) --
	(295.91,236.95) --
	(337.26,252.37);
\definecolor{drawColor}{RGB}{27,158,119}
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (254.55,212.10) circle (  1.96);
\definecolor{drawColor}{RGB}{217,95,2}
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (254.55,206.43) circle (  1.96);
\definecolor{drawColor}{RGB}{117,112,179}
\definecolor{fillColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (254.55,210.56) circle (  1.96);
\definecolor{drawColor}{RGB}{231,41,138}
\definecolor{fillColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (254.55,227.18) circle (  1.96);
\definecolor{drawColor}{RGB}{102,166,30}
\definecolor{fillColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (254.55,223.69) circle (  1.96);
\definecolor{drawColor}{RGB}{230,171,2}
\definecolor{fillColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (254.55,226.85) circle (  1.96);
\definecolor{drawColor}{RGB}{27,158,119}
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (295.91,221.05) circle (  1.96);
\definecolor{drawColor}{RGB}{217,95,2}
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (295.91,214.71) circle (  1.96);
\definecolor{drawColor}{RGB}{117,112,179}
\definecolor{fillColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (295.91,221.30) circle (  1.96);
\definecolor{drawColor}{RGB}{231,41,138}
\definecolor{fillColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (295.91,238.03) circle (  1.96);
\definecolor{drawColor}{RGB}{102,166,30}
\definecolor{fillColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (295.91,232.98) circle (  1.96);
\definecolor{drawColor}{RGB}{230,171,2}
\definecolor{fillColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (295.91,236.95) circle (  1.96);
\definecolor{drawColor}{RGB}{27,158,119}
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (337.26,235.32) circle (  1.96);
\definecolor{drawColor}{RGB}{217,95,2}
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (337.26,226.12) circle (  1.96);
\definecolor{drawColor}{RGB}{117,112,179}
\definecolor{fillColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (337.26,233.56) circle (  1.96);
\definecolor{drawColor}{RGB}{231,41,138}
\definecolor{fillColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (337.26,251.65) circle (  1.96);
\definecolor{drawColor}{RGB}{102,166,30}
\definecolor{fillColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (337.26,247.85) circle (  1.96);
\definecolor{drawColor}{RGB}{230,171,2}
\definecolor{fillColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (337.26,252.37) circle (  1.96);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (250.42,204.13) rectangle (341.40,254.67);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (245.47,212.64) {7};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (245.47,229.13) {8};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (245.47,245.61) {9};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (247.67,215.67) --
	(250.42,215.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (247.67,232.16) --
	(250.42,232.16);

\path[draw=drawColor,line width= 0.6pt,line join=round] (247.67,248.64) --
	(250.42,248.64);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (262.82,201.38) --
	(262.82,204.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] (279.36,201.38) --
	(279.36,204.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] (295.91,201.38) --
	(295.91,204.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] (312.45,201.38) --
	(312.45,204.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] (328.99,201.38) --
	(328.99,204.13);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (262.82,193.12) {30};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (279.36,193.12) {40};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (295.91,193.12) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (312.45,193.12) {60};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (328.99,193.12) {70};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (295.91,181.09) {Probabilistic (\%)};
\end{scope}
\begin{scope}
\path[clip] ( 12.91, 86.72) rectangle (124.24,173.45);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 12.91, 86.72) rectangle (124.24,173.45);
\end{scope}
\begin{scope}
\path[clip] ( 32.16,117.41) rectangle (118.74,167.95);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 32.16,117.41) rectangle (118.74,167.95);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 32.16,128.06) --
	(118.74,128.06);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 32.16,144.84) --
	(118.74,144.84);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 32.16,161.63) --
	(118.74,161.63);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 45.83,117.41) --
	( 45.83,167.95);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 65.54,117.41) --
	( 65.54,167.95);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 85.24,117.41) --
	( 85.24,167.95);

\path[draw=drawColor,line width= 0.3pt,line join=round] (104.95,117.41) --
	(104.95,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.16,119.67) --
	(118.74,119.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.16,136.45) --
	(118.74,136.45);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.16,153.24) --
	(118.74,153.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.97,117.41) --
	( 35.97,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 55.68,117.41) --
	( 55.68,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.39,117.41) --
	( 75.39,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.10,117.41) --
	( 95.10,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.80,117.41) --
	(114.80,167.95);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 36.09,119.72) --
	( 36.21,119.77) --
	( 36.45,119.88) --
	( 36.76,120.09) --
	( 36.92,120.09) --
	( 37.87,120.46) --
	( 41.95,122.00) --
	( 42.06,121.25) --
	( 42.30,122.28) --
	( 43.86,123.42) --
	( 47.80,124.68) --
	( 47.92,124.73) --
	( 48.15,124.86) --
	( 53.77,127.57) --
	( 54.01,127.77) --
	( 59.62,130.91) --
	( 59.74,129.19) --
	( 59.86,130.97) --
	( 59.98,128.46) --
	( 60.45,134.18) --
	( 65.71,132.99) --
	( 71.57,135.39) --
	( 77.42,136.47) --
	( 83.27,148.25) --
	( 83.51,142.00) --
	( 83.98,141.34) --
	(107.04,151.71) --
	(107.51,150.96) --
	(114.80,160.18);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 36.09,119.71) --
	( 36.21,119.75) --
	( 36.45,119.86) --
	( 36.76,120.06) --
	( 36.92,120.04) --
	( 37.87,120.43) --
	( 41.95,122.21) --
	( 42.06,121.72) --
	( 42.30,121.78) --
	( 43.86,123.23) --
	( 47.80,125.46) --
	( 47.92,124.49) --
	( 48.15,125.11) --
	( 53.77,127.15) --
	( 54.01,127.34) --
	( 59.62,129.94) --
	( 59.74,128.39) --
	( 59.86,128.78) --
	( 59.98,128.97) --
	( 60.45,130.60) --
	( 65.71,132.43) --
	( 71.57,134.46) --
	( 77.42,136.74) --
	( 83.27,148.62) --
	( 83.51,137.63) --
	( 83.98,139.91) --
	(107.04,148.68) --
	(107.51,151.41) --
	(114.80,157.85);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 36.09,119.72) --
	( 36.21,119.80) --
	( 36.45,119.91) --
	( 36.76,120.11) --
	( 36.92,120.11) --
	( 37.87,120.53) --
	( 41.95,121.97) --
	( 42.06,121.57) --
	( 42.30,122.16) --
	( 43.86,123.50) --
	( 47.80,125.79) --
	( 47.92,125.05) --
	( 48.15,124.49) --
	( 53.77,127.44) --
	( 54.01,127.85) --
	( 59.62,128.96) --
	( 59.74,128.40) --
	( 59.86,129.86) --
	( 59.98,128.71) --
	( 60.45,129.25) --
	( 65.71,132.97) --
	( 71.57,136.19) --
	( 77.42,135.39) --
	( 83.27,145.85) --
	( 83.51,139.99) --
	( 83.98,143.21) --
	(107.04,148.76) --
	(107.51,151.40) --
	(114.80,159.74);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 36.09,119.72) --
	( 36.21,119.77) --
	( 36.45,119.90) --
	( 36.76,120.12) --
	( 36.92,120.09) --
	( 37.87,120.59) --
	( 41.95,122.13) --
	( 42.06,121.81) --
	( 42.30,122.38) --
	( 43.86,123.94) --
	( 47.80,127.25) --
	( 47.92,125.25) --
	( 48.15,124.05) --
	( 53.77,127.79) --
	( 54.01,128.92) --
	( 59.62,131.74) --
	( 59.74,131.68) --
	( 59.86,131.74) --
	( 59.98,132.83) --
	( 60.45,132.18) --
	( 65.71,133.74) --
	( 71.57,136.49) --
	( 77.42,138.64) --
	( 83.27,149.54) --
	( 83.51,141.59) --
	( 83.98,137.80) --
	(107.04,155.32) --
	(107.51,155.78) --
	(114.80,165.65);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round] ( 36.09,119.73) --
	( 36.21,119.78) --
	( 36.45,119.90) --
	( 36.76,120.14) --
	( 36.92,120.11) --
	( 37.87,120.59) --
	( 41.95,122.31) --
	( 42.06,122.77) --
	( 42.30,122.88) --
	( 43.86,123.76) --
	( 47.80,125.71) --
	( 47.92,125.16) --
	( 48.15,124.65) --
	( 53.77,128.14) --
	( 54.01,128.34) --
	( 59.62,131.35) --
	( 59.74,129.35) --
	( 59.86,131.05) --
	( 59.98,129.44) --
	( 60.45,132.32) --
	( 65.71,134.56) --
	( 71.57,137.57) --
	( 77.42,139.20) --
	( 83.27,153.56) --
	( 83.51,144.11) --
	( 83.98,143.55) --
	(107.04,152.34) --
	(107.51,152.40) --
	(114.80,164.25);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt on 4pt off 3pt ,line join=round] ( 36.09,119.71) --
	( 36.21,119.79) --
	( 36.45,119.90) --
	( 36.76,120.13) --
	( 36.92,120.12) --
	( 37.87,120.58) --
	( 41.95,122.27) --
	( 42.06,121.03) --
	( 42.30,122.91) --
	( 43.86,123.95) --
	( 47.80,126.79) --
	( 47.92,126.12) --
	( 48.15,124.49) --
	( 53.77,128.53) --
	( 54.01,128.94) --
	( 59.62,131.40) --
	( 59.74,132.84) --
	( 59.86,132.17) --
	( 59.98,133.57) --
	( 60.45,131.59) --
	( 65.71,133.74) --
	( 71.57,137.52) --
	( 77.42,140.05) --
	( 83.27,151.84) --
	( 83.51,142.28) --
	( 83.98,142.84) --
	(107.04,154.31) --
	(107.51,157.04) --
	(114.80,165.44);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 32.16,117.41) rectangle (118.74,167.95);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 27.21,116.63) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 27.21,133.42) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 27.21,150.21) {20};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 29.41,119.67) --
	( 32.16,119.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 29.41,136.45) --
	( 32.16,136.45);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 29.41,153.24) --
	( 32.16,153.24);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.97,114.66) --
	( 35.97,117.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 55.68,114.66) --
	( 55.68,117.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.39,114.66) --
	( 75.39,117.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.10,114.66) --
	( 95.10,117.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.80,114.66) --
	(114.80,117.41);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.97,106.40) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 55.68,106.40) {25};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 75.39,106.40) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 95.10,106.40) {75};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (114.80,106.40) {100};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 75.45, 94.36) {Facts ($\times 10^3$)};
\end{scope}
\begin{scope}
\path[clip] (124.24, 86.72) rectangle (235.57,173.45);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (124.24, 86.72) rectangle (235.57,173.45);
\end{scope}
\begin{scope}
\path[clip] (139.09,117.41) rectangle (230.07,167.95);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (139.09,117.41) rectangle (230.07,167.95);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (139.09,125.20) --
	(230.07,125.20);

\path[draw=drawColor,line width= 0.3pt,line join=round] (139.09,137.64) --
	(230.07,137.64);

\path[draw=drawColor,line width= 0.3pt,line join=round] (139.09,150.08) --
	(230.07,150.08);

\path[draw=drawColor,line width= 0.3pt,line join=round] (139.09,162.53) --
	(230.07,162.53);

\path[draw=drawColor,line width= 0.3pt,line join=round] (157.99,117.41) --
	(157.99,167.95);

\path[draw=drawColor,line width= 0.3pt,line join=round] (187.53,117.41) --
	(187.53,167.95);

\path[draw=drawColor,line width= 0.3pt,line join=round] (217.07,117.41) --
	(217.07,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.09,118.97) --
	(230.07,118.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.09,131.42) --
	(230.07,131.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.09,143.86) --
	(230.07,143.86);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.09,156.30) --
	(230.07,156.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (143.22,117.41) --
	(143.22,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (172.76,117.41) --
	(172.76,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (202.30,117.41) --
	(202.30,167.95);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (143.22,139.22) --
	(146.18,155.92) --
	(152.08,149.90) --
	(155.04,144.58) --
	(157.99,119.97) --
	(160.95,148.61) --
	(166.85,150.58) --
	(169.81,134.55) --
	(172.76,120.32) --
	(175.72,119.71) --
	(178.67,145.34) --
	(187.53,156.56) --
	(190.49,148.79) --
	(193.44,152.28) --
	(199.35,145.83) --
	(202.30,137.52) --
	(205.25,160.94) --
	(208.21,153.17) --
	(211.16,158.51) --
	(220.02,147.15) --
	(222.98,150.54) --
	(225.93,157.87);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (143.22,137.59) --
	(146.18,152.49) --
	(152.08,147.86) --
	(155.04,143.63) --
	(157.99,119.89) --
	(160.95,147.13) --
	(166.85,148.48) --
	(169.81,133.92) --
	(172.76,120.21) --
	(175.72,119.77) --
	(178.67,144.01) --
	(187.53,155.28) --
	(190.49,146.35) --
	(193.44,151.46) --
	(199.35,144.05) --
	(202.30,136.79) --
	(205.25,158.32) --
	(208.21,151.95) --
	(211.16,157.12) --
	(220.02,145.33) --
	(222.98,148.60) --
	(225.93,155.10);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (143.22,139.02) --
	(146.18,154.20) --
	(152.08,149.08) --
	(155.04,144.06) --
	(157.99,120.08) --
	(160.95,149.06) --
	(166.85,150.27) --
	(169.81,134.93) --
	(172.76,120.26) --
	(175.72,119.89) --
	(178.67,145.20) --
	(187.53,156.80) --
	(190.49,149.30) --
	(193.44,152.29) --
	(199.35,146.04) --
	(202.30,139.11) --
	(205.25,159.46) --
	(208.21,152.25) --
	(211.16,158.93) --
	(220.02,147.40) --
	(222.98,150.46) --
	(225.93,158.55);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (143.22,141.93) --
	(146.18,159.04) --
	(152.08,155.16) --
	(155.04,148.18) --
	(157.99,120.05) --
	(160.95,153.61) --
	(166.85,156.02) --
	(169.81,137.76) --
	(172.76,120.45) --
	(175.72,119.89) --
	(178.67,149.94) --
	(187.53,162.77) --
	(190.49,151.09) --
	(193.44,158.05) --
	(199.35,149.64) --
	(202.30,139.09) --
	(205.25,165.65) --
	(208.21,157.19) --
	(211.16,164.32) --
	(220.02,148.44) --
	(222.98,153.84) --
	(225.93,161.54);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round] (143.22,140.95) --
	(146.18,158.76) --
	(152.08,151.56) --
	(155.04,147.74) --
	(157.99,120.04) --
	(160.95,151.92) --
	(166.85,153.94) --
	(169.81,136.38) --
	(172.76,120.40) --
	(175.72,119.79) --
	(178.67,148.77) --
	(187.53,160.96) --
	(190.49,151.05) --
	(193.44,156.05) --
	(199.35,148.99) --
	(202.30,140.68) --
	(205.25,164.32) --
	(208.21,155.58) --
	(211.16,162.98) --
	(220.02,149.46) --
	(222.98,152.57) --
	(225.93,162.34);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt on 4pt off 3pt ,line join=round] (143.22,141.69) --
	(146.18,159.20) --
	(152.08,154.84) --
	(155.04,147.27) --
	(157.99,120.09) --
	(160.95,154.14) --
	(166.85,155.58) --
	(169.81,137.53) --
	(172.76,120.51) --
	(175.72,119.88) --
	(178.67,149.27) --
	(187.53,162.44) --
	(190.49,152.59) --
	(193.44,158.05) --
	(199.35,150.06) --
	(202.30,140.19) --
	(205.25,164.92) --
	(208.21,156.18) --
	(211.16,164.59) --
	(220.02,149.49) --
	(222.98,153.89) --
	(225.93,161.55);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (139.09,117.41) rectangle (230.07,167.95);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (134.14,115.94) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (134.14,128.39) {3};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (134.14,140.83) {6};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (134.14,153.27) {9};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (136.34,118.97) --
	(139.09,118.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (136.34,131.42) --
	(139.09,131.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] (136.34,143.86) --
	(139.09,143.86);

\path[draw=drawColor,line width= 0.6pt,line join=round] (136.34,156.30) --
	(139.09,156.30);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (143.22,114.66) --
	(143.22,117.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (172.76,114.66) --
	(172.76,117.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (202.30,114.66) --
	(202.30,117.41);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (143.22,106.40) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (172.76,106.40) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (202.30,106.40) {20};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (184.58, 94.36) {Independent pairs};
\end{scope}
\begin{scope}
\path[clip] (235.57, 86.72) rectangle (346.90,173.45);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (235.57, 86.72) rectangle (346.90,173.45);
\end{scope}
\begin{scope}
\path[clip] (250.42,117.41) rectangle (341.40,167.95);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (250.42,117.41) rectangle (341.40,167.95);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (250.42,125.38) --
	(341.40,125.38);

\path[draw=drawColor,line width= 0.3pt,line join=round] (250.42,137.76) --
	(341.40,137.76);

\path[draw=drawColor,line width= 0.3pt,line join=round] (250.42,150.15) --
	(341.40,150.15);

\path[draw=drawColor,line width= 0.3pt,line join=round] (250.42,162.54) --
	(341.40,162.54);

\path[draw=drawColor,line width= 0.3pt,line join=round] (264.89,117.41) --
	(264.89,167.95);

\path[draw=drawColor,line width= 0.3pt,line join=round] (285.57,117.41) --
	(285.57,167.95);

\path[draw=drawColor,line width= 0.3pt,line join=round] (306.24,117.41) --
	(306.24,167.95);

\path[draw=drawColor,line width= 0.3pt,line join=round] (326.92,117.41) --
	(326.92,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (250.42,119.18) --
	(341.40,119.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] (250.42,131.57) --
	(341.40,131.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] (250.42,143.96) --
	(341.40,143.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (250.42,156.35) --
	(341.40,156.35);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.55,117.41) --
	(254.55,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (275.23,117.41) --
	(275.23,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (295.91,117.41) --
	(295.91,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (316.58,117.41) --
	(316.58,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (337.26,117.41) --
	(337.26,167.95);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.55,139.33) --
	(257.51,153.19) --
	(263.41,149.97) --
	(266.37,147.54) --
	(268.34,158.45) --
	(269.32,120.56) --
	(272.27,120.30) --
	(278.18,150.65) --
	(281.14,134.69) --
	(284.09,120.52) --
	(287.04,119.91) --
	(290.00,145.43) --
	(298.86,156.60) --
	(301.81,148.87) --
	(304.77,152.34) --
	(309.69,142.15) --
	(310.68,145.92) --
	(313.63,137.65) --
	(316.58,160.96) --
	(319.54,153.23) --
	(322.49,158.54) --
	(323.48,119.82) --
	(331.35,147.23) --
	(334.31,150.61) --
	(337.26,155.49);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (254.55,137.72) --
	(257.51,149.95) --
	(263.41,147.94) --
	(266.37,147.05) --
	(268.34,155.61) --
	(269.32,120.51) --
	(272.27,120.06) --
	(278.18,148.56) --
	(281.14,134.06) --
	(284.09,120.41) --
	(287.04,119.97) --
	(290.00,144.10) --
	(298.86,155.33) --
	(301.81,146.44) --
	(304.77,151.52) --
	(309.69,140.79) --
	(310.68,144.15) --
	(313.63,136.91) --
	(316.58,158.35) --
	(319.54,152.01) --
	(322.49,157.16) --
	(323.48,119.71) --
	(331.35,145.43) --
	(334.31,148.68) --
	(337.26,152.58);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (254.55,139.14) --
	(257.51,151.37) --
	(263.41,149.16) --
	(266.37,147.66) --
	(268.34,157.54) --
	(269.32,120.78) --
	(272.27,120.36) --
	(278.18,150.34) --
	(281.14,135.07) --
	(284.09,120.47) --
	(287.04,120.09) --
	(290.00,145.29) --
	(298.86,156.84) --
	(301.81,149.37) --
	(304.77,152.35) --
	(309.69,141.07) --
	(310.68,146.13) --
	(313.63,139.23) --
	(316.58,159.49) --
	(319.54,152.31) --
	(322.49,158.96) --
	(323.48,119.82) --
	(331.35,147.49) --
	(334.31,150.53) --
	(337.26,154.98);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (254.55,142.04) --
	(257.51,155.46) --
	(263.41,155.20) --
	(266.37,152.47) --
	(268.34,163.20) --
	(269.32,120.74) --
	(272.27,120.28) --
	(278.18,156.06) --
	(281.14,137.88) --
	(284.09,120.65) --
	(287.04,120.09) --
	(290.00,150.01) --
	(298.86,162.78) --
	(301.81,151.15) --
	(304.77,158.08) --
	(309.69,144.54) --
	(310.68,149.72) --
	(313.63,139.21) --
	(316.58,165.65) --
	(319.54,157.22) --
	(322.49,164.33) --
	(323.48,119.80) --
	(331.35,148.52) --
	(334.31,153.89) --
	(337.26,159.35);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round] (254.55,141.06) --
	(257.51,157.32) --
	(263.41,151.62) --
	(266.37,150.39) --
	(268.34,161.36) --
	(269.32,120.67) --
	(272.27,120.32) --
	(278.18,153.99) --
	(281.14,136.51) --
	(284.09,120.60) --
	(287.04,119.99) --
	(290.00,148.85) --
	(298.86,160.98) --
	(301.81,151.12) --
	(304.77,156.09) --
	(309.69,145.54) --
	(310.68,149.06) --
	(313.63,140.79) --
	(316.58,164.32) --
	(319.54,155.62) --
	(322.49,162.99) --
	(323.48,119.83) --
	(331.35,149.53) --
	(334.31,152.63) --
	(337.26,158.52);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt on 4pt off 3pt ,line join=round] (254.55,141.80) --
	(257.51,155.92) --
	(263.41,154.89) --
	(266.37,151.09) --
	(268.34,162.99) --
	(269.32,120.78) --
	(272.27,120.43) --
	(278.18,155.62) --
	(281.14,137.65) --
	(284.09,120.71) --
	(287.04,120.09) --
	(290.00,149.34) --
	(298.86,162.45) --
	(301.81,152.65) --
	(304.77,158.08) --
	(309.69,144.05) --
	(310.68,150.13) --
	(313.63,140.30) --
	(316.58,164.93) --
	(319.54,156.22) --
	(322.49,164.60) --
	(323.48,119.84) --
	(331.35,149.57) --
	(334.31,153.94) --
	(337.26,159.64);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (250.42,117.41) rectangle (341.40,167.95);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (245.47,116.15) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (245.47,128.54) {3};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (245.47,140.93) {6};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (245.47,153.32) {9};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (247.67,119.18) --
	(250.42,119.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] (247.67,131.57) --
	(250.42,131.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] (247.67,143.96) --
	(250.42,143.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (247.67,156.35) --
	(250.42,156.35);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.55,114.66) --
	(254.55,117.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (275.23,114.66) --
	(275.23,117.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (295.91,114.66) --
	(295.91,117.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (316.58,114.66) --
	(316.58,117.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (337.26,114.66) --
	(337.26,117.41);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (254.55,106.40) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (275.23,106.40) {25};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (295.91,106.40) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (316.58,106.40) {75};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (337.26,106.40) {100};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (295.91, 94.36) {Independent (\%)};
\end{scope}
\begin{scope}
\path[clip] ( 12.91,  0.00) rectangle (124.24, 86.72);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 12.91,  0.00) rectangle (124.24, 86.72);
\end{scope}
\begin{scope}
\path[clip] ( 32.16, 30.69) rectangle (118.74, 81.22);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 32.16, 30.69) rectangle (118.74, 81.22);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 32.16, 40.36) --
	(118.74, 40.36);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 32.16, 56.68) --
	(118.74, 56.68);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 32.16, 73.00) --
	(118.74, 73.00);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.59, 30.69) --
	( 46.59, 81.22);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 67.58, 30.69) --
	( 67.58, 81.22);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 88.57, 30.69) --
	( 88.57, 81.22);

\path[draw=drawColor,line width= 0.3pt,line join=round] (109.56, 30.69) --
	(109.56, 81.22);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.16, 32.20) --
	(118.74, 32.20);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.16, 48.52) --
	(118.74, 48.52);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.16, 64.84) --
	(118.74, 64.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.16, 81.16) --
	(118.74, 81.16);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 36.09, 30.69) --
	( 36.09, 81.22);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 57.08, 30.69) --
	( 57.08, 81.22);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.07, 30.69) --
	( 78.07, 81.22);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 99.06, 30.69) --
	( 99.06, 81.22);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 36.09, 33.22) --
	( 37.09, 55.98) --
	( 38.09, 61.81) --
	( 39.08, 67.20) --
	( 40.08, 70.71) --
	( 41.07, 72.69) --
	( 42.07, 73.54) --
	( 43.07, 73.63) --
	( 44.06, 73.32) --
	( 45.06, 72.94) --
	( 46.06, 72.56) --
	( 47.05, 72.19) --
	( 48.05, 71.81) --
	( 49.05, 71.44) --
	( 50.04, 71.07) --
	( 51.04, 70.69) --
	( 52.03, 70.32) --
	( 53.03, 69.95) --
	( 54.03, 69.58) --
	( 55.02, 69.21) --
	( 56.02, 68.84) --
	( 57.02, 68.48) --
	( 58.01, 68.11) --
	( 59.01, 67.74) --
	( 60.00, 67.38) --
	( 61.00, 67.01) --
	( 62.00, 66.65) --
	( 62.99, 66.28) --
	( 63.99, 65.92) --
	( 64.99, 65.56) --
	( 65.98, 65.20) --
	( 66.98, 64.84) --
	( 67.98, 64.48) --
	( 68.97, 64.12) --
	( 69.97, 63.76) --
	( 70.96, 63.40) --
	( 71.96, 63.04) --
	( 72.96, 62.69) --
	( 73.95, 62.33) --
	( 74.95, 61.97) --
	( 75.95, 61.62) --
	( 76.94, 61.26) --
	( 77.94, 60.91) --
	( 78.94, 60.56) --
	( 79.93, 60.20) --
	( 80.93, 59.85) --
	( 81.92, 59.50) --
	( 82.92, 59.14) --
	( 83.92, 58.79) --
	( 84.91, 58.44) --
	( 85.91, 58.09) --
	( 86.91, 57.74) --
	( 87.90, 57.39) --
	( 88.90, 57.04) --
	( 89.89, 56.69) --
	( 90.89, 56.34) --
	( 91.89, 55.99) --
	( 92.88, 55.64) --
	( 93.88, 55.29) --
	( 94.88, 54.95) --
	( 95.87, 54.60) --
	( 96.87, 54.25) --
	( 97.87, 53.90) --
	( 98.86, 53.56) --
	( 99.86, 53.21) --
	(100.85, 52.86) --
	(101.85, 52.52) --
	(102.85, 52.17) --
	(103.84, 51.82) --
	(104.84, 51.48) --
	(105.84, 51.13) --
	(106.83, 50.79) --
	(107.83, 50.44) --
	(108.83, 50.09) --
	(109.82, 49.75) --
	(110.82, 49.40) --
	(111.81, 49.06) --
	(112.81, 48.71) --
	(113.81, 48.37) --
	(114.80, 48.02);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 36.09, 32.98) --
	( 37.09, 54.54) --
	( 38.09, 59.85) --
	( 39.08, 64.85) --
	( 40.08, 68.09) --
	( 41.07, 69.93) --
	( 42.07, 70.71) --
	( 43.07, 70.77) --
	( 44.06, 70.48) --
	( 45.06, 70.12) --
	( 46.06, 69.76) --
	( 47.05, 69.40) --
	( 48.05, 69.04) --
	( 49.05, 68.68) --
	( 50.04, 68.33) --
	( 51.04, 67.97) --
	( 52.03, 67.62) --
	( 53.03, 67.27) --
	( 54.03, 66.92) --
	( 55.02, 66.57) --
	( 56.02, 66.22) --
	( 57.02, 65.87) --
	( 58.01, 65.53) --
	( 59.01, 65.18) --
	( 60.00, 64.84) --
	( 61.00, 64.50) --
	( 62.00, 64.15) --
	( 62.99, 63.81) --
	( 63.99, 63.47) --
	( 64.99, 63.13) --
	( 65.98, 62.80) --
	( 66.98, 62.46) --
	( 67.98, 62.12) --
	( 68.97, 61.79) --
	( 69.97, 61.45) --
	( 70.96, 61.12) --
	( 71.96, 60.79) --
	( 72.96, 60.45) --
	( 73.95, 60.12) --
	( 74.95, 59.79) --
	( 75.95, 59.46) --
	( 76.94, 59.13) --
	( 77.94, 58.80) --
	( 78.94, 58.47) --
	( 79.93, 58.15) --
	( 80.93, 57.82) --
	( 81.92, 57.49) --
	( 82.92, 57.17) --
	( 83.92, 56.84) --
	( 84.91, 56.52) --
	( 85.91, 56.20) --
	( 86.91, 55.87) --
	( 87.90, 55.55) --
	( 88.90, 55.23) --
	( 89.89, 54.91) --
	( 90.89, 54.58) --
	( 91.89, 54.26) --
	( 92.88, 53.94) --
	( 93.88, 53.62) --
	( 94.88, 53.30) --
	( 95.87, 52.98) --
	( 96.87, 52.67) --
	( 97.87, 52.35) --
	( 98.86, 52.03) --
	( 99.86, 51.71) --
	(100.85, 51.39) --
	(101.85, 51.08) --
	(102.85, 50.76) --
	(103.84, 50.44) --
	(104.84, 50.12) --
	(105.84, 49.81) --
	(106.83, 49.49) --
	(107.83, 49.18) --
	(108.83, 48.86) --
	(109.82, 48.54) --
	(110.82, 48.23) --
	(111.81, 47.91) --
	(112.81, 47.60) --
	(113.81, 47.28) --
	(114.80, 46.96);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 36.09, 33.06) --
	( 37.09, 55.40) --
	( 38.09, 61.11) --
	( 39.08, 66.53) --
	( 40.08, 70.05) --
	( 41.07, 72.05) --
	( 42.07, 72.90) --
	( 43.07, 72.99) --
	( 44.06, 72.68) --
	( 45.06, 72.31) --
	( 46.06, 71.93) --
	( 47.05, 71.55) --
	( 48.05, 71.18) --
	( 49.05, 70.81) --
	( 50.04, 70.44) --
	( 51.04, 70.07) --
	( 52.03, 69.70) --
	( 53.03, 69.33) --
	( 54.03, 68.96) --
	( 55.02, 68.59) --
	( 56.02, 68.23) --
	( 57.02, 67.86) --
	( 58.01, 67.50) --
	( 59.01, 67.14) --
	( 60.00, 66.77) --
	( 61.00, 66.41) --
	( 62.00, 66.05) --
	( 62.99, 65.69) --
	( 63.99, 65.33) --
	( 64.99, 64.98) --
	( 65.98, 64.62) --
	( 66.98, 64.26) --
	( 67.98, 63.91) --
	( 68.97, 63.55) --
	( 69.97, 63.20) --
	( 70.96, 62.85) --
	( 71.96, 62.49) --
	( 72.96, 62.14) --
	( 73.95, 61.79) --
	( 74.95, 61.44) --
	( 75.95, 61.09) --
	( 76.94, 60.74) --
	( 77.94, 60.39) --
	( 78.94, 60.04) --
	( 79.93, 59.70) --
	( 80.93, 59.35) --
	( 81.92, 59.00) --
	( 82.92, 58.66) --
	( 83.92, 58.31) --
	( 84.91, 57.97) --
	( 85.91, 57.62) --
	( 86.91, 57.28) --
	( 87.90, 56.94) --
	( 88.90, 56.59) --
	( 89.89, 56.25) --
	( 90.89, 55.91) --
	( 91.89, 55.57) --
	( 92.88, 55.23) --
	( 93.88, 54.89) --
	( 94.88, 54.54) --
	( 95.87, 54.20) --
	( 96.87, 53.86) --
	( 97.87, 53.52) --
	( 98.86, 53.19) --
	( 99.86, 52.85) --
	(100.85, 52.51) --
	(101.85, 52.17) --
	(102.85, 51.83) --
	(103.84, 51.49) --
	(104.84, 51.15) --
	(105.84, 50.82) --
	(106.83, 50.48) --
	(107.83, 50.14) --
	(108.83, 49.80) --
	(109.82, 49.46) --
	(110.82, 49.13) --
	(111.81, 48.79) --
	(112.81, 48.45) --
	(113.81, 48.12) --
	(114.80, 47.78);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 36.09, 33.25) --
	( 37.09, 59.80) --
	( 38.09, 66.04) --
	( 39.08, 71.90) --
	( 40.08, 75.67) --
	( 41.07, 77.78) --
	( 42.07, 78.63) --
	( 43.07, 78.64) --
	( 44.06, 78.22) --
	( 45.06, 77.72) --
	( 46.06, 77.23) --
	( 47.05, 76.75) --
	( 48.05, 76.27) --
	( 49.05, 75.79) --
	( 50.04, 75.31) --
	( 51.04, 74.84) --
	( 52.03, 74.38) --
	( 53.03, 73.91) --
	( 54.03, 73.45) --
	( 55.02, 73.00) --
	( 56.02, 72.54) --
	( 57.02, 72.09) --
	( 58.01, 71.65) --
	( 59.01, 71.20) --
	( 60.00, 70.76) --
	( 61.00, 70.32) --
	( 62.00, 69.89) --
	( 62.99, 69.46) --
	( 63.99, 69.03) --
	( 64.99, 68.61) --
	( 65.98, 68.18) --
	( 66.98, 67.76) --
	( 67.98, 67.35) --
	( 68.97, 66.93) --
	( 69.97, 66.52) --
	( 70.96, 66.11) --
	( 71.96, 65.71) --
	( 72.96, 65.30) --
	( 73.95, 64.90) --
	( 74.95, 64.50) --
	( 75.95, 64.10) --
	( 76.94, 63.71) --
	( 77.94, 63.32) --
	( 78.94, 62.93) --
	( 79.93, 62.54) --
	( 80.93, 62.15) --
	( 81.92, 61.77) --
	( 82.92, 61.38) --
	( 83.92, 61.00) --
	( 84.91, 60.62) --
	( 85.91, 60.24) --
	( 86.91, 59.87) --
	( 87.90, 59.49) --
	( 88.90, 59.12) --
	( 89.89, 58.75) --
	( 90.89, 58.38) --
	( 91.89, 58.01) --
	( 92.88, 57.64) --
	( 93.88, 57.28) --
	( 94.88, 56.91) --
	( 95.87, 56.55) --
	( 96.87, 56.19) --
	( 97.87, 55.82) --
	( 98.86, 55.46) --
	( 99.86, 55.10) --
	(100.85, 54.75) --
	(101.85, 54.39) --
	(102.85, 54.03) --
	(103.84, 53.67) --
	(104.84, 53.32) --
	(105.84, 52.96) --
	(106.83, 52.61) --
	(107.83, 52.25) --
	(108.83, 51.90) --
	(109.82, 51.54) --
	(110.82, 51.19) --
	(111.81, 50.84) --
	(112.81, 50.48) --
	(113.81, 50.13) --
	(114.80, 49.78);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 1pt off 3pt ,line join=round] ( 36.09, 33.22) --
	( 37.09, 58.30) --
	( 38.09, 64.82) --
	( 39.08, 70.85) --
	( 40.08, 74.75) --
	( 41.07, 76.94) --
	( 42.07, 77.84) --
	( 43.07, 77.89) --
	( 44.06, 77.49) --
	( 45.06, 77.02) --
	( 46.06, 76.55) --
	( 47.05, 76.08) --
	( 48.05, 75.62) --
	( 49.05, 75.16) --
	( 50.04, 74.70) --
	( 51.04, 74.25) --
	( 52.03, 73.80) --
	( 53.03, 73.35) --
	( 54.03, 72.91) --
	( 55.02, 72.47) --
	( 56.02, 72.03) --
	( 57.02, 71.59) --
	( 58.01, 71.16) --
	( 59.01, 70.72) --
	( 60.00, 70.30) --
	( 61.00, 69.87) --
	( 62.00, 69.45) --
	( 62.99, 69.03) --
	( 63.99, 68.61) --
	( 64.99, 68.19) --
	( 65.98, 67.78) --
	( 66.98, 67.37) --
	( 67.98, 66.96) --
	( 68.97, 66.55) --
	( 69.97, 66.15) --
	( 70.96, 65.74) --
	( 71.96, 65.34) --
	( 72.96, 64.94) --
	( 73.95, 64.55) --
	( 74.95, 64.15) --
	( 75.95, 63.76) --
	( 76.94, 63.37) --
	( 77.94, 62.98) --
	( 78.94, 62.59) --
	( 79.93, 62.21) --
	( 80.93, 61.82) --
	( 81.92, 61.44) --
	( 82.92, 61.06) --
	( 83.92, 60.68) --
	( 84.91, 60.30) --
	( 85.91, 59.92) --
	( 86.91, 59.55) --
	( 87.90, 59.17) --
	( 88.90, 58.80) --
	( 89.89, 58.43) --
	( 90.89, 58.06) --
	( 91.89, 57.69) --
	( 92.88, 57.32) --
	( 93.88, 56.95) --
	( 94.88, 56.59) --
	( 95.87, 56.22) --
	( 96.87, 55.86) --
	( 97.87, 55.49) --
	( 98.86, 55.13) --
	( 99.86, 54.77) --
	(100.85, 54.41) --
	(101.85, 54.05) --
	(102.85, 53.69) --
	(103.84, 53.33) --
	(104.84, 52.97) --
	(105.84, 52.61) --
	(106.83, 52.25) --
	(107.83, 51.89) --
	(108.83, 51.54) --
	(109.82, 51.18) --
	(110.82, 50.82) --
	(111.81, 50.46) --
	(112.81, 50.11) --
	(113.81, 49.75) --
	(114.80, 49.39);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 1pt off 3pt on 4pt off 3pt ,line join=round] ( 36.09, 33.25) --
	( 37.09, 59.84) --
	( 38.09, 66.25) --
	( 39.08, 72.14) --
	( 40.08, 75.94) --
	( 41.07, 78.06) --
	( 42.07, 78.92) --
	( 43.07, 78.93) --
	( 44.06, 78.51) --
	( 45.06, 78.01) --
	( 46.06, 77.52) --
	( 47.05, 77.03) --
	( 48.05, 76.55) --
	( 49.05, 76.07) --
	( 50.04, 75.59) --
	( 51.04, 75.12) --
	( 52.03, 74.65) --
	( 53.03, 74.18) --
	( 54.03, 73.72) --
	( 55.02, 73.26) --
	( 56.02, 72.81) --
	( 57.02, 72.36) --
	( 58.01, 71.91) --
	( 59.01, 71.46) --
	( 60.00, 71.02) --
	( 61.00, 70.58) --
	( 62.00, 70.15) --
	( 62.99, 69.72) --
	( 63.99, 69.29) --
	( 64.99, 68.86) --
	( 65.98, 68.44) --
	( 66.98, 68.02) --
	( 67.98, 67.60) --
	( 68.97, 67.18) --
	( 69.97, 66.77) --
	( 70.96, 66.36) --
	( 71.96, 65.96) --
	( 72.96, 65.55) --
	( 73.95, 65.15) --
	( 74.95, 64.75) --
	( 75.95, 64.35) --
	( 76.94, 63.96) --
	( 77.94, 63.56) --
	( 78.94, 63.17) --
	( 79.93, 62.78) --
	( 80.93, 62.40) --
	( 81.92, 62.01) --
	( 82.92, 61.63) --
	( 83.92, 61.25) --
	( 84.91, 60.87) --
	( 85.91, 60.49) --
	( 86.91, 60.11) --
	( 87.90, 59.74) --
	( 88.90, 59.37) --
	( 89.89, 58.99) --
	( 90.89, 58.63) --
	( 91.89, 58.26) --
	( 92.88, 57.89) --
	( 93.88, 57.52) --
	( 94.88, 57.16) --
	( 95.87, 56.80) --
	( 96.87, 56.43) --
	( 97.87, 56.07) --
	( 98.86, 55.71) --
	( 99.86, 55.35) --
	(100.85, 54.99) --
	(101.85, 54.64) --
	(102.85, 54.28) --
	(103.84, 53.92) --
	(104.84, 53.57) --
	(105.84, 53.21) --
	(106.83, 52.86) --
	(107.83, 52.50) --
	(108.83, 52.15) --
	(109.82, 51.79) --
	(110.82, 51.44) --
	(111.81, 51.09) --
	(112.81, 50.74) --
	(113.81, 50.38) --
	(114.80, 50.03);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 32.16, 30.69) rectangle (118.74, 81.22);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 27.21, 29.17) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 27.21, 45.49) {5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 27.21, 61.81) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 27.21, 78.13) {15};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 29.41, 32.20) --
	( 32.16, 32.20);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 29.41, 48.52) --
	( 32.16, 48.52);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 29.41, 64.84) --
	( 32.16, 64.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 29.41, 81.16) --
	( 32.16, 81.16);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 36.09, 27.94) --
	( 36.09, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 57.08, 27.94) --
	( 57.08, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.07, 27.94) --
	( 78.07, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 99.06, 27.94) --
	( 99.06, 30.69);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 36.09, 19.68) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 57.08, 19.68) {0.2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 78.07, 19.68) {0.4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 99.06, 19.68) {0.6};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 75.45,  7.64) {Proportion listed};
\end{scope}
\begin{scope}
\path[clip] (124.24,  0.00) rectangle (235.57, 86.72);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (124.24,  0.00) rectangle (235.57, 86.72);
\end{scope}
\begin{scope}
\path[clip] (139.09, 32.18) rectangle (230.07, 81.22);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (139.09, 32.18) rectangle (230.07, 81.22);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (139.09, 40.82) --
	(230.07, 40.82);

\path[draw=drawColor,line width= 0.3pt,line join=round] (139.09, 52.61) --
	(230.07, 52.61);

\path[draw=drawColor,line width= 0.3pt,line join=round] (139.09, 64.41) --
	(230.07, 64.41);

\path[draw=drawColor,line width= 0.3pt,line join=round] (139.09, 76.20) --
	(230.07, 76.20);

\path[draw=drawColor,line width= 0.3pt,line join=round] (139.34, 32.18) --
	(139.34, 81.22);

\path[draw=drawColor,line width= 0.3pt,line join=round] (145.79, 32.18) --
	(145.79, 81.22);

\path[draw=drawColor,line width= 0.3pt,line join=round] (158.70, 32.18) --
	(158.70, 81.22);

\path[draw=drawColor,line width= 0.3pt,line join=round] (171.60, 32.18) --
	(171.60, 81.22);

\path[draw=drawColor,line width= 0.3pt,line join=round] (184.51, 32.18) --
	(184.51, 81.22);

\path[draw=drawColor,line width= 0.3pt,line join=round] (197.42, 32.18) --
	(197.42, 81.22);

\path[draw=drawColor,line width= 0.3pt,line join=round] (210.32, 32.18) --
	(210.32, 81.22);

\path[draw=drawColor,line width= 0.3pt,line join=round] (223.23, 32.18) --
	(223.23, 81.22);

\path[draw=drawColor,line width= 0.3pt,line join=round] (229.68, 32.18) --
	(229.68, 81.22);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.09, 34.92) --
	(230.07, 34.92);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.09, 46.71) --
	(230.07, 46.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.09, 58.51) --
	(230.07, 58.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.09, 70.30) --
	(230.07, 70.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (152.24, 32.18) --
	(152.24, 81.22);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.15, 32.18) --
	(165.15, 81.22);

\path[draw=drawColor,line width= 0.6pt,line join=round] (178.06, 32.18) --
	(178.06, 81.22);

\path[draw=drawColor,line width= 0.6pt,line join=round] (190.96, 32.18) --
	(190.96, 81.22);

\path[draw=drawColor,line width= 0.6pt,line join=round] (203.87, 32.18) --
	(203.87, 81.22);

\path[draw=drawColor,line width= 0.6pt,line join=round] (216.78, 32.18) --
	(216.78, 81.22);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 1.1pt,line join=round] (143.22, 34.40) --
	(144.27, 34.41) --
	(145.32, 34.42) --
	(146.36, 34.43) --
	(147.41, 34.46) --
	(148.46, 34.50) --
	(149.50, 34.56) --
	(150.55, 34.64) --
	(151.60, 34.75) --
	(152.65, 34.89) --
	(153.69, 35.06) --
	(154.74, 35.28) --
	(155.79, 35.53) --
	(156.83, 35.83) --
	(157.88, 36.18) --
	(158.93, 36.58) --
	(159.97, 37.04) --
	(161.02, 37.55) --
	(162.07, 38.14) --
	(163.11, 38.79) --
	(164.16, 39.51) --
	(165.21, 40.31) --
	(166.26, 41.19) --
	(167.30, 42.15) --
	(168.35, 43.20) --
	(169.40, 44.34) --
	(170.44, 45.58) --
	(171.49, 46.91) --
	(172.54, 48.35) --
	(173.58, 49.89) --
	(174.63, 51.54) --
	(175.68, 53.30) --
	(176.73, 55.15) --
	(177.77, 57.04) --
	(178.82, 58.95) --
	(179.87, 60.85) --
	(180.91, 62.68) --
	(181.96, 64.43) --
	(183.01, 66.06) --
	(184.05, 67.53) --
	(185.10, 68.81) --
	(186.15, 69.86) --
	(187.19, 70.65) --
	(188.24, 71.18) --
	(189.29, 71.50) --
	(190.34, 71.67) --
	(191.38, 71.75) --
	(192.43, 71.78) --
	(193.48, 71.84) --
	(194.52, 71.96) --
	(195.57, 72.17) --
	(196.62, 72.40) --
	(197.66, 72.61) --
	(198.71, 72.76) --
	(199.76, 72.80) --
	(200.81, 72.75) --
	(201.85, 72.64) --
	(202.90, 72.51) --
	(203.95, 72.38) --
	(204.99, 72.26) --
	(206.04, 72.14) --
	(207.09, 72.03) --
	(208.13, 71.91) --
	(209.18, 71.80) --
	(210.23, 71.69) --
	(211.27, 71.59) --
	(212.32, 71.53) --
	(213.37, 71.50) --
	(214.42, 71.51) --
	(215.46, 71.59) --
	(216.51, 71.71) --
	(217.56, 71.87) --
	(218.60, 72.06) --
	(219.65, 72.26) --
	(220.70, 72.46) --
	(221.74, 72.66) --
	(222.79, 72.85) --
	(223.84, 73.05) --
	(224.88, 73.24) --
	(225.93, 73.43);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] (143.22, 34.82) --
	(144.27, 34.78) --
	(145.32, 34.75) --
	(146.36, 34.72) --
	(147.41, 34.71) --
	(148.46, 34.71) --
	(149.50, 34.73) --
	(150.55, 34.77) --
	(151.60, 34.84) --
	(152.65, 34.93) --
	(153.69, 35.06) --
	(154.74, 35.23) --
	(155.79, 35.44) --
	(156.83, 35.69) --
	(157.88, 35.99) --
	(158.93, 36.34) --
	(159.97, 36.74) --
	(161.02, 37.21) --
	(162.07, 37.73) --
	(163.11, 38.32) --
	(164.16, 38.99) --
	(165.21, 39.72) --
	(166.26, 40.54) --
	(167.30, 41.43) --
	(168.35, 42.41) --
	(169.40, 43.48) --
	(170.44, 44.64) --
	(171.49, 45.89) --
	(172.54, 47.25) --
	(173.58, 48.70) --
	(174.63, 50.27) --
	(175.68, 51.94) --
	(176.73, 53.69) --
	(177.77, 55.49) --
	(178.82, 57.30) --
	(179.87, 59.10) --
	(180.91, 60.84) --
	(181.96, 62.50) --
	(183.01, 64.03) --
	(184.05, 65.42) --
	(185.10, 66.62) --
	(186.15, 67.59) --
	(187.19, 68.32) --
	(188.24, 68.79) --
	(189.29, 69.06) --
	(190.34, 69.20) --
	(191.38, 69.24) --
	(192.43, 69.27) --
	(193.48, 69.33) --
	(194.52, 69.47) --
	(195.57, 69.71) --
	(196.62, 69.99) --
	(197.66, 70.26) --
	(198.71, 70.46) --
	(199.76, 70.55) --
	(200.81, 70.56) --
	(201.85, 70.52) --
	(202.90, 70.46) --
	(203.95, 70.43) --
	(204.99, 70.40) --
	(206.04, 70.38) --
	(207.09, 70.35) --
	(208.13, 70.30) --
	(209.18, 70.22) --
	(210.23, 70.13) --
	(211.27, 70.02) --
	(212.32, 69.93) --
	(213.37, 69.87) --
	(214.42, 69.85) --
	(215.46, 69.90) --
	(216.51, 69.99) --
	(217.56, 70.12) --
	(218.60, 70.29) --
	(219.65, 70.46) --
	(220.70, 70.64) --
	(221.74, 70.82) --
	(222.79, 70.99) --
	(223.84, 71.16) --
	(224.88, 71.32) --
	(225.93, 71.49);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] (143.22, 34.84) --
	(144.27, 34.81) --
	(145.32, 34.78) --
	(146.36, 34.76) --
	(147.41, 34.76) --
	(148.46, 34.76) --
	(149.50, 34.79) --
	(150.55, 34.84) --
	(151.60, 34.92) --
	(152.65, 35.03) --
	(153.69, 35.18) --
	(154.74, 35.36) --
	(155.79, 35.58) --
	(156.83, 35.86) --
	(157.88, 36.18) --
	(158.93, 36.56) --
	(159.97, 36.99) --
	(161.02, 37.49) --
	(162.07, 38.05) --
	(163.11, 38.68) --
	(164.16, 39.39) --
	(165.21, 40.18) --
	(166.26, 41.04) --
	(167.30, 41.99) --
	(168.35, 43.03) --
	(169.40, 44.17) --
	(170.44, 45.40) --
	(171.49, 46.73) --
	(172.54, 48.16) --
	(173.58, 49.71) --
	(174.63, 51.37) --
	(175.68, 53.13) --
	(176.73, 54.99) --
	(177.77, 56.89) --
	(178.82, 58.81) --
	(179.87, 60.70) --
	(180.91, 62.54) --
	(181.96, 64.28) --
	(183.01, 65.88) --
	(184.05, 67.32) --
	(185.10, 68.56) --
	(186.15, 69.55) --
	(187.19, 70.27) --
	(188.24, 70.72) --
	(189.29, 70.95) --
	(190.34, 71.02) --
	(191.38, 71.00) --
	(192.43, 70.95) --
	(193.48, 70.94) --
	(194.52, 71.01) --
	(195.57, 71.19) --
	(196.62, 71.42) --
	(197.66, 71.66) --
	(198.71, 71.84) --
	(199.76, 71.93) --
	(200.81, 71.95) --
	(201.85, 71.95) --
	(202.90, 71.96) --
	(203.95, 72.01) --
	(204.99, 72.08) --
	(206.04, 72.14) --
	(207.09, 72.17) --
	(208.13, 72.16) --
	(209.18, 72.07) --
	(210.23, 71.91) --
	(211.27, 71.71) --
	(212.32, 71.52) --
	(213.37, 71.35) --
	(214.42, 71.25) --
	(215.46, 71.25) --
	(216.51, 71.34) --
	(217.56, 71.51) --
	(218.60, 71.75) --
	(219.65, 72.05) --
	(220.70, 72.40) --
	(221.74, 72.79) --
	(222.79, 73.21) --
	(223.84, 73.65) --
	(224.88, 74.11) --
	(225.93, 74.58);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] (143.22, 34.59) --
	(144.27, 34.57) --
	(145.32, 34.56) --
	(146.36, 34.55) --
	(147.41, 34.55) --
	(148.46, 34.57) --
	(149.50, 34.62) --
	(150.55, 34.69) --
	(151.60, 34.78) --
	(152.65, 34.92) --
	(153.69, 35.09) --
	(154.74, 35.30) --
	(155.79, 35.56) --
	(156.83, 35.88) --
	(157.88, 36.24) --
	(158.93, 36.67) --
	(159.97, 37.16) --
	(161.02, 37.72) --
	(162.07, 38.35) --
	(163.11, 39.06) --
	(164.16, 39.85) --
	(165.21, 40.73) --
	(166.26, 41.69) --
	(167.30, 42.75) --
	(168.35, 43.91) --
	(169.40, 45.17) --
	(170.44, 46.53) --
	(171.49, 48.01) --
	(172.54, 49.60) --
	(173.58, 51.31) --
	(174.63, 53.15) --
	(175.68, 55.11) --
	(176.73, 57.16) --
	(177.77, 59.27) --
	(178.82, 61.40) --
	(179.87, 63.51) --
	(180.91, 65.56) --
	(181.96, 67.52) --
	(183.01, 69.34) --
	(184.05, 70.99) --
	(185.10, 72.43) --
	(186.15, 73.62) --
	(187.19, 74.53) --
	(188.24, 75.14) --
	(189.29, 75.54) --
	(190.34, 75.78) --
	(191.38, 75.93) --
	(192.43, 76.07) --
	(193.48, 76.25) --
	(194.52, 76.55) --
	(195.57, 76.96) --
	(196.62, 77.42) --
	(197.66, 77.84) --
	(198.71, 78.17) --
	(199.76, 78.34) --
	(200.81, 78.38) --
	(201.85, 78.35) --
	(202.90, 78.29) --
	(203.95, 78.24) --
	(204.99, 78.19) --
	(206.04, 78.13) --
	(207.09, 78.05) --
	(208.13, 77.94) --
	(209.18, 77.79) --
	(210.23, 77.61) --
	(211.27, 77.40) --
	(212.32, 77.21) --
	(213.37, 77.05) --
	(214.42, 76.94) --
	(215.46, 76.91) --
	(216.51, 76.95) --
	(217.56, 77.05) --
	(218.60, 77.19) --
	(219.65, 77.37) --
	(220.70, 77.57) --
	(221.74, 77.78) --
	(222.79, 78.00) --
	(223.84, 78.23) --
	(224.88, 78.47) --
	(225.93, 78.71);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 1pt off 3pt ,line join=round] (143.22, 34.93) --
	(144.27, 34.88) --
	(145.32, 34.83) --
	(146.36, 34.79) --
	(147.41, 34.76) --
	(148.46, 34.75) --
	(149.50, 34.76) --
	(150.55, 34.80) --
	(151.60, 34.87) --
	(152.65, 34.97) --
	(153.69, 35.11) --
	(154.74, 35.29) --
	(155.79, 35.53) --
	(156.83, 35.81) --
	(157.88, 36.15) --
	(158.93, 36.55) --
	(159.97, 37.02) --
	(161.02, 37.55) --
	(162.07, 38.16) --
	(163.11, 38.85) --
	(164.16, 39.62) --
	(165.21, 40.47) --
	(166.26, 41.42) --
	(167.30, 42.46) --
	(168.35, 43.60) --
	(169.40, 44.84) --
	(170.44, 46.20) --
	(171.49, 47.66) --
	(172.54, 49.24) --
	(173.58, 50.95) --
	(174.63, 52.77) --
	(175.68, 54.73) --
	(176.73, 56.78) --
	(177.77, 58.89) --
	(178.82, 61.01) --
	(179.87, 63.12) --
	(180.91, 65.17) --
	(181.96, 67.13) --
	(183.01, 68.94) --
	(184.05, 70.59) --
	(185.10, 72.02) --
	(186.15, 73.20) --
	(187.19, 74.09) --
	(188.24, 74.69) --
	(189.29, 75.06) --
	(190.34, 75.26) --
	(191.38, 75.36) --
	(192.43, 75.42) --
	(193.48, 75.50) --
	(194.52, 75.67) --
	(195.57, 75.93) --
	(196.62, 76.22) --
	(197.66, 76.47) --
	(198.71, 76.62) --
	(199.76, 76.63) --
	(200.81, 76.53) --
	(201.85, 76.38) --
	(202.90, 76.23) --
	(203.95, 76.11) --
	(204.99, 76.03) --
	(206.04, 75.97) --
	(207.09, 75.91) --
	(208.13, 75.83) --
	(209.18, 75.73) --
	(210.23, 75.60) --
	(211.27, 75.46) --
	(212.32, 75.34) --
	(213.37, 75.27) --
	(214.42, 75.25) --
	(215.46, 75.31) --
	(216.51, 75.44) --
	(217.56, 75.62) --
	(218.60, 75.83) --
	(219.65, 76.05) --
	(220.70, 76.28) --
	(221.74, 76.49) --
	(222.79, 76.69) --
	(223.84, 76.88) --
	(224.88, 77.07) --
	(225.93, 77.26);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 1pt off 3pt on 4pt off 3pt ,line join=round] (143.22, 34.70) --
	(144.27, 34.67) --
	(145.32, 34.64) --
	(146.36, 34.63) --
	(147.41, 34.62) --
	(148.46, 34.63) --
	(149.50, 34.67) --
	(150.55, 34.73) --
	(151.60, 34.82) --
	(152.65, 34.95) --
	(153.69, 35.11) --
	(154.74, 35.32) --
	(155.79, 35.58) --
	(156.83, 35.89) --
	(157.88, 36.26) --
	(158.93, 36.68) --
	(159.97, 37.18) --
	(161.02, 37.74) --
	(162.07, 38.38) --
	(163.11, 39.09) --
	(164.16, 39.89) --
	(165.21, 40.78) --
	(166.26, 41.75) --
	(167.30, 42.83) --
	(168.35, 44.00) --
	(169.40, 45.28) --
	(170.44, 46.66) --
	(171.49, 48.17) --
	(172.54, 49.78) --
	(173.58, 51.52) --
	(174.63, 53.39) --
	(175.68, 55.38) --
	(176.73, 57.47) --
	(177.77, 59.62) --
	(178.82, 61.78) --
	(179.87, 63.92) --
	(180.91, 66.00) --
	(181.96, 67.97) --
	(183.01, 69.80) --
	(184.05, 71.45) --
	(185.10, 72.88) --
	(186.15, 74.04) --
	(187.19, 74.90) --
	(188.24, 75.46) --
	(189.29, 75.79) --
	(190.34, 75.97) --
	(191.38, 76.05) --
	(192.43, 76.14) --
	(193.48, 76.28) --
	(194.52, 76.56) --
	(195.57, 76.97) --
	(196.62, 77.44) --
	(197.66, 77.88) --
	(198.71, 78.21) --
	(199.76, 78.35) --
	(200.81, 78.35) --
	(201.85, 78.26) --
	(202.90, 78.12) --
	(203.95, 77.97) --
	(204.99, 77.81) --
	(206.04, 77.65) --
	(207.09, 77.48) --
	(208.13, 77.29) --
	(209.18, 77.08) --
	(210.23, 76.86) --
	(211.27, 76.64) --
	(212.32, 76.46) --
	(213.37, 76.32) --
	(214.42, 76.25) --
	(215.46, 76.25) --
	(216.51, 76.34) --
	(217.56, 76.49) --
	(218.60, 76.69) --
	(219.65, 76.95) --
	(220.70, 77.23) --
	(221.74, 77.55) --
	(222.79, 77.89) --
	(223.84, 78.25) --
	(224.88, 78.62) --
	(225.93, 78.99);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (139.09, 32.18) rectangle (230.07, 81.22);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (134.14, 31.89) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (134.14, 43.68) {3};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (134.14, 55.48) {6};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (134.14, 67.27) {9};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (136.34, 34.92) --
	(139.09, 34.92);

\path[draw=drawColor,line width= 0.6pt,line join=round] (136.34, 46.71) --
	(139.09, 46.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] (136.34, 58.51) --
	(139.09, 58.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] (136.34, 70.30) --
	(139.09, 70.30);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (152.24, 29.43) --
	(152.24, 32.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.15, 29.43) --
	(165.15, 32.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] (178.06, 29.43) --
	(178.06, 32.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] (190.96, 29.43) --
	(190.96, 32.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] (203.87, 29.43) --
	(203.87, 32.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] (216.78, 29.43) --
	(216.78, 32.18);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (146.31, 19.68) {10};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.62] at (155.10, 23.27) {3};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (159.21, 19.68) {10};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.62] at (168.01, 23.27) {4};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (172.12, 19.68) {10};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.62] at (180.92, 23.27) {5};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (185.03, 19.68) {10};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.62] at (193.82, 23.27) {6};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (197.93, 19.68) {10};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.62] at (206.73, 23.27) {7};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (210.84, 19.68) {10};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.62] at (219.64, 23.27) {8};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (184.58,  7.64) {Possible facts};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (233.95,  8.57) rectangle (348.52, 78.15);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at (239.45, 64.01) {Algorithm};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (239.45, 42.98) rectangle (253.90, 57.44);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (240.89, 50.21) -- (252.45, 50.21);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{RGB}{27,158,119}
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (246.67, 50.21) circle (  1.96);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (239.45, 28.53) rectangle (253.90, 42.98);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (240.89, 35.75) -- (252.45, 35.75);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{RGB}{217,95,2}
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (246.67, 35.75) circle (  1.96);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (239.45, 14.07) rectangle (253.90, 28.53);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (240.89, 21.30) -- (252.45, 21.30);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{RGB}{117,112,179}
\definecolor{fillColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (246.67, 21.30) circle (  1.96);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (298.38, 42.98) rectangle (312.83, 57.44);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (299.83, 50.21) -- (311.39, 50.21);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{RGB}{231,41,138}
\definecolor{fillColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (305.61, 50.21) circle (  1.96);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (298.38, 28.53) rectangle (312.83, 42.98);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round] (299.83, 35.75) -- (311.39, 35.75);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{RGB}{102,166,30}
\definecolor{fillColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (305.61, 35.75) circle (  1.96);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (298.38, 14.07) rectangle (312.83, 28.53);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt on 4pt off 3pt ,line join=round] (299.83, 21.30) -- (311.39, 21.30);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{RGB}{230,171,2}
\definecolor{fillColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (305.61, 21.30) circle (  1.96);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (259.40, 47.18) {BDD};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (259.40, 32.72) {d-DNNF};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (259.40, 18.27) {K-Best};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (318.33, 47.18) {NNF};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (318.33, 32.72) {SDD};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (318.33, 18.27) {SDDX};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,346.90);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 13.34,173.45) {Mean inference time (s)};
\end{scope}
\end{tikzpicture}

\end{document}

### 2020-05-30 text/paper2/paper.tex
New plots

@@
 decomposable NNF (d-DNNF) \cite{DBLP:journals/jair/DarwicheM02}, K-Best
-\cite{DBLP:conf/pkdd/GutmannKKR08}, and two encodings based on sentential
+\cite{DBLP:conf/ijcai/RaedtKT07}, and two encodings based on sentential
 decision diagrams \cite{DBLP:conf/ijcai/Darwiche11}, one of which encodes the
@@
 
+\bibliographystyle{splncs04}
+\bibliography{paper}
+
+\appendix
+
+% \section{Entailment Checking of Negative Cycles}
+
+% Ideally, we would like to design a constraint for negative cycles similar to the
+% constraint for independence in the previous section. However, the difficulty
+% with creating a propagation algorithm for negative cycles is that there seems to
+% be no good way to extend \cref{def:adjacency_matrix} so that the adjacency
+% matrix captures positivity/negativity. Thus, we settle for an entailment
+% algorithm with no propagation.
+
+% \begin{algorithm}
+%  \KwData{a program $\mathscr{P}$}
+%  \SetKwFunction{hasNegativeCycles}{hasNegativeCycles}
+%  Let $\mathscr{R} \subseteq \mathscr{P}$ be the largest subprogram of
+%  $\mathscr{P}$ with its $\variable{structure}$ and predicates in both body
+%  and head fully determined\footnotemark\;
+%  \lIf{\hasNegativeCycles($G_{\mathscr{R}}$)}{\Return{\textsc{false}}}
+%  \leIf{$\mathscr{R} = \mathscr{P}$}{\Return{\textsc{true}}}{\Return{\textsc{undefined}}}
+%  \caption{Entailment for negative cycles}
+%  \label{alg:negative_cycles}
+% \end{algorithm}
+% \footnotetext{Variables and constants are irrelevant to our definition of
+%  independence.}
+
+% The algorithm takes all clauses whose structure and predicates have been fully
+% determined and uses them to construct a full dependency graph. In our
+% implementation, \texttt{hasNegativeCycles} function is just a simple extension
+% of the backtracking cycle detection algorithm that `travels' around the graph
+% following edges and checking if each vertex has already been visited or not.
+% Alternatively, one could assign weights to the edges (e.g., $1$ for positive
+% and $-\infty$ for negative edges), thus reducing our negative cycle detection
+% problem to what is typically known as the negative cycle detection problem in
+% the literature, and use an algorithm such as Bellman-Ford.
+
+% If the algorithm finds a negative cycle in this fully-determined part of the
+% program, then we must return \textsc{false}. If there was no negative cycle and
+% the entire program is (sufficiently) determined, then there cannot be any
+% negative cycles. In all other cases, it is too early to tell.
+
+%    \begin{tikzpicture}
+%      \node[draw,circle,gray,text=black] (and) at (0, 0) {$\land$};
+%      \node[draw,circle,gray,text=black] (not) at (1.5, -1) {$\neg$};
+%      \node[draw,gray,text=black] (parent) at (-1.5, -1) {$\mathsf{parent}(X, Y)$};
+%      \node[draw,gray,text=black] (mother) at (1.5, -2) {$\mathsf{mother}(X, Y)$};
+%      \draw[gray] (and) -- (parent);
+%      \draw[gray] (and) -- (not);
+%      \draw[gray] (not) -- (mother);
+%    \end{tikzpicture}%
+%    \captionof{figure}{A tree representation of the body of \eqref{eq:example_clause}}
+%    \label{fig:example_tree2}
+
+\section{Additional Plots}
+
+\begin{figure*}
+ \centering
+ \input{phase_transition.tex}
+ \caption{The distribution of the number of nodes in the search tree of the
+   constraint solver as a function of the number of independent pairs of
+   predicates for $|\predicates{}| = 8$. Outliers are hidden, the dots denote
+   mean values, and the vertical axis is on a $\log_{10}$ scale. This plot
+   suggests that exceptional runs when the constraint solver takes much longer
+   than usual are most likely to occur with average levels of independence.}
+ \label{fig:phase_transition}
+\end{figure*}
+
+\begin{figure}
+  \centering
+  \input{scatterplot.tex}
+  \caption{An instance-by-instance comparison of the inference times of SDD and
+    SDDX knowledge compilation techniques. The colours show the percentage of
+    predicate pairs that were constrained to be independent. With
+    mostly-independent programs, one would expect SDD to outperform SDDX,
+    however, the data shows no significant difference.}
+\end{figure}
+
+%\begin{figure}
+%  \centering
+%  \includegraphics{algorithms.pdf}
+%\end{figure}
+
+%\begin{figure}
+%  \centering
+%  \includegraphics{cumulative.pdf}
+%  \caption{The cumulative number of instances solved by inference algorithms for
+%    increasing time limits}
+%\end{figure}
+
+\section{Example Programs}
+
+In this appendix, we provide examples of probabilistic logic programs generated
+by various combinations of parameters. In all cases, we use
+\[
+  [0.1, 0.2, \dots, 0.9, 1, 1, 1, 1, 1]
+\]
+as the list of probabilities. Each clause is written on a separate line and ends
+with a full stop. The head and the body of each clause are separated with
+\texttt{:-} (instead of $\gets$). The probability of each clause is prepended to
+the clause, using \texttt{::} as a separator. Probabilities equal to one and
+empty bodies of clauses can be omitted. Conjunction, disjunction, and negation
+are denoted by commas, semicolons, and `\texttt{\textbackslash+}', respectively.
+Parentheses are used to demonstrate precedence, although many of them are
+redundant.
+
+By setting $\predicates{} = [\texttt{p}]$, $\arities{} = [1]$, $\variables{} =
+\{ \texttt{X} \}$, $\constants{} = \emptyset$, $\maxNumNodes{} = 4$, and
+$\maxNumClauses{} = 1$, we get fifteen one-line programs, six of which are
+without negative cycles (as highlighted below). Only the last program has no
+cycles at all.
+
+\begin{enumerate}[label=\arabic*.]
+\item
+\begin{verbatim}
+0.5 :: p(X) :- (\+(p(X))), (p(X)).
+\end{verbatim}
+\item
+\begin{verbatim}
+0.8 :: p(X) :- (\+(p(X))); (p(X)).
+\end{verbatim}
+\hlitem
+\begin{verbatim}
+0.8 :: p(X) :- (p(X)); (p(X)).
+\end{verbatim}
+\hlitem
+\begin{verbatim}
+0.7 :: p(X) :- (p(X)), (p(X)).
+\end{verbatim}
+\item
+\begin{verbatim}
+0.6 :: p(X) :- (p(X)), (\+(p(X))).
+\end{verbatim}
+\item
+\begin{verbatim}
+p(X) :- (p(X)); (\+(p(X))).
+\end{verbatim}
+\hlitem
+\begin{verbatim}
+0.1 :: p(X) :- (p(X)); (p(X)); (p(X)).
+\end{verbatim}
+\hlitem
+\begin{verbatim}
+0.8 :: p(X) :- (p(X)), (p(X)), (p(X)).
+\end{verbatim}
+\item
+\begin{verbatim}
+p(X) :- \+(p(X)).
+\end{verbatim}
+\item
+\begin{verbatim}
+0.1 :: p(X) :- \+(\+(p(X))).
+\end{verbatim}
+\item
+\begin{verbatim}
+p(X) :- \+((p(X)); (p(X))).
+\end{verbatim}
+\item
+\begin{verbatim}
+0.4 :: p(X) :- \+((p(X)), (p(X))).
+\end{verbatim}
+\item
+\begin{verbatim}
+0.4 :: p(X) :- \+(\+(\+(p(X)))).
+\end{verbatim}
+\hlitem
+\begin{verbatim}
+0.7 :: p(X) :- p(X).
+\end{verbatim}
+\hlitem
+\begin{verbatim}
+p(X).
+\end{verbatim}
+\end{enumerate}
+
+Note that:
+\begin{itemize}
+\item A program such as Program~14, because of its cyclic definition, defines a
+  predicate that has probability zero across all constants. This can more easily
+  be seen as solving the equation $0.7x = x$.
+\item Programs 10 and 14 are not equivalent (i.e., double negation does not
+  cancel out) because Program 10 has a negative cycle and is thus considered to
+  be ill-defined.
+\end{itemize}
+
+To demonstrate variable symmetry reduction in action, we set $\predicates{} =
+[\texttt{p}]$, $\arities{} = [3]$, $\variables{} = \{\texttt{X}, \texttt{Y},
+\texttt{Z} \}$, $\constants{} = \emptyset$, $\maxNumNodes{} = 1$,
+$\maxNumClauses{} = 1$, and forbid all cycles. This gives us the following five
+programs:
+
+\begin{itemize}
+\item
+\begin{verbatim}
+0.8 :: p(Z, Z, Z).
+\end{verbatim}
+\item
+\begin{verbatim}
+p(Y, Y, Z).
+\end{verbatim}
+\item
+\begin{verbatim}
+p(Y, Z, Z).
+\end{verbatim}
+\item
+\begin{verbatim}
+p(Y, Z, Y).
+\end{verbatim}
+\item
+\begin{verbatim}
+0.1 :: p(X, Y, Z).
+\end{verbatim}
+\end{itemize}
+
+This is one of many possible programs with $\predicates{} = [\texttt{p},
+\texttt{q}, \texttt{r}]$, $\arities{} = [1, 2, 3]$, $\variables{} =
+\{\texttt{X}, \texttt{Y}, \texttt{Z} \}$, $\constants{} = \{ \texttt{a},
+\texttt{b}, \texttt{c} \}$, $\maxNumNodes{} = 5$, $\maxNumClauses{} = 5$, and
+without negative cycles:
+
+\begin{verbatim}
+p(b) :- \+((q(a, b)), (q(X, Y)), (q(Z, X))).
+0.4 :: q(X, X) :- \+(r(Y, Z, a)).
+q(X, a) :- r(Y, Y, Z).
+q(X, a) :- r(Y, b, Z).
+r(Y, b, Z).
+\end{verbatim}
+
+Finally, we set
+$\predicates{} = [\texttt{p}, \texttt{q}, \texttt{r}]$, $\arities{} = [1, 1,
+1]$, $\variables{} = \emptyset$, $\constants{} = \{ \texttt{a} \}$,
+$\maxNumNodes{} = 3$, $\maxNumClauses{} = 3$, forbid negative cycles, and
+constrain predicates \texttt{p} and \texttt{q} to be independent. The resulting
+search space contains thousands of programs such as:
+
+\begin{itemize}
+\item
+\begin{verbatim}
+0.5 :: p(a) :- (p(a)); (p(a)).
+0.2 :: q(a) :- (q(a)), (q(a)).
+0.4 :: r(a) :- \+(q(a)).
+\end{verbatim}
+\item
+\begin{verbatim}
+p(a) :- p(a).
+0.5 :: q(a) :- (r(a)); (q(a)).
+r(a) :- (r(a)); (r(a)).
+\end{verbatim}
+\item
+\begin{verbatim}
+p(a) :- (p(a)); (p(a)).
+0.6 :: q(a) :- q(a).
+0.7 :: r(a) :- \+(q(a)).
+\end{verbatim}
+\end{itemize}
+
 % ==============================================================================
@@
 %and we can either quickly find a solution or identify that there is none.
-
-%\begin{figure*}
-%  \centering
-%  \input{phase_transition.tex}
-%  \caption{The distribution of the number of nodes in the binary search tree as
-%    a function of the number of independent pairs of predicates for
-%    $|\predicates{}| = 8$. Outliers are hidden, the dots denote mean values, and
-%    the vertical axis is on a $\log_{10}$ scale.}
-%  \label{fig:phase_transition}
-%\end{figure*}
 
@@
 
-% \section{Entailment Checking of Negative Cycles} \label{sec:cycles}
-
-% Ideally, we would like to design a constraint for negative cycles similar to the
-% constraint for independence in the previous section. However, the difficulty
-% with creating a propagation algorithm for negative cycles is that there seems to
-% be no good way to extend \cref{def:adjacency_matrix} so that the adjacency
-% matrix captures positivity/negativity. Thus, we settle for an entailment
-% algorithm with no propagation.
-
-%\begin{algorithm}
-%  \KwData{a program $\mathscr{P}$}
-%  \SetKwFunction{hasNegativeCycles}{hasNegativeCycles}
-%  Let $\mathscr{R} \subseteq \mathscr{P}$ be the largest subprogram of
-%  $\mathscr{P}$ with its $\variable{structure}$ and predicates in both body
-%  and head fully determined\footnotemark\;
-%  \lIf{\hasNegativeCycles($G_{\mathscr{R}}$)}{\Return{\textsc{false}}}
-%  \leIf{$\mathscr{R} = \mathscr{P}$}{\Return{\textsc{true}}}{\Return{\textsc{undefined}}}
-%  \caption{Entailment for negative cycles}
-%  \label{alg:negative_cycles}
-%\end{algorithm}
-%\footnotetext{Variables and constants are irrelevant to our definition of
-%  independence.}
-
-% The algorithm takes all clauses whose structure and predicates have been fully
-% determined and uses them to construct a full dependency graph. In our
-% implementation, \texttt{hasNegativeCycles} function is just a simple extension
-% of the backtracking cycle detection algorithm that `travels' around the graph
-% following edges and checking if each vertex has already been visited or not.
-% Alternatively, one could assign weights to the edges (e.g., $1$ for positive
-% and $-\infty$ for negative edges), thus reducing our negative cycle detection
-% problem to what is typically known as the negative cycle detection problem in
-% the literature, and use an algorithm such as Bellman-Ford
-% \cite{shimbel1954structure}.
-
-% If the algorithm finds a negative cycle in this fully-determined part of the
-% program, then we must return \textsc{false}. If there was no negative cycle and
-% the entire program is (sufficiently) determined, then there cannot be any
-% negative cycles. In all other cases, it is too early to tell.
-
-%    \begin{tikzpicture}
-%      \node[draw,circle,gray,text=black] (and) at (0, 0) {$\land$};
-%      \node[draw,circle,gray,text=black] (not) at (1.5, -1) {$\neg$};
-%      \node[draw,gray,text=black] (parent) at (-1.5, -1) {$\mathsf{parent}(X, Y)$};
-%      \node[draw,gray,text=black] (mother) at (1.5, -2) {$\mathsf{mother}(X, Y)$};
-%      \draw[gray] (and) -- (parent);
-%      \draw[gray] (and) -- (not);
-%      \draw[gray] (not) -- (mother);
-%    \end{tikzpicture}%
-%    \captionof{figure}{A tree representation of the body of \eqref{eq:example_clause}}
-%    \label{fig:example_tree2}
-
-% We checked that our model agrees with the derived combinatorial formula in up
-% to a thousand different scenarios. The details of this empirical investigation
-% are omitted as they are not crucial to the thrust of this paper.
-
-\bibliographystyle{splncs04}
-\bibliography{paper}
-
 \end{document}

### 2020-05-30 text/paper2/phase_transition.tex
New plots

% Created by tikzDevice version 0.12.3 on 2020-05-30 12:36:49
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (346.90,130.09);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (346.90,130.09);
\end{scope}
\begin{scope}
\path[clip] ( 34.79, 30.69) rectangle (341.40,124.59);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 34.79, 30.69) rectangle (341.40,124.59);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.79, 77.01) --
	(341.40, 77.01);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.79,100.92) --
	(341.40,100.92);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.79,107.58) --
	(341.40,107.58);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.79, 34.95) --
	(341.40, 34.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.79, 91.75) --
	(341.40, 91.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.09, 30.69) --
	( 41.09,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 51.59, 30.69) --
	( 51.59,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.09, 30.69) --
	( 62.09,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 72.59, 30.69) --
	( 72.59,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 83.09, 30.69) --
	( 83.09,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 93.59, 30.69) --
	( 93.59,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (104.09, 30.69) --
	(104.09,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.59, 30.69) --
	(114.59,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (125.09, 30.69) --
	(125.09,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (135.59, 30.69) --
	(135.59,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (146.09, 30.69) --
	(146.09,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (156.59, 30.69) --
	(156.59,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (167.09, 30.69) --
	(167.09,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (177.59, 30.69) --
	(177.59,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (188.09, 30.69) --
	(188.09,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (198.59, 30.69) --
	(198.59,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.09, 30.69) --
	(209.09,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (219.59, 30.69) --
	(219.59,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (230.09, 30.69) --
	(230.09,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (240.59, 30.69) --
	(240.59,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (251.09, 30.69) --
	(251.09,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (261.59, 30.69) --
	(261.59,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (272.09, 30.69) --
	(272.09,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (282.60, 30.69) --
	(282.60,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (293.10, 30.69) --
	(293.10,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (303.60, 30.69) --
	(303.60,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (314.10, 30.69) --
	(314.10,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (324.60, 30.69) --
	(324.60,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (335.10, 30.69) --
	(335.10,124.59);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.09, 75.95) --
	( 41.09, 92.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.09, 52.30) --
	( 41.09, 43.78) --
	( 41.09, 30.65) --
	( 41.09,  0.76);
\definecolor{fillColor}{RGB}{224,236,244}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 37.15, 75.95) --
	( 37.15, 52.30) --
	( 41.09, 52.30) --
	( 45.03, 52.30) --
	( 45.03, 75.95) --
	( 41.09, 75.95) --
	( 37.15, 75.95) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 37.15, 64.33) --
	( 41.09, 64.33) --
	( 45.03, 64.33);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 51.59, 78.10) --
	( 51.59, 94.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 51.59, 52.30) --
	( 51.59, 39.14) --
	( 51.59,  9.06);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 47.65, 78.10) --
	( 47.65, 52.30) --
	( 51.59, 52.30) --
	( 55.53, 52.30) --
	( 55.53, 78.10) --
	( 51.59, 78.10) --
	( 47.65, 78.10) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 47.65, 64.78) --
	( 51.59, 64.78) --
	( 55.53, 64.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.09, 78.40) --
	( 62.09, 95.33);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.09, 51.68) --
	( 62.09, 37.75) --
	( 62.09,  2.66);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 58.15, 78.40) --
	( 58.15, 51.68) --
	( 62.09, 51.68) --
	( 66.03, 51.68) --
	( 66.03, 78.40) --
	( 62.09, 78.40) --
	( 58.15, 78.40) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 58.15, 65.00) --
	( 62.09, 65.00) --
	( 66.03, 65.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 72.59, 79.27) --
	( 72.59, 96.45);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 72.59, 51.80) --
	( 72.59, 38.19) --
	( 72.59,  5.26);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 68.65, 79.27) --
	( 68.65, 51.80) --
	( 72.59, 51.80) --
	( 76.53, 51.80) --
	( 76.53, 79.27) --
	( 72.59, 79.27) --
	( 68.65, 79.27) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 68.65, 65.00) --
	( 72.59, 65.00) --
	( 76.53, 65.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 83.09, 80.00) --
	( 83.09, 97.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 83.09, 51.80) --
	( 83.09, 38.19) --
	( 83.09,  5.26);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 79.15, 80.00) --
	( 79.15, 51.80) --
	( 83.09, 51.80) --
	( 87.03, 51.80) --
	( 87.03, 80.00) --
	( 83.09, 80.00) --
	( 79.15, 80.00) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 79.15, 65.50) --
	( 83.09, 65.50) --
	( 87.03, 65.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 93.59, 80.28) --
	( 93.59, 97.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 93.59, 51.93) --
	( 93.59, 38.08) --
	( 93.59,  3.55);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 89.65, 80.28) --
	( 89.65, 51.93) --
	( 93.59, 51.93) --
	( 97.53, 51.93) --
	( 97.53, 80.28) --
	( 93.59, 80.28) --
	( 89.65, 80.28) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 89.65, 65.29) --
	( 93.59, 65.29) --
	( 97.53, 65.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (104.09, 80.04) --
	(104.09, 97.53);

\path[draw=drawColor,line width= 0.6pt,line join=round] (104.09, 51.30) --
	(104.09, 37.75) --
	(104.09,  5.26);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (100.15, 80.04) --
	(100.15, 51.30) --
	(104.09, 51.30) --
	(108.03, 51.30) --
	(108.03, 80.04) --
	(104.09, 80.04) --
	(100.15, 80.04) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (100.15, 65.00) --
	(104.09, 65.00) --
	(108.03, 65.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.59, 81.09) --
	(114.59, 98.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.59, 51.30) --
	(114.59, 37.97) --
	(114.59,  6.85);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (110.66, 81.09) --
	(110.66, 51.30) --
	(114.59, 51.30) --
	(118.53, 51.30) --
	(118.53, 81.09) --
	(114.59, 81.09) --
	(110.66, 81.09) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (110.66, 65.36) --
	(114.59, 65.36) --
	(118.53, 65.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (125.09, 80.74) --
	(125.09, 98.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (125.09, 51.68) --
	(125.09, 38.62) --
	(125.09,  9.06);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (121.16, 80.74) --
	(121.16, 51.68) --
	(125.09, 51.68) --
	(129.03, 51.68) --
	(129.03, 80.74) --
	(125.09, 80.74) --
	(121.16, 80.74) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (121.16, 65.43) --
	(125.09, 65.43) --
	(129.03, 65.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (135.59, 81.32) --
	(135.59, 99.08);

\path[draw=drawColor,line width= 0.6pt,line join=round] (135.59, 51.30) --
	(135.59, 37.64) --
	(135.59,  4.42);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (131.66, 81.32) --
	(131.66, 51.30) --
	(135.59, 51.30) --
	(139.53, 51.30) --
	(139.53, 81.32) --
	(135.59, 81.32) --
	(131.66, 81.32) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (131.66, 65.29) --
	(135.59, 65.29) --
	(139.53, 65.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (146.09, 81.32) --
	(146.09, 98.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (146.09, 51.43) --
	(146.09, 42.90) --
	(146.09, 29.76) --
	(146.09,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (142.16, 81.32) --
	(142.16, 51.43) --
	(146.09, 51.43) --
	(150.03, 51.43) --
	(150.03, 81.32) --
	(146.09, 81.32) --
	(142.16, 81.32) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (142.16, 65.64) --
	(146.09, 65.64) --
	(150.03, 65.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (156.59, 81.39) --
	(156.59, 99.17);

\path[draw=drawColor,line width= 0.6pt,line join=round] (156.59, 51.30) --
	(156.59, 37.97) --
	(156.59,  6.85);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (152.66, 81.39) --
	(152.66, 51.30) --
	(156.59, 51.30) --
	(160.53, 51.30) --
	(160.53, 81.39) --
	(156.59, 81.39) --
	(152.66, 81.39) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (152.66, 65.64) --
	(156.59, 65.64) --
	(160.53, 65.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (167.09, 81.77) --
	(167.09, 99.66);

\path[draw=drawColor,line width= 0.6pt,line join=round] (167.09, 51.17) --
	(167.09, 37.53) --
	(167.09,  4.42);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (163.16, 81.77) --
	(163.16, 51.17) --
	(167.09, 51.17) --
	(171.03, 51.17) --
	(171.03, 81.77) --
	(167.09, 81.77) --
	(163.16, 81.77) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (163.16, 65.43) --
	(167.09, 65.43) --
	(171.03, 65.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (177.59, 81.73) --
	(177.59, 99.63);

\path[draw=drawColor,line width= 0.6pt,line join=round] (177.59, 51.05) --
	(177.59, 37.64) --
	(177.59,  6.06);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (173.66, 81.73) --
	(173.66, 51.05) --
	(177.59, 51.05) --
	(181.53, 51.05) --
	(181.53, 81.73) --
	(177.59, 81.73) --
	(173.66, 81.73) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (173.66, 65.14) --
	(177.59, 65.14) --
	(181.53, 65.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (188.09, 81.95) --
	(188.09, 99.79);

\path[draw=drawColor,line width= 0.6pt,line join=round] (188.09, 51.17) --
	(188.09, 37.97) --
	(188.09,  7.61);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (184.16, 81.95) --
	(184.16, 51.17) --
	(188.09, 51.17) --
	(192.03, 51.17) --
	(192.03, 81.95) --
	(188.09, 81.95) --
	(184.16, 81.95) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (184.16, 65.43) --
	(188.09, 65.43) --
	(192.03, 65.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (198.59, 81.87) --
	(198.59, 99.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] (198.59, 51.43) --
	(198.59, 38.19) --
	(198.59,  7.61);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (194.66, 81.87) --
	(194.66, 51.43) --
	(198.59, 51.43) --
	(202.53, 51.43) --
	(202.53, 81.87) --
	(198.59, 81.87) --
	(194.66, 81.87) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (194.66, 65.64) --
	(198.59, 65.64) --
	(202.53, 65.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.09, 82.43) --
	(209.09,100.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.09, 51.05) --
	(209.09, 37.53) --
	(209.09,  5.26);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (205.16, 82.43) --
	(205.16, 51.05) --
	(209.09, 51.05) --
	(213.03, 51.05) --
	(213.03, 82.43) --
	(209.09, 82.43) --
	(205.16, 82.43) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (205.16, 65.68) --
	(209.09, 65.68) --
	(213.03, 65.68);

\path[draw=drawColor,line width= 0.6pt,line join=round] (219.59, 82.36) --
	(219.59,100.38);

\path[draw=drawColor,line width= 0.6pt,line join=round] (219.59, 50.92) --
	(219.59, 37.97) --
	(219.59,  9.06);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (215.66, 82.36) --
	(215.66, 50.92) --
	(219.59, 50.92) --
	(223.53, 50.92) --
	(223.53, 82.36) --
	(219.59, 82.36) --
	(215.66, 82.36) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (215.66, 65.43) --
	(219.59, 65.43) --
	(223.53, 65.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (230.09, 82.57) --
	(230.09,100.73);

\path[draw=drawColor,line width= 0.6pt,line join=round] (230.09, 50.66) --
	(230.09, 37.31) --
	(230.09,  6.06);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (226.16, 82.57) --
	(226.16, 50.66) --
	(230.09, 50.66) --
	(234.03, 50.66) --
	(234.03, 82.57) --
	(230.09, 82.57) --
	(226.16, 82.57) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (226.16, 65.36) --
	(230.09, 65.36) --
	(234.03, 65.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (240.59, 83.13) --
	(240.59,101.31);

\path[draw=drawColor,line width= 0.6pt,line join=round] (240.59, 50.92) --
	(240.59, 37.53) --
	(240.59,  6.06);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (236.66, 83.13) --
	(236.66, 50.92) --
	(240.59, 50.92) --
	(244.53, 50.92) --
	(244.53, 83.13) --
	(240.59, 83.13) --
	(236.66, 83.13) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (236.66, 65.50) --
	(240.59, 65.50) --
	(244.53, 65.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (251.09, 83.03) --
	(251.09,101.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] (251.09, 50.66) --
	(251.09, 36.97) --
	(251.09,  3.55);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (247.16, 83.03) --
	(247.16, 50.66) --
	(251.09, 50.66) --
	(255.03, 50.66) --
	(255.03, 83.03) --
	(251.09, 83.03) --
	(247.16, 83.03) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (247.16, 65.36) --
	(251.09, 65.36) --
	(255.03, 65.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (261.59, 83.55) --
	(261.59,101.89);

\path[draw=drawColor,line width= 0.6pt,line join=round] (261.59, 50.53) --
	(261.59, 36.97) --
	(261.59,  4.42);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (257.66, 83.55) --
	(257.66, 50.53) --
	(261.59, 50.53) --
	(265.53, 50.53) --
	(265.53, 83.55) --
	(261.59, 83.55) --
	(257.66, 83.55) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (257.66, 65.36) --
	(261.59, 65.36) --
	(265.53, 65.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (272.09, 82.85) --
	(272.09,100.68);

\path[draw=drawColor,line width= 0.6pt,line join=round] (272.09, 50.79) --
	(272.09, 37.53) --
	(272.09,  6.85);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (268.16, 82.85) --
	(268.16, 50.79) --
	(272.09, 50.79) --
	(276.03, 50.79) --
	(276.03, 82.85) --
	(272.09, 82.85) --
	(268.16, 82.85) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (268.16, 65.21) --
	(272.09, 65.21) --
	(276.03, 65.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (282.60, 83.58) --
	(282.60,101.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (282.60, 50.39) --
	(282.60, 37.08) --
	(282.60,  6.06);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (278.66, 83.58) --
	(278.66, 50.39) --
	(282.60, 50.39) --
	(286.53, 50.39) --
	(286.53, 83.58) --
	(282.60, 83.58) --
	(278.66, 83.58) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (278.66, 64.78) --
	(282.60, 64.78) --
	(286.53, 64.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (293.10, 83.79) --
	(293.10,102.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] (293.10, 50.26) --
	(293.10, 36.97) --
	(293.10,  6.06);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (289.16, 83.79) --
	(289.16, 72.33) --
	(289.16, 50.26) --
	(293.10, 50.26) --
	(297.03, 50.26) --
	(297.03, 72.33) --
	(297.03, 83.79) --
	(293.10, 83.79) --
	(289.16, 83.79) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (289.16, 65.07) --
	(293.10, 65.07) --
	(297.03, 65.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (303.60, 84.22) --
	(303.60,102.80);

\path[draw=drawColor,line width= 0.6pt,line join=round] (303.60, 50.00) --
	(303.60, 37.31) --
	(303.60,  9.75);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (299.66, 84.22) --
	(299.66, 72.62) --
	(299.66, 50.00) --
	(303.60, 50.00) --
	(307.53, 50.00) --
	(307.53, 72.62) --
	(307.53, 84.22) --
	(303.60, 84.22) --
	(299.66, 84.22) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (299.66, 64.78) --
	(303.60, 64.78) --
	(307.53, 64.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (314.10, 84.32) --
	(314.10,102.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (314.10, 49.73) --
	(314.10, 36.27) --
	(314.10,  4.42);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (310.16, 84.32) --
	(310.16, 72.65) --
	(310.16, 49.73) --
	(314.10, 49.73) --
	(318.03, 49.73) --
	(318.03, 72.65) --
	(318.03, 84.32) --
	(314.10, 84.32) --
	(310.16, 84.32) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (310.16, 64.63) --
	(314.10, 64.63) --
	(318.03, 64.63);

\path[draw=drawColor,line width= 0.6pt,line join=round] (324.60, 84.89) --
	(324.60,103.68);

\path[draw=drawColor,line width= 0.6pt,line join=round] (324.60, 49.45) --
	(324.60, 36.39) --
	(324.60,  6.85);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (320.66, 84.89) --
	(320.66, 73.06) --
	(320.66, 49.45) --
	(324.60, 49.45) --
	(328.53, 49.45) --
	(328.53, 73.06) --
	(328.53, 84.89) --
	(324.60, 84.89) --
	(320.66, 84.89) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (320.66, 63.57) --
	(324.60, 63.57) --
	(328.53, 63.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] (335.10, 86.34) --
	(335.10,105.44);

\path[draw=drawColor,line width= 0.6pt,line join=round] (335.10, 49.04) --
	(335.10, 35.80) --
	(335.10,  5.26);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (331.16, 86.34) --
	(331.16, 74.16) --
	(331.16, 49.04) --
	(335.10, 49.04) --
	(339.03, 49.04) --
	(339.03, 74.16) --
	(339.03, 86.34) --
	(335.10, 86.34) --
	(331.16, 86.34) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (331.16, 62.38) --
	(335.10, 62.38) --
	(339.03, 62.38);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 41.09, 71.66) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 51.59, 79.45) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 62.09, 87.80) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 72.59, 91.37) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 83.09, 92.89) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 93.59, 98.48) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.09,100.35) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.59,104.38) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.09,105.75) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (135.59,110.28) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (146.09,110.49) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (156.59,109.72) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.09,114.89) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (177.59,113.61) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (188.09,115.59) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (198.59,116.86) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (209.09,115.92) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (219.59,117.85) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (230.09,116.11) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (240.59,117.57) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (251.09,117.72) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (261.59,118.06) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (272.09,117.37) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (282.60,116.43) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (293.10,113.89) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (303.60,112.76) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (314.10,107.36) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (324.60,102.11) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (335.10, 98.37) circle (  1.96);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 34.79, 30.69) rectangle (341.40,124.59);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96, 31.18) {10};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.62] at ( 26.76, 34.78) {2};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96, 87.98) {10};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.62] at ( 26.76, 91.58) {3};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.04, 34.95) --
	( 34.79, 34.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.04, 91.75) --
	( 34.79, 91.75);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.09, 27.94) --
	( 41.09, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 51.59, 27.94) --
	( 51.59, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.09, 27.94) --
	( 62.09, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 72.59, 27.94) --
	( 72.59, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 83.09, 27.94) --
	( 83.09, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 93.59, 27.94) --
	( 93.59, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (104.09, 27.94) --
	(104.09, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.59, 27.94) --
	(114.59, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (125.09, 27.94) --
	(125.09, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (135.59, 27.94) --
	(135.59, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (146.09, 27.94) --
	(146.09, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (156.59, 27.94) --
	(156.59, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (167.09, 27.94) --
	(167.09, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (177.59, 27.94) --
	(177.59, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (188.09, 27.94) --
	(188.09, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (198.59, 27.94) --
	(198.59, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.09, 27.94) --
	(209.09, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (219.59, 27.94) --
	(219.59, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (230.09, 27.94) --
	(230.09, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (240.59, 27.94) --
	(240.59, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (251.09, 27.94) --
	(251.09, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (261.59, 27.94) --
	(261.59, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (272.09, 27.94) --
	(272.09, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (282.60, 27.94) --
	(282.60, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (293.10, 27.94) --
	(293.10, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (303.60, 27.94) --
	(303.60, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (314.10, 27.94) --
	(314.10, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (324.60, 27.94) --
	(324.60, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (335.10, 27.94) --
	(335.10, 30.69);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 41.09, 19.68) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 51.59, 19.68) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 62.09, 19.68) {2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 72.59, 19.68) {3};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 83.09, 19.68) {4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 93.59, 19.68) {5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (104.09, 19.68) {6};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (114.59, 19.68) {7};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (125.09, 19.68) {8};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (135.59, 19.68) {9};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (146.09, 19.68) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (156.59, 19.68) {11};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (167.09, 19.68) {12};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (177.59, 19.68) {13};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (188.09, 19.68) {14};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (198.59, 19.68) {15};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (209.09, 19.68) {16};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (219.59, 19.68) {17};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (230.09, 19.68) {18};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (240.59, 19.68) {19};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (251.09, 19.68) {20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (261.59, 19.68) {21};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (272.09, 19.68) {22};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (282.60, 19.68) {23};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (293.10, 19.68) {24};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (303.60, 19.68) {25};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (314.10, 19.68) {26};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (324.60, 19.68) {27};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (335.10, 19.68) {28};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (188.09,  7.64) {Independent pairs};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08, 77.64) {Nodes};
\end{scope}
\end{tikzpicture}

### 2020-05-30 scripts/analyse_problog.R

@@ -6,6 +6,8 @@ require(scales)
 require(grid)
 require(tidyr)
 require(tikzDevice)
+require(tidyverse)
+require(plyr)
 
 only_relevant_columns <- c("number.of.predicates", "number.of.variables",
                            "maximum.number.of.nodes", "maximum.arity",
@@ -17,12 +19,12 @@ relevant_columns <- c("number.of.predicates", "number.of.variables",
                       "number.of.independent.pairs", "domain.size",
                       "number.of.facts", "proportion.probabilistic",
                       "proportion.listed", "proportion.independent.pairs", "universe.size", "Total.time")
-pretty_names <- c("The number of predicates", "The number of variables",
-                  "Maximum number of nodes", "Maximum arity",
-                  "The number of independent pairs", "Domain size",
-                  "The number of facts", "The proportion of probabilistic facts",
-                  "The proportion of listed facts", "The proportion of independent pairs",
-                  "The number of possible facts")
+pretty_names <- c("Predicates", "Variables",
+                  "Nodes", "Maximum arity",
+                  "Independent", "Domain size",
+                  "Facts ($\\times 10^3$)", "Probabilistic (\\%)",
+                  "Proportion listed", "Independent (\\%)",
+                  "Possible facts")
 
 prepare.csv <- function(filename) {
   df <- read.csv(filename, header = TRUE, sep = ",")
@@ -54,12 +56,27 @@ sddx <- sddx[sddx$ID %in% sdd$ID,]
 ddnnf <- ddnnf[ddnnf$ID %in% sdd$ID,]
 bdd <- bdd[bdd$ID %in% sdd$ID,]
 
+sdd <- sdd %>% mutate(count = map_int(Total.time, ~ sum(.x >= Total.time)))
+nnf <- nnf %>% mutate(count = map_int(Total.time, ~ sum(.x >= Total.time)))
+kbest <- kbest %>% mutate(count = map_int(Total.time, ~ sum(.x >= Total.time)))
+sddx <- sddx %>% mutate(count = map_int(Total.time, ~ sum(.x >= Total.time)))
+ddnnf <- ddnnf %>% mutate(count = map_int(Total.time, ~ sum(.x >= Total.time)))
+bdd <- bdd %>% mutate(count = map_int(Total.time, ~ sum(.x >= Total.time)))
+
+combined.pure <- rbind.fill(cbind(sdd, Algorithm = "SDD"),
[…]

### 2020-06-02 text/paper2/paper.tex
Un-anonymise

@@
 \title{Generating Random Logic Programs Using Constraint Programming}
-%\author{Paulius Dilkas\inst{1} \and
-%Vaishak Belle\inst{1,2}}
-%\authorrunning{P. Dilkas and V. Belle}
-%\institute{University of Edinburgh, Edinburgh, UK \email{\{p.dilkas@sms.,vaishak@\}ed.ac.uk} \and Alan Turing Institute, London, UK}
+\author{Paulius Dilkas\inst{1} \and
+Vaishak Belle\inst{1,2}}
+\authorrunning{P. Dilkas and V. Belle}
+\institute{University of Edinburgh, Edinburgh, UK \email{\{p.dilkas@sms.,vaishak@\}ed.ac.uk} \and Alan Turing Institute, London, UK}
 
@@
 
-%\subsubsection*{Acknowledgments.}
-%This work was supported by the EPSRC Centre for Doctoral Training in Robotics
-%and Autonomous Systems, funded by the UK Engineering and Physical Sciences
-%Research Council (grant EP/S023208/1).
+\subsubsection*{Acknowledgments.}
+This work was supported by the EPSRC Centre for Doctoral Training in Robotics
+and Autonomous Systems, funded by the UK Engineering and Physical Sciences
+Research Council (grant EP/S023208/1).
 

### 2020-07-12 text/paper2/paper.tex
arXiv compatibility
Finishing touches

--- 2020-05-21 text/paper2/paper.tex
@@
 \usepackage{booktabs}
-
+\usepackage[misc,geometry]{ifsym}
+
+\usetikzlibrary{arrows.meta}
 \captionsetup[subfigure]{width=\linewidth}
+\spnewtheorem{constraint}{Constraint}{\bfseries}{\itshape}
 
@@
 \newcommand{\hilight}[1]{\setlength{\fboxsep}{1pt}\colorbox{lightgray}{#1}}
-\newcommand{\hlitem}{\stepcounter{enumi}\item[\hilight{\theenumi}]}
 
@@
 
-\makeatletter
-\newcommand{\nosemic}{\renewcommand{\@endalgocfline}{\relax}}% Drop semi-colon ;
-\newcommand{\dosemic}{\renewcommand{\@endalgocfline}{\algocf@endline}}% Reinstate semi-colon ;
-\newcommand{\pushline}{\Indp}% Indent
-\newcommand{\popline}{\Indm\dosemic}% Undent
-\makeatother
-
-\spnewtheorem{constraint}{Constraint}{\bfseries}{\itshape}
-
 \DeclareMathOperator{\Determined}{\Delta}
@@
 
-\usetikzlibrary{arrows.meta}
-%\relpenalty=10000
-%\binoppenalty=10000
-
 \begin{document}
@@
 \title{Generating Random Logic Programs Using Constraint Programming}
-%\author{Paulius Dilkas\inst{1} \and
-%Vaishak Belle\inst{1,2}}
-%\authorrunning{P. Dilkas and V. Belle}
-%\institute{University of Edinburgh, Edinburgh, UK \email{\{p.dilkas@sms.,vaishak@\}ed.ac.uk} \and Alan Turing Institute, London, UK}
+\author{Paulius Dilkas\inst{1} \and Vaishak Belle\inst{1,2}$^{(\textrm{\Letter})}$}
+\authorrunning{P. Dilkas and V. Belle}
+\institute{University of Edinburgh, Edinburgh, UK
+  \email{\{p.dilkas@sms.,vaishak@\}ed.ac.uk} \and Alan Turing Institute, London,
+  UK}
 
@@
   \keywords{Constraint programming \and Probabilistic logic programming \and
-    Statistical relational learning.}
+    Statistical relational learning}
 \end{abstract}
@@
 integer refers to a logical construct (e.g., a logical variable or a constant),
-we will make no distinction between the two and often use names of logical
-constructs to refer to the underlying integers. We say that a constraint
-variable is \emph{(fully) determined} if its domain (at the given moment in the
-execution) has exactly one value. We will often use $\Box$ as a special domain
-value to indicate a `disabled' (i.e., fixed and ignored) part of the model. We
-write $\arrayd{a}{b}{c}$ to mean that $\variable{a}$ is an array of variables of
-length $b$ such that each element of $\variable{a}$ has domain $c$. Similarly,
-we write $\arrayt{a}{b}{c}$ to denote an array $\variable{a}$ of length $b$ such
-that each element of $\variable{a}$ has type $\variable{c}$. Finally, we assume
-that all arrays start with index zero.
-
-\paragraph{Parameters of the model.} We begin defining the parameters of our
-model by initialising sets and lists of the primitives used in constructing
-logic programs: a list of predicates $\predicates{}$, a list of their
-corresponding arities $\arities{}$ (so $|\arities{}|$ = $|\predicates{}|$), a
-set of variables $\variables{}$, and a set of constants $\constants{}$. Either
-$\variables{}$ or $\constants{}$ can be empty, but we assume that
-$|\constants{}| + |\variables{}| > 0$. Similarly, the model supports zero-arity
-predicates but requires at least one predicate to have non-zero arity. For
-notational convenience, we also set $\maxArity{} = \max \arities{}$. Next, we
-need a measure of how complex a body of a clause can be. As we represent each
-body by a tree (see \cref{sec:bodies}), we set $\maxNumNodes{} \ge 1$ to
-be the maximum number of nodes in the tree representation of any clause. We also
-set $\maxNumClauses{}$ to be the maximum number of clauses in a program. We must
-have that $\maxNumClauses{} \ge |\predicates{}|$ because we require each
-predicate to have at least one clause that defines it. The model supports
-enforcing predicate independence (see \cref{sec:independence}), so a set of
-independent pairs of predicates is another parameter. Since this model can
-generate probabilistic as well as non-probabilistic programs, each clause is
-paired with a probability which is randomly selected from a given list---our
-last parameter. For generating non-probabilistic programs, one can set this list
-to $[1]$. Finally, we define $\tokens{} = \{ \neg, \land, \lor, \top \}$ as the
-set of tokens that (together with atoms) form a clause. All decision variables
-of the model can now be divided into $2 \times \maxNumClauses{}$ separate
-groups, treating the body and the head of each clause separately. We say that
-the variables are contained in two arrays:
-$\arrayt{bodies}{\maxNumClauses{}}{Body}$ and
+we will make no distinction between the two. We say that a constraint variable
+is \emph{(fully) determined} if its domain (at the time) has exactly one value.
+We let $\Box$ denote the absent/disabled value of an optional variable
+\cite{DBLP:conf/cpaior/MearsSSTMW14}. We write $\arrayd{a}{b}{c}$ to mean that
+$\variable{a}$ is an array of variables of length $b$ such that each element of
+$\variable{a}$ has domain $c$. Similarly, we write $\arrayt{a}{b}{c}$ to denote
+an array $\variable{a}$ of length $b$ such that each element of $\variable{a}$
+has type $\variable{c}$. Finally, we assume that all arrays start with index
+zero.
+
+\paragraph{Parameters of the model.} We begin by defining sets and lists of the
+primitives used in constructing logic programs: a list of predicates
+$\predicates{}$, a list of their corresponding arities $\arities{}$ (so
+$|\arities{}|$ = $|\predicates{}|$), a set of variables $\variables{}$, and a
+set of constants $\constants{}$. Either $\variables{}$ or $\constants{}$ can be
+empty, but we assume that $|\constants{}| + |\variables{}| > 0$. Similarly, the
+model supports zero-arity predicates but requires at least one predicate to have
+non-zero arity. For notational convenience, we also set $\maxArity{} = \max
+\arities{}$. Next, we need a measure of how complex a body of a clause can be.
+As we represent each body by a tree (see \cref{sec:bodies}), we set
+$\maxNumNodes{} \ge 1$ to be the maximum number of nodes in the tree
+representation of any clause. We also set $\maxNumClauses{}$ to be the maximum
+number of clauses in a program. We must have that $\maxNumClauses{} \ge
+|\predicates{}|$ because we require each predicate to have at least one clause
+that defines it. The model supports enforcing predicate independence (see
+\cref{sec:independence}), so a set of independent pairs of predicates is another
+parameter. Since this model can generate probabilistic as well as
+non-probabilistic programs, each clause is paired with a probability which is
+randomly selected from a given list---our last parameter. For generating
+non-probabilistic programs, one can set this list to $[1]$. Finally, we define
+$\tokens{} = \{ \neg, \land, \lor, \top \}$ as the set of tokens that (together
+with atoms) form a clause. All decision variables of the model can now be
+divided into $2 \times \maxNumClauses{}$ separate groups, treating the body and
+the head of each clause separately. We say that the variables are contained in
+two arrays: $\arrayt{bodies}{\maxNumClauses{}}{Body}$ and
 $\arrayt{heads}{\maxNumClauses{}}{Head}$.
@@
 \end{constraint}
-We can also add a constraint that each predicate $\mathsf{P} \in \predicates{}$
-should have at least one clause with $\mathsf{P}$ at its head.
+We also add a constraint that each predicate should get at least one clause.
 \begin{constraint}
@@
 \end{constraint}
-Finally, clauses are supposed to constitute a set but with one important
-exception: there may be more than one disabled clause, i.e., a clause with head
-$\variable{predicate} = \Box$. Assuming a lexicographic order over entire
-clauses such that $\Box > \mathsf{P}$ for all $\mathsf{P} \in \predicates{}$ and
-the head predicate is the `first digit' of this representation, we get the
-following constraint.
+Finally, we want to disable duplicate clauses but with one exception: there may
+be more than one disabled clause, i.e., a clause with head $\variable{predicate}
+= \Box$. Assuming a lexicographic order over entire clauses such that $\Box >
+\mathsf{P}$ for all $\mathsf{P} \in \predicates{}$ and the head predicate is the
+`first digit' of this representation, the following constraint disables
+duplicates as well as orders the clauses.
 \begin{constraint}
@@
 
-To demonstrate the correctness of the model, in this section we are going to
-derive combinatorial expressions for counting the number of programs with up to
-$\maxNumClauses{}$ clauses and up to $\maxNumNodes{}$ nodes per clause, and
-arbitrary $\predicates{}$, $\arities{}$, $\variables{}$, and $\constants{}$.
-Being able to establish two ways to generate the same sequence of numbers (i.e.,
-numbers of programs with certain properties and parameters) allows us to gain
-confidence that the constraint model accurately matches our intentions. For this
-section, we introduce the term \emph{total arity} of a body of a clause to refer
-to the sum total of arities of all predicates in the body.
+To demonstrate the correctness of the model, this section derives combinatorial
+expressions for counting the number of programs with up to $\maxNumClauses{}$
+clauses and up to $\maxNumNodes{}$ nodes per clause, and arbitrary
+$\predicates{}$, $\arities{}$, $\variables{}$, and $\constants{}$. Being able to
+establish two ways to generate the same sequence of numbers (i.e., numbers of
+programs with certain properties and parameters) allows us to gain confidence
+that the constraint model accurately matches our intentions. For this section,
+we introduce the term \emph{total arity} of a body of a clause to refer to the
+sum total of arities of all predicates in the body.
 
@@
 $i$th predicate. The number of programs is then:
-\[
+\begin{equation} \label{eq:counting}
   \sum_{\substack{ \sum_{i=1}^{|\predicates{}|} h_i = n,\\
@@
   \binom{\sum_{a=0}^{\maxArity{} \times \maxNumNodes{}} C(a) P(a+a_i)}{h_i},
-\]
-Here, we sum over all possible ways to distribute $|\predicates{}| \le n \le
+\end{equation}
+Here, we sum over all ways to distribute $|\predicates{}| \le n \le
 \maxNumClauses{}$ clauses among $|\predicates{}|$ predicates so that each
@@
 select the required $a+a_i$ terms in the body and the head of the clause.
+Finally, we compare the numbers produced by \eqref{eq:counting} with the numbers
+of programs generated by our model in \num{1032} different scenarios, thus
+showing that the combinatorial description developed in this section matches the
+model's behaviour.
 
@@
 
-In this section, we present custom constraints for stratification and
-independence. Stratification is a condition necessary for probabilistic logic
-programs \cite{DBLP:conf/padl/MantadelisR17} and often enforced on logic
-programs \cite{DBLP:journals/tcs/Bidoit91} that helps to ensure a unique answer
-to every query, while independence is a fundamental concept in probability
-theory that imposes structure on the probability distribution and simplifies
-inference. In the context of probabilistic logic programming languages, these
-two seemingly disparate concepts can be defined using the same building block,
-i.e., a predicate dependency graph. Constraints are usually presented with two
-algorithms: one for \emph{entailment} checking, i.e., checking if the (partially
-solved) constraint model satisfies the constraint or not, and one for
-\emph{propagation}, i.e., removing values from domains that are incompatible
-with the current state of the model. We present both algorithms for independence
-while settling for a short description of entailment for stratification.
-
-Let $\mathscr{P}$ be a probabilistic logic program with its set of predicates
-$\predicates{}$. Its \emph{(predicate) dependency graph} is a directed graph
-$G_{\mathscr{P}}$ with elements of $\predicates{}$ as nodes and an edge between
-$\mathsf{P}, \mathsf{Q} \in \predicates{}$ if there is a clause in $\mathscr{P}$
-with $\mathsf{Q}$ as the head and $\mathsf{P}$ mentioned in the body. We say
-that the edge is \emph{negative} if there exists a clause with $\mathsf{Q}$ as
-the head and at least one instance of $\mathsf{P}$ at the body such that the
-path from the root to the $\mathsf{P}$ node in the tree representation of the
-clause passes through at least one negation node; otherwise, it is
-\emph{positive}. We say that $\mathscr{P}$ (or $G_{\mathscr{P}}$) has a
-\emph{negative cycle} if $G_{\mathscr{P}}$ has a cycle with at least one
-negative edge. A program $\mathscr{P}$ is \emph{stratified} if $G_{\mathscr{P}}$
-has no negative cycles.\footnote{This definition is an extension of a well-known
-  result for logic programs \cite{DBLP:journals/jlp/BalbinPRM91} to
-  probabilistic logic programs with arbitrary complex clause bodies.} Thus a
-simple entailment algorithm for stratification can be constructed by selecting
-all clauses, all predicates of which are fully determined, and looking for
-negative cycles in the dependency graph constructed based on those clauses using
-an algorithm such as Bellman-Ford.
+\emph{Stratification} is a condition necessary for probabilistic logic programs
+\cite{DBLP:conf/padl/MantadelisR17} and often enforced on logic programs
+\cite{DBLP:journals/tcs/Bidoit91} that helps to ensure a unique answer to every
+query. This is achieved by restricting the use of negation so that any program
+$\mathscr{P}$ can be partitioned into a sequence of programs $\mathscr{P} =
+\bigsqcup_{i=1}^n \mathscr{P}_i$ such that, for all $i$, the negative literals
+in $\mathscr{P}_i$ can only refer to predicates defined in $\mathscr{P}_j$ for
+$j \le i$ \cite{DBLP:journals/tcs/Bidoit91}.
+
+\emph{Independence}, on the other hand, is defined on a pair of predicates (say,
+$\mathsf{P}, \mathsf{Q} \in \mathcal{P}$) and can be interpreted in two ways.
+First, if $\mathsf{P}$ and $\mathsf{Q}$ are independent, then any ground atom of
+$\mathsf{P}$ is independent of any ground atom of $\mathsf{Q}$ in the underlying
+probability distribution of the probabilistic program. Second, the part of the
+program needed to fully define $\mathsf{P}$ is disjoint from the part of the
+program needed to define $\mathsf{Q}$.
+
+These two seemingly disparate concepts can be defined using the same building
+block, i.e., a predicate dependency graph. Let $\mathscr{P}$ be a probabilistic
+logic program with its set of predicates $\predicates{}$. Its \emph{(predicate)
+  dependency graph} is a directed graph $G_{\mathscr{P}}$ with elements of
+$\predicates{}$ as nodes and an edge between $\mathsf{P}, \mathsf{Q} \in
+\predicates{}$ if there is a clause in $\mathscr{P}$ with $\mathsf{Q}$ as the
+head and $\mathsf{P}$ mentioned in the body. We say that the edge is
+\emph{negative} if there exists a clause with $\mathsf{Q}$ as the head and at
+least one instance of $\mathsf{P}$ at the body such that the path from the root
+to the $\mathsf{P}$ node in the tree representation of the clause passes through
+at least one negation node; otherwise, it is \emph{positive}. We say that
+$\mathscr{P}$ (or $G_{\mathscr{P}}$) has a \emph{negative cycle} if
+$G_{\mathscr{P}}$ has a cycle with at least one negative edge. A program
+$\mathscr{P}$ is \emph{stratified} if $G_{\mathscr{P}}$ has no negative
+cycles.\footnote{This definition is an extension of a well-known result for
+  logic programs \cite{DBLP:journals/jlp/BalbinPRM91} to probabilistic logic
+  programs with arbitrary complex clause bodies.} Thus a simple entailment
+algorithm for stratification can be constructed by selecting all clauses, all
+predicates of which are fully determined, and looking for negative cycles in the
+dependency graph constructed based on those clauses using an algorithm such as
+Bellman-Ford.
 
@@
     \captionof{figure}{The predicate dependency graph of the program from
-      \cref{ex:program}. Positive edges are labelled with `$+$', and negative
-      edges with `$-$'.}
+      \protect{\cref{ex:program}}. Positive edges are labelled with `$+$', and
+      negative edges with `$-$'.}
     \label{fig:predicate_dependencies}
@@
     \end{minipage}
-    \caption{The predicate dependency graph of \cref{example:independence}}
+    \caption{The predicate dependency graph of \protect{\cref{example:independence}}}
     \label{fig:example}
@@
 programs. The experiments were run on a system with Intel Core i5-8250U
-processor, \SI{8}{\giga\byte} RAM, and Arch Linux~5.6.11-arch1-1 operating
-system. The constraint model was implemented in Java~8 with
-Choco~4.10.2 \cite{choco}. All inference algorithms are implemented in
-\textsc{ProbLog}~2.1.0.39 and were run using Python~3.8.2 with PySDD~0.2.10 and
-PyEDA~0.28.0. For both sets of experiments, we generate programs without
+processor and \SI{8}{\giga\byte} of RAM. The constraint model was implemented in
+Java~8 with Choco~4.10.2 \cite{choco}. All inference algorithms are implemented
+in \textsc{ProbLog}~2.1.0.39 and were run using Python~3.8.2 with PySDD~0.2.10
+and PyEDA~0.28.0. For both sets of experiments, we generate programs without
 negative cycles and use a \SI{60}{\second} timeout.
@@
   solutions, in which case search is complete regardless of the variable
-  ordering heuristic.} We ran close to \num{400000} experiments, investigating
-whether the model is efficient enough to generate reasonably-sized programs and
-gaining insight into what parameter values make the CSP harder. For
-$|\predicates{}|$, $|\variables{}|$, $|\constants{}|$, $\maxNumNodes{}$, and
-$\maxNumClauses{} - |\predicates{}|$ (i.e., the number of clauses in addition to
-the mandatory $|\predicates{}|$ clauses), we assign all combinations of 1, 2, 4,
-8. $\maxArity{}$ is assigned to values 1--4. For each $|\predicates{}|$, we also
-iterate over all possible numbers of independent pairs of predicates, ranging
-from 0 up to $\binom{|\predicates{}|}{2}$. For each combination of the
-above-mentioned parameters, we pick ten random ways to assign arities to
-predicates (such that $\maxArity{}$ occurs at least once) and ten random
-combinations of independent pairs.
+  ordering heuristic.} We ran \num{399360} experiments, investigating the
+model's efficiency and gaining insight into what parameter values make the CSP
+harder. For $|\predicates{}|$, $|\variables{}|$, $|\constants{}|$,
+$\maxNumNodes{}$, and $\maxNumClauses{} - |\predicates{}|$ (i.e., the number of
+clauses in addition to the mandatory $|\predicates{}|$ clauses), we assign all
+combinations of 1, 2, 4, 8. $\maxArity{}$ is assigned to values 1--4. For each
+$|\predicates{}|$, we also iterate over all possible numbers of independent
+pairs of predicates, ranging from 0 up to $\binom{|\predicates{}|}{2}$. For each
+combination of the above-mentioned parameters, we pick ten random ways to assign
+arities to predicates (such that $\maxArity{}$ occurs at least once) and ten
+random combinations of independent pairs.
 
@@
     \captionof{figure}{Inference time for different values of $\maxArity{}$ and
-      proportions of facts that are probabilistic. The total number of facts is
-      fixed at $10^5$.}
+      proportions of probabilistic facts that are probabilistic. The total
+      number of facts is fixed at $10^5$.}
     \label{fig:bars}
@@
 |\variables{}|, \maxNumNodes{} \in \{ 2, 4, 8 \}$, $\maxArity{} \in \{ 1, 2, 3
-\}$, $\maxNumClauses{} = |\predicates{}|$, $\constants{} = \emptyset$. Just like
+\}$, $\maxNumClauses{} = |\predicates{}|$, $\constants{} = \emptyset$. These
+values are (approximately) representative of many standard benchmarking
+instances which often have 2--8 predicates of arity one or two, 0--8 rules, and
+a larger database of facts \cite{DBLP:journals/tplp/FierensBRSGTJR15}. Just like
 before, we explore all possible numbers of independent predicate pairs. We also
@@
 decomposable NNF (d-DNNF) \cite{DBLP:journals/jair/DarwicheM02}, K-Best
-\cite{DBLP:conf/pkdd/GutmannKKR08}, and two encodings based on sentential
-decision diagrams \cite{DBLP:conf/ijcai/Darwiche11}, one of which encodes the
-entire program (SDDX), while the other one encodes only the part of the program
+\cite{DBLP:conf/ijcai/RaedtKT07}, and two encodings based on sentential decision
+diagrams \cite{DBLP:conf/ijcai/Darwiche11}, one of which encodes the entire
+program (SDDX), while the other one encodes only the part of the program
 relevant to the query (SDD).\footnote{Forward SDDs (FSDDs) and forward BDDs
-  (FBDDs)
-  \cite{DBLP:journals/corr/abs-1911-07750,DBLP:conf/ijcai/VlasselaerBKMR15} are
-  omitted because the former uses too much memory and the implementation of the
-  latter seems to be broken at the time of writing.}
-
-Out of over \num{11000} generated problem instances, about \SI{35}{\percent} were
+  (FBDDs) \cite{DBLP:conf/aaai/TsamouraGK20,DBLP:conf/ijcai/VlasselaerBKMR15}
+  are omitted because the former uses too much memory and the implementation of
+  the latter seems to be broken at the time of writing.}
+
+Out of \num{11310} generated problem instances, about \SI{35}{\percent} were
 discarded because one or more algorithms were not able to ground the instance
@@
 reasonably efficient and supports additional constraints such as predicate
-independence. The advantages of this approach lie in customisability and speed,
-although the main disadvantage is that there are no guarantees about the
-underlying probability distribution from which programs are sampled.
-
-As a side note, our model treats logically equivalent but syntactically
-different formulas as different. This is so in part because designing a
-constraint for logical equivalence fell outside the scope of this work and in
-part because in some situations one might want to enumerate all ways to express
-the same probability distribution or knowledge base, e.g., to investigate
-whether inference algorithms are robust to changes in representation.
-
-Finally, our experimental results provide the first comparison of inference
+independence. Our experimental results provide the first comparison of inference
 algorithms for probabilistic logic programming languages that generalises over
@@
 they did reveal a shared weakness, i.e., the inability to ignore the part of a
-program that is easily seen to be irrelevant to the given query. We hope that
-our work can facilitate the development of inference (as well as learning)
-algorithms and provide a better understanding of the strengths and weaknesses of
-current approaches.
-
-%\subsubsection*{Acknowledgments.}
-%This work was supported by the EPSRC Centre for Doctoral Training in Robotics
-%and Autonomous Systems, funded by the UK Engineering and Physical Sciences
-%Research Council (grant EP/S023208/1).
-
-% ==============================================================================
-%                                   NOTES
-% ==============================================================================
-
-% Empirical tasks:
-% 1) make the CP model faster: apply the redundant constraints to predicates
-% (not just variables). Check if everything works out.
-% 2) compare to parameter learning with ProbFOIL
-% 3) create a constraint for groundedness (see the ProbLog FAQ)
-% New things I could talk about:
-% 1) entailment for conditional independence
-% 2) the 'required formula' part of the model
-% 3) how linear models can predict inference time
-
-% Notes on papers that test ProbLog inference algorithms:
-% - On the Implementation: published, one biological network
-% -(removed) Nesting Probabilistic Inference: NOT published, one Alzheimer
-% network
-% -(removed) DNF Sampling: NOT published, two networks: a family tree and the
-% Alzheimer network
-% -ProbLog Technology: published, two networks: a custom theory with randomly
-% generated data, and citation data
-% -Anytime Inference: published, four networks: the Smokers social network,
-% Alzheimer data, biological network of genetic data, data about the world wide
-% web
-
-%Interestingly, in the [???] of
-%probabilistic logic programming, random logic program generators can be useful
-%in combination with methods that generate random data with probabilistic logic
-%programs \cite{DBLP:conf/soict/Dries15} and can be used as a component of
-%learning.
-
-%\cref{fig:phase_transition} takes the data for $|\predicates{}| = 8$ (almost
-%\num{300000} observations) and shows how the number of nodes in the search tree
-%varies with the number of independent pairs of predicates. The box plots show
-%that the median number of nodes stays about the same while the dots
-%(representing the means) draw an arc. This suggests a type of phase transition,
-%but only in mean rather than median, i.e., most problems remain easy, but with
-%some parameter values hard problems become more likely. On the one hand, with
-%few pairs of independent predicates, one can easily find the right combination
-%of predicates to use in each clause. On the other hand, if most predicates must
-%be independent, this leaves fewer predicates that can be used in the body of
-%each clause (since all of them have to be independent with the head predicate),
-%and we can either quickly find a solution or identify that there is none.
-
-%\begin{figure*}
-%  \centering
-%  \input{phase_transition.tex}
-%  \caption{The distribution of the number of nodes in the binary search tree as
-%    a function of the number of independent pairs of predicates for
-%    $|\predicates{}| = 8$. Outliers are hidden, the dots denote mean values, and
-%    the vertical axis is on a $\log_{10}$ scale.}
-%  \label{fig:phase_transition}
-%\end{figure*}
-
-%\begin{figure}[t]
-%  \centering
-%  \begin{tikzpicture}
-%    \node[draw,circle,gray,text=black] (or) at (-0.375, 0) {$\lor$};
-%    \node[draw,circle,gray,text=black] (not) at (-1.5, -1) {$\neg$};
-%    \node[draw,circle,gray,text=black] (and) at (0.75, -1) {$\land$};
-%    \node[draw,gray,text=black] (P) at (-1.5, -2) {$\mathsf{P}(X)$};
-%    \node[draw,gray,text=black] (Q) at (0, -2) {$\mathsf{Q}(X)$};
-%    \node[draw,gray,text=black] (R) at (1.5, -2) {$\mathsf{P}(X)$};
-%    \draw[gray] (or) -- (not);
-%    \draw[gray] (or) -- (and);
-%    \draw[gray] (not) -- (P);
-%    \draw[gray] (and) -- (Q);
-%    \draw[gray] (and) -- (R);
-%  \end{tikzpicture}
-%  \caption{A tree representation of the formula from \cref{example:formula}}
-%  \label{fig:example_tree}
-%\end{figure}
-
-% Extra notes.
-% 1. Randomness. The value heuristic is random because we want randomness. After
-% finding one solution, one can continue the search for more, but they will be
-% similar (acceptable if the search space is small and we want to find all
-% solutions).
-% 2. Logic programs don't have disjunctions and parentheses. Is there an easy
-% way to eliminate them?
-% 3. We can do the same thing for predicates within the body of a clause that we
-% do with variables, i.e., predicates within a clause are permutable (except for
-% the head predicate), so we can have a set of 'allowed' predicates.
-% 4. One example of a clear bias exhibited by our model is that of complexity
-% over simplicity, i.e., if a tree that represents the body of a clause can have
-% up to $\maxNumNodes{}$ nodes---because the number of possible trees with $n$
-% nodes grows with $n$---it is much more likely to have $\maxNumNodes{}$ or
-% $\maxNumNodes{} - 1$ nodes than, e.g., one or two.
-% 5. It can easily be shown that all generated logic programs are satisfiable
-
-% \section{Entailment Checking of Negative Cycles} \label{sec:cycles}
-
-% Ideally, we would like to design a constraint for negative cycles similar to the
-% constraint for independence in the previous section. However, the difficulty
-% with creating a propagation algorithm for negative cycles is that there seems to
-% be no good way to extend \cref{def:adjacency_matrix} so that the adjacency
-% matrix captures positivity/negativity. Thus, we settle for an entailment
-% algorithm with no propagation.
-
-%\begin{algorithm}
-%  \KwData{a program $\mathscr{P}$}
-%  \SetKwFunction{hasNegativeCycles}{hasNegativeCycles}
-%  Let $\mathscr{R} \subseteq \mathscr{P}$ be the largest subprogram of
-%  $\mathscr{P}$ with its $\variable{structure}$ and predicates in both body
-%  and head fully determined\footnotemark\;
-%  \lIf{\hasNegativeCycles($G_{\mathscr{R}}$)}{\Return{\textsc{false}}}
-%  \leIf{$\mathscr{R} = \mathscr{P}$}{\Return{\textsc{true}}}{\Return{\textsc{undefined}}}
-%  \caption{Entailment for negative cycles}
-%  \label{alg:negative_cycles}
-%\end{algorithm}
-%\footnotetext{Variables and constants are irrelevant to our definition of
-%  independence.}
-
-% The algorithm takes all clauses whose structure and predicates have been fully
-% determined and uses them to construct a full dependency graph. In our
-% implementation, \texttt{hasNegativeCycles} function is just a simple extension
-% of the backtracking cycle detection algorithm that `travels' around the graph
-% following edges and checking if each vertex has already been visited or not.
-% Alternatively, one could assign weights to the edges (e.g., $1$ for positive
-% and $-\infty$ for negative edges), thus reducing our negative cycle detection
-% problem to what is typically known as the negative cycle detection problem in
-% the literature, and use an algorithm such as Bellman-Ford
-% \cite{shimbel1954structure}.
-
-% If the algorithm finds a negative cycle in this fully-determined part of the
-% program, then we must return \textsc{false}. If there was no negative cycle and
-% the entire program is (sufficiently) determined, then there cannot be any
-% negative cycles. In all other cases, it is too early to tell.
-
-%    \begin{tikzpicture}
-%      \node[draw,circle,gray,text=black] (and) at (0, 0) {$\land$};
-%      \node[draw,circle,gray,text=black] (not) at (1.5, -1) {$\neg$};
-%      \node[draw,gray,text=black] (parent) at (-1.5, -1) {$\mathsf{parent}(X, Y)$};
-%      \node[draw,gray,text=black] (mother) at (1.5, -2) {$\mathsf{mother}(X, Y)$};
-%      \draw[gray] (and) -- (parent);
-%      \draw[gray] (and) -- (not);
-%      \draw[gray] (not) -- (mother);
-%    \end{tikzpicture}%
-%    \captionof{figure}{A tree representation of the body of \eqref{eq:example_clause}}
-%    \label{fig:example_tree2}
-
-% We checked that our model agrees with the derived combinatorial formula in up
-% to a thousand different scenarios. The details of this empirical investigation
-% are omitted as they are not crucial to the thrust of this paper.
+program that is easily seen to be irrelevant to the given query.
+
+Nonetheless, we would like to outline two directions for future work. First, the
+experimental evaluation in \cref{sec:experiment1} revealed scalability issues,
+particularly concerning the length/complexity of clauses. However, this
+particular issue is likely to resolve itself if the format of a clause is
+restricted to a conjunction of literals. Second, random instance generation
+typically focuses on either realistic instances or sampling from a simple and
+well-defined probability distribution. Our approach can be used to achieve the
+former, but the latter remains an open problem (at least in its full
+generality).
+
+\subsubsection*{Acknowledgments.}
+This work was supported by the EPSRC Centre for Doctoral Training in Robotics
+and Autonomous Systems, funded by the UK Engineering and Physical Sciences
+Research Council (grant EP/S023208/1).
 

### 2020-07-12 scripts/analyse_problog.R

@@ -28,6 +28,7 @@ pretty_names <- c("Predicates", "Variables",
 
 prepare.csv <- function(filename) {
   df <- read.csv(filename, header = TRUE, sep = ",")
+  print(nrow(df))
   print(mean(is.na(df$answer)))
   df <- df[!is.na(df$answer),]
   df$proportion.listed <- df$number.of.facts / df$universe.size

### 2020-07-22 paper/paper.tex
New page
Move things around

--- 2020-02-13 paper/paper.tex
@@
 \usepackage{blkarray}
-\usepackage{siunitx}
-\usepackage{amsthm}
-\usepackage[round]{natbib}
-\usepackage[inline]{enumitem}
-
-\newtheorem{constraint}{Constraint}
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
-\newtheorem{example}{Example}
+\usepackage[binary-units]{siunitx}
+\usepackage[inline,shortlabels]{enumitem}
+\usepackage{capt-of}
+\usepackage[caption=false]{subfig}
+\usepackage{booktabs}
+\usepackage[misc,geometry]{ifsym}
+
+\usetikzlibrary{arrows.meta}
+\captionsetup[subfigure]{width=\linewidth}
+\spnewtheorem{constraint}{Constraint}{\bfseries}{\itshape}
 
 \renewcommand\fbox{\fcolorbox{red}{white}}
-
-\makeatletter
-\newcommand{\nosemic}{\renewcommand{\@endalgocfline}{\relax}}% Drop semi-colon ;
-\newcommand{\dosemic}{\renewcommand{\@endalgocfline}{\algocf@endline}}% Reinstate semi-colon ;
-\newcommand{\pushline}{\Indp}% Indent
-\newcommand{\popline}{\Indm\dosemic}% Undent
-\makeatother
+\newcommand{\hilight}[1]{\setlength{\fboxsep}{1pt}\colorbox{lightgray}{#1}}
 
@@
 \Crefname{constraint}{Constraint}{Constraints}
-\Crefname{clause}{Clause}{Clauses}
-\creflabelformat{clause}{#2(#1)#3}
-
-\usetikzlibrary{arrows.meta}
-\relpenalty=10000
-\binoppenalty=10000
-\def\multiset#1#2{\ensuremath{\left(\kern-.3em\left(\genfrac{}{}{0pt}{}{#1}{#2}\right)\kern-.3em\right)}}
+\crefname{section}{Sect.}{Sects.}
+
+\begin{document}
 
 \title{Generating Random Logic Programs Using Constraint Programming}
-
-\author{}
-
-%\author{ {\bf Paulius Dilkas} \\
-%School of Informatics \\
-%University of Edinburgh \\
-%Edinburgh, United Kingdom \\
-%}
-
-\begin{document}
-\bibliographystyle{plainnat}
+\author{Paulius Dilkas\inst{1} \and Vaishak Belle\inst{1,2}$^{(\textrm{\Letter})}$}
+\authorrunning{P. Dilkas and V. Belle}
+\institute{University of Edinburgh, Edinburgh, UK
+  \email{\{p.dilkas@sms.,vaishak@\}ed.ac.uk} \and Alan Turing Institute, London,
+  UK}
+
 \maketitle
@@
 \begin{abstract}
-  We present a novel approach to generating random logic programs and
-  random probabilistic logic programs using constraint programming. The
-  generated programs are useful in empirical testing of inference algorithms,
-  random data generation, and program learning. This approach has a major
-  advantage in that one can easily add additional conditions for the generated
-  programs. As an example of this, we introduce a new constraint for predicate
-  independence with efficient propagation and entailment algorithms, allowing
-  one to generate programs that have a certain independence structure. In order
-  to generate valid probabilistic logic programs, we also present a new
-  constraint for negative cycle detection. Finally, we provide a combinatorial
-  argument for correctness and describe how the parameters of the model affect
-  the empirical difficulty of the program generation task.
+  Testing algorithms across a wide range of problem instances is crucial to
+  ensure the validity of any claim about one algorithm's superiority over
+  another. However, when it comes to inference algorithms for probabilistic
+  logic programs, experimental evaluations are limited to only a few programs.
+  Existing methods to generate random logic programs are limited to
+  propositional programs and often impose stringent syntactic restrictions. We
+  present a novel approach to generating random logic programs and random
+  probabilistic logic programs using constraint programming, introducing a new
+  constraint to control the independence structure of the underlying probability
+  distribution. We also provide a combinatorial argument for the correctness of
+  the model, show how the model scales with parameter values, and use the model
+  to compare probabilistic inference algorithms across a range of synthetic
+  problems. Our model allows inference algorithm developers to evaluate and
+  compare the algorithms across a wide range of instances, providing a detailed
+  picture of their (comparative) strengths and weaknesses.
+
+  \keywords{Constraint programming \and Probabilistic logic programming \and
+    Statistical relational learning}
 \end{abstract}
 
-\section{INTRODUCTION}
-
-How confidently can we claim that an algorithm works well if it is only tested
-on a few types of problems? Perhaps the `inferior' algorithm is actually
-better in some specific circumstances. Maybe there are identifiable
-types of inputs that make every algorithm default to exponential behaviour
-that could be easily overcome with the right strategy. At present, most
-inference algorithms for probabilistic logic programs are only evaluated on at
-most four different problems: sometimes just a single network
-\citep{DBLP:journals/tplp/KimmigDRCR11,DBLP:journals/corr/abs-1112-3785},
-sometimes two
-\citep{DBLP:journals/corr/abs-1009-3798,DBLP:conf/ecai/BruynoogheMKGVJR10} or
-four networks \citep{DBLP:conf/ijcai/VlasselaerBKMR15}, all coming from a range
-of areas such as social networks and citation/genetic/biological data sets. To
-better understand the strengths and weaknesses of these algorithms, along with
-real data they should also be evaluated on a range of synthetic problems that
-accurately represent the potential complexities that have to be handled by a
-well-designed inference algorithm. Furthermore, random logic program generators
-can be useful in combination with methods that generate random data with
-probabilistic logic programs \citep{DBLP:conf/soict/Dries15} and can be used as
-a component of learning.
-
-Most current approaches to generating random logic programs are restrictive,
-e.g., limited to clauses with only two literals
-\citep{DBLP:conf/lpnmr/NamasivayamT09}, or to clauses of the form $a \gets \neg
-b$ \citep{DBLP:journals/tocl/WenWSL16}, but others are more expressive, e.g.,
-defining a program only by the (maximum) number of atoms in the body and the
-total number of rules \citep{DBLP:conf/iclp/ZhaoL03}. We introduce a way to
-generate random logic programs using a constraint model. The same model can
-generate both probabilistic programs directly in the syntax of ProbLog
-\citep{DBLP:conf/ijcai/RaedtKT07} as well as non-probabilistic Prolog programs.
-For generated probabilistic programs to be valid, we use a custom constraint to
-detect negative cycles (as described in \cref{sec:cycles}). A major advantage of
-our constraint-based approach is that one can easily add additional constraints
-to the model. To demonstrate that, in \cref{sec:independence} we present a
-custom constraint with propagation and entailment algorithms that can ensure
-predicate independence. \cref{sec:counting} also presents a combinatorial
-argument for correctness, where we produce combinatorial expressions that count
-the number of programs that the model should produce for various parameter
-values. Finally, \cref{sec:experiments} shows how the model scales when tasked
-with producing more complicated programs and identifies the relationships
-between parameter values and the empirical hardness of the program generation
-task.
-
-Overall, our main contributions are concerned purely with logic programming-based
-languages and frameworks, which capture a major fragment of statistical
-relational learning \citep{DBLP:series/synthesis/2016Raedt}.
-However, since probabilistic logic programming languages are closely related
-to other areas of machine learning, including (imperative) probabilistic
-programming \citep{DBLP:journals/ml/RaedtK15}, our results can lay the
-foundations for exploring broader questions on generating and testing
-programs/algorithms in machine learning.
-
-\section{PRELIMINARIES}
+\section{Introduction}
+
+Unifying logic and probability is a long-standing challenge in artificial
+intelligence \cite{DBLP:journals/cacm/Russell15}, and, in that regard,
+statistical relational learning (SRL) has developed into an exciting area that
+mixes machine learning and symbolic (logical and relational) structures. In
+particular, probabilistic logic programs---including languages such as
+\textsc{PRISM} \cite{DBLP:conf/ijcai/SatoK97}, \textsc{ICL}
+\cite{DBLP:journals/ai/Poole97}, and \textsc{ProbLog}
+\cite{DBLP:conf/ijcai/RaedtKT07}---are promising frameworks for codifying
+complex SRL models. With the enhanced structure, however, inference becomes more
+challenging. At the moment, we have no precise way of evaluating and comparing
+inference algorithms. Incidentally, if one were to survey the literature, one
+often finds that an inference algorithm is only tested on a small number (1--4)
+of data sets
+\cite{DBLP:conf/ecai/BruynoogheMKGVJR10,DBLP:journals/tplp/KimmigDRCR11,DBLP:conf/ijcai/VlasselaerBKMR15},
+originating from areas such as social networks, citation patterns, and
+biological data. But how confident can we be that an algorithm works well if it
+is only tested on a few problems?
+
+About thirty years ago, SAT solving technology was dealing with a similar lack
+of clarity \cite{DBLP:journals/ai/SelmanML96}. This changed with the study of
+generating random SAT instances against different input parameters (e.g.,
+clause length and the total number of variables) to better understand the
+behaviour of algorithms and their ability to solve random synthetic problems.
+Unfortunately, when it comes to generating random logic programs, all approaches
+so far focused exclusively on propositional programs
+\cite{DBLP:conf/ijcai/AmendolaRT17,DBLP:journals/ai/AmendolaRT20,DBLP:journals/tplp/WangWM15,DBLP:conf/iclp/ZhaoL03},
+often with severely limiting conditions such as two-literal clauses
+\cite{DBLP:conf/iclp/Namasivayam09,DBLP:conf/lpnmr/NamasivayamT09} or clauses of
+the form $a \gets \neg b$ \cite{DBLP:journals/tocl/WenWSL16}.
+
+In this work (\cref{sec:heads,sec:bodies,sec:variable_symmetry}), we introduce a
+constraint-based representation for logic programs based on simple parameters
+that describe the program's size, what predicates and constants it uses, etc.
+This representation takes the form of a \emph{constraint satisfaction problem}
+(CSP), i.e., a set of discrete variables and restrictions on what values they
+can take. Every solution to this problem (as output by a constraint solver)
+directly translates into a logic program. One can either output all
+(sufficiently small) programs that satisfy the given conditions or use random
+value-ordering heuristics and restarts to generate random programs. For sampling
+from a uniform distribution, the CSP can be transformed into a belief network
+\cite{DBLP:conf/aaai/DechterKBE02}. In fact, the same model can generate both
+probabilistic programs in the syntax of \textsc{ProbLog}
+\cite{DBLP:conf/ijcai/RaedtKT07} and non-probabilistic \textsc{Prolog} programs.
+To the best of our knowledge, this is the first work that
+\begin{enumerate*}[(a)]
+\item addresses the problem of generating random logic programs in its full
+  generality (i.e., including first-order clauses with variables), and
+\item compares and evaluates inference algorithms for probabilistic logic
+  programs on more than a handful of instances.
+\end{enumerate*}
+
+A major advantage of a constraint-based approach is the ability to add
+additional constraints as needed, and to do that efficiently (compared to
+generate-and-test approaches). As an example of this, in \cref{sec:independence}
+we develop a custom constraint that, given two predicates $\mathsf{P}$ and
+$\mathsf{Q}$, ensures that any ground atom with predicate $\mathsf{P}$ is
+independent of any ground atom with predicate $\mathsf{Q}$. In this way, we can
+easily regulate the independence structure of the underlying probability
+distribution. In \cref{sec:counting} we also present a combinatorial argument
+for correctness that counts the number of programs that the model produces for
+various parameter values. We end the paper with two experimental results in
+\cref{sec:experiments}: one investigating how the constraint model scales when
+tasked with producing more complex programs, and one showing how the model can
+be used to evaluate and compare probabilistic inference algorithms.
+
+Overall, our main contributions are concerned with logic programming-based
+languages and frameworks, which capture a major fragment of SRL
+\cite{DBLP:series/synthesis/2016Raedt}. However, since probabilistic logic
+programming languages are closely related to other areas of machine learning,
+including (imperative) probabilistic programming
+\cite{DBLP:journals/ml/RaedtK15}, our results can lay the foundations for
+exploring broader questions on generating models and testing algorithms in
+machine learning.
+
+\section{Preliminaries}
 
 The basic primitives of logic programs are \emph{constants}, \emph{(logic)
-  variables}, and \emph{predicates}. Each predicate has an \emph{arity} that
-defines the number of terms that it can applied to. A \emph{term} is either a
-variable or a constant, and an \emph{atom} is a predicate of arity $n$ applied
-to $n$ terms. A \emph{formula} is a grammatically-valid expression that connects
-atoms using conjunction ($\land$), disjunction ($\lor$), and negation ($\neg$).
-A \emph{clause} is a pair of a \emph{head} (which is an atom) and a \emph{body}
-(which is a formula). A \emph{(logic) program} is a multiset of clauses. Given a
-program $\mathscr{P}$, a \emph{subprogram} $\mathscr{R}$ of $\mathscr{P}$ is a
-subset of the clauses of $\mathscr{P}$ and is denoted by $\mathscr{R} \subseteq
-\mathscr{P}$.
-
-In the world of constraint satisfaction, we also have \emph{(constraint)
-  variables}, each with its own \emph{domain}, whose values are restricted using
-\emph{constraints}. All constraint variables in the model are integer or set
-variables, however, if an integer refers to a logical construct
-(e.g., a logical variable or a constant), we will make no distinction between
-the two and often use names of logical constructs to refer to the underlying
-integers. We say that a constraint variable is \emph{(fully) determined} if its
-domain (at the given moment in the execution) has exactly one value. We will
-often use $\Box$ as a special domain value to indicate a `disabled' (i.e., fixed
-and ignored) part of the model. We write $\arrayd{a}{b}{c}$ to mean that
+  variables}, and \emph{predicates} with their \emph{arities}. A \emph{term} is
+either a variable or a constant, and an \emph{atom} is a predicate of arity $n$
+applied to $n$ terms. A \emph{formula} is any well-formed expression that
+connects atoms using conjunction $\land$, disjunction $\lor$, and negation
+$\neg$. A \emph{clause} is a pair of a \emph{head} (which is an atom) and a
+\emph{body} (which is a formula\footnote{Our model supports arbitrarily complex
+  bodies of clauses (e.g., $\neg\mathsf{P}(X) \lor (\mathsf{Q}(X) \land
+  \mathsf{P}(X))$) because \textsc{ProbLog} does too. However, one can easily
+  restrict our representation of a body to a single conjunction of literals
+  (e.g., $\mathsf{Q}(X) \land \neg\mathsf{P}(X))$) by adding a couple of
+  additional constraints.}). A \emph{(logic) program} is a set of clauses, and a
+\emph{\textsc{ProbLog} program} is a set of clause-probability pairs
+\cite{DBLP:journals/tplp/FierensBRSGTJR15}.
+
+In the world of CSPs, we also have \emph{(constraint) variables}, each with a
+\emph{domain}, whose values are restricted using \emph{constraints}. All
+constraint variables in the model are integer or set variables, however, if an
+integer refers to a logical construct (e.g., a logical variable or a constant),
+we will make no distinction between the two. We say that a constraint variable
+is \emph{(fully) determined} if its domain (at the time) has exactly one value.
+We let $\Box$ denote the absent/disabled value of an optional variable
+\cite{DBLP:conf/cpaior/MearsSSTMW14}. We write $\arrayd{a}{b}{c}$ to mean that
 $\variable{a}$ is an array of variables of length $b$ such that each element of
@@
 
-\subsection{PARAMETERS OF THE MODEL}
-
-We begin defining the parameters of our model by initialising sets and lists
-of the primitives used in constructing logic programs: a list of predicates
+\paragraph{Parameters of the model.} We begin by defining sets and lists of the
+primitives used in constructing logic programs: a list of predicates
 $\predicates{}$, a list of their corresponding arities $\arities{}$ (so
@@
 model supports zero-arity predicates but requires at least one predicate to have
-non-zero arity. For notational convenience, we also set $\maxArity{} \coloneqq
-\max \arities{}$.
-
-We also define a measure of how complicated a body of a clause can become. As
-each body is represented by a tree (see \cref{sec:bodies}), we set
+non-zero arity. For notational convenience, we also set $\maxArity{} = \max
+\arities{}$. Next, we need a measure of how complex a body of a clause can be.
+As we represent each body by a tree (see \cref{sec:bodies}), we set
 $\maxNumNodes{} \ge 1$ to be the maximum number of nodes in the tree
@@
 |\predicates{}|$ because we require each predicate to have at least one clause
-that defines it. The model supports eliminating either all cycles or just
-negative cycles (see \cref{sec:cycles}) and enforcing predicate independence
-(see \cref{sec:independence}), so a set of independent pairs of predicates is
-another parameter. Since this model can generate probabilistic as well as
+that defines it. The model supports enforcing predicate independence (see
+\cref{sec:independence}), so a set of independent pairs of predicates is another
+parameter. Since this model can generate probabilistic as well as
 non-probabilistic programs, each clause is paired with a probability which is
-randomly selected from a given multiset (i.e., our last parameter). For
-generating non-probabilistic programs, one can set this list equal to $\{ 1 \}$.
-Finally, we define $\tokens{} = \{ \neg, \land, \lor, \top \}$ as the set of
-tokens that (together with atoms) form a clause. All decision variables of the
-model can now be divided into $2 \times \maxNumClauses{}$ separate groups,
-treating the body and the head of each clause separately. We say that the
-variables are contained in two arrays: $\arrayt{bodies}{\maxNumClauses{}}{Body}$
-and $\arrayt{heads}{\maxNumClauses{}}{Head}$. Since the order of the clauses
-does not change the meaning of the program, we can also state our first
-constraint:
-
+randomly selected from a given list---our last parameter. For generating
+non-probabilistic programs, one can set this list to $[1]$. Finally, we define
+$\tokens{} = \{ \neg, \land, \lor, \top \}$ as the set of tokens that (together
+with atoms) form a clause. All decision variables of the model can now be
+divided into $2 \times \maxNumClauses{}$ separate groups, treating the body and
+the head of each clause separately. We say that the variables are contained in
+two arrays: $\arrayt{bodies}{\maxNumClauses{}}{Body}$ and
+$\arrayt{heads}{\maxNumClauses{}}{Head}$.
+
+\section{Heads of Clauses} \label{sec:heads}
+
+We define the \emph{head} of a clause as a $\variable{predicate} \in \predicates{}
+\cup \{ \Box \}$ and $\arrayd{arguments}{\maxArity{}}{\constants{} \cup
+  \variables{}} \cup \{ \Box \}$. Here, we use $\Box$ to denote either a
+disabled clause that we choose not to use or disabled arguments if the arity of
+the $\variable{predicate}$ is less than $\maxArity{}$. The reason why we need a
+separate value for the latter (i.e., why it is not enough to fix disabled
+arguments to a single already-existing value) will become clear in
+\cref{sec:variable_symmetry}. This $\variable{predicate}$ variable has a
+corresponding arity that depends on the $\variable{predicate}$. We can
+define $\variable{arity} \in [0, \maxArity{}]$ as the arity of the
+$\variable{predicate}$ if $\variable{predicate} \in \predicates{}$ and zero
+otherwise using the table constraint \cite{DBLP:conf/cpaior/MairyDL15}. This
+constraint uses a set of pairs of the form $(p, a)$, where $p$ ranges over all
+possible values of the $\variable{predicate}$, and $a$ is either the arity of
+predicate $p$ or zero. Having defined arity, we can now fix the superfluous
+arguments.
+\begin{constraint} \label{constr:arity}
+  For $i = 0, \dots, \maxArity{} - 1$, $\variable{arguments}[i] = \Box \iff i
+  \ge \variable{arity}$.
+\end{constraint}
+We also add a constraint that each predicate should get at least one clause.
 \begin{constraint}
-  Clauses are sorted.
+  Let $P = \{ h.\variable{predicate} \mid h \in \variable{heads} \}$ be a
+  multiset. Then
+  \[
+    \variable{nValues}(P) = \begin{cases}
+      |\predicates{}| & \text{if } \variable{count}(\Box, P) = 0 \\
+      |\predicates{}| + 1 & \text{otherwise,}
+    \end{cases}
+  \]
+  where $\variable{nValues}(P)$ counts the number of unique values in $P$, and
+  $\variable{count}(\Box, P)$ counts how many times $\Box$ appears in $P$.
 \end{constraint}
-
-Here and henceforth, the exact ordering is immaterial: we only impose an order
-to eliminate permutation symmetries.
-
-\section{HEADS OF CLAUSES} \label{sec:heads}
-
-\begin{definition}
-  The \emph{head} of a clause is composed of a $\variable{predicate} \in
-  \predicates \cup \{ \Box \}$, and
-  $\arrayd{arguments}{\maxArity{}}{\constants{} \cup \variables{}} \cup \{ \Box
-  \}$.
-\end{definition}
-
-Here, we use $\Box$ to denote either a disabled clause that we choose not to use
-or disabled arguments if the arity of the $\variable{predicate}$ is less than
-$\maxArity{}$. The reason why we need a separate value for the latter (i.e., why
-it is not enough to fix disabled arguments to a single already-existing value)
-will become clear in \cref{sec:variable_symmetry}.
-
-\begin{definition} \label{def:arity}
-  The \variable{predicate}'s $\variable{arity} \in [0, \maxArity{}]$ can then be
-  defined using the \variable{table} constraint as the arity of the
-  $\variable{predicate}$ if $\variable{predicate} \in \predicates{}$, and zero
-  otherwise.
-\end{definition}
-
-Having defined arity, we can now fix the superfluous arguments:
-
-\begin{constraint} \label{constr:arity}
-  For $i = 0, \dots, \maxArity{} - 1$,
-  \[
-    \variable{arguments}[i] = \Box \iff i \ge \variable{arity}.
+Finally, we want to disable duplicate clauses but with one exception: there may
+be more than one disabled clause, i.e., a clause with head $\variable{predicate}
+= \Box$. Assuming a lexicographic order over entire clauses such that $\Box >
+\mathsf{P}$ for all $\mathsf{P} \in \predicates{}$ and the head predicate is the
+`first digit' of this representation, the following constraint disables
+duplicates as well as orders the clauses.
+\begin{constraint}
+  For $i = 1, \dots, \maxNumClauses{} - 1$, if $\variable{heads}[i].\variable{predicate}
+  \ne \Box$, then
+  \[
+    (\variable{heads}[i-1], \variable{bodies}[i-1]) < (\variable{heads}[i],
+    \variable{bodies}[i]).
   \]
@@
 
-We can also add a constraint that each predicate $\mathsf{P} \in \predicates{}$
-should have at least one clause with $\mathsf{P}$ at its head:
-
-\begin{constraint}
-Let
-  \[
-    P = \{ h.\variable{predicate} \mid h \in \variable{heads} \}.
-  \]
-  Then
-  \[
-    \variable{nValues}(P) =
-    \begin{cases}
-      |\predicates{}| + 1 & \text{if } \variable{count}(\Box, P) > 0 \\
-      |\predicates{}| & \text{otherwise.}
-    \end{cases}
-  \]
-\end{constraint}
-
-Here, $\variable{nValues}(P)$ counts the number of unique values in $P$.
-
-\section{BODIES OF CLAUSES} \label{sec:bodies}
-
-As was briefly mentioned before, the body of a clause is represented by a tree.
-
-\begin{definition}
-  The \emph{body} of a clause has two parts. First, we have the
-  $\arrayd{structure}{\maxNumNodes{}}{[0, \maxNumNodes{} - 1]}$ array that
-  encodes the structure of the tree using the following two rules:
-  $\variable{structure}[i] = i$ means that the $i$-th node is a root, and
-  $\variable{structure}[i] = j$ (for $j \ne i$) means that the $i$-th node's
+\section{Bodies of Clauses} \label{sec:bodies}
+
+As was briefly mentioned before, the \emph{body} of a clause is represented by a
+tree. It has two parts. First, there is the
+$\arrayd{structure}{\maxNumNodes{}}{[0, \maxNumNodes{} - 1]}$ array that encodes
+the structure of the tree using the following two rules:
+$\variable{structure}[i] = i$ means that the $i$th node is a root, and
+$\variable{structure}[i] = j$ (for $j \ne i$) means that the $i$th node's
 parent is node $j$. The second part is the array
 $\arrayt{values}{\maxNumNodes{}}{Node}$ such that $\variable{values}[i]$ holds
-  the value of the $i$-th node.
-\end{definition}
-
-We can use the $\variable{tree}$ constraint \citep{DBLP:conf/cp/FagesL11} to
+the value of the $i$th node, i.e., a representation of the atom or logical
+operator.
+
+We can use the $\variable{tree}$ constraint \cite{DBLP:conf/cp/FagesL11} to
 forbid cycles in the $\variable{structure}$ array and simultaneously define
@@
 restrict all other trees to single nodes. For this to work, we need to make sure
-that the zeroth node is indeed a root:
-
-\begin{constraint}
-  $\variable{structure}[0] = 0$.
-\end{constraint}
-
-\begin{definition}
+that the zeroth node is indeed a root, i.e., fix $\variable{structure}[0] = 0$.
 For convenience, we also define $\variable{numNodes} \in \{ 1, \dots,
 \maxNumNodes{} \}$ to count the number of nodes in the main tree. We define it
-  as
-  \[
-    \variable{numNodes} = \maxNumNodes{} - \variable{numTrees} + 1.
-  \]
-\end{definition}
-
-\begin{figure}
-  \centering
-  \begin{tikzpicture}
-    \node[draw,circle,gray,text=black] (or) at (-0.375, 0) {$\lor$};
-    \node[draw,circle,gray,text=black] (not) at (-1.5, -1) {$\neg$};
-    \node[draw,circle,gray,text=black] (and) at (0.75, -1) {$\land$};
-    \node[draw,gray,text=black] (P) at (-1.5, -2) {$\mathsf{P}(X)$};
-    \node[draw,gray,text=black] (Q) at (0, -2) {$\mathsf{Q}(X)$};
-    \node[draw,gray,text=black] (R) at (1.5, -2) {$\mathsf{P}(X)$};
-    \draw[gray] (or) -- (not);
-    \draw[gray] (or) -- (and);
-    \draw[gray] (not) -- (P);
-    \draw[gray] (and) -- (Q);
-    \draw[gray] (and) -- (R);
-  \end{tikzpicture}
-  \caption{A tree representation of the formula from \cref{example:formula}}
-  \label{fig:example_tree}
-\end{figure}
+as $\variable{numNodes} = \maxNumNodes{} - \variable{numTrees} + 1$.
 
 \begin{example} \label{example:formula}
-  Let $\maxNumNodes{} = 8$. Then
-  \[
-    \neg\mathsf{P}(X) \lor (\mathsf{Q}(X) \land \mathsf{P}(X))
-  \]
-  corresponds to the tree in \cref{fig:example_tree} and can be encoded as:
-  \begin{alignat*}{8}
-    \variable{structure} &= [0, &&0, &&0, &&1, &&2, &&2, &&6, &&7],\\
-    \variable{values} &= [{\lor}, &&{\neg}, &&{\land}, \mathsf{P}(&&X), \mathsf{Q}(&&X), \mathsf{P}(&&X), &&\top, &&\top],\\
-    \variable{numNodes} &= 6, && && && && && && &&\\
-    \variable{numTrees} &= 3. && && && && && && &&
+  Let $\maxNumNodes{} = 8$. Then $\neg\mathsf{P}(X) \lor (\mathsf{Q}(X) \land
+  \mathsf{P}(X))$ can be encoded as:
+  \begin{alignat*}{9}
+    \variable{structure} &= [0, &&0, &&0, &&1, &&2, &&2, &&6, &&7], \quad
+    &&\variable{numNodes} = 6, \\
+    \variable{values} &= [{\lor}, &&{\neg}, &&{\land}, \mathsf{P}(&&X),
+    \mathsf{Q}(&&X), \mathsf{P}(&&X), &&\top, &&\top], \quad
+    &&\variable{numTrees} = 3.
   \end{alignat*}
@@
 We need to constrain the forest represented by the $\variable{structure}$
-array together with its $\variable{values}$ to eliminate unnecessary symmetries
-and adhere to our desired format. First, we can recognise that the order of the
-elements in the $\variable{structure}$ array does not matter, i.e., the
-structure is only defined by how the elements link to each other, so we can add
-a constraint saying that:
-
+array together with its $\variable{values}$ to eliminate symmetries and adhere
+to our desired format. First, we can recognise that the order of the elements in
+the $\variable{structure}$ array does not matter, i.e., the structure is only
+defined by how the elements link to each other, so we can add a constraint for
+sorting the $\variable{structure}$ array. Next, since we already have a
+variable that counts the number of nodes in the main tree, we can fix the
+structure and the values of the remaining trees to some constant values.
 \begin{constraint}
-  \variable{structure} is sorted.
-\end{constraint}
-
-Next, since we already have a variable that counts the number of nodes in the
-main tree, we can fix the structure and the values of the remaining trees to
-some constant values:
-
-\begin{constraint}
-  For $i = 1, \dots, \maxNumNodes{} - 1$, if $i \ge \variable{numNodes}$, then
+  For $i = 1, \dots, \maxNumNodes{} - 1$, if $i < \variable{numNodes}$, then
   \[
@@
 number of children (zero, one, and two, respectively).
-
 \begin{constraint} \label{constraint:node_types}
   For $i = 0, \dots, \maxNumNodes{} - 1$, let $C_i$ be the number of times $i$
-  appears in the \variable{struture} array with index greater than $i$. Then
+  appears in the \variable{structure} array with index greater than $i$. Then
   \begin{align*}
@@
 \end{constraint}
-
 The value $\top$ serves a twofold purpose: it is used as the fixed value for
 nodes outside the main tree, and, when located at the zeroth node, it can
-represent a clause with no body. Thus, we can say that only root nodes can have
-$\top$ as the value:
-
+represent a clause with an empty body. Thus, we can say that only root nodes can
+have $\top$ as the value.
 \begin{constraint}
@@
 \end{constraint}
-
 Finally, we add a way to disable a clause by setting its head predicate to
-$\Box$:
-
+$\Box$.
 \begin{constraint}
@@
   \[
-    \variable{bodies}[i].\variable{numNodes} = 1,
-  \]
-  and
-  \[
-    \variable{bodies}[i].\variable{values}[0].\variable{name} =
-    \top.
+    \variable{bodies}[i].\variable{numNodes} = 1, \quad \text{and}
+    \quad \variable{bodies}[i].\variable{values}[0].\variable{name} = \top.
   \]
@@
 
-\section{VARIABLE SYMMETRIES} \label{sec:variable_symmetry}
-
-Given any clause, we can permute the variables in that clause without changing
-the meaning of the clause or the entire program. Thus, we want to fix the order
-of variables to eliminate unnecessary symmetries. Informally, we can say that
-variable $X$ goes before variable $Y$ if the first occurrence of $X$ in either
-the head or the body of the clause is before the first occurrence of $Y$. Note
-that the constrains described in this section only make sense if $|\variables| >
-1$. Also note that all definitions and constraints here are on a per-clause
-basis.
-
+\section{Variable Symmetry Breaking} \label{sec:variable_symmetry}
+
+Ideally, we want to avoid generating programs that are equivalent in the sense
+that they produce the same answers to all queries. Even more importantly, we
+want to avoid generating multiple internal representations that ultimately
+result in the same program. This is the purpose of \emph{symmetry-breaking
+  constraints}, another important benefit of which is that the constraint
+solving task becomes easier \cite{DBLP:conf/cp/Walsh06}. Given any clause, we
+can permute the variables in that clause without changing the meaning of the
+clause or the entire program. Thus, we want to fix the order of variables.
+Informally, we can say that variable $X$ goes before variable $Y$ if the first
+occurrence of $X$ in either the head or the body of the clause is before the
+first occurrence of $Y$. Note that the constraints described in this section
+only make sense if $|\variables{}| > 1$ and that all definitions and constraints
+here are on a per-clause basis.
 \begin{definition}
@@
   $\variable{terms}[N] \in \constants{} \cup \variables{} \cup \{ \Box
-  \}$ be a flattened array of all arguments in a particular clause.
-
-  Then we can use a channeling constraint to define
-  $\variable{occ}[|\constants{}| + |\variables{}| + 1]$ as an array of subsets
-  of $\{ 0, \dots, N-1 \}$ such that for all $i = 0, \dots, N - 1$, and $t \in
-  \constants{} \cup \variables{} \cup \{ \Box \}$,
+  \}$ be a flattened array of all arguments in a particular clause. Then we can
+  use a channeling constraint to define $\variable{occ}[|\constants{}| +
+  |\variables{}| + 1]$ as an array of subsets of $\{ 0, \dots, N-1 \}$ such that
+  for all $i = 0, \dots, N - 1$, and $t \in \constants{} \cup \variables{} \cup
+  \{ \Box \}$,
   \[
     i \in \variable{occ}[t] \quad \iff \quad
-    \variable{terms}[i] = t
+    \variable{terms}[i] = t.
   \]
 \end{definition}
-
-Next, we introduce an array that, for each variable, holds the position of its
-first occurrence:
-
+Next, we introduce an array that holds the first occurrence of each variable.
 \begin{definition}
@@
 \end{definition}
-
-Here, a value of zero means that the variable does not occur in the clause. The
-reason why we want to use specifically zero for this will become clear with
-\cref{constraint:diffbutzero}. Because of this choice, the definition of
-$\variable{intros}$ shifts all indices by one. Lastly, we add the constraint
-that eliminates variable symmetries:
-
-\begin{constraint}
-  $\variable{intros}$ are sorted.
-\end{constraint}
-
-In other words, we constrain the model so that the variable listed first in
-whatever order $\variables{}$ is presented in has to occur first in our
-representation of a clause.
+Here, a value of zero means that the variable does not occur in the clause (this
+choice is motivated by subsequent constraints). As a consequence, all other
+indices are shifted by one. Having set this up, we can now eliminate variable
+symmetries simply by sorting $\variable{intros}$. In other words, we constrain
+the model so that the variable listed first (in whatever order $\variables{}$ is
+presented in) has to occur first in our representation of a clause.
 
@@
 
-\subsection{REDUNDANT CONSTRAINTS}
-
-We add a number of redundant constraints to make search more efficient. First,
-we can formally state that the positions occupied by different terms must be
-different:
-
+We end the section with several redundant constraints that make the CSP easier
+to solve. First, we can state that the positions occupied by different terms
+must be different.
 \begin{constraint} \label{constraint:all_diff}
   For $u \ne v \in \constants{} \cup \variables{} \cup \{ \Box \}$,
-  \[
-    \variable{occ}[u] \cap \variable{occ}[v] = \emptyset.
-  \]
+  $\variable{occ}[u] \cap \variable{occ}[v] = \emptyset$.
 \end{constraint}
-
-The reason why we used zero to represent an unused variable is so that we could
-efficiently rephrase \cref{constraint:all_diff} for the $\variable{intros}$
-array:
-
-\begin{constraint} \label{constraint:diffbutzero}
-  $\variable{allDifferentExcept0}(\variable{intros})$.
+The reason why we use zero to represent an unused variable is so that we could
+now use the `all different except zero' constraint for the $\variable{intros}$
+array. We can also add another link between $\variable{intros}$ and
+$\variable{occ}$ that essentially says that the smallest element of a set is an
+element of the set.
+\begin{constraint}
+  For $v \in \variables{}$, $\variable{intros}[v] \ne 0 \iff
+  \variable{intros}[v] - 1 \in \variable{occ}[v]$.
 \end{constraint}
-
-We can also add another link between $\variable{intros}$ and $\variable{occ}$
-that essentially says that the smallest element of a set is an element of the
-set:
-
-\begin{constraint}
-  For $v \in \variables{}$,
-  \[
-    \variable{intros}[v] \ne 0 \quad \iff \quad
-    \variable{intros}[v] - 1 \in \variable{occ}[v].
-  \]
-\end{constraint}
-
 Finally, we define an auxiliary set variable to act as a set of possible values
-that $\variable{intros}$ can take:
-
-\begin{definition}
-  Let $\variable{potentials} \subseteq \{ 0, \dots, N \}$ be such that for $v
-  \in \variables{}$, $\variable{intros}[v] \in \variable{potentials}$.
-\end{definition}
-
-Using this new variable, we can add a constraint saying that non-predicate nodes
-in the tree representation of a clause cannot have variables as arguments:
-
+that $\variable{intros}$ can take. Let $\variable{potentials} \subseteq \{ 0,
+\dots, N \}$ be such that for $v \in \variables{}$, $\variable{intros}[v] \in
+\variable{potentials}$. Using this new variable, we can add a constraint saying
+that non-predicate nodes in the tree representation of a clause cannot have
+variables as arguments.
 \begin{constraint} \label{constraint:potentialIntroductions}
@@
 
-\section{COUNTING PROGRAMS} \label{sec:counting}
-
-In order to demonstrate the correctness of the model and explain it in more
-detail, in this section we are going to derive combinatorial expressions for
-counting the number of programs with up to $\maxNumClauses{}$ clauses and up to
-$\maxNumNodes{}$ nodes per clause, and arbitrary $\predicates{}$,
-$\arities{}$, $\variables{}$, and $\constants{}$\footnote{We checked that the
-  our model agrees with the derived combinatorial formula in close to a thousand
-  different scenarios. The details of this empirical investigation are omitted
-  as they are not crucial to the thrust of this paper.}. To simplify the task,
-we only consider clauses without probabilities and disable (negative) cycle
-elimination. We also introduce the term \emph{total arity} of a body of a clause
-to refer to the sum total of arities of all predicates in the body.
-
-We will first consider clauses with gaps, i.e., without taking variables and
-constants into account. Let $T(n, a)$ denote the number of possible clause
+\section{Counting Programs} \label{sec:counting}
+
+To demonstrate the correctness of the model, this section derives combinatorial
+expressions for counting the number of programs with up to $\maxNumClauses{}$
+clauses and up to $\maxNumNodes{}$ nodes per clause, and arbitrary
+$\predicates{}$, $\arities{}$, $\variables{}$, and $\constants{}$. Being able to
+establish two ways to generate the same sequence of numbers (i.e., numbers of
+programs with certain properties and parameters) allows us to gain confidence
+that the constraint model accurately matches our intentions. For this section,
+we introduce the term \emph{total arity} of a body of a clause to refer to the
+sum total of arities of all predicates in the body.
+
+We will first consider clauses with \emph{gaps}, i.e., without taking variables
+and constants into account. Let $T(n, a)$ denote the number of possible clause
 bodies with $n$ nodes and total arity $a$. Then $T(1, a)$ is the number of
@@
 definition can be applied for $n > 1$:
-\begin{align*}
-  T(n, a) = T(n-1, a) + 2&\sum_{\substack{c_1 + \dots + c_k = n - 1,\\
-      2 \le k \le \frac{a}{\min \arities{}},\\
-  c_i \ge 1 \text{ for all } i}}\\
-  &\sum_{\substack{d_1 + \dots + d_k = a,\\
-  d_i \ge \min \arities{} \text{ for all } i}} \prod_{i=1}^k T(c_i, d_i).
-\end{align*}
+\[
+  T(n, a) = T(n-1, a) + 2\sum_{\substack{c_1 + \dots + c_k = n - 1,\\ 2 \le k
+      \le \frac{a}{\min \arities{}},\\ c_i \ge 1 \text{ for all } i}}
+  \sum_{\substack{d_1 + \dots + d_k = a,\\ d_i \ge \min \arities{} \text{ for
+        all } i}} \prod_{i=1}^k T(c_i, d_i).
+\]
 The first term here represents negation, i.e., negating a formula consumes
 one node but otherwise leaves the task unchanged. If the first operation is not
-negation, then it must be either conjunction or disjunction (hence the
+a negation, then it must be either conjunction or disjunction (hence the
 coefficient `2'). In the first sum, $k$ represents the number of children of the
@@
 \]
-Here, the empty clause is considered separately.
 
 The number of ways to select $n$ terms is
-\begin{align*}
-  P(n) = |\constants{}|^n + &\sum_{\substack{1 \le k \le |\variables{}|, \\ 0 =
-      s_0 < s_1 < \dots < s_k < s_{k+1} = n+1}}\\
-  &\prod_{i=0}^k (|\constants{}| + i)^{s_{i+1} - s_i - 1}.
-\end{align*}
-The first term is the number of ways select $n$ constants. The parameter $k$ is
-the number of variables used in the clause, and $s_1, \dots, s_k$ mark the first
-occurrence of each variable. For each gap between any two introductions (or
-before the first introduction, or after the last introduction), we have
+\[
+  P(n) = |\constants{}|^n + \sum_{\substack{1 \le k \le |\variables{}|, \\ 0 =
+      s_0 < s_1 < \dots < s_k < s_{k+1} = n+1}} \prod_{i=0}^k (|\constants{}| +
+  i)^{s_{i+1} - s_i - 1}.
+\]
+The first term is the number of ways to select $n$ constants. The parameter $k$
+is the number of variables used in the clause, and $s_1, \dots, s_k$ mark the
+first occurrence of each variable. For each gap between any two introductions
+(or before the first introduction, or after the last introduction), we have
 $s_{i+1}-s_i-1$ spaces to be filled with any of the $|\constants{}|$ constants
@@
 Let us order the elements of $\predicates{}$, and let $a_i$ be the arity of the
-$i$-th predicate. The number of programs is then:
-\[
+$i$th predicate. The number of programs is then:
+\begin{equation} \label{eq:counting}
   \sum_{\substack{ \sum_{i=1}^{|\predicates{}|} h_i = n,\\
-      |\predicates{}| \le n \le \maxNumClauses,\\
+      |\predicates{}| \le n \le \maxNumClauses{},\\
       h_i \ge 1 \text{ for all } i}} \prod_{i=1}^{|\predicates{}|}
-  \multiset{\sum_{a=0}^{\maxArity{} \times \maxNumNodes{}} C(a) P(a+a_i)}{h_i},
-\]
-where
-\[
-  \multiset{n}{k} = \binom{n+k-1}{k}
-\]
-counts the number of ways to select $k$ out of $n$ items with repetition (and
-without ordering). Here, we sum over all possible ways to distribute
-$|\predicates{}| \le n \le \maxNumClauses{}$ clauses among $|\predicates{}|$
-predicates so that each predicate gets at least one clause. For each predicate,
-we can then count the number of ways to select its clauses out of all possible
-clauses. The number of possible clauses can be computed by considering each
-possible arity $a$, and multiplying the number of `unfinished' clauses $C(a)$ by
-the number of ways to select the required $a+a_i$ terms in the body and the head
-of the clause.
-
-\section{PREDICATE INDEPENDENCE} \label{sec:independence}
-
-In this section, we define a notion of predicate independence as a way to
-constrain the probability distributions defined by the generated programs. We
-also describe efficient algorithms for propagation and entailment checking.
-
-\begin{definition}
-  Let $\mathscr{P}$ be a probabilistic logic program. Its \emph{predicate
-    dependency graph} is a directed graph $G_{\mathscr{P}} = (V, E)$ with the
-  set of nodes $V$ consisting of all predicates in $\mathscr{P}$. For any two
-  different predicates $\mathsf{P}$ and $\mathsf{Q}$, we add an edge from
-  $\mathsf{P}$ to $\mathsf{Q}$ if there is a clause in $\mathscr{P}$ with
-  $\mathsf{Q}$ as the head and $\mathsf{P}$ mentioned in the body. We say that
-  the edge is \emph{negative} if there exists a clause with $\mathsf{Q}$ as the
-  head and at least one instance of $\mathsf{P}$ at the body such that the path
-  from the root to the $\mathsf{P}$ node in the tree representation of the
-  clause passes through at least one negation node. Otherwise it is
-  \emph{positive}. We say that $\mathscr{P}$ (or $G_{\mathscr{P}}$) has a
-  \emph{negative cycle} if $G_{\mathscr{P}}$ has a cycle with at least one
-  negative edge.
-\end{definition}
-
-Labelling the edges as positive/negative will be immaterial for predicate
-independence, but the same graph will play a crucial role in negative cycle
-detection in the next section.
-
-\begin{definition}
-  Let $\mathsf{P}$ be a predicate in a program $\mathscr{P}$. The set of
-  \emph{dependencies} of $\mathsf{P}$ is the smallest set $D_{\mathsf{P}}$ such
-  that $\mathsf{P} \in D_{\mathsf{P}}$, and, for every $\mathsf{Q} \in
-  D_{\mathsf{P}}$, all direct predecessors of $\mathsf{Q}$ in $G_{\mathscr{P}}$
-  are in $D_{\mathsf{P}}$.
-\end{definition}
-
-\begin{definition}
-  Two predicates $\mathsf{P}$ and $\mathsf{Q}$ are \emph{independent} if
+  \binom{\sum_{a=0}^{\maxArity{} \times \maxNumNodes{}} C(a) P(a+a_i)}{h_i},
+\end{equation}
+Here, we sum over all ways to distribute $|\predicates{}| \le n \le
+\maxNumClauses{}$ clauses among $|\predicates{}|$ predicates so that each
+predicate gets at least one clause. For each predicate, we can then count the
+number of ways to select its clauses out of all possible clauses. The number of
+possible clauses can be computed by considering each possible arity $a$, and
+multiplying the number of `unfinished' clauses $C(a)$ by the number of ways to
+select the required $a+a_i$ terms in the body and the head of the clause.
+Finally, we compare the numbers produced by \eqref{eq:counting} with the numbers
+of programs generated by our model in \num{1032} different scenarios, thus
+showing that the combinatorial description developed in this section matches the
+model's behaviour.
+
+\section{Stratification and Independence} \label{sec:independence}
+
+\emph{Stratification} is a condition necessary for probabilistic logic programs
+\cite{DBLP:conf/padl/MantadelisR17} and often enforced on logic programs
+\cite{DBLP:journals/tcs/Bidoit91} that helps to ensure a unique answer to every
+query. This is achieved by restricting the use of negation so that any program
+$\mathscr{P}$ can be partitioned into a sequence of programs $\mathscr{P} =
+\bigsqcup_{i=1}^n \mathscr{P}_i$ such that, for all $i$, the negative literals
+in $\mathscr{P}_i$ can only refer to predicates defined in $\mathscr{P}_j$ for
+$j \le i$ \cite{DBLP:journals/tcs/Bidoit91}.
+
+\emph{Independence}, on the other hand, is defined on a pair of predicates (say,
+$\mathsf{P}, \mathsf{Q} \in \mathcal{P}$) and can be interpreted in two ways.
+First, if $\mathsf{P}$ and $\mathsf{Q}$ are independent, then any ground atom of
+$\mathsf{P}$ is independent of any ground atom of $\mathsf{Q}$ in the underlying
+probability distribution of the probabilistic program. Second, the part of the
+program needed to fully define $\mathsf{P}$ is disjoint from the part of the
+program needed to define $\mathsf{Q}$.
+
+These two seemingly disparate concepts can be defined using the same building
+block, i.e., a predicate dependency graph. Let $\mathscr{P}$ be a probabilistic
+logic program with its set of predicates $\predicates{}$. Its \emph{(predicate)
+  dependency graph} is a directed graph $G_{\mathscr{P}}$ with elements of
+$\predicates{}$ as nodes and an edge between $\mathsf{P}, \mathsf{Q} \in
+\predicates{}$ if there is a clause in $\mathscr{P}$ with $\mathsf{Q}$ as the
+head and $\mathsf{P}$ mentioned in the body. We say that the edge is
+\emph{negative} if there exists a clause with $\mathsf{Q}$ as the head and at
+least one instance of $\mathsf{P}$ at the body such that the path from the root
+to the $\mathsf{P}$ node in the tree representation of the clause passes through
+at least one negation node; otherwise, it is \emph{positive}. We say that
+$\mathscr{P}$ (or $G_{\mathscr{P}}$) has a \emph{negative cycle} if
+$G_{\mathscr{P}}$ has a cycle with at least one negative edge. A program
+$\mathscr{P}$ is \emph{stratified} if $G_{\mathscr{P}}$ has no negative
+cycles.\footnote{This definition is an extension of a well-known result for
+  logic programs \cite{DBLP:journals/jlp/BalbinPRM91} to probabilistic logic
+  programs with arbitrary complex clause bodies.} Thus a simple entailment
+algorithm for stratification can be constructed by selecting all clauses, all
+predicates of which are fully determined, and looking for negative cycles in the
+dependency graph constructed based on those clauses using an algorithm such as
+Bellman-Ford.
+
+For any predicate $\mathsf{P} \in \predicates{}$, the set of \emph{dependencies}
+of $\mathsf{P}$ is the smallest set $D_{\mathsf{P}}$ such that $\mathsf{P} \in
+D_{\mathsf{P}}$, and, for every $\mathsf{Q} \in D_{\mathsf{P}}$, all direct
+predecessors of $\mathsf{Q}$ in $G_{\mathscr{P}}$ are in $D_{\mathsf{P}}$. Two
+predicates $\mathsf{P}$ and $\mathsf{Q}$ are \emph{independent} if
 $D_{\mathsf{P}} \cap D_{\mathsf{Q}} = \emptyset$.
-\end{definition}
-
-\begin{figure}
+
+\begin{example} \label{ex:program}
+  Consider the following (fragment of a) program:
+  \begin{align}
+    \mathsf{sibling}(X, Y) &\gets \mathsf{parent}(X, Z) \land \mathsf{parent}(Y, Z), \nonumber \\
+    \mathsf{father}(X, Y) &\gets \mathsf{parent}(X, Y) \land \neg\mathsf{mother}(X, Y). \label[clause]{eq:example_clause}
+  \end{align}
+  Its predicate dependency graph is in \cref{fig:predicate_dependencies}.
+  Because of the negation in \eqref{eq:example_clause}, the edge from
+  $\mathsf{mother}$ to $\mathsf{father}$ is negative, while the other two edges
+  are positive. The dependencies of each predicate are:
+  \begin{alignat*}{3}
+    D_{\mathsf{parent}} &= \{ \mathsf{parent} \}, \quad && D_{\mathsf{sibling}}
+    &&= \{\mathsf{sibling}, \mathsf{parent} \},\\
+    D_{\mathsf{mother}} &= \{ \mathsf{mother} \}, \quad && D_{\mathsf{father}}
+    &&= \{ \mathsf{father}, \mathsf{mother}, \mathsf{parent} \}.
+  \end{alignat*}
+  Hence, we have two pairs of independent predicates, i.e., $\mathsf{mother}$ is
+  independent of $\mathsf{parent}$ and $\mathsf{sibling}$.
+\end{example}
+
+\begin{figure}[t]
   \centering
-  \begin{tikzpicture}
-    \node[draw,circle,gray,text=black] (and) at (0, 0) {$\land$};
-    \node[draw,circle,gray,text=black] (not) at (1.5, -1) {$\neg$};
-    \node[draw,gray,text=black] (parent) at (-1.5, -1) {$\mathsf{parent}(X, Y)$};
-    \node[draw,gray,text=black] (mother) at (1.5, -2) {$\mathsf{mother}(X, Y)$};
-    \draw[gray] (and) -- (parent);
-    \draw[gray] (and) -- (not);
-    \draw[gray] (not) -- (mother);
-  \end{tikzpicture}
-  \caption{A tree representation of the body of \cref{eq:example_clause}}
-  \label{fig:example_tree2}
-\end{figure}
-\begin{figure}
+  \begin{minipage}{.49\textwidth}
     \centering
@@
       \draw[-{Stealth[scale=1.5]}] (mother) edge node[below] {$-$} (father);
-  \end{tikzpicture}
-  \caption{The predicate dependency graph of the program in \cref{ex:program}.
-    Positive edges are labelled with `$+$', and negative edges with `$-$'.}
+    \end{tikzpicture}%
+    \captionof{figure}{The predicate dependency graph of the program from
+      \protect{\cref{ex:program}}. Positive edges are labelled with `$+$', and
+      negative edges with `$-$'.}
     \label{fig:predicate_dependencies}
+  \end{minipage}
+  \begin{minipage}{.49\textwidth}
+    \centering
+    \captionof{table}{Types of (potential) dependencies of a predicate
+      $\mathsf{P}$ based on the number of undetermined edges on the path from
+      the dependency to $\mathsf{P}$}
+    \label{tbl:dependencies}
+    \begin{tabular}{clc}
+      \toprule
+      Edges & Name & Notation \\
+      \midrule
+      $0$ & determined & $\Determined(p)$ \\
+      $1$ & almost determined & $\AlmostDetermined(p, s, t)$ \\
+      $>1$ & undetermined & $\Undetermined(p)$ \\
+      \bottomrule
+    \end{tabular}
+  \end{minipage}
 \end{figure}
 
-\begin{example} \label{ex:program}
-  Consider the following (fragment of a) program:
-  \begin{align}
-    \mathsf{sibling}(X, Y) &\gets \mathsf{parent}(X, Z) \land \mathsf{parent}(Y, Z), \nonumber \\
-    \mathsf{father}(X, Y) &\gets \mathsf{parent}(X, Y) \land \neg\mathsf{mother}(X, Y) \label[clause]{eq:example_clause}
-  \end{align}
-  Its predicate dependency graph is in \cref{fig:predicate_dependencies}.
-  Because of the negation in \cref{eq:example_clause} (as seen in
-  \cref{fig:example_tree2}), the edge from $\mathsf{mother}$ to
-  $\mathsf{father}$ is negative, while the other two edges are positive.
-
-  We can now list the dependencies of each predicate:
-  \begin{alignat*}{3}
-    D_{\mathsf{parent}} &= \{ \mathsf{parent} \}, && D_{\mathsf{sibling}}
-    &&= \{\mathsf{sibling}, \mathsf{parent} \},\\
-    D_{\mathsf{mother}} &= \{ \mathsf{mother} \}, && D_{\mathsf{father}}
-    &&= \{ \mathsf{father}, \mathsf{mother}, \mathsf{parent} \}.
-  \end{alignat*}
-  Hence, we have two pairs of independent predicates, i.e., $\mathsf{mother}$ is
-  independent from $\mathsf{parent}$ and $\mathsf{sibling}$.
-\end{example}
-
-We can now add a constraint to define an adjacency matrix for the predicate
-dependency graph but without positivity/negativity:
-
-\begin{definition} \label{def:adjacency_matrix}
-  An $|\predicates{}| \times |\predicates{}|$ adjacency matrix $\mathbf{A}$ with
-  $\{ 0, 1 \}$ as its domain is defined by stating that $\mathbf{A}[i][j] = 0$
-  if and only if, for all $k \in \{ 0, \dots, \maxNumClauses{} - 1 \}$, either
-  \[
-    \variable{heads}[k].\variable{predicate} \ne j
-  \]
-  or
-  \[
-    i \not\in \{a.\variable{name} \mid a \in
-    \variable{bodies}[k].\variable{values} \}.
-  \]
-\end{definition}
-
-Given an undetermined model, we can classify all dependencies of a predicate
-$\mathsf{P}$ into three categories based on how many of the edges on the path
-from the dependency to $\mathsf{P}$ are undetermined. In the case of zero, we
-call the dependency \emph{determined}. In the case of one, we call it
-\emph{almost determined}. Otherwise, it is \emph{undetermined}. In the context
-of propagation and entailment algorithms, we define a \emph{dependency} as the
-sum type:
-\begin{grammar}
-  <dependency> ::= $\Determined(p)$ | $\Undetermined(p)$ | $\AlmostDetermined(p,
-  s, t)$
-\end{grammar}
-where each alternative represents a determined, undetermined, and almost
-determined dependency, respectively. Here, $p \in \predicates{}$ is the name of
-the predicate which is the dependency of $\mathsf{P}$, and---in the case of
-$\AlmostDetermined$---$(s, t) \in \predicates{}^2$ is the one undetermined edge
-in $\mathbf{A}$ that prevents the dependency from being determined. For a
+Since the definition of independence relies on the dependency graph, we can
+represent this graph as an adjacency matrix constructed as part of the model.
+Let $\mathbf{A}$ be a $|\predicates{}| \times |\predicates{}|$ binary matrix
+defined element-wise by stating that $\mathbf{A}[i][j] = 0$ if and only if, for
+all $k = 0, \dots, \maxNumClauses{} - 1$, either
+$\variable{heads}[k].\variable{predicate} \ne j$ or $ i \not\in
+\{a.\variable{name} \mid a \in \variable{bodies}[k].\variable{values} \}$.
+
+Given a partially-solved model with its predicate dependency graph, let us pick
+an arbitrary path from $\mathsf{Q}$ to $\mathsf{P}$ (for some $\mathsf{P},
+\mathsf{Q} \in \predicates{}$) that consists of determined edges that are
+denoted by $1$ in $\mathbf{A}$ and potential/undetermined edges that are
+denoted by $\{ 0, 1 \}$. Each such path characterises a \emph{(potential)
+  dependency} $\mathsf{Q}$ for $\mathsf{P}$. We classify all such dependencies
+into three classes depending on the number of undetermined edges on the path.
+These classes are outlined in \cref{tbl:dependencies}, where $p$ represents the
+dependency predicate $\mathsf{Q}$, and, in the case of $\AlmostDetermined{}$,
+$(s, t) \in \predicates{}^2$ is the one undetermined edge on the path. For a
 dependency $d$---regardless of its exact type---we will refer to its predicate
-$p$ as $d.\mathsf{predicate}$. In describing the algorithms, we will use an
-underscore to replace any of $p$, $s$, $t$ in situations where the name is
-unimportant.
-
-\begin{algorithm}
+$p$ as $d.\mathsf{predicate}$. In describing the algorithms, we will use `$\_$'
+to replace any of $p$, $s$, $t$ in situations where the name is unimportant.
+
+\begin{algorithm}[t]
   \SetKwFunction{getDependencies}{deps}
@@
   \For{$(d_1, d_2) \in \getDependencies{$p_1$, 0} \times \getDependencies{$p_2$,
-      0}$ such that $d_1.\predicate = d_2.\predicate$}{
+      0}$ s.t. $d_1.\predicate = d_2.\predicate$}{
     \lIf{$d_1$ {\bf is} $\Determined(\_)$ {\bf and} $d_2$ {\bf is}
       $\Determined(\_)$}{\fail{}} \label{line:fail}
-    \If{$d_1$ {\bf is} $\Determined(\_)$ {\bf and} $d_2$ {\bf is}
-      $\AlmostDetermined(\_, s, t)$ {\bf or} \hspace{50pt} $d_2$ {\bf is}
-      $\Determined(\_)$ {\bf and} $d_1$ {\bf is} $\AlmostDetermined(\_, s,
-      t)$ \label{line:propagation_condition}}{
-      $\mathbf{A}[s][t]$.\removeValue{$1$}\; \label{line:propagation_result}
-    }
+    \lIf{$\{ d_1, d_2 \} = \{ \Determined(\_), \AlmostDetermined(\_, s, t)
+      \}$ \label{line:propagation_condition}}{$\mathbf{A}[s][t]$.\removeValue{$1$}}
   }
@@
 that prevents the $\AlmostDetermined$ from becoming a $\Determined$ cannot
-exist--\cref{line:propagation_condition,line:propagation_result} handle this
-possibility.
-
-\begin{algorithm}
+exist---\cref{line:propagation_condition} handles this possibility.
+
+\begin{algorithm}[t]
   \SetKwData{edgeExists}{edge}
@@
 
-\begin{figure}
+\begin{example} \label{example:independence}
+  Consider this partially determined (fragment of a) program:
+  \begin{align*}
+    \Box(X, Y) &\gets \mathsf{parent}(X, Z) \land \mathsf{parent}(Y, Z),\\
+    \mathsf{father}(X, Y) &\gets \mathsf{parent}(X, Y) \land \neg\mathsf{mother}(X, Y),
+  \end{align*}
+  where $\Box$ indicates an unknown predicate with domain
+  \[
+    D_\Box = \{ \mathsf{father}, \mathsf{mother}, \mathsf{parent},
+    \mathsf{sibling} \}.
+  \]
+  The predicate dependency graph is pictured in \cref{fig:example}. Suppose we
+  have a constraint that $\mathsf{mother}$ and $\mathsf{parent}$ must be
+  independent. The lists of potential dependencies for both predicates are:
+  \begin{align*}
+    D_{\mathsf{mother}} &= \{ \Determined(\mathsf{mother}), \AlmostDetermined(\mathsf{parent}, \mathsf{parent}, \mathsf{mother}) \}, \\
+    D_{\mathsf{parent}} &= \{ \Determined(\mathsf{parent}) \}.
+  \end{align*}
+  An entailment check at this stage would produce \textsc{undefined}, but
+  propagation replaces the boxed value in \cref{fig:dependencies_matrix} with
+  zero, eliminating the potential edge from $\mathsf{parent}$ to
+  $\mathsf{mother}$. This also eliminates $\mathsf{mother}$ from $D_\Box$, and
+  this is enough to make \cref{alg:independence_entailment} return
+  \textsc{true}.
+\end{example}
+
+  \begin{figure}[t]
+    \begin{minipage}{.49\textwidth}
       \centering
-  \[
-    \begin{blockarray}{ccccc}
-      \begin{block}{c(cccc)}
+      \subfloat[The adjacency matrix of the graph. The boxed value is the
+      decision variable that will be propagated by
+      \cref{alg:independence_propagation}.\label{fig:dependencies_matrix}]{
+        $\begin{blockarray}{lcccc}
+          \begin{block}{l!{\quad}(cccc)}
             \mathsf{father} & 0 & 0 & 0 & 0 \\
@@
           \end{block}
-    \end{blockarray}
-  \]
-  \caption{The adjacency matrix defined using \cref{def:adjacency_matrix} for
-    \cref{example:independence}}
-  \label{fig:dependencies_matrix}
-\end{figure}
-\begin{figure}
+        \end{blockarray}$
+      }
+    \end{minipage}
+    \hfill
+    \begin{minipage}{.49\textwidth}
       \centering
+      \subfloat[A drawing of the graph. Dashed edges are undetermined---they may
+      or may not exist.\label{fig:dependencies2}]{
+        \centering
+        \makebox[\linewidth]{
           \begin{tikzpicture}
@@
           \end{tikzpicture}
-  \caption{The predicate dependency graph that corresponds to
-    \cref{fig:dependencies_matrix}. Dashed edges are undetermined---they may
-    or may not exist.}
-  \label{fig:dependencies2}
+        }
+      }
+    \end{minipage}
+    \caption{The predicate dependency graph of \protect{\cref{example:independence}}}
+    \label{fig:example}
   \end{figure}
 
-\begin{example} \label{example:independence}
-  Consider this partially determined (fragment of a) program:
-  \begin{align*}
-    \Box(X, Y) &\gets \mathsf{parent}(X, Z) \land \mathsf{parent}(Y, Z),\\
-    \mathsf{father}(X, Y) &\gets \mathsf{parent}(X, Y) \land \neg\mathsf{mother}(X, Y)
-  \end{align*}
-  where $\Box$ indicates an unknown predicate with domain
-  \[
-    D_\Box = \{ \mathsf{father}, \mathsf{mother}, \mathsf{parent},
-    \mathsf{sibling} \}.
-  \]
-  The predicate dependency graph without positivity/negativity (as defined in
-  \cref{def:adjacency_matrix}) is represented in
-  \cref{fig:dependencies_matrix,fig:dependencies2}.
-
-  Suppose we have a constraint that $\mathsf{mother}$ and $\mathsf{parent}$ must
-  be independent. The lists of potential dependencies for both predicates are:
-  \begin{align*}
-    D_{\mathsf{mother}} &= \{ \Determined(\mathsf{mother}), \AlmostDetermined(\mathsf{parent}, \mathsf{parent}, \mathsf{mother}) \}, \\
-    D_{\mathsf{parent}} &= \{ \Determined(\mathsf{parent}) \}.
-  \end{align*}
-  An entailment check at this stage would produce \textsc{undefined}, but
-  propagation replaces the boxed value in \cref{fig:dependencies_matrix} with
-  zero, eliminating the potential edge from $\mathsf{parent}$ to
-  $\mathsf{mother}$. This also eliminates $\mathsf{mother}$ from $D_\Box$, and,
-  although some undetermined variables remain, this is enough to make
-  \cref{alg:independence_entailment} return \textsc{true}.
-\end{example}
-
-\section{NEGATIVE CYCLES} \label{sec:cycles}
-
-Having no negative cycles in the predicate dependency graph is a requirement for
-probabilistic logic programming language ProbLog \citep{kimmig2009trading},
-although it has been shown how the requirement can be alleviated by introducing
-negative probabilities \citep{DBLP:journals/ijar/BuchmanP17}. Ideally, we would
-like to design a constraint for negative cycles similar to the constraint for
-independence in the previous section. However, the difficulty with creating a
-propagation algorithm for negative cycles is that there seems to be no good way
-to extend \cref{def:adjacency_matrix} so that the adjacency matrix captures
-positivity/negativity. Thus, we settle for an entailment algorithm with no
-propagation.
-
-\begin{algorithm}
-  \KwData{a program $\mathscr{P}$}
-  \SetKwFunction{hasNegativeCycles}{hasNegativeCycles}
-  Let $\mathscr{R} \subseteq \mathscr{P}$ be the largest subprogram of
-  $\mathscr{P}$ with its $\variable{structure}$ and predicates in both body
-  and head fully determined\footnotemark\;
-  \If{\hasNegativeCycles($G_{\mathscr{R}}$)}{
-    \Return{\textsc{false}}\;
-  }
-  \lIf{$\mathscr{R} = \mathscr{P}$}{\Return{\textsc{true}}}
-  \Return{\textsc{undefined}}\;
-  \caption{Entailment for negative cycles}
-  \label{alg:negative_cycles}
-\end{algorithm}
-\footnotetext{The arguments (whether variables or constants) are irrelevant to
-  our definition of independence.}
-
-The algorithm takes all clauses whose structure and predicates have been fully
-determined and uses them to construct a full dependency graph. In our
-implementation, \texttt{hasNegativeCycles} function is just a simple extension
-of the backtracking cycle detection algorithm that `travels' around the graph
-following edges and checking if each vertex has already been visited or not.
-Alternatively, one could assign weights to the edges (e.g., $1$ for positive
-and $-\infty$ for negative edges), thus reducing our negative cycle detection
-problem to what is typically known as the negative cycle detection problem in
-the literature, and use an algorithm such as Bellman-Ford
-\citep{shimbel1954structure}.
-
-If the algorithm finds a negative cycle in this fully-determined part of the
-program, then we must return \textsc{false}. If there was no negative cycle and
-the entire program is (sufficiently) determined, then there cannot be any
-negative cycles. In all other cases, it is too early to tell.
-
-\section{EMPIRICAL PERFORMANCE} \label{sec:experiments}
-
-\begin{figure}
-  \centering
-  \input{impact.tex}
-  \caption{The mean number of nodes in the binary search tree for each value of
-    each experimental parameter. Note that the horizontal axis is on a $\log_2$
-    scale.}
-  \label{fig:impact}
-\end{figure}
-
-\begin{figure*}
-  \centering
-  \input{phase_transition.tex}
-  \caption{The distribution of the number of nodes in the binary search tree as
-    a function of the number of independent pairs of predicates for
-    $|\predicates| = 8$. Outliers are hidden, the dots denote mean values, and
-    the vertical axis is on a $\log_{10}$ scale.}
-  \label{fig:phase_transition}
-\end{figure*}
+\section{Experimental Results} \label{sec:experiments}
+
+We now present the results of two experiments: in \cref{sec:experiment1} we
+examine the scalability of our constraint model with respect to its parameters
+and in \cref{sec:experiment2} we demonstrate how the model can be used to
+compare inference algorithms and describe their behaviour across a wide range of
+programs. The experiments were run on a system with Intel Core i5-8250U
+processor and \SI{8}{\giga\byte} of RAM. The constraint model was implemented in
+Java~8 with Choco~4.10.2 \cite{choco}. All inference algorithms are implemented
+in \textsc{ProbLog}~2.1.0.39 and were run using Python~3.8.2 with PySDD~0.2.10
+and PyEDA~0.28.0. For both sets of experiments, we generate programs without
+negative cycles and use a \SI{60}{\second} timeout.
+
+\subsection{Empirical Performance of the Model} \label{sec:experiment1}
 
@@
 are needed to complete the model: heuristics and restarts. By trial and error,
-the variable ordering heuristic was devised to eliminate sources of thrashing,
-i.e., situations where a contradiction is being `fixed' by making changes that
-have no hope of fixing the contradiction. Thus, we partition all decision
-variables into an ordered list of groups, and require the values of all
-variables from one group to be determined before moving to the next group.
+the variable ordering heuristic was devised to eliminate sources of
+\emph{thrashing}, i.e., situations where a contradiction is being `fixed' by
+making changes that have no hope of fixing the contradiction. Thus, we partition
+all decision variables into an ordered list of groups and require the values of
+all variables from one group to be determined before moving to the next group.
 Within each group, we use the `fail first' variable ordering heuristic. The
@@
 decision variables from the first clause before proceeding to the next. The
-decision variables within each clause are divided into:
-\begin{enumerate*}
+decision variables within each clause are divided into
+\begin{enumerate*}[(a)]
 \item the $\variable{structure}$ array,
@@
 \]
-We also employ a geometric restart policy, restarting after $10, 20, 40,
-80, \dots$ contradictions.
-
-We ran close to \num{400000} experiments, investigating whether the model is
-efficient enough to generate reasonably-sized programs and gaining insight into
-what parameter values make the constraint satisfaction problem harder. For these
-experiments, we use Choco~4.10.2 \citep{choco} with Java~8. For
-$|\predicates{}|$, $|\variables{}|$, $|\constants{}|$, $\maxNumNodes{}$, and
-$\maxNumClauses{} - |\predicates{}|$ (i.e., the number of clauses in addition to
-the mandatory $|\predicates{}|$ clauses), we assign all combinations of 1, 2, 4,
-8. $\maxArity{}$ is assigned to values 1--4. For each $|\predicates{}|$, we also
-iterate over all possible numbers of independent pairs of predicates, ranging
-from 0 up to $\binom{|\predicates{}|}{2}$. For each combination of the
-above-mentioned parameters, we pick ten random ways to assign arities to
-predicates (such that $\maxArity{}$ occurs at least once) and ten random
-combinations of independent pairs. We then run the solver with a
-\SI{60}{\second} timeout.
-
-The vast majority (\SI{97.7}{\percent}) of runs finished in under
-\SI{1}{\second}, while four instances timed out: all with $|\predicates| =
-\maxNumClauses{} - |\predicates{}| = \maxNumNodes{} = 8$ and the remaining
-parameters all different. This suggests that---regardless of parameter
-values---most of the time a solution can be identified instantaneously while
-occasionally a series of wrong decisions can lead the solver into a part of the
-search space with no solutions.
+We also employ a geometric restart policy, restarting after $10, 10 \times 1.1,
+10 \times 1.1^2, \dots$ contradictions.\footnote{Restarts help overcome early
+  mistakes in the search process but can be disabled if one wants to find all
+  solutions, in which case search is complete regardless of the variable
+  ordering heuristic.} We ran \num{399360} experiments, investigating the
+model's efficiency and gaining insight into what parameter values make the CSP
+harder. For $|\predicates{}|$, $|\variables{}|$, $|\constants{}|$,
+$\maxNumNodes{}$, and $\maxNumClauses{} - |\predicates{}|$ (i.e., the number of
+clauses in addition to the mandatory $|\predicates{}|$ clauses), we assign all
+combinations of 1, 2, 4, 8. $\maxArity{}$ is assigned to values 1--4. For each
+$|\predicates{}|$, we also iterate over all possible numbers of independent
+pairs of predicates, ranging from 0 up to $\binom{|\predicates{}|}{2}$. For each
+combination of the above-mentioned parameters, we pick ten random ways to assign
+arities to predicates (such that $\maxArity{}$ occurs at least once) and ten
+random combinations of independent pairs.
+
+The majority (\SI{97.7}{\percent}) of runs finished in under \SI{1}{\second},
+while four instances timed out: all with $|\predicates{}| = \maxNumClauses{} -
+|\predicates{}| = \maxNumNodes{} = 8$ and the remaining parameters all
+different. This suggests that---regardless of parameter values---most of the
+time a solution can be identified instantaneously while occasionally a series of
+wrong decisions can lead the solver into a part of the search space with no
+solutions.
 
@@
 tree grows as a function of each parameter (the plot for the median is very
-similar). The growth of each curve suggest how well/poorly the model scales with
-higher values of the parameter. From this plot, it is clear that
-$\maxNumNodes{}$ is the limiting factor. This is because some tree structures
-can be impossible to fill with predicates without creating either a negative
-cycle or a forbidden dependency, and such trees become more common as the number
-of nodes increases. Likewise, a higher number of predicates complicates the
-situation as well.
-
-\cref{fig:phase_transition} takes the data for $|\predicates{}| = 8$ (almost
-\num{300000} observations) and shows how the number of nodes in the search tree
-varies with the number of independent pairs of predicates. The box plots show
-that the median number of nodes stays about the same while the dots
-(representing the means) draw an arc. This suggests a type of phase transition,
-but only in mean rather than median, i.e., most problems remain easy, but with
-some parameter values hard problems become more likely. On the one hand, with
-few pairs of independent predicates, one can easily find the right combination
-of predicates to use in each clause. On the other hand, if most predicates must
-be independent, this leaves fewer predicates that can be used in the body of
-each clause (since all of them have to be independent with the head predicate),
-and we can either quickly find a solution or identify that there is none.
-
-% TODO: Extra notes.
-% 1. Randomness. The value heuristic is random because we want randomness. After
-% finding one solution, one can continue the search for more, but they will be
-% similar (acceptable if the search space is small and we want to find all
-% solutions).
-% 2. Logic programs don't have disjunctions and parentheses. Is there an easy
-% way to eliminate them?
-% 3. We can do the same thing for predicates within the body of a clause that we
-% do with variables, i.e., predicates within a clause are permutable (except for
-% the head predicate), so we can have a set of 'allowed' predicates.
-% 4. One example of a clear bias exhibited by our model is that of complexity
-% over simplicity, i.e., if a tree that represents the body of a clause can have
-% up to $\maxNumNodes{}$ nodes---because the number of possible trees with $n$
-% nodes grows with $n$---it is much more likely to have $\maxNumNodes{}$ or
-% $\maxNumNodes{} - 1$ nodes than, e.g., one or two.
-
-\section{CONCLUSIONS \& FUTURE WORK}
-
-We were able to design an efficient model for generating both logic programs and
-probabilistic logic programs. The model avoids unnecessary symmetries, generates
-valid programs, and can ensure predicate independence. Note that our model
-treats logically equivalent but syntactically different formulas as different.
-While there are many situations where one would prefer to eliminate them like
-symmetries, there are also situations where we do care about enumerating
-different ways to express the same probability distribution or knowledge base.
-For instance, one could look for the `best' logically equivalent formula, or
-investigate whether some formulas result in faster inference than others.
-
-Another topic worth mentioning is randomness. Most random models sample from a
-well-defined probability distribution whereas a constraint model, while
-sufficiently random, provides no such guarantees. In future work, it would be
-interesting to examine the probability distribution of logic programs as
-generated by our model, although it is not obvious how such a probability
-distribution could be characterised.
-
-%\subsubsection*{Acknowledgements}
-
-%This work was supported by the EPSRC Centre for Doctoral Training in
-%Robotics and Autonomous Systems, funded by the UK Engineering and Physical
-%Sciences Research Council (grant EP/S023208/1).
-
-\renewcommand{\bibsection}{\subsubsection*{References}}
+similar). The growth of each curve suggests how the model scales with higher
+values of the parameter. From this plot, it is clear that $\maxNumNodes{}$ is
+the limiting factor. This is because some tree structures can be impossible to
+fill with predicates without creating either a negative cycle or a forbidden
+dependency, and such trees become more common as the number of nodes increases.
+Likewise, a higher number of predicates complicates the situation as well.
+
+\begin{figure}[t]
+  \centering
+  \begin{minipage}[t]{.49\textwidth}
+    \centering
+    \input{impact.tex}%
+    \captionof{figure}{The mean number of nodes in the binary search tree for
+      each value of each experimental parameter. Note that the horizontal axis
+      is on a $\log_2$ scale.}
+    \label{fig:impact}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[t]{.49\textwidth}
+    \centering
+    \input{bars.tex}%
+    \captionof{figure}{Inference time for different values of $\maxArity{}$ and
+      proportions of probabilistic facts that are probabilistic. The total
+      number of facts is fixed at $10^5$.}
+    \label{fig:bars}
+  \end{minipage}
+\end{figure}
+
+\subsection{Experimental Comparison of Inference Algorithms} \label{sec:experiment2}
+
+For this experiment, we consider clauses of two types: \emph{rules} are clauses
+such that the head atom has at least one variable, and \emph{facts} are clauses
+with empty bodies and no variables. We use our constraint model to generate the
+rules according to the following parameter values: $|\predicates{}|,
+|\variables{}|, \maxNumNodes{} \in \{ 2, 4, 8 \}$, $\maxArity{} \in \{ 1, 2, 3
+\}$, $\maxNumClauses{} = |\predicates{}|$, $\constants{} = \emptyset$. These
+values are (approximately) representative of many standard benchmarking
+instances which often have 2--8 predicates of arity one or two, 0--8 rules, and
+a larger database of facts \cite{DBLP:journals/tplp/FierensBRSGTJR15}. Just like
+before, we explore all possible numbers of independent predicate pairs. We also
+add a constraint that forbids empty bodies. For both rules and facts,
+probabilities are uniformly sampled from $\{ 0.1, 0.2, \dots, 0.9 \}$.
+Furthermore, all rules are probabilistic, while we vary the proportion of
+probabilistic facts among \SI{25}{\percent}, \SI{50}{\percent}, and
+\SI{75}{\percent}. For generating facts, we consider $|\constants{}| \in \{100,
+200, 400 \}$ and vary the number of facts among $10^3$, $10^4$, and $10^5$ but
+with one exception: the number of facts is not allowed to exceed
+\SI{75}{\percent} of all possible facts with the given values of
+$\predicates{}$, $\arities{}$, and $\constants{}$. Facts are generated using a
+simple procedure that randomly selects a predicate, combines it with the right
+number of constants, and checks whether the generated atom is already included
+or not. We randomly select configurations from the description above and
+generate ten programs with a complete restart of the constraint solver before
+the generation of each program, including choosing different arities and
+independent pairs. Finally, we set the query of each program to a random fact
+not explicitly included in the program and consider six natively supported
+algorithms and knowledge compilation techniques: binary decision diagrams (BDDs)
+\cite{DBLP:journals/tc/Bryant86}, negation normal form (NNF), deterministic
+decomposable NNF (d-DNNF) \cite{DBLP:journals/jair/DarwicheM02}, K-Best
+\cite{DBLP:conf/ijcai/RaedtKT07}, and two encodings based on sentential decision
+diagrams \cite{DBLP:conf/ijcai/Darwiche11}, one of which encodes the entire
+program (SDDX), while the other one encodes only the part of the program
+relevant to the query (SDD).\footnote{Forward SDDs (FSDDs) and forward BDDs
+  (FBDDs) \cite{DBLP:conf/aaai/TsamouraGK20,DBLP:conf/ijcai/VlasselaerBKMR15}
+  are omitted because the former uses too much memory and the implementation of
+  the latter seems to be broken at the time of writing.}
+
+Out of \num{11310} generated problem instances, about \SI{35}{\percent} were
+discarded because one or more algorithms were not able to ground the instance
+unambiguously. The first observation (pictured in \cref{fig:line_plots}) is that
+the algorithms are remarkably similar, i.e., the differences in performance are
+small and consistent across all parameter values (including parameters not shown
+in the figure). Unsurprisingly, the most important predictor of inference time
+is the number of facts. However, after fixing the number of facts to a constant
+value, we can still observe that inference becomes harder with higher arity
+predicates as well as when facts are mostly probabilistic (see \cref{fig:bars}).
+Finally, according to \cref{fig:line_plots}, the independence structure of a
+program does not affect inference time, i.e., state-of-the-art inference
+algorithms---although they are supposed to
+\cite{DBLP:conf/uai/FierensBTGR11}---do not exploit situations where separate
+parts of a program can be handled independently.
+
+\begin{figure}[t]
+  \centering
+  \input{line_plots.tex}%
+  \caption{Mean inference time for a range of \textsc{ProbLog} inference
+    algorithms as a function of the total number of facts in the program and the
+    proportion of independent pairs of predicates. For the second plot, the
+    number of facts is fixed at $10^5$.}
+  \label{fig:line_plots}
+\end{figure}
+
+\section{Conclusion}
+
+We described a constraint model for generating both logic programs and
+probabilistic logic programs. The model avoids unnecessary symmetries, is
+reasonably efficient and supports additional constraints such as predicate
+independence. Our experimental results provide the first comparison of inference
+algorithms for probabilistic logic programming languages that generalises over
+programs, i.e., is not restricted to just a few programs and data sets. While
+the results did not reveal any significant differences among the algorithms,
+they did reveal a shared weakness, i.e., the inability to ignore the part of a
+program that is easily seen to be irrelevant to the given query.
+
+Nonetheless, we would like to outline two directions for future work. First, the
+experimental evaluation in \cref{sec:experiment1} revealed scalability issues,
+particularly concerning the length/complexity of clauses. However, this
+particular issue is likely to resolve itself if the format of a clause is
+restricted to a conjunction of literals. Second, random instance generation
+typically focuses on either realistic instances or sampling from a simple and
+well-defined probability distribution. Our approach can be used to achieve the
+former, but it is an open question how it could accommodate the latter.
+
+\subsubsection*{Acknowledgments.}
+Paulius was supported by the EPSRC Centre for Doctoral Training in Robotics
+and Autonomous Systems, funded by the UK Engineering and Physical Sciences
+Research Council (grant EP/S023208/1). Vaishak was supported by a Royal Society
+University Research Fellowship.
+
+\bibliographystyle{splncs04}
 \bibliography{paper}
 
-\appendix
-\section{EXAMPLE PROGRAMS}
-
-In this appendix, we provide examples of probabilistic logic programs generated
-by various combinations of parameters. In all cases, we use $\{ 0.1, 0.2, \dots,
-0.9, 1, 1, 1, 1, 1\}$ as the multiset of probabilities. Each clause is written
-on a separate line and ends with a full stop. The head and the body of each
-clause are separated with \texttt{:-} (instead of $\gets$). The probability of
-each clause is prepended to the clause, using \texttt{::} as a separator.
-Probabilities equal to one and empty bodies of clauses can be omitted.
-Conjunction, disjunction, and negation are denoted by commas, semicolons, and
-`\texttt{\textbackslash+}', respectively. Parentheses are used to demonstrate
-precedence, although many of them are redundant.
-
-By setting $\predicates{} = [\texttt{p}]$, $\arities{} = [1]$, $\variables{} =
-\{ \texttt{X} \}$, $\constants{} = \emptyset$, $\maxNumNodes{} = 4$, and
-$\maxNumClauses{} = 1$, we get fifteen one-line programs, five of which are
-without negative cycles (denoted by `+'). Only the last program has no cycles at
-all.
-
-\begin{itemize}
-\item
-\begin{verbatim}
-0.5 :: p(X) :- (\+(p(X))), (p(X)).
-\end{verbatim}
-\item
-\begin{verbatim}
-0.8 :: p(X) :- (\+(p(X))); (p(X)).
-\end{verbatim}
-\item[+]
-\begin{verbatim}
-0.8 :: p(X) :- (p(X)); (p(X)).
-\end{verbatim}
-\item[+]
-\begin{verbatim}
-0.7 :: p(X) :- (p(X)), (p(X)).
-\end{verbatim}
-\item
-\begin{verbatim}
-0.6 :: p(X) :- (p(X)), (\+(p(X))).
-\end{verbatim}
-\item
-\begin{verbatim}
-p(X) :- (p(X)); (\+(p(X))).
-\end{verbatim}
-\item[+]
-\begin{verbatim}
-0.1 :: p(X) :- (p(X)); (p(X)); (p(X)).
-\end{verbatim}
-\item[+]
-\begin{verbatim}
-0.8 :: p(X) :- (p(X)), (p(X)), (p(X)).
-\end{verbatim}
-\item
-\begin{verbatim}
-p(X) :- \+(p(X)).
-\end{verbatim}
-\item
-\begin{verbatim}
-0.1 :: p(X) :- \+(\+(p(X))).
-\end{verbatim}
-\item
-\begin{verbatim}
-p(X) :- \+((p(X)); (p(X))).
-\end{verbatim}
-\item
-\begin{verbatim}
-0.4 :: p(X) :- \+((p(X)), (p(X))).
-\end{verbatim}
-\item
-\begin{verbatim}
-0.4 :: p(X) :- \+(\+(\+(p(X)))).
-\end{verbatim}
-\item[+]
-\begin{verbatim}
-0.7 :: p(X) :- p(X).
-\end{verbatim}
-\item[+]
-\begin{verbatim}
-p(X).
-\end{verbatim}
-\end{itemize}
-
-To demonstrate variable symmetry reduction in action, we set $\predicates{} =
-[\texttt{p}]$, $\arities{} = [3]$, $\variables{} = \{\texttt{X}, \texttt{Y},
-\texttt{Z} \}$, $\constants{} = \emptyset$, $\maxNumNodes{} = 1$,
-$\maxNumClauses{} = 1$, and forbid all cycles. This gives us the following five
-programs:
-
-\begin{itemize}
-\item
-\begin{verbatim}
-0.8 :: p(Z, Z, Z).
-\end{verbatim}
-\item
-\begin{verbatim}
-p(Y, Y, Z).
-\end{verbatim}
-\item
-\begin{verbatim}
-p(Y, Z, Z).
-\end{verbatim}
-\item
-\begin{verbatim}
-p(Y, Z, Y).
-\end{verbatim}
-\item
-\begin{verbatim}
-0.1 :: p(X, Y, Z).
-\end{verbatim}
-\end{itemize}
-
-This is one of many possible programs with $\predicates{} = [\texttt{p},
-\texttt{q}, \texttt{r}]$, $\arities{} = [1, 2, 3]$, $\variables{} =
-\{\texttt{X}, \texttt{Y}, \texttt{Z} \}$, $\constants{} = \{ \texttt{a},
-\texttt{b}, \texttt{c} \}$, $\maxNumNodes{} = 5$, $\maxNumClauses{} = 5$, and
-without negative cycles:
-
-\begin{verbatim}
-p(b) :- \+((q(a, b)), (q(X, Y)), (q(Z, X))).
-0.4 :: q(X, X) :- \+(r(Y, Z, a)).
-q(X, a) :- r(Y, Y, Z).
-q(X, a) :- r(Y, b, Z).
-r(Y, b, Z).
-\end{verbatim}
-
-Finally, we set
-$\predicates{} = [\texttt{p}, \texttt{q}, \texttt{r}]$, $\arities{} = [1, 1,
-1]$, $\variables{} = \emptyset$, $\constants{} = \{ \texttt{a} \}$,
-$\maxNumNodes{} = 3$, $\maxNumClauses{} = 3$, forbid negative cycles, and
-constrain predicates \texttt{p} and \texttt{q} to be independent. The resulting
-search space contains thousands of programs such as:
-
-\begin{itemize}
-\item
-\begin{verbatim}
-0.5 :: p(a) :- (p(a)); (p(a)).
-0.2 :: q(a) :- (q(a)), (q(a)).
-0.4 :: r(a) :- \+(q(a)).
-\end{verbatim}
-\item
-\begin{verbatim}
-p(a) :- p(a).
-0.5 :: q(a) :- (r(a)); (q(a)).
-r(a) :- (r(a)); (r(a)).
-\end{verbatim}
-\item
-\begin{verbatim}
-p(a) :- (p(a)); (p(a)).
-0.6 :: q(a) :- q(a).
-0.7 :: r(a) :- \+(q(a)).
-\end{verbatim}
-\end{itemize}
-
 \end{document}

### 2020-07-22 talk/impact.tex
Adapt plots to slides

% Created by tikzDevice version 0.12.3 on 2020-07-22 15:37:51
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (303.53,130.09);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (303.53,130.09);
\end{scope}
\begin{scope}
\path[clip] ( 40.51, 30.69) rectangle (127.90,124.59);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 40.51, 30.69) rectangle (127.90,124.59);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51, 50.03) --
	(127.90, 50.03);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51, 81.30) --
	(127.90, 81.30);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51,112.57) --
	(127.90,112.57);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 56.44, 30.69) --
	( 56.44,124.59);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 80.36, 30.69) --
	( 80.36,124.59);

\path[draw=drawColor,line width= 0.3pt,line join=round] (104.27, 30.69) --
	(104.27,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.51, 34.40) --
	(127.90, 34.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.51, 65.67) --
	(127.90, 65.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.51, 96.94) --
	(127.90, 96.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.48, 30.69) --
	( 44.48,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.40, 30.69) --
	( 68.40,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 92.31, 30.69) --
	( 92.31,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (116.23, 30.69) --
	(116.23,124.59);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.48, 34.95) --
	( 68.40, 35.86) --
	( 92.31, 39.64) --
	(116.23, 66.05);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.48, 54.81) --
	( 68.40, 57.14) --
	( 82.39, 60.74) --
	( 92.31, 63.15);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.48, 55.77) --
	( 68.40, 58.31) --
	( 92.31, 59.68) --
	(116.23, 62.08);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.48, 57.27) --
	( 68.40, 58.33) --
	( 92.31, 59.95) --
	(116.23, 60.30);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.48, 54.34) --
	( 68.40, 55.03) --
	( 92.31, 58.92) --
	(116.23, 67.56);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.48, 37.33) --
	( 68.40, 37.69) --
	( 92.31, 40.51) --
	(116.23,120.32);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 30.69) rectangle (127.90,124.59);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56, 31.37) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56, 62.64) {2000};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56, 93.91) {4000};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 37.76, 34.40) --
	( 40.51, 34.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 37.76, 65.67) --
	( 40.51, 65.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 37.76, 96.94) --
	( 40.51, 96.94);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.48, 27.94) --
	( 44.48, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.40, 27.94) --
	( 68.40, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 92.31, 27.94) --
	( 92.31, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (116.23, 27.94) --
	(116.23, 30.69);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 44.48, 19.68) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 68.40, 19.68) {2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 92.31, 19.68) {4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (116.23, 19.68) {8};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 84.20,  7.64) {Value};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08, 77.64) {Mean number of nodes};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (138.90, 21.17) rectangle (298.03,134.11);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at (144.40,119.96) {Variable};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (144.40, 98.94) rectangle (158.85,113.39);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (145.84,106.16) -- (157.41,106.16);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (144.40, 84.48) rectangle (158.85, 98.94);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round] (145.84, 91.71) -- (157.41, 91.71);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (144.40, 70.03) rectangle (158.85, 84.48);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,line join=round] (145.84, 77.26) -- (157.41, 77.26);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (144.40, 55.57) rectangle (158.85, 70.03);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,line join=round] (145.84, 62.80) -- (157.41, 62.80);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (144.40, 41.12) rectangle (158.85, 55.57);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.6pt,line join=round] (145.84, 48.35) -- (157.41, 48.35);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (144.40, 26.67) rectangle (158.85, 41.12);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.6pt,line join=round] (145.84, 33.89) -- (157.41, 33.89);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (164.35,103.13) {The number of predicates};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (164.35, 88.68) {Maximum arity};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (164.35, 74.23) {The number of variables};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (164.35, 59.77) {The number of constants};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (164.35, 45.32) {The number of additional clauses};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (164.35, 30.86) {The maximum number of nodes};
\end{scope}
\end{tikzpicture}

### 2020-07-22 talk/talk.tex
Adapt plots to slides

\documentclass{beamer}
\usepackage{tikz}

\usetheme{Singapore}
\usecolortheme{lily}
\beamertemplatenavigationsymbolsempty

\author{\textbf{Paulius Dilkas}\inst{1} \and Vaishak Belle\inst{1,2}}
\title{Generating Random Logic Programs Using Constraint Programming}
\date{CP 2020}
\institute{\inst{1} University of Edinburgh, Edinburgh, UK \and \inst{2} Alan
  Turing Institute, London, UK}

\begin{document}

\begin{frame}[noframenumbering,plain]
  \tikz[remember picture,overlay]{
    \node at ([yshift=25pt,xshift=30pt]current page.south)
    {\includegraphics[height=40pt]{inf.png}};
    \node at ([yshift=25pt,xshift=75pt]current page.south)
    {\includegraphics[height=40pt]{ecr.jpg}};
    \node at ([yshift=20pt,xshift=140pt]current page.south)
    {\includegraphics[height=20pt]{epsrc.png}};
  }
  \titlepage
\end{frame}

% TODO: examples of programs (actually introduce what they are about)

% TODO: clauses as trees

\begin{frame}{Scalability}
  \centering
  \input{impact.tex}
\end{frame}

\begin{frame}{Properties of Programs vs. Inference Algorithms}
  \centering
  \input{line_plots.tex}
\end{frame}

\begin{frame}{Properties of Programs vs. Inference Algorithms}
  \centering
  \input{../paper/bars.tex}
\end{frame}

% width: 4.2679148611112
% height: 3.5575922222223

\begin{frame}{Overview}
  \begin{block}{General parameters}
    \begin{itemize}
    \item maximum number of solutions
    \item \texttt{maxNumNodes} (in the tree representation of a clause)
    \item list of predicates with their variables
    \item maximum number of clauses
    \item option to forbid all cycles or just negative cycles
    \item list of probabilities that are randomly assigned to clauses: $\{ 0.1,
      0.2, \dots, 0.9, 1, 1, 1, 1, 1, 1 \}$
    \end{itemize}
  \end{block}
  \begin{block}{Decision variables}
    \begin{itemize}
    \item \texttt{IntVar[] clauseAssignments}: a predicate or disabled
    \item \texttt{Clause[] clauses}
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Constraints}
  \begin{block}{Each predicate should get at least one constraint}
    \begin{itemize}
    \item \texttt{numDisabledClauses}: defined by a \texttt{count} constraint
    \item $\texttt{numDistinctValues} = \begin{cases}
        \texttt{numPredicates} + 1 & \text{if } \texttt{numDisabledValues} > 0 \\
        \texttt{numPredicates} & \text{otherwise.}
      \end{cases}$
      \begin{itemize}
      \item also constrained using the \texttt{nValues} constraint
      \end{itemize}
    \end{itemize}
  \end{block}
  \begin{block}{Miscellaneous}
    \begin{itemize}
    \item \texttt{clauseAssignments} are sorted.
    \item If $\texttt{clauseAssignments}[i-1] = \texttt{clauseAssignments}[i]$,
      \begin{itemize}
      \item then $\texttt{clause}[i-1] \preceq \texttt{clause}[i]$.
      \end{itemize}
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Clauses}
  \begin{block}{A clause is defined by...}
    \begin{itemize}
    \item \texttt{IntVar[] treeStructure}
      \begin{itemize}
      \item $\texttt{treeStructure}[i] = i$: the $i$-th node is a root.
      \item $\texttt{treeStructure}[i] = j$: the $i$-th node's parent is node $j$.
      \end{itemize}
    \item \texttt{IntVar[] treeValues}: $\neg$, $\land$, $\lor$, $\top$, and any
      predefined predicates with variables.
    \end{itemize}
  \end{block}
  \begin{block}{Auxiliary variables}
    \begin{itemize}
    \item $\texttt{numNodes}, \texttt{numTrees} \in \{ 1, \dots, \texttt{maxNumNodes} \}$
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Clause constraints}
  \begin{itemize}
  \item \texttt{treeStructure} represents \texttt{numTrees} trees.
  \item $\texttt{treeStructure}[0] = 0$
  \item $\texttt{numTrees} + \texttt{numNodes} = \texttt{maxNumNodes} + 1$
  \item \texttt{treeStructure} is sorted
  \item For $i = 0, \dots, \texttt{maxNumNodes} - 1$,
    \begin{itemize}
    \item If $\texttt{numNodes} \le i$,
    \item then $\texttt{treeStructure}[i] = i$ and $\texttt{treeValues}[i] = \top$,
    \item else $\texttt{treeStructure}[i] < \texttt{numNodes}$.
    \item has 0 children $\iff$ $\texttt{treeValues}[i]$ is a predicate
    \item has 1 child $\iff$ $\texttt{treeValues}[i] = \neg$
    \item has $>1$ child $\iff$ $\texttt{treeValues}[i] \in \{ \land, \lor \}$
    \item $\texttt{treeStructure}[i] \ne i \implies \texttt{treeValues}[i] \ne \top$
    \end{itemize}
  \item If the clause should be disabled, $\texttt{numNodes} = 1$ and
    $\texttt{treeValues}[0] = \top$.
  \end{itemize}
\end{frame}

\begin{frame}
  \begin{block}{Adjacency matrix representation}
    $A[i][j] = 0 \iff \nexists k: \texttt{clauseAssignments}[k] = j$ and $i
    \in \texttt{clauses}[k].\texttt{treeValues}$
  \end{block}
  \begin{block}{New constraints}
    \begin{itemize}
    \item No (negative) cycles
      \begin{itemize}
      \item No clever propagation, just entailment checking.
      \end{itemize}
    \item Independence. Propagation:
      \begin{itemize}
      \item Two types of dependencies: determined and
        one-undetermined-edge-away-from-being-determined.
      \item Look up the dependencies of both predicates. For each pair of
        matching dependencies:
        \begin{itemize}
        \item If both are determined, fail.
        \item If one is determined, the selected edge of the other must not
          exist.
        \end{itemize}
      \end{itemize}
    \item Conditional independence
      \begin{itemize}
      \item Same propagation, but with a `filter' that masks out the expression
        that the independence is conditioned on.
      \end{itemize}
    \end{itemize}
  \end{block}
\end{frame}

\end{document}

### 2020-07-22 scripts/analyse_model.R

@@ -5,7 +5,6 @@ library(ggrepel)
 library(RColorBrewer)
 
 # This is all for the runtime data of the CP model
-
 df <- read.csv("../data/runtime.csv", header = FALSE, sep = ";", skip = 1)
 df <- df[, colSums(is.na(df)) < nrow(df)]
 names(df) <- c("numPredicates", "maxArity", "numVariables", "numConstants", "numAdditionalClauses", "numIndependentPairs", "maxNumNodes",
@@ -26,7 +25,7 @@ big <- df[df$numPredicates == 8, ]
 #colourCount = length(unique(big$numIndependentPairs))
 #getPalette = colorRampPalette(brewer.pal(9, "BuPu"))
 # fill = getPalette(colourCount)
-tikz(file = "../text/paper2/phase_transition.tex", width = 4.8, height = 1.8)
+tikz(file = "../paper/phase_transition.tex", width = 4.8, height = 1.8)
 ggplot(big, aes(factor(numIndependentPairs), nodes, group = numIndependentPairs)) +
   geom_boxplot(outlier.shape = NA, fill = "#e0ecf4") +
   coord_trans(y = "log10", limy = c(100, quantile(big$nodes, 0.91))) +
@@ -121,17 +120,32 @@ for (Variable in factors) {
 effects$label <- ifelse(effects$Value == 8, sapply(as.character(effects$Variable), mytolatex), "")
 effects$aritylabel[effects$Variable == "maxArity" & effects$Value == 4] <- "$\\mathcal{M}_{\\mathcal{A}}$"
 
-tikz(file = "../text/paper2/impact.tex", width = 2.4, height = 1.8)
+# Paper version
+tikz(file = "../paper/impact.tex", width = 2.4, height = 1.8)
 ggplot(effects, aes(Value, mean, color = factor(Variable))) +
   geom_line(aes(linetype = factor(Variable))) +
   scale_x_continuous(trans = "log2", limits = c(1, 10)) +
   ylab("Mean number of nodes") +
   geom_label_repel(aes(label = label, size = 1), nudge_x = 1, segment.color = "transparent", box.padding = 0.1) +
   geom_label_repel(aes(label = aritylabel, size = 1), segment.color = "transparent", nudge_y = 300) +
-#  theme_set(theme_minimal(base_size = 7)) +
   xlab("The value of each parameter") +
   scale_color_brewer(palette = "Dark2") +
   scale_size_area(max_size = 2) +
   theme_bw() +
   theme(legend.position = "none")
+dev.off()
+
[…]

### 2020-07-22 scripts/analyse_problog.R

@@ -1,13 +1,14 @@
 require(reshape2)
 require(ggplot2)
-require(dplyr)
 require(gridExtra)
 require(scales)
 require(grid)
-require(tidyr)
 require(tikzDevice)
-require(tidyverse)
+
 require(plyr)
+require(tidyr)
+require(tidyverse)
+require(dplyr)
 
 only_relevant_columns <- c("number.of.predicates", "number.of.variables",
                            "maximum.number.of.nodes", "maximum.arity",
@@ -140,7 +141,7 @@ plot <- function(var.name, c, s, scale = F, dots = T, legend = F, smooth = F,
 }
 
 # This might cause more questions than answer
-tikz(file = "../text/paper2/algorithms.tex", width = 4.8, height = 4.8, standAlone = T)
+tikz(file = "../paper/algorithms.tex", width = 4.8, height = 4.8, standAlone = T)
 p1 <- plot("number.of.predicates", combined, summarised, legend = T)
 legend <- get_legend(p1)
 grid.arrange(plot("number.of.predicates", combined, summarised),
@@ -180,8 +181,7 @@ summarised2 <- combined2 %>% group_by(variable, value, Algorithm) %>%
   summarize(mean.time = mean(Total.time), sd.time = sd(Total.time))
 summary <- rbind(summarised2[summarised2$variable %in% c("proportion.independent.pairs", "Total.time"),],
                  summarised[summarised$variable %in% c("number.of.facts", "Total.time"),])
-summary$variable <- factor(summary$variable, levels = c("number.of.facts", "proportion.independent.pairs"),
-                           labels = c("The number of facts ($\\times 10^3$)", "Proportion of independent pairs"))
+
 
 # ===================== Camera-ready ================================
 
@@ -198,11 +198,28 @@ plot2 <- function(df, column.names, df2 = NULL, column.names2 = NULL, factors = 
     theme_bw()
 }
 
-tikz(file = "../text/paper2/bars.tex", width = 2.4, height = 1.8)
+tikz(file = "../paper/bars.tex", width = 2.4, height = 1.8)
 plot2(combined2, c("maximum.arity", "proportion.probabilistic", "Total.time"))
 dev.off()
 
-tikz(file = "../text/paper2/line_plots.tex", width = 4.8, height = 1.8)
+# Paper version
[…]

### 2020-07-23 talk/talk.tex
Numbers of programs per paper

@@
 \usepackage{tikz}
+\usepackage[style=authoryear]{biblatex}
+\usepackage{empheq}
+
+\usetikzlibrary{decorations.pathreplacing}
+\tikzstyle{every picture}+=[remember picture]
 
@@
 \beamertemplatenavigationsymbolsempty
+
+\DeclareMathOperator{\ifff}{:-}
+\DeclareMathOperator{\prob}{::}
+
+\definecolor{predicate}{HTML}{1b9e77}
+\definecolor{probability}{HTML}{e7298a}
+\definecolor{variable}{HTML}{d95f02}
+\definecolor{constant}{HTML}{7570b3}
+\definecolor{color5}{HTML}{66a61e}
+\definecolor{color6}{HTML}{e6ab02}
+
+\addbibresource{talk.bib}
 
@@
 
-% TODO: examples of programs (actually introduce what they are about)
+% width: 4.2679148611112
+% height: 3.5575922222223
 
-% TODO: clauses as trees
+\begin{frame}{Probabilistic Logic Programs (\textsc{ProbLog})}
+  \begin{block}{Smokers (\cite{DBLP:conf/ilp/DomingosKLPRS08,DBLP:journals/tplp/FierensBRSGTJR15})}
+    \vspace*{-\baselineskip}\setlength\belowdisplayshortskip{0pt}
+    \begin{align*}
+      \textcolor{probability}{0.2} \prob &\textcolor{predicate}{\mathtt{stress}}(\textcolor{variable}{\mathsf{P}}) \ifff \textcolor{predicate}{\mathtt{person}}(\textcolor{variable}{\mathsf{P}}). \\
+      \textcolor{probability}{0.3} \prob &\textcolor{predicate}{\mathtt{influences}}(\textcolor{variable}{\mathsf{P}_1}, \textcolor{variable}{\mathsf{P}_2}) \ifff \textcolor{predicate}{\mathtt{friend}}(\textcolor{variable}{\mathsf{P}_1}, \textcolor{variable}{\mathsf{P}_2}).
+\\
+      \textcolor{probability}{0.1} \prob &\textcolor{predicate}{\mathtt{cancer\_spont}}(\textcolor{variable}{\mathsf{P}}) \ifff \textcolor{predicate}{\mathtt{person}}(\textcolor{variable}{\mathsf{P}}).
+\\
+      \textcolor{probability}{0.3} \prob &\textcolor{predicate}{\mathtt{cancer\_smoke}}(\textcolor{variable}{\mathsf{P}}) \ifff \textcolor{predicate}{\mathtt{person}}(\textcolor{variable}{\mathsf{P}}).
+\\
+                                         &\textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{X}}) \ifff \textcolor{predicate}{\mathtt{stress}}(\textcolor{variable}{\mathsf{X}}). \\
+                                         &\textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{X}}) \ifff \textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{Y}}), \textcolor{predicate}{\mathtt{influences}}(\textcolor{variable}{\mathsf{Y}}, \textcolor{variable}{\mathsf{X}}).
+\\
+                                         &\textcolor{predicate}{\mathtt{cancer}}(\textcolor{variable}{\mathsf{P}}) \ifff \textcolor{predicate}{\mathtt{cancer\_spont}}(\textcolor{variable}{\mathsf{P}}).
+\\
+                                         &\textcolor{predicate}{\mathtt{cancer}}(\textcolor{variable}{\mathsf{P}}) \ifff \textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{P}}), \textcolor{predicate}{\mathtt{cancer\_smoke}}(\textcolor{variable}{\mathsf{P}}).
+\\
+                                         &\textcolor{predicate}{\mathtt{person}}(\textcolor{constant}{\mathit{michelle}}). \\
+                                         &\textcolor{predicate}{\mathtt{person}}(\textcolor{constant}{\mathit{timothy}}). \\
+                                         &\textcolor{predicate}{\mathtt{friend}}(\textcolor{constant}{\mathit{timothy}}, \textcolor{constant}{\mathit{michelle}}).
+    \end{align*}
+  \end{block}
+\end{frame}
+
+\begin{frame}{How Many Programs Are Used to Test Algorithms?}
+  \begin{columns}
+    \begin{column}{0.5\textwidth}
+      \pause
+      \fbox{
+        \begin{tikzpicture}
+          \node[inner sep = 0pt] (a) {\includegraphics[width=\textwidth]{inference3.png}};
+          \node[anchor=center] at (a.center) {\Huge\alert{4}};
+        \end{tikzpicture}
+      }
+      \pause
+      \fbox{
+        \begin{tikzpicture}
+          \node[inner sep = 0pt] (a) {\includegraphics[width=\textwidth]{inference8.png}};
+          \node[anchor=center] at (a.center) {\Huge\alert{3}};
+        \end{tikzpicture}
+      }
+      \pause
+      \fbox{
+        \begin{tikzpicture}
+          \node[inner sep = 0pt] (a) {\includegraphics[width=\textwidth]{inference7.png}};
+          \node[anchor=center] at (a.center) {\Huge\alert{1}};
+        \end{tikzpicture}
+      }
+    \end{column}
+    \begin{column}{0.5\textwidth}
+      \pause
+      \fbox{
+        \begin{tikzpicture}
+          \node[inner sep = 0pt] (a) {\includegraphics[width=\textwidth]{inference6.png}};
+          \node[anchor=center] at (a.center) {\Huge\alert{1}};
+        \end{tikzpicture}
+      }
+      \pause
+      \fbox{
+        \begin{tikzpicture}
+          \node[inner sep = 0pt] (a) {\includegraphics[width=\textwidth]{inference2.png}};
+          \node[anchor=center] at (a.center) {\Huge\alert{1}};
+        \end{tikzpicture}
+      }
+      \pause
+      \fbox{
+        \begin{tikzpicture}
+          \node[inner sep = 0pt] (a) {\includegraphics[width=\textwidth]{inference1.png}};
+          \node[anchor=center] at (a.center) {\Huge\alert{2}};
+        \end{tikzpicture}
+      }
+    \end{column}
+  \end{columns}
+\end{frame}
+
+% TODO: real-world applications of problog or other PLP languages (maybe tease
+% people with DeepProbLog?)
+% TODO: overview inference algorithms
+% TODO: have a slide with all the inference papers and numbers of programs
+
+\begin{frame}{What Characterises a (Probabilistic) Logic Program?}
+  \begin{columns}
+    \hspace*{-0.7cm}\begin{column}{0.75\textwidth}
+      \begin{empheq}[left =\onslide<6->{\color{color5}\empheqlbrace}]{equation}
+        \begin{align*}
+      \textcolor<5->{probability}{0.2} \prob &\textcolor<2->{predicate}{\mathtt{stress}}(\textcolor<3->{variable}{\mathsf{P}}) \ifff \textcolor<2->{predicate}{\mathtt{person}}(\textcolor<3->{variable}{\mathsf{P}}).
+\\
+      \textcolor<5->{probability}{0.3} \prob &\textcolor<2->{predicate}{\mathtt{influences}}(\textcolor<3->{variable}{\mathsf{P}_1}, \textcolor<3->{variable}{\mathsf{P}_2}) \ifff \textcolor<2->{predicate}{\mathtt{friend}}(\textcolor<3->{variable}{\mathsf{P}_1}, \textcolor<3->{variable}{\mathsf{P}_2}).
+\\
+      \textcolor<5->{probability}{0.1} \prob &\textcolor<2->{predicate}{\mathtt{cancer\_spont}}(\textcolor<3->{variable}{\mathsf{P}}) \ifff \textcolor<2->{predicate}{\mathtt{person}}(\textcolor<3->{variable}{\mathsf{P}}).
+\\
+      \textcolor<5->{probability}{0.3} \prob &\textcolor<2->{predicate}{\mathtt{cancer\_smoke}}(\textcolor<3->{variable}{\mathsf{P}}) \ifff \textcolor<2->{predicate}{\mathtt{person}}(\textcolor<3->{variable}{\mathsf{P}}).
+\\
+                                         &\textcolor<2->{predicate}{\mathtt{smokes}}(\textcolor<3->{variable}{\mathsf{X}}) \ifff \textcolor<2->{predicate}{\mathtt{stress}}(\textcolor<3->{variable}{\mathsf{X}}).
+\\
+                                         &\textcolor<2->{predicate}{\mathtt{smokes}}(\textcolor<3->{variable}{\mathsf{X}}) \ifff \textcolor<2->{predicate}{\mathtt{smokes}}(\textcolor<3->{variable}{\mathsf{Y}}), \textcolor<2->{predicate}{\mathtt{influences}}(\textcolor<3->{variable}{\mathsf{Y}}, \textcolor<3->{variable}{\mathsf{X}}).
+\\
+                                         &\textcolor<2->{predicate}{\mathtt{cancer}}(\textcolor<3->{variable}{\mathsf{P}}) \ifff \textcolor<2->{predicate}{\mathtt{cancer\_spont}}(\textcolor<3->{variable}{\mathsf{P}}).
+\\
+                                         &\textcolor<2->{predicate}{\mathtt{cancer}}(\textcolor<3->{variable}{\mathsf{P}}) \ifff \tikz \coordinate (start);\textcolor<2->{predicate}{\mathtt{smokes}}(\textcolor<3->{variable}{\mathsf{P}}), \textcolor<2->{predicate}{\mathtt{cancer\_smoke}}(\textcolor<3->{variable}{\mathsf{P}})\tikz \coordinate (end);.
+\\
+                                         &\textcolor<2->{predicate}{\mathtt{person}}(\textcolor<4->{constant}{\mathit{michelle}}). \\
+                                         &\textcolor<2->{predicate}{\mathtt{person}}(\textcolor<4->{constant}{\mathit{timothy}}). \\
+                                         &\textcolor<2->{predicate}{\mathtt{friend}}(\textcolor<4->{constant}{\mathit{timothy}}, \textcolor<4->{constant}{\mathit{michelle}}).
+        \end{align*}
+      \end{empheq}
+    \end{column}
+    \begin{column}{0.25\textwidth}
+      \begin{itemize}
+      \item[\textcolor{predicate}{\textbullet}]<2-> predicates, arities
+      \item[\textcolor{variable}{\textbullet}]<3-> variables
+      \item[\textcolor{constant}{\textbullet}]<4-> constants
+      \item[\textcolor{probability}{\textbullet}]<5-> probabilities
+      \item[\textcolor{color5}{\textbullet}]<6-> length
+      \item[\textcolor{color6}{\textbullet}]<7-> complexity
+      \end{itemize}
+    \end{column}
+  \end{columns}
+  \onslide<7->{
+    \begin{tikzpicture}[overlay]
+      \draw [decorate,decoration={brace,amplitude=10pt,mirror},color=color6] (start) -- (end);
+    \end{tikzpicture}
+  }
+\end{frame}
+
+% TODO: describe clauses as trees (showing an example of a clause)
+% TODO: describe the rest of the model
+% TODO: add a link to GitHub at the end
 
@@
 
-% width: 4.2679148611112
-% height: 3.5575922222223
+% ===============================================================
 

### 2020-07-24 talk/talk.tex
Applications
Diagrams

@@
 
+\usetikzlibrary{arrows}
+\usetikzlibrary{calc}
 \usetikzlibrary{decorations.pathreplacing}
+\usetikzlibrary{positioning}
+\usetikzlibrary{shapes}
 \tikzstyle{every picture}+=[remember picture]
@@
 \begin{frame}{Probabilistic Logic Programs (\textsc{ProbLog})}
-  \begin{block}{Smokers (\cite{DBLP:conf/ilp/DomingosKLPRS08,DBLP:journals/tplp/FierensBRSGTJR15})}
+  \begin{block}{The Smokers Network (\cite{DBLP:conf/ilp/DomingosKLPRS08})}
     \vspace*{-\baselineskip}\setlength\belowdisplayshortskip{0pt}
@@
   \end{block}
+\end{frame}
+
+\begin{frame}{Applications}
+  \begin{columns}[b]
+    \begin{column}{0.5\textwidth}
+      \includegraphics[width=\textwidth]{application1.png}
+      {\small \cite{DBLP:conf/icra/MoldovanMOSR12}}
+    \end{column}
+    \begin{column}{0.5\textwidth}
+      \includegraphics[width=\textwidth]{application3.png}
+      {\small \cite{DBLP:conf/ijcai/DriesKDBR17}}
+    \end{column}
+  \end{columns}
+  \vfill
+  \begin{columns}[b]
+    \begin{column}{0.5\textwidth}
+      \includegraphics[width=\textwidth]{application2.png}
+      {\small \cite{DBLP:conf/ilp/Corte-RealD017}}
+    \end{column}
+    \begin{column}{0.5\textwidth}
+      \includegraphics[width=\textwidth]{application4.png}
+      {\small \cite{de2013phenetic}}
+    \end{column}
+  \end{columns}
+\end{frame}
+
+% TODO: finish the explanation
+\begin{frame}{Inference Algorithms and Knowledge Compilation Maps}
+  \begin{description}
+  \item[NNF] negation normal form
+  \item[d-DNNF] deterministic decomposable negation normal form
+  \item[BDD] binary decision diagrams
+  \item[SDD] sentential decision diagrams
+  \item[$k$-Best] ???
+  \end{description}
+\end{frame}
+
+\begin{frame}{Example Diagrams for $C \land (A \lor \neg B)$}
+  \vspace{-1em}
+  % \begin{tikzpicture}
+  %   \node[draw,circle] {$\land$}
+  %   child {node[draw,rectangle] {$C$}}
+  %   child {node[draw,circle] {$\lor$}
+  %     child {node[draw,rectangle] {$A$}}
+  %     child {node[draw,rectangle] {$\neg B$}
+  %     }
+  %   };
+  % \end{tikzpicture}
+  \begin{columns}[b]
+    \begin{column}{0.33\textwidth}
+      \begin{figure}
+        \begin{tikzpicture}
+          \node[draw,circle] (A) {$A$}
+          child {edge from parent[draw=none]}
+          child {node[draw,circle] (B) {$B$} edge from parent[dashed]
+            child {node[draw,circle,solid] (C) {$C$} edge from parent[dashed]
+              child {node[draw,rectangle,solid] {$1$} edge from parent[solid]}
+              child {node[draw,rectangle,solid] (0) {$0$}}
+            }
+            child {edge from parent[draw=none]}
+          };
+          \draw (A) -- (C);
+          \draw (B) -- (0);
+        \end{tikzpicture}
+        \caption{BDD}
+      \end{figure}
+    \end{column}
+    \begin{column}{0.34\textwidth}
+      \begin{figure}
+        \begin{tikzpicture}
+          \node[draw,circle] {$\land$}
+          child {node[draw,circle] {$\lor$}
+            child {node[draw,circle] (parent) {$\land$}
+              child {node[draw,rectangle] {$B$}}
+              child {edge from parent[draw=none]}
+            }
+            child {node[draw,circle] {$\land$}
+              child {node[draw,circle] {$\lor$}
+                child {node[draw,rectangle] (A) {$A$}}
+                child {node[draw,rectangle] {$\neg A$}}
+              }
+              child {node[draw,rectangle] {$\neg B$}}
+            }
+          }
+          child {node[draw,rectangle] {$C$}};
+          \draw (parent) -- (A);
+        \end{tikzpicture}
+        \caption{d-DNNF}
+      \end{figure}
+    \end{column}
+    \begin{column}{0.33\textwidth}
+      \begin{figure}
+        \begin{tikzpicture}
+          \tikzset{
+            mysplit/.style={
+              draw,
+              rectangle,
+              rectangle split,
+              rectangle split horizontal,
+              rectangle split parts=2
+            }
+          }
+          \node[draw,circle] {$1$}
+          child {node[mysplit] (bullet) {
+              \nodepart{one} $\neg A$
+              \nodepart{two}
+            }
+            child {node[draw,circle] (3) {$3$} edge from parent[draw=none]
+              child {node[mysplit] {
+                  \nodepart{one} $\neg B$
+                  \nodepart{two} $C$
+                }
+              }
+              child {node[mysplit] {
+                  \nodepart{one} $B$
+                  \nodepart{two} $0$
+                }
+              }
+            }
+          }
+          child {node[mysplit] {
+              \nodepart{one} $A$
+              \nodepart{two} $C$
+            }};
+          \draw[*-] let \p1 = (bullet.two), \p2 = (bullet.center) in ({\x1 + 2.5},{\y2 + 2}) -- (3);
+        \end{tikzpicture}
+        \caption{SDD}
+      \end{figure}
+    \end{column}
+  \end{columns}
 \end{frame}
@@
 \end{frame}
-
-% TODO: real-world applications of problog or other PLP languages (maybe tease
-% people with DeepProbLog?)
-% TODO: overview inference algorithms
-% TODO: have a slide with all the inference papers and numbers of programs
 

### 2020-07-25 talk/talk.tex
A few more slides

@@
 \usetikzlibrary{arrows}
+\usetikzlibrary{arrows.meta}
 \usetikzlibrary{calc}
@@
 
+\newcommand\independent{\protect\mathpalette{\protect\independenT}{\perp}}
+\def\independenT#1#2{\mathrel{\rlap{$#1#2$}\mkern2mu{#1#2}}}
+
 \DeclareMathOperator{\ifff}{:-}
 \DeclareMathOperator{\prob}{::}
+\DeclareMathOperator{\negg}{\backslash+}
 
@@
 \begin{frame}{Probabilistic Logic Programs (\textsc{ProbLog})}
-  \begin{block}{The Smokers Network (\cite{DBLP:conf/ilp/DomingosKLPRS08})}
+  \begin{block}{``Smokers'' (\cite{DBLP:conf/ilp/DomingosKLPRS08,DBLP:journals/tplp/FierensBRSGTJR15})}
     \vspace*{-\baselineskip}\setlength\belowdisplayshortskip{0pt}
@@
     \begin{column}{0.5\textwidth}
+      \centering
       \includegraphics[width=\textwidth]{application1.png}
@@
     \begin{column}{0.5\textwidth}
+      \centering
       \includegraphics[width=\textwidth]{application3.png}
@@
     \begin{column}{0.5\textwidth}
+      \centering
       \includegraphics[width=\textwidth]{application2.png}
@@
     \begin{column}{0.5\textwidth}
+      \centering
       \includegraphics[width=\textwidth]{application4.png}
@@
 
-% TODO: finish the explanation
 \begin{frame}{Inference Algorithms and Knowledge Compilation Maps}
@@
   \item[SDD] sentential decision diagrams
-  \item[$k$-Best] ???
+  \item[$k$-Best] only use the $k$ most probable proofs
   \end{description}
@@
       \begin{figure}
+      \centering
         \begin{tikzpicture}
@@
       \begin{figure}
+        \centering
         \begin{tikzpicture}
@@
 
-\begin{frame}{What Characterises a (Probabilistic) Logic Program?}
+\begin{frame}{What Characterizes a (Probabilistic) Logic Program?}
   \begin{columns}
@@
 
-% TODO: describe clauses as trees (showing an example of a clause)
-% TODO: describe the rest of the model
-% TODO: add a link to GitHub at the end
+\begin{frame}{Clauses As Trees}
+  \[
+    \neg \textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{X}})
+    \lor (\textcolor{predicate}{\mathtt{q}}(\textcolor{variable}{\mathsf{X}})
+    \land \textcolor{predicate}{\mathtt{r}}(\textcolor{variable}{\mathsf{X}}))
+  \]
+  \vfill
+  \begin{columns}
+    \begin{column}{0.5\textwidth}
+      \pause
+      \centering
+      \begin{tikzpicture}[level 1/.style={sibling distance=30mm},level 2/.style={sibling distance=15mm}]
+        \node[draw,circle] {$\lor$}
+        child {node[draw,circle] {$\neg$}
+          child {node[draw,rectangle] {$\textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{X}})$}}
+        }
+        child {node[draw,circle] {$\land$}
+          child {node[draw,rectangle] {$\textcolor{predicate}{\mathtt{q}}(\textcolor{variable}{\mathsf{X}})$}}
+          child {node[draw,rectangle] {$\textcolor{predicate}{\mathtt{r}}(\textcolor{variable}{\mathsf{X}})$}}
+        };
+      \end{tikzpicture}
+    \end{column}
+    \begin{column}{0.5\textwidth}
+      \pause
+      \centering
+      \begin{tabular}{|c|c|c|c|c|c|}
+        \hline
+        0 & 0 & 0 & 1 & 2 & 2 \\
+        \hline
+        $\lor$ & $\neg$ & $\land$ & $\textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{X}})$ & $\textcolor{predicate}{\mathtt{q}}(\textcolor{variable}{\mathsf{X}})$ & $\textcolor{predicate}{\mathtt{r}}(\textcolor{variable}{\mathsf{X}})$ \\
+        \hline
+      \end{tabular}
+    \end{column}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{Predicate Dependency Graph}
+  \centering
+  \begin{tikzpicture}
+    \node[draw,ellipse] (friend) {\textcolor{predicate}{friend}};
+    \node[draw,ellipse,right=of friend] (influences) {\textcolor{predicate}{influences}};
+    \node[draw,ellipse,below=of influences] (stress) {\textcolor{predicate}{stress}};
+    \node[draw,ellipse,below=of stress] (spont) {\textcolor{predicate}{cancer\_spont}};
+    \node[draw,ellipse,below=of spont] (smoke) {\textcolor{predicate}{cancer\_smoke}};
+    \node[draw,ellipse,left=of spont] (person) {\textcolor{predicate}{person}};
+    \node[draw,ellipse,right=of spont] (cancer) {\textcolor{predicate}{cancer}};
+    \node[draw,ellipse,above=of cancer] (smokes) {\textcolor{predicate}{smokes}};
+    \draw[-{Latex[length=2mm]}] (friend) -- (influences);
+    \draw[-{Latex[length=2mm]}] (influences) -- (smokes);
+    \draw[-{Latex[length=2mm]}] (smokes) -- (cancer);
+    \draw[-{Latex[length=2mm]}] (stress) -- (smokes);
+    \draw[-{Latex[length=2mm]}] (spont) -- (cancer);
+    \draw[-{Latex[length=2mm]}] (smoke) -- (cancer);
+    \draw[-{Latex[length=2mm]}] (person) -- (stress);
+    \draw[-{Latex[length=2mm]}] (person) -- (spont);
+    \draw[-{Latex[length=2mm]}] (person) -- (smoke);
+  \end{tikzpicture}
+\end{frame}
+
+\begin{frame}{Independence: $\textcolor{predicate}{\mathrm{influences}}
+    \independent \textcolor{predicate}{\mathrm{stress}}$}
+  \centering
+  \begin{tikzpicture}
+    \node[draw,ellipse] (friend) {\textcolor{predicate}{friend}};
+    \node[draw,ellipse,right=of friend] (influences) {\textcolor{predicate}{influences}};
+    \node[draw,ellipse,below=of influences] (stress) {\textcolor{predicate}{stress}};
+    \node[draw,ellipse,below=of stress] (spont) {\textcolor{predicate}{cancer\_spont}};
+    \node[draw,ellipse,below=of spont] (smoke) {\textcolor{predicate}{cancer\_smoke}};
+    \node[draw,ellipse,left=of spont] (person) {\textcolor{predicate}{person}};
+    \node[draw,ellipse,right=of spont] (cancer) {\textcolor{predicate}{cancer}};
+    \node[draw,ellipse,above=of cancer] (smokes) {\textcolor{predicate}{smokes}};
+    \draw[-{Latex[length=2mm]}] (friend) -- (influences);
+    \draw[-{Latex[length=2mm]}] (influences) -- (smokes);
+    \draw[-{Latex[length=2mm]}] (smokes) -- (cancer);
+    \draw[-{Latex[length=2mm]}] (stress) -- (smokes);
+    \draw[-{Latex[length=2mm]}] (spont) -- (cancer);
+    \draw[-{Latex[length=2mm]}] (smoke) -- (cancer);
+    \draw[-{Latex[length=2mm]}] (person) -- (stress);
+    \draw[-{Latex[length=2mm]}] (person) -- (spont);
+    \draw[-{Latex[length=2mm]}] (person) -- (smoke);
+    \draw<2->[-{Latex[length=2mm]}] (influences) edge[draw=red,bend left=15] (stress);
+    \draw<2->[-{Latex[length=2mm]}] (stress) edge[draw=red,bend left=15] (influences);
+    \draw<2->[-{Latex[length=2mm]}] (stress) edge[draw=red,bend left=15] (friend);
+    \draw<2->[-{Latex[length=2mm]}] (friend) edge[draw=red,bend left=15] (stress);
+  \end{tikzpicture}
+\end{frame}
+
+\begin{frame}{Stratification and Negative Cycles}
+  \centering
+  \begin{tikzpicture}
+    \node[draw,ellipse] (friend) {\textcolor{predicate}{friend}};
+    \node[draw,ellipse,right=of friend] (influences) {\textcolor{predicate}{influences}};
+    \node[draw,ellipse,below=of influences] (stress) {\textcolor{predicate}{stress}};
+    \node[draw,ellipse,below=of stress] (spont) {\textcolor{predicate}{cancer\_spont}};
+    \node[draw,ellipse,below=of spont] (smoke) {\textcolor{predicate}{cancer\_smoke}};
+    \node[draw,ellipse,left=of spont] (person) {\textcolor{predicate}{person}};
+    \node[draw,ellipse,right=of spont] (cancer) {\textcolor{predicate}{cancer}};
+    \node[draw,ellipse,above=of cancer] (smokes) {\textcolor{predicate}{smokes}};
+    \draw[-{Latex[length=2mm]}] (friend) -- (influences);
+    \draw[-{Latex[length=2mm]}] (influences) -- (smokes);
+    \draw[-{Latex[length=2mm]}] (smokes) -- (cancer);
+    \draw[-{Latex[length=2mm]}] (stress) -- (smokes);
+    \draw[-{Latex[length=2mm]}] (spont) -- (cancer);
+    \draw[-{Latex[length=2mm]}] (smoke) -- (cancer);
+    \draw[-{Latex[length=2mm]}] (person) -- (stress);
+    \draw[-{Latex[length=2mm]}] (person) -- (spont);
+    \draw[-{Latex[length=2mm]}] (person) -- (smoke);
+    \draw<2->[-{Latex[length=2mm]},draw=red] (smokes) -- (friend);
+  \end{tikzpicture}
+  \[
+    \textcolor{probability}{0.1} \prob
+    \textcolor{predicate}{\mathtt{friend}}(\textcolor{variable}{\mathsf{X}},
+    \textcolor{variable}{\mathsf{Y}}) \ifff
+    \negg\textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{Y}}).
+  \]
+\end{frame}
 
@@
   \input{../paper/bars.tex}
+\end{frame}
+
+% TODO: add a link to GitHub at the end
+\begin{frame}{Summary}
+%  \begin{itemize}
+%  \end{itemize}
 \end{frame}

### 2020-08-09 conference_talk/talk.tex
A longer version of the talk

--- 2020-07-25 talk/talk.tex
@@
 \end{frame}
-
-% width: 4.2679148611112
-% height: 3.5575922222223
 
@@
 
-% TODO: add a link to GitHub at the end
+% TODO: finish the slide
 \begin{frame}{Summary}
-%  \begin{itemize}
-%  \end{itemize}
-\end{frame}
-
-% ===============================================================
-
-\begin{frame}{Overview}
-  \begin{block}{General parameters}
   \begin{itemize}
-    \item maximum number of solutions
-    \item \texttt{maxNumNodes} (in the tree representation of a clause)
-    \item list of predicates with their variables
-    \item maximum number of clauses
-    \item option to forbid all cycles or just negative cycles
-    \item list of probabilities that are randomly assigned to clauses: $\{ 0.1,
-      0.2, \dots, 0.9, 1, 1, 1, 1, 1, 1 \}$
+  \item foo
+  \item bar
+  \item baz
   \end{itemize}
-  \end{block}
-  \begin{block}{Decision variables}
-    \begin{itemize}
-    \item \texttt{IntVar[] clauseAssignments}: a predicate or disabled
-    \item \texttt{Clause[] clauses}
-    \end{itemize}
-  \end{block}
-\end{frame}
-
-\begin{frame}{Constraints}
-  \begin{block}{Each predicate should get at least one constraint}
-    \begin{itemize}
-    \item \texttt{numDisabledClauses}: defined by a \texttt{count} constraint
-    \item $\texttt{numDistinctValues} = \begin{cases}
-        \texttt{numPredicates} + 1 & \text{if } \texttt{numDisabledValues} > 0 \\
-        \texttt{numPredicates} & \text{otherwise.}
-      \end{cases}$
-      \begin{itemize}
-      \item also constrained using the \texttt{nValues} constraint
-      \end{itemize}
-    \end{itemize}
-  \end{block}
-  \begin{block}{Miscellaneous}
-    \begin{itemize}
-    \item \texttt{clauseAssignments} are sorted.
-    \item If $\texttt{clauseAssignments}[i-1] = \texttt{clauseAssignments}[i]$,
-      \begin{itemize}
-      \item then $\texttt{clause}[i-1] \preceq \texttt{clause}[i]$.
-      \end{itemize}
-    \end{itemize}
-  \end{block}
-\end{frame}
-
-\begin{frame}{Clauses}
-  \begin{block}{A clause is defined by...}
-    \begin{itemize}
-    \item \texttt{IntVar[] treeStructure}
-      \begin{itemize}
-      \item $\texttt{treeStructure}[i] = i$: the $i$-th node is a root.
-      \item $\texttt{treeStructure}[i] = j$: the $i$-th node's parent is node $j$.
-      \end{itemize}
-    \item \texttt{IntVar[] treeValues}: $\neg$, $\land$, $\lor$, $\top$, and any
-      predefined predicates with variables.
-    \end{itemize}
-  \end{block}
-  \begin{block}{Auxiliary variables}
-    \begin{itemize}
-    \item $\texttt{numNodes}, \texttt{numTrees} \in \{ 1, \dots, \texttt{maxNumNodes} \}$
-    \end{itemize}
-  \end{block}
-\end{frame}
-
-\begin{frame}{Clause constraints}
-  \begin{itemize}
-  \item \texttt{treeStructure} represents \texttt{numTrees} trees.
-  \item $\texttt{treeStructure}[0] = 0$
-  \item $\texttt{numTrees} + \texttt{numNodes} = \texttt{maxNumNodes} + 1$
-  \item \texttt{treeStructure} is sorted
-  \item For $i = 0, \dots, \texttt{maxNumNodes} - 1$,
-    \begin{itemize}
-    \item If $\texttt{numNodes} \le i$,
-    \item then $\texttt{treeStructure}[i] = i$ and $\texttt{treeValues}[i] = \top$,
-    \item else $\texttt{treeStructure}[i] < \texttt{numNodes}$.
-    \item has 0 children $\iff$ $\texttt{treeValues}[i]$ is a predicate
-    \item has 1 child $\iff$ $\texttt{treeValues}[i] = \neg$
-    \item has $>1$ child $\iff$ $\texttt{treeValues}[i] \in \{ \land, \lor \}$
-    \item $\texttt{treeStructure}[i] \ne i \implies \texttt{treeValues}[i] \ne \top$
-    \end{itemize}
-  \item If the clause should be disabled, $\texttt{numNodes} = 1$ and
-    $\texttt{treeValues}[0] = \top$.
-  \end{itemize}
-\end{frame}
-
-\begin{frame}
-  \begin{block}{Adjacency matrix representation}
-    $A[i][j] = 0 \iff \nexists k: \texttt{clauseAssignments}[k] = j$ and $i
-    \in \texttt{clauses}[k].\texttt{treeValues}$
-  \end{block}
-  \begin{block}{New constraints}
-    \begin{itemize}
-    \item No (negative) cycles
-      \begin{itemize}
-      \item No clever propagation, just entailment checking.
-      \end{itemize}
-    \item Independence. Propagation:
-      \begin{itemize}
-      \item Two types of dependencies: determined and
-        one-undetermined-edge-away-from-being-determined.
-      \item Look up the dependencies of both predicates. For each pair of
-        matching dependencies:
-        \begin{itemize}
-        \item If both are determined, fail.
-        \item If one is determined, the selected edge of the other must not
-          exist.
-        \end{itemize}
-      \end{itemize}
-    \item Conditional independence
-      \begin{itemize}
-      \item Same propagation, but with a `filter' that masks out the expression
-        that the independence is conditioned on.
-      \end{itemize}
-    \end{itemize}
+  \begin{block}{The implementation of the model is available at}
+    \url{https://github.com/dilkas/random-logic-programs}
   \end{block}

### 2020-08-09 seminar_talk/talk.tex
A longer version of the talk

--- 2020-07-25 talk/talk.tex
@@
 
-\author{\textbf{Paulius Dilkas}\inst{1} \and Vaishak Belle\inst{1,2}}
+\author{Paulius Dilkas}
 \title{Generating Random Logic Programs Using Constraint Programming}
-\date{CP 2020}
-\institute{\inst{1} University of Edinburgh, Edinburgh, UK \and \inst{2} Alan
-  Turing Institute, London, UK}
+\date{AIAI Seminar}
 
@@
 
+\begin{frame}{Inference}
+  \begin{minipage}[t][0.5\textheight]{\textwidth}
+    Let $a \oplus b = a + b - ab$.
+
+    \only<1>{
+      $\begin{aligned}[t]
+        \Pr[\textcolor{predicate}{\mathtt{cancer}}(\textcolor{constant}{\mathit{michelle}})]
+        &=
+        \Pr[\textcolor{predicate}{\mathtt{cancer\_spont}}(\textcolor{constant}{\mathit{michelle}})]
+        \\
+        &\oplus
+        \Pr[\textcolor{predicate}{\mathtt{smokes}}(\textcolor{constant}{\mathit{michelle}})]
+        \\
+        &\times
+        \Pr[\textcolor{predicate}{\mathtt{cancer\_smoke}}(\textcolor{constant}{\mathit{michelle}})]
+      \end{aligned}$
+    }
+    \only<2->{
+      $\Pr[\textcolor{predicate}{\mathtt{cancer}}(\textcolor{constant}{\mathit{michelle}})]
+      = \textcolor{probability}{0.1} \oplus \textcolor{probability}{0.3} \times
+      \Pr[\textcolor{predicate}{\mathtt{smokes}}(\textcolor{constant}{\mathit{michelle}})]$
+    }
+
+    \only<3>{
+      $\begin{aligned}[t]
+        \Pr[\textcolor{predicate}{\mathtt{smokes}}(\textcolor{constant}{\mathit{michelle}})]
+        &=
+        \Pr[\textcolor{predicate}{\mathtt{stress}}(\textcolor{constant}{\mathit{michelle}})]
+        \\
+        &\oplus
+        \Pr[\textcolor{predicate}{\mathtt{smokes}}(\textcolor{constant}{\mathit{timothy}})]
+        \\
+        &\times
+        \Pr[\textcolor{predicate}{\mathtt{influences}}(\textcolor{constant}{\mathit{timothy}},
+        \textcolor{constant}{\mathit{michelle}})]
+      \end{aligned}$
+    }
+    \only<4->{
+      $\Pr[\textcolor{predicate}{\mathtt{smokes}}(\textcolor{constant}{\mathit{michelle}})]
+      = \textcolor{probability}{0.2} \oplus \textcolor{probability}{0.3} \times
+      \Pr[\textcolor{predicate}{\mathtt{smokes}}(\textcolor{constant}{\mathit{timothy}})]$
+    }
+
+    \only<5->{
+      $\Pr[\textcolor{predicate}{\mathtt{smokes}}(\textcolor{constant}{\mathit{timothy}})]
+      =
+      \Pr[\textcolor{predicate}{\mathtt{stress}}(\textcolor{constant}{\mathit{timothy}})]
+      = \textcolor{probability}{0.2}$
+    }
+  \end{minipage}
+  \vfill
+  \begin{overprint}
+    \begin{onlyenv}<1>
+      \begin{empheq}[box=\fbox]{align*}
+        \textcolor{predicate}{\mathtt{cancer}}(\textcolor{variable}{\mathsf{P}})
+        &\ifff
+        \textcolor{predicate}{\mathtt{cancer\_spont}}(\textcolor{variable}{\mathsf{P}}).
+        \\
+        \textcolor{predicate}{\mathtt{cancer}}(\textcolor{variable}{\mathsf{P}})
+        &\ifff
+        \textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{P}}),
+        \textcolor{predicate}{\mathtt{cancer\_smoke}}(\textcolor{variable}{\mathsf{P}}).
+      \end{empheq}
+    \end{onlyenv}
+    \begin{onlyenv}<2>
+      \begin{empheq}[box=\fbox]{align*}
+        \textcolor{probability}{0.1} \prob
+        &\textcolor{predicate}{\mathtt{cancer\_spont}}(\textcolor{variable}{\mathsf{P}})
+        \ifff
+        \textcolor{predicate}{\mathtt{person}}(\textcolor{variable}{\mathsf{P}}).
+        \\
+        \textcolor{probability}{0.3} \prob
+        &\textcolor{predicate}{\mathtt{cancer\_smoke}}(\textcolor{variable}{\mathsf{P}})
+        \ifff
+        \textcolor{predicate}{\mathtt{person}}(\textcolor{variable}{\mathsf{P}}).
+      \end{empheq}
+    \end{onlyenv}
+    \begin{onlyenv}<3>
+      \begin{empheq}[box=\fbox]{align*}
+        \textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{X}})
+        &\ifff
+        \textcolor{predicate}{\mathtt{stress}}(\textcolor{variable}{\mathsf{X}}).
+        \\
+        \textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{X}})
+        &\ifff
+        \textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{Y}}),
+        \textcolor{predicate}{\mathtt{influences}}(\textcolor{variable}{\mathsf{Y}},
+        \textcolor{variable}{\mathsf{X}}).
+      \end{empheq}
+    \end{onlyenv}
+    \begin{onlyenv}<4>
+      \begin{empheq}[box=\fbox]{align*}
+        \textcolor{probability}{0.2} \prob &\textcolor{predicate}{\mathtt{stress}}(\textcolor{variable}{\mathsf{P}}) \ifff \textcolor{predicate}{\mathtt{person}}(\textcolor{variable}{\mathsf{P}}). \\
+        \textcolor{probability}{0.3} \prob &\textcolor{predicate}{\mathtt{influences}}(\textcolor{variable}{\mathsf{P}_1}, \textcolor{variable}{\mathsf{P}_2}) \ifff \textcolor{predicate}{\mathtt{friend}}(\textcolor{variable}{\mathsf{P}_1}, \textcolor{variable}{\mathsf{P}_2}).
+      \end{empheq}
+    \end{onlyenv}
+    \begin{onlyenv}<5>
+      \begin{empheq}[box=\fbox]{align*}
+        \textcolor{probability}{0.2} \prob &\textcolor{predicate}{\mathtt{stress}}(\textcolor{variable}{\mathsf{P}}) \ifff \textcolor{predicate}{\mathtt{person}}(\textcolor{variable}{\mathsf{P}}). \\
+        &\textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{X}}) \ifff \textcolor{predicate}{\mathtt{stress}}(\textcolor{variable}{\mathsf{X}}).
+      \end{empheq}
+    \end{onlyenv}
+  \end{overprint}
+\end{frame}
+% TODO: colours for numbers/probabilities
+
 \begin{frame}{Applications}
@@
 
+% TODO: what properties does d-DNNF ensure?
+% TODO: what about SDD?
+% TODO: explain how each of them works
 \begin{frame}{Inference Algorithms and Knowledge Compilation Maps}
@@
 \begin{frame}{Example Diagrams for $C \land (A \lor \neg B)$}
-  \vspace{-1em}
-  % \begin{tikzpicture}
-  %   \node[draw,circle] {$\land$}
-  %   child {node[draw,rectangle] {$C$}}
-  %   child {node[draw,circle] {$\lor$}
-  %     child {node[draw,rectangle] {$A$}}
-  %     child {node[draw,rectangle] {$\neg B$}
-  %     }
-  %   };
-  % \end{tikzpicture}
   \begin{columns}[b]
@@
         \centering
-        \begin{tikzpicture}
+        \begin{tikzpicture}[level distance=0.8cm]
+          \node[draw,circle] {$\land$}
+          child {node[draw,rectangle] {$C$}}
+          child {node[draw,circle] {$\lor$}
+            child {node[draw,rectangle] {$A$}}
+            child {node[draw,rectangle] {$\neg B$}
+            }
+          };
+        \end{tikzpicture}
+        \caption{NNF}
+      \end{figure}
+      \vspace{-1em}
+      \begin{figure}
+      \centering
+        \begin{tikzpicture}[level distance=0.8cm]
           \node[draw,circle] (A) {$A$}
@@
     \end{column}
-    \begin{column}{0.34\textwidth}
+    \begin{column}{0.33\textwidth}
       \begin{figure}
         \centering
-        \begin{tikzpicture}
+        \begin{tikzpicture}[level distance=0.8cm]
           \node[draw,circle] {$\land$}
@@
         \centering
-        \begin{tikzpicture}
+        \begin{tikzpicture}[level distance=0.8cm]
           \tikzset{
@@
         \caption{SDD}
+      \end{figure}
+      \vspace{-2em}
+      \begin{figure}
+      \centering
+      \begin{tikzpicture}[level distance=0.8cm]
+        \node[draw,circle] {$1$}
+        child {node[draw,circle] {$0$}
+          child {node[draw,rectangle] {$A$}}
+        }
+        child {node[draw,circle] {$3$}
+          child {node[draw,circle] {$2$}
+            child {node[draw,rectangle] {$B$}}
+          }
+          child {node[draw,circle] {$4$}
+            child {node[draw,rectangle] {$C$}}
+          }
+        };
+      \end{tikzpicture}
+      \caption{vtree}
       \end{figure}
@@
   \begin{columns}
-    \begin{column}{0.5\textwidth}
+    \begin{column}{0.4\textwidth}
       \pause
@@
     \end{column}
-    \begin{column}{0.5\textwidth}
+    \begin{column}{0.6\textwidth}
       \pause
       \centering
-      \begin{tabular}{|c|c|c|c|c|c|}
+      \begin{tabular}{|c|c|c|c|c|c|c|}
         \hline
-        0 & 0 & 0 & 1 & 2 & 2 \\
+        0 & 0 & 0 & 1 & 2 & 2 & 6 \\
         \hline
-        $\lor$ & $\neg$ & $\land$ & $\textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{X}})$ & $\textcolor{predicate}{\mathtt{q}}(\textcolor{variable}{\mathsf{X}})$ & $\textcolor{predicate}{\mathtt{r}}(\textcolor{variable}{\mathsf{X}})$ \\
+        $\lor$ & $\neg$ & $\land$ & $\textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{X}})$ & $\textcolor{predicate}{\mathtt{q}}(\textcolor{variable}{\mathsf{X}})$ & $\textcolor{predicate}{\mathtt{r}}(\textcolor{variable}{\mathsf{X}})$ & $\top$ \\
         \hline
@@
 
-% TODO: add a link to GitHub at the end
+% TODO: finish the slide
 \begin{frame}{Summary}
-%  \begin{itemize}
-%  \end{itemize}
+  \begin{itemize}
+  \item foo
+  \item bar
+  \item baz
+  \end{itemize}
+  \begin{block}{The implementation of the model is available at}
+    \url{https://github.com/dilkas/random-logic-programs}
+  \end{block}
 \end{frame}
@@
 % ===============================================================
-
-\begin{frame}{Overview}
-  \begin{block}{General parameters}
-    \begin{itemize}
-    \item maximum number of solutions
-    \item \texttt{maxNumNodes} (in the tree representation of a clause)
-    \item list of predicates with their variables
-    \item maximum number of clauses
-    \item option to forbid all cycles or just negative cycles
-    \item list of probabilities that are randomly assigned to clauses: $\{ 0.1,
-      0.2, \dots, 0.9, 1, 1, 1, 1, 1, 1 \}$
-    \end{itemize}
-  \end{block}
-  \begin{block}{Decision variables}
-    \begin{itemize}
-    \item \texttt{IntVar[] clauseAssignments}: a predicate or disabled
-    \item \texttt{Clause[] clauses}
-    \end{itemize}
-  \end{block}
-\end{frame}
-
-\begin{frame}{Constraints}
-  \begin{block}{Each predicate should get at least one constraint}
-    \begin{itemize}
-    \item \texttt{numDisabledClauses}: defined by a \texttt{count} constraint
-    \item $\texttt{numDistinctValues} = \begin{cases}
-        \texttt{numPredicates} + 1 & \text{if } \texttt{numDisabledValues} > 0 \\
-        \texttt{numPredicates} & \text{otherwise.}
-      \end{cases}$
-      \begin{itemize}
-      \item also constrained using the \texttt{nValues} constraint
-      \end{itemize}
-    \end{itemize}
-  \end{block}
-  \begin{block}{Miscellaneous}
-    \begin{itemize}
-    \item \texttt{clauseAssignments} are sorted.
-    \item If $\texttt{clauseAssignments}[i-1] = \texttt{clauseAssignments}[i]$,
-      \begin{itemize}
-      \item then $\texttt{clause}[i-1] \preceq \texttt{clause}[i]$.
-      \end{itemize}
-    \end{itemize}
-  \end{block}
-\end{frame}
-
-\begin{frame}{Clauses}
-  \begin{block}{A clause is defined by...}
-    \begin{itemize}
-    \item \texttt{IntVar[] treeStructure}
-      \begin{itemize}
-      \item $\texttt{treeStructure}[i] = i$: the $i$-th node is a root.
-      \item $\texttt{treeStructure}[i] = j$: the $i$-th node's parent is node $j$.
-      \end{itemize}
-    \item \texttt{IntVar[] treeValues}: $\neg$, $\land$, $\lor$, $\top$, and any
-      predefined predicates with variables.
-    \end{itemize}
-  \end{block}
-  \begin{block}{Auxiliary variables}
-    \begin{itemize}
-    \item $\texttt{numNodes}, \texttt{numTrees} \in \{ 1, \dots, \texttt{maxNumNodes} \}$
-    \end{itemize}
-  \end{block}
-\end{frame}
 
@@
       \end{itemize}
-    \item Conditional independence
-      \begin{itemize}
-      \item Same propagation, but with a `filter' that masks out the expression
-        that the independence is conditioned on.
-      \end{itemize}
     \end{itemize}

### 2020-08-10 seminar_talk/talk.tex
A bit about symmetry breaking

@@
 \usepackage{empheq}
+\usepackage{pifont}
+
+\usetheme{Singapore}
+\usecolortheme{lily}
+\beamertemplatenavigationsymbolsempty
 
@@
 \tikzstyle{every picture}+=[remember picture]
-
-\usetheme{Singapore}
-\usecolortheme{lily}
-\beamertemplatenavigationsymbolsempty
+\tikzset{onslide/.code args={<#1>#2}{%
+  \only<#1>{\pgfkeysalso{#2}}
+}}
 
@@
 \DeclareMathOperator{\negg}{\backslash+}
+
+\newcommand{\cmark}{\textcolor{green!50!black}{\ding{51}}}%
+\newcommand{\xmark}{\textcolor{red}{\ding{55}}}%
 
@@
 
-% width: 4.2679148611112
-% height: 3.5575922222223
+\begin{frame}{How Many Programs Are Used to Test Algorithms?}
+  \begin{columns}
+    \begin{column}{0.5\textwidth}
+      \pause
+      \fbox{
+        \begin{tikzpicture}
+          \node[inner sep = 0pt] (a) {\includegraphics[width=\textwidth]{inference3.png}};
+          \node[anchor=center] at (a.center) {\Huge\alert{4}};
+        \end{tikzpicture}
+      }
+      \pause
+      \fbox{
+        \begin{tikzpicture}
+          \node[inner sep = 0pt] (a) {\includegraphics[width=\textwidth]{inference8.png}};
+          \node[anchor=center] at (a.center) {\Huge\alert{3}};
+        \end{tikzpicture}
+      }
+      \pause
+      \fbox{
+        \begin{tikzpicture}
+          \node[inner sep = 0pt] (a) {\includegraphics[width=\textwidth]{inference7.png}};
+          \node[anchor=center] at (a.center) {\Huge\alert{1}};
+        \end{tikzpicture}
+      }
+    \end{column}
+    \begin{column}{0.5\textwidth}
+      \pause
+      \fbox{
+        \begin{tikzpicture}
+          \node[inner sep = 0pt] (a) {\includegraphics[width=\textwidth]{inference6.png}};
+          \node[anchor=center] at (a.center) {\Huge\alert{1}};
+        \end{tikzpicture}
+      }
+      \pause
+      \fbox{
+        \begin{tikzpicture}
+          \node[inner sep = 0pt] (a) {\includegraphics[width=\textwidth]{inference2.png}};
+          \node[anchor=center] at (a.center) {\Huge\alert{1}};
+        \end{tikzpicture}
+      }
+      \pause
+      \fbox{
+        \begin{tikzpicture}
+          \node[inner sep = 0pt] (a) {\includegraphics[width=\textwidth]{inference1.png}};
+          \node[anchor=center] at (a.center) {\Huge\alert{2}};
+        \end{tikzpicture}
+      }
+    \end{column}
+  \end{columns}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Outline}
+  \tableofcontents
+\end{frame}
+
+\section{Probabilistic Logic Programming}
 
@@
 
-\begin{frame}{Inference}
+\begin{frame}{Applications}
+  \begin{columns}[b]
+    \begin{column}{0.5\textwidth}
+      \centering
+      \includegraphics[width=\textwidth]{application1.png}
+      {\small \cite{DBLP:conf/icra/MoldovanMOSR12}}
+    \end{column}
+    \begin{column}{0.5\textwidth}
+      \centering
+      \includegraphics[width=\textwidth]{application3.png}
+      {\small \cite{DBLP:conf/ijcai/DriesKDBR17}}
+    \end{column}
+  \end{columns}
+  \vfill
+  \begin{columns}[b]
+    \begin{column}{0.5\textwidth}
+      \centering
+      \includegraphics[width=\textwidth]{application2.png}
+      {\small \cite{DBLP:conf/ilp/Corte-RealD017}}
+    \end{column}
+    \begin{column}{0.5\textwidth}
+      \centering
+      \includegraphics[width=\textwidth]{application4.png}
+      {\small \cite{de2013phenetic}}
+    \end{column}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{Probabilistic Inference}
   \begin{minipage}[t][0.5\textheight]{\textwidth}
-    Let $a \oplus b = a + b - ab$.
+    Let \alert{$a \oplus b = a + b - ab$}.
 
@@
 \end{frame}
-% TODO: colours for numbers/probabilities
 
-\begin{frame}{Applications}
-  \begin{columns}[b]
-    \begin{column}{0.5\textwidth}
-      \centering
-      \includegraphics[width=\textwidth]{application1.png}
-      {\small \cite{DBLP:conf/icra/MoldovanMOSR12}}
-    \end{column}
-    \begin{column}{0.5\textwidth}
-      \centering
-      \includegraphics[width=\textwidth]{application3.png}
-      {\small \cite{DBLP:conf/ijcai/DriesKDBR17}}
-    \end{column}
-  \end{columns}
-  \vfill
-  \begin{columns}[b]
-    \begin{column}{0.5\textwidth}
-      \centering
-      \includegraphics[width=\textwidth]{application2.png}
-      {\small \cite{DBLP:conf/ilp/Corte-RealD017}}
-    \end{column}
-    \begin{column}{0.5\textwidth}
-      \centering
-      \includegraphics[width=\textwidth]{application4.png}
-      {\small \cite{de2013phenetic}}
-    \end{column}
-  \end{columns}
-\end{frame}
-
-% TODO: what properties does d-DNNF ensure?
-% TODO: what about SDD?
-% TODO: explain how each of them works
 \begin{frame}{Inference Algorithms and Knowledge Compilation Maps}
@@
   \item[NNF] negation normal form
-  \item[d-DNNF] deterministic decomposable negation normal form
   \item[BDD] binary decision diagrams
   \item[SDD] sentential decision diagrams
-  \item[$k$-Best] only use the $k$ most probable proofs
+  \item[$k$-Best] only use the \alert{$k$} most probable proofs
+  \item[d-DNNF] deterministic decomposable negation normal form
+    \begin{itemize}
+    \item<2-> for every pair \alert{$\alpha \lor \beta$}, we have \alert{$\alpha
+        \land \beta = \bot$}
+    \item<2-> for every pair \alert{$\alpha \land \beta$}, no atoms are shared
+      between \alert{$\alpha$} and \alert{$\beta$}
+    \item[\xmark\xmark]<3> $(A \lor C) \land (A \lor \neg B)$
+    \item[\xmark\cmark]<3> $C \land (A \lor \neg B)$
+    \item[\cmark\xmark]<3> $B \land C \land [(B \land A) \lor \neg B]$
+    \item[\cmark\cmark]<3> $C \land [(B \land A) \lor \neg B]$
+    \end{itemize}
   \end{description}
@@
 
-\begin{frame}{Example Diagrams for $C \land (A \lor \neg B)$}
+\begin{frame}{Example Diagrams for \alert{$C \land (A \lor \neg B)$}}
   \begin{columns}[b]
@@
                   \nodepart{one} $B$
-                  \nodepart{two} $0$
+                  \nodepart{two} $\bot$
                 }
@@
 
-\begin{frame}{How Many Programs Are Used to Test Algorithms?}
-  \begin{columns}
-    \begin{column}{0.5\textwidth}
-      \pause
-      \fbox{
-        \begin{tikzpicture}
-          \node[inner sep = 0pt] (a) {\includegraphics[width=\textwidth]{inference3.png}};
-          \node[anchor=center] at (a.center) {\Huge\alert{4}};
-        \end{tikzpicture}
-      }
-      \pause
-      \fbox{
-        \begin{tikzpicture}
-          \node[inner sep = 0pt] (a) {\includegraphics[width=\textwidth]{inference8.png}};
-          \node[anchor=center] at (a.center) {\Huge\alert{3}};
-        \end{tikzpicture}
-      }
-      \pause
-      \fbox{
-        \begin{tikzpicture}
-          \node[inner sep = 0pt] (a) {\includegraphics[width=\textwidth]{inference7.png}};
-          \node[anchor=center] at (a.center) {\Huge\alert{1}};
-        \end{tikzpicture}
-      }
-    \end{column}
-    \begin{column}{0.5\textwidth}
-      \pause
-      \fbox{
-        \begin{tikzpicture}
-          \node[inner sep = 0pt] (a) {\includegraphics[width=\textwidth]{inference6.png}};
-          \node[anchor=center] at (a.center) {\Huge\alert{1}};
-        \end{tikzpicture}
-      }
-      \pause
-      \fbox{
-        \begin{tikzpicture}
-          \node[inner sep = 0pt] (a) {\includegraphics[width=\textwidth]{inference2.png}};
-          \node[anchor=center] at (a.center) {\Huge\alert{1}};
-        \end{tikzpicture}
-      }
-      \pause
-      \fbox{
-        \begin{tikzpicture}
-          \node[inner sep = 0pt] (a) {\includegraphics[width=\textwidth]{inference1.png}};
-          \node[anchor=center] at (a.center) {\Huge\alert{2}};
-        \end{tikzpicture}
-      }
-    \end{column}
-  \end{columns}
-\end{frame}
+\section{The Constraint Model}
 
-\begin{frame}{What Characterizes a (Probabilistic) Logic Program?}
+\begin{frame}{What Characterises a (Probabilistic) Logic Program?}
   \begin{columns}
@@
 
+% TODO: I could talk about the constraints behind this
 \begin{frame}{Clauses As Trees}
@@
 
+% TODO: and how is a predicate with its arguments represented?
+\begin{frame}{Variable Symmetry Breaking}
+  \begin{block}{The Problem}
+    Let $\{ \textcolor{variable}{\mathsf{W}}, \textcolor{variable}{\mathsf{X}},
+    \textcolor{variable}{\mathsf{Y}} \}$ be the set of variables. Then
+    \[
+      \textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{X}})
+      \ifff
+      \textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{Y}}),
+      \textcolor{predicate}{\mathtt{influences}}(\textcolor{variable}{\mathsf{Y}},
+      \textcolor{variable}{\mathsf{X}})
+    \]
+    is equivalent to
+    \[
+      \textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{Y}})
+      \ifff
+      \textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{X}}),
+      \textcolor{predicate}{\mathtt{influences}}(\textcolor{variable}{\mathsf{X}},
+      \textcolor{variable}{\mathsf{Y}})
+    \]
+    and to
+    \[
+      \textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{W}})
+      \ifff
+      \textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{X}}),
+      \textcolor{predicate}{\mathtt{influences}}(\textcolor{variable}{\mathsf{X}},
+      \textcolor{variable}{\mathsf{W}})
+    \]
+  \end{block}
+\end{frame}
+
+\begin{frame}{Variable Symmetry Breaking}
+  \begin{overprint}
+    \onslide<1>
+    \centering
+    \begin{tabular}{|c|c|c|c|}
+      \hline
+      $\textcolor{variable}{\mathsf{X}}$ & $\textcolor{variable}{\mathsf{Y}}$ & $\textcolor{variable}{\mathsf{Y}}$ & $\textcolor{variable}{\mathsf{X}}$ \\
+      \hline
+    \end{tabular}
+    \onslide<2>
+    \centering
+    \begin{tabular}{|c|c|c|c|}
+      \hline
+      $\textcolor{variable}{\mathsf{Y}}$ & $\textcolor{variable}{\mathsf{X}}$ & $\textcolor{variable}{\mathsf{X}}$ & $\textcolor{variable}{\mathsf{Y}}$ \\
+      \hline
+    \end{tabular}
+    \onslide<3>
+    \centering
+    \begin{tabular}{|c|c|c|c|}
+      \hline
+      $\textcolor{variable}{\mathsf{W}}$ & $\textcolor{variable}{\mathsf{X}}$ & $\textcolor{variable}{\mathsf{X}}$ & $\textcolor{variable}{\mathsf{W}}$ \\
+      \hline
+    \end{tabular}
+  \end{overprint}
+  \vfill
+  \begin{columns}[t]
+    \begin{column}{0.5\textwidth}
+      \begin{block}{\centering Occurrences}
+        \centering
+        (channeling)
+        \begin{overprint}
+          \onslide<1>
+          \begin{align*}
+            \textcolor{variable}{\mathsf{W}} &\mapsto \emptyset \\
+            \textcolor{variable}{\mathsf{X}} &\mapsto \{ 0, 3 \} \\
+            \textcolor{variable}{\mathsf{Y}} &\mapsto \{ 1, 2 \}
+          \end{align*}
+          \onslide<2>
+          \begin{align*}
+            \textcolor{variable}{\mathsf{W}} &\mapsto \emptyset \\
+            \textcolor{variable}{\mathsf{X}} &\mapsto \alert{\{ 1, 2 \}} \\
+            \textcolor{variable}{\mathsf{Y}} &\mapsto \alert{\{ 0, 3 \}}
+          \end{align*}
+          \onslide<3>
+          \begin{align*}
+            \textcolor{variable}{\mathsf{W}} &\mapsto \alert{\{ 0, 3 \}} \\
+            \textcolor{variable}{\mathsf{X}} &\mapsto \{ 1, 2 \} \\
+            \textcolor{variable}{\mathsf{Y}} &\mapsto \alert{\emptyset}
+          \end{align*}
+        \end{overprint}
+      \end{block}
+    \end{column}
+    \begin{column}{0.5\textwidth}
+      \begin{block}{\centering Introductions}
+        \centering
+        $1 + \min \mathsf{occurrences}(v)$ or $0$
+        \begin{overprint}
+          \onslide<1>
+          \begin{align*}
+            \textcolor{variable}{\mathsf{W}} &\mapsto 0 \\
+            \textcolor{variable}{\mathsf{X}} &\mapsto 1 \\
+            \textcolor{variable}{\mathsf{Y}} &\mapsto 2
+          \end{align*}
+          \smallskip
+          \onslide<2>
+          \begin{align*}
+            \textcolor{variable}{\mathsf{W}} &\mapsto 0 \\
+            \textcolor{variable}{\mathsf{X}} &\mapsto \alert{2} \\
+            \textcolor{variable}{\mathsf{Y}} &\mapsto \alert{1}
+          \end{align*}
+          \onslide<3>
+          \begin{align*}
+            \textcolor{variable}{\mathsf{W}} &\mapsto \alert{1} \\
+            \textcolor{variable}{\mathsf{X}} &\mapsto 2 \\
+            \textcolor{variable}{\mathsf{Y}} &\mapsto \alert{0}
+          \end{align*}
+        \end{overprint}
+        \only<1>{\textcolor{green!50!black}{sorted!}}
+        \only<2-3>{\alert{not sorted!}}
+      \end{block}
+    \end{column}
+  \end{columns}
+\end{frame}
+
 \begin{frame}{Predicate Dependency Graph}
@@
   \begin{tikzpicture}
-    \node[draw,ellipse] (friend) {\textcolor{predicate}{friend}};
-    \node[draw,ellipse,right=of friend] (influences) {\textcolor{predicate}{influences}};
-    \node[draw,ellipse,below=of influences] (stress) {\textcolor{predicate}{stress}};
+    \node[draw,ellipse,onslide=<2->{fill=constant!25}] (friend) {\textcolor{predicate}{friend}};
+    \node[draw,ellipse,onslide=<2->{fill=constant!25},right=of friend] (influences) {\textcolor{predicate}{influences}};
+    \node[draw,ellipse,onslide=<2->{fill=variable!25},below=of influences] (stress) {\textcolor{predicate}{stress}};
     \node[draw,ellipse,below=of stress] (spont) {\textcolor{predicate}{cancer\_spont}};
@@
     \draw[-{Latex[length=2mm]}] (person) -- (smoke);
-    \draw<2->[-{Latex[length=2mm]}] (influences) edge[draw=red,bend left=15] (stress);
-    \draw<2->[-{Latex[length=2mm]}] (stress) edge[draw=red,bend left=15] (influences);
-    \draw<2->[-{Latex[length=2mm]}] (stress) edge[draw=red,bend left=15] (friend);
-    \draw<2->[-{Latex[length=2mm]}] (friend) edge[draw=red,bend left=15] (stress);
+    \draw<3->[-{Latex[length=2mm]}] (influences) edge[draw=red,bend left=15] (stress);
+    \draw<3->[-{Latex[length=2mm]}] (stress) edge[draw=red,bend left=15] (influences);
+    \draw<3->[-{Latex[length=2mm]}] (stress) edge[draw=red,bend left=15] (friend);
+    \draw<3->[-{Latex[length=2mm]}] (friend) edge[draw=red,bend left=15] (stress);
   \end{tikzpicture}
@@
 
+\section{Experimental Results}
+
 \begin{frame}{Scalability}
@@
 
+\section{Summary}
+
+% * a full example for independence propagation (with an adjacency matrix)
+% * specific constraints
 % TODO: finish the slide

### 2020-08-11 seminar_talk/talk.tex
A bit more writing

@@
 \usepackage{pifont}
+\usepackage{colortbl}
+\usepackage{enumitem}
+
+\setitemize{label=\usebeamerfont*{itemize item}%
+  \usebeamercolor[fg]{itemize item}
+  \usebeamertemplate{itemize item}}
 
@@
   \begin{minipage}[t][0.5\textheight]{\textwidth}
-    Let \alert{$a \oplus b = a + b - ab$}.
+    Let \alert{$a \oplus b \coloneqq a + b - ab$}. Then
 
@@
 
-% TODO: I could talk about the constraints behind this
-\begin{frame}{Clauses As Trees}
+% 1. Formula
+% 2. Tree
+% 3. First two rows
+% 4. s is a forest
+% 5. first digit
+% 6. sorted, implication
+% 7. length, number of nodes, for
+% 8. third row, last 3 constraints
+
+\begin{frame}{Formulas As Trees}
+  \begin{columns}
+    \begin{column}{0.37\textwidth}
       \[
@@
       \]
-  \vfill
-  \begin{columns}
-    \begin{column}{0.4\textwidth}
-      \pause
-      \centering
+      \onslide<2->{
         \begin{tikzpicture}[level 1/.style={sibling distance=30mm},level 2/.style={sibling distance=15mm}]
@@
         \end{tikzpicture}
+      }
+      \begin{itemize}
+      \item<6-> $\alert{\mathbf{s}}$ is sorted
+      \item<6-> $\alert{\mathbf{s}_i \ne i} \implies \alert{\mathbf{v}_i \ne \top}$
+      \end{itemize}
     \end{column}
-    \begin{column}{0.6\textwidth}
-      \pause
+    \begin{column}{0.63\textwidth}
+      \alt<7>{\newcolumntype{C}{>{\columncolor{constant!25}}c}}{\newcolumntype{C}{c}}
+      \alt<7>{\newcolumntype{D}{>{\columncolor{probability!25}}c}}{\newcolumntype{D}{c}}
       \centering
-      \begin{tabular}{|c|c|c|c|c|c|c|}
-        \hline
-        0 & 0 & 0 & 1 & 2 & 2 & 6 \\
-        \hline
-        $\lor$ & $\neg$ & $\land$ & $\textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{X}})$ & $\textcolor{predicate}{\mathtt{q}}(\textcolor{variable}{\mathsf{X}})$ & $\textcolor{predicate}{\mathtt{r}}(\textcolor{variable}{\mathsf{X}})$ & $\top$ \\
-        \hline
+      \onslide<3->{
+        \begin{tabular}{c c|C|C|C|C|C|D}
+          \cline{2-8}
+          $\alert{\mathbf{s}}\colon$ & \alert<5->{0} & 0 & 0 & 1 & 2 & 2 & 6 \\
+          \cline{2-8}
+          $\alert{\mathbf{v}}\colon$ & $\lor$ & $\neg$ & $\land$ & $\textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{X}})$ & $\textcolor{predicate}{\mathtt{q}}(\textcolor{variable}{\mathsf{X}})$ & $\textcolor{predicate}{\mathtt{r}}(\textcolor{variable}{\mathsf{X}})$ & $\top$ \\
+          \cline{2-8}
+          \onslide<8->{$\alert{\mathbf{c}}\colon$ & 2 & 1 & 2 & 0 & 0 & 0 & 0 \\ \cline{2-8}}
         \end{tabular}
+      }
+      \begin{itemize}
+      \item<4-> $\alert{\mathbf{s}}$ is a forest with $\alert{T = 2}$ trees
+      \item<7-> length \alert{$L = 7$}
+      \item<7-> number of nodes \alert{$N \coloneqq L - T + 1 = 6$}
+      \item<7-> for \alert{$i = 1, \dots, L - 1$},
+        \begin{itemize}
+        \item if \alert{$i < N$}, then \alert{$\mathbf{s}_i < i$}
+        \item else \alert{$\mathbf{s}_i = i$} and \alert{$\mathbf{v}_i = \top$}
+        \end{itemize}
+      \item<8-> $\alert{\mathbf{c}_i = 0} \iff \alert{\mathbf{v}_i = \top}$ or is a predicate
+      \item<8-> $\alert{\mathbf{c}_i = 1} \iff \alert{\mathbf{v}_i = \neg}$
+      \item<8-> $\alert{\mathbf{c}_i > 1} \iff \alert{\mathbf{v}_i \in \{ \land, \lor \}}$
+      \end{itemize}
     \end{column}
@@
 
+% TODO: a longer intro to experiments (the setup)
+% TODO: conditional independence?
 % TODO: and how is a predicate with its arguments represented?
+% TODO: could add more experimental graphs
+% TODO: a full(er) example of independence propagation
+% TODO: could talk about what algorithms are behind the negative cycle detection
+% TODO: for the bigraph talk, I had 28 slides full info and it still wasn't
+% enough. Maybe I should aim for at least 30.
+% TODO: more constraints
+% TODO: more motivation and related work
 \begin{frame}{Variable Symmetry Breaking}
@@
 
-\begin{frame}{Independence: $\textcolor{predicate}{\mathrm{influences}}
-    \independent \textcolor{predicate}{\mathrm{stress}}$}
-  \centering
-  \begin{tikzpicture}
-    \node[draw,ellipse,onslide=<2->{fill=constant!25}] (friend) {\textcolor{predicate}{friend}};
-    \node[draw,ellipse,onslide=<2->{fill=constant!25},right=of friend] (influences) {\textcolor{predicate}{influences}};
-    \node[draw,ellipse,onslide=<2->{fill=variable!25},below=of influences] (stress) {\textcolor{predicate}{stress}};
-    \node[draw,ellipse,below=of stress] (spont) {\textcolor{predicate}{cancer\_spont}};
-    \node[draw,ellipse,below=of spont] (smoke) {\textcolor{predicate}{cancer\_smoke}};
-    \node[draw,ellipse,left=of spont] (person) {\textcolor{predicate}{person}};
-    \node[draw,ellipse,right=of spont] (cancer) {\textcolor{predicate}{cancer}};
-    \node[draw,ellipse,above=of cancer] (smokes) {\textcolor{predicate}{smokes}};
-    \draw[-{Latex[length=2mm]}] (friend) -- (influences);
-    \draw[-{Latex[length=2mm]}] (influences) -- (smokes);
-    \draw[-{Latex[length=2mm]}] (smokes) -- (cancer);
-    \draw[-{Latex[length=2mm]}] (stress) -- (smokes);
-    \draw[-{Latex[length=2mm]}] (spont) -- (cancer);
-    \draw[-{Latex[length=2mm]}] (smoke) -- (cancer);
-    \draw[-{Latex[length=2mm]}] (person) -- (stress);
-    \draw[-{Latex[length=2mm]}] (person) -- (spont);
-    \draw[-{Latex[length=2mm]}] (person) -- (smoke);
-    \draw<3->[-{Latex[length=2mm]}] (influences) edge[draw=red,bend left=15] (stress);
-    \draw<3->[-{Latex[length=2mm]}] (stress) edge[draw=red,bend left=15] (influences);
-    \draw<3->[-{Latex[length=2mm]}] (stress) edge[draw=red,bend left=15] (friend);
-    \draw<3->[-{Latex[length=2mm]}] (friend) edge[draw=red,bend left=15] (stress);
-  \end{tikzpicture}
-\end{frame}
-
+% TODO: all the extra plots and example I had in the appendix
 \begin{frame}{Stratification and Negative Cycles}
-  \centering
+  \[
+    \textcolor{probability}{0.1} \prob
+    \textcolor{predicate}{\mathtt{friend}}(\textcolor{variable}{\mathsf{X}},
+    \textcolor{variable}{\mathsf{Y}}) \ifff
+    \negg\textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{Y}}).
+  \]
+  \vfill
+  \begin{columns}
+    \begin{column}{0.4\textwidth}
+      \begin{itemize}[leftmargin=0pt]
+      \item<3-> \alert{Stratum 1}: predicates with no negation
+      \item<3-> \alert{Stratum 2}: new predicates s.t. negative literals refer to
+        predicates in \alert{Stratum~1}
+      \end{itemize}
+      \vspace{5em}
+    \end{column}
+    \begin{column}{0.6\textwidth}
+      \hspace{-6.92em}
       \begin{tikzpicture}
@@
       \end{tikzpicture}
-  \[
-    \textcolor{probability}{0.1} \prob
-    \textcolor{predicate}{\mathtt{friend}}(\textcolor{variable}{\mathsf{X}},
-    \textcolor{variable}{\mathsf{Y}}) \ifff
-    \negg\textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{Y}}).
-  \]
+    \end{column}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{Independence: $\textcolor{predicate}{\mathrm{friend}} \independent \textcolor{predicate}{\mathrm{stress}}$}
+  \centering
+  \begin{tikzpicture}
+    \node[draw,ellipse,onslide=<2->{fill=constant!25}] (friend) {\textcolor{predicate}{friend}};
+    \node[draw,ellipse,right=of friend] (influences) {\textcolor{predicate}{influences}};
+    \node[draw,ellipse,onslide=<2->{fill=variable!25},below=of influences] (stress) {\textcolor{predicate}{stress}};
+    \node[draw,ellipse,below=of stress] (spont) {\textcolor{predicate}{cancer\_spont}};
+    \node[draw,ellipse,below=of spont] (smoke) {\textcolor{predicate}{cancer\_smoke}};
+    \node[draw,ellipse,onslide=<2->{fill=variable!25},left=of spont] (person) {\textcolor{predicate}{person}};
+    \node[draw,ellipse,right=of spont] (cancer) {\textcolor{predicate}{cancer}};
+    \node[draw,ellipse,above=of cancer] (smokes) {\textcolor{predicate}{smokes}};
+    \draw[-{Latex[length=2mm]}] (friend) -- (influences);
+    \draw[-{Latex[length=2mm]}] (influences) -- (smokes);
+    \draw[-{Latex[length=2mm]}] (smokes) -- (cancer);
+    \draw[-{Latex[length=2mm]}] (stress) -- (smokes);
+    \draw[-{Latex[length=2mm]}] (spont) -- (cancer);
+    \draw[-{Latex[length=2mm]}] (smoke) -- (cancer);
+    \draw[-{Latex[length=2mm]}] (person) -- (stress);
+    \draw[-{Latex[length=2mm]}] (person) -- (spont);
+    \draw[-{Latex[length=2mm]}] (person) -- (smoke);
+
+    \draw<3->[-{Latex[length=2mm]}] (friend) edge[draw=red,bend left=15] (person);
+    \draw<3->[-{Latex[length=2mm]}] (person) edge[draw=red,bend left=15] (friend);
+
+    \draw<3->[-{Latex[length=2mm]}] (stress) edge[draw=red,bend left=15] (friend);
+    \draw<3->[-{Latex[length=2mm]}] (friend) edge[draw=red,bend left=15] (stress);
+  \end{tikzpicture}
 \end{frame}
@@
 
-\begin{frame}{Clause constraints}
-  \begin{itemize}
-  \item \texttt{treeStructure} represents \texttt{numTrees} trees.
-  \item $\texttt{treeStructure}[0] = 0$
-  \item $\texttt{numTrees} + \texttt{numNodes} = \texttt{maxNumNodes} + 1$
-  \item \texttt{treeStructure} is sorted
-  \item For $i = 0, \dots, \texttt{maxNumNodes} - 1$,
-    \begin{itemize}
-    \item If $\texttt{numNodes} \le i$,
-    \item then $\texttt{treeStructure}[i] = i$ and $\texttt{treeValues}[i] = \top$,
-    \item else $\texttt{treeStructure}[i] < \texttt{numNodes}$.
-    \item has 0 children $\iff$ $\texttt{treeValues}[i]$ is a predicate
-    \item has 1 child $\iff$ $\texttt{treeValues}[i] = \neg$
-    \item has $>1$ child $\iff$ $\texttt{treeValues}[i] \in \{ \land, \lor \}$
-    \item $\texttt{treeStructure}[i] \ne i \implies \texttt{treeValues}[i] \ne \top$
-    \end{itemize}
-  \item If the clause should be disabled, $\texttt{numNodes} = 1$ and
-    $\texttt{treeValues}[0] = \top$.
-  \end{itemize}
-\end{frame}
-
 \begin{frame}

### 2020-08-13 seminar_talk/phase_transition.tex
More slides

% Created by tikzDevice version 0.12.3 on 2020-08-12 19:57:41
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (303.53,130.09);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (303.53,130.09);
\end{scope}
\begin{scope}
\path[clip] ( 34.79, 30.69) rectangle (298.03,124.59);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 34.79, 30.69) rectangle (298.03,124.59);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.79, 77.01) --
	(298.03, 77.01);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.79,100.92) --
	(298.03,100.92);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.79,107.58) --
	(298.03,107.58);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.79, 34.95) --
	(298.03, 34.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.79, 91.75) --
	(298.03, 91.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.20, 30.69) --
	( 40.20,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 49.22, 30.69) --
	( 49.22,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 58.23, 30.69) --
	( 58.23,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 67.25, 30.69) --
	( 67.25,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 76.26, 30.69) --
	( 76.26,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 85.28, 30.69) --
	( 85.28,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.29, 30.69) --
	( 94.29,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (103.31, 30.69) --
	(103.31,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (112.32, 30.69) --
	(112.32,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (121.34, 30.69) --
	(121.34,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (130.35, 30.69) --
	(130.35,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.37, 30.69) --
	(139.37,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (148.38, 30.69) --
	(148.38,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (157.40, 30.69) --
	(157.40,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (166.41, 30.69) --
	(166.41,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (175.43, 30.69) --
	(175.43,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (184.44, 30.69) --
	(184.44,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (193.46, 30.69) --
	(193.46,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (202.47, 30.69) --
	(202.47,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (211.49, 30.69) --
	(211.49,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (220.50, 30.69) --
	(220.50,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (229.52, 30.69) --
	(229.52,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (238.53, 30.69) --
	(238.53,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (247.55, 30.69) --
	(247.55,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (256.56, 30.69) --
	(256.56,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (265.58, 30.69) --
	(265.58,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59, 30.69) --
	(274.59,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (283.61, 30.69) --
	(283.61,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (292.62, 30.69) --
	(292.62,124.59);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.20, 75.95) --
	( 40.20, 92.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.20, 52.30) --
	( 40.20, 43.78) --
	( 40.20, 30.65) --
	( 40.20,  0.76);
\definecolor{fillColor}{RGB}{224,236,244}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 36.82, 75.95) --
	( 36.82, 52.30) --
	( 40.20, 52.30) --
	( 43.58, 52.30) --
	( 43.58, 75.95) --
	( 40.20, 75.95) --
	( 36.82, 75.95) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 36.82, 64.33) --
	( 40.20, 64.33) --
	( 43.58, 64.33);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 49.22, 78.10) --
	( 49.22, 94.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 49.22, 52.30) --
	( 49.22, 39.14) --
	( 49.22,  9.06);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 45.84, 78.10) --
	( 45.84, 52.30) --
	( 49.22, 52.30) --
	( 52.60, 52.30) --
	( 52.60, 78.10) --
	( 49.22, 78.10) --
	( 45.84, 78.10) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 45.84, 64.78) --
	( 49.22, 64.78) --
	( 52.60, 64.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 58.23, 78.40) --
	( 58.23, 95.33);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 58.23, 51.68) --
	( 58.23, 37.75) --
	( 58.23,  2.66);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 54.85, 78.40) --
	( 54.85, 51.68) --
	( 58.23, 51.68) --
	( 61.61, 51.68) --
	( 61.61, 78.40) --
	( 58.23, 78.40) --
	( 54.85, 78.40) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 54.85, 65.00) --
	( 58.23, 65.00) --
	( 61.61, 65.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 67.25, 79.27) --
	( 67.25, 96.45);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 67.25, 51.80) --
	( 67.25, 38.19) --
	( 67.25,  5.26);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 63.87, 79.27) --
	( 63.87, 51.80) --
	( 67.25, 51.80) --
	( 70.63, 51.80) --
	( 70.63, 79.27) --
	( 67.25, 79.27) --
	( 63.87, 79.27) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 63.87, 65.00) --
	( 67.25, 65.00) --
	( 70.63, 65.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 76.26, 80.00) --
	( 76.26, 97.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 76.26, 51.80) --
	( 76.26, 38.19) --
	( 76.26,  5.26);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 72.88, 80.00) --
	( 72.88, 51.80) --
	( 76.26, 51.80) --
	( 79.64, 51.80) --
	( 79.64, 80.00) --
	( 76.26, 80.00) --
	( 72.88, 80.00) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 72.88, 65.50) --
	( 76.26, 65.50) --
	( 79.64, 65.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 85.28, 80.28) --
	( 85.28, 97.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 85.28, 51.93) --
	( 85.28, 38.08) --
	( 85.28,  3.55);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 81.90, 80.28) --
	( 81.90, 51.93) --
	( 85.28, 51.93) --
	( 88.66, 51.93) --
	( 88.66, 80.28) --
	( 85.28, 80.28) --
	( 81.90, 80.28) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 81.90, 65.29) --
	( 85.28, 65.29) --
	( 88.66, 65.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.29, 80.04) --
	( 94.29, 97.53);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.29, 51.30) --
	( 94.29, 37.75) --
	( 94.29,  5.26);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 90.91, 80.04) --
	( 90.91, 51.30) --
	( 94.29, 51.30) --
	( 97.67, 51.30) --
	( 97.67, 80.04) --
	( 94.29, 80.04) --
	( 90.91, 80.04) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 90.91, 65.00) --
	( 94.29, 65.00) --
	( 97.67, 65.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] (103.31, 81.09) --
	(103.31, 98.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] (103.31, 51.30) --
	(103.31, 37.97) --
	(103.31,  6.85);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 99.93, 81.09) --
	( 99.93, 51.30) --
	(103.31, 51.30) --
	(106.69, 51.30) --
	(106.69, 81.09) --
	(103.31, 81.09) --
	( 99.93, 81.09) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 99.93, 65.36) --
	(103.31, 65.36) --
	(106.69, 65.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (112.32, 80.74) --
	(112.32, 98.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (112.32, 51.68) --
	(112.32, 38.62) --
	(112.32,  9.06);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (108.94, 80.74) --
	(108.94, 51.68) --
	(112.32, 51.68) --
	(115.70, 51.68) --
	(115.70, 80.74) --
	(112.32, 80.74) --
	(108.94, 80.74) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (108.94, 65.43) --
	(112.32, 65.43) --
	(115.70, 65.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (121.34, 81.32) --
	(121.34, 99.08);

\path[draw=drawColor,line width= 0.6pt,line join=round] (121.34, 51.30) --
	(121.34, 37.64) --
	(121.34,  4.42);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (117.96, 81.32) --
	(117.96, 51.30) --
	(121.34, 51.30) --
	(124.72, 51.30) --
	(124.72, 81.32) --
	(121.34, 81.32) --
	(117.96, 81.32) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (117.96, 65.29) --
	(121.34, 65.29) --
	(124.72, 65.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (130.35, 81.32) --
	(130.35, 98.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (130.35, 51.43) --
	(130.35, 42.90) --
	(130.35, 29.76) --
	(130.35,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (126.97, 81.32) --
	(126.97, 51.43) --
	(130.35, 51.43) --
	(133.73, 51.43) --
	(133.73, 81.32) --
	(130.35, 81.32) --
	(126.97, 81.32) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (126.97, 65.64) --
	(130.35, 65.64) --
	(133.73, 65.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.37, 81.39) --
	(139.37, 99.17);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.37, 51.30) --
	(139.37, 37.97) --
	(139.37,  6.85);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (135.99, 81.39) --
	(135.99, 51.30) --
	(139.37, 51.30) --
	(142.75, 51.30) --
	(142.75, 81.39) --
	(139.37, 81.39) --
	(135.99, 81.39) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (135.99, 65.64) --
	(139.37, 65.64) --
	(142.75, 65.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (148.38, 81.77) --
	(148.38, 99.66);

\path[draw=drawColor,line width= 0.6pt,line join=round] (148.38, 51.17) --
	(148.38, 37.53) --
	(148.38,  4.42);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (145.00, 81.77) --
	(145.00, 51.17) --
	(148.38, 51.17) --
	(151.76, 51.17) --
	(151.76, 81.77) --
	(148.38, 81.77) --
	(145.00, 81.77) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (145.00, 65.43) --
	(148.38, 65.43) --
	(151.76, 65.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (157.40, 81.73) --
	(157.40, 99.63);

\path[draw=drawColor,line width= 0.6pt,line join=round] (157.40, 51.05) --
	(157.40, 37.64) --
	(157.40,  6.06);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (154.02, 81.73) --
	(154.02, 51.05) --
	(157.40, 51.05) --
	(160.78, 51.05) --
	(160.78, 81.73) --
	(157.40, 81.73) --
	(154.02, 81.73) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (154.02, 65.14) --
	(157.40, 65.14) --
	(160.78, 65.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (166.41, 81.95) --
	(166.41, 99.79);

\path[draw=drawColor,line width= 0.6pt,line join=round] (166.41, 51.17) --
	(166.41, 37.97) --
	(166.41,  7.61);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (163.03, 81.95) --
	(163.03, 51.17) --
	(166.41, 51.17) --
	(169.79, 51.17) --
	(169.79, 81.95) --
	(166.41, 81.95) --
	(163.03, 81.95) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (163.03, 65.43) --
	(166.41, 65.43) --
	(169.79, 65.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (175.43, 81.87) --
	(175.43, 99.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] (175.43, 51.43) --
	(175.43, 38.19) --
	(175.43,  7.61);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (172.05, 81.87) --
	(172.05, 51.43) --
	(175.43, 51.43) --
	(178.81, 51.43) --
	(178.81, 81.87) --
	(175.43, 81.87) --
	(172.05, 81.87) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (172.05, 65.64) --
	(175.43, 65.64) --
	(178.81, 65.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (184.44, 82.43) --
	(184.44,100.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (184.44, 51.05) --
	(184.44, 37.53) --
	(184.44,  5.26);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (181.06, 82.43) --
	(181.06, 51.05) --
	(184.44, 51.05) --
	(187.82, 51.05) --
	(187.82, 82.43) --
	(184.44, 82.43) --
	(181.06, 82.43) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (181.06, 65.68) --
	(184.44, 65.68) --
	(187.82, 65.68);

\path[draw=drawColor,line width= 0.6pt,line join=round] (193.46, 82.36) --
	(193.46,100.38);

\path[draw=drawColor,line width= 0.6pt,line join=round] (193.46, 50.92) --
	(193.46, 37.97) --
	(193.46,  9.06);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (190.08, 82.36) --
	(190.08, 50.92) --
	(193.46, 50.92) --
	(196.84, 50.92) --
	(196.84, 82.36) --
	(193.46, 82.36) --
	(190.08, 82.36) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (190.08, 65.43) --
	(193.46, 65.43) --
	(196.84, 65.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (202.47, 82.57) --
	(202.47,100.73);

\path[draw=drawColor,line width= 0.6pt,line join=round] (202.47, 50.66) --
	(202.47, 37.31) --
	(202.47,  6.06);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (199.09, 82.57) --
	(199.09, 50.66) --
	(202.47, 50.66) --
	(205.85, 50.66) --
	(205.85, 82.57) --
	(202.47, 82.57) --
	(199.09, 82.57) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (199.09, 65.36) --
	(202.47, 65.36) --
	(205.85, 65.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (211.49, 83.13) --
	(211.49,101.31);

\path[draw=drawColor,line width= 0.6pt,line join=round] (211.49, 50.92) --
	(211.49, 37.53) --
	(211.49,  6.06);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (208.11, 83.13) --
	(208.11, 50.92) --
	(211.49, 50.92) --
	(214.87, 50.92) --
	(214.87, 83.13) --
	(211.49, 83.13) --
	(208.11, 83.13) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (208.11, 65.50) --
	(211.49, 65.50) --
	(214.87, 65.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (220.50, 83.03) --
	(220.50,101.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] (220.50, 50.66) --
	(220.50, 36.97) --
	(220.50,  3.55);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (217.12, 83.03) --
	(217.12, 50.66) --
	(220.50, 50.66) --
	(223.88, 50.66) --
	(223.88, 83.03) --
	(220.50, 83.03) --
	(217.12, 83.03) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (217.12, 65.36) --
	(220.50, 65.36) --
	(223.88, 65.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (229.52, 83.55) --
	(229.52,101.89);

\path[draw=drawColor,line width= 0.6pt,line join=round] (229.52, 50.53) --
	(229.52, 36.97) --
	(229.52,  4.42);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (226.14, 83.55) --
	(226.14, 50.53) --
	(229.52, 50.53) --
	(232.90, 50.53) --
	(232.90, 83.55) --
	(229.52, 83.55) --
	(226.14, 83.55) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (226.14, 65.36) --
	(229.52, 65.36) --
	(232.90, 65.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (238.53, 82.85) --
	(238.53,100.68);

\path[draw=drawColor,line width= 0.6pt,line join=round] (238.53, 50.79) --
	(238.53, 37.53) --
	(238.53,  6.85);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (235.15, 82.85) --
	(235.15, 50.79) --
	(238.53, 50.79) --
	(241.91, 50.79) --
	(241.91, 82.85) --
	(238.53, 82.85) --
	(235.15, 82.85) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (235.15, 65.21) --
	(238.53, 65.21) --
	(241.91, 65.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (247.55, 83.58) --
	(247.55,101.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (247.55, 50.39) --
	(247.55, 37.08) --
	(247.55,  6.06);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (244.17, 83.58) --
	(244.17, 50.39) --
	(247.55, 50.39) --
	(250.93, 50.39) --
	(250.93, 83.58) --
	(247.55, 83.58) --
	(244.17, 83.58) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (244.17, 64.78) --
	(247.55, 64.78) --
	(250.93, 64.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (256.56, 83.79) --
	(256.56,102.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] (256.56, 50.26) --
	(256.56, 36.97) --
	(256.56,  6.06);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (253.18, 83.79) --
	(253.18, 72.33) --
	(253.18, 50.26) --
	(256.56, 50.26) --
	(259.94, 50.26) --
	(259.94, 72.33) --
	(259.94, 83.79) --
	(256.56, 83.79) --
	(253.18, 83.79) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (253.18, 65.07) --
	(256.56, 65.07) --
	(259.94, 65.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (265.58, 84.22) --
	(265.58,102.80);

\path[draw=drawColor,line width= 0.6pt,line join=round] (265.58, 50.00) --
	(265.58, 37.31) --
	(265.58,  9.75);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (262.20, 84.22) --
	(262.20, 72.62) --
	(262.20, 50.00) --
	(265.58, 50.00) --
	(268.96, 50.00) --
	(268.96, 72.62) --
	(268.96, 84.22) --
	(265.58, 84.22) --
	(262.20, 84.22) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (262.20, 64.78) --
	(265.58, 64.78) --
	(268.96, 64.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59, 84.32) --
	(274.59,102.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59, 49.73) --
	(274.59, 36.27) --
	(274.59,  4.42);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (271.21, 84.32) --
	(271.21, 72.65) --
	(271.21, 49.73) --
	(274.59, 49.73) --
	(277.98, 49.73) --
	(277.98, 72.65) --
	(277.98, 84.32) --
	(274.59, 84.32) --
	(271.21, 84.32) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (271.21, 64.63) --
	(274.59, 64.63) --
	(277.98, 64.63);

\path[draw=drawColor,line width= 0.6pt,line join=round] (283.61, 84.89) --
	(283.61,103.68);

\path[draw=drawColor,line width= 0.6pt,line join=round] (283.61, 49.45) --
	(283.61, 36.39) --
	(283.61,  6.85);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (280.23, 84.89) --
	(280.23, 73.06) --
	(280.23, 49.45) --
	(283.61, 49.45) --
	(286.99, 49.45) --
	(286.99, 73.06) --
	(286.99, 84.89) --
	(283.61, 84.89) --
	(280.23, 84.89) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (280.23, 63.57) --
	(283.61, 63.57) --
	(286.99, 63.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] (292.62, 86.34) --
	(292.62,105.44);

\path[draw=drawColor,line width= 0.6pt,line join=round] (292.62, 49.04) --
	(292.62, 35.80) --
	(292.62,  5.26);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (289.24, 86.34) --
	(289.24, 74.16) --
	(289.24, 49.04) --
	(292.62, 49.04) --
	(296.01, 49.04) --
	(296.01, 74.16) --
	(296.01, 86.34) --
	(292.62, 86.34) --
	(289.24, 86.34) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (289.24, 62.38) --
	(292.62, 62.38) --
	(296.01, 62.38);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 40.20, 71.66) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 49.22, 79.45) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 58.23, 87.80) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 67.25, 91.37) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 76.26, 92.89) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 85.28, 98.48) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 94.29,100.35) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.31,104.38) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.32,105.75) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.34,110.28) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.35,110.49) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.37,109.72) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (148.38,114.89) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (157.40,113.61) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.41,115.59) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.43,116.86) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (184.44,115.92) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (193.46,117.85) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (202.47,116.11) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (211.49,117.57) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (220.50,117.72) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (229.52,118.06) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (238.53,117.37) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (247.55,116.43) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (256.56,113.89) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (265.58,112.76) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (274.59,107.36) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (283.61,102.11) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (292.62, 98.37) circle (  1.96);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 34.79, 30.69) rectangle (298.03,124.59);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96, 31.18) {10};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.62] at ( 26.76, 34.78) {2};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96, 87.98) {10};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.62] at ( 26.76, 91.58) {3};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.04, 34.95) --
	( 34.79, 34.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 32.04, 91.75) --
	( 34.79, 91.75);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.20, 27.94) --
	( 40.20, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 49.22, 27.94) --
	( 49.22, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 58.23, 27.94) --
	( 58.23, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 67.25, 27.94) --
	( 67.25, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 76.26, 27.94) --
	( 76.26, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 85.28, 27.94) --
	( 85.28, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.29, 27.94) --
	( 94.29, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (103.31, 27.94) --
	(103.31, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (112.32, 27.94) --
	(112.32, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (121.34, 27.94) --
	(121.34, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (130.35, 27.94) --
	(130.35, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.37, 27.94) --
	(139.37, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (148.38, 27.94) --
	(148.38, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (157.40, 27.94) --
	(157.40, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (166.41, 27.94) --
	(166.41, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (175.43, 27.94) --
	(175.43, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (184.44, 27.94) --
	(184.44, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (193.46, 27.94) --
	(193.46, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (202.47, 27.94) --
	(202.47, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (211.49, 27.94) --
	(211.49, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (220.50, 27.94) --
	(220.50, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (229.52, 27.94) --
	(229.52, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (238.53, 27.94) --
	(238.53, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (247.55, 27.94) --
	(247.55, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (256.56, 27.94) --
	(256.56, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (265.58, 27.94) --
	(265.58, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59, 27.94) --
	(274.59, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (283.61, 27.94) --
	(283.61, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (292.62, 27.94) --
	(292.62, 30.69);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 40.20, 19.68) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 49.22, 19.68) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 58.23, 19.68) {2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 67.25, 19.68) {3};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 76.26, 19.68) {4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 85.28, 19.68) {5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 94.29, 19.68) {6};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (103.31, 19.68) {7};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (112.32, 19.68) {8};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (121.34, 19.68) {9};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (130.35, 19.68) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (139.37, 19.68) {11};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (148.38, 19.68) {12};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (157.40, 19.68) {13};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (166.41, 19.68) {14};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (175.43, 19.68) {15};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (184.44, 19.68) {16};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (193.46, 19.68) {17};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (202.47, 19.68) {18};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (211.49, 19.68) {19};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (220.50, 19.68) {20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (229.52, 19.68) {21};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (238.53, 19.68) {22};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (247.55, 19.68) {23};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (256.56, 19.68) {24};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (265.58, 19.68) {25};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (274.59, 19.68) {26};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (283.61, 19.68) {27};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (292.62, 19.68) {28};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (166.41,  7.64) {Independent pairs of predicates};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08, 77.64) {Search nodes};
\end{scope}
\end{tikzpicture}

\end{document}

### 2020-08-13 seminar_talk/talk.tex
More slides

@@
 \usepackage{colortbl}
-\usepackage{enumitem}
-
-\setitemize{label=\usebeamerfont*{itemize item}%
-  \usebeamercolor[fg]{itemize item}
-  \usebeamertemplate{itemize item}}
+\usepackage{soul}
 
@@
 
-\begin{frame}{Probabilistic Inference}
+\begin{frame}{Probabilistic Inference: Reasoning by Hand}
   \begin{minipage}[t][0.5\textheight]{\textwidth}
@@
 
+\begin{frame}{Probabilistic Inference: Probabilities of Worlds}
+  \vspace{-0.5em}
+  \onslide<2->{
+    \[
+      \textcolor{predicate}{\mathtt{cancer}}(\textcolor{constant}{\mathit{michelle}})
+      = \alt<5>{\alert{\bot}}{\top}
+    \]
+    \[
+      \Pr(\mathit{world}) =
+      \only<2>{
+        \textcolor{probability}{0.2} \times (1 - \textcolor{probability}{0.3})
+        \times \textcolor{probability}{0.1} \times \textcolor{probability}{0.3}
+      }
+      \only<3>{
+        \textcolor{probability}{0.2} \times \textcolor{probability}{0.3} \times
+        \textcolor{probability}{0.1} \times (1 - \textcolor{probability}{0.3})
+      }
+      \only<4>{
+        (1 - \textcolor{probability}{0.2}) \times (1 -
+        \textcolor{probability}{0.3}) \times \textcolor{probability}{0.1} \times
+        \textcolor{probability}{0.3}
+      }
+      \only<5>{
+        (1 - \textcolor{probability}{0.2}) \times (1 -
+        \textcolor{probability}{0.3}) \times (1 - \textcolor{probability}{0.1})
+        \times (1 - \textcolor{probability}{0.3})
+      }
+    \]
+  }
+  \vspace{-1.5em}
+  \begin{align*}
+    \alt<2->{\hbox{\st{$\textcolor{probability}{0.2} \prob$}}}{\textcolor{probability}{0.2} \prob} &\alt<4,5>{\hbox{\st{$\textcolor{predicate}{\mathtt{stress}}(\textcolor{variable}{\mathsf{P}}) \ifff \textcolor{predicate}{\mathtt{person}}(\textcolor{variable}{\mathsf{P}}).$}}}{\textcolor{predicate}{\mathtt{stress}}(\textcolor{variable}{\mathsf{P}}) \ifff \textcolor{predicate}{\mathtt{person}}(\textcolor{variable}{\mathsf{P}}).} \\
+    \alt<2->{\hbox{\st{$\textcolor{probability}{0.3} \prob$}}}{\textcolor{probability}{0.3} \prob} &\alt<2,4,5>{\hbox{\st{$\textcolor{predicate}{\mathtt{influences}}(\textcolor{variable}{\mathsf{P}_1}, \textcolor{variable}{\mathsf{P}_2}) \ifff \textcolor{predicate}{\mathtt{friend}}(\textcolor{variable}{\mathsf{P}_1}, \textcolor{variable}{\mathsf{P}_2}).$}}}{\textcolor{predicate}{\mathtt{influences}}(\textcolor{variable}{\mathsf{P}_1}, \textcolor{variable}{\mathsf{P}_2}) \ifff \textcolor{predicate}{\mathtt{friend}}(\textcolor{variable}{\mathsf{P}_1}, \textcolor{variable}{\mathsf{P}_2}).} \\
+    \alt<2->{\hbox{\st{$\textcolor{probability}{0.1} \prob$}}}{\textcolor{probability}{0.1} \prob} &\alt<5>{\hbox{\st{$\textcolor{predicate}{\mathtt{cancer\_spont}}(\textcolor{variable}{\mathsf{P}}) \ifff \textcolor{predicate}{\mathtt{person}}(\textcolor{variable}{\mathsf{P}}).$}}}{\textcolor{predicate}{\mathtt{cancer\_spont}}(\textcolor{variable}{\mathsf{P}}) \ifff \textcolor{predicate}{\mathtt{person}}(\textcolor{variable}{\mathsf{P}}).} \\
+    \alt<2->{\hbox{\st{$\textcolor{probability}{0.3} \prob$}}}{\textcolor{probability}{0.3} \prob} &\alt<3,5>{\hbox{\st{$\textcolor{predicate}{\mathtt{cancer\_smoke}}(\textcolor{variable}{\mathsf{P}}) \ifff \textcolor{predicate}{\mathtt{person}}(\textcolor{variable}{\mathsf{P}}).$}}}{\textcolor{predicate}{\mathtt{cancer\_smoke}}(\textcolor{variable}{\mathsf{P}}) \ifff \textcolor{predicate}{\mathtt{person}}(\textcolor{variable}{\mathsf{P}}).} \\
+                                                                                                   &\alt<4,5>{\hbox{\st{$\textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{X}}) \ifff \textcolor{predicate}{\mathtt{stress}}(\textcolor{variable}{\mathsf{X}}).$}}}{\textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{X}}) \ifff \textcolor{predicate}{\mathtt{stress}}(\textcolor{variable}{\mathsf{X}}).} \\
+                                                                                                   &\alt<2,4,5>{\hbox{\st{$\textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{X}}) \ifff \textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{Y}}), \textcolor{predicate}{\mathtt{influences}}(\textcolor{variable}{\mathsf{Y}}, \textcolor{variable}{\mathsf{X}}).$}}}{\textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{X}}) \ifff \textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{Y}}), \textcolor{predicate}{\mathtt{influences}}(\textcolor{variable}{\mathsf{Y}}, \textcolor{variable}{\mathsf{X}}).} \\
+                                                                                                   &\alt<5>{\hbox{\st{$\textcolor{predicate}{\mathtt{cancer}}(\textcolor{variable}{\mathsf{P}}) \ifff \textcolor{predicate}{\mathtt{cancer\_spont}}(\textcolor{variable}{\mathsf{P}}).$}}}{\textcolor{predicate}{\mathtt{cancer}}(\textcolor{variable}{\mathsf{P}}) \ifff \textcolor{predicate}{\mathtt{cancer\_spont}}(\textcolor{variable}{\mathsf{P}}).} \\
+                                                                                                   &\alt<3-5>{\hbox{\st{$\textcolor{predicate}{\mathtt{cancer}}(\textcolor{variable}{\mathsf{P}}) \ifff \textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{P}}), \textcolor{predicate}{\mathtt{cancer\_smoke}}(\textcolor{variable}{\mathsf{P}}).$}}}{\textcolor{predicate}{\mathtt{cancer}}(\textcolor{variable}{\mathsf{P}}) \ifff \textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{P}}), \textcolor{predicate}{\mathtt{cancer\_smoke}}(\textcolor{variable}{\mathsf{P}}).} \\
+                                                                                                   &\textcolor{predicate}{\mathtt{person}}(\textcolor{constant}{\mathit{michelle}}). \\
+                                                                                                   &\textcolor{predicate}{\mathtt{person}}(\textcolor{constant}{\mathit{timothy}}). \\
+                                                                                                   &\textcolor{predicate}{\mathtt{friend}}(\textcolor{constant}{\mathit{timothy}}, \textcolor{constant}{\mathit{michelle}}).
+  \end{align*}
+\end{frame}
+
 \begin{frame}{Inference Algorithms and Knowledge Compilation Maps}
@@
       between \alert{$\alpha$} and \alert{$\beta$}
-    \item[\xmark\xmark]<3> $(A \lor C) \land (A \lor \neg B)$
-    \item[\xmark\cmark]<3> $C \land (A \lor \neg B)$
-    \item[\cmark\xmark]<3> $B \land C \land [(B \land A) \lor \neg B]$
-    \item[\cmark\cmark]<3> $C \land [(B \land A) \lor \neg B]$
+    \item<3-> examples:
+      \begin{itemize}
+      \item[\visible<4->{\xmark}\visible<5->{\xmark}]<3-> $(A \lor C) \land (A \lor \neg B)$
+      \item[\visible<7->{\xmark}\visible<8->{\cmark}]<6-> $C \land (A \lor \neg B)$
+      \item[\visible<10->{\cmark}\visible<11->{\xmark}]<9-> $B \land C \land [(B \land A) \lor \neg B]$
+      \item[\visible<13->{\cmark}\visible<14->{\cmark}]<12-> $C \land [(B \land A) \lor \neg B]$
+      \end{itemize}
     \end{itemize}
@@
 
-% TODO: a longer intro to experiments (the setup)
 % TODO: conditional independence?
-% TODO: and how is a predicate with its arguments represented?
-% TODO: could add more experimental graphs
+% TODO: how is a predicate with its arguments represented?
 % TODO: a full(er) example of independence propagation
@@
 % TODO: for the bigraph talk, I had 28 slides full info and it still wasn't
-% enough. Maybe I should aim for at least 30.
+% enough. Maybe I should aim for at least 30. Right now I have 26.
 % TODO: more constraints
@@
     \begin{column}{0.4\textwidth}
-      \begin{itemize}[leftmargin=0pt]
+      \setlength{\leftmargini}{0pt}
+      \begin{itemize}
       \item<3-> \alert{Stratum 1}: predicates with no negation
@@
 
+\begin{frame}{How Predicate Independence Affects Search Complexity}
+  \centering
+  \includegraphics{phase_transition.pdf}
+\end{frame}
+
+\begin{frame}{What Programs Should We Generate?}
+  \begin{itemize}
+  \item each program is divided into:
+    \begin{itemize}
+    \item rules
+      \begin{itemize}
+      \item e.g., $\textcolor{probability}{0.2} \prob
+        \textcolor{predicate}{\mathtt{stress}}(\textcolor{variable}{\mathsf{P}})
+        \ifff
+        \textcolor{predicate}{\mathtt{person}}(\textcolor{variable}{\mathsf{P}}).$
+      \end{itemize}
+    \item facts
+      \begin{itemize}
+      \item e.g.,
+        $\textcolor{predicate}{\mathtt{friend}}(\textcolor{constant}{\mathit{timothy}},
+        \textcolor{constant}{\mathit{michelle}}).$
+      \end{itemize}
+    \end{itemize}
+  \item predicates, variables, nodes: 2, 4, 8
+  \item maximum arity: 1, 2, 3
+  \item all possible numbers of pairs of independent predicates
+  \item 10 programs per configuration
+    \begin{itemize}
+    \item fully restarting the constraint solver
+    \end{itemize}
+  \item probabilities sampled from $\{ 0.1, 0.2, \dots, 0.9 \}$
+  \item query: random unlisted fact
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Rules}
+  \[
+    \textcolor{probability}{0.2} \prob
+    \textcolor{predicate}{\mathtt{stress}}(\textcolor{variable}{\mathsf{P}})
+    \ifff
+    \textcolor{predicate}{\mathtt{person}}(\textcolor{variable}{\mathsf{P}}).
+  \]
+  \bigskip
+  \begin{itemize}
+  \item no constants, no empty bodies
+  \item one rule per predicate
+  \item all rules are probabilistic
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Facts}
+  \[
+    \textcolor{predicate}{\mathtt{friend}}(\textcolor{constant}{\mathit{timothy}},
+    \textcolor{constant}{\mathit{michelle}}).
+  \]
+  \bigskip
+  \begin{itemize}
+  \item proportion probabilistic: 25\%, 50\%, 75\%
+  \item constants: 100, 200, 400
+  \item number of facts: $10^3$, $10^4$, $10^5$
+    \begin{itemize}
+    \item but only up to 75\% of all possible facts
+    \end{itemize}
+  \end{itemize}
+\end{frame}
+
 \begin{frame}{Properties of Programs vs. Inference Algorithms}
@@
 
+\begin{frame}{How Encodings Compare Across Instances}
+  \includegraphics{scatterplot.pdf}
+\end{frame}
+
+\begin{frame}{The Ratio of Listed Facts to Possible Facts}
+  \includegraphics{proportion.pdf}
+\end{frame}
+
 \section{Summary}
 
-% * a full example for independence propagation (with an adjacency matrix)
-% * specific constraints
 % TODO: finish the slide

### 2020-08-13 scripts/analyse_model.R

@@ -21,11 +21,8 @@ nrow(small)/nrow(df)*100
 tail(sort(df$totalTime))
 df %>% group_by(df$numPredicates) %>% tally()
 
-# Phase transition
+# Phase transition: paper version
 big <- df[df$numPredicates == 8, ]
-#colourCount = length(unique(big$numIndependentPairs))
-#getPalette = colorRampPalette(brewer.pal(9, "BuPu"))
-# fill = getPalette(colourCount)
 tikz(file = "../paper/phase_transition.tex", width = 4.8, height = 1.8)
 ggplot(big, aes(factor(numIndependentPairs), nodes, group = numIndependentPairs)) +
   geom_boxplot(outlier.shape = NA, fill = "#e0ecf4") +
@@ -35,6 +32,21 @@ ggplot(big, aes(factor(numIndependentPairs), nodes, group = numIndependentPairs)
   stat_summary(fun.y = mean, geom = "point") +
   xlab("Independent pairs") +
   ylab("Nodes") +
+  theme_set(theme_minimal(base_size = 7)) +
+  theme_bw() +
+  theme(legend.position = "none")
+dev.off()
+
+# Phase transition: talk version
+tikz(file = "../seminar_talk/phase_transition.tex", width = 4.2, height = 1.8, standAlone = T)
+ggplot(big, aes(factor(numIndependentPairs), nodes, group = numIndependentPairs)) +
+  geom_boxplot(outlier.shape = NA, fill = "#e0ecf4") +
+  coord_trans(y = "log10", limy = c(100, quantile(big$nodes, 0.91))) +
+  scale_y_continuous(breaks = c(1, 20, 100, 1000, 10000),
+                     labels = c("1", "20", expression(10^2), expression(10^3), expression(10^4))) +
+  stat_summary(fun.y = mean, geom = "point") +
+  xlab("Independent pairs of predicates") +
+  ylab("Search nodes") +
   theme_set(theme_minimal(base_size = 7)) +
   theme_bw() +
   theme(legend.position = "none")

### 2020-08-13 seminar_talk/talk.tex
Example programs

@@
 
+% TODO: say something about heuristics
 % TODO: conditional independence?
@@
 
-% TODO: all the extra plots and example I had in the appendix
 \begin{frame}{Stratification and Negative Cycles}
@@
 
+\section{Example Programs}
+
+\begin{frame}{One-Liners}
+  \begin{columns}
+    \begin{column}{0.4\textwidth}
+      \begin{block}{Setup}
+        \setlength{\leftmargini}{7pt}
+        \begin{itemize}
+        \item predicate $\textcolor{predicate}{\mathtt{p}}/1$
+        \item variable $\textcolor{variable}{\mathsf{X}}$
+        \item no constants
+        \item \alert{1} clause
+        \item \alert{4} nodes
+        \item no negative cycles
+        \end{itemize}
+      \end{block}
+    \end{column}
+    \begin{column}{0.6\textwidth}
+      \begin{block}{(All) Programs}
+        \begin{itemize}
+        \item
+          $\textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{X}}).$
+        \item $\textcolor{probability}{0.7} \prob
+          \textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{X}})
+          \ifff
+          \textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{X}}).$
+        \item $\textcolor{probability}{0.8} \prob
+          \textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{X}})
+          \ifff
+          \textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{X}});
+          \textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{X}}).$
+        \item $\textcolor{probability}{0.7} \prob
+          \textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{X}})
+          \ifff
+          \textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{X}}),
+          \textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{X}}).$
+        \item $\textcolor{probability}{0.1} \prob
+          \textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{X}})
+          \ifff
+          \textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{X}});
+          \textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{X}});
+          \textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{X}}).$
+        \item $\textcolor{probability}{0.8} \prob
+          \textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{X}})
+          \ifff
+          \textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{X}}),
+          \textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{X}}),
+          \textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{X}}).$
+        \end{itemize}
+      \end{block}
+    \end{column}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{Symmetry Breaking in Action}
+  \begin{columns}
+    \begin{column}{0.4\textwidth}
+      \begin{block}{Setup}
+        \setlength{\leftmargini}{7pt}
+        \begin{itemize}
+        \item predicate $\textcolor{predicate}{\mathtt{p}}/3$
+        \item variables: $\textcolor{variable}{\mathsf{X}}$,
+          $\textcolor{variable}{\mathsf{Y}}$, $\textcolor{variable}{\mathsf{Z}}$
+        \item no constants
+        \item \alert{1} clause
+        \item \alert{1} node
+        \item no cycles at all
+        \end{itemize}
+      \end{block}
+    \end{column}
+    \begin{column}{0.6\textwidth}
+      \begin{block}{(All) Programs}
+        \begin{itemize}
+        \item $\textcolor{probability}{0.8} \prob
+          \textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{Z}},
+          \textcolor{variable}{\mathsf{Z}}, \textcolor{variable}{\mathsf{Z}}).$
+        \item
+          $\textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{Y}},
+          \textcolor{variable}{\mathsf{Y}}, \textcolor{variable}{\mathsf{Z}}).$
+        \item
+          $\textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{Y}},
+          \textcolor{variable}{\mathsf{Z}}, \textcolor{variable}{\mathsf{Y}}).$
+        \item $\textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{Y}},
+          \textcolor{variable}{\mathsf{Z}}, \textcolor{variable}{\mathsf{Z}}).$
+        \item $\textcolor{probability}{0.1} \prob
+          \textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{X}},
+          \textcolor{variable}{\mathsf{Y}}, \textcolor{variable}{\mathsf{Z}}).$
+        \end{itemize}
+      \end{block}
+    \end{column}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{A Larger Example}
+  \begin{columns}
+    \begin{column}{0.4\textwidth}
+      \begin{block}{Setup}
+        \setlength{\leftmargini}{7pt}
+        \begin{itemize}
+        \item predicates: $\textcolor{predicate}{\mathtt{p}}/1$,
+          $\textcolor{predicate}{\mathtt{q}}/2$,
+          $\textcolor{predicate}{\mathtt{r}}/3$
+        \item variables: $\textcolor{variable}{\mathsf{X}}$,
+          $\textcolor{variable}{\mathsf{Y}}$, $\textcolor{variable}{\mathsf{Z}}$
+        \item constants: $\textcolor{constant}{\mathit{a}}$,
+          $\textcolor{constant}{\mathit{b}}$, $\textcolor{constant}{\mathit{c}}$
+        \item \alert{5} clauses
+        \item \alert{5} nodes
+        \item no negative cycles
+        \end{itemize}
+      \end{block}
+    \end{column}
+    \begin{column}{0.6\textwidth}
+      \begin{block}{A Random Program}
+        \begin{align*}
+          &\textcolor{predicate}{\mathtt{p}}(\textcolor{constant}{\mathit{b}}) \ifff \negg(\textcolor{predicate}{\mathtt{q}}(\textcolor{constant}{\mathit{a}}, \textcolor{constant}{\mathit{b}}), \textcolor{predicate}{\mathtt{q}}(\textcolor{variable}{\mathsf{X}}, \textcolor{variable}{\mathsf{Y}}), \textcolor{predicate}{\mathtt{q}}(\textcolor{variable}{\mathsf{Z}}, \textcolor{variable}{\mathsf{X}})).
+\\
+          \textcolor{probability}{0.4} \prob &\textcolor{predicate}{\mathtt{q}}(\textcolor{variable}{\mathsf{X}}, \textcolor{variable}{\mathsf{X}}) \ifff \negg \textcolor{predicate}{\mathtt{r}}(\textcolor{variable}{\mathsf{Y}}, \textcolor{variable}{\mathsf{Z}}, \textcolor{constant}{\mathit{a}}).
+\\
+          &\textcolor{predicate}{\mathtt{q}}(\textcolor{variable}{\mathsf{X}}, \textcolor{constant}{\mathit{a}}) \ifff \textcolor{predicate}{\mathtt{r}}(\textcolor{variable}{\mathsf{Y}}, \textcolor{variable}{\mathsf{Y}}, \textcolor{variable}{\mathsf{Z}}).
+\\
+          &\textcolor{predicate}{\mathtt{q}}(\textcolor{variable}{\mathsf{X}}, \textcolor{constant}{\mathit{a}}) \ifff \textcolor{predicate}{\mathtt{r}}(\textcolor{variable}{\mathsf{Y}}, \textcolor{constant}{\mathit{b}}, \textcolor{variable}{\mathsf{Z}}).
+\\
+          &\textcolor{predicate}{\mathtt{r}}(\textcolor{variable}{\mathsf{Y}}, \textcolor{constant}{\mathit{b}}, \textcolor{variable}{\mathsf{Z}}).
+        \end{align*}
+      \end{block}
+    \end{column}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{Examples of Predicate Independence}
+  \begin{columns}
+    \begin{column}{0.4\textwidth}
+      \begin{block}{Setup}
+        \setlength{\leftmargini}{7pt}
+        \begin{itemize}
+        \item predicates: $\textcolor{predicate}{\mathtt{p}}/1$,
+          $\textcolor{predicate}{\mathtt{q}}/1$,
+          $\textcolor{predicate}{\mathtt{r}}/1$
+        \item no variables
+        \item constant $\textcolor{constant}{\mathit{a}}$
+        \item \alert{3} clauses
+        \item \alert{3} nodes
+        \item no negative cycles
+        \item $\textcolor{predicate}{\mathtt{p}} \independent
+          \textcolor{predicate}{\mathtt{q}}$
+        \end{itemize}
+      \end{block}
+    \end{column}
+    \begin{column}{0.6\textwidth}
+      \begin{block}{A Few Random Programs}
+        \begin{itemize}
+          \setlength\itemsep{1em}
+        \item $\begin{aligned}[t]
+            \textcolor{probability}{0.5} \prob
+            &\textcolor{predicate}{\mathtt{p}}(\textcolor{constant}{\mathit{a}})
+            \ifff
+            \textcolor{predicate}{\mathtt{p}}(\textcolor{constant}{\mathit{a}});
+            \textcolor{predicate}{\mathtt{p}}(\textcolor{constant}{\mathit{a}}).
+            \\ \textcolor{probability}{0.2} \prob
+            &\textcolor{predicate}{\mathtt{q}}(\textcolor{constant}{\mathit{a}})
+            \ifff
+            \textcolor{predicate}{\mathtt{q}}(\textcolor{constant}{\mathit{a}}),
+            \textcolor{predicate}{\mathtt{q}}(\textcolor{constant}{\mathit{a}}).
+            \\ \textcolor{probability}{0.4} \prob
+            &\textcolor{predicate}{\mathtt{r}}(\textcolor{constant}{\mathit{a}})
+            \ifff \negg
+            \textcolor{predicate}{\mathtt{q}}(\textcolor{constant}{\mathit{a}}).
+          \end{aligned}$
+        \item $\begin{aligned}[t]
+            &\textcolor{predicate}{\mathtt{p}}(\textcolor{constant}{\mathit{a}})
+            \ifff
+            \textcolor{predicate}{\mathtt{p}}(\textcolor{constant}{\mathit{a}}).
+            \\ \textcolor{probability}{0.5} \prob
+            &\textcolor{predicate}{\mathtt{q}}(\textcolor{constant}{\mathit{a}})
+            \ifff
+            \textcolor{predicate}{\mathtt{r}}(\textcolor{constant}{\mathit{a}});
+            \textcolor{predicate}{\mathtt{q}}(\textcolor{constant}{\mathit{a}}).
+            \\
+            &\textcolor{predicate}{\mathtt{r}}(\textcolor{constant}{\mathit{a}})
+            \ifff
+            \textcolor{predicate}{\mathtt{r}}(\textcolor{constant}{\mathit{a}});
+            \textcolor{predicate}{\mathtt{r}}(\textcolor{constant}{\mathit{a}}).
+          \end{aligned}$
+        \item $\begin{aligned}[t]
+            &\textcolor{predicate}{\mathtt{p}}(\textcolor{constant}{\mathit{a}})
+            \ifff
+            \textcolor{predicate}{\mathtt{p}}(\textcolor{constant}{\mathit{a}});
+            \textcolor{predicate}{\mathtt{p}}(\textcolor{constant}{\mathit{a}}).
+            \\ \textcolor{probability}{0.6} \prob
+            &\textcolor{predicate}{\mathtt{q}}(\textcolor{constant}{\mathit{a}})
+            \ifff
+            \textcolor{predicate}{\mathtt{q}}(\textcolor{constant}{\mathit{a}}).
+            \\ \textcolor{probability}{0.7} \prob
+            &\textcolor{predicate}{\mathtt{r}}(\textcolor{constant}{\mathit{a}})
+            \ifff \negg
+            \textcolor{predicate}{\mathtt{q}}(\textcolor{constant}{\mathit{a}}).
+          \end{aligned}$
+        \end{itemize}
+      \end{block}
+    \end{column}
+  \end{columns}
+\end{frame}
+
 \section{Experimental Results}

### 2020-08-14 conference_talk/talk.tex
More slides
Move things around

@@
 \usepackage{tikz}
-\usepackage[style=authoryear]{biblatex}
+\usepackage[style=authoryear,backend=bibtex]{biblatex}
 \usepackage{empheq}
@@
 \tikzstyle{every picture}+=[remember picture]
+\tikzset{onslide/.code args={<#1>#2}{%
+  \only<#1>{\pgfkeysalso{#2}}
+}}
 
@@
 \end{frame}
+
+\section{Introduction}
 
@@
       {\small \cite{de2013phenetic}}
-    \end{column}
-  \end{columns}
-\end{frame}
-
-\begin{frame}{Inference Algorithms and Knowledge Compilation Maps}
-  \begin{description}
-  \item[NNF] negation normal form
-  \item[d-DNNF] deterministic decomposable negation normal form
-  \item[BDD] binary decision diagrams
-  \item[SDD] sentential decision diagrams
-  \item[$k$-Best] only use the $k$ most probable proofs
-  \end{description}
-\end{frame}
-
-\begin{frame}{Example Diagrams for $C \land (A \lor \neg B)$}
-  \vspace{-1em}
-  % \begin{tikzpicture}
-  %   \node[draw,circle] {$\land$}
-  %   child {node[draw,rectangle] {$C$}}
-  %   child {node[draw,circle] {$\lor$}
-  %     child {node[draw,rectangle] {$A$}}
-  %     child {node[draw,rectangle] {$\neg B$}
-  %     }
-  %   };
-  % \end{tikzpicture}
-  \begin{columns}[b]
-    \begin{column}{0.33\textwidth}
-      \begin{figure}
-      \centering
-        \begin{tikzpicture}
-          \node[draw,circle] (A) {$A$}
-          child {edge from parent[draw=none]}
-          child {node[draw,circle] (B) {$B$} edge from parent[dashed]
-            child {node[draw,circle,solid] (C) {$C$} edge from parent[dashed]
-              child {node[draw,rectangle,solid] {$1$} edge from parent[solid]}
-              child {node[draw,rectangle,solid] (0) {$0$}}
-            }
-            child {edge from parent[draw=none]}
-          };
-          \draw (A) -- (C);
-          \draw (B) -- (0);
-        \end{tikzpicture}
-        \caption{BDD}
-      \end{figure}
-    \end{column}
-    \begin{column}{0.34\textwidth}
-      \begin{figure}
-        \centering
-        \begin{tikzpicture}
-          \node[draw,circle] {$\land$}
-          child {node[draw,circle] {$\lor$}
-            child {node[draw,circle] (parent) {$\land$}
-              child {node[draw,rectangle] {$B$}}
-              child {edge from parent[draw=none]}
-            }
-            child {node[draw,circle] {$\land$}
-              child {node[draw,circle] {$\lor$}
-                child {node[draw,rectangle] (A) {$A$}}
-                child {node[draw,rectangle] {$\neg A$}}
-              }
-              child {node[draw,rectangle] {$\neg B$}}
-            }
-          }
-          child {node[draw,rectangle] {$C$}};
-          \draw (parent) -- (A);
-        \end{tikzpicture}
-        \caption{d-DNNF}
-      \end{figure}
-    \end{column}
-    \begin{column}{0.33\textwidth}
-      \begin{figure}
-        \centering
-        \begin{tikzpicture}
-          \tikzset{
-            mysplit/.style={
-              draw,
-              rectangle,
-              rectangle split,
-              rectangle split horizontal,
-              rectangle split parts=2
-            }
-          }
-          \node[draw,circle] {$1$}
-          child {node[mysplit] (bullet) {
-              \nodepart{one} $\neg A$
-              \nodepart{two}
-            }
-            child {node[draw,circle] (3) {$3$} edge from parent[draw=none]
-              child {node[mysplit] {
-                  \nodepart{one} $\neg B$
-                  \nodepart{two} $C$
-                }
-              }
-              child {node[mysplit] {
-                  \nodepart{one} $B$
-                  \nodepart{two} $0$
-                }
-              }
-            }
-          }
-          child {node[mysplit] {
-              \nodepart{one} $A$
-              \nodepart{two} $C$
-            }};
-          \draw[*-] let \p1 = (bullet.two), \p2 = (bullet.center) in ({\x1 + 2.5},{\y2 + 2}) -- (3);
-        \end{tikzpicture}
-        \caption{SDD}
-      \end{figure}
     \end{column}
@@
 
+\begin{frame}
+  \frametitle{Outline}
+  \tableofcontents
+\end{frame}
+
+\section{The Constraint Model}
+
 \begin{frame}{What Characterizes a (Probabilistic) Logic Program?}
@@
 
-\begin{frame}{Clauses As Trees}
+\begin{frame}{Formulas As Trees}
   \[
@@
 
-\begin{frame}{Independence: $\textcolor{predicate}{\mathrm{influences}}
-    \independent \textcolor{predicate}{\mathrm{stress}}$}
+\begin{frame}{Independence: $\textcolor{predicate}{\mathrm{friend}} \independent
+    \textcolor{predicate}{\mathrm{stress}}$}
   \centering
   \begin{tikzpicture}
-    \node[draw,ellipse] (friend) {\textcolor{predicate}{friend}};
+    \node[draw,ellipse,onslide=<2->{fill=constant!25}] (friend) {\textcolor{predicate}{friend}};
     \node[draw,ellipse,right=of friend] (influences) {\textcolor{predicate}{influences}};
-    \node[draw,ellipse,below=of influences] (stress) {\textcolor{predicate}{stress}};
+    \node[draw,ellipse,onslide=<2->{fill=variable!25},below=of influences] (stress) {\textcolor{predicate}{stress}};
     \node[draw,ellipse,below=of stress] (spont) {\textcolor{predicate}{cancer\_spont}};
     \node[draw,ellipse,below=of spont] (smoke) {\textcolor{predicate}{cancer\_smoke}};
-    \node[draw,ellipse,left=of spont] (person) {\textcolor{predicate}{person}};
+    \node[draw,ellipse,onslide=<2->{fill=variable!25},left=of spont] (person) {\textcolor{predicate}{person}};
     \node[draw,ellipse,right=of spont] (cancer) {\textcolor{predicate}{cancer}};
@@
     \draw[-{Latex[length=2mm]}] (person) -- (smoke);
-    \draw<2->[-{Latex[length=2mm]}] (influences) edge[draw=red,bend left=15] (stress);
-    \draw<2->[-{Latex[length=2mm]}] (stress) edge[draw=red,bend left=15] (influences);
-    \draw<2->[-{Latex[length=2mm]}] (stress) edge[draw=red,bend left=15] (friend);
-    \draw<2->[-{Latex[length=2mm]}] (friend) edge[draw=red,bend left=15] (stress);
+
+    \draw<3->[-{Latex[length=2mm]}] (friend) edge[draw=red,bend left=15] (person);
+    \draw<3->[-{Latex[length=2mm]}] (person) edge[draw=red,bend left=15] (friend);
+
+    \draw<3->[-{Latex[length=2mm]}] (stress) edge[draw=red,bend left=15] (friend);
+    \draw<3->[-{Latex[length=2mm]}] (friend) edge[draw=red,bend left=15] (stress);
   \end{tikzpicture}
@@
 \begin{frame}{Stratification and Negative Cycles}
-  \centering
+  \[
+    \textcolor{probability}{0.1} \prob
+    \textcolor{predicate}{\mathtt{friend}}(\textcolor{variable}{\mathsf{X}},
+    \textcolor{variable}{\mathsf{Y}}) \ifff
+    \negg\textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{Y}}).
+  \]
+  \vfill
+  \begin{columns}
+    \begin{column}{0.4\textwidth}
+      \setlength{\leftmargini}{0pt}
+      \begin{itemize}
+      \item<3-> \alert{Stratum 1}: predicates with no negation
+      \item<3-> \alert{Stratum 2}: new predicates s.t. negative literals refer to
+        predicates in \alert{Stratum~1}
+      \end{itemize}
+      \vspace{5em}
+    \end{column}
+    \begin{column}{0.6\textwidth}
+      \hspace{-6.92em}
       \begin{tikzpicture}
@@
       \end{tikzpicture}
-  \[
-    \textcolor{probability}{0.1} \prob
-    \textcolor{predicate}{\mathtt{friend}}(\textcolor{variable}{\mathsf{X}},
-    \textcolor{variable}{\mathsf{Y}}) \ifff
-    \negg\textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{Y}}).
-  \]
+    \end{column}
+  \end{columns}
 \end{frame}
@@
   \input{impact.tex}
+\end{frame}
+
+\section{Probabilistic Inference}
+
+\begin{frame}{Inference Algorithms and Knowledge Compilation Maps}
+  \begin{description}
+  \item[NNF] negation normal form
+  \item[BDD] binary decision diagrams
+  \item[SDD] sentential decision diagrams
+  \item[$k$-Best] only use the \alert{$k$} most probable proofs
+  \item[d-DNNF] deterministic decomposable negation normal form
+    \begin{itemize}
+    \item<2-> for every pair \alert{$\alpha \lor \beta$}, we have \alert{$\alpha
+        \land \beta = \bot$}
+    \item<2-> for every pair \alert{$\alpha \land \beta$}, no atoms are shared
+      between \alert{$\alpha$} and \alert{$\beta$}
+    \end{itemize}
+  \end{description}
+\end{frame}
+
+\begin{frame}{Example Diagrams for \alert{$C \land (A \lor \neg B)$}}
+  \begin{columns}[b]
+    \begin{column}{0.33\textwidth}
+      \begin{figure}
+        \centering
+        \begin{tikzpicture}[level distance=0.8cm]
+          \node[draw,circle] {$\land$}
+          child {node[draw,rectangle] {$C$}}
+          child {node[draw,circle] {$\lor$}
+            child {node[draw,rectangle] {$A$}}
+            child {node[draw,rectangle] {$\neg B$}
+            }
+          };
+        \end{tikzpicture}
+        \caption{NNF}
+      \end{figure}
+      \vspace{-1em}
+      \begin{figure}
+      \centering
+        \begin{tikzpicture}[level distance=0.8cm]
+          \node[draw,circle] (A) {$A$}
+          child {edge from parent[draw=none]}
+          child {node[draw,circle] (B) {$B$} edge from parent[dashed]
+            child {node[draw,circle,solid] (C) {$C$} edge from parent[dashed]
+              child {node[draw,rectangle,solid] {$1$} edge from parent[solid]}
+              child {node[draw,rectangle,solid] (0) {$0$}}
+            }
+            child {edge from parent[draw=none]}
+          };
+          \draw (A) -- (C);
+          \draw (B) -- (0);
+        \end{tikzpicture}
+        \caption{BDD}
+      \end{figure}
+    \end{column}
+    \begin{column}{0.33\textwidth}
+      \begin{figure}
+        \centering
+        \begin{tikzpicture}[level distance=0.8cm]
+          \node[draw,circle] {$\land$}
+          child {node[draw,circle] {$\lor$}
+            child {node[draw,circle] (parent) {$\land$}
+              child {node[draw,rectangle] {$B$}}
+              child {edge from parent[draw=none]}
+            }
+            child {node[draw,circle] {$\land$}
+              child {node[draw,circle] {$\lor$}
+                child {node[draw,rectangle] (A) {$A$}}
+                child {node[draw,rectangle] {$\neg A$}}
+              }
+              child {node[draw,rectangle] {$\neg B$}}
+            }
+          }
+          child {node[draw,rectangle] {$C$}};
+          \draw (parent) -- (A);
+        \end{tikzpicture}
+        \caption{d-DNNF}
+      \end{figure}
+    \end{column}
+    \begin{column}{0.33\textwidth}
+      \begin{figure}
+        \centering
+        \begin{tikzpicture}[level distance=0.8cm]
+          \tikzset{
+            mysplit/.style={
+              draw,
+              rectangle,
+              rectangle split,
+              rectangle split horizontal,
+              rectangle split parts=2
+            }
+          }
+          \node[draw,circle] {$1$}
+          child {node[mysplit] (bullet) {
+              \nodepart{one} $\neg A$
+              \nodepart{two}
+            }
+            child {node[draw,circle] (3) {$3$} edge from parent[draw=none]
+              child {node[mysplit] {
+                  \nodepart{one} $\neg B$
+                  \nodepart{two} $C$
+                }
+              }
+              child {node[mysplit] {
+                  \nodepart{one} $B$
+                  \nodepart{two} $\bot$
+                }
+              }
+            }
+          }
+          child {node[mysplit] {
+              \nodepart{one} $A$
+              \nodepart{two} $C$
+            }};
+          \draw[*-] let \p1 = (bullet.two), \p2 = (bullet.center) in ({\x1 + 2.5},{\y2 + 2}) -- (3);
+        \end{tikzpicture}
+        \caption{SDD}
+      \end{figure}
+      \vspace{-2em}
+      \begin{figure}
+      \centering
+      \begin{tikzpicture}[level distance=0.8cm]
+        \node[draw,circle] {$1$}
+        child {node[draw,circle] {$0$}
+          child {node[draw,rectangle] {$A$}}
+        }
+        child {node[draw,circle] {$3$}
+          child {node[draw,circle] {$2$}
+            child {node[draw,rectangle] {$B$}}
+          }
+          child {node[draw,circle] {$4$}
+            child {node[draw,rectangle] {$C$}}
+          }
+        };
+      \end{tikzpicture}
+      \caption{vtree}
+      \end{figure}
+    \end{column}
+  \end{columns}
 \end{frame}
@@
 
-% TODO: finish the slide
+\section{Summary}
+
 \begin{frame}{Summary}
   \begin{itemize}
-  \item foo
-  \item bar
-  \item baz
+  \item The model can generate (approximately) realistic instances of reasonable
+    size
+  \item The main performance bottleneck can be addressed by generating programs
+    with a simpler structure
+  \item Open questions and future work
+    \begin{itemize}
+    \item Can the model be used to ensure uniform sampling?
+    \item What is the reason behind all algorithms behaving similarly?
+    \item Why does independence have no effect on inference time?
+    \item Can random program generation be useful in, e.g., learning?
+    \end{itemize}
   \end{itemize}

### 2020-08-16 conference_talk/talk.tex
Minor changes

@@
 \usetikzlibrary{decorations.pathreplacing}
+\usetikzlibrary{patterns}
 \usetikzlibrary{positioning}
@@
         \hline
-        0 & 0 & 0 & 1 & 2 & 2 \\
+        0\tikz \coordinate (disjunction2);&\tikz \coordinate (negation1);0\tikz \coordinate (negation2);&\tikz \coordinate (conjunction1);0\tikz \coordinate (conjunction2);&\tikz \coordinate (p);1 &\tikz \coordinate (q);2 &\tikz \coordinate (r);2 \\
         \hline
@@
       \end{tabular}
+      \begin{tikzpicture}[overlay]
+        \draw[->,bend right=60,draw=red] ([yshift=0.75\baselineskip]negation1) to ([yshift=0.75\baselineskip]disjunction2);
+        \draw[->,bend right=60,draw=red] ([yshift=0.75\baselineskip]conjunction1) to ([yshift=0.75\baselineskip]disjunction2);
+        \draw[->,bend right=60,draw=red] ([yshift=0.75\baselineskip]p) to ([yshift=0.75\baselineskip]negation2);
+        \draw[->,bend right=60,draw=red] ([yshift=0.75\baselineskip]q) to ([yshift=0.75\baselineskip]conjunction2);
+        \draw[->,bend right=60,draw=red] ([yshift=0.75\baselineskip]r) to ([yshift=0.75\baselineskip]conjunction2);
+      \end{tikzpicture}
     \end{column}
@@
 
-\begin{frame}{Independence: $\textcolor{predicate}{\mathrm{friend}} \independent
-    \textcolor{predicate}{\mathrm{stress}}$}
-  \centering
-  \begin{tikzpicture}
-    \node[draw,ellipse,onslide=<2->{fill=constant!25}] (friend) {\textcolor{predicate}{friend}};
-    \node[draw,ellipse,right=of friend] (influences) {\textcolor{predicate}{influences}};
-    \node[draw,ellipse,onslide=<2->{fill=variable!25},below=of influences] (stress) {\textcolor{predicate}{stress}};
-    \node[draw,ellipse,below=of stress] (spont) {\textcolor{predicate}{cancer\_spont}};
-    \node[draw,ellipse,below=of spont] (smoke) {\textcolor{predicate}{cancer\_smoke}};
-    \node[draw,ellipse,onslide=<2->{fill=variable!25},left=of spont] (person) {\textcolor{predicate}{person}};
-    \node[draw,ellipse,right=of spont] (cancer) {\textcolor{predicate}{cancer}};
-    \node[draw,ellipse,above=of cancer] (smokes) {\textcolor{predicate}{smokes}};
-    \draw[-{Latex[length=2mm]}] (friend) -- (influences);
-    \draw[-{Latex[length=2mm]}] (influences) -- (smokes);
-    \draw[-{Latex[length=2mm]}] (smokes) -- (cancer);
-    \draw[-{Latex[length=2mm]}] (stress) -- (smokes);
-    \draw[-{Latex[length=2mm]}] (spont) -- (cancer);
-    \draw[-{Latex[length=2mm]}] (smoke) -- (cancer);
-    \draw[-{Latex[length=2mm]}] (person) -- (stress);
-    \draw[-{Latex[length=2mm]}] (person) -- (spont);
-    \draw[-{Latex[length=2mm]}] (person) -- (smoke);
-
-    \draw<3->[-{Latex[length=2mm]}] (friend) edge[draw=red,bend left=15] (person);
-    \draw<3->[-{Latex[length=2mm]}] (person) edge[draw=red,bend left=15] (friend);
-
-    \draw<3->[-{Latex[length=2mm]}] (stress) edge[draw=red,bend left=15] (friend);
-    \draw<3->[-{Latex[length=2mm]}] (friend) edge[draw=red,bend left=15] (stress);
-  \end{tikzpicture}
-\end{frame}
-
 \begin{frame}{Stratification and Negative Cycles}
@@
   \vfill
-  \begin{columns}
-    \begin{column}{0.4\textwidth}
-      \setlength{\leftmargini}{0pt}
-      \begin{itemize}
-      \item<3-> \alert{Stratum 1}: predicates with no negation
-      \item<3-> \alert{Stratum 2}: new predicates s.t. negative literals refer to
-        predicates in \alert{Stratum~1}
-      \end{itemize}
-      \vspace{5em}
-    \end{column}
-    \begin{column}{0.6\textwidth}
-      \hspace{-6.92em}
+%  \begin{columns}
+%    \begin{column}{0.4\textwidth}
+%      \setlength{\leftmargini}{0pt}
+%      \begin{itemize}
+%      \item<3-> \alert{Stratum 1}: predicates with no negation
+%      \item<3-> \alert{Stratum 2}: new predicates s.t. negative literals refer to
+%        predicates in \alert{Stratum~1}
+%      \end{itemize}
+%      \vspace{5em}
+%    \end{column}
+%    \begin{column}{0.6\textwidth}
+%      \hspace{-6.92em}
+  \centering
       \begin{tikzpicture}
@@
       \end{tikzpicture}
-    \end{column}
-  \end{columns}
+%    \end{column}
+%  \end{columns}
+\end{frame}
+
+\begin{frame}{Predicate Independence: $\textcolor{predicate}{\mathrm{friend}}
+    \independent \textcolor{predicate}{\mathrm{stress}}$}
+  \centering
+  \begin{tikzpicture}
+    \node[draw,ellipse,onslide=<2->{fill=constant!25}] (friend) {\textcolor{predicate}{friend}};
+    \node[draw,ellipse,right=of friend,onslide=<5-6>{pattern=north east lines,pattern color=constant}] (influences) {\textcolor{predicate}{influences}};
+    \node[draw,ellipse,onslide=<2->{fill=variable!25},below=of influences] (stress) {\textcolor{predicate}{stress}};
+    \node[draw,ellipse,below=of stress,onslide=<3-4>{pattern=north west lines,pattern color=variable}] (spont) {\textcolor{predicate}{cancer\_spont}};
+    \node[draw,ellipse,below=of spont,onslide=<3-4>{pattern=north west lines,pattern color=variable}] (smoke) {\textcolor{predicate}{cancer\_smoke}};
+    \node[draw,ellipse,onslide=<2->{fill=variable!25},left=of spont] (person) {\textcolor{predicate}{person}};
+    \node[draw,ellipse,right=of spont,onslide=<3-4>{pattern=north west lines,pattern color=variable},onslide=<5-6>{pattern=north east lines,pattern color=constant}] (cancer) {\textcolor{predicate}{cancer}};
+    \node[draw,ellipse,above=of cancer,onslide=<3-4>{pattern=north west lines,pattern color=variable},onslide=<5-6>{pattern=north east lines,pattern color=constant}] (smokes) {\textcolor{predicate}{smokes}};
+    \draw[-{Latex[length=2mm]}] (friend) -- (influences);
+    \draw[-{Latex[length=2mm]}] (influences) -- (smokes);
+    \draw[-{Latex[length=2mm]}] (smokes) -- (cancer);
+    \draw[-{Latex[length=2mm]}] (stress) -- (smokes);
+    \draw[-{Latex[length=2mm]}] (spont) -- (cancer);
+    \draw[-{Latex[length=2mm]}] (smoke) -- (cancer);
+    \draw[-{Latex[length=2mm]}] (person) -- (stress);
+    \draw[-{Latex[length=2mm]}] (person) -- (spont);
+    \draw[-{Latex[length=2mm]}] (person) -- (smoke);
+
+    \draw<4>[-{Latex[length=2mm]}] (person) edge[draw=red] (friend);
+    \draw<4>[-{Latex[length=2mm]}] (stress) edge[draw=red] (friend);
+    \draw<4>[-{Latex[length=2mm]}] (smokes) edge[draw=red] (friend);
+    \draw<4>[-{Latex[length=2mm]}] (spont) edge[draw=red] (friend);
+    \draw<4>[-{Latex[length=2mm]}] (cancer) edge[draw=red,bend left=20] (friend);
+    \draw<4>[-{Latex[length=2mm]}] (smoke) edge[draw=red,bend left=20] (friend);
+
+    \draw<6>[-{Latex[length=2mm]}] (friend) edge[draw=red] (person);
+    \draw<6>[-{Latex[length=2mm]}] (influences) edge[draw=red] (person);
+    \draw<6>[-{Latex[length=2mm]}] (smokes) edge[draw=red] (person);
+    \draw<6>[-{Latex[length=2mm]}] (cancer) edge[draw=red,bend left=15] (person);
+
+    \draw<6>[-{Latex[length=2mm]}] (friend) edge[draw=red] (stress);
+    \draw<6>[-{Latex[length=2mm]}] (influences) edge[draw=red] (stress);
+    \draw<6>[-{Latex[length=2mm]}] (smokes) edge[draw=red,bend right=15] (stress);
+    \draw<6>[-{Latex[length=2mm]}] (cancer) edge[draw=red] (stress);
+  \end{tikzpicture}
 \end{frame}
@@
 
-\section{Probabilistic Inference}
+\section{Inference}
 
-\begin{frame}{Inference Algorithms and Knowledge Compilation Maps}
+\begin{frame}{Inference and Knowledge Compilation}
   \begin{description}
   \item[NNF] negation normal form
+  \item[d-DNNF] deterministic decomposable negation normal form
   \item[BDD] binary decision diagrams
@@
   \item[$k$-Best] only use the \alert{$k$} most probable proofs
-  \item[d-DNNF] deterministic decomposable negation normal form
-    \begin{itemize}
-    \item<2-> for every pair \alert{$\alpha \lor \beta$}, we have \alert{$\alpha
-        \land \beta = \bot$}
-    \item<2-> for every pair \alert{$\alpha \land \beta$}, no atoms are shared
-      between \alert{$\alpha$} and \alert{$\beta$}
-    \end{itemize}
+%    \begin{itemize}
+%    \item<2-> for every pair \alert{$\alpha \lor \beta$}, we have \alert{$\alpha
+%        \land \beta = \bot$}
+%    \item<2-> for every pair \alert{$\alpha \land \beta$}, no atoms are shared
+%      between \alert{$\alpha$} and \alert{$\beta$}
+%    \end{itemize}
   \end{description}
@@
       \end{figure}
-      \vspace{-2em}
-      \begin{figure}
-      \centering
-      \begin{tikzpicture}[level distance=0.8cm]
-        \node[draw,circle] {$1$}
-        child {node[draw,circle] {$0$}
-          child {node[draw,rectangle] {$A$}}
-        }
-        child {node[draw,circle] {$3$}
-          child {node[draw,circle] {$2$}
-            child {node[draw,rectangle] {$B$}}
-          }
-          child {node[draw,circle] {$4$}
-            child {node[draw,rectangle] {$C$}}
-          }
-        };
-      \end{tikzpicture}
-      \caption{vtree}
-      \end{figure}
+%     \vspace{-2em}
+      % \begin{figure}
+      % \centering
+      % \begin{tikzpicture}[level distance=0.8cm]
+      %   \node[draw,circle] {$1$}
+      %   child {node[draw,circle] {$0$}
+      %     child {node[draw,rectangle] {$A$}}
+      %   }
+      %   child {node[draw,circle] {$3$}
+      %     child {node[draw,circle] {$2$}
+      %       child {node[draw,rectangle] {$B$}}
+      %     }
+      %     child {node[draw,circle] {$4$}
+      %       child {node[draw,rectangle] {$C$}}
+      %     }
+      %   };
+      % \end{tikzpicture}
+      % \caption{vtree}
+      % \end{figure}
     \end{column}
@@
 \begin{frame}{Properties of Programs vs. Inference Algorithms}
+  \begin{alignat*}{2}
+  &\text{Facts:} \quad
+  &&\textcolor{predicate}{\mathtt{friend}}(\textcolor{constant}{\mathit{timothy}},
+  \textcolor{constant}{\mathit{michelle}}). \\
+  &\text{Rules:} \quad &&\textcolor{probability}{0.2} \prob
+  \textcolor{predicate}{\mathtt{stress}}(\textcolor{variable}{\mathsf{P}}) \ifff
+  \textcolor{predicate}{\mathtt{person}}(\textcolor{variable}{\mathsf{P}}).
+  \end{alignat*}
   \centering
@@
 
-\section{Summary}
+\section{Conclusions}
 
-\begin{frame}{Summary}
+\begin{frame}{Conclusions and Future Work}
   \begin{itemize}
@@
     with a simpler structure
-  \item Open questions and future work
+  \item Open questions for future work
     \begin{itemize}
@@
     \item Why does independence have no effect on inference time?
-    \item Can random program generation be useful in, e.g., learning?
+%    \item Can random program generation be useful in learning?
     \end{itemize}

### 2020-08-16 seminar_talk/talk.tex
Move things around
Minor changes

@@
 
-% TODO: say something about heuristics
-% TODO: conditional independence?
-% TODO: how is a predicate with its arguments represented?
-% TODO: a full(er) example of independence propagation
-% TODO: could talk about what algorithms are behind the negative cycle detection
-% TODO: for the bigraph talk, I had 28 slides full info and it still wasn't
-% enough. Maybe I should aim for at least 30. Right now I have 26.
-% TODO: more constraints
-% TODO: more motivation and related work
 \begin{frame}{Variable Symmetry Breaking}
@@
 
-\begin{frame}{Independence: $\textcolor{predicate}{\mathrm{friend}} \independent \textcolor{predicate}{\mathrm{stress}}$}
+\begin{frame}{Independence: $\textcolor{predicate}{\mathrm{friend}} \independent
+    \textcolor{predicate}{\mathrm{stress}}$}
   \centering
@@
 
-% TODO: finish the slide
 \begin{frame}{Summary}
   \begin{itemize}
-  \item foo
-  \item bar
-  \item baz
-  \end{itemize}
+  \item The model can generate (approximately) realistic instances of reasonable
+    size
+  \item The main performance bottleneck can be addressed by generating programs
+    with a simpler structure
+  \item Open questions and future work
+    \begin{itemize}
+    \item Can the model be used to ensure uniform sampling?
+    \item What is the reason behind all algorithms behaving similarly?
+    \item Why does independence have no effect on inference time?
+    \item Can random program generation be useful in learning?
+    \end{itemize}
+  \end{itemize}
+  \pause
   \begin{block}{The implementation of the model is available at}
@@
 
-% ===============================================================
-
-\begin{frame}
-  \begin{block}{Adjacency matrix representation}
-    $A[i][j] = 0 \iff \nexists k: \texttt{clauseAssignments}[k] = j$ and $i
-    \in \texttt{clauses}[k].\texttt{treeValues}$
-  \end{block}
-  \begin{block}{New constraints}
-    \begin{itemize}
-    \item No (negative) cycles
-      \begin{itemize}
-      \item No clever propagation, just entailment checking.
-      \end{itemize}
-    \item Independence. Propagation:
-      \begin{itemize}
-      \item Two types of dependencies: determined and
-        one-undetermined-edge-away-from-being-determined.
-      \item Look up the dependencies of both predicates. For each pair of
-        matching dependencies:
-        \begin{itemize}
-        \item If both are determined, fail.
-        \item If one is determined, the selected edge of the other must not
-          exist.
-        \end{itemize}
-      \end{itemize}
-    \end{itemize}
-  \end{block}
-\end{frame}
+% Things I could mention:
+% 1) say something about heuristics
+% 2) conditional independence?
+% 3) how is a predicate with its arguments represented?
+% 4) a full(er) example of independence propagation
+% 5) could talk about what algorithms are behind the negative cycle detection
+% 6) for the bigraph talk, I had 28 slides full info and it still wasn't
+% enough. Maybe I should aim for at least 30. Right now I have 26.
+% 7) more constraints
+% 8) more motivation and related work
 

### 2020-08-16 seminar_talk/talk.tex
Move changes from the conference talk to the seminar talk

@@
 
-\begin{frame}{Independence: $\textcolor{predicate}{\mathrm{friend}} \independent
+\begin{frame}{Predicate Independence: $\textcolor{predicate}{\mathrm{friend}} \independent
     \textcolor{predicate}{\mathrm{stress}}$}
@@
     \node[draw,ellipse,onslide=<2->{fill=constant!25}] (friend) {\textcolor{predicate}{friend}};
-    \node[draw,ellipse,right=of friend] (influences) {\textcolor{predicate}{influences}};
+    \node[draw,ellipse,right=of friend,onslide=<5-6>{pattern=north east lines,pattern color=constant}] (influences) {\textcolor{predicate}{influences}};
     \node[draw,ellipse,onslide=<2->{fill=variable!25},below=of influences] (stress) {\textcolor{predicate}{stress}};
-    \node[draw,ellipse,below=of stress] (spont) {\textcolor{predicate}{cancer\_spont}};
-    \node[draw,ellipse,below=of spont] (smoke) {\textcolor{predicate}{cancer\_smoke}};
+    \node[draw,ellipse,below=of stress,onslide=<3-4>{pattern=north west lines,pattern color=variable}] (spont) {\textcolor{predicate}{cancer\_spont}};
+    \node[draw,ellipse,below=of spont,onslide=<3-4>{pattern=north west lines,pattern color=variable}] (smoke) {\textcolor{predicate}{cancer\_smoke}};
     \node[draw,ellipse,onslide=<2->{fill=variable!25},left=of spont] (person) {\textcolor{predicate}{person}};
-    \node[draw,ellipse,right=of spont] (cancer) {\textcolor{predicate}{cancer}};
-    \node[draw,ellipse,above=of cancer] (smokes) {\textcolor{predicate}{smokes}};
+    \node[draw,ellipse,right=of spont,onslide=<3-4>{pattern=north west lines,pattern color=variable},onslide=<5-6>{pattern=north east lines,pattern color=constant}] (cancer) {\textcolor{predicate}{cancer}};
+    \node[draw,ellipse,above=of cancer,onslide=<3-4>{pattern=north west lines,pattern color=variable},onslide=<5-6>{pattern=north east lines,pattern color=constant}] (smokes) {\textcolor{predicate}{smokes}};
     \draw[-{Latex[length=2mm]}] (friend) -- (influences);
@@
 
-    \draw<3->[-{Latex[length=2mm]}] (friend) edge[draw=red,bend left=15] (person);
-    \draw<3->[-{Latex[length=2mm]}] (person) edge[draw=red,bend left=15] (friend);
-
-    \draw<3->[-{Latex[length=2mm]}] (stress) edge[draw=red,bend left=15] (friend);
-    \draw<3->[-{Latex[length=2mm]}] (friend) edge[draw=red,bend left=15] (stress);
+    \draw<4>[-{Latex[length=2mm]}] (person) edge[draw=red] (friend);
+    \draw<4>[-{Latex[length=2mm]}] (stress) edge[draw=red] (friend);
+    \draw<4>[-{Latex[length=2mm]}] (smokes) edge[draw=red] (friend);
+    \draw<4>[-{Latex[length=2mm]}] (spont) edge[draw=red] (friend);
+    \draw<4>[-{Latex[length=2mm]}] (cancer) edge[draw=red,bend left=20] (friend);
+    \draw<4>[-{Latex[length=2mm]}] (smoke) edge[draw=red,bend left=20] (friend);
+
+    \draw<6>[-{Latex[length=2mm]}] (friend) edge[draw=red] (person);
+    \draw<6>[-{Latex[length=2mm]}] (influences) edge[draw=red] (person);
+    \draw<6>[-{Latex[length=2mm]}] (smokes) edge[draw=red] (person);
+    \draw<6>[-{Latex[length=2mm]}] (cancer) edge[draw=red,bend left=15] (person);
+
+    \draw<6>[-{Latex[length=2mm]}] (friend) edge[draw=red] (stress);
+    \draw<6>[-{Latex[length=2mm]}] (influences) edge[draw=red] (stress);
+    \draw<6>[-{Latex[length=2mm]}] (smokes) edge[draw=red,bend right=15] (stress);
+    \draw<6>[-{Latex[length=2mm]}] (cancer) edge[draw=red] (stress);
   \end{tikzpicture}
@@
 
-\section{Summary}
-
-\begin{frame}{Summary}
+\section{Conclusions}
+
+\begin{frame}{Conclusions and Future Work}
   \begin{itemize}
@@
   \end{itemize}
-  \pause
   \begin{block}{The implementation of the model is available at}

### 2020-09-12 paper/paper.tex
Bring back the appendix

@@
 \newcommand{\hilight}[1]{\setlength{\fboxsep}{1pt}\colorbox{lightgray}{#1}}
+\newcommand{\hlitem}{\stepcounter{enumi}\item[\hilight{\theenumi}]}
 
@@
 \authorrunning{P. Dilkas and V. Belle}
-\institute{University of Edinburgh, Edinburgh, UK
-  \email{\{p.dilkas@sms.,vaishak@\}ed.ac.uk} \and Alan Turing Institute, London,
-  UK}
+\institute{University of Edinburgh, Edinburgh, UK \\
+  \email{p.dilkas@sms.ed.ac.uk, vaishak@ed.ac.uk} \and Alan Turing Institute,
+  London, UK}
 
@@
       \midrule
-      $0$ & determined & $\Determined(p)$ \\
-      $1$ & almost determined & $\AlmostDetermined(p, s, t)$ \\
-      $>1$ & undetermined & $\Undetermined(p)$ \\
+      $0$ & Determined & $\Determined(p)$ \\
+      $1$ & Almost determined & $\AlmostDetermined(p, s, t)$ \\
+      $>1$ & Undetermined & $\Undetermined(p)$ \\
       \bottomrule
@@
 
+\newpage
+\appendix
+\section{Example Programs}
+
+In this appendix, we provide examples of probabilistic logic programs generated
+by various combinations of parameters. In all cases, we use
+\[
+  \{ 0.1, 0.2, \dots, 0.9, 1, 1, 1, 1, 1\}
+\]
+as the multiset of probabilities. Each clause is written on a separate line and
+ends with a full stop. The head and the body of each clause are separated with
+\texttt{:-} (instead of $\gets$). The probability of each clause is prepended to
+the clause, using \texttt{::} as a separator. Probabilities equal to one and
+empty bodies of clauses can be omitted. Conjunction, disjunction, and negation
+are denoted by commas, semicolons, and `\texttt{\textbackslash+}', respectively.
+Parentheses are used to demonstrate precedence, although many of them are
+redundant.
+
+By setting $\predicates{} = [\texttt{p}]$, $\arities{} = [1]$, $\variables{} =
+\{ \texttt{X} \}$, $\constants{} = \emptyset$, $\maxNumNodes{} = 4$, and
+$\maxNumClauses{} = 1$, we get fifteen one-line programs, six of which are
+without negative cycles (as highlighted below). Only the last program has no
+cycles at all.
+
+\begin{enumerate}[label=\arabic*.]
+\item
+\begin{verbatim}
+0.5 :: p(X) :- (\+(p(X))), (p(X)).
+\end{verbatim}
+\item
+\begin{verbatim}
+0.8 :: p(X) :- (\+(p(X))); (p(X)).
+\end{verbatim}
+\hlitem
+\begin{verbatim}
+0.8 :: p(X) :- (p(X)); (p(X)).
+\end{verbatim}
+\hlitem
+\begin{verbatim}
+0.7 :: p(X) :- (p(X)), (p(X)).
+\end{verbatim}
+\item
+\begin{verbatim}
+0.6 :: p(X) :- (p(X)), (\+(p(X))).
+\end{verbatim}
+\item
+\begin{verbatim}
+p(X) :- (p(X)); (\+(p(X))).
+\end{verbatim}
+\hlitem
+\begin{verbatim}
+0.1 :: p(X) :- (p(X)); (p(X)); (p(X)).
+\end{verbatim}
+\hlitem
+\begin{verbatim}
+0.8 :: p(X) :- (p(X)), (p(X)), (p(X)).
+\end{verbatim}
+\item
+\begin{verbatim}
+p(X) :- \+(p(X)).
+\end{verbatim}
+\item
+\begin{verbatim}
+0.1 :: p(X) :- \+(\+(p(X))).
+\end{verbatim}
+\item
+\begin{verbatim}
+p(X) :- \+((p(X)); (p(X))).
+\end{verbatim}
+\item
+\begin{verbatim}
+0.4 :: p(X) :- \+((p(X)), (p(X))).
+\end{verbatim}
+\item
+\begin{verbatim}
+0.4 :: p(X) :- \+(\+(\+(p(X)))).
+\end{verbatim}
+\hlitem
+\begin{verbatim}
+0.7 :: p(X) :- p(X).
+\end{verbatim}
+\hlitem
+\begin{verbatim}
+p(X).
+\end{verbatim}
+\end{enumerate}
+
+Note that:
+\begin{itemize}
+\item A program such as Program~14, because of its cyclic definition, defines a
+  predicate that has probability zero across all constants. This can more easily
+  be seen as solving equation $0.7x = x$.
+\item Programs 10 and 14 are not equivalent (i.e., double negation does not
+  cancel out) because Program 10 has a negative cycle and is thus considered to
+  be ill-defined.
+\end{itemize}
+
+To demonstrate variable symmetry reduction in action, we set $\predicates{} =
+[\texttt{p}]$, $\arities{} = [3]$, $\variables{} = \{\texttt{X}, \texttt{Y},
+\texttt{Z} \}$, $\constants{} = \emptyset$, $\maxNumNodes{} = 1$,
+$\maxNumClauses{} = 1$, and forbid all cycles. This gives us the following five
+programs:
+
+\begin{itemize}
+\item
+\begin{verbatim}
+0.8 :: p(Z, Z, Z).
+\end{verbatim}
+\item
+\begin{verbatim}
+p(Y, Y, Z).
+\end{verbatim}
+\item
+\begin{verbatim}
+p(Y, Z, Z).
+\end{verbatim}
+\item
+\begin{verbatim}
+p(Y, Z, Y).
+\end{verbatim}
+\item
+\begin{verbatim}
+0.1 :: p(X, Y, Z).
+\end{verbatim}
+\end{itemize}
+
+This is one of many possible programs with $\predicates{} = [\texttt{p},
+\texttt{q}, \texttt{r}]$, $\arities{} = [1, 2, 3]$, $\variables{} =
+\{\texttt{X}, \texttt{Y}, \texttt{Z} \}$, $\constants{} = \{ \texttt{a},
+\texttt{b}, \texttt{c} \}$, $\maxNumNodes{} = 5$, $\maxNumClauses{} = 5$, and
+without negative cycles:
+
+\begin{verbatim}
+p(b) :- \+((q(a, b)), (q(X, Y)), (q(Z, X))).
+0.4 :: q(X, X) :- \+(r(Y, Z, a)).
+q(X, a) :- r(Y, Y, Z).
+q(X, a) :- r(Y, b, Z).
+r(Y, b, Z).
+\end{verbatim}
+
+Finally, we set
+$\predicates{} = [\texttt{p}, \texttt{q}, \texttt{r}]$, $\arities{} = [1, 1,
+1]$, $\variables{} = \emptyset$, $\constants{} = \{ \texttt{a} \}$,
+$\maxNumNodes{} = 3$, $\maxNumClauses{} = 3$, forbid negative cycles, and
+constrain predicates \texttt{p} and \texttt{q} to be independent. The resulting
+search space contains thousands of programs such as:
+
+\begin{itemize}
+\item
+\begin{verbatim}
+0.5 :: p(a) :- (p(a)); (p(a)).
+0.2 :: q(a) :- (q(a)), (q(a)).
+0.4 :: r(a) :- \+(q(a)).
+\end{verbatim}
+\item
+\begin{verbatim}
+p(a) :- p(a).
+0.5 :: q(a) :- (r(a)); (q(a)).
+r(a) :- (r(a)); (r(a)).
+\end{verbatim}
+\item
+\begin{verbatim}
+p(a) :- (p(a)); (p(a)).
+0.6 :: q(a) :- q(a).
+0.7 :: r(a) :- \+(q(a)).
+\end{verbatim}
+\end{itemize}
+
 \end{document}

### 2020-10-19 talks/aiai_seminar/line_plots.tex
One more presentation

% Created by tikzDevice version 0.12.3 on 2020-07-22 15:14:14
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (303.53,130.09);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (303.53,130.09);
\end{scope}
\begin{scope}
\path[clip] ( 31.71, 30.69) rectangle (124.41,108.01);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 31.71, 30.69) rectangle (124.41,108.01);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 46.03) --
	(124.41, 46.03);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 69.81) --
	(124.41, 69.81);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 93.59) --
	(124.41, 93.59);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.35, 30.69) --
	( 46.35,108.01);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 67.45, 30.69) --
	( 67.45,108.01);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 88.54, 30.69) --
	( 88.54,108.01);

\path[draw=drawColor,line width= 0.3pt,line join=round] (109.64, 30.69) --
	(109.64,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71, 34.14) --
	(124.41, 34.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71, 57.92) --
	(124.41, 57.92);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71, 81.70) --
	(124.41, 81.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71,105.48) --
	(124.41,105.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.80, 30.69) --
	( 35.80,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.90, 30.69) --
	( 56.90,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.00, 30.69) --
	( 78.00,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 99.09, 30.69) --
	( 99.09,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.19, 30.69) --
	(120.19,108.01);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.93, 34.22) --
	( 36.05, 34.28) --
	( 36.31, 34.45) --
	( 36.64, 34.74) --
	( 36.81, 34.74) --
	( 37.82, 35.27) --
	( 42.19, 37.45) --
	( 42.32, 36.38) --
	( 42.57, 37.84) --
	( 44.24, 39.46) --
	( 48.46, 41.24) --
	( 48.58, 41.31) --
	( 48.84, 41.51) --
	( 54.85, 45.33) --
	( 55.10, 45.62) --
	( 61.12, 50.08) --
	( 61.24, 47.64) --
	( 61.37, 50.15) --
	( 61.50, 46.59) --
	( 62.00, 54.70) --
	( 67.64, 53.02) --
	( 73.90, 56.41) --
	( 80.17, 57.95) --
	( 86.43, 74.63) --
	( 86.69, 65.78) --
	( 87.19, 64.84) --
	(111.88, 79.54) --
	(112.39, 78.48) --
	(120.19, 91.54);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 35.93, 34.20) --
	( 36.05, 34.26) --
	( 36.31, 34.41) --
	( 36.64, 34.70) --
	( 36.81, 34.68) --
	( 37.82, 35.23) --
	( 42.19, 37.74) --
	( 42.32, 37.05) --
	( 42.57, 37.14) --
	( 44.24, 39.19) --
	( 48.46, 42.35) --
	( 48.58, 40.98) --
	( 48.84, 41.86) --
	( 54.85, 44.75) --
	( 55.10, 45.01) --
	( 61.12, 48.70) --
	( 61.24, 46.51) --
	( 61.37, 47.05) --
	( 61.50, 47.32) --
	( 62.00, 49.64) --
	( 67.64, 52.22) --
	( 73.90, 55.11) --
	( 80.17, 58.33) --
	( 86.43, 75.16) --
	( 86.69, 59.59) --
	( 87.19, 62.82) --
	(111.88, 75.24) --
	(112.39, 79.11) --
	(120.19, 88.23);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 35.93, 34.22) --
	( 36.05, 34.33) --
	( 36.31, 34.49) --
	( 36.64, 34.77) --
	( 36.81, 34.77) --
	( 37.82, 35.37) --
	( 42.19, 37.40) --
	( 42.32, 36.84) --
	( 42.57, 37.68) --
	( 44.24, 39.58) --
	( 48.46, 42.81) --
	( 48.58, 41.77) --
	( 48.84, 40.98) --
	( 54.85, 45.16) --
	( 55.10, 45.74) --
	( 61.12, 47.31) --
	( 61.24, 46.52) --
	( 61.37, 48.59) --
	( 61.50, 46.96) --
	( 62.00, 47.72) --
	( 67.64, 52.99) --
	( 73.90, 57.55) --
	( 80.17, 56.42) --
	( 86.43, 71.23) --
	( 86.69, 62.93) --
	( 87.19, 67.49) --
	(111.88, 75.36) --
	(112.39, 79.09) --
	(120.19, 90.92);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 35.93, 34.22) --
	( 36.05, 34.29) --
	( 36.31, 34.48) --
	( 36.64, 34.79) --
	( 36.81, 34.74) --
	( 37.82, 35.45) --
	( 42.19, 37.64) --
	( 42.32, 37.18) --
	( 42.57, 37.98) --
	( 44.24, 40.20) --
	( 48.46, 44.88) --
	( 48.58, 42.06) --
	( 48.84, 40.35) --
	( 54.85, 45.65) --
	( 55.10, 47.25) --
	( 61.12, 51.25) --
	( 61.24, 51.16) --
	( 61.37, 51.25) --
	( 61.50, 52.79) --
	( 62.00, 51.87) --
	( 67.64, 54.08) --
	( 73.90, 57.97) --
	( 80.17, 61.03) --
	( 86.43, 76.47) --
	( 86.69, 65.20) --
	( 87.19, 59.83) --
	(111.88, 84.66) --
	(112.39, 85.31) --
	(120.19, 99.29);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round] ( 35.93, 34.24) --
	( 36.05, 34.31) --
	( 36.31, 34.48) --
	( 36.64, 34.81) --
	( 36.81, 34.77) --
	( 37.82, 35.45) --
	( 42.19, 37.88) --
	( 42.32, 38.54) --
	( 42.57, 38.69) --
	( 44.24, 39.95) --
	( 48.46, 42.70) --
	( 48.58, 41.93) --
	( 48.84, 41.20) --
	( 54.85, 46.14) --
	( 55.10, 46.43) --
	( 61.12, 50.70) --
	( 61.24, 47.87) --
	( 61.37, 50.28) --
	( 61.50, 47.98) --
	( 62.00, 52.07) --
	( 67.64, 55.24) --
	( 73.90, 59.51) --
	( 80.17, 61.81) --
	( 86.43, 82.15) --
	( 86.69, 68.77) --
	( 87.19, 67.98) --
	(111.88, 80.43) --
	(112.39, 80.51) --
	(120.19, 97.30);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt on 4pt off 3pt ,line join=round] ( 35.93, 34.20) --
	( 36.05, 34.32) --
	( 36.31, 34.47) --
	( 36.64, 34.80) --
	( 36.81, 34.78) --
	( 37.82, 35.44) --
	( 42.19, 37.83) --
	( 42.32, 36.07) --
	( 42.57, 38.73) --
	( 44.24, 40.20) --
	( 48.46, 44.23) --
	( 48.58, 43.29) --
	( 48.84, 40.97) --
	( 54.85, 46.70) --
	( 55.10, 47.28) --
	( 61.12, 50.76) --
	( 61.24, 52.81) --
	( 61.37, 51.86) --
	( 61.50, 53.84) --
	( 62.00, 51.03) --
	( 67.64, 54.08) --
	( 73.90, 59.44) --
	( 80.17, 63.01) --
	( 86.43, 79.72) --
	( 86.69, 66.18) --
	( 87.19, 66.97) --
	(111.88, 83.22) --
	(112.39, 87.08) --
	(120.19, 98.99);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.71, 30.69) rectangle (124.41,108.01);
\end{scope}
\begin{scope}
\path[clip] (129.91, 30.69) rectangle (222.60,108.01);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (129.91, 30.69) rectangle (222.60,108.01);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (129.91, 46.03) --
	(222.60, 46.03);

\path[draw=drawColor,line width= 0.3pt,line join=round] (129.91, 69.81) --
	(222.60, 69.81);

\path[draw=drawColor,line width= 0.3pt,line join=round] (129.91, 93.59) --
	(222.60, 93.59);

\path[draw=drawColor,line width= 0.3pt,line join=round] (144.65, 30.69) --
	(144.65,108.01);

\path[draw=drawColor,line width= 0.3pt,line join=round] (165.72, 30.69) --
	(165.72,108.01);

\path[draw=drawColor,line width= 0.3pt,line join=round] (186.79, 30.69) --
	(186.79,108.01);

\path[draw=drawColor,line width= 0.3pt,line join=round] (207.85, 30.69) --
	(207.85,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (129.91, 34.14) --
	(222.60, 34.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (129.91, 57.92) --
	(222.60, 57.92);

\path[draw=drawColor,line width= 0.6pt,line join=round] (129.91, 81.70) --
	(222.60, 81.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] (129.91,105.48) --
	(222.60,105.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] (134.12, 30.69) --
	(134.12,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (155.19, 30.69) --
	(155.19,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (176.25, 30.69) --
	(176.25,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (197.32, 30.69) --
	(197.32,108.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (218.39, 30.69) --
	(218.39,108.01);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (134.12, 87.17) --
	(137.13, 93.17) --
	(143.15, 93.97) --
	(146.16, 85.86) --
	(148.16, 95.63) --
	(158.20, 90.99) --
	(161.20, 86.16) --
	(170.23, 88.72) --
	(179.26, 93.71) --
	(182.27, 85.21) --
	(185.28, 88.26) --
	(190.30, 81.94) --
	(191.30, 84.46) --
	(194.31, 82.43) --
	(197.32, 92.42) --
	(200.33, 95.04) --
	(203.34, 93.76) --
	(212.37, 84.82) --
	(215.38, 89.64) --
	(218.39, 94.51);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (134.12, 81.98) --
	(137.13, 87.03) --
	(143.15, 90.51) --
	(146.16, 84.86) --
	(148.16, 90.95) --
	(158.20, 87.07) --
	(161.20, 82.10) --
	(170.23, 86.31) --
	(179.26, 91.58) --
	(182.27, 81.17) --
	(185.28, 86.92) --
	(190.30, 82.36) --
	(191.30, 81.20) --
	(194.31, 82.46) --
	(197.32, 88.61) --
	(200.33, 93.14) --
	(203.34, 91.31) --
	(212.37, 83.85) --
	(215.38, 86.37) --
	(218.39, 89.25);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (134.12, 88.97) --
	(137.13, 89.35) --
	(143.15, 92.54) --
	(146.16, 85.10) --
	(148.16, 93.89) --
	(158.20, 90.38) --
	(161.20, 87.37) --
	(170.23, 88.45) --
	(179.26, 94.07) --
	(182.27, 82.90) --
	(185.28, 88.35) --
	(190.30, 81.32) --
	(191.30, 84.81) --
	(194.31, 85.30) --
	(197.32, 90.02) --
	(200.33, 93.14) --
	(203.34, 94.41) --
	(212.37, 85.94) --
	(215.38, 89.62) --
	(218.39, 93.56);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (134.12, 95.74) --
	(137.13, 96.35) --
	(143.15,104.50) --
	(146.16, 94.79) --
	(148.16,102.91) --
	(158.20,101.65) --
	(161.20, 94.35) --
	(170.23, 98.68) --
	(179.26,103.55) --
	(182.27, 88.20) --
	(185.28, 97.47) --
	(190.30, 89.92) --
	(191.30, 91.22) --
	(194.31, 87.06) --
	(197.32, 98.75) --
	(200.33,102.58) --
	(203.34,102.50) --
	(212.37, 90.37) --
	(215.38, 96.15) --
	(218.39,100.82);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round] (134.12, 90.34) --
	(137.13,100.33) --
	(143.15, 97.34) --
	(146.16, 90.63) --
	(148.16, 99.99) --
	(158.20, 96.75) --
	(161.20, 91.32) --
	(170.23, 97.00) --
	(179.26,100.90) --
	(182.27, 88.11) --
	(185.28, 94.51) --
	(190.30, 92.66) --
	(191.30, 90.99) --
	(194.31, 92.19) --
	(197.32, 96.98) --
	(200.33, 99.26) --
	(203.34,100.29) --
	(212.37, 92.01) --
	(215.38, 93.41) --
	(218.39, 99.52);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt on 4pt off 3pt ,line join=round] (134.12, 90.96) --
	(137.13, 96.67) --
	(143.15,104.39) --
	(146.16, 90.59) --
	(148.16,102.58) --
	(158.20,100.48) --
	(161.20, 95.50) --
	(170.23, 97.48) --
	(179.26,103.31) --
	(182.27, 90.87) --
	(185.28, 97.96) --
	(190.30, 87.48) --
	(191.30, 91.85) --
	(194.31, 91.08) --
	(197.32, 98.02) --
	(200.33,100.29) --
	(203.34,102.81) --
	(212.37, 90.81) --
	(215.38, 95.58) --
	(218.39,101.07);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (129.91, 30.69) rectangle (222.60,108.01);
\end{scope}
\begin{scope}
\path[clip] ( 31.71,108.01) rectangle (124.41,124.59);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,108.01) rectangle (124.41,124.59);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 78.06,113.27) {Facts ($\times 10^3$)};
\end{scope}
\begin{scope}
\path[clip] (129.91,108.01) rectangle (222.60,124.59);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (129.91,108.01) rectangle (222.60,124.59);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (176.25,113.27) {Prop. independent};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.80, 27.94) --
	( 35.80, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.90, 27.94) --
	( 56.90, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.00, 27.94) --
	( 78.00, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 99.09, 27.94) --
	( 99.09, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.19, 27.94) --
	(120.19, 30.69);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.80, 19.68) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 56.90, 19.68) {25};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 78.00, 19.68) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 99.09, 19.68) {75};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (120.19, 19.68) {100};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (134.12, 27.94) --
	(134.12, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (155.19, 27.94) --
	(155.19, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (176.25, 27.94) --
	(176.25, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (197.32, 27.94) --
	(197.32, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (218.39, 27.94) --
	(218.39, 30.69);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (134.12, 19.68) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (155.19, 19.68) {0.25};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (176.25, 19.68) {0.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (197.32, 19.68) {0.75};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (218.39, 19.68) {1};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76, 31.11) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76, 54.89) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76, 78.67) {20};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76,102.45) {30};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96, 34.14) --
	( 31.71, 34.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96, 57.92) --
	( 31.71, 57.92);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96, 81.70) --
	( 31.71, 81.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,105.48) --
	( 31.71,105.48);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08, 69.35) {Mean inference time (s)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (233.60, 12.88) rectangle (298.03,125.82);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at (239.10,111.67) {Algorithm};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (239.10, 90.65) rectangle (253.55,105.10);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (240.54, 97.88) -- (252.11, 97.88);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (239.10, 76.20) rectangle (253.55, 90.65);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (240.54, 83.42) -- (252.11, 83.42);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (239.10, 61.74) rectangle (253.55, 76.20);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (240.54, 68.97) -- (252.11, 68.97);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (239.10, 47.29) rectangle (253.55, 61.74);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (240.54, 54.52) -- (252.11, 54.52);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (239.10, 32.83) rectangle (253.55, 47.29);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round] (240.54, 40.06) -- (252.11, 40.06);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (239.10, 18.38) rectangle (253.55, 32.83);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt on 4pt off 3pt ,line join=round] (240.54, 25.61) -- (252.11, 25.61);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (259.05, 94.85) {BDD};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (259.05, 80.39) {d-DNNF};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (259.05, 65.94) {K-Best};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (259.05, 51.49) {NNF};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (259.05, 37.03) {SDD};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (259.05, 22.58) {SDDX};
\end{scope}
\end{tikzpicture}

### 2020-10-19 talks/aiai_seminar/talk.tex
One more presentation

--- 2020-08-16 conference_talk/talk.tex
@@
 
-\author{\textbf{Paulius Dilkas}\inst{1} \and Vaishak Belle\inst{1,2}}
+\author{\textbf{Paulius Dilkas} \and Vaishak Belle}
 \title{Generating Random Logic Programs Using Constraint Programming}
-\date{CP 2020}
-\institute{\inst{1} University of Edinburgh, Edinburgh, UK \and \inst{2} Alan
-  Turing Institute, London, UK}
+\date{AIAI Seminar}
 
@@
 
-\begin{frame}{What Characterizes a (Probabilistic) Logic Program?}
+\begin{frame}{What Characterises a (Probabilistic) Logic Program?}
   \begin{columns}
@@
 
-\begin{frame}{Scalability}
-  \centering
-  \input{impact.tex}
-\end{frame}
-
 \section{Inference}
@@
   \item[SDD] sentential decision diagrams
-  \item[$k$-Best] only use the \alert{$k$} most probable proofs
-%    \begin{itemize}
-%    \item<2-> for every pair \alert{$\alpha \lor \beta$}, we have \alert{$\alpha
-%        \land \beta = \bot$}
-%    \item<2-> for every pair \alert{$\alpha \land \beta$}, no atoms are shared
-%      between \alert{$\alpha$} and \alert{$\beta$}
-%    \end{itemize}
   \end{description}
@@
 
-\begin{frame}{Properties of Programs vs. Inference Algorithms}
-  \centering
-  \input{../paper/bars.tex}
-\end{frame}
+%\begin{frame}{Properties of Programs vs. Inference Algorithms}
+%  \centering
+%  \input{../../paper/bars.tex}
+%\end{frame}
 
-\section{Conclusions}
+\section{Summary}
 
-\begin{frame}{Conclusions and Future Work}
+\begin{frame}{Summary}
   \begin{itemize}
   \item The model can generate (approximately) realistic instances of reasonable
-    size
-  \item The main performance bottleneck can be addressed by generating programs
-    with a simpler structure
-  \item Open questions for future work
+    size.
+  \item Open questions for future work:
     \begin{itemize}
-    \item Can the model be used to ensure uniform sampling?
-    \item What is the reason behind all algorithms behaving similarly?
+    \item Can we ensure uniform sampling?
+    \item Why do all of the algorithms behave so similarly?
     \item Why does independence have no effect on inference time?
-%    \item Can random program generation be useful in learning?
     \end{itemize}
   \end{itemize}
-  \begin{block}{The implementation of the model is available at}
-    \url{https://github.com/dilkas/random-logic-programs}
-  \end{block}
 \end{frame}
-
 \end{document}

### 2020-10-19 talks/fata_seminar/proportion.tex
One more presentation

% Created by tikzDevice version 0.12.3 on 2020-08-12 18:22:39
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (303.53,130.09);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (303.53,130.09);
\end{scope}
\begin{scope}
\path[clip] ( 31.71, 30.69) rectangle (222.60,124.59);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 31.71, 30.69) rectangle (222.60,124.59);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 48.66) --
	(222.60, 48.66);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 78.98) --
	(222.60, 78.98);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71,109.30) --
	(222.60,109.30);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 63.53, 30.69) --
	( 63.53,124.59);

\path[draw=drawColor,line width= 0.3pt,line join=round] (109.80, 30.69) --
	(109.80,124.59);

\path[draw=drawColor,line width= 0.3pt,line join=round] (156.08, 30.69) --
	(156.08,124.59);

\path[draw=drawColor,line width= 0.3pt,line join=round] (202.35, 30.69) --
	(202.35,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71, 33.50) --
	(222.60, 33.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71, 63.82) --
	(222.60, 63.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71, 94.14) --
	(222.60, 94.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71,124.46) --
	(222.60,124.46);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.39, 30.69) --
	( 40.39,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 86.66, 30.69) --
	( 86.66,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (132.94, 30.69) --
	(132.94,124.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (179.22, 30.69) --
	(179.22,124.59);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 40.39, 35.39) --
	( 42.59, 77.68) --
	( 44.78, 88.52) --
	( 46.98, 98.54) --
	( 49.18,105.04) --
	( 51.37,108.74) --
	( 53.57,110.31) --
	( 55.77,110.47) --
	( 57.96,109.90) --
	( 60.16,109.20) --
	( 62.36,108.50) --
	( 64.55,107.80) --
	( 66.75,107.10) --
	( 68.95,106.41) --
	( 71.14,105.71) --
	( 73.34,105.02) --
	( 75.53,104.33) --
	( 77.73,103.64) --
	( 79.93,102.95) --
	( 82.12,102.27) --
	( 84.32,101.58) --
	( 86.52,100.90) --
	( 88.71,100.22) --
	( 90.91, 99.54) --
	( 93.11, 98.86) --
	( 95.30, 98.18) --
	( 97.50, 97.50) --
	( 99.70, 96.83) --
	(101.89, 96.16) --
	(104.09, 95.48) --
	(106.29, 94.81) --
	(108.48, 94.14) --
	(110.68, 93.47) --
	(112.88, 92.80) --
	(115.07, 92.14) --
	(117.27, 91.47) --
	(119.47, 90.81) --
	(121.66, 90.14) --
	(123.86, 89.48) --
	(126.06, 88.82) --
	(128.25, 88.16) --
	(130.45, 87.50) --
	(132.65, 86.84) --
	(134.84, 86.18) --
	(137.04, 85.53) --
	(139.24, 84.87) --
	(141.43, 84.21) --
	(143.63, 83.56) --
	(145.83, 82.91) --
	(148.02, 82.25) --
	(150.22, 81.60) --
	(152.42, 80.95) --
	(154.61, 80.30) --
	(156.81, 79.65) --
	(159.01, 79.00) --
	(161.20, 78.35) --
	(163.40, 77.70) --
	(165.60, 77.05) --
	(167.79, 76.41) --
	(169.99, 75.76) --
	(172.19, 75.11) --
	(174.38, 74.47) --
	(176.58, 73.82) --
	(178.78, 73.18) --
	(180.97, 72.53) --
	(183.17, 71.89) --
	(185.37, 71.25) --
	(187.56, 70.60) --
	(189.76, 69.96) --
	(191.96, 69.32) --
	(194.15, 68.67) --
	(196.35, 68.03) --
	(198.55, 67.39) --
	(200.74, 66.75) --
	(202.94, 66.10) --
	(205.14, 65.46) --
	(207.33, 64.82) --
	(209.53, 64.18) --
	(211.73, 63.54) --
	(213.92, 62.90);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 40.39, 34.95) --
	( 42.59, 75.01) --
	( 44.78, 84.87) --
	( 46.98, 94.16) --
	( 49.18,100.19) --
	( 51.37,103.60) --
	( 53.57,105.04) --
	( 55.77,105.17) --
	( 57.96,104.62) --
	( 60.16,103.95) --
	( 62.36,103.28) --
	( 64.55,102.61) --
	( 66.75,101.95) --
	( 68.95,101.28) --
	( 71.14,100.63) --
	( 73.34, 99.97) --
	( 75.53, 99.31) --
	( 77.73, 98.66) --
	( 79.93, 98.01) --
	( 82.12, 97.36) --
	( 84.32, 96.71) --
	( 86.52, 96.07) --
	( 88.71, 95.42) --
	( 90.91, 94.78) --
	( 93.11, 94.14) --
	( 95.30, 93.51) --
	( 97.50, 92.87) --
	( 99.70, 92.24) --
	(101.89, 91.61) --
	(104.09, 90.98) --
	(106.29, 90.35) --
	(108.48, 89.72) --
	(110.68, 89.10) --
	(112.88, 88.47) --
	(115.07, 87.85) --
	(117.27, 87.23) --
	(119.47, 86.61) --
	(121.66, 85.99) --
	(123.86, 85.38) --
	(126.06, 84.76) --
	(128.25, 84.15) --
	(130.45, 83.54) --
	(132.65, 82.93) --
	(134.84, 82.32) --
	(137.04, 81.71) --
	(139.24, 81.10) --
	(141.43, 80.50) --
	(143.63, 79.89) --
	(145.83, 79.29) --
	(148.02, 78.69) --
	(150.22, 78.08) --
	(152.42, 77.48) --
	(154.61, 76.88) --
	(156.81, 76.28) --
	(159.01, 75.69) --
	(161.20, 75.09) --
	(163.40, 74.49) --
	(165.60, 73.90) --
	(167.79, 73.30) --
	(169.99, 72.71) --
	(172.19, 72.12) --
	(174.38, 71.52) --
	(176.58, 70.93) --
	(178.78, 70.34) --
	(180.97, 69.75) --
	(183.17, 69.16) --
	(185.37, 68.57) --
	(187.56, 67.98) --
	(189.76, 67.39) --
	(191.96, 66.80) --
	(194.15, 66.22) --
	(196.35, 65.63) --
	(198.55, 65.04) --
	(200.74, 64.45) --
	(202.94, 63.86) --
	(205.14, 63.28) --
	(207.33, 62.69) --
	(209.53, 62.10) --
	(211.73, 61.52) --
	(213.92, 60.93);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 40.39, 35.09) --
	( 42.59, 76.60) --
	( 44.78, 87.21) --
	( 46.98, 97.28) --
	( 49.18,103.82) --
	( 51.37,107.54) --
	( 53.57,109.13) --
	( 55.77,109.29) --
	( 57.96,108.72) --
	( 60.16,108.02) --
	( 62.36,107.32) --
	( 64.55,106.62) --
	( 66.75,105.93) --
	( 68.95,105.23) --
	( 71.14,104.54) --
	( 73.34,103.85) --
	( 75.53,103.17) --
	( 77.73,102.48) --
	( 79.93,101.80) --
	( 82.12,101.12) --
	( 84.32,100.44) --
	( 86.52, 99.76) --
	( 88.71, 99.08) --
	( 90.91, 98.41) --
	( 93.11, 97.74) --
	( 95.30, 97.07) --
	( 97.50, 96.40) --
	( 99.70, 95.73) --
	(101.89, 95.06) --
	(104.09, 94.40) --
	(106.29, 93.73) --
	(108.48, 93.07) --
	(110.68, 92.41) --
	(112.88, 91.75) --
	(115.07, 91.10) --
	(117.27, 90.44) --
	(119.47, 89.78) --
	(121.66, 89.13) --
	(123.86, 88.48) --
	(126.06, 87.83) --
	(128.25, 87.18) --
	(130.45, 86.53) --
	(132.65, 85.88) --
	(134.84, 85.23) --
	(137.04, 84.59) --
	(139.24, 83.94) --
	(141.43, 83.30) --
	(143.63, 82.66) --
	(145.83, 82.02) --
	(148.02, 81.38) --
	(150.22, 80.74) --
	(152.42, 80.10) --
	(154.61, 79.46) --
	(156.81, 78.82) --
	(159.01, 78.19) --
	(161.20, 77.55) --
	(163.40, 76.92) --
	(165.60, 76.28) --
	(167.79, 75.65) --
	(169.99, 75.02) --
	(172.19, 74.38) --
	(174.38, 73.75) --
	(176.58, 73.12) --
	(178.78, 72.49) --
	(180.97, 71.86) --
	(183.17, 71.23) --
	(185.37, 70.60) --
	(187.56, 69.97) --
	(189.76, 69.34) --
	(191.96, 68.71) --
	(194.15, 68.09) --
	(196.35, 67.46) --
	(198.55, 66.83) --
	(200.74, 66.20) --
	(202.94, 65.58) --
	(205.14, 64.95) --
	(207.33, 64.32) --
	(209.53, 63.70) --
	(211.73, 63.07) --
	(213.92, 62.44);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 40.39, 35.45) --
	( 42.59, 84.78) --
	( 44.78, 96.38) --
	( 46.98,107.26) --
	( 49.18,114.27) --
	( 51.37,118.18) --
	( 53.57,119.76) --
	( 55.77,119.78) --
	( 57.96,119.00) --
	( 60.16,118.08) --
	( 62.36,117.17) --
	( 64.55,116.27) --
	( 66.75,115.37) --
	( 68.95,114.49) --
	( 71.14,113.60) --
	( 73.34,112.73) --
	( 75.53,111.86) --
	( 77.73,111.00) --
	( 79.93,110.15) --
	( 82.12,109.30) --
	( 84.32,108.45) --
	( 86.52,107.62) --
	( 88.71,106.79) --
	( 90.91,105.97) --
	( 93.11,105.15) --
	( 95.30,104.34) --
	( 97.50,103.53) --
	( 99.70,102.73) --
	(101.89,101.93) --
	(104.09,101.14) --
	(106.29,100.36) --
	(108.48, 99.58) --
	(110.68, 98.80) --
	(112.88, 98.03) --
	(115.07, 97.27) --
	(117.27, 96.51) --
	(119.47, 95.75) --
	(121.66, 95.00) --
	(123.86, 94.26) --
	(126.06, 93.51) --
	(128.25, 92.78) --
	(130.45, 92.04) --
	(132.65, 91.31) --
	(134.84, 90.59) --
	(137.04, 89.86) --
	(139.24, 89.15) --
	(141.43, 88.43) --
	(143.63, 87.72) --
	(145.83, 87.01) --
	(148.02, 86.31) --
	(150.22, 85.61) --
	(152.42, 84.91) --
	(154.61, 84.21) --
	(156.81, 83.52) --
	(159.01, 82.83) --
	(161.20, 82.14) --
	(163.40, 81.46) --
	(165.60, 80.77) --
	(167.79, 80.09) --
	(169.99, 79.42) --
	(172.19, 78.74) --
	(174.38, 78.07) --
	(176.58, 77.39) --
	(178.78, 76.72) --
	(180.97, 76.06) --
	(183.17, 75.39) --
	(185.37, 74.72) --
	(187.56, 74.06) --
	(189.76, 73.40) --
	(191.96, 72.73) --
	(194.15, 72.07) --
	(196.35, 71.41) --
	(198.55, 70.76) --
	(200.74, 70.10) --
	(202.94, 69.44) --
	(205.14, 68.78) --
	(207.33, 68.13) --
	(209.53, 67.47) --
	(211.73, 66.82) --
	(213.92, 66.16);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 1pt off 3pt ,line join=round] ( 40.39, 35.39) --
	( 42.59, 82.00) --
	( 44.78, 94.11) --
	( 46.98,105.31) --
	( 49.18,112.55) --
	( 51.37,116.62) --
	( 53.57,118.30) --
	( 55.77,118.38) --
	( 57.96,117.65) --
	( 60.16,116.77) --
	( 62.36,115.90) --
	( 64.55,115.03) --
	( 66.75,114.17) --
	( 68.95,113.32) --
	( 71.14,112.47) --
	( 73.34,111.63) --
	( 75.53,110.79) --
	( 77.73,109.96) --
	( 79.93,109.13) --
	( 82.12,108.31) --
	( 84.32,107.50) --
	( 86.52,106.69) --
	( 88.71,105.88) --
	( 90.91,105.08) --
	( 93.11,104.28) --
	( 95.30,103.49) --
	( 97.50,102.71) --
	( 99.70,101.92) --
	(101.89,101.15) --
	(104.09,100.37) --
	(106.29, 99.60) --
	(108.48, 98.84) --
	(110.68, 98.08) --
	(112.88, 97.32) --
	(115.07, 96.57) --
	(117.27, 95.82) --
	(119.47, 95.08) --
	(121.66, 94.34) --
	(123.86, 93.60) --
	(126.06, 92.87) --
	(128.25, 92.14) --
	(130.45, 91.41) --
	(132.65, 90.69) --
	(134.84, 89.97) --
	(137.04, 89.25) --
	(139.24, 88.54) --
	(141.43, 87.83) --
	(143.63, 87.12) --
	(145.83, 86.41) --
	(148.02, 85.71) --
	(150.22, 85.01) --
	(152.42, 84.31) --
	(154.61, 83.62) --
	(156.81, 82.92) --
	(159.01, 82.23) --
	(161.20, 81.54) --
	(163.40, 80.86) --
	(165.60, 80.17) --
	(167.79, 79.49) --
	(169.99, 78.81) --
	(172.19, 78.13) --
	(174.38, 77.45) --
	(176.58, 76.78) --
	(178.78, 76.10) --
	(180.97, 75.43) --
	(183.17, 74.76) --
	(185.37, 74.09) --
	(187.56, 73.42) --
	(189.76, 72.75) --
	(191.96, 72.09) --
	(194.15, 71.42) --
	(196.35, 70.75) --
	(198.55, 70.09) --
	(200.74, 69.42) --
	(202.94, 68.76) --
	(205.14, 68.10) --
	(207.33, 67.44) --
	(209.53, 66.77) --
	(211.73, 66.11) --
	(213.92, 65.45);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 1pt off 3pt on 4pt off 3pt ,line join=round] ( 40.39, 35.44) --
	( 42.59, 84.85) --
	( 44.78, 96.76) --
	( 46.98,107.71) --
	( 49.18,114.77) --
	( 51.37,118.71) --
	( 53.57,120.30) --
	( 55.77,120.32) --
	( 57.96,119.54) --
	( 60.16,118.61) --
	( 62.36,117.70) --
	( 64.55,116.79) --
	( 66.75,115.89) --
	( 68.95,115.00) --
	( 71.14,114.12) --
	( 73.34,113.24) --
	( 75.53,112.37) --
	( 77.73,111.50) --
	( 79.93,110.64) --
	( 82.12,109.79) --
	( 84.32,108.95) --
	( 86.52,108.11) --
	( 88.71,107.28) --
	( 90.91,106.45) --
	( 93.11,105.63) --
	( 95.30,104.82) --
	( 97.50,104.01) --
	( 99.70,103.21) --
	(101.89,102.41) --
	(104.09,101.62) --
	(106.29,100.83) --
	(108.48,100.05) --
	(110.68, 99.27) --
	(112.88, 98.50) --
	(115.07, 97.74) --
	(117.27, 96.97) --
	(119.47, 96.22) --
	(121.66, 95.47) --
	(123.86, 94.72) --
	(126.06, 93.97) --
	(128.25, 93.24) --
	(130.45, 92.50) --
	(132.65, 91.77) --
	(134.84, 91.04) --
	(137.04, 90.32) --
	(139.24, 89.60) --
	(141.43, 88.89) --
	(143.63, 88.18) --
	(145.83, 87.47) --
	(148.02, 86.76) --
	(150.22, 86.06) --
	(152.42, 85.36) --
	(154.61, 84.67) --
	(156.81, 83.97) --
	(159.01, 83.28) --
	(161.20, 82.60) --
	(163.40, 81.91) --
	(165.60, 81.23) --
	(167.79, 80.55) --
	(169.99, 79.87) --
	(172.19, 79.20) --
	(174.38, 78.52) --
	(176.58, 77.85) --
	(178.78, 77.18) --
	(180.97, 76.51) --
	(183.17, 75.85) --
	(185.37, 75.18) --
	(187.56, 74.52) --
	(189.76, 73.86) --
	(191.96, 73.20) --
	(194.15, 72.54) --
	(196.35, 71.88) --
	(198.55, 71.22) --
	(200.74, 70.56) --
	(202.94, 69.91) --
	(205.14, 69.25) --
	(207.33, 68.59) --
	(209.53, 67.94) --
	(211.73, 67.28) --
	(213.92, 66.63);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.71, 30.69) rectangle (222.60,124.59);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76, 30.47) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76, 60.79) {5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76, 91.11) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76,121.43) {15};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96, 33.50) --
	( 31.71, 33.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96, 63.82) --
	( 31.71, 63.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96, 94.14) --
	( 31.71, 94.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,124.46) --
	( 31.71,124.46);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.39, 27.94) --
	( 40.39, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 86.66, 27.94) --
	( 86.66, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (132.94, 27.94) --
	(132.94, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (179.22, 27.94) --
	(179.22, 30.69);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 40.39, 19.68) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 86.66, 19.68) {0.2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (132.94, 19.68) {0.4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (179.22, 19.68) {0.6};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (127.16,  7.64) {Proportion of listed facts};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08, 77.64) {Inference time (s)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (233.60, 21.17) rectangle (298.03,134.11);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at (239.10,119.96) {Algorithm};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (239.10, 98.94) rectangle (253.55,113.39);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 1.1pt,line join=round] (240.54,106.16) -- (252.11,106.16);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (239.10, 84.48) rectangle (253.55, 98.94);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] (240.54, 91.71) -- (252.11, 91.71);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (239.10, 70.03) rectangle (253.55, 84.48);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] (240.54, 77.26) -- (252.11, 77.26);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (239.10, 55.57) rectangle (253.55, 70.03);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] (240.54, 62.80) -- (252.11, 62.80);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (239.10, 41.12) rectangle (253.55, 55.57);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{102,166,30}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 1pt off 3pt ,line join=round] (240.54, 48.35) -- (252.11, 48.35);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (239.10, 26.67) rectangle (253.55, 41.12);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{230,171,2}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 1pt off 3pt on 4pt off 3pt ,line join=round] (240.54, 33.89) -- (252.11, 33.89);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (259.05,103.13) {BDD};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (259.05, 88.68) {d-DNNF};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (259.05, 74.23) {K-Best};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (259.05, 59.77) {NNF};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (259.05, 45.32) {SDD};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (303.53,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (259.05, 30.86) {SDDX};
\end{scope}
\end{tikzpicture}

\end{document}

### 2021-04-13 talks/fata_seminar/talk.tex
One more presentation
Minor changes to presentations

--- 2020-08-16 seminar_talk/talk.tex
@@
 
-\author{Paulius Dilkas}
+% TODO: maybe add a specific date
+\author{\textbf{Paulius Dilkas}\inst{1} \and Vaishak Belle\inst{1,2}}
 \title{Generating Random Logic Programs Using Constraint Programming}
-\date{AIAI Seminar}
+\date{FATA Seminar}
+\institute{\inst{1} University of Edinburgh, Edinburgh, UK \and \inst{2} Alan
+  Turing Institute, London, UK}
 
@@
 \\
-                                         &\textcolor{predicate}{\mathtt{person}}(\textcolor{constant}{\mathit{michelle}}). \\
-                                         &\textcolor{predicate}{\mathtt{person}}(\textcolor{constant}{\mathit{timothy}}). \\
-                                         &\textcolor{predicate}{\mathtt{friend}}(\textcolor{constant}{\mathit{timothy}}, \textcolor{constant}{\mathit{michelle}}).
+                                         &\textcolor{predicate}{\mathtt{person}}(\textcolor{constant}{\mathit{mary}}). \\
+                                         &\textcolor{predicate}{\mathtt{person}}(\textcolor{constant}{\mathit{albert}}). \\
+                                         &\textcolor{predicate}{\mathtt{friend}}(\textcolor{constant}{\mathit{albert}}, \textcolor{constant}{\mathit{mary}}).
     \end{align*}
@@
       $\begin{aligned}[t]
-        \Pr[\textcolor{predicate}{\mathtt{cancer}}(\textcolor{constant}{\mathit{michelle}})]
+        \Pr[\textcolor{predicate}{\mathtt{cancer}}(\textcolor{constant}{\mathit{mary}})]
         &=
-        \Pr[\textcolor{predicate}{\mathtt{cancer\_spont}}(\textcolor{constant}{\mathit{michelle}})]
+        \Pr[\textcolor{predicate}{\mathtt{cancer\_spont}}(\textcolor{constant}{\mathit{mary}})]
         \\
         &\oplus
-        \Pr[\textcolor{predicate}{\mathtt{smokes}}(\textcolor{constant}{\mathit{michelle}})]
+        \Pr[\textcolor{predicate}{\mathtt{smokes}}(\textcolor{constant}{\mathit{mary}})]
         \\
         &\times
-        \Pr[\textcolor{predicate}{\mathtt{cancer\_smoke}}(\textcolor{constant}{\mathit{michelle}})]
+        \Pr[\textcolor{predicate}{\mathtt{cancer\_smoke}}(\textcolor{constant}{\mathit{mary}})]
       \end{aligned}$
@@
     \only<2->{
-      $\Pr[\textcolor{predicate}{\mathtt{cancer}}(\textcolor{constant}{\mathit{michelle}})]
+      $\Pr[\textcolor{predicate}{\mathtt{cancer}}(\textcolor{constant}{\mathit{mary}})]
       = \textcolor{probability}{0.1} \oplus \textcolor{probability}{0.3} \times
-      \Pr[\textcolor{predicate}{\mathtt{smokes}}(\textcolor{constant}{\mathit{michelle}})]$
+      \Pr[\textcolor{predicate}{\mathtt{smokes}}(\textcolor{constant}{\mathit{mary}})]$
     }
@@
       $\begin{aligned}[t]
-        \Pr[\textcolor{predicate}{\mathtt{smokes}}(\textcolor{constant}{\mathit{michelle}})]
+        \Pr[\textcolor{predicate}{\mathtt{smokes}}(\textcolor{constant}{\mathit{mary}})]
         &=
-        \Pr[\textcolor{predicate}{\mathtt{stress}}(\textcolor{constant}{\mathit{michelle}})]
+        \Pr[\textcolor{predicate}{\mathtt{stress}}(\textcolor{constant}{\mathit{mary}})]
         \\
         &\oplus
-        \Pr[\textcolor{predicate}{\mathtt{smokes}}(\textcolor{constant}{\mathit{timothy}})]
+        \Pr[\textcolor{predicate}{\mathtt{smokes}}(\textcolor{constant}{\mathit{albert}})]
         \\
         &\times
-        \Pr[\textcolor{predicate}{\mathtt{influences}}(\textcolor{constant}{\mathit{timothy}},
-        \textcolor{constant}{\mathit{michelle}})]
+        \Pr[\textcolor{predicate}{\mathtt{influences}}(\textcolor{constant}{\mathit{albert}},
+        \textcolor{constant}{\mathit{mary}})]
       \end{aligned}$
@@
     \only<4->{
-      $\Pr[\textcolor{predicate}{\mathtt{smokes}}(\textcolor{constant}{\mathit{michelle}})]
+      $\Pr[\textcolor{predicate}{\mathtt{smokes}}(\textcolor{constant}{\mathit{mary}})]
       = \textcolor{probability}{0.2} \oplus \textcolor{probability}{0.3} \times
-      \Pr[\textcolor{predicate}{\mathtt{smokes}}(\textcolor{constant}{\mathit{timothy}})]$
+      \Pr[\textcolor{predicate}{\mathtt{smokes}}(\textcolor{constant}{\mathit{albert}})]$
     }
@@
     \only<5->{
-      $\Pr[\textcolor{predicate}{\mathtt{smokes}}(\textcolor{constant}{\mathit{timothy}})]
+      $\Pr[\textcolor{predicate}{\mathtt{smokes}}(\textcolor{constant}{\mathit{albert}})]
       =
-      \Pr[\textcolor{predicate}{\mathtt{stress}}(\textcolor{constant}{\mathit{timothy}})]
+      \Pr[\textcolor{predicate}{\mathtt{stress}}(\textcolor{constant}{\mathit{albert}})]
       = \textcolor{probability}{0.2}$
@@
     \[
-      \textcolor{predicate}{\mathtt{cancer}}(\textcolor{constant}{\mathit{michelle}})
+      \textcolor{predicate}{\mathtt{cancer}}(\textcolor{constant}{\mathit{mary}})
       = \alt<5>{\alert{\bot}}{\top}
@@
                                                                                                    &\alt<3-5>{\hbox{\st{$\textcolor{predicate}{\mathtt{cancer}}(\textcolor{variable}{\mathsf{P}}) \ifff \textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{P}}), \textcolor{predicate}{\mathtt{cancer\_smoke}}(\textcolor{variable}{\mathsf{P}}).$}}}{\textcolor{predicate}{\mathtt{cancer}}(\textcolor{variable}{\mathsf{P}}) \ifff \textcolor{predicate}{\mathtt{smokes}}(\textcolor{variable}{\mathsf{P}}), \textcolor{predicate}{\mathtt{cancer\_smoke}}(\textcolor{variable}{\mathsf{P}}).} \\
-                                                                                                   &\textcolor{predicate}{\mathtt{person}}(\textcolor{constant}{\mathit{michelle}}). \\
-                                                                                                   &\textcolor{predicate}{\mathtt{person}}(\textcolor{constant}{\mathit{timothy}}). \\
-                                                                                                   &\textcolor{predicate}{\mathtt{friend}}(\textcolor{constant}{\mathit{timothy}}, \textcolor{constant}{\mathit{michelle}}).
+                                                                                                   &\textcolor{predicate}{\mathtt{person}}(\textcolor{constant}{\mathit{mary}}). \\
+                                                                                                   &\textcolor{predicate}{\mathtt{person}}(\textcolor{constant}{\mathit{albert}}). \\
+                                                                                                   &\textcolor{predicate}{\mathtt{friend}}(\textcolor{constant}{\mathit{albert}}, \textcolor{constant}{\mathit{mary}}).
   \end{align*}
@@
       \begin{itemize}
-      \item[\visible<4->{\xmark}\visible<5->{\xmark}]<3-> $(A \lor C) \land (A \lor \neg B)$
-      \item[\visible<7->{\xmark}\visible<8->{\cmark}]<6-> $C \land (A \lor \neg B)$
-      \item[\visible<10->{\cmark}\visible<11->{\xmark}]<9-> $B \land C \land [(B \land A) \lor \neg B]$
-      \item[\visible<13->{\cmark}\visible<14->{\cmark}]<12-> $C \land [(B \land A) \lor \neg B]$
+      \item[\xmark\xmark]<3-> $(A \lor C) \land (A \lor \neg B)$
+      \item[\xmark\cmark]<4-> $C \land (A \lor \neg B)$
+      \item[\cmark\xmark]<5-> $B \land C \land [(B \land A) \lor \neg B]$
+      \item[\cmark\cmark]<6-> $C \land [(B \land A) \lor \neg B]$
       \end{itemize}
@@
 \\
-                                         &\textcolor<2->{predicate}{\mathtt{person}}(\textcolor<4->{constant}{\mathit{michelle}}). \\
-                                         &\textcolor<2->{predicate}{\mathtt{person}}(\textcolor<4->{constant}{\mathit{timothy}}). \\
-                                         &\textcolor<2->{predicate}{\mathtt{friend}}(\textcolor<4->{constant}{\mathit{timothy}}, \textcolor<4->{constant}{\mathit{michelle}}).
+                                         &\textcolor<2->{predicate}{\mathtt{person}}(\textcolor<4->{constant}{\mathit{mary}}). \\
+                                         &\textcolor<2->{predicate}{\mathtt{person}}(\textcolor<4->{constant}{\mathit{albert}}). \\
+                                         &\textcolor<2->{predicate}{\mathtt{friend}}(\textcolor<4->{constant}{\mathit{albert}}, \textcolor<4->{constant}{\mathit{mary}}).
         \end{align*}
@@
 \end{frame}
-
-% 1. Formula
-% 2. Tree
-% 3. First two rows
-% 4. s is a forest
-% 5. first digit
-% 6. sorted, implication
-% 7. length, number of nodes, for
-% 8. third row, last 3 constraints
 
@@
       \begin{itemize}
-      \item<6-> $\alert{\mathbf{s}}$ is sorted
-      \item<6-> $\alert{\mathbf{s}_i \ne i} \implies \alert{\mathbf{v}_i \ne \top}$
+      \item<6-> $\structure{\mathbf{s}}$ is sorted
+      \item<6-> $\structure{\mathbf{s}_i \ne i} \implies \structure{\mathbf{v}_i \ne \top}$
       \end{itemize}
@@
           \cline{2-8}
-          $\alert{\mathbf{s}}\colon$ & \alert<5->{0} & 0 & 0 & 1 & 2 & 2 & 6 \\
+          $\structure{\mathbf{s}}\colon$ & \alert<5->{0} & 0 & 0 & 1 & 2 & 2 & 6 \\
           \cline{2-8}
-          $\alert{\mathbf{v}}\colon$ & $\lor$ & $\neg$ & $\land$ & $\textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{X}})$ & $\textcolor{predicate}{\mathtt{q}}(\textcolor{variable}{\mathsf{X}})$ & $\textcolor{predicate}{\mathtt{r}}(\textcolor{variable}{\mathsf{X}})$ & $\top$ \\
+          $\structure{\mathbf{v}}\colon$ & $\lor$ & $\neg$ & $\land$ & $\textcolor{predicate}{\mathtt{p}}(\textcolor{variable}{\mathsf{X}})$ & $\textcolor{predicate}{\mathtt{q}}(\textcolor{variable}{\mathsf{X}})$ & $\textcolor{predicate}{\mathtt{r}}(\textcolor{variable}{\mathsf{X}})$ & $\top$ \\
           \cline{2-8}
-          \onslide<8->{$\alert{\mathbf{c}}\colon$ & 2 & 1 & 2 & 0 & 0 & 0 & 0 \\ \cline{2-8}}
+          \onslide<8->{$\structure{\mathbf{c}}\colon$ & 2 & 1 & 2 & 0 & 0 & 0 & 0 \\ \cline{2-8}}
         \end{tabular}
@@
       \begin{itemize}
-      \item<4-> $\alert{\mathbf{s}}$ is a forest with $\alert{T = 2}$ trees
-      \item<7-> length \alert{$L = 7$}
-      \item<7-> number of nodes \alert{$N \coloneqq L - T + 1 = 6$}
-      \item<7-> for \alert{$i = 1, \dots, L - 1$},
-        \begin{itemize}
-        \item if \alert{$i < N$}, then \alert{$\mathbf{s}_i < i$}
-        \item else \alert{$\mathbf{s}_i = i$} and \alert{$\mathbf{v}_i = \top$}
-        \end{itemize}
-      \item<8-> $\alert{\mathbf{c}_i = 0} \iff \alert{\mathbf{v}_i = \top}$ or is a predicate
-      \item<8-> $\alert{\mathbf{c}_i = 1} \iff \alert{\mathbf{v}_i = \neg}$
-      \item<8-> $\alert{\mathbf{c}_i > 1} \iff \alert{\mathbf{v}_i \in \{ \land, \lor \}}$
+      \item<4-> $\structure{\mathbf{s}}$ is a forest with $\structure{T = 2}$ trees
+      \item<7-> length \structure{$L = 7$}
+      \item<7-> number of nodes \structure{$N \coloneqq L - T + 1 = 6$}
+      \item<7-> for \structure{$i = 1, \dots, L - 1$},
+        \begin{itemize}
+        \item if \structure{$i < N$}, then \structure{$\mathbf{s}_i < i$}
+        \item else \structure{$\mathbf{s}_i = i$} and \structure{$\mathbf{v}_i = \top$}
+        \end{itemize}
+      \item<8-> $\structure{\mathbf{c}_i = 0} \iff \structure{\mathbf{v}_i =
+          \top}$ or an atom
+      \item<8-> $\structure{\mathbf{c}_i = 1} \iff \structure{\mathbf{v}_i = \neg}$
+      \item<8-> $\structure{\mathbf{c}_i > 1} \iff \structure{\mathbf{v}_i \in \{ \land, \lor \}}$
       \end{itemize}
@@
 \begin{frame}{Variable Symmetry Breaking}
-  \begin{block}{The Problem}
+%  \begin{block}{The Problem}
     Let $\{ \textcolor{variable}{\mathsf{W}}, \textcolor{variable}{\mathsf{X}},
@@
     \]
-  \end{block}
+%  \end{block}
 \end{frame}
@@
       \begin{itemize}
-      \item<3-> \alert{Stratum 1}: predicates with no negation
-      \item<3-> \alert{Stratum 2}: new predicates s.t. negative literals refer to
-        predicates in \alert{Stratum~1}
+      \item<3-> \structure{Stratum 1}: predicates with no negation
+      \item<3-> \structure{Stratum 2}: new predicates s.t. negative literals refer to
+        predicates in \structure{Stratum~1}
       \end{itemize}
@@
 
-\begin{frame}{How Predicate Independence Affects Search Complexity}
-  \centering
-  \includegraphics{phase_transition.pdf}
-\end{frame}
+%\begin{frame}{How Predicate Independence Affects Search Complexity}
+%  \centering
+%  \includegraphics{phase_transition.pdf}
+%\end{frame}
 
@@
       \item e.g.,
-        $\textcolor{predicate}{\mathtt{friend}}(\textcolor{constant}{\mathit{timothy}},
-        \textcolor{constant}{\mathit{michelle}}).$
+        $\textcolor{predicate}{\mathtt{friend}}(\textcolor{constant}{\mathit{albert}},
+        \textcolor{constant}{\mathit{mary}}).$
       \end{itemize}
@@
   \[
-    \textcolor{predicate}{\mathtt{friend}}(\textcolor{constant}{\mathit{timothy}},
-    \textcolor{constant}{\mathit{michelle}}).
+    \textcolor{predicate}{\mathtt{friend}}(\textcolor{constant}{\mathit{albert}},
+    \textcolor{constant}{\mathit{mary}}).
   \]
@@
   \centering
-  \input{../paper/bars.tex}
+  \input{../../paper/bars.tex}
 \end{frame}
@@
 
-\section{Conclusions}
-
-\begin{frame}{Conclusions and Future Work}
+\section{Summary}
+
+\begin{frame}{Summary}
   \begin{itemize}
@@
     \begin{itemize}
-    \item Can the model be used to ensure uniform sampling?
-    \item What is the reason behind all algorithms behaving similarly?
+    \item Can we ensure uniform sampling?
+    \item Why do all of the algorithms behave so similarly?
     \item Why does independence have no effect on inference time?
-    \item Can random program generation be useful in learning?
-    \end{itemize}
-  \end{itemize}
-  \begin{block}{The implementation of the model is available at}
-    \url{https://github.com/dilkas/random-logic-programs}
-  \end{block}
+%    \item Can random program generation be useful in learning?
+    \end{itemize}
+  \end{itemize}
+%  \begin{block}{The implementation of the model is available at}
+%    \url{https://github.com/dilkas/random-logic-programs}
+%  \end{block}
 \end{frame}

### 2022-06-28 scripts/analyse_model.R
New plots (and some minor changes)

@@ -119,12 +119,19 @@ mytolatex <- function(name) {
   }
 }
 
-# reformat the table to have 3 columns: parameter_name, value (1, 2, 4, 8), and mean of nodes
-effects <- data.frame(Variable = factor(), Value = integer(), mean = numeric(), aritylabel = character())
-factors <- c('numPredicates', 'maxArity', 'numVariables', 'numConstants', 'numAdditionalClauses', 'maxNumNodes')
-labels <- c("$|\\mathcal{P}|$", "$\\mathcal{M}_{\\mathcal{A}}$", "$|\\mathcal{V}|$", "$|\\mathcal{C}|$", "$\\mathcal{M}_{\\mathcal{C}}-|\\mathcal{P}|$", "$\\mathcal{M}_{\\mathcal{N}}$")
+# reformat the table to have 3 columns: parameter_name, value (1, 2, 4, 8),
+# and mean of nodes
+effects <- data.frame(Variable = factor(), Value = integer(),
+                      mean = numeric(), aritylabel = character())
+factors <- c('numPredicates', 'maxArity', 'numVariables', 'numConstants',
+             'numAdditionalClauses', 'maxNumNodes')
+labels <- c("$|\\mathcal{P}|$", "$\\mathcal{M}_{\\mathcal{A}}$",
+            "$|\\mathcal{V}|$", "$|\\mathcal{C}|$",
+            "$\\mathcal{M}_{\\mathcal{C}}-|\\mathcal{P}|$",
+            "$\\mathcal{M}_{\\mathcal{N}}$")
 for (Variable in factors) {
-  foo <- df %>% group_by_at(Variable) %>% summarise(mean(nodes)) %>% rename(Value = Variable, mean = "mean(nodes)")
+  foo <- df %>% group_by_at(Variable) %>% summarise(mean(nodes)) %>%
+    rename(Value = Variable, mean = "mean(nodes)")
 #  foo$Variable <- factor(Variable, levels = factors, labels = labels)
   foo$Variable <- as.factor(Variable)
   foo$aritylabel <- ""
@@ -134,18 +141,20 @@ effects$label <- ifelse(effects$Value == 8, sapply(as.character(effects$Variable
 effects$aritylabel[effects$Variable == "maxArity" & effects$Value == 4] <- "$\\mathcal{M}_{\\mathcal{A}}$"
 
 # Paper version
-tikz(file = "../paper/impact.tex", width = 2.4, height = 1.8)
[…]

### 2022-06-28 scripts/analyse_problog.R

@@ -92,7 +92,8 @@ get_legend <- function(myggplot){
 }
 
 plot <- function(var.name, c, s, scale = F, dots = T, legend = F, smooth = F,
-                 breaks = NULL, labels = NULL, ylims = NULL, separated = F, disable.y.axis = T, ribbon.size = 0.1) {
+                 breaks = NULL, labels = NULL, ylims = NULL, separated = F,
+                 disable.y.axis = T, ribbon.size = 0.1) {
   if (smooth) {
     data <- c[c$variable == var.name,]
     y <- data$Total.time
@@ -101,10 +102,11 @@ plot <- function(var.name, c, s, scale = F, dots = T, legend = F, smooth = F,
     y <- data$mean.time
   }
 
-  p <- ggplot(data = data, aes(x = value, y = y, color = Algorithm, fill = Algorithm, linetype = Algorithm)) +
+  p <- ggplot(data = data, aes(x = value, y = y, color = Algorithm,
+                               fill = Algorithm, linetype = Algorithm)) +
     xlab(pretty_names[relevant_columns == var.name]) +
     ylab("Total time (s)") +
-    theme_bw() +
+    theme_bw(base_size = 9) +
     scale_colour_brewer(palette = "Dark2") +
     scale_fill_brewer(palette = "Dark2")
 
@@ -202,27 +204,33 @@ summary <- rbind(summarised2[summarised2$variable %in% c("proportion.independent
 
 # ===================== Camera-ready ================================
 
-plot2 <- function(df, column.names, df2 = NULL, column.names2 = NULL, factors = T, replace.labels = T) {
+plot2 <- function(df, column.names, df2 = NULL, column.names2 = NULL,
+                  factors = T, replace.labels = T) {
   smaller <- df[df$variable %in% column.names,]
   smaller$value <- as.factor(smaller$value)
-  smaller$variable <- ifelse(smaller$variable == "maximum.arity", "Maximum arity", "Probabilistic")
+  smaller$variable <- ifelse(smaller$variable == "maximum.arity",
+                             "Maximum arity", "Probabilistic")
   p <- ggplot(smaller, aes(x = value, y = Total.time, group = value))
   p <- p + geom_boxplot(outlier.shape = 4, outlier.alpha = 0.25)
   p + facet_wrap(~ variable, scales = "free_x") +
     scale_x_discrete() +
[…]
